### 2015-10-04 ComparisonsMain.Rmd
Add Comparisons.Rmd

---
title: "Comparaciones Teórico-Experimental"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning=FALSE,echo=FALSE,message=FALSE)
```

```{r}
#Remove objects#
rm (list=ls())

#Read Input#
input <- read.csv("DATA/InputComp.csv")

family <- input$family[1]
p.ref <- input$p.ref[1]
heme <- input$heme[1]
index = as.vector(input$index)

if (family == "Globins"){
  family <- paste(family,"Heme",heme,sep ="")
  p.ref <- paste(p.ref,"Heme",heme,sep ="")
}

#Nmodes to analyze#
nmodes1 = 10 
nmodes2 = 25
nmodes3 = 50
nmodes4 = 100

#Load librarys# 
library(flux) #function "auc"#

#Read files#
dir.t <- "OUT/Theoretical"
dir.e <- "OUT/Experimental"

df.Pnt = read.csv(file.path(dir.t,paste(p.ref,".Out.df.Pn.csv",sep="")))[,1:nmodes4]
df.Qnt = t(apply(df.Pnt,1,cumsum))
evalues = read.csv(file.path(dir.t,paste(p.ref,".Out.evalues.csv",sep="")))$x[1:nmodes4]
ievalues = 1/evalues

df.Pne = read.csv(file.path(dir.e,paste(family,".Out.df.Pn.csv",sep="")))[index,1:nmodes4]
df.Qne = t(apply(df.Pne,1,cumsum))

df.evaluese = read.csv(file.path(dir.e,paste(family,".Out.df.evalues.csv",sep="")))[index,1:nmodes4]
evaluese = colMeans(df.evaluese)
ievaluese = 1/evaluese

lalign = read.csv(file.path(dir.e,paste(family,".Out.df.lalign.csv",sep="")))$x
MSD = read.csv(file.path(dir.e,paste(family,".Out.MSD.csv",sep="")))$x
id = read.csv(file.path(dir.e,paste(family,".Out.df.ID.csv",sep="")))$x
id.index = id[index]
pdbid <- read.csv(file.path("DATA/Experimental",paste(family,"Dataset.csv",sep="")))$pdbid
pdbid <- pdbid[pdbid!=as.character(p.ref)]

#Number of t and e proteins#
nmut = nrow(df.Pnt)
nexp = length(index)

#Number of t groups#
ngroups = as.integer(nmut/nexp)

```

Conjunto teórico: `r nmut` mutantes de `r p.ref` de `r id.index` % de identidad secuencial con ANM R0 = 12 y Fmax= 2. Se seleccionó esta proteína ya que es la que presenta menor MSD con respecto a las coordenadas xyz promedio de todas las proteínas del conjunto experimental. El porcentaje de mutaciones se seleccionó de acuerdo al promedio de identidad secuencial de proteínas del conjunto experimental.

Conjunto experimental: `r nexp` proteínas de la familia de `r family`.Las proteínas tienen un promedio de identidad secuencial de `r id.index`. Todas las proteínas del sub-conjunto elegidas alinean en todos los sitios de `r p.ref`, o en como máximo 1 sitio menos.
```{r}

#Analysis experimental dataset#

layout(matrix(1:4,2,2,byrow=T))

  hist(id,main="%ID con referencia",col="grey")
  hist(lalign,main="Número de sitios alineados con referencia",col="grey")
  hist(MSD,main="MSD con la referencia",col="grey")
  plot(id,MSD,xlab = "%ID", main ="MSD vs. %ID")

  caract <- data.frame(pdbid,id,lalign,MSD)
  caract
```

```{r, echo = FALSE, warning=FALSE, message=FALSE}

  #rho#

   rho.t.1 <- matrix(0,nrow=nmut,ncol=1)
   rho.t.2 <- matrix(0,nrow=nmut,ncol=1)
   rho.t.3 <- matrix(0,nrow=nmut,ncol=1)
   rho.t.4 <- matrix(0,nrow=nmut,ncol=1)

  for (i in (1: nmut)){
	  rho.t.1[i,] <- cor((as.vector(as.matrix(df.Pnt[i,1:nmodes1]))*evalues[1:nmodes1]),ievalues[1:nmodes1],method="pearson")	
	  rho.t.2[i,] <- cor((as.vector(as.matrix(df.Pnt[i,1:nmodes2]))*evalues[1:nmodes2]),ievalues[1:nmodes2],method="pearson")	   
	  rho.t.3[i,] <- cor((as.vector(as.matrix(df.Pnt[i,1:nmodes3]))*evalues[1:nmodes3]),ievalues[1:nmodes3],method="pearson")	  
	  rho.t.4[i,] <- cor((as.vector(as.matrix(df.Pnt[i,1:nmodes4]))*evalues[1:nmodes4]),ievalues[1:nmodes4],method="pearson")	   
  }

  rho.e.1 <- matrix(0,nrow=nexp,ncol=1)
  rho.e.2 <- matrix(0,nrow=nexp,ncol=1)
  rho.e.3 <- matrix(0,nrow=nexp,ncol=1) 
  rho.e.4 <- matrix(0,nrow=nexp,ncol=1)

  for (i in (1: nexp)){
	  rho.e.1[i,] <- cor((as.vector(as.matrix(df.Pne[i,1:nmodes1]))*evaluese[1:nmodes1]),ievaluese[1:nmodes1],method="pearson")
	  rho.e.2[i,] <- cor((as.vector(as.matrix(df.Pne[i,1:nmodes2]))*evaluese[1:nmodes2]),ievaluese[1:nmodes2],method="pearson")
	  rho.e.3[i,] <- cor((as.vector(as.matrix(df.Pne[i,1:nmodes3]))*evaluese[1:nmodes3]),ievaluese[1:nmodes3],method="pearson")
	  rho.e.4[i,] <- cor((as.vector(as.matrix(df.Pne[i,1:nmodes4]))*evaluese[1:nmodes4]),ievaluese[1:nmodes4],method="pearson")
  }

  #auc#
  auc.t.1 <- matrix(0,nrow=nmut,ncol=1)
  auc.t.2 <- matrix(0,nrow=nmut,ncol=1)
  auc.t.3 <- matrix(0,nrow=nmut,ncol=1)
  auc.t.4 <- matrix(0,nrow=nmut,ncol=1)

  for (i in (1:nmut)){
	  auc.t.1[i,] <- auc(seq(1:nmodes1),df.Qnt[i,1:nmodes1])
	  auc.t.2[i,] <- auc(seq(1:nmodes2),df.Qnt[i,1:nmodes2])
	  auc.t.3[i,] <- auc(seq(1:nmodes3),df.Qnt[i,1:nmodes3])
	  auc.t.4[i,] <- auc(seq(1:nmodes4),df.Qnt[i,1:nmodes4])
  }

  auc.e.1 <- matrix(0,nrow=nexp,ncol=1)
  auc.e.2 <- matrix(0,nrow=nexp,ncol=1)
  auc.e.3 <- matrix(0,nrow=nexp,ncol=1)
  auc.e.4 <- matrix(0,nrow=nexp,ncol=1)

  for (i in (1:nexp)){
	  auc.e.1[i,] <- auc(seq(1:nmodes1),df.Qne[i,1:nmodes1])
	  auc.e.2[i,] <- auc(seq(1:nmodes2),df.Qne[i,1:nmodes2])
	  auc.e.3[i,] <- auc(seq(1:nmodes3),df.Qne[i,1:nmodes3])
	  auc.e.4[i,] <- auc(seq(1:nmodes4),df.Qne[i,1:nmodes4])
  }
```

Las distribuciones de auc y rho para cada conjunto se muestran a continuación (azul= teórico, rojo = experimental)

```{r}

layout(matrix(1:4,2,2,byrow=T))

plot(density(rho.t.1),col="blue",ylab="Frecuencia",xlab="rho",main="Histograma rho 10 modos")
points(x=c(rho.e.1),y=rep(0,nexp),col="red")

plot(density(auc.t.1),col="blue",ylab="Frecuencia",xlab="auc",main="Histograma auc 10 modos")
points(x=c(auc.e.1),y=rep(0,nexp),col="red")

plot(density(rho.t.2),col="blue",ylab="Frecuencia",xlab="rho",main="Histograma rho 25 modos")
points(x=c(rho.e.2),y=rep(0,nexp),col="red")

plot(density(auc.t.2),col="blue",ylab="Frecuencia",xlab="auc",main="Histograma auc 25 modos")
points(x=c(auc.e.2),y=rep(0,nexp),col="red")
```

```{r}
layout(matrix(1:4,2,2,byrow=T))

plot(density(rho.t.3),col="blue",ylab="Frecuencia",xlab="rho",main="Histograma rho 50 modos")
points(x=c(rho.e.3),y=rep(0,nexp),col="red")

plot(density(auc.t.3),col="blue",ylab="Frecuencia",xlab="auc",main="Histograma auc 50 modos")
points(x=c(auc.e.3),y=rep(0,nexp),col="red")

plot(density(rho.t.4),col="blue",ylab="Frecuencia",xlab="rho",main="Histograma rho 100 modos")
points(x=c(rho.e.4),y=rep(0,nexp),col="red")

plot(density(auc.t.4),col="blue",ylab="Frecuencia",xlab="auc",main="Histograma auc 100 nmodos")
points(x=c(auc.e.4),y=rep(0,nexp),col="red")

```

Las distribuciones de Pn y Qn de los conjuntos son las siguientes:

```{r}

#Calculate groups#

source("FUNCTIONS/mean.groups.R")

Pne.mean = colMeans(df.Pne)
Qne.mean = colMeans(df.Qne)

Pntgroup <- mean.groups(ngroups,nexp,df.Pnt)
df.Pntgroup <- Pntgroup$mean.group
Pntgroup.mean <- Pntgroup$mean.total
Pntgroup.quantile5 <- Pntgroup$quantile[1,]
Pntgroup.quantile95 <- Pntgroup$quantile[2,]

Qntgroup <- mean.groups(ngroups,nexp,df.Qnt)
df.Qntgroup <- Qntgroup$mean.group
Qntgroup.mean <- Qntgroup$mean.total
Qntgroup.quantile5 <- Qntgroup$quantile[1,]
Qntgroup.quantile95 <- Qntgroup$quantile[2,]

layout(matrix(1:2,1,2,byrow=T))

plot(Pntgroup.mean,ylab ="Pn promedio", xlab = "nmodo",type="l",ylim=c(0,0.07),main="Pn promedio vs. nmodo")
lines(Pntgroup.quantile5,col="green")
lines(Pntgroup.quantile95,col="green")
points(Pne.mean,col="red")

plot(Qntgroup.mean,ylab ="Qn promedio", xlab = "nmodo",type="l",ylim=c(0,0.7),main ="Qn promedio vs. nmodo")
lines(Qntgroup.quantile5,col="green")
lines(Qntgroup.quantile95,col="green")
points(Qne.mean,col="red")
```

Negro: Teorico
Rojo: Experimental
Verdes: cuartiles 0.05 y 0.95 de 100 grupos de 7 mutantes te?ricas

### 2015-10-05 ComparisonsMain.Rmd
cambios

@@
+# INFORMACIÓN
+# este programa genera un archivo HTLM comparando la divergencia etsructural de proteínas
+# experimentales y mutantes teóricas.
+# Para correrlo se debe completar un Input ("DATA/inputComp.csv") especificando:
+# -family: la familia de proteínas a comparar, debe estar escrita consistentemente con los
+# archivos inputT e inputE (Ingés y plural).
+# -p.ref: la proteína dereferencia de la familia, que debe ser consisntente con el archivo 
+# inputE, es decir que se debe escribir de la forma en la que está escrita en el Dataset.
+# -heme: solo se utiliza para la familia de las globinas, puede ser "TRUE" o "FALSE" 
+# dependiendo de si se quiere considerar o no al grupo HEMO. 
+# -index: el índice de las proteínas de la familia que se desea analizar.
 ---
-title: "Comparaciones Teórico-Experimental"
+title: "Comparaciones"
 output: html_document
 ---
-
 ```{r setup, include=FALSE}
@@
   family <- paste(family,"Heme",heme,sep ="")
-  p.ref <- paste(p.ref,"Heme",heme,sep ="")
 }
@@
 dir.t <- "OUT/Theoretical"
-dir.e <- "OUT/Experimental"
-
-df.Pnt = read.csv(file.path(dir.t,paste(p.ref,".Out.df.Pn.csv",sep="")))[,1:nmodes4]
-df.Qnt = t(apply(df.Pnt,1,cumsum))
-evalues = read.csv(file.path(dir.t,paste(p.ref,".Out.evalues.csv",sep="")))$x[1:nmodes4]
+m.Pnt = read.csv(file.path(dir.t,paste(family,".Out.m.Pn.csv",sep="")))[,1:nmodes4]
+m.Qnt = t(apply(m.Pnt,1,cumsum))
+evalues = read.csv(file.path(dir.t,paste(family,".Out.evalues.csv",sep="")))$x[1:nmodes4]
 ievalues = 1/evalues
 
-df.Pne = read.csv(file.path(dir.e,paste(family,".Out.df.Pn.csv",sep="")))[index,1:nmodes4]
-df.Qne = t(apply(df.Pne,1,cumsum))
-
-df.evaluese = read.csv(file.path(dir.e,paste(family,".Out.df.evalues.csv",sep="")))[index,1:nmodes4]
-evaluese = colMeans(df.evaluese)
+dir.e <- "OUT/Experimental"
+m.Pne = read.csv(file.path(dir.e,paste(family,".Out.m.Pn.csv",sep="")))[index,1:nmodes4]
+m.Qne = t(apply(m.Pne,1,cumsum))
+m.evaluese = read.csv(file.path(dir.e,paste(family,".Out.m.evalues.csv",sep="")))[index,1:nmodes4]
+evaluese = colMeans(m.evaluese)
 ievaluese = 1/evaluese
 
-lalign = read.csv(file.path(dir.e,paste(family,".Out.df.lalign.csv",sep="")))$x
+lalign = read.csv(file.path(dir.e,paste(family,".Out.m.lalign.csv",sep="")))$x
 MSD = read.csv(file.path(dir.e,paste(family,".Out.MSD.csv",sep="")))$x
-id = read.csv(file.path(dir.e,paste(family,".Out.df.ID.csv",sep="")))$x
+id = read.csv(file.path(dir.e,paste(family,".Out.m.ID.csv",sep="")))$x
 id.index = id[index]
@@
 #Number of t and e proteins#
-nmut = nrow(df.Pnt)
+nmut = nrow(m.Pnt)
 nexp = length(index)
@@
   for (i in (1: nmut)){
-	  rho.t.1[i,] <- cor((as.vector(as.matrix(df.Pnt[i,1:nmodes1]))*evalues[1:nmodes1]),ievalues[1:nmodes1],method="pearson")	
-	  rho.t.2[i,] <- cor((as.vector(as.matrix(df.Pnt[i,1:nmodes2]))*evalues[1:nmodes2]),ievalues[1:nmodes2],method="pearson")	   
-	  rho.t.3[i,] <- cor((as.vector(as.matrix(df.Pnt[i,1:nmodes3]))*evalues[1:nmodes3]),ievalues[1:nmodes3],method="pearson")	  
-	  rho.t.4[i,] <- cor((as.vector(as.matrix(df.Pnt[i,1:nmodes4]))*evalues[1:nmodes4]),ievalues[1:nmodes4],method="pearson")	   
+	  rho.t.1[i,] <- cor((as.vector(as.matrix(m.Pnt[i,1:nmodes1]))*evalues[1:nmodes1]),ievalues[1:nmodes1],method="pearson")	
+	  rho.t.2[i,] <- cor((as.vector(as.matrix(m.Pnt[i,1:nmodes2]))*evalues[1:nmodes2]),ievalues[1:nmodes2],method="pearson")	   
+	  rho.t.3[i,] <- cor((as.vector(as.matrix(m.Pnt[i,1:nmodes3]))*evalues[1:nmodes3]),ievalues[1:nmodes3],method="pearson")	  
+	  rho.t.4[i,] <- cor((as.vector(as.matrix(m.Pnt[i,1:nmodes4]))*evalues[1:nmodes4]),ievalues[1:nmodes4],method="pearson")	   
   }
@@
   for (i in (1: nexp)){
-	  rho.e.1[i,] <- cor((as.vector(as.matrix(df.Pne[i,1:nmodes1]))*evaluese[1:nmodes1]),ievaluese[1:nmodes1],method="pearson")
-	  rho.e.2[i,] <- cor((as.vector(as.matrix(df.Pne[i,1:nmodes2]))*evaluese[1:nmodes2]),ievaluese[1:nmodes2],method="pearson")
-	  rho.e.3[i,] <- cor((as.vector(as.matrix(df.Pne[i,1:nmodes3]))*evaluese[1:nmodes3]),ievaluese[1:nmodes3],method="pearson")
-	  rho.e.4[i,] <- cor((as.vector(as.matrix(df.Pne[i,1:nmodes4]))*evaluese[1:nmodes4]),ievaluese[1:nmodes4],method="pearson")
+	  rho.e.1[i,] <- cor((as.vector(as.matrix(m.Pne[i,1:nmodes1]))*evaluese[1:nmodes1]),ievaluese[1:nmodes1],method="pearson")
+	  rho.e.2[i,] <- cor((as.vector(as.matrix(m.Pne[i,1:nmodes2]))*evaluese[1:nmodes2]),ievaluese[1:nmodes2],method="pearson")
+	  rho.e.3[i,] <- cor((as.vector(as.matrix(m.Pne[i,1:nmodes3]))*evaluese[1:nmodes3]),ievaluese[1:nmodes3],method="pearson")
+	  rho.e.4[i,] <- cor((as.vector(as.matrix(m.Pne[i,1:nmodes4]))*evaluese[1:nmodes4]),ievaluese[1:nmodes4],method="pearson")
   }
@@
   for (i in (1:nmut)){
-	  auc.t.1[i,] <- auc(seq(1:nmodes1),df.Qnt[i,1:nmodes1])
-	  auc.t.2[i,] <- auc(seq(1:nmodes2),df.Qnt[i,1:nmodes2])
-	  auc.t.3[i,] <- auc(seq(1:nmodes3),df.Qnt[i,1:nmodes3])
-	  auc.t.4[i,] <- auc(seq(1:nmodes4),df.Qnt[i,1:nmodes4])
+	  auc.t.1[i,] <- auc(seq(1:nmodes1),m.Qnt[i,1:nmodes1])
+	  auc.t.2[i,] <- auc(seq(1:nmodes2),m.Qnt[i,1:nmodes2])
+	  auc.t.3[i,] <- auc(seq(1:nmodes3),m.Qnt[i,1:nmodes3])
+	  auc.t.4[i,] <- auc(seq(1:nmodes4),m.Qnt[i,1:nmodes4])
   }
@@
   for (i in (1:nexp)){
-	  auc.e.1[i,] <- auc(seq(1:nmodes1),df.Qne[i,1:nmodes1])
-	  auc.e.2[i,] <- auc(seq(1:nmodes2),df.Qne[i,1:nmodes2])
-	  auc.e.3[i,] <- auc(seq(1:nmodes3),df.Qne[i,1:nmodes3])
-	  auc.e.4[i,] <- auc(seq(1:nmodes4),df.Qne[i,1:nmodes4])
+	  auc.e.1[i,] <- auc(seq(1:nmodes1),m.Qne[i,1:nmodes1])
+	  auc.e.2[i,] <- auc(seq(1:nmodes2),m.Qne[i,1:nmodes2])
+	  auc.e.3[i,] <- auc(seq(1:nmodes3),m.Qne[i,1:nmodes3])
+	  auc.e.4[i,] <- auc(seq(1:nmodes4),m.Qne[i,1:nmodes4])
   }
@@
 
-Pne.mean = colMeans(df.Pne)
-Qne.mean = colMeans(df.Qne)
+Pne.mean = colMeans(m.Pne)
+Qne.mean = colMeans(m.Qne)
 
-Pntgroup <- mean.groups(ngroups,nexp,df.Pnt)
-df.Pntgroup <- Pntgroup$mean.group
+Pntgroup <- mean.groups(ngroups,nexp,m.Pnt)
+m.Pntgroup <- Pntgroup$mean.group
 Pntgroup.mean <- Pntgroup$mean.total
@@
 
-Qntgroup <- mean.groups(ngroups,nexp,df.Qnt)
-df.Qntgroup <- Qntgroup$mean.group
+Qntgroup <- mean.groups(ngroups,nexp,m.Qnt)
+m.Qntgroup <- Qntgroup$mean.group
 Qntgroup.mean <- Qntgroup$mean.total
@@
 Rojo: Experimental
-Verdes: cuartiles 0.05 y 0.95 de 100 grupos de 7 mutantes te?ricas
+Verdes: cuartiles 0.05 y 0.95 de `r ngroups` grupos de `r nexp` mutantes teóricas

### 2015-10-05 ExperimentalMain.R

@@ -6,7 +6,7 @@
 # Para utilizar el programa se debe completar un input ("DATA/Experimental/inputE.csv") especificando: 
 # -family:la familia de proteínas del alineamiento, que puede ser "SerinProteases", "Globins" o "Plastocyanins"
 # -p.ref: la proteína de referncia que se desee utilizar, teniendo en cuenta que la misma debe ser escrita de 
-# la msima forma en la que se encuentra en el dataset.
+# la misma forma en la que se encuentra en el dataset.
 # -heme: solo se utiliza para la familia de las globinas, puede ser "TRUE" o "FALSE", dependiendo de si 
 # se desea o no considerar al grupo HEMO. 
 # -model: el modelo de red elástica a usar, que solo puede ser "ANM" por el momento.
@@ -31,7 +31,7 @@ model <- input$model
 R0 = input$R0
 
 #Files dir#
-align.dir <- file.path(data.dir,paste(family,"Alignments.txt",sep="")) #File with a multiple sequence alignment from Homstrad#
+align.dir <- file.path(data.dir,paste(family,"Alignments.txt",sep="")) #File with a multiple sequence alignmet#
 pdbs.dir <- file.path(data.dir,paste(family,"Coordinates.pdb",sep="")) #Coordinates of the proteins# 
 dataset.dir <- file.path(data.dir,paste(family,"Dataset.csv",sep="")) #Dataset with pdbids and chains# 
 
@@ -75,139 +75,139 @@ nprot = length(pdbids)
 alignments.id <- read.fasta(align.dir)
 alignments <- alignments.id$ali[,-ncol(alignments.id$ali)]
 
-#Read PDB & alignment of P.ref#
-chain.Pref <- chains[pdbids == as.character(p.ref)]
-pdb.Pref <- readCA(pdbs.dir,chain.Pref)
-r.Pref = pdb.Pref$xyz.calpha
-nsites.Pref = pdb.Pref$nsites 
[…]

### 2015-10-07 ComparisonsMain.Rmd
ActualizaciónDatos

@@
-# INFORMACIÓN
-# este programa genera un archivo HTLM comparando la divergencia etsructural de proteínas
-# experimentales y mutantes teóricas.
-# Para correrlo se debe completar un Input ("DATA/inputComp.csv") especificando:
-# -family: la familia de proteínas a comparar, debe estar escrita consistentemente con los
-# archivos inputT e inputE (Ingés y plural).
-# -p.ref: la proteína dereferencia de la familia, que debe ser consisntente con el archivo 
-# inputE, es decir que se debe escribir de la forma en la que está escrita en el Dataset.
-# -heme: solo se utiliza para la familia de las globinas, puede ser "TRUE" o "FALSE" 
-# dependiendo de si se quiere considerar o no al grupo HEMO. 
-# -index: el índice de las proteínas de la familia que se desea analizar.
 ---
-title: "Comparaciones"
+title: "Comparaciones Teórico-Experimental"
 output: html_document
@@
 ```{r}
+
+# INFORMACIÓN
+#
+# este programa genera un archivo HTLM comparando la divergencia etsructural de
+# proteínas experimentales y mutantes teóricas.
+# Para correrlo se debe completar un Input ("DATA/inputComp.csv") especificando:
+# -family: la familia de proteínas a comparar, debe estar escrita consistentemente # con los archivos inputT e inputE (Ingés y plural).
+# -p.ref: la proteína dereferencia de la familia, que debe ser escrita 
+# consisntentemente con el archivo inputE, es decir que debe ser escrita de la 
+# forma en la que está escrita en el Dataset.
+# -heme: solo se utiliza para la familia de las globinas, puede ser "TRUE" o 
+# "FALSE" dependiendo de si se quiere considerar o no al grupo HEMO. 
+# -index: el índice de las proteínas de la familia que se desea analizar.
+
 #Remove objects#
@@
 
-if (family == "Globins"){
-  family <- paste(family,"Heme",heme,sep ="")
-}
-
 #Nmodes to analyze#
@@
 #Read files#
-dir.t <- "OUT/Theoretical"
-m.Pnt = read.csv(file.path(dir.t,paste(family,".Out.m.Pn.csv",sep="")))[,1:nmodes4]
-m.Qnt = t(apply(m.Pnt,1,cumsum))
-evalues = read.csv(file.path(dir.t,paste(family,".Out.evalues.csv",sep="")))$x[1:nmodes4]
-ievalues = 1/evalues
 
 dir.e <- "OUT/Experimental"
+pdbid <- read.csv(file.path("DATA/Experimental",paste(family,"Dataset.csv",sep="")))$pdbid
+pdbid <- pdbid[pdbid!=as.character(p.ref)]
+
+if (as.character(family) == "Globins"){
+  family <- paste(family,"Heme",heme,sep ="")
+}
+
 m.Pne = read.csv(file.path(dir.e,paste(family,".Out.m.Pn.csv",sep="")))[index,1:nmodes4]
@@
 id.index = id[index]
-pdbid <- read.csv(file.path("DATA/Experimental",paste(family,"Dataset.csv",sep="")))$pdbid
-pdbid <- pdbid[pdbid!=as.character(p.ref)]
+
+dir.t <- "OUT/Theoretical"
+m.Pnt = read.csv(file.path(dir.t,paste(family,".Out.m.Pn.csv",sep="")))[,1:nmodes4]
+m.Qnt = t(apply(m.Pnt,1,cumsum))
+evalues = read.csv(file.path(dir.t,paste(family,".Out.evalues.csv",sep="")))$x[1:nmodes4]
+ievalues = 1/evalues
 
@@
 
-Conjunto teórico: `r nmut` mutantes de `r p.ref` de `r id.index` % de identidad secuencial con ANM R0 = 12 y Fmax= 2.
+Conjunto teórico: `r nmut` mutantes de `r p.ref` de `r round(mean(id.index))` % de identidad secuencial con ANM R0 = 12 y Fmax= 2.
 Se seleccionó esta proteína ya que es la que presenta menor MSD con respecto a las coordenadas xyz promedio de todas las proteínas del conjunto experimental.
@@
 
-Conjunto experimental: `r nexp` proteínas de la familia de `r family`.Las proteínas tienen un promedio de identidad secuencial de `r id.index`.
+Conjunto experimental: `r nexp` proteínas de la familia de `r family`.Las proteínas tienen un promedio de identidad secuencial de `r round(mean(id.index))`%.
 Todas las proteínas del sub-conjunto elegidas alinean en todos los sitios de `r p.ref`, o en como máximo 1 sitio menos.
@@
 
-```{r, echo = FALSE, warning=FALSE, message=FALSE}
+```{r}
 
@@
 
-source("FUNCTIONS/mean.groups.R")
+source("FUNCTIONS/Mean.groups.R")
 

### 2015-10-07 TheoreticalMain.R

@@ -7,7 +7,8 @@
 #
 # Para utilizar el programa se debe completar un input ("DATA/Theoretical/inputT.csv") especificando: 
 # -family: la familia de proteínas a la que pertenece la proteína a mutar escrita en inglés y plural 
-# (ej.:"Globins").
+# (ej.:"Globins"). Tener en cuenta que las familias que pueden ser analizadas experimentalmente son
+# "SerinProteases", "Globins" o "Plastocyanins".
 # -p.ref: el código de pdb (pdbid) de la proteína a mutar (ej.:"1a6m")
 # -chain: la cadena de p.ref que se desea mutar.
 # -heme: solo se utiliza para la familia de las globinas, puede ser "TRUE" o "FALSE" dependiendo de 
@@ -171,8 +172,8 @@ write.csv(K.p.ref.2$va,file = file.path(OUT , paste(family , ".Out.evalues.csv" 
 write.csv(mean.nH,file = file.path(OUT , paste(family , ".Out.nH.mean.csv" , sep = "")) , row.names = FALSE)
 write.csv(mean.Pn,file = file.path(OUT , paste(family , ".Out.Pn.mean.csv" , sep = "")) , row.names = FALSE)
 write.csv(mean.d.evalues,file = file.path(OUT , paste(family , ".Out.d.evalues.mean.csv" , sep = "")) , row.names = FALSE)
-write.csv(MSDi,file = file.path(OUT , paste(family , ".Out.dr.squarei.mean.csv" , sep = "")) , row.names = FALSE)
-write.csv(MSD,file = file.path(OUT , paste(family , ".Out.dr.square.mean.csv", sep = "")) , row.names = FALSE)
+write.csv(MSDi,file = file.path(OUT , paste(family , ".Out.MSDi.csv" , sep = "")) , row.names = FALSE)
+write.csv(MSD,file = file.path(OUT , paste(family , ".Out.MSD.csv", sep = "")) , row.names = FALSE)
 
 #input#
 write.csv(input,file = file.path(OUT , paste(family , ".Input" , sep = "")) , row.names = FALSE)

### 2015-10-18 ComparisonsMain.Rmd
agregué lo que faltaba para usar las nuevas funciones

@@
 ```{r}
-
 # INFORMACIÓN
 #
-# este programa genera un archivo HTLM comparando la divergencia etsructural de
+# Este programa genera un archivo HTLM comparando la divergencia etsructural de
 # proteínas experimentales y mutantes teóricas.
-# Para correrlo se debe completar un Input ("DATA/inputComp.csv") especificando:
-# -family: la familia de proteínas a comparar, debe estar escrita consistentemente # con los archivos inputT e inputE (Ingés y plural).
+# Para correrlo se debe completar un Input ("DATA/comp_input.csv") especificando:
+# -family: la familia de proteínas a comparar, debe estar escrita consistentemente 
+# con los archivos theoretical_input y experimental_input.
 # -p.ref: la proteína dereferencia de la familia, que debe ser escrita 
-# consisntentemente con el archivo inputE, es decir que debe ser escrita de la 
-# forma en la que está escrita en el Dataset.
+# consisntentemente con el archivo experimental_input, es decir que debe ser escrita de la 
+# forma en la que está escrita en el dataset.
 # -heme: solo se utiliza para la familia de las globinas, puede ser "TRUE" o 
@@
 # -index: el índice de las proteínas de la familia que se desea analizar.
-
-#Remove objects#
+# Remove objects.
 rm (list=ls())
-
-#Read Input#
-input <- read.csv("DATA/InputComp.csv")
-
+# Read Input.
+input <- read.csv("DATA/comp_input.csv")
 family <- input$family[1]
@@
 index = as.vector(input$index)
-
-#Nmodes to analyze#
+# Nmodes to analyze.
 nmodes1 = 10 
@@
 nmodes4 = 100
-
-#Load librarys# 
-library(flux) #function "auc"#
-
-#Read files#
-
+# Load librarys. 
+library(flux)  # function "auc".
+# Source functions.
+source("FUNCTIONS/CalculateGroupsMeansQuantiles.R")
+# Read files and calculate measures.
+# Experimental.
 dir.e <- "OUT/Experimental"
-pdbid <- read.csv(file.path("DATA/Experimental",paste(family,"Dataset.csv",sep="")))$pdbid
-pdbid <- pdbid[pdbid!=as.character(p.ref)]
-
-if (as.character(family) == "Globins"){
-  family <- paste(family,"Heme",heme,sep ="")
+pdbid <- read.csv(file.path("DATA/Experimental", paste(family, "_dataset.csv", sep = "")))$pdbid
+pdbid <- pdbid[pdbid != as.character(p.ref)]
+if (as.character(family) == "globins"){
+  family <- paste(family, "_heme_", heme, sep = "")
 }
-
-m.Pne = read.csv(file.path(dir.e,paste(family,".Out.m.Pn.csv",sep="")))[index,1:nmodes4]
-m.Qne = t(apply(m.Pne,1,cumsum))
-m.evaluese = read.csv(file.path(dir.e,paste(family,".Out.m.evalues.csv",sep="")))[index,1:nmodes4]
+m.Pne = read.csv(file.path(dir.e, paste(family, "_out_m.Pn.csv", sep = "")))[index, 1:nmodes4]
+Pne.mean = colMeans(m.Pne)
+m.Qne = t(apply(m.Pne, 1, cumsum))
+Qne.mean = colMeans(m.Qne)
+m.evaluese = read.csv(file.path(dir.e, paste(family, "_out_m.evalues.csv", sep = "")))[index, 1:nmodes4]
 evaluese = colMeans(m.evaluese)
 ievaluese = 1/evaluese
-
-lalign = read.csv(file.path(dir.e,paste(family,".Out.m.lalign.csv",sep="")))$x
-MSD = read.csv(file.path(dir.e,paste(family,".Out.MSD.csv",sep="")))$x
-id = read.csv(file.path(dir.e,paste(family,".Out.m.ID.csv",sep="")))$x
+laligned = read.csv(file.path(dir.e, paste(family, "_out_m.laligned.csv", sep = "")))$x
+MSD = read.csv(file.path(dir.e, paste(family, "_out_MSD.csv", sep = "")))$x
+id = read.csv(file.path(dir.e, paste(family, "_out_m.ID.csv", sep = "")))$x
 id.index = id[index]
-
+# Theoretical.
 dir.t <- "OUT/Theoretical"
-m.Pnt = read.csv(file.path(dir.t,paste(family,".Out.m.Pn.csv",sep="")))[,1:nmodes4]
-m.Qnt = t(apply(m.Pnt,1,cumsum))
-evalues = read.csv(file.path(dir.t,paste(family,".Out.evalues.csv",sep="")))$x[1:nmodes4]
+m.Pnt = read.csv(file.path(dir.t, paste(family, "_out_m.Pn.csv", sep = "")))[, 1:nmodes4]
+m.Qnt = t(apply(m.Pnt, 1, cumsum))
+evalues = read.csv(file.path(dir.t, paste(family, "_out_evalues.csv", sep = "")))$x[1:nmodes4]
 ievalues = 1/evalues
-
-#Number of t and e proteins#
+# Number of t and e proteins.
 nmut = nrow(m.Pnt)
 nexp = length(index)
-
-#Number of t groups#
-ngroups = as.integer(nmut/nexp)
-
+# Number of t groups.
+ngroups = as.integer(nmut / nexp)
 ```
 
-Conjunto teórico: `r nmut` mutantes de `r p.ref` de `r round(mean(id.index))` % de identidad secuencial con ANM R0 = 12 y Fmax= 2.
+Conjunto teórico: `r nmut` mutantes de `r p.ref` de `r round(mean(id.index))` % de identidad secuencial con ANM R0 = 12 y Fmax = 2.
 Se seleccionó esta proteína ya que es la que presenta menor MSD con respecto a las coordenadas xyz promedio de todas las proteínas del conjunto experimental.
@@
 ```{r}
-
-#Analysis experimental dataset#
-
-layout(matrix(1:4,2,2,byrow=T))
-
-  hist(id,main="%ID con referencia",col="grey")
-  hist(lalign,main="Número de sitios alineados con referencia",col="grey")
-  hist(MSD,main="MSD con la referencia",col="grey")
-  plot(id,MSD,xlab = "%ID", main ="MSD vs. %ID")
-
-  caract <- data.frame(pdbid,id,lalign,MSD)
+# Analysis experimental dataset.
+layout(matrix(1:4, 2, 2, byrow = T))
+hist(id, main = "%ID con referencia", col = "grey")
+hist(laligned, main = "Número de sitios alineados con referencia", col = "grey")
+hist(MSD, main = "MSD con la referencia", col = "grey")
+plot(id, MSD, xlab = "%ID", main = "MSD vs. %ID")
+caract <- data.frame(pdbid, id, laligned, MSD)
 caract
@@
 ```{r}
-
-  #rho#
-
-   rho.t.1 <- matrix(0,nrow=nmut,ncol=1)
-   rho.t.2 <- matrix(0,nrow=nmut,ncol=1)
-   rho.t.3 <- matrix(0,nrow=nmut,ncol=1)
-   rho.t.4 <- matrix(0,nrow=nmut,ncol=1)
-
-  for (i in (1: nmut)){
-	  rho.t.1[i,] <- cor((as.vector(as.matrix(m.Pnt[i,1:nmodes1]))*evalues[1:nmodes1]),ievalues[1:nmodes1],method="pearson")	
-	  rho.t.2[i,] <- cor((as.vector(as.matrix(m.Pnt[i,1:nmodes2]))*evalues[1:nmodes2]),ievalues[1:nmodes2],method="pearson")	   
-	  rho.t.3[i,] <- cor((as.vector(as.matrix(m.Pnt[i,1:nmodes3]))*evalues[1:nmodes3]),ievalues[1:nmodes3],method="pearson")	  
-	  rho.t.4[i,] <- cor((as.vector(as.matrix(m.Pnt[i,1:nmodes4]))*evalues[1:nmodes4]),ievalues[1:nmodes4],method="pearson")	   
+# Calculate rho.
+rho.t.1 <- matrix(0, nrow = nmut, ncol = 1)
+rho.t.2 <- matrix(0, nrow = nmut, ncol = 1)
+rho.t.3 <- matrix(0, nrow = nmut, ncol = 1)
+rho.t.4 <- matrix(0, nrow = nmut, ncol = 1)
+for (i in (1:nmut)) {
+  rho.t.1[i, ] <- cor((as.vector(as.matrix(m.Pnt[i, 1:nmodes1])) * evalues[1:nmodes1]), ievalues[1:nmodes1], method = "pearson")	
+  rho.t.2[i, ] <- cor((as.vector(as.matrix(m.Pnt[i, 1:nmodes2])) * evalues[1:nmodes2]), ievalues[1:nmodes2], method = "pearson")	
+  rho.t.3[i, ] <- cor((as.vector(as.matrix(m.Pnt[i, 1:nmodes3])) * evalues[1:nmodes3]), ievalues[1:nmodes3], method = "pearson")	
+  rho.t.4[i, ] <- cor((as.vector(as.matrix(m.Pnt[i, 1:nmodes4])) * evalues[1:nmodes4]), ievalues[1:nmodes4], method = "pearson")	   
 }
-
-  rho.e.1 <- matrix(0,nrow=nexp,ncol=1)
-  rho.e.2 <- matrix(0,nrow=nexp,ncol=1)
-  rho.e.3 <- matrix(0,nrow=nexp,ncol=1) 
-  rho.e.4 <- matrix(0,nrow=nexp,ncol=1)
-
-  for (i in (1: nexp)){
-	  rho.e.1[i,] <- cor((as.vector(as.matrix(m.Pne[i,1:nmodes1]))*evaluese[1:nmodes1]),ievaluese[1:nmodes1],method="pearson")
-	  rho.e.2[i,] <- cor((as.vector(as.matrix(m.Pne[i,1:nmodes2]))*evaluese[1:nmodes2]),ievaluese[1:nmodes2],method="pearson")
-	  rho.e.3[i,] <- cor((as.vector(as.matrix(m.Pne[i,1:nmodes3]))*evaluese[1:nmodes3]),ievaluese[1:nmodes3],method="pearson")
-	  rho.e.4[i,] <- cor((as.vector(as.matrix(m.Pne[i,1:nmodes4]))*evaluese[1:nmodes4]),ievaluese[1:nmodes4],method="pearson")
+rho.e.1 <- matrix(0, nrow = nexp, ncol = 1)
+rho.e.2 <- matrix(0, nrow = nexp, ncol = 1)
+rho.e.3 <- matrix(0, nrow = nexp, ncol = 1) 
+rho.e.4 <- matrix(0, nrow = nexp, ncol = 1) 
+for (i in (1:nexp)) {
+  rho.e.1[i, ] <- cor((as.vector(as.matrix(m.Pne[i, 1:nmodes1])) * evaluese[1:nmodes1]), ievaluese[1:nmodes1], method = "pearson")
+  rho.e.2[i, ] <- cor((as.vector(as.matrix(m.Pne[i, 1:nmodes2])) * evaluese[1:nmodes2]), ievaluese[1:nmodes2], method = "pearson")
+  rho.e.3[i, ] <- cor((as.vector(as.matrix(m.Pne[i, 1:nmodes3])) * evaluese[1:nmodes3]), ievaluese[1:nmodes3], method = "pearson")
+  rho.e.4[i, ] <- cor((as.vector(as.matrix(m.Pne[i, 1:nmodes4])) * evaluese[1:nmodes4]), ievaluese[1:nmodes4], method = "pearson")
 }
-
-  #auc#
-  auc.t.1 <- matrix(0,nrow=nmut,ncol=1)
-  auc.t.2 <- matrix(0,nrow=nmut,ncol=1)
-  auc.t.3 <- matrix(0,nrow=nmut,ncol=1)
-  auc.t.4 <- matrix(0,nrow=nmut,ncol=1)
-
-  for (i in (1:nmut)){
-	  auc.t.1[i,] <- auc(seq(1:nmodes1),m.Qnt[i,1:nmodes1])
-	  auc.t.2[i,] <- auc(seq(1:nmodes2),m.Qnt[i,1:nmodes2])
-	  auc.t.3[i,] <- auc(seq(1:nmodes3),m.Qnt[i,1:nmodes3])
-	  auc.t.4[i,] <- auc(seq(1:nmodes4),m.Qnt[i,1:nmodes4])
+# Calculate auc.
+auc.t.1 <- matrix(0, nrow = nmut, ncol = 1)
+auc.t.2 <- matrix(0, nrow = nmut, ncol = 1)
+auc.t.3 <- matrix(0, nrow = nmut, ncol = 1)
+auc.t.4 <- matrix(0, nrow = nmut, ncol = 1)
+for (i in (1:nmut)) {
+  auc.t.1[i, ] <- auc(seq(1:nmodes1), m.Qnt[i,1:nmodes1])
+  auc.t.2[i, ] <- auc(seq(1:nmodes2), m.Qnt[i,1:nmodes2])
+  auc.t.3[i, ] <- auc(seq(1:nmodes3), m.Qnt[i,1:nmodes3])
+  auc.t.4[i, ] <- auc(seq(1:nmodes4), m.Qnt[i,1:nmodes4])
 }
-
-  auc.e.1 <- matrix(0,nrow=nexp,ncol=1)
-  auc.e.2 <- matrix(0,nrow=nexp,ncol=1)
-  auc.e.3 <- matrix(0,nrow=nexp,ncol=1)
-  auc.e.4 <- matrix(0,nrow=nexp,ncol=1)
-
-  for (i in (1:nexp)){
-	  auc.e.1[i,] <- auc(seq(1:nmodes1),m.Qne[i,1:nmodes1])
-	  auc.e.2[i,] <- auc(seq(1:nmodes2),m.Qne[i,1:nmodes2])
-	  auc.e.3[i,] <- auc(seq(1:nmodes3),m.Qne[i,1:nmodes3])
-	  auc.e.4[i,] <- auc(seq(1:nmodes4),m.Qne[i,1:nmodes4])
+auc.e.1 <- matrix(0, nrow = nexp, ncol = 1)
+auc.e.2 <- matrix(0, nrow = nexp, ncol = 1)
+auc.e.3 <- matrix(0, nrow = nexp, ncol = 1)
+auc.e.4 <- matrix(0, nrow = nexp, ncol = 1)
+for (i in (1:nexp)) {
+  auc.e.1[i, ] <- auc(seq(1:nmodes1), m.Qne[i, 1:nmodes1])
+  auc.e.2[i, ] <- auc(seq(1:nmodes2), m.Qne[i, 1:nmodes2])
+  auc.e.3[i, ] <- auc(seq(1:nmodes3), m.Qne[i, 1:nmodes3])
+  auc.e.4[i, ] <- auc(seq(1:nmodes4), m.Qne[i, 1:nmodes4])
 }
@@
 ```{r}
-
-layout(matrix(1:4,2,2,byrow=T))
-
-plot(density(rho.t.1),col="blue",ylab="Frecuencia",xlab="rho",main="Histograma rho 10 modos")
-points(x=c(rho.e.1),y=rep(0,nexp),col="red")
-
-plot(density(auc.t.1),col="blue",ylab="Frecuencia",xlab="auc",main="Histograma auc 10 modos")
-points(x=c(auc.e.1),y=rep(0,nexp),col="red")
-
-plot(density(rho.t.2),col="blue",ylab="Frecuencia",xlab="rho",main="Histograma rho 25 modos")
-points(x=c(rho.e.2),y=rep(0,nexp),col="red")
-
-plot(density(auc.t.2),col="blue",ylab="Frecuencia",xlab="auc",main="Histograma auc 25 modos")
-points(x=c(auc.e.2),y=rep(0,nexp),col="red")
+layout(matrix(1:4, 2, 2, byrow = T))
+plot(density(rho.t.1), col = "blue", ylab = "Frecuencia", xlab = "rho", main = "Histograma rho 10 modos")
+points(x = c(rho.e.1), y = rep(0, nexp), col = "red")
+plot(density(auc.t.1), col = "blue", ylab = "Frecuencia", xlab = "auc", main = "Histograma auc 10 modos")
+points(x = c(auc.e.1), y = rep(0, nexp), col = "red")
+plot(density(rho.t.2), col = "blue", ylab = "Frecuencia", xlab = "rho", main = "Histograma rho 25 modos")
+points(x = c(rho.e.2), y = rep(0, nexp), col = "red")
+plot(density(auc.t.2), col = "blue", ylab = "Frecuencia", xlab = "auc", main = "Histograma auc 25 modos")
+points(x = c(auc.e.2), y = rep(0, nexp), col = "red")
 ```
@@
 ```{r}
-layout(matrix(1:4,2,2,byrow=T))
-
-plot(density(rho.t.3),col="blue",ylab="Frecuencia",xlab="rho",main="Histograma rho 50 modos")
-points(x=c(rho.e.3),y=rep(0,nexp),col="red")
-
-plot(density(auc.t.3),col="blue",ylab="Frecuencia",xlab="auc",main="Histograma auc 50 modos")
-points(x=c(auc.e.3),y=rep(0,nexp),col="red")
-
-plot(density(rho.t.4),col="blue",ylab="Frecuencia",xlab="rho",main="Histograma rho 100 modos")
-points(x=c(rho.e.4),y=rep(0,nexp),col="red")
-
-plot(density(auc.t.4),col="blue",ylab="Frecuencia",xlab="auc",main="Histograma auc 100 nmodos")
-points(x=c(auc.e.4),y=rep(0,nexp),col="red")
-
+layout(matrix(1:4, 2, 2, byrow = T))
+plot(density(rho.t.3), col = "blue", ylab = "Frecuencia", xlab = "rho", main = "Histograma rho 50 modos")
+points(x = c(rho.e.3), y = rep(0, nexp), col = "red")
+plot(density(auc.t.3), col = "blue", ylab = "Frecuencia", xlab = "auc", main = "Histograma auc 50 modos")
+points(x = c(auc.e.3), y = rep(0, nexp), col = "red")
+plot(density(rho.t.4), col = "blue", ylab = "Frecuencia", xlab = "rho", main = "Histograma rho 100 modos")
+points(x = c(rho.e.4), y = rep(0, nexp), col = "red")
+plot(density(auc.t.4), col = "blue", ylab = "Frecuencia", xlab = "auc", main = "Histograma auc 100 nmodos")
+points(x = c(auc.e.4), y = rep(0, nexp), col = "red")
 ```
@@
 
-#Calculate groups#
-
-source("FUNCTIONS/Mean.groups.R")
-
-Pne.mean = colMeans(m.Pne)
-Qne.mean = colMeans(m.Qne)
-
-Pntgroup <- mean.groups(ngroups,nexp,m.Pnt)
+# Calculate groups, means and quantiles.
+Pntgroup <- CalculateGroupsMeansQuantiles(m.Pnt, ngroups, nexp)
 m.Pntgroup <- Pntgroup$mean.group
 Pntgroup.mean <- Pntgroup$mean.total
-Pntgroup.quantile5 <- Pntgroup$quantile[1,]
-Pntgroup.quantile95 <- Pntgroup$quantile[2,]
-
-Qntgroup <- mean.groups(ngroups,nexp,m.Qnt)
+Pntgroup.quantile5 <- Pntgroup$quantile[1, ]
+Pntgroup.quantile95 <- Pntgroup$quantile[2, ] 
+Qntgroup <- CalculateGroupsMeansQuantiles(m.Qnt, ngroups, nexp)
 m.Qntgroup <- Qntgroup$mean.group
 Qntgroup.mean <- Qntgroup$mean.total
-Qntgroup.quantile5 <- Qntgroup$quantile[1,]
-Qntgroup.quantile95 <- Qntgroup$quantile[2,]
-
-layout(matrix(1:2,1,2,byrow=T))
-
-plot(Pntgroup.mean,ylab ="Pn promedio", xlab = "nmodo",type="l",ylim=c(0,0.07),main="Pn promedio vs. nmodo")
-lines(Pntgroup.quantile5,col="green")
-lines(Pntgroup.quantile95,col="green")
-points(Pne.mean,col="red")
-
-plot(Qntgroup.mean,ylab ="Qn promedio", xlab = "nmodo",type="l",ylim=c(0,0.7),main ="Qn promedio vs. nmodo")
-lines(Qntgroup.quantile5,col="green")
-lines(Qntgroup.quantile95,col="green")
-points(Qne.mean,col="red")
+Qntgroup.quantile5 <- Qntgroup$quantile[1, ]
+Qntgroup.quantile95 <- Qntgroup$quantile[2, ]
+# Graphics.
+layout(matrix(1:2, 1, 2, byrow = T))
+plot(Pntgroup.mean, ylab = "Pn promedio", xlab = "nmodo", type = "l", ylim = c(0, 0.07), main = "Pn promedio vs. nmodo")
+lines(Pntgroup.quantile5, col = "green")
+lines(Pntgroup.quantile95, col = "green")
+points(Pne.mean, col = "red")
+plot(Qntgroup.mean, ylab = "Qn promedio", xlab = "nmodo", type = "l", ylim = c(0, 0.7), main = "Qn promedio vs. nmodo")
+lines(Qntgroup.quantile5, col = "green")
+lines(Qntgroup.quantile95, col = "green")
+points(Qne.mean, col = "red")
 ```

### 2015-10-18 ExperimentalMain.R

@@ -3,220 +3,176 @@
 # El programa calcula medidas de variabilidad estructural y dinámica de alineamientos múltiples de 
 # familias de proteínas provenientes de la base de datos de alineamientos múltiples "Homstrad".
 #
-# Para utilizar el programa se debe completar un input ("DATA/Experimental/inputE.csv") especificando: 
-# -family:la familia de proteínas del alineamiento, que puede ser "SerinProteases", "Globins" o "Plastocyanins"
+# Para utilizar el programa se debe completar un input ("DATA/Experimental/experimental_input.csv") especificando: 
+# -family:la familia de proteínas del alineamiento, que puede ser "serinProteases", "globins" o "plastocyanins"
 # -p.ref: la proteína de referncia que se desee utilizar, teniendo en cuenta que la misma debe ser escrita de 
 # la misma forma en la que se encuentra en el dataset de la familia correspondiente 
-# (ej:"DATA/Experimental/SerinProteasesDataset.csv").
+# (ej:"DATA/Experimental/serinProteases_dataset.csv").
 # -heme: solo se utiliza para la familia de las globinas, puede ser "TRUE" o "FALSE", dependiendo de si 
 # se desea o no considerar al grupo HEMO. 
 # -model: el modelo de red elástica a usar, que solo puede ser "ANM" por el momento.
 # -R0: cut-off del ANM.
-
-#Remove objects#
+# Remove objects.
 rm(list = ls())
-
-#Read input#
+# Read input.
 data.dir <- "DATA/Experimental"
-
-input.dir <- file.path(data.dir,"InputE.csv")
-input <- read.csv(input.dir)
-
-#Reference family and protein#
+input.fname <- file.path(data.dir, "experimental_input.csv")
+input <- read.csv(input.fname)
 family <- input$family
 p.ref <- input$p.ref 
-heme = input$heme
-
-#ENM#
[…]

### 2015-10-18 TheoreticalMain.R

@@ -5,10 +5,10 @@
 # entre sí. Además, calcula medidas de variabilidad estructural y dinámica entre las proteínas mutantes 
 # generadas y la proteína de referencia.
 #
-# Para utilizar el programa se debe completar un input ("DATA/Theoretical/inputT.csv") especificando: 
-# -family: la familia de proteínas a la que pertenece la proteína a mutar escrita en inglés y plural 
-# (ej.:"Globins"). Tener en cuenta que las familias que pueden ser analizadas experimentalmente son
-# "SerinProteases", "Globins" o "Plastocyanins".
+# Para utilizar el programa se debe completar un input ("DATA/Theoretical/theoretical_input.csv") especificando: 
+# -family: la familia de proteínas a la que pertenece la proteína a mutar. 
+# Tener en cuenta que las familias que pueden ser analizadas experimentalmente son
+# "serinProteases", "globins" o "plastocyanins".
 # -p.ref: el código de pdb (pdbid) de la proteína a mutar (ej.:"1a6m")
 # -chain: la cadena de p.ref que se desea mutar.
 # -heme: solo se utiliza para la familia de las globinas, puede ser "TRUE" o "FALSE" dependiendo de 
@@ -18,164 +18,129 @@
 # -Fmax: valor máximo de las fuerzas usadas para la simulación de las mutaciones.
 # -model: el modelo de red elástica a usar, que solo puede ser "ANM" por el momento.
 # -R0: cut-off del ANM.
-
-#Remove objects#
+# Remove objects.
 rm(list = ls()) 
-
-#Read input#
+# Read input.
 data.dir <- "DATA/Theoretical"
-
-input.dir <- file.path(data.dir,"InputT.csv")
-input <- read.csv(input.dir)
-
-#Reference family and protein#
+input.fname <- file.path(data.dir, "theoretical_input.csv")
+input <- read.csv(input.fname)
 family <- input$family
 p.ref <- input$p.ref 
 chain <- input$chain
[…]

### 2015-10-19 ComparisonsMain.Rmd
Hice pequeñas modificaciones a ComparisonsMain.Rmd, ExperimentalMain.R y TheoreticalMain.R

@@
 ---
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(warning=FALSE,echo=FALSE,message=FALSE)
+```{r setup, include = FALSE}
+knitr::opts_chunk$set(warning=FALSE, echo=FALSE, message = FALSE)
 ```
@@
 # Remove objects.
-rm (list=ls())
+rm (list = ls())
 # Read Input.
@@
 # Read files and calculate measures.
-# Experimental.
-dir.e <- "OUT/Experimental"
+# Read pdbid.
 pdbid <- read.csv(file.path("DATA/Experimental", paste(family, "_dataset.csv", sep = "")))$pdbid
 pdbid <- pdbid[pdbid != as.character(p.ref)]
-if (as.character(family) == "globins"){
+# Read experimental output.
+dir.e <- "OUT/Experimental"
+if (as.character(family) == "globins") {
   family <- paste(family, "_heme_", heme, sep = "")
@@
 m.evaluese = read.csv(file.path(dir.e, paste(family, "_out_m.evalues.csv", sep = "")))[index, 1:nmodes4]
-evaluese = colMeans(m.evaluese)
-ievaluese = 1/evaluese
+evaluese.mean = colMeans(m.evaluese)
+ievaluese.mean = 1/evaluese.mean
 laligned = read.csv(file.path(dir.e, paste(family, "_out_m.laligned.csv", sep = "")))$x
@@
 id.index = id[index]
-# Theoretical.
+# Read theoretical output.
 dir.t <- "OUT/Theoretical"
@@
 
-Conjunto experimental: `r nexp` proteínas de la familia de `r family`.Las proteínas tienen un promedio de identidad secuencial de `r round(mean(id.index))`%.
+Conjunto experimental: `r nexp` proteínas de la familia de `r family`.
+Las proteínas tienen un promedio de identidad secuencial de `r round(mean(id.index))`%.
 Todas las proteínas del sub-conjunto elegidas alinean en todos los sitios de `r p.ref`, o en como máximo 1 sitio menos.
@@
 for (i in (1:nexp)) {
-  rho.e.1[i, ] <- cor((as.vector(as.matrix(m.Pne[i, 1:nmodes1])) * evaluese[1:nmodes1]), ievaluese[1:nmodes1], method = "pearson")
-  rho.e.2[i, ] <- cor((as.vector(as.matrix(m.Pne[i, 1:nmodes2])) * evaluese[1:nmodes2]), ievaluese[1:nmodes2], method = "pearson")
-  rho.e.3[i, ] <- cor((as.vector(as.matrix(m.Pne[i, 1:nmodes3])) * evaluese[1:nmodes3]), ievaluese[1:nmodes3], method = "pearson")
-  rho.e.4[i, ] <- cor((as.vector(as.matrix(m.Pne[i, 1:nmodes4])) * evaluese[1:nmodes4]), ievaluese[1:nmodes4], method = "pearson")
+  rho.e.1[i, ] <- cor((as.vector(as.matrix(m.Pne[i, 1:nmodes1])) * evaluese.mean[1:nmodes1]), ievaluese.mean[1:nmodes1], method = "pearson")
+  rho.e.2[i, ] <- cor((as.vector(as.matrix(m.Pne[i, 1:nmodes2])) * evaluese.mean[1:nmodes2]), ievaluese.mean[1:nmodes2], method = "pearson")
+  rho.e.3[i, ] <- cor((as.vector(as.matrix(m.Pne[i, 1:nmodes3])) * evaluese.mean[1:nmodes3]), ievaluese.mean[1:nmodes3], method = "pearson")
+  rho.e.4[i, ] <- cor((as.vector(as.matrix(m.Pne[i, 1:nmodes4])) * evaluese.mean[1:nmodes4]), ievaluese.mean[1:nmodes4], method = "pearson")
 }
@@
 # Calculate groups, means and quantiles.
-Pntgroup <- CalculateGroupsMeansQuantiles(m.Pnt, ngroups, nexp)
-m.Pntgroup <- Pntgroup$mean.group
-Pntgroup.mean <- Pntgroup$mean.total
-Pntgroup.quantile5 <- Pntgroup$quantile[1, ]
-Pntgroup.quantile95 <- Pntgroup$quantile[2, ] 
-Qntgroup <- CalculateGroupsMeansQuantiles(m.Qnt, ngroups, nexp)
-m.Qntgroup <- Qntgroup$mean.group
-Qntgroup.mean <- Qntgroup$mean.total
-Qntgroup.quantile5 <- Qntgroup$quantile[1, ]
-Qntgroup.quantile95 <- Qntgroup$quantile[2, ]
+Pnt.group <- CalculateGroupsMeansQuantiles(m.Pnt, ngroups, nexp)
+Pnt.group.mean <- Pnt.group$mean.total
+Pnt.group.quantile5 <- Pnt.group$quantile[1, ]
+Pnt.group.quantile95 <- Pnt.group$quantile[2, ] 
+Qnt.group <- CalculateGroupsMeansQuantiles(m.Qnt, ngroups, nexp)
+Qnt.group.mean <- Qnt.group$mean.total
+Qnt.group.quantile5 <- Qnt.group$quantile[1, ]
+Qnt.group.quantile95 <- Qnt.group$quantile[2, ]
 # Graphics.
 layout(matrix(1:2, 1, 2, byrow = T))
-plot(Pntgroup.mean, ylab = "Pn promedio", xlab = "nmodo", type = "l", ylim = c(0, 0.07), main = "Pn promedio vs. nmodo")
-lines(Pntgroup.quantile5, col = "green")
-lines(Pntgroup.quantile95, col = "green")
+plot(Pnt.group.mean, ylab = "Pn promedio", xlab = "nmodo", type = "l", ylim = c(0, 0.07), main = "Pn promedio vs. nmodo")
+lines(Pnt.group.quantile5, col = "green")
+lines(Pnt.group.quantile95, col = "green")
 points(Pne.mean, col = "red")
-plot(Qntgroup.mean, ylab = "Qn promedio", xlab = "nmodo", type = "l", ylim = c(0, 0.7), main = "Qn promedio vs. nmodo")
-lines(Qntgroup.quantile5, col = "green")
-lines(Qntgroup.quantile95, col = "green")
+plot(Qnt.group.mean, ylab = "Qn promedio", xlab = "nmodo", type = "l", ylim = c(0, 0.7), main = "Qn promedio vs. nmodo")
+lines(Qnt.group.quantile5, col = "green")
+lines(Qnt.group.quantile95, col = "green")
 points(Qne.mean, col = "red")

### 2015-10-19 TheoreticalMain.R

@@ -113,7 +113,7 @@ for(mut in seq(nmut)) {
     VA <- CalculateVariability(dr, K.p.ref.2, K.mut)
     m.nH[mut, 1:nmodes.p.ref.2] = t(VA$nH)
     m.Pn[mut, 1:nmodes.p.ref.2] = t(VA$Pn)
-    m.d.evalues[mut, 1:nmodes.p.ref.2]  = t(VA$d.evalues[1:nmodes.p.ref.2])
+    m.d.evalues[mut, 1:nmodes.p.ref.2] = t(VA$d.evalues[1:nmodes.p.ref.2])
     dr.squarei = rbind(VA$dr.squarei, seq(1, naa))
     for (i in (1:naa)) {
       m.dr.squarei[mut, i] = matrix(dr.squarei[1, dr.squarei[2, ] == i], ncol = 1, nrow = 1)
@@ -124,10 +124,10 @@ for(mut in seq(nmut)) {
   }
 }
 # Calculate Means.
-mean.nH = colMeans(as.matrix(m.nH), na.rm = T)
-mean.Pn = colMeans(as.matrix(m.Pn), na.rm = T)
-mean.d.evalues = colMeans(as.matrix(m.d.evalues), na.rm = T)
-MSDi = colMeans(as.matrix(m.dr.squarei), na.rm = T)
+mean.nH = colMeans(m.nH, na.rm = T)
+mean.Pn = colMeans(m.Pn, na.rm = T)
+mean.d.evalues = colMeans(m.d.evalues, na.rm = T)
+MSDi = colMeans(m.dr.squarei, na.rm = T)
 MSD = rowMeans(m.dr.squarei, na.rm = T)
 # Save information.
 if (family == "globins") {

### 2015-11-09 ComparisonsMain.Rmd
Added core

@@
 ```{r setup, include = FALSE}
-knitr::opts_chunk$set(warning=FALSE, echo=FALSE, message = FALSE)
+knitr::opts_chunk$set(warning = FALSE, echo = FALSE, message = FALSE)
 ```
@@
 # Para correrlo se debe completar un Input ("DATA/comp_input.csv") especificando:
-# -family: la familia de proteínas a comparar, debe estar escrita consistentemente 
+# - family: la familia de proteínas a comparar, debe estar escrita consistentemente 
 # con los archivos theoretical_input y experimental_input.
-# -p.ref: la proteína dereferencia de la familia, que debe ser escrita 
+# - p.ref: la proteína dereferencia de la familia, que debe ser escrita 
 # consisntentemente con el archivo experimental_input, es decir que debe ser escrita de la 
 # forma en la que está escrita en el dataset.
-# -heme: solo se utiliza para la familia de las globinas, puede ser "TRUE" o 
+# - heme: solo se utiliza para la familia de las globinas, puede ser "TRUE" o 
 # "FALSE" dependiendo de si se quiere considerar o no al grupo HEMO. 
-# -index: el índice de las proteínas de la familia que se desea analizar.
+# - index: el índice de las proteínas de la familia que se desea analizar.
+
 # Remove objects.
 rm (list = ls())
+
 # Read Input.
@@
 heme <- input$heme[1]
+core <- input$core[1]
 index = as.vector(input$index)
+
 # Nmodes to analyze.
@@
 nmodes4 = 100
+
 # Load librarys. 
 library(flux)  # function "auc".
+
 # Source functions.
 source("FUNCTIONS/CalculateGroupsMeansQuantiles.R")
+
 # Read files and calculate measures.
@@
 pdbid <- pdbid[pdbid != as.character(p.ref)]
+
 # Read experimental output.
@@
 }
-m.Pne = read.csv(file.path(dir.e, paste(family, "_out_m.Pn.csv", sep = "")))[index, 1:nmodes4]
+m.Pne = read.csv(file.path(dir.e, paste(family, "_core_", core, "_out_m.Pn.csv", sep = "")))[index, 1:nmodes4]
 Pne.mean = colMeans(m.Pne)
@@
 Qne.mean = colMeans(m.Qne)
-m.evaluese = read.csv(file.path(dir.e, paste(family, "_out_m.evalues.csv", sep = "")))[index, 1:nmodes4]
+m.evaluese = read.csv(file.path(dir.e, paste(family, "_core_", core, "_out_m.evalues.csv", sep = "")))[index, 1:nmodes4]
 evaluese.mean = colMeans(m.evaluese)
 ievaluese.mean = 1/evaluese.mean
-laligned = read.csv(file.path(dir.e, paste(family, "_out_m.laligned.csv", sep = "")))$x
-MSD = read.csv(file.path(dir.e, paste(family, "_out_MSD.csv", sep = "")))$x
-id = read.csv(file.path(dir.e, paste(family, "_out_m.ID.csv", sep = "")))$x
+laligned = read.csv(file.path(dir.e, paste(family, "_core_", core, "_out_m.laligned.csv", sep = "")))$x
+MSD = read.csv(file.path(dir.e, paste(family, "_core_", core, "_out_MSD.csv", sep = "")))$x
+id = read.csv(file.path(dir.e, paste(family, "_core_", core, "_out_m.ID.csv", sep = "")))$x
 id.index = id[index]
+
 # Read theoretical output.
 dir.t <- "OUT/Theoretical"
-m.Pnt = read.csv(file.path(dir.t, paste(family, "_out_m.Pn.csv", sep = "")))[, 1:nmodes4]
+m.Pnt = read.csv(file.path(dir.t, paste(family, "_core_", core, "_out_m.Pn.csv", sep = "")))[, 1:nmodes4]
 m.Qnt = t(apply(m.Pnt, 1, cumsum))
-evalues = read.csv(file.path(dir.t, paste(family, "_out_evalues.csv", sep = "")))$x[1:nmodes4]
+evalues = read.csv(file.path(dir.t, paste(family, "_core_", core, "_out_evalues.csv", sep = "")))$x[1:nmodes4]
 ievalues = 1/evalues
+
 # Number of t and e proteins.
@@
 nexp = length(index)
+
 # Number of t groups.
@@
 
-Conjunto teórico: `r nmut` mutantes de `r p.ref` de `r round(mean(id.index))` % de identidad secuencial con ANM R0 = 12 y Fmax = 2.
-Se seleccionó esta proteína ya que es la que presenta menor MSD con respecto a las coordenadas xyz promedio de todas las proteínas del conjunto experimental.
+## Conjuntos de proteínas
+
+### Conjunto teórico
+`r nmut` mutantes de `r p.ref` de `r round(mean(id.index))` % de identidad secuencial con ANM *R0* = 12 y *Fmax* = 2.
+Se seleccionó esta proteína ya que es la que presenta menor *MSD* con respecto a las coordenadas xyz promedio de todas las proteínas del conjunto experimental.
 El porcentaje de mutaciones se seleccionó de acuerdo al promedio de identidad secuencial de proteínas del conjunto experimental.
 
-Conjunto experimental: `r nexp` proteínas de la familia de `r family`.
+### Conjunto experimental 
+`r nexp` proteínas de la familia de `r family`.
 Las proteínas tienen un promedio de identidad secuencial de `r round(mean(id.index))`%.
 Todas las proteínas del sub-conjunto elegidas alinean en todos los sitios de `r p.ref`, o en como máximo 1 sitio menos.
+
+La caracterización del conjunto experimental se muestra a continuación:
 ```{r}
@@
 }
+
 # Calculate auc.
@@
 
-Las distribuciones de auc y rho para cada conjunto se muestran a continuación (azul= teórico, rojo = experimental)
+## Comparaciones
+
+### RHO y AUC
+Las distribuciones de *auc* y *rho* para cada conjunto se muestran a continuación (azul= teórico, rojo = experimental)
 
@@
 
-Las distribuciones de Pn y Qn de los conjuntos son las siguientes:
+## Pn y Qn
+Las distribuciones de *Pn* y *Qn* de los conjuntos son las siguientes:
 
@@
 Qnt.group.quantile95 <- Qnt.group$quantile[2, ]
+
 # Graphics.

### 2015-11-09 FUNCTIONS/AnalyzeAlignmentGeneral.R

@@ -1,0 +1,122 @@
+AnalyzeAlignmentGeneral <- function(df.alignment)UseMethod("AnalyzeAlignmentGeneral") 
+
+AnalyzeAlignmentGeneral.NoCore <- function(df.alignment) {
+  
+  # Prepare data.
+  alignment <- df.alignment$alignment
+  id <- df.alignment$id
+  p.1 <- df.alignment$p.1
+  p.2 <- df.alignment$p.2
+  
+  # Extract data form the alignment.
+  lalignment = ncol(alignment)
+  alignment.p.1 = alignment[id == p.1,]
+  alignment.p.2 = alignment[id == p.2,]
+
+  # Get indexes.
+  p.1.index = c()
+  p.2.index = c()
+  aa.p.1 = 1
+  aa.p.2 = 1
+  
+  for (i in (1:lalignment)) {
+    if (alignment.p.1[i] != "-") {
+      p.1.index[i] <- aa.p.1
+      aa.p.1 = aa.p.1 + 1
+    }
+    if (alignment.p.2[i] != "-") {
+      p.2.index[i] <- aa.p.2
+      aa.p.2 = aa.p.2 + 1
+    }
+  }	
+  
+  # Get aligned and not.aligned indexes.
+  aligned.p.1.index = c()
+  aligned.p.2.index = c()
+  not.aligned.p.1.index = c()
+  not.aligned.p.2.index = c()
+  
+  for (i in (1:lalignment)) {
+    if (alignment.p.1[i] != "-" & alignment.p.2[i] != "-") {
+      aligned.p.1.index <- cbind(aligned.p.1.index, p.1.index[i])
+      aligned.p.2.index <- cbind(aligned.p.2.index, p.2.index[i])
+    }
+    if (alignment.p.1[i] != "-" & alignment.p.2[i] == "-") {
+      not.aligned.p.1.index <- cbind(not.aligned.p.1.index, p.1.index[i])
+    }
+    if (alignment.p.2[i] != "-" & alignment.p.1[i] == "-") {
+      not.aligned.p.2.index <- cbind(not.aligned.p.2.index, p.2.index[i])
+    }
+  }	
+  naligned <- length(aligned.p.1.index)
+  output = list("aligned.p.1.index" = aligned.p.1.index,
+                "aligned.p.2.index" = aligned.p.2.index,
+                "not.aligned.p.1.index" = not.aligned.p.1.index,
[…]

### 2015-11-09 FUNCTIONS/CalculateKeff.R

@@ -3,8 +3,9 @@
 #  Args:
 #    r: 3 x nsites matrix containing the equilibrium coordinates of each site.
 #    aligned.index: aligned sites
-#    not.aligned.index: not aligned sites
-#    kijFunction: name of the function that calculates kij between 2 sites i and j.
+#    not.aligned.index: not aligned sites.
+#    CalculateK: name of the function that calculates tha matrix K.
+#    Calculatekij: name of the function that calculates kij between 2 sites i and j.
 #    R0: cut-off for ANM.
 #    TOLERANCE: 0 tolerance.
 #
@@ -12,7 +13,7 @@
 #    KEFF: 3*naligned x 3*naligned KEFF matrix.
 #    va: eigenvalues > TOLERANCE of KEFF.
 #    ve: eigenvectors > TOLERANCE of KEFF.
-CalculateKeff <- function(r, aligned.index, not.aligned.index, CalculateKij, R0, TOLERANCE) {
+CalculateKeff <- function(r, aligned.index, not.aligned.index, CalculateK, CalculateKij, R0, TOLERANCE) {
   naligned = length(aligned.index)
   n.not.aligned = length(not.aligned.index)
   nsites = ncol(r)

### 2015-11-16 MultipleComparisonsMain.Rmd
agregué archivo de comparaciones múltiples

---
title: "Comparaciones Teórico-Experimental"
output: html_document
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(warning = FALSE, echo = FALSE, message = FALSE)
```

```{r, fig.width = 20, fig.height = 40}
# INFORMACIÓN
#
# Este programa genera un archivo HTLM comparando la divergencia etsructural de
# proteínas experimentales y mutantes teóricas.
# Para correrlo se debe completar un Input ("DATA/comp_input.csv") especificando:
# - family: la familia de proteínas a comparar, debe estar escrita consistentemente 
# con los archivos theoretical_input y experimental_input.
# - p.ref: la proteína dereferencia de la familia, que debe ser escrita 
# consisntentemente con el archivo experimental_input, es decir que debe ser escrita de la 
# forma en la que está escrita en el dataset.
# - heme: solo se utiliza para la familia de las globinas, puede ser "TRUE" o 
# "FALSE" dependiendo de si se quiere considerar o no al grupo HEMO.
# - core: puede ser "TRUE" o "FALSE" dependiendo de si se quiere analizar solo los sectores
# del alineamiento donde no hay gaps.

# Remove objects.
rm (list = ls())

# Nmodes to analyze.
nmodes1 = 10
nmodes2 = 25
nmodes3 = 100

# Load librarys. 
library(flux)  # function "auc".

# Source functions. 
source("FUNCTIONS/CalculateGroupsMeansQuantiles.R")

# Read Input.
input <- read.csv("DATA/comp_input.csv")

# Layout.
layout(matrix(1:(10 * nrow(input)), 2 * nrow(input), 5, byrow = T), widths = rep(10, 10 * nrow(input)), heights = rep(10, 10 * nrow(input)))

for (f in (1:nrow(input))) { 
  family <- input$family[f]
  p.ref <- input$p.ref[f]
  heme <- input$heme[f]
  core <- input$core[f]

  # Read files and calculate measures.
  ## Read experimental output.
  dir.e <- "OUT/Experimental"
  if (as.character(family) == "globins") {
    family <- paste(family, "_heme_", heme, sep = "")
  }
  family <- paste(family, "_core_", core, sep = "")

  laligned = read.csv(file.path(dir.e, paste(family, "_out_m.laligned.csv", sep = "")))$x
  index <- c()
  for (i in (1:length(laligned))) {
    if (laligned[i] == max(laligned)) {
      index[i] <- i
    }
  }
  index <- index[!is.na(index)]

  m.Pne = read.csv(file.path(dir.e, paste(family, "_out_m.Pn.csv", sep = "")))[index, 1:nmodes3]
  Pne.mean = colMeans(m.Pne)

  m.Qne = t(apply(m.Pne, 1, cumsum))
Qne.mean = colMeans(m.Qne)

  m.evaluese = read.csv(file.path(dir.e, paste(family, "_out_m.evalues.csv", sep = "")))[index, 1:nmodes3]
  evaluese.mean = colMeans(m.evaluese)
  ievaluese.mean = 1/evaluese.mean

  MSD = read.csv(file.path(dir.e, paste(family, "_out_MSD.csv", sep = "")))$x

  id = read.csv(file.path(dir.e, paste(family, "_out_m.ID.csv", sep = "")))$x
  id.index = id[index]

  ## Read theoretical output.
  dir.t <- "OUT/Theoretical"
  m.Pnt = read.csv(file.path(dir.t, paste(family, "_out_m.Pn.csv", sep = "")))[, 1:nmodes3]
  evalues = read.csv(file.path(dir.t, paste(family, "_out_evalues.csv", sep = "")))$x[1:nmodes3]
  m.Qnt = t(apply(m.Pnt, 1, cumsum))
  ievalues = 1/evalues

  # Number of t and e proteins.
  nmut = nrow(m.Pnt)
  nexp = length(index)

  # Number of t groups.
  ngroups = as.integer(nmut / nexp)

  # Calculate rho and auc.
  rho.t <- matrix(0, nrow = nmut, ncol = 2)
  auc.t <- matrix(0, nrow = nmut, ncol = 2)

  for (i in (1:nmut)) {
    rho.t[i, 1] <- cor((as.vector(as.matrix(m.Pnt[i, 1:nmodes1])) * evalues[1:nmodes1]), ievalues[1:nmodes1], method = "pearson")	
    rho.t[i, 2] <- cor((as.vector(as.matrix(m.Pnt[i, 1:nmodes2])) * evalues[1:nmodes2]), ievalues[1:nmodes2], method = "pearson")	
    auc.t[i, 1] <- auc(seq(1:nmodes1), m.Qnt[i,1:nmodes1])
    auc.t[i, 2] <- auc(seq(1:nmodes2), m.Qnt[i,1:nmodes2])
  }

  rho.e <- matrix(0, nrow = nexp, ncol = 2)
  auc.e <- matrix(0, nrow = nexp, ncol = 2)

  for (i in (1:nexp)) {
    rho.e[i, 1] <- cor((as.vector(as.matrix(m.Pne[i, 1:nmodes1])) * evaluese.mean[1:nmodes1]), ievaluese.mean[1:nmodes1], method = "pearson")
    rho.e[i, 2] <- cor((as.vector(as.matrix(m.Pne[i, 1:nmodes2])) * evaluese.mean[1:nmodes2]), ievaluese.mean[1:nmodes2], method = "pearson")
    auc.e[i, 1] <- auc(seq(1:nmodes1), m.Qne[i, 1:nmodes1])
    auc.e[i, 2] <- auc(seq(1:nmodes2), m.Qne[i, 1:nmodes2])
  }

  # Calculate groups, means and quantiles.
  Pnt.group <- CalculateGroupsMeansQuantiles(m.Pnt, ngroups, nexp)
  Pnt.group.mean <- Pnt.group$mean.total
  Pnt.group.quantile5 <- Pnt.group$quantile[1, ]
  Pnt.group.quantile95 <- Pnt.group$quantile[2, ]

  Qnt.group <- CalculateGroupsMeansQuantiles(m.Qnt, ngroups, nexp)
  Qnt.group.mean <- Qnt.group$mean.total
  Qnt.group.quantile5 <- Qnt.group$quantile[1, ]
  Qnt.group.quantile95 <- Qnt.group$quantile[2, ]

  # Plots.
  hist(id, main = family, col = "grey", xlab = "% ID con referencia")
  hist(laligned, main = family, xlab = "Número de sitios alineados", col = "grey")
  hist(MSD, main = family, xlab = "MSD", col = "grey")

  plot(Pnt.group.mean, ylab = "Pn promedio", xlab = "nmodo", type = "l", ylim = c(0, 0.07), main = family)
  lines(Pnt.group.quantile5, col = "green")
  lines(Pnt.group.quantile95, col = "green")
  points(Pne.mean, col = "red")

  plot(y = Pnt.group.mean, x = ievalues, ylab = "Pn promedio teórico", xlab = "1/evalue", ylim = c(0, 0.07), main = family)

  plot(y = Pne.mean, x = ievaluese.mean, ylab = "Pn promedio experimental", xlab = "1/evalue", ylim = c(0, 0.07), main = family)

  plot(density(rho.t[, 1]), col = "blue", ylab = "Frecuencia", xlab = "rho 10 modos", main = family)
  points(x = c(rho.e[, 1]), y = rep(0, nexp), col = "red")

  plot(density(rho.t[, 2]), col = "blue", ylab = "Frecuencia", xlab = "rho 25 modos", main = family)
  points(x = c(rho.e[, 2]), y = rep(0, nexp), col = "red")

  plot(density(auc.t[, 1]), col = "blue", ylab = "Frecuencia", xlab = "auc 10 modos", main = family)
  points(x = c(auc.e[, 1]), y = rep(0, nexp), col = "red")

  plot(density(auc.t[, 2]), col = "blue", ylab = "Frecuencia", xlab = "auc 25 modos", main = family)
  points(x = c(auc.e[, 2]), y = rep(0, nexp), col = "red")
}
```

### 2015-11-16 ExperimentalMain.R

@@ -126,12 +126,12 @@ for (P in (1:nprot)) {
 	    r.p.ref = cbind(r.p.ref, r.heme.p.ref)
 	    nsites.p.ref = ncol(r.p.ref)
 	  }
-	  not.aligned.p.ref.index <- c(not.aligned.p.ref.index, t(seq((naa.p.ref+1), nsites.p.ref)))
+	  not.aligned.p.ref.index <- c(not.aligned.p.ref.index, t(seq((naa.p.ref + 1), nsites.p.ref)))
 	  
 	  r.heme.p.2 = ReadHeme(pdbs.fname, chain.p.2)
 	  r.p.2 = cbind(r.p.2, r.heme.p.2)
 	  nsites.p.2 = ncol(r.p.2)
-	  not.aligned.p.2.index <- c(not.aligned.p.2.index, t(seq((naa.p.2+1), nsites.p.2)))
+	  not.aligned.p.2.index <- c(not.aligned.p.2.index, t(seq((naa.p.2 + 1), nsites.p.2)))
 	} else {
 	  nsites.p.ref = naa.p.ref
 	  nsites.p.2 = naa.p.2

### 2015-11-19 ComparisonsMain.Rmd
cambie ComparisonsMain.Rmd y comp_input.csv

@@
 core <- input$core[1]
-index = as.vector(input$index)
 
@@
 }
+laligned = read.csv(file.path(dir.e, paste(family, "_core_", core, "_out_m.laligned.csv", sep = "")))$x
+  index <- c()
+  for (i in (1:length(laligned))) {
+    if (laligned[i] == max(laligned)) {
+      index[i] <- i
+    }
+  }
+index <- index[!is.na(index)]
 m.Pne = read.csv(file.path(dir.e, paste(family, "_core_", core, "_out_m.Pn.csv", sep = "")))[index, 1:nmodes4]
@@
 ievaluese.mean = 1/evaluese.mean
-laligned = read.csv(file.path(dir.e, paste(family, "_core_", core, "_out_m.laligned.csv", sep = "")))$x
+
 MSD = read.csv(file.path(dir.e, paste(family, "_core_", core, "_out_MSD.csv", sep = "")))$x

### 2015-11-22 Report.Rmd
agregué archivos para crear los reportes de todas las familias

--- 2015-11-09 ComparisonsMain.Rmd
@@
 ---
-title: "Comparaciones Teórico-Experimental"
+title: "Report"
+date: "22 de noviembre de 2015"
 output: html_document
@@
 ```{r}
-# INFORMACIÓN
-#
-# Este programa genera un archivo HTLM comparando la divergencia etsructural de
-# proteínas experimentales y mutantes teóricas.
-# Para correrlo se debe completar un Input ("DATA/comp_input.csv") especificando:
-# - family: la familia de proteínas a comparar, debe estar escrita consistentemente 
-# con los archivos theoretical_input y experimental_input.
-# - p.ref: la proteína dereferencia de la familia, que debe ser escrita 
-# consisntentemente con el archivo experimental_input, es decir que debe ser escrita de la 
-# forma en la que está escrita en el dataset.
-# - heme: solo se utiliza para la familia de las globinas, puede ser "TRUE" o 
-# "FALSE" dependiendo de si se quiere considerar o no al grupo HEMO. 
-# - index: el índice de las proteínas de la familia que se desea analizar.
+# Load packages. 
+library(flux)  #  Contains function "auc".
+library(knitr)
+library(markdown)
+library(rmarkdown)
 
-# Remove objects.
-rm (list = ls())
-
-# Read Input.
-input <- read.csv("DATA/comp_input.csv")
-family <- input$family[1]
-p.ref <- input$p.ref[1]
-heme <- input$heme[1]
-core <- input$core[1]
-index = as.vector(input$index)
+# Source functions.
+source("FUNCTIONS/CalculateGroupsMeansQuantiles.R")
 
@@
 
-# Load librarys. 
-library(flux)  # function "auc".
-
-# Source functions.
-source("FUNCTIONS/CalculateGroupsMeansQuantiles.R")
-
 # Read files and calculate measures.
-# Read pdbid.
-pdbid <- read.csv(file.path("DATA/Experimental", paste(family, "_dataset.csv", sep = "")))$pdbid
-pdbid <- pdbid[pdbid != as.character(p.ref)]
+# Read pdbids.
+pdbid <- read.csv(file.path("DATA/Experimental", paste(family[f], "_dataset.csv", sep = "")))$pdbid
+pdbid <- pdbid[-which(grepl(p.ref[f], pdbid))]
 
@@
 dir.e <- "OUT/Experimental"
-if (as.character(family) == "globins") {
-  family <- paste(family, "_heme_", heme, sep = "")
+
+laligned = read.csv(file.path(dir.e, paste(input.i, "_out_m.laligned.csv", sep = "")))$x
+index <- c()
+for (i in (1:length(laligned))) {
+  if (laligned[i] == max(laligned)) {
+    index[i] <- i
   }
-m.Pne = read.csv(file.path(dir.e, paste(family, "_core_", core, "_out_m.Pn.csv", sep = "")))[index, 1:nmodes4]
+}
+index <- index[!is.na(index)]
+
+m.Pne = read.csv(file.path(dir.e, paste(input.i, "_out_m.Pn.csv", sep = "")))[index, 1:nmodes4]
 Pne.mean = colMeans(m.Pne)
+
 m.Qne = t(apply(m.Pne, 1, cumsum))
 Qne.mean = colMeans(m.Qne)
-m.evaluese = read.csv(file.path(dir.e, paste(family, "_core_", core, "_out_m.evalues.csv", sep = "")))[index, 1:nmodes4]
+
+m.evaluese = read.csv(file.path(dir.e, paste(input.i, "_out_m.evalues.csv", sep = "")))[index, 1:nmodes4]
 evaluese.mean = colMeans(m.evaluese)
 ievaluese.mean = 1/evaluese.mean
-laligned = read.csv(file.path(dir.e, paste(family, "_core_", core, "_out_m.laligned.csv", sep = "")))$x
-MSD = read.csv(file.path(dir.e, paste(family, "_core_", core, "_out_MSD.csv", sep = "")))$x
-id = read.csv(file.path(dir.e, paste(family, "_core_", core, "_out_m.ID.csv", sep = "")))$x
+
+MSD = read.csv(file.path(dir.e, paste(input.i, "_out_MSD.csv", sep = "")))$x
+
+id = read.csv(file.path(dir.e, paste(input.i, "_out_m.ID.csv", sep = "")))$x
 id.index = id[index]
@@
 dir.t <- "OUT/Theoretical"
-m.Pnt = read.csv(file.path(dir.t, paste(family, "_core_", core, "_out_m.Pn.csv", sep = "")))[, 1:nmodes4]
+
+m.Pnt = read.csv(file.path(dir.t, paste(input.i, "_out_m.Pn.csv", sep = "")))[, 1:nmodes4]
+
 m.Qnt = t(apply(m.Pnt, 1, cumsum))
-evalues = read.csv(file.path(dir.t, paste(family, "_core_", core, "_out_evalues.csv", sep = "")))$x[1:nmodes4]
-ievalues = 1/evalues
+
+evaluest = read.csv(file.path(dir.t, paste(input.i, "_out_evalues.csv", sep = "")))$x[1:nmodes4]
+
+ievaluest = 1/evaluest
 
@@
 ### Conjunto teórico
-`r nmut` mutantes de `r p.ref` de `r round(mean(id.index))` % de identidad secuencial con ANM *R0* = 12 y *Fmax* = 2.
+`r nmut` mutantes de `r p.ref[f]` de `r round(mean(id.index))` % de identidad secuencial con ANM *R0* = 12 y *Fmax* = 2.
 Se seleccionó esta proteína ya que es la que presenta menor *MSD* con respecto a las coordenadas xyz promedio de todas las proteínas del conjunto experimental.
@@
 ### Conjunto experimental 
-`r nexp` proteínas de la familia de `r family`.
+`r nexp` proteínas de la familia de `r input.i`.
 Las proteínas tienen un promedio de identidad secuencial de `r round(mean(id.index))`%.
-Todas las proteínas del sub-conjunto elegidas alinean en todos los sitios de `r p.ref`, o en como máximo 1 sitio menos.
+Todas las proteínas del sub-conjunto elegidas alinean en todos los sitios de `r p.ref[f]`.
 
@@
 for (i in (1:nmut)) {
-  rho.t.1[i, ] <- cor((as.vector(as.matrix(m.Pnt[i, 1:nmodes1])) * evalues[1:nmodes1]), ievalues[1:nmodes1], method = "pearson")	
-  rho.t.2[i, ] <- cor((as.vector(as.matrix(m.Pnt[i, 1:nmodes2])) * evalues[1:nmodes2]), ievalues[1:nmodes2], method = "pearson")	
-  rho.t.3[i, ] <- cor((as.vector(as.matrix(m.Pnt[i, 1:nmodes3])) * evalues[1:nmodes3]), ievalues[1:nmodes3], method = "pearson")	
-  rho.t.4[i, ] <- cor((as.vector(as.matrix(m.Pnt[i, 1:nmodes4])) * evalues[1:nmodes4]), ievalues[1:nmodes4], method = "pearson")	   
+  rho.t.1[i, ] <- cor((as.vector(as.matrix(m.Pnt[i, 1:nmodes1])) * evaluest[1:nmodes1]), ievaluest[1:nmodes1], method = "pearson")	
+  rho.t.2[i, ] <- cor((as.vector(as.matrix(m.Pnt[i, 1:nmodes2])) * evaluest[1:nmodes2]), ievaluest[1:nmodes2], method = "pearson")	
+  rho.t.3[i, ] <- cor((as.vector(as.matrix(m.Pnt[i, 1:nmodes3])) * evaluest[1:nmodes3]), ievaluest[1:nmodes3], method = "pearson")	
+  rho.t.4[i, ] <- cor((as.vector(as.matrix(m.Pnt[i, 1:nmodes4])) * evaluest[1:nmodes4]), ievaluest[1:nmodes4], method = "pearson")	   
 }
@@
 # Graphics.
-layout(matrix(1:2, 1, 2, byrow = T))
-plot(Pnt.group.mean, ylab = "Pn promedio", xlab = "nmodo", type = "l", ylim = c(0, 0.07), main = "Pn promedio vs. nmodo")
+layout(matrix(1:4, 2, 2, byrow = T))
+
+plot(y = Pnt.group.mean, x = ievaluest, ylab = "Pn promedio teórico", xlab = "1/evalue")
+
+plot(y = Pne.mean, x = ievaluese.mean, ylab = "Pn promedio experimental", xlab = "1/evalue")
+
+plot(Pnt.group.mean, 
+     ylab = "Pn promedio", 
+     xlab = "nmodo", 
+     type = "l", 
+     ylim = c(0, max(c(Pnt.group.quantile95, Pne.mean))))
 lines(Pnt.group.quantile5, col = "green")
@@
 points(Pne.mean, col = "red")
-plot(Qnt.group.mean, ylab = "Qn promedio", xlab = "nmodo", type = "l", ylim = c(0, 0.7), main = "Qn promedio vs. nmodo")
+
+plot(Qnt.group.mean, 
+     ylab = "Qn promedio", 
+     xlab = "nmodo", 
+     type = "l", 
+     ylim = c(0, max(c(Qnt.group.quantile95, Qne.mean))))
 lines(Qnt.group.quantile5, col = "green")
@@
 points(Qne.mean, col = "red")
+
 ```
@@
 Rojo: Experimental
-Verdes: cuartiles 0.05 y 0.95 de `r ngroups` grupos de `r nexp` mutantes teóricas
+Verdes: Cuartiles 0.05 y 0.95 de `r ngroups` grupos de `r nexp` mutantes teóricas

### 2015-11-22 CreateReports.R

@@ -1,0 +1,29 @@
+# load packages.
+library(knitr)
+library(markdown)
+library(rmarkdown)
+
+# Remove objects.
+rm (list = ls())
+
+# Read Input.
+input <- read.csv("DATA/comp_input.csv")
+family <- input$family
+p.ref <- input$p.ref
+heme <- input$heme
+core <- input$core
+
+# For each input family in the data create a report.
+# These reports are saved with the name specified by output_file
+for (f in (1:nrow(input))) {
+  print(f)
+  if (as.character(family[f]) == "globins") {
+    family.heme <- paste(family[f], "_heme_", heme[f], sep = "")
+  } else {
+    family.heme <- family[f]
+  }
+  input.i <- paste(family.heme, "_core_", core[f], sep = "")
+  rmarkdown::render('Report.Rmd', 
+                    output_file =  paste("report_", input.i, ".html", sep='') 
+                    )
+}

### 2015-11-22 FUNCTIONS/AnalyzeAlignmentGeneral.R

@@ -10,8 +10,8 @@ AnalyzeAlignmentGeneral.NoCore <- function(df.alignment) {
   
   # Extract data form the alignment.
   lalignment = ncol(alignment)
-  alignment.p.1 = alignment[id == p.1, ]
-  alignment.p.2 = alignment[id == p.2, ]
+  alignment.p.1 = alignment[which(grepl(p.1, id)), ]
+  alignment.p.2 = alignment[which(grepl(p.2, id)), ]
 
   # Get indexes.
   p.1.index = c()
@@ -68,8 +68,8 @@ AnalyzeAlignmentGeneral.Core <- function(df.alignment) {
   # Extract data form the alignment.
   nprot = nrow(alignment)
   lalignment = ncol(alignment)
-  alignment.p.1 = alignment[id == p.1, ]
-  alignment.p.2 = alignment[id == p.2, ]
+  alignment.p.1 = alignment[which(grepl(p.1, id)), ]
+  alignment.p.2 = alignment[which(grepl(p.2, id)), ]
   
   # Calculate core.index.
   gaps = matrix(nrow = lalignment, ncol = 2)

### 2016-02-09 Report.Rmd
cambios 2016

@@
 ---
-title: "Report"
-date: "22 de noviembre de 2015"
+title: "Estudio variabilidad estructural proteica"
+date: "30/01/2016"
 output: html_document
@@
 ```{r}
-# Load packages. 
-library(flux)  #  Contains function "auc".
-library(knitr)
-library(markdown)
-library(rmarkdown)
 
@@
 # Read files and calculate measures.
-# Read pdbids.
-pdbid <- read.csv(file.path("DATA/Experimental", paste(family[f], "_dataset.csv", sep = "")))$pdbid
-pdbid <- pdbid[-which(grepl(p.ref[f], pdbid))]
 
-# Read experimental output.
-dir.e <- "OUT/Experimental"
+### Experimental ###
 
-laligned = read.csv(file.path(dir.e, paste(input.i, "_out_m.laligned.csv", sep = "")))$x
-index <- c()
-for (i in (1:length(laligned))) {
-  if (laligned[i] == max(laligned)) {
-    index[i] <- i
-  }
-}
-index <- index[!is.na(index)]
+pdbid <- read.csv(file.path(data.dir, paste(family, "_dataset.csv", sep = "")))$pdbid
 
-m.Pne = read.csv(file.path(dir.e, paste(input.i, "_out_m.Pn.csv", sep = "")))[index, 1:nmodes4]
-Pne.mean = colMeans(m.Pne)
+n.sites.p.1 = read.csv(file.path(out.dir, paste(family, "_out_m.n.sites.p.1.csv", sep = "")))$V1[1]
+m.n.sites.p.2 = read.csv(file.path(out.dir, paste(family, "_out_m.n.sites.p.2.csv", sep = "")))$V1
 
-m.Qne = t(apply(m.Pne, 1, cumsum))
-Qne.mean = colMeans(m.Qne)
+n.core = read.csv(file.path(out.dir, paste(family, "_out_m.n.core.csv", sep = "")))$V1[1]
+m.n.aligned = read.csv(file.path(out.dir, paste(family, "_out_m.n.aligned.csv", sep = "")))$V1
 
-m.evaluese = read.csv(file.path(dir.e, paste(input.i, "_out_m.evalues.csv", sep = "")))[index, 1:nmodes4]
-evaluese.mean = colMeans(m.evaluese)
-ievaluese.mean = 1/evaluese.mean
+identity = read.csv(file.path(out.dir, paste(family, "_out_m.identity.csv", sep = "")))$V1
 
-MSD = read.csv(file.path(dir.e, paste(input.i, "_out_MSD.csv", sep = "")))$x
+m.exp.va = read.csv(file.path(out.dir, paste(family.heme.model.core, "_out_m.exp.va.csv", sep = "")))[, 1:nmodes4]
+mean.exp.va = colMeans(m.exp.va)
+i.mean.exp.va = 1/mean.exp.va
 
-id = read.csv(file.path(dir.e, paste(input.i, "_out_m.ID.csv", sep = "")))$x
-id.index = id[index]
+m.exp.Pn = read.csv(file.path(out.dir, paste(family.heme.model.core, "_out_m.exp.Pn.csv", sep = "")))[, 1:nmodes4]
+mean.exp.Pn = colMeans(m.exp.Pn)
 
-# Read theoretical output.
-dir.t <- "OUT/Theoretical"
+m.exp.dr.squarei = read.csv(file.path(out.dir, paste(family.heme.model.core, "_out_m.exp.dr.squarei.csv", sep = "")))
+exp.MSDi = colMeans(m.exp.dr.squarei, na.rm = T )
+exp.MSD = rowMeans(m.exp.dr.squarei, na.rm = T)
 
-m.Pnt = read.csv(file.path(dir.t, paste(input.i, "_out_m.Pn.csv", sep = "")))[, 1:nmodes4]
+m.exp.Qn = t(apply(m.exp.Pn, 1, cumsum))
+mean.exp.Qn = colMeans(m.exp.Qn)
 
-m.Qnt = t(apply(m.Pnt, 1, cumsum))
+family.data <- data.frame(pdbid, nsites = m.n.sites.p.2, naligned = m.n.aligned, identity, MSD = exp.MSD)
 
-evaluest = read.csv(file.path(dir.t, paste(input.i, "_out_evalues.csv", sep = "")))$x[1:nmodes4]
+### Theoretical ###
+m.theo.va = read.csv(file.path(out.dir, paste(family.heme.model.core, "_out_m.theo.va.csv", sep = "")))[, 1:nmodes4]
+mean.theo.va = colMeans(m.theo.va)
+i.mean.theo.va = 1/mean.theo.va
 
-ievaluest = 1/evaluest
+m.theo.Pn = read.csv(file.path(out.dir, paste(family.heme.model.core, "_out_m.theo.Pn.csv", sep = "")))[, 1:nmodes4]
+
+m.theo.dr.squarei = read.csv(file.path(out.dir, paste(family.heme.model.core, "_out_m.theo.dr.squarei.csv", sep = "")))
+theo.MSDi = colMeans(m.theo.dr.squarei, na.rm = T)
+theo.MSD = rowMeans(m.theo.dr.squarei, na.rm = T)
+
+m.theo.Qn = t(apply(m.theo.Pn, 1, cumsum))
 
 # Number of t and e proteins.
-nmut = nrow(m.Pnt)
-nexp = length(index)
+n.mut = nrow(m.theo.Pn)
+n.exp = length(pdbid)
 
-# Number of t groups.
-ngroups = as.integer(nmut / nexp)
 ```
 
-## Conjuntos de proteínas
+## Conjuntos de proteinas
 
-### Conjunto teórico
-`r nmut` mutantes de `r p.ref[f]` de `r round(mean(id.index))` % de identidad secuencial con ANM *R0* = 12 y *Fmax* = 2.
-Se seleccionó esta proteína ya que es la que presenta menor *MSD* con respecto a las coordenadas xyz promedio de todas las proteínas del conjunto experimental.
-El porcentaje de mutaciones se seleccionó de acuerdo al promedio de identidad secuencial de proteínas del conjunto experimental.
+### Conjunto teorico
+`r n.mut` mutantes de `r p.ref` (`r n.sites.p.1` sitios) simuladas con el modelo mutacional `r mut.model` con ANM *R0* = 12 y *Fmax* = 2.
+Para determinar que sitios mutar, se alineo `r p.ref` con cada una de las proteinas del conjunto, se obtuvieron los indices de los sitios alineados pero mutados y se simularon `r n.mut.p` mutantes por cada par de proteinas, obteniendose un total de `r n.mut.p * n.exp` mutantes.
 
 ### Conjunto experimental 
-`r nexp` proteínas de la familia de `r input.i`.
-Las proteínas tienen un promedio de identidad secuencial de `r round(mean(id.index))`%.
-Todas las proteínas del sub-conjunto elegidas alinean en todos los sitios de `r p.ref[f]`.
+`r n.exp` proteinas de la familia de `r family`. Las proteinas tienen un promedio de identidad secuencial de `r round(mean(identity))`%. El core del alineamiento de la familia es de `r n.core` sitios.
 
-La caracterización del conjunto experimental se muestra a continuación:
+La caracterizacion del conjunto experimental se muestra a continuacion:
 ```{r}
-# Analysis experimental dataset.
-layout(matrix(1:4, 2, 2, byrow = T))
-hist(id, main = "%ID con referencia", col = "grey")
-hist(laligned, main = "Número de sitios alineados con referencia", col = "grey")
-hist(MSD, main = "MSD con la referencia", col = "grey")
-plot(id, MSD, xlab = "%ID", main = "MSD vs. %ID")
-caract <- data.frame(pdbid, id, laligned, MSD)
-caract
+family.data
+
+layout(matrix(1:2, 1, 2, byrow = T)) 
+hist(exp.MSD, main = "Experimental MSD", xlab = "MSD")
+hist(theo.MSD, main = "Theoretical MSD", xlab = "MSD")
+
 ```
@@
 # Calculate rho.
-rho.t.1 <- matrix(0, nrow = nmut, ncol = 1)
-rho.t.2 <- matrix(0, nrow = nmut, ncol = 1)
-rho.t.3 <- matrix(0, nrow = nmut, ncol = 1)
-rho.t.4 <- matrix(0, nrow = nmut, ncol = 1)
-for (i in (1:nmut)) {
-  rho.t.1[i, ] <- cor((as.vector(as.matrix(m.Pnt[i, 1:nmodes1])) * evaluest[1:nmodes1]), ievaluest[1:nmodes1], method = "pearson")	
-  rho.t.2[i, ] <- cor((as.vector(as.matrix(m.Pnt[i, 1:nmodes2])) * evaluest[1:nmodes2]), ievaluest[1:nmodes2], method = "pearson")	
-  rho.t.3[i, ] <- cor((as.vector(as.matrix(m.Pnt[i, 1:nmodes3])) * evaluest[1:nmodes3]), ievaluest[1:nmodes3], method = "pearson")	
-  rho.t.4[i, ] <- cor((as.vector(as.matrix(m.Pnt[i, 1:nmodes4])) * evaluest[1:nmodes4]), ievaluest[1:nmodes4], method = "pearson")	   
+rho.t.1 <- matrix(0, nrow = n.mut, ncol = 1)
+rho.t.2 <- matrix(0, nrow = n.mut, ncol = 1)
+rho.t.3 <- matrix(0, nrow = n.mut, ncol = 1)
+rho.t.4 <- matrix(0, nrow = n.mut, ncol = 1)
+for (i in (1:n.mut)) {
+  rho.t.1[i, ] <- cor((as.vector(as.matrix(m.theo.Pn[i, 1:nmodes1])) * mean.theo.va[1:nmodes1]), i.mean.theo.va[1:nmodes1], method = "pearson")	
+  rho.t.2[i, ] <- cor((as.vector(as.matrix(m.theo.Pn[i, 1:nmodes2])) * mean.theo.va[1:nmodes2]), i.mean.theo.va[1:nmodes2], method = "pearson")	
+  rho.t.3[i, ] <- cor((as.vector(as.matrix(m.theo.Pn[i, 1:nmodes3])) * mean.theo.va[1:nmodes3]), i.mean.theo.va[1:nmodes3], method = "pearson")	
+  rho.t.4[i, ] <- cor((as.vector(as.matrix(m.theo.Pn[i, 1:nmodes4])) * mean.theo.va[1:nmodes4]), i.mean.theo.va[1:nmodes4], method = "pearson")	   
 }
-rho.e.1 <- matrix(0, nrow = nexp, ncol = 1)
-rho.e.2 <- matrix(0, nrow = nexp, ncol = 1)
-rho.e.3 <- matrix(0, nrow = nexp, ncol = 1) 
-rho.e.4 <- matrix(0, nrow = nexp, ncol = 1) 
-for (i in (1:nexp)) {
-  rho.e.1[i, ] <- cor((as.vector(as.matrix(m.Pne[i, 1:nmodes1])) * evaluese.mean[1:nmodes1]), ievaluese.mean[1:nmodes1], method = "pearson")
-  rho.e.2[i, ] <- cor((as.vector(as.matrix(m.Pne[i, 1:nmodes2])) * evaluese.mean[1:nmodes2]), ievaluese.mean[1:nmodes2], method = "pearson")
-  rho.e.3[i, ] <- cor((as.vector(as.matrix(m.Pne[i, 1:nmodes3])) * evaluese.mean[1:nmodes3]), ievaluese.mean[1:nmodes3], method = "pearson")
-  rho.e.4[i, ] <- cor((as.vector(as.matrix(m.Pne[i, 1:nmodes4])) * evaluese.mean[1:nmodes4]), ievaluese.mean[1:nmodes4], method = "pearson")
+rho.e.1 <- matrix(0, nrow = n.exp, ncol = 1)
+rho.e.2 <- matrix(0, nrow = n.exp, ncol = 1)
+rho.e.3 <- matrix(0, nrow = n.exp, ncol = 1) 
+rho.e.4 <- matrix(0, nrow = n.exp, ncol = 1) 
+for (i in (1:n.exp)) {
+  rho.e.1[i, ] <- cor((as.vector(as.matrix(m.exp.Pn[i, 1:nmodes1])) * mean.exp.va[1:nmodes1]), i.mean.exp.va[1:nmodes1], method = "pearson")
+  rho.e.2[i, ] <- cor((as.vector(as.matrix(m.exp.Pn[i, 1:nmodes2])) * mean.exp.va[1:nmodes2]), i.mean.exp.va[1:nmodes2], method = "pearson")
+  rho.e.3[i, ] <- cor((as.vector(as.matrix(m.exp.Pn[i, 1:nmodes3])) * mean.exp.va[1:nmodes3]), i.mean.exp.va[1:nmodes3], method = "pearson")
+  rho.e.4[i, ] <- cor((as.vector(as.matrix(m.exp.Pn[i, 1:nmodes4])) * mean.exp.va[1:nmodes4]), i.mean.exp.va[1:nmodes4], method = "pearson")
 }
@@
 # Calculate auc.
-auc.t.1 <- matrix(0, nrow = nmut, ncol = 1)
-auc.t.2 <- matrix(0, nrow = nmut, ncol = 1)
-auc.t.3 <- matrix(0, nrow = nmut, ncol = 1)
-auc.t.4 <- matrix(0, nrow = nmut, ncol = 1)
-for (i in (1:nmut)) {
-  auc.t.1[i, ] <- auc(seq(1:nmodes1), m.Qnt[i,1:nmodes1])
-  auc.t.2[i, ] <- auc(seq(1:nmodes2), m.Qnt[i,1:nmodes2])
-  auc.t.3[i, ] <- auc(seq(1:nmodes3), m.Qnt[i,1:nmodes3])
-  auc.t.4[i, ] <- auc(seq(1:nmodes4), m.Qnt[i,1:nmodes4])
+auc.t.1 <- matrix(0, nrow = n.mut, ncol = 1)
+auc.t.2 <- matrix(0, nrow = n.mut, ncol = 1)
+auc.t.3 <- matrix(0, nrow = n.mut, ncol = 1)
+auc.t.4 <- matrix(0, nrow = n.mut, ncol = 1)
+for (i in (1:n.mut)) {
+  auc.t.1[i, ] <- auc(seq(1:nmodes1), m.theo.Qn[i,1:nmodes1])
+  auc.t.2[i, ] <- auc(seq(1:nmodes2), m.theo.Qn[i,1:nmodes2])
+  auc.t.3[i, ] <- auc(seq(1:nmodes3), m.theo.Qn[i,1:nmodes3])
+  auc.t.4[i, ] <- auc(seq(1:nmodes4), m.theo.Qn[i,1:nmodes4])
 }
-auc.e.1 <- matrix(0, nrow = nexp, ncol = 1)
-auc.e.2 <- matrix(0, nrow = nexp, ncol = 1)
-auc.e.3 <- matrix(0, nrow = nexp, ncol = 1)
-auc.e.4 <- matrix(0, nrow = nexp, ncol = 1)
-for (i in (1:nexp)) {
-  auc.e.1[i, ] <- auc(seq(1:nmodes1), m.Qne[i, 1:nmodes1])
-  auc.e.2[i, ] <- auc(seq(1:nmodes2), m.Qne[i, 1:nmodes2])
-  auc.e.3[i, ] <- auc(seq(1:nmodes3), m.Qne[i, 1:nmodes3])
-  auc.e.4[i, ] <- auc(seq(1:nmodes4), m.Qne[i, 1:nmodes4])
+auc.e.1 <- matrix(0, nrow = n.exp, ncol = 1)
+auc.e.2 <- matrix(0, nrow = n.exp, ncol = 1)
+auc.e.3 <- matrix(0, nrow = n.exp, ncol = 1)
+auc.e.4 <- matrix(0, nrow = n.exp, ncol = 1)
+for (i in (1:n.exp)) {
+  auc.e.1[i, ] <- auc(seq(1:nmodes1), m.exp.Qn[i, 1:nmodes1])
+  auc.e.2[i, ] <- auc(seq(1:nmodes2), m.exp.Qn[i, 1:nmodes2])
+  auc.e.3[i, ] <- auc(seq(1:nmodes3), m.exp.Qn[i, 1:nmodes3])
+  auc.e.4[i, ] <- auc(seq(1:nmodes4), m.exp.Qn[i, 1:nmodes4])
 }
@@
 ### RHO y AUC
-Las distribuciones de *auc* y *rho* para cada conjunto se muestran a continuación (azul= teórico, rojo = experimental)
+Las distribuciones de *auc* y *rho* para cada conjunto se muestran a continuacion (azul= teorico, rojo = experimental)
 
@@
 plot(density(rho.t.1), col = "blue", ylab = "Frecuencia", xlab = "rho", main = "Histograma rho 10 modos")
-points(x = c(rho.e.1), y = rep(0, nexp), col = "red")
+points(x = c(rho.e.1), y = rep(0, n.exp), col = "red")
 plot(density(auc.t.1), col = "blue", ylab = "Frecuencia", xlab = "auc", main = "Histograma auc 10 modos")
-points(x = c(auc.e.1), y = rep(0, nexp), col = "red")
+points(x = c(auc.e.1), y = rep(0, n.exp), col = "red")
 plot(density(rho.t.2), col = "blue", ylab = "Frecuencia", xlab = "rho", main = "Histograma rho 25 modos")
-points(x = c(rho.e.2), y = rep(0, nexp), col = "red")
+points(x = c(rho.e.2), y = rep(0, n.exp), col = "red")
 plot(density(auc.t.2), col = "blue", ylab = "Frecuencia", xlab = "auc", main = "Histograma auc 25 modos")
-points(x = c(auc.e.2), y = rep(0, nexp), col = "red")
+points(x = c(auc.e.2), y = rep(0, n.exp), col = "red")
 ```
@@
 plot(density(rho.t.3), col = "blue", ylab = "Frecuencia", xlab = "rho", main = "Histograma rho 50 modos")
-points(x = c(rho.e.3), y = rep(0, nexp), col = "red")
+points(x = c(rho.e.3), y = rep(0, n.exp), col = "red")
 plot(density(auc.t.3), col = "blue", ylab = "Frecuencia", xlab = "auc", main = "Histograma auc 50 modos")
-points(x = c(auc.e.3), y = rep(0, nexp), col = "red")
+points(x = c(auc.e.3), y = rep(0, n.exp), col = "red")
 plot(density(rho.t.4), col = "blue", ylab = "Frecuencia", xlab = "rho", main = "Histograma rho 100 modos")
-points(x = c(rho.e.4), y = rep(0, nexp), col = "red")
+points(x = c(rho.e.4), y = rep(0, n.exp), col = "red")
 plot(density(auc.t.4), col = "blue", ylab = "Frecuencia", xlab = "auc", main = "Histograma auc 100 nmodos")
-points(x = c(auc.e.4), y = rep(0, nexp), col = "red")
+points(x = c(auc.e.4), y = rep(0, n.exp), col = "red")
 ```
@@
 # Calculate groups, means and quantiles.
-Pnt.group <- CalculateGroupsMeansQuantiles(m.Pnt, ngroups, nexp)
-Pnt.group.mean <- Pnt.group$mean.total
-Pnt.group.quantile5 <- Pnt.group$quantile[1, ]
-Pnt.group.quantile95 <- Pnt.group$quantile[2, ] 
-Qnt.group <- CalculateGroupsMeansQuantiles(m.Qnt, ngroups, nexp)
-Qnt.group.mean <- Qnt.group$mean.total
-Qnt.group.quantile5 <- Qnt.group$quantile[1, ]
-Qnt.group.quantile95 <- Qnt.group$quantile[2, ]
+theo.Pn.group <- CalculateGroupsMeansQuantiles(m.theo.Pn, n.mut.p, n.exp)
+mean.theo.Pn.group <- theo.Pn.group$mean.total
+theo.Pn.group.quantile5 <- theo.Pn.group$quantile[1, ]
+theo.Pn.group.quantile95 <- theo.Pn.group$quantile[2, ] 
+theo.Qn.group <- CalculateGroupsMeansQuantiles(m.theo.Qn, n.mut.p, n.exp)
+mean.theo.Qn.group <- theo.Qn.group$mean.total
+theo.Qn.group.quantile5 <- theo.Qn.group$quantile[1, ]
+theo.Qn.group.quantile95 <- theo.Qn.group$quantile[2, ]
 
@@
 
-plot(y = Pnt.group.mean, x = ievaluest, ylab = "Pn promedio teórico", xlab = "1/evalue")
+plot(y = mean.theo.Pn.group, x = i.mean.theo.va, ylab = "Pn promedio teorico", xlab = "1/evalue") 
+plot(y = mean.exp.Pn, x = i.mean.exp.va, ylab = "Pn promedio experimental", xlab = "1/evalue")
 
-plot(y = Pne.mean, x = ievaluese.mean, ylab = "Pn promedio experimental", xlab = "1/evalue")
-
-plot(Pnt.group.mean, 
+plot(mean.theo.Pn.group, 
      ylab = "Pn promedio", 
@@
      type = "l", 
-     ylim = c(0, max(c(Pnt.group.quantile95, Pne.mean))))
-lines(Pnt.group.quantile5, col = "green")
-lines(Pnt.group.quantile95, col = "green")
-points(Pne.mean, col = "red")
+     ylim = c(0, max(c(theo.Pn.group.quantile95, mean.exp.Pn))))
+lines(theo.Pn.group.quantile5, col = "green")
+lines(theo.Pn.group.quantile95, col = "green")
+points(mean.exp.Pn, col = "red")
 
-plot(Qnt.group.mean, 
+plot(mean.theo.Qn.group, 
      ylab = "Qn promedio", 
@@
      type = "l", 
-     ylim = c(0, max(c(Qnt.group.quantile95, Qne.mean))))
-lines(Qnt.group.quantile5, col = "green")
-lines(Qnt.group.quantile95, col = "green")
-points(Qne.mean, col = "red")
+     ylim = c(0, max(c(theo.Qn.group.quantile95, mean.exp.Qn))))
+lines(theo.Qn.group.quantile5, col = "green")
+lines(theo.Qn.group.quantile95, col = "green")
+points(mean.exp.Qn, col = "red")
 
@@
 Rojo: Experimental
-Verdes: Cuartiles 0.05 y 0.95 de `r ngroups` grupos de `r nexp` mutantes teóricas
+Verdes: Cuartiles 0.05 y 0.95 de `r n.mut.p` grupos de `r n.exp` mutantes teoricas.

### 2016-02-09 ExperimentalMain.R

@@ -1,221 +1,0 @@
-# INFORMACIÓN:
-#
-# El programa calcula medidas de variabilidad estructural y dinámica de alineamientos múltiples de 
-# familias de proteínas provenientes de la base de datos de alineamientos múltiples "Homstrad".
-#
-# Para utilizar el programa se debe completar un input ("DATA/Experimental/inputE.csv") especificando: 
-# -family:la familia de proteínas del alineamiento, que puede ser "SerinProteases", "Globins" o "Plastocyanins"
-# -p.ref: la proteína de referncia que se desee utilizar, teniendo en cuenta que la misma debe ser escrita de 
-# la msima forma en la que se encuentra en el dataset.
-# -heme: solo se utiliza para la familia de las globinas, puede ser "TRUE" o "FALSE", dependiendo de si 
-# se desea o no considerar al grupo HEMO. 
-# -model: el modelo de red elástica a usar, que solo puede ser "ANM" por el momento.
-# -R0: cut-off del ANM.
-
-#Remove objects#
-rm(list = ls())
-
-#Read input#
-data.dir <- "DATA/Experimental"
-
-input.dir <- file.path(data.dir,"InputE.csv")
-input <- read.csv(input.dir)
-
-#Reference family and protein#
-family <- input$family
-p.ref <- input$p.ref 
-heme = input$heme
-
-#ENM#
-model <- input$model
-R0 = input$R0
-
-#Files dir#
-align.dir <- file.path(data.dir,paste(family,"Alignments.txt",sep="")) #File with a multiple sequence alignment from Homstrad#
-pdbs.dir <- file.path(data.dir,paste(family,"Coordinates.pdb",sep="")) #Coordinates of the proteins# 
-dataset.dir <- file.path(data.dir,paste(family,"Dataset.csv",sep="")) #Dataset with pdbids and chains# 
-
-#Functions dir#
-f.readCA <-"FUNCTIONS/ReadCA.R" 
-f.readHeme <- "FUNCTIONS/ReadHeme.R"  
[…]

### 2016-02-09 FUNCTIONS/Alignment.R

@@ -1,40 +1,0 @@
-#Function that analyzes the alignment of 2 proteins in terms of aligned and not aligned sites
-#The alignment of P1 and P2 (character string) and nsites of P1 must be specified
-
-alignment <- function(alignment.P1,alignment.P2,nsites.P1){
-	lalign = length(alignment.P1)
-	index.P1 = seq(1,nsites.P1)
-	
-	align.P1.index.tot = matrix(ncol = lalign , nrow = 2)
-	align.P1.index.tot[1,] = alignment.P1
-
-	count = 1
-	for (i in (1:lalign)) {
-		if (alignment.P1[i] != "-"){
-			align.P1.index.tot[2,i] <- index.P1[count]
-			count <- count +1
-		}
-	}	
-
-	align.P1.index = matrix(ncol=1,nrow=1)
-	no.align.P1.index = matrix(ncol=1,nrow=1)
-	
-	for (i in (1:lalign)) {
-		if ((alignment.P2[i] != "-") & (alignment.P1[i] != "-")){
-			align.P1.index <- cbind(align.P1.index , align.P1.index.tot[2,i])
-		}
-		if ((alignment.P2[i] == "-") & (alignment.P1[i] != "-")){
-		  no.align.P1.index <- cbind(no.align.P1.index , align.P1.index.tot[2,i])
-		}
-	}	
-	
-	align.P1.index = matrix(as.numeric(align.P1.index[-1]) , nrow=1)
-	no.align.P1.index = matrix(as.numeric(no.align.P1.index[-1]) , nrow=1)	
-	
-	nalign <- ncol(align.P1.index)
-
-output = list("align.index" = align.P1.index,"no.align.index" = no.align.P1.index,"nalign" = nalign)
-output
-}
-
-

### 2016-02-09 FUNCTIONS/AnalyzeExperimentalTheoretical.R

@@ -1,0 +1,195 @@
+# This function analises experimental and theoretical data calculating measures of variability 
+# of experimental proteins or simulated mutants respectibly. 
+# 
+#  Args:
+#    family: the family of p.ref.
+#    exp.chain.p.ref: chain of p.ref in the pdb file containing rotated coordinates of experimental proteins.
+#    n.mut.p: the number of simulated mutants to analyze for each protein of the family.
+#    R0: cut-off for the ANM.
+#    rotate: it can be "TRUE" or "FALSE". If it is "TRUE" r.p.2 is rotaded in order to minimize RMSD with r.p.ref.
+#    core: it can be "TRUE" or "FALSE". If it is "TRUE" the program only considers the conserved core of 
+#    the alignment. If it is "FALSE" the program analyzes the whole alignment.
+#    heme: argument for globins. It can be "TRUE" or "FALSE". If it is "TRUE" the program considers the hemo. 
+#    data.dir: directory of the data. It must contain the dataset and pdb file with rotated coordinates of the experimental proteins.
+#    out.dir: directory of the output. It must contain files generated with AnalyzeFamily() and GenerateMutants(). The output of this program 
+#    is also saved in out.dir.
+#    mut.name: ID of filnames of mutant proteins.
+#    out.name: ID of output filenames.
+#    TOLERANCE: 0 tolerance.
+#
+#  Requires:
+#    ReadCA
+#    ReadHeme
+#    CalculateVariability
+#    CalculateENMKeff
+#    CalculateENMK
+#
+#  Returns:
+#    File with m.exp.va in out.dir.
+#    File with m.exp.Pn in out.dir.
+#    File with m.exp.dr.squarei in out.dir.
+#    File with m.theo.va in out.dir.
+#    File with m.theo.Pn in out.dir.
+#    File with m.theo.dr.squarei in out.dir.
+
+AnalyzeExperimentalTheoretical <- function(family,
+                                           exp.chain.p.ref,
+                                           n.mut.p,
+                                           R0, 
+                                           core,
[…]

### 2016-02-09 FUNCTIONS/CalculateENMK.R

@@ -1,0 +1,50 @@
+# This function calculates K of r, its Covariance, eigenvalues and eigenvectors.
+#
+#  Args:
+#    r: 3 x nsites matrix containing the equilibrium coordinates of each site.
+#    CalculateKij: function that calculates kij between 2 sites i and j.
+#    R0: cut-off for ANM.
+#    TOLERANCE: 0 tolerance.
+#
+#  Returns;
+#    K: 3*nsites x 3*nsites K matrix of r.
+#    kij: nsites x nsites kij matrix of r.
+#    cov: 3*nsites x 3*nsites covariance matrix of K.
+#    va: eigenvalues > TOLERANCE of K.
+#    ve: eigenvectors > TOLERANCE of K.
+CalculateENMK <- function(r, CalculateKij, R0, TOLERANCE) {
+  # Calculate K.
+  nsites <- ncol(r)
+  kij <- matrix(0, ncol = nsites, nrow = nsites)
+  K <- matrix(0, ncol = 3*nsites, nrow = 3*nsites)
+  for (i in (1:(nsites - 1))) {
+    ai <- (i + (2 * (i - 1)))
+    bi <- ai + 2
+    for (j in ((i + 1) : nsites)) {
+      aj <- (j + (2 * (j - 1)))				
+      bj <- aj + 2	
+      rij <- r[1:3, j] - r[1:3, i]
+      dij <- drop(sqrt(rij %*% rij))
+      eij <- rij / dij
+      kij[i, j] <- CalculateKij(dij, R0)
+      kij[j, i] <- kij[i, j]					
+      K[ai:bi, aj:bj] <- -kij[i, j] * (eij %*% t(eij))
+      K[aj:bj, ai:bi] <- K[ai:bi, aj:bj]
+      K[ai:bi, ai:bi] <- K[ai:bi, ai:bi] - K[ai:bi, aj:bj]
+      K[aj:bj, aj:bj] <- K[aj:bj, aj:bj] - K[aj:bj, ai:bi]
+    }	
+  }
+  # Calculate and order eigenvalues and eigenvectors of K.
+  eig <- eigen(K, symmetric = TRUE)
+  ord <- sort.list(Mod(eig$values), decreasing = FALSE)
+  va <- eig$values[ord]
+  ve <- eig$vectors[, ord]
+  modes <- va > TOLERANCE
+  va <- va[modes]
+  ve  <- ve[, modes]
+  nmodes <- length(va)
[…]

### 2016-02-09 FUNCTIONS/CalculateENMKeff.R

@@ -1,0 +1,95 @@
+# This function calculates K effective of r, its eigenvalues and eigenvectors.
+#
+#  Args:
+#    r: 3 x nsites matrix containing the equilibrium coordinates of each site.
+#    aligned.index: aligned sites
+#    not.aligned.index: not aligned sites.
+#    R0: cut-off for ANM.
+#    TOLERANCE: 0 tolerance.
+#
+#  Requires:
+#    CalculateENMK
+#
+#  Returns:
+#    KEFF: 3*naligned x 3*naligned KEFF matrix.
+#    va: eigenvalues > TOLERANCE of KEFF.
+#    ve: eigenvectors > TOLERANCE of KEFF.
+
+CalculateENMKeff <- function(r, aligned.index, not.aligned.index, R0, TOLERANCE) {
+  
+  naligned = length(aligned.index)
+  n.not.aligned = length(not.aligned.index)
+  nsites = ncol(r)
+  
+  # Bind aligned and not aligned index.
+  aligned.not.aligned.index <- c(aligned.index, not.aligned.index)
+  
+  # Calculate K.
+  K <- CalculateENMK(r, CalculateKij, R0, TOLERANCE)$K
+  
+  # Order K in order to get KPP, KQQ, KPQ and KQP and KEFF.
+  sortm <- matrix(0, ncol = 3 * nsites, nrow = 1)
+  count = 1
+  for (i in (1:nsites)) {
+    for (j in (1:naligned)) {
+      if (aligned.not.aligned.index[j] == i) {
+        sortm[1, (3 * count - 2)] <- 3 * aligned.not.aligned.index[j] - 2
+        sortm[1, (3 * count - 1)] <- 3 * aligned.not.aligned.index[j] - 1
+        sortm[1, (3 * count)] <- 3 * aligned.not.aligned.index[j]
+        count <- count + 1
+      }
+    }
+  }
+  if (n.not.aligned > 0) {
+    for (i in (1:nsites)) {
+      for (j in ((naligned + 1):nsites)) {
+        if (aligned.not.aligned.index[j] == i) {
+          sortm[1, (3 * count - 2)] <- 3 * aligned.not.aligned.index[j] - 2
[…]

### 2016-02-09 FUNCTIONS/Force.R

@@ -1,21 +1,0 @@
-#Function that calculates the force that models a mutantion using LF-ENM
-#i (mutated site), r(equilibrium coordinates of atoms), kij (kij between sites i and j) and fmax (maximum value for f) must be specified
-
-force = function(i,r,kij,fmax){
-    nsites = ncol(r)
-    fvec = matrix(0,3,nsites)
-    for (j in seq(nsites)){
-        if(kij[i,j] > 0.9) {
-            rij = r[1:3,j] - r[1:3,i]
-            eij = rij/sqrt(sum(rij^2))
-            fij = fmax*sqrt(3)*runif(1,-1,1)
-            fvec[,j] = fij*eij
-            fvec[,i] = fvec[,i] - fvec[,j]
-        }
-    }
-    dim(fvec)=c(3*nsites)
-    fvec
-}
-
-
-

### 2016-02-09 FUNCTIONS/Keff.R

@@ -1,83 +1,0 @@
-#Function that calculates KEFF (K effective), its va (eigenvalues) and ve (eigenvecors)
-#r (equilibrium coordinates of atoms), aligned and not aligned indexes, kij.function (see for example Kij.ANM), R0 (cut-off for ANM) and TOLERANCE (0) must be specified
-
-keff <- function(r,align.index,no.align.index,kij.function,R0,TOLERANCE){
-
-	nalign = length(align.index)
-	n.no.align = length(no.align.index)
-	nsites = ncol(r)
-	
-	#Calculate K#
-	K <- K(r,kij.function,R0,TOLERANCE)$K 
-
-	#Order K in order to get KPP, KQQ, KPQ and KQP and KEFF = KPP - (KPQ%*%CovQQ%*%KQP)#
-	sortm <- matrix(0 , ncol = 3*nsites , nrow = 1)
-	count = 1
-	for (i in (1: nsites)){
-		for (j in (1:nalign)){
-			if (align.index[j] == i){
-				sortm[1,(3*i-2)]<- 3*count-2
-				sortm[1,(3*i-1)]<- 3*count-1
-				sortm[1,(3*i)]<- 3*count
-				count <- count + 1
-			}
-		}
-	}
-
-	if (n.no.align > 0){
-		for (i in (1:nsites)){
-			for (j in (1:n.no.align)){
-				if (no.align.index[j] == i){
-					sortm[1,(3*i-2)]<- 3*count-2
-					sortm[1,(3*i-1)]<- 3*count-1
-					sortm[1,(3*i)]<- 3*count
-					count <- count + 1
-				}
-			}
-		}
-	}
-
-
-	Kord <- K[sortm,sortm]
-
-	KPP <- Kord[(1:(3*nalign)),(1:(3*nalign))]
-
-	if(n.no.align > 0){
-
-		KQQ <- Kord[((3*nalign+1):(3*nsites)),((3*nalign+1):(3*nsites))]
-		KPQ <- Kord[(1:(3*nalign)),((3*nalign+1):(3*nsites))]
-		KQP <- t(KPQ)
-
-		#KQQ^-1#
-
-		eigQQ <- eigen(KQQ,symmetric = T)
-		veQQ <- eigQQ$vectors
-		vaQQ <- eigQQ$values
[…]

### 2016-02-09 FUNCTIONS/ReadHeme.R

@@ -1,14 +1,22 @@
-#Function that reads a pdb file and returns coordinates of NA, NB, NC, ND and Fe of the Heme group
-#A pdb file name and the chain must be specified
-
-readHeme <- function(pdb.fname,chain){
-	pdb <- read.pdb(file=pdb.fname,het2atom = TRUE)     
-	selNA <- atom.select(pdb,chain=chain,elety="NA") 
-	selNB <- atom.select(pdb,chain=chain,elety="NB")    
-	selNC <- atom.select(pdb,chain=chain,elety="NC")    
-	selND <- atom.select(pdb,chain=chain,elety="ND")    
-	selFE <- atom.select(pdb,chain=chain,elety="FE")    
-
-	xyz.heme <- matrix(c(pdb$xyz[selNA$xyz],pdb$xyz[selNB$xyz],pdb$xyz[selNC$xyz],pdb$xyz[selND$xyz],pdb$xyz[selFE$xyz]),nrow=3)
-	xyz.heme
+# This function reads a pdb file and returns coordinates of NA, NB, NC, ND and Fe of the Heme group.
+#
+#  Args:
+#    pdb.fname: pdb file name.
+#    chain: chain to read.
+#
+#  Returns:
+#    xyz.heme: Equilibrium coordinates of NA, NB, NC, ND and Fe of the Heme group.
+ReadHeme <- function(pdb.fname, chain) {
+  pdb <- read.pdb(file = pdb.fname, het2atom = TRUE)     
+  selNA <- atom.select(pdb, chain = chain, elety = "NA") 
+  selNB <- atom.select(pdb, chain = chain, elety = "NB")    
+  selNC <- atom.select(pdb, chain = chain, elety = "NC")    
+  selND <- atom.select(pdb, chain = chain, elety = "ND")    
+  selFE <- atom.select(pdb, chain = chain, elety = "FE")    
+  xyz.heme <- matrix(c(pdb$xyz[selNA$xyz], 
+                       pdb$xyz[selNB$xyz], 
+                       pdb$xyz[selNC$xyz], 
+                       pdb$xyz[selND$xyz], 
+                       pdb$xyz[selFE$xyz]), nrow=3)
+  xyz.heme
 }

### 2016-02-09 FUNCTIONS/Variability.R

@@ -1,16 +1,0 @@
-#Function that calculates measures of structural and dynamical variability between 2 proteins 
-#dr (diference between P1 and P2 equilibrium coordinates of atoms), enm.1 and enm.2 (enm containing K, va and ve) must be specified
-
-variability <- function(dr,enm.1,enm.2){
-			
-	dr.squarei <- (colSums(dr^2))
-	ov = t(enm.1$ve) %*% enm.2$ve
-  nH = exp(-rowSums(ov^2*log(ov^2+1e-10)))
-  nR = 1/rowSums(ov^4)
-  d.evalues = enm.2$va - enm.1$va
-	Pn = (t(enm.1$ve)%*%matrix(dr[1:3,],ncol=1))^2/sum((t(enm.1$ve)%*%matrix(dr[1:3,],ncol=1))^2)
-	Qn = cumsum(Pn)
-
-	output = list(dr.squarei = dr.squarei , nH = nH , nR = nR , d.evalues = d.evalues , Pn = Pn , Qn = Qn)
-	output
-}

### 2016-02-09 MainProgram.R

@@ -1,0 +1,140 @@
+# This is the main program of the project. The program simulates mutants of a given protein, analyzes the multiple
+# alignment of the family to which the protein belongs, calculates measures of variabilty of theoretical and 
+# experimental data, compares them, and generates a report.
+# To run the program it is necessary to fill the input file ("input.csv") with the following information:
+#
+#    - family: the family of the protein to mutate. It can be "globins", "serinProteases", "plastocyanins", 
+#    "snakesToxin", "sh3", "proteasome", "lipocalin", "fabp", "kinase", "rrm", "phoslip", "gluts" and "ldh".
+#    - p.ref: the pdb code (pdbid) of the protein to mutate (example: "1a6m"). The protein must be a member of
+#    the selected family.
+#    - theo.chain.p.ref: the chain of p.ref to mutate.
+#    - exp.chain.p.ref: the chain of p.ref in the pdb file obtained from Homstrad.
+#    - mut.model: mutational model. It can be "LFENM" or "MND".
+#    - n.mut.p: the number of mutants to generate for each member of the family.
+#    - fmax: the maximun value for the forces that model the mutations.
+#    - R0: the cut-off for the ANM.
+#    - rotate: it can be "TRUE" or "FALSE". If it is "TRUE" r.p.2 is rotated in order to minimize RMSD with r.p.ref.
+#    - core: it can be "TRUE" or "FALSE". If it is "TRUE" the program only considers the conserved core of 
+#    the alignment. If it is "FALSE" the program analyzes the whole alignment.
+#    - heme: argument for globins. It can be "TRUE" or "FALSE". If it is "TRUE" the program considers the hemo group.
+#    - analyze.family: It can be "TRUE" or "FALSE". If it is true the program analyzes the family.
+#    - generate.mutants: It can be "TRUE" or "FALSE". If it is true the program generates new mutants.
+
+# Remove objects.
+rm(list = ls())
+
+# Load packages.
+library(bio3d) 
+library(flux)
+library(knitr)
+library(markdown)
+library(MASS)
+library(rmarkdown)
+library(seqinr) 
+
+# Data dir.
+data.dir <- "DATA"
+
+# Output dir.
+out.dir <- "OUT"
+
+# General parameters.
+TOLERANCE = 1e-10
+
+# Functions filenames.
[…]

### 2016-02-15 Report.Rmd
nuevos informes

@@
 pdbid <- read.csv(file.path(data.dir, paste(family, "_dataset.csv", sep = "")))$pdbid
+n.exp = length(pdbid)
 
@@
 m.theo.Pn = read.csv(file.path(out.dir, paste(family.heme.model.core, "_out_m.theo.Pn.csv", sep = "")))[, 1:nmodes4]
+n.mut = nrow(m.theo.Pn)
 
@@
 
+theo.MSD.group <- CalculateGroupsMeansQuantiles(cbind(theo.MSD,theo.MSD), n.exp, n.mut.p)
+mean.theo.MSD.group <- theo.MSD.group$mean.group[,1]
+
 m.theo.Qn = t(apply(m.theo.Pn, 1, cumsum))
-
-# Number of t and e proteins.
-n.mut = nrow(m.theo.Pn)
-n.exp = length(pdbid)
 
@@
 ### Conjunto teorico
-`r n.mut` mutantes de `r p.ref` (`r n.sites.p.1` sitios) simuladas con el modelo mutacional `r mut.model` con ANM *R0* = 12 y *Fmax* = 2.
+`r n.mut` mutantes de `r p.ref` (`r n.sites.p.1` sitios) simuladas con el modelo mutacional `r mut.model` con ANM *R0* = 12 y *Fmax* = 2 (solo para LFENM).
 Para determinar que sitios mutar, se alineo `r p.ref` con cada una de las proteinas del conjunto, se obtuvieron los indices de los sitios alineados pero mutados y se simularon `r n.mut.p` mutantes por cada par de proteinas, obteniendose un total de `r n.mut.p * n.exp` mutantes.
+Luego, para el analisis, se tomaron como alineados los sitios alineados de `r p.ref` para cada par de proteinas.
 
@@
 
-layout(matrix(1:2, 1, 2, byrow = T)) 
+layout(matrix(1:4, 2, 2, byrow = T)) 
 hist(exp.MSD, main = "Experimental MSD", xlab = "MSD")
 hist(theo.MSD, main = "Theoretical MSD", xlab = "MSD")
+
+plot(exp.MSD, identity, xlab = "experimental MSD")
+plot(mean.theo.MSD.group, identity, xlab = "mean theoretical MSD")
 
@@
 ```{r}
+# Re-ordenate Pn and Qn.
+m.theo.index = matrix(ncol = 1, nrow = n.mut)
+for (P in (1:n.exp)) {
+  for (mut in (1:n.mut.p)) {
+    m.theo.index[(P - 1) * n.mut.p + mut, ] = (mut - 1) * 10 + P
+  }
+}
+m.theo.Pn = m.theo.Pn[as.vector(m.theo.index), ]
+m.theo.Qn = m.theo.Qn[as.vector(m.theo.index), ]
 

### 2016-02-15 FUNCTIONS/AnalyzeAlignment.R

@@ -1,50 +1,50 @@
-# This function calculates aligned and not aligned sites of two proteins p.1 and p.2 in a 
+# This function calculates aligned and not aligned sites of two proteins p.ref and p.2 in a 
 # multiple alignment. It does two types of analysis:
-#  - CORE = TRUE: aligned and not aligned sites of p.1 and p.2 that are in the 
+#  - CORE = FALSE: all aligned and not aligned sites of p.ref and p.2.
+#  - CORE = TRUE: aligned and not aligned sites of p.ref and p.2 that are in the 
 # conserved core of the alignment: positions with no gaps in the whole alignemnt.
-#  - CORE = FALSE: all aligned and not aligned sites of p.1 and p.2.
 #
 #  Args:
 #      alignment: multiple alignment.
-#      pdbid: pdbid of proteins in the rows of the alignment.
-#      p.1: pdbid of one of the reference protein.
+#      pdbid: pdbidS of proteins in the rows of the alignment.
+#      p.ref: pdbid of the reference protein.
 #      p.2: pdbid of the other protein to analyze.
 #
 #  Returns:
-#    n.sites.p.1: n sites of p.1.
+#    n.sites.p.ref: n sites of p.ref.
 #    n.sites.p.2: n sites of p.2.
-#    n.aligned: n aligned sites of p.1.
-#    aligned.p.1.index: aligned sites of p.1.
+#    n.aligned: n aligned sites of p.ref.
+#    aligned.p.ref.index: aligned sites of p.ref.
 #    aligned.p.2.index: aligned sites of p.2.
-#    not.aligned.p.1.index: not aligned sites of p.1.
+#    not.aligned.p.ref.index: not aligned sites of p.ref.
 #    not.aligned.p.2.index: not aligned sites of p.2.
-#    n.aligned.mut.p.1: n aligned but mutated sites of p.1.
-#    aligned.mut.p.1.index: aligned but mutated sites of p.1.
+#    n.aligned.mut.p.ref: n aligned but mutated sites of p.ref.
+#    aligned.mut.p.ref.index: aligned but mutated sites of p.ref.
 #    n.core: n core sites.
-#    core.p.1.index: core sites of p.1.
+#    core.p.ref.index: core sites of p.ref.
[…]

### 2016-02-15 FUNCTIONS/AnalyzeExperimentalTheoretical.R

@@ -1,18 +1,19 @@
-# This function analises experimental and theoretical data calculating measures of variability 
-# of experimental proteins or simulated mutants respectibly. 
+# This function analyzes experimental and theoretical data calculating measures of variability 
+# of experimental proteins and simulated mutants respectibly. 
 # 
 #  Args:
 #    family: the family of p.ref.
-#    exp.chain.p.ref: chain of p.ref in the pdb file containing rotated coordinates of experimental proteins.
-#    n.mut.p: the number of simulated mutants to analyze for each protein of the family.
+#    exp.chain.p.ref: the chain of p.ref in the pdb file obtained from Homstrad.
+#    n.mut.p: the number of simulated mutants generated for each protein of the family.
 #    R0: cut-off for the ANM.
-#    rotate: it can be "TRUE" or "FALSE". If it is "TRUE" r.p.2 is rotaded in order to minimize RMSD with r.p.ref.
-#    core: it can be "TRUE" or "FALSE". If it is "TRUE" the program only considers the conserved core of 
-#    the alignment. If it is "FALSE" the program analyzes the whole alignment.
-#    heme: argument for globins. It can be "TRUE" or "FALSE". If it is "TRUE" the program considers the hemo. 
-#    data.dir: directory of the data. It must contain the dataset and pdb file with rotated coordinates of the experimental proteins.
-#    out.dir: directory of the output. It must contain files generated with AnalyzeFamily() and GenerateMutants(). The output of this program 
-#    is also saved in out.dir.
+#    rotate: it can be "TRUE" or "FALSE". If it is "TRUE", r.p.2 is rotaded in order to minimize RMSD with r.p.ref.
+#    core: it can be "TRUE" or "FALSE". If it is "TRUE", the program only considers the conserved core of 
+#    the alignment. If it is "FALSE", the program analyzes the whole alignment.
+#    heme: argument for globins. It can be "TRUE" or "FALSE". If it is "TRUE", the program considers the heme group. 
+#    data.dir: directory of the data. It must contain the file with the dataset ("data.dir/family_dataset.csv") and the pdb file 
[…]

### 2016-02-15 FUNCTIONS/GenerateMutants.R

@@ -1,16 +1,17 @@
-# This function generates  mutants of a given protein using two possible models:
-# - "LFENM" (Linearly Forced - Elastic Network Model) considering additive single mutations.
-# - "MND" (Multivariate Normal Distribution) considering mu = dr expected value = 0 and Sigma = Cov.
+# This function generates mutants of a given protein using two possible models:
+# - "LFENM" (Linearly Forced - Elastic Network Model), considering additive single mutations.
+# - "MND" (Multivariate Normal Distribution), considering mu = dr expected value = 0 and Sigma = Cov.
 #
 #  Args:
+#    family: the family of the protein to mutate.
 #    p.ref: the pdb code (pdbid) of the protein to mutate.
+#    chain: the chain of p.ref to mutate.
 #    mut.model: mutational model. It can be "LFENM" or "MND".
-#    theo.chain.p.ref: the chain of p.ref to mutate.
 #    n.mut.p: the number of mutants to generate for each protein of the family.
-#    fmax: the maximun value for the forces that model the mutations.
-#    R0: the cut-off for the ANM.
-#    heme: argument for globins. It can be "TRUE" or "FALSE". If it is "TRUE" the program considers the hemo group.
-#    data.dir: directory of the data. It must contain the file "_out_m.aligned.mut.p.1.index.csv" with indexes to mutate.
+#    fmax: argument for "LFENM". It is the maximun value for the forces that model the mutations.
+#    R0: the cut-off for the ANM ("Anisotropic Network Model").
+#    heme: argument for "globins". It can be "TRUE" or "FALSE". If it is "TRUE" the program considers the heme group.
+#    data.dir: directory of the data. It must contain the file "_out_m.aligned.mut.p.ref.index.csv" with indexes to mutate.
 #    This file is generated using AnalyzeFamily().
 #    out.dir: output directory.
 #    out.name: ID for output filenames.
@@ -41,7 +42,7 @@ GenerateMutants <- function(family,
 
   # Filenames.
   pdb.fname <- file.path(data.dir, paste(p.ref, ".pdb", sep = ""))
[…]

### 2016-03-06 MultipleReport.Rmd
cambios 6/3/16

---
title: "Estudio variabilidad estructural proteica"
output: html_document
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(warning = FALSE, echo = FALSE, message = FALSE)
```

```{r}
# Load library.
library(flux)

# Source functions.
source("FUNCTIONS/CalculateGroupsMeansQuantiles.R")

# Nmodes to analyze.
nmodes1 = 10 
nmodes2 = 25
nmodes3 = 50

# Read files and calculate measures.

data.dir <- "DATA"
out.dir <- "OUT"

# Family.

pdbid <- read.csv(file.path(data.dir, paste(family, "_dataset.csv", sep = "")))$pdbid
n.exp = length(pdbid)

n.sites.p.1 = read.csv(file.path(out.dir, paste(family, "_out_m.n.sites.p.ref.csv", sep = "")))$V1[1]
m.n.sites.p.2 = read.csv(file.path(out.dir, paste(family, "_out_m.n.sites.p.2.csv", sep = "")))$V1

n.core = read.csv(file.path(out.dir, paste(family, "_out_m.n.core.csv", sep = "")))$V1[1]
m.n.aligned = read.csv(file.path(out.dir, paste(family, "_out_m.n.aligned.csv", sep = "")))$V1

identity = read.csv(file.path(out.dir, paste(family, "_out_m.identity.csv", sep = "")))$V1

### natural_selection = FALSE, core = FALSE ####

analysis.fname.id <- paste(family, "_mut.model_", mut.model, "_naturalSelection_", "FALSE", "_R0_", R0, "_core_", "FALSE", "_K.analysis_", K.analysis, sep = "")

m.cF.exp.va = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.exp.va.csv", sep = "")))[, 1:nmodes3]
i.m.cF.exp.va = 1/m.cF.exp.va

m.cF.exp.Pn = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.exp.Pn.csv", sep = "")))[, 1:nmodes3]
mean.cF.exp.Pn = colMeans(m.cF.exp.Pn)

cF.exp.Pn.quantile1 = matrix(0, ncol = ncol(m.cF.exp.Pn), nrow = 1)
cF.exp.Pn.quantile2 = matrix(0, ncol = ncol(m.cF.exp.Pn), nrow = 1)

for (i in (1:ncol(m.cF.exp.Pn))){
    cF.exp.Pn.quantiles = as.vector(quantile((m.cF.exp.Pn[, i]), probs = c(0.05, 0.95)))
    cF.exp.Pn.quantile1[1, i] = cF.exp.Pn.quantiles[1]
    cF.exp.Pn.quantile2[1, i] = cF.exp.Pn.quantiles[2]
}

m.cF.exp.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.exp.dr.squarei.csv", sep = "")))
cF.exp.MSDi = colMeans(m.cF.exp.dr.squarei, na.rm = T )
cF.exp.MSD = rowMeans(m.cF.exp.dr.squarei, na.rm = T)

m.cF.exp.Qn = t(apply(m.cF.exp.Pn, 1, cumsum))
mean.cF.exp.Qn = colMeans(m.cF.exp.Qn)

cF.exp.Qn.quantile1 = matrix(0, ncol = ncol(m.cF.exp.Qn), nrow = 1)
cF.exp.Qn.quantile2 = matrix(0, ncol = ncol(m.cF.exp.Qn), nrow = 1)

for (i in (1:ncol(m.cF.exp.Qn))){
    cF.exp.Qn.quantiles = as.vector(quantile((m.cF.exp.Qn[, i]), probs = c(0.05, 0.95)))
    cF.exp.Qn.quantile1[1, i] = cF.exp.Qn.quantiles[1]
    cF.exp.Qn.quantile2[1, i] = cF.exp.Qn.quantiles[2]
}

family.data <- data.frame(pdbid, nsites = m.n.sites.p.2, naligned = m.n.aligned, identity, MSD = cF.exp.MSD)

### Theoretical ###

m.nsF.cF.theo.va = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.va.csv", sep = "")))[, 1:nmodes3]
i.m.nsF.cF.theo.va = 1/m.nsF.cF.theo.va

m.nsF.cF.theo.Pn = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.Pn.csv", sep = "")))[, 1:nmodes3]
n.mut = nrow(m.nsF.cF.theo.Pn)

m.nsF.cF.theo.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.dr.squarei.csv", sep = "")))
nsF.cF.theo.MSDi = colMeans(m.nsF.cF.theo.dr.squarei, na.rm = T)
nsF.cF.theo.MSD = rowMeans(m.nsF.cF.theo.dr.squarei, na.rm = T)

nsF.cF.theo.MSD.group <- CalculateGroupsMeansQuantiles(cbind(nsF.cF.theo.MSD,nsF.cF.theo.MSD), n.exp, n.mut.p)
mean.nsF.cF.theo.MSD.group <- nsF.cF.theo.MSD.group$mean.group[,1]

m.nsF.cF.theo.Qn = t(apply(m.nsF.cF.theo.Pn, 1, cumsum))

### natural_selection = TRUE, core = FALSE ####

analysis.fname.id <- paste(family, "_mut.model_", mut.model, "_naturalSelection_", "TRUE", "_R0_", R0, "_core_", "FALSE", "_K.analysis_", K.analysis, sep = "")

m.nsT.cF.theo.va = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.va.csv", sep = "")))[, 1:nmodes3]
i.m.nsT.cF.theo.va = 1/m.nsT.cF.theo.va

m.nsT.cF.theo.Pn = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.Pn.csv", sep = "")))[, 1:nmodes3]
n.mut = nrow(m.nsT.cF.theo.Pn)

m.nsT.cF.theo.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.dr.squarei.csv", sep = "")))
nsT.cF.theo.MSDi = colMeans(m.nsT.cF.theo.dr.squarei, na.rm = T)
nsT.cF.theo.MSD = rowMeans(m.nsT.cF.theo.dr.squarei, na.rm = T)

nsT.cF.theo.MSD.group <- CalculateGroupsMeansQuantiles(cbind(nsT.cF.theo.MSD,nsT.cF.theo.MSD), n.exp, n.mut.p)
mean.nsT.cF.theo.MSD.group <- nsT.cF.theo.MSD.group$mean.group[,1]

m.nsT.cF.theo.Qn = t(apply(m.nsT.cF.theo.Pn, 1, cumsum))

### natural_selection = FALSE, core = TRUE ####

analysis.fname.id <- paste(family, "_mut.model_", mut.model, "_naturalSelection_", "FALSE", "_R0_", R0, "_core_", "TRUE", "_K.analysis_", K.analysis, sep = "")

m.cT.exp.va = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.exp.va.csv", sep = "")))[, 1:nmodes3]
i.m.cT.exp.va = 1/m.cT.exp.va

m.cT.exp.Pn = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.exp.Pn.csv", sep = "")))[, 1:nmodes3]
mean.cT.exp.Pn = colMeans(m.cT.exp.Pn)

cT.exp.Pn.quantile1 = matrix(0, ncol = ncol(m.cT.exp.Pn), nrow = 1)
cT.exp.Pn.quantile2 = matrix(0, ncol = ncol(m.cT.exp.Pn), nrow = 1)

for (i in (1:ncol(m.cT.exp.Pn))){
    cT.exp.Pn.quantiles <- as.vector(quantile((m.cT.exp.Pn[, i]), probs = c(0.05, 0.95)))
    cT.exp.Pn.quantile1[1, i] = cT.exp.Pn.quantiles[1]
    cT.exp.Pn.quantile2[1, i] = cT.exp.Pn.quantiles[2]
}

m.cT.exp.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.exp.dr.squarei.csv", sep = "")))
cT.exp.MSDi = colMeans(m.cT.exp.dr.squarei, na.rm = T )
cT.exp.MSD = rowMeans(m.cT.exp.dr.squarei, na.rm = T)

m.cT.exp.Qn = t(apply(m.cT.exp.Pn, 1, cumsum))
mean.cT.exp.Qn = colMeans(m.cT.exp.Qn)

cT.exp.Qn.quantile1 = matrix(0, ncol = ncol(m.cT.exp.Qn), nrow = 1)
cT.exp.Qn.quantile2 = matrix(0, ncol = ncol(m.cT.exp.Qn), nrow = 1)

for (i in (1:ncol(m.cT.exp.Qn))){
    cT.exp.Qn.quantiles = as.vector(quantile((m.cT.exp.Qn[, i]), probs = c(0.05, 0.95)))
    cT.exp.Qn.quantile1[1, i] = cT.exp.Qn.quantiles[1]
    cT.exp.Qn.quantile2[1, i] = cT.exp.Qn.quantiles[2]
}

### Theoretical ###

m.nsF.cT.theo.va = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.va.csv", sep = "")))[, 1:nmodes3]
i.m.nsF.cT.theo.va = 1/m.nsF.cT.theo.va

m.nsF.cT.theo.Pn = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.Pn.csv", sep = "")))[, 1:nmodes3]
n.mut = nrow(m.nsF.cT.theo.Pn)

m.nsF.cT.theo.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.dr.squarei.csv", sep = "")))
nsF.cT.theo.MSDi = colMeans(m.nsF.cT.theo.dr.squarei, na.rm = T)
nsF.cT.theo.MSD = rowMeans(m.nsF.cT.theo.dr.squarei, na.rm = T)
nsF.cT.theo.MSD.group <- CalculateGroupsMeansQuantiles(cbind(nsF.cT.theo.MSD,nsF.cT.theo.MSD), n.exp, n.mut.p)
mean.nsF.cT.theo.MSD.group <- nsF.cT.theo.MSD.group$mean.group[,1]

m.nsF.cT.theo.Qn = t(apply(m.nsF.cT.theo.Pn, 1, cumsum))

### natural_selection = TRUE, core = TRUE ####

analysis.fname.id <- paste(family, "_mut.model_", mut.model, "_naturalSelection_", "TRUE", "_R0_", R0, "_core_", "TRUE", "_K.analysis_", K.analysis, sep = "")

m.nsT.cT.theo.va = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.va.csv", sep = "")))[, 1:nmodes3]
i.m.nsT.cT.theo.va = 1/m.nsT.cT.theo.va

m.nsT.cT.theo.Pn = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.Pn.csv", sep = "")))[, 1:nmodes3]
n.mut = nrow(m.nsT.cT.theo.Pn)

m.nsT.cT.theo.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.dr.squarei.csv", sep = "")))
nsT.cT.theo.MSDi = colMeans(m.nsT.cT.theo.dr.squarei, na.rm = T)
nsT.cT.theo.MSD = rowMeans(m.nsT.cT.theo.dr.squarei, na.rm = T)

nsT.cT.theo.MSD.group <- CalculateGroupsMeansQuantiles(cbind(nsT.cT.theo.MSD,nsT.cT.theo.MSD), n.exp, n.mut.p)
mean.nsT.cT.theo.MSD.group <- nsT.cT.theo.MSD.group$mean.group[,1]

m.nsT.cT.theo.Qn = t(apply(m.nsT.cT.theo.Pn, 1, cumsum))

```

## Conjuntos de proteinas

### Conjunto teorico
`r n.mut` mutantes de `r p.ref` (`r n.sites.p.1` sitios) simuladas con el modelo mutacional `r mut.model` con ANM *R0* = `r R0` y *Fmax* = 2 (solo para LFENM).

Con seleccion natural (ns = T): para determinar que sitios mutar, se alineo `r p.ref` con cada una de las proteinas del conjunto, se obtuvieron los indices de los sitios alineados pero mutados y de los sitios con gaps y se simularon `r n.mut.p` mutantes por cada par de proteinas, obteniendose un total de `r n.mut.p * n.exp` mutantes. Luego, para el analisis, se tomaron como alineados los sitios alineados de `r p.ref` para cada par de proteinas.

Sin seleccion natural (ns = F): se mutaron al azar la cantidad de sitios correspondientes al % id del conjunto experimental y luego, para el analisis, se tomaron como alineados todos los sitios.

### Conjunto experimental 
`r n.exp` proteinas de la familia de `r family`. Las proteinas tienen un promedio de identidad secuencial de `r round(mean(identity))`%. El core del alineamiento de la familia es de `r n.core` sitios.

### Analisis

Se realizaron 2 tipos de analisis:

*Core (C = T)*: se analizo solo el core conservado del alinemiento (sitios sin gaps en el alineamiento multiple).

*No Core (C = F)*: no se utilizo el core para el analisis.

La caracterizacion del conjunto experimental se muestra a continuacion:
```{r}

family.data
```
## Comparaciones

### MSD
```{r}

layout(matrix(1:6, 3, 2, byrow = T))

hist(cF.exp.MSD, main = "Experimental MSD C = F", xlab = "MSD")
hist(cT.exp.MSD, main = "Experimental MSD C = T", xlab = "MSD")

hist(nsF.cF.theo.MSD, main = "Theoretical MSD ns = F, C = F", xlab = "MSD")
hist(nsT.cF.theo.MSD, main = "Theoretical MSD ns = T, C = F", xlab = "MSD")
hist(nsF.cT.theo.MSD, main = "Theoretical MSD ns = F, C = T", xlab = "MSD")
hist(nsT.cT.theo.MSD, main = "Theoretical MSD ns = T, C = T", xlab = "MSD")

```

### MSDi
```{r}

layout(matrix(1:4, 2, 2, byrow = T)) 
plot(rank(nsF.cF.theo.MSDi), main = "MSDi ns = F, c = F", xlab = "site", ylab = "rank MSDi")
points(rank(cF.exp.MSDi), col = "red")
plot(rank(nsT.cF.theo.MSDi), main = "MSDi ns = T, c = F", xlab = "site", ylab = "rank MSDi")
points(rank(cF.exp.MSDi), col = "red")
plot(rank(nsF.cT.theo.MSDi), main = "MSDi ns = F, c = T", xlab = "site", ylab = "rank MSDi")
points(rank(cT.exp.MSDi), col = "red")
plot(rank(nsT.cT.theo.MSDi), main = "MSDi ns = T, c = T", xlab = "site", ylab = "rank MSDi")
points(rank(cT.exp.MSDi), col = "red")
```
rojo: experimental
negro: teorico

Los perfiles de MSDi fueron normalizados con la funcion rank().

```{r}
# Calculate rho.
nsF.cF.rho.t.1 <- matrix(0, nrow = n.mut, ncol = 1)
nsF.cF.rho.t.3 <- matrix(0, nrow = n.mut, ncol = 1)
for (i in (1:n.mut)) {
  nsF.cF.rho.t.1[i, ] <- cor(as.numeric(m.nsF.cF.theo.Pn[i, 1:nmodes1] * m.nsF.cF.theo.va[i, 1:nmodes1]), as.numeric(i.m.nsF.cF.theo.va[i, 1:nmodes1]), method = "pearson")

  nsF.cF.rho.t.3[i, ] <- cor(as.numeric(m.nsF.cF.theo.Pn[i, 1:nmodes3] * m.nsF.cF.theo.va[i, 1:nmodes3]), as.numeric(i.m.nsF.cF.theo.va[i, 1:nmodes3]), method = "pearson")	
}

nsT.cF.rho.t.1 <- matrix(0, nrow = n.mut, ncol = 1)
nsT.cF.rho.t.3 <- matrix(0, nrow = n.mut, ncol = 1)
for (i in (1:n.mut)) {
  nsT.cF.rho.t.1[i, ] <- cor(as.numeric(m.nsT.cF.theo.Pn[i, 1:nmodes1] * m.nsT.cF.theo.va[i, 1:nmodes1]), as.numeric(i.m.nsT.cF.theo.va[i, 1:nmodes1]), method = "pearson")	
  nsT.cF.rho.t.3[i, ] <- cor(as.numeric(m.nsT.cF.theo.Pn[i, 1:nmodes3] * m.nsT.cF.theo.va[i, 1:nmodes3]), as.numeric(i.m.nsT.cF.theo.va[i, 1:nmodes3]), method = "pearson")	
}

nsF.cT.rho.t.1 <- matrix(0, nrow = n.mut, ncol = 1)
nsF.cT.rho.t.3 <- matrix(0, nrow = n.mut, ncol = 1)
for (i in (1:n.mut)) {
  nsF.cT.rho.t.1[i, ] <- cor(as.numeric(m.nsF.cT.theo.Pn[i, 1:nmodes1] * m.nsF.cT.theo.va[i, 1:nmodes1]), as.numeric(i.m.nsF.cT.theo.va[i, 1:nmodes1]), method = "pearson")	
  nsF.cT.rho.t.3[i, ] <- cor(as.numeric(m.nsF.cT.theo.Pn[i, 1:nmodes3] * m.nsF.cT.theo.va[i, 1:nmodes3]), as.numeric(i.m.nsF.cT.theo.va[i, 1:nmodes3]), method = "pearson")	
}

nsT.cT.rho.t.1 <- matrix(0, nrow = n.mut, ncol = 1)
nsT.cT.rho.t.3 <- matrix(0, nrow = n.mut, ncol = 1)
for (i in (1:n.mut)) {
  nsT.cT.rho.t.1[i, ] <- cor(as.numeric(m.nsT.cT.theo.Pn[i, 1:nmodes1] * m.nsT.cT.theo.va[i, 1:nmodes1]), as.numeric(i.m.nsT.cT.theo.va[i, 1:nmodes1]), method = "pearson")	
  nsT.cT.rho.t.3[i, ] <- cor(as.numeric(m.nsT.cT.theo.Pn[i, 1:nmodes3] * m.nsT.cT.theo.va[i, 1:nmodes3]), as.numeric(i.m.nsT.cT.theo.va[i, 1:nmodes3]), method = "pearson")	
}

cF.rho.e.1 <- matrix(0, nrow = n.exp, ncol = 1)
cF.rho.e.3 <- matrix(0, nrow = n.exp, ncol = 1) 
for (i in (1:n.exp)) {
  cF.rho.e.1[i, ] <- cor(as.numeric(m.cF.exp.Pn[i, 1:nmodes1] * m.cF.exp.va[i, 1:nmodes1]), as.numeric(i.m.cF.exp.va[i, 1:nmodes1]), method = "pearson")
  cF.rho.e.3[i, ] <- cor(as.numeric(m.cF.exp.Pn[i, 1:nmodes3] * m.cF.exp.va[i, 1:nmodes3]), as.numeric(i.m.cF.exp.va[i, 1:nmodes3]), method = "pearson")
}

cT.rho.e.1 <- matrix(0, nrow = n.exp, ncol = 1)
cT.rho.e.3 <- matrix(0, nrow = n.exp, ncol = 1) 
for (i in (1:n.exp)) {
  cT.rho.e.1[i, ] <- cor(as.numeric(m.cT.exp.Pn[i, 1:nmodes1] * m.cT.exp.va[i, 1:nmodes1]), as.numeric(i.m.cT.exp.va[i, 1:nmodes1]), method = "pearson")
  cT.rho.e.3[i, ] <- cor(as.numeric(m.cT.exp.Pn[i, 1:nmodes3] * m.cT.exp.va[i, 1:nmodes3]), as.numeric(i.m.cT.exp.va[i, 1:nmodes3]), method = "pearson")
}

# Calculate auc.
nsF.cF.auc.t.1 <- matrix(0, nrow = n.mut, ncol = 1)
nsF.cF.auc.t.3 <- matrix(0, nrow = n.mut, ncol = 1)
for (i in (1:n.mut)) {
  nsF.cF.auc.t.1[i, ] <- auc(seq(1:nmodes1), m.nsF.cF.theo.Qn[i,1:nmodes1])
  nsF.cF.auc.t.3[i, ] <- auc(seq(1:nmodes3), m.nsF.cF.theo.Qn[i,1:nmodes3])
}
nsT.cF.auc.t.1 <- matrix(0, nrow = n.mut, ncol = 1)
nsT.cF.auc.t.3 <- matrix(0, nrow = n.mut, ncol = 1)
for (i in (1:n.mut)) {
  nsT.cF.auc.t.1[i, ] <- auc(seq(1:nmodes1), m.nsT.cF.theo.Qn[i,1:nmodes1])
  nsT.cF.auc.t.3[i, ] <- auc(seq(1:nmodes3), m.nsT.cF.theo.Qn[i,1:nmodes3])
}

cF.auc.e.1 <- matrix(0, nrow = n.exp, ncol = 1)
cF.auc.e.3 <- matrix(0, nrow = n.exp, ncol = 1)
for (i in (1:n.exp)) {
  cF.auc.e.1[i, ] <- auc(seq(1:nmodes1), m.cF.exp.Qn[i, 1:nmodes1])
  cF.auc.e.3[i, ] <- auc(seq(1:nmodes3), m.cF.exp.Qn[i, 1:nmodes3])
}

nsF.cT.auc.t.1 <- matrix(0, nrow = n.mut, ncol = 1)
nsF.cT.auc.t.3 <- matrix(0, nrow = n.mut, ncol = 1)
for (i in (1:n.mut)) {
  nsF.cT.auc.t.1[i, ] <- auc(seq(1:nmodes1), m.nsF.cT.theo.Qn[i,1:nmodes1])
  nsF.cT.auc.t.3[i, ] <- auc(seq(1:nmodes3), m.nsF.cT.theo.Qn[i,1:nmodes3])
}
nsT.cT.auc.t.1 <- matrix(0, nrow = n.mut, ncol = 1)
nsT.cT.auc.t.3 <- matrix(0, nrow = n.mut, ncol = 1)
for (i in (1:n.mut)) {
  nsT.cT.auc.t.1[i, ] <- auc(seq(1:nmodes1), m.nsT.cT.theo.Qn[i,1:nmodes1])
  nsT.cT.auc.t.3[i, ] <- auc(seq(1:nmodes3), m.nsT.cT.theo.Qn[i,1:nmodes3])
}

cT.auc.e.1 <- matrix(0, nrow = n.exp, ncol = 1)
cT.auc.e.3 <- matrix(0, nrow = n.exp, ncol = 1)
for (i in (1:n.exp)) {
  cT.auc.e.1[i, ] <- auc(seq(1:nmodes1), m.cT.exp.Qn[i, 1:nmodes1])
  cT.auc.e.3[i, ] <- auc(seq(1:nmodes3), m.cT.exp.Qn[i, 1:nmodes3])
}
```

### RHO y AUC
Las distribuciones de *auc* y *rho* para cada conjunto se muestran a continuacion (negro = teorico, rojo = experimental)

```{r}
layout(matrix(1:4, 2, 2, byrow = T))
plot(density(nsF.cF.rho.t.1), ylab = "Frecuencia", xlab = "rho", main = "Histograma rho 10 modos ns = F, c = F")
points(x = c(cF.rho.e.1), y = rep(0, n.exp), col = "red")
plot(density(nsT.cF.rho.t.1), ylab = "Frecuencia", xlab = "rho", main = "Histograma rho 10 modos ns = T, c = F")
points(x = c(cF.rho.e.1), y = rep(0, n.exp), col = "red")
plot(density(nsF.cT.rho.t.1), ylab = "Frecuencia", xlab = "rho", main = "Histograma rho 10 modos ns = F, c = T")
points(x = c(cT.rho.e.1), y = rep(0, n.exp), col = "red")
plot(density(nsT.cT.rho.t.1), ylab = "Frecuencia", xlab = "rho", main = "Histograma rho 10 modos ns = T, c = T")
points(x = c(cT.rho.e.1), y = rep(0, n.exp), col = "red")

```
```{r}
layout(matrix(1:4, 2, 2, byrow = T))
plot(density(nsF.cF.rho.t.3), ylab = "Frecuencia", xlab = "rho", main = "Histograma rho 50 modos ns = F, c = F")
points(x = c(cF.rho.e.3), y = rep(0, n.exp), col = "red")
plot(density(nsT.cF.rho.t.3), ylab = "Frecuencia", xlab = "rho", main = "Histograma rho 50 modos ns = T, c = F")
points(x = c(cF.rho.e.3), y = rep(0, n.exp), col = "red")
plot(density(nsF.cT.rho.t.3), ylab = "Frecuencia", xlab = "rho", main = "Histograma rho 50 modos ns = F, c = T")
points(x = c(cT.rho.e.3), y = rep(0, n.exp), col = "red")
plot(density(nsT.cT.rho.t.3), ylab = "Frecuencia", xlab = "rho", main = "Histograma rho 50 modos ns = T, c = T")
points(x = c(cT.rho.e.3), y = rep(0, n.exp), col = "red")

```
```{r}
layout(matrix(1:4, 2, 2, byrow = T))
plot(density(nsF.cF.auc.t.1), ylab = "Frecuencia", xlab = "auc", main = "Histograma auc 10 modos ns = F, c = F")
points(x = c(cF.auc.e.1), y = rep(0, n.exp), col = "red")
plot(density(nsT.cF.auc.t.1), ylab = "Frecuencia", xlab = "auc", main = "Histograma auc 10 modos ns = T, c = F")
points(x = c(cF.auc.e.1), y = rep(0, n.exp), col = "red")
plot(density(nsF.cT.auc.t.1), ylab = "Frecuencia", xlab = "auc", main = "Histograma auc 10 modos ns = F, c = T")
points(x = c(cT.auc.e.1), y = rep(0, n.exp), col = "red")
plot(density(nsT.cT.auc.t.1), ylab = "Frecuencia", xlab = "auc", main = "Histograma auc 10 modos ns = T, c = T")
points(x = c(cT.auc.e.1), y = rep(0, n.exp), col = "red")

```
```{r}
layout(matrix(1:4, 2, 2, byrow = T))
plot(density(nsF.cF.auc.t.3), ylab = "Frecuencia", xlab = "auc", main = "Histograma auc 50 modos ns = F, c = F")
points(x = c(cF.auc.e.3), y = rep(0, n.exp), col = "red")
plot(density(nsT.cF.auc.t.3), ylab = "Frecuencia", xlab = "auc", main = "Histograma auc 50 modos ns = T, c = F")
points(x = c(cF.auc.e.3), y = rep(0, n.exp), col = "red")
plot(density(nsF.cT.auc.t.3), ylab = "Frecuencia", xlab = "auc", main = "Histograma auc 50 modos ns = F, c = T")
points(x = c(cT.auc.e.3), y = rep(0, n.exp), col = "red")
plot(density(nsT.cT.auc.t.3), ylab = "Frecuencia", xlab = "auc", main = "Histograma auc 50 modos ns = T, c = T")
points(x = c(cT.auc.e.3), y = rep(0, n.exp), col = "red")

```

## Pn y Qn
Las distribuciones de *Pn* y *Qn* de los conjuntos son las siguientes:

```{r}
# Re-ordenate Pn and Qn.
m.theo.index = matrix(ncol = 1, nrow = n.mut)
for (P in (1:n.exp)) {
  for (mut in (1:n.mut.p)) {
    m.theo.index[(P - 1) * n.mut.p + mut, ] = ((mut - 1) * 10 + P)
  }
}
m.nsF.cF.theo.Pn = m.nsF.cF.theo.Pn[as.vector(m.theo.index), ]
m.nsF.cF.theo.Qn = m.nsF.cF.theo.Qn[as.vector(m.theo.index), ]

m.nsT.cF.theo.Pn = m.nsT.cF.theo.Pn[as.vector(m.theo.index), ]
m.nsT.cF.theo.Qn = m.nsT.cF.theo.Qn[as.vector(m.theo.index), ]

m.nsF.cT.theo.Pn = m.nsF.cT.theo.Pn[as.vector(m.theo.index), ]
m.nsF.cT.theo.Qn = m.nsF.cT.theo.Qn[as.vector(m.theo.index), ]

m.nsT.cT.theo.Pn = m.nsT.cT.theo.Pn[as.vector(m.theo.index), ]
m.nsT.cT.theo.Qn = m.nsT.cT.theo.Qn[as.vector(m.theo.index), ]

# Calculate groups, means and quantiles.
nsF.cF.theo.Pn.group = CalculateGroupsMeansQuantiles(m.nsF.cF.theo.Pn, n.mut.p, n.exp)
mean.nsF.cF.theo.Pn.group = nsF.cF.theo.Pn.group$mean.mean.group
nsF.cF.theo.Pn.group.quantile1 = nsF.cF.theo.Pn.group$mean.quantile1.group
nsF.cF.theo.Pn.group.quantile2 = nsF.cF.theo.Pn.group$mean.quantile2.group

nsT.cF.theo.Pn.group = CalculateGroupsMeansQuantiles(m.nsT.cF.theo.Pn, n.mut.p, n.exp)
mean.nsT.cF.theo.Pn.group = nsT.cF.theo.Pn.group$mean.mean.group
nsT.cF.theo.Pn.group.quantile1 = nsT.cF.theo.Pn.group$mean.quantile1.group
nsT.cF.theo.Pn.group.quantile2 = nsT.cF.theo.Pn.group$mean.quantile2.group

nsF.cT.theo.Pn.group = CalculateGroupsMeansQuantiles(m.nsF.cT.theo.Pn, n.mut.p, n.exp)
mean.nsF.cT.theo.Pn.group = nsF.cT.theo.Pn.group$mean.mean.group
nsF.cT.theo.Pn.group.quantile1 = nsF.cT.theo.Pn.group$mean.quantile1.group
nsF.cT.theo.Pn.group.quantile2 = nsF.cT.theo.Pn.group$mean.quantile2.group

nsT.cT.theo.Pn.group = CalculateGroupsMeansQuantiles(m.nsT.cT.theo.Pn, n.mut.p, n.exp)
mean.nsT.cT.theo.Pn.group = nsT.cT.theo.Pn.group$mean.mean.group
nsT.cT.theo.Pn.group.quantile1 = nsT.cT.theo.Pn.group$mean.quantile1.group
nsT.cT.theo.Pn.group.quantile2 = nsT.cT.theo.Pn.group$mean.quantile2.group

nsF.cF.theo.Qn.group = CalculateGroupsMeansQuantiles(m.nsF.cF.theo.Qn, n.mut.p, n.exp)
mean.nsF.cF.theo.Qn.group = nsF.cF.theo.Qn.group$mean.mean.group
nsF.cF.theo.Qn.group.quantile1 = nsF.cF.theo.Qn.group$mean.quantile1.group
nsF.cF.theo.Qn.group.quantile2 = nsF.cF.theo.Qn.group$mean.quantile2.group

nsT.cF.theo.Qn.group = CalculateGroupsMeansQuantiles(m.nsT.cF.theo.Qn, n.mut.p, n.exp)
mean.nsT.cF.theo.Qn.group = nsT.cF.theo.Qn.group$mean.mean.group
nsT.cF.theo.Qn.group.quantile1 = nsT.cF.theo.Qn.group$mean.quantile1.group
nsT.cF.theo.Qn.group.quantile2 = nsT.cF.theo.Qn.group$mean.quantile2.group

nsF.cT.theo.Qn.group = CalculateGroupsMeansQuantiles(m.nsF.cT.theo.Qn, n.mut.p, n.exp)
mean.nsF.cT.theo.Qn.group = nsF.cT.theo.Qn.group$mean.mean.group
nsF.cT.theo.Qn.group.quantile1 = nsF.cT.theo.Qn.group$mean.quantile1.group
nsF.cT.theo.Qn.group.quantile2 = nsF.cT.theo.Qn.group$mean.quantile2.group

nsT.cT.theo.Qn.group = CalculateGroupsMeansQuantiles(m.nsT.cT.theo.Qn, n.mut.p, n.exp)
mean.nsT.cT.theo.Qn.group = nsT.cT.theo.Qn.group$mean.mean.group
nsT.cT.theo.Qn.group.quantile1 = nsT.cT.theo.Qn.group$mean.quantile1.group
nsT.cT.theo.Qn.group.quantile2 = nsT.cT.theo.Qn.group$mean.quantile2.group

# Graphics.

layout(matrix(1:4, 2, 2, byrow = T))

plot(mean.nsF.cF.theo.Pn.group, 
     main = "Pn promedio ns = F, C = F", 
     xlab = "nmodo",
     ylab = "Pn",
     ylim = c(0, max(c(nsF.cF.theo.Pn.group.quantile2, mean.cF.exp.Pn))))
lines(nsF.cF.theo.Pn.group.quantile1)
lines(nsF.cF.theo.Pn.group.quantile2)
points(mean.cF.exp.Pn, col = "red")
lines(as.vector(cF.exp.Pn.quantile1), col = "red")
lines(as.vector(cF.exp.Pn.quantile2), col = "red")

plot(mean.nsT.cF.theo.Pn.group, 
     main = "Pn promedio ns = T, C = F", 
     xlab = "nmodo",
     ylab = "Pn",
     ylim = c(0, max(c(nsT.cF.theo.Pn.group.quantile2, mean.cF.exp.Pn))))
lines(nsT.cF.theo.Pn.group.quantile1)
lines(nsT.cF.theo.Pn.group.quantile2)
points(mean.cF.exp.Pn, col = "red")
lines(as.vector(cF.exp.Pn.quantile1), col = "red")
lines(as.vector(cF.exp.Pn.quantile2), col = "red")

plot(mean.nsF.cT.theo.Pn.group, 
     main = "Pn promedio ns = F, C = T", 
     xlab = "nmodo",
     ylab = "Pn",
     ylim = c(0, max(c(nsF.cT.theo.Pn.group.quantile2, mean.cT.exp.Pn))))
lines(nsF.cT.theo.Pn.group.quantile1)
lines(nsF.cT.theo.Pn.group.quantile2)
points(mean.cT.exp.Pn, col = "red")
lines(as.vector(cT.exp.Pn.quantile1), col = "red")
lines(as.vector(cT.exp.Pn.quantile2), col = "red")

plot(mean.nsT.cT.theo.Pn.group, 
     main = "Pn promedio ns = T, C = T", 
     xlab = "nmodo",
     ylab = "Pn",
     ylim = c(0, max(c(nsT.cT.theo.Pn.group.quantile2, mean.cT.exp.Pn))))
lines(nsT.cT.theo.Pn.group.quantile1)
lines(nsT.cT.theo.Pn.group.quantile2)
points(mean.cT.exp.Pn, col = "red")
lines(as.vector(cT.exp.Pn.quantile1), col = "red")
lines(as.vector(cT.exp.Pn.quantile2), col = "red")
```

```{r}

layout(matrix(1:4, 2, 2, byrow = T))

plot(mean.nsF.cF.theo.Qn.group, 
     main = "Qn promedio ns = F, C = F", 
     xlab = "nmodo", 
     ylab = "Qn",
     ylim = c(0, max(c(nsF.cF.theo.Qn.group.quantile2, mean.cF.exp.Qn))))
lines(nsF.cF.theo.Qn.group.quantile1)
lines(nsF.cF.theo.Qn.group.quantile2)
points(mean.cF.exp.Qn, col = "red")
lines(as.vector(cF.exp.Qn.quantile1), col = "red")
lines(as.vector(cF.exp.Qn.quantile2), col = "red")

plot(mean.nsT.cF.theo.Qn.group, 
     main = "Qn promedio ns = T, C = F", 
     xlab = "nmodo",     
     ylab = "Qn",
     ylim = c(0, max(c(nsT.cF.theo.Qn.group.quantile2, mean.cF.exp.Qn))))
lines(nsT.cF.theo.Qn.group.quantile1)
lines(nsT.cF.theo.Qn.group.quantile2)
points(mean.cF.exp.Qn, col = "red")
lines(as.vector(cF.exp.Qn.quantile1), col = "red")
lines(as.vector(cF.exp.Qn.quantile2), col = "red")

plot(mean.nsF.cT.theo.Qn.group, 
     main = "Qn promedio ns = F, C = T", 
     xlab = "nmodo",      
     ylab = "Qn",
     ylim = c(0, max(c(nsF.cT.theo.Qn.group.quantile2, mean.cT.exp.Qn))))
lines(nsF.cT.theo.Qn.group.quantile1)
lines(nsF.cT.theo.Qn.group.quantile2)
points(mean.cT.exp.Qn, col = "red")
lines(as.vector(cT.exp.Qn.quantile1), col = "red")
lines(as.vector(cT.exp.Qn.quantile2), col = "red")

plot(mean.nsT.cT.theo.Qn.group, 
     main = "Qn promedio ns = T, C = T", 
     xlab = "nmodo",     
     ylab = "Qn",
     ylim = c(0, max(c(nsT.cT.theo.Qn.group.quantile2, mean.cT.exp.Qn))))
lines(nsT.cT.theo.Qn.group.quantile1)
lines(nsT.cT.theo.Qn.group.quantile2)
points(mean.cT.exp.Qn, col = "red")
lines(as.vector(cT.exp.Qn.quantile1), col = "red")
lines(as.vector(cT.exp.Qn.quantile2), col = "red")
```

*Negro*: Puntos: promedio de promedios teorico. Lineas: promedio de cuartiles 0.05 y 0.95 de `r n.mut.p` grupos de `r n.exp` mutantes teoricas.
*Rojo*: Experimental. Puntos: promedio. Lineas: cuartiles 0.05 y 0.95.

### 2016-03-06 Report.Rmd
cambios 6/3/16

@@
 
-m.exp.va = read.csv(file.path(out.dir, paste(family.heme.model.core, "_out_m.exp.va.csv", sep = "")))[, 1:nmodes4]
+####
+
+m.exp.va = read.csv(file.path(out.dir, paste(family.model.naturalSelection.core, "_out_m.exp.va.csv", sep = "")))[, 1:nmodes4]
 mean.exp.va = colMeans(m.exp.va)
@@
 
-m.exp.Pn = read.csv(file.path(out.dir, paste(family.heme.model.core, "_out_m.exp.Pn.csv", sep = "")))[, 1:nmodes4]
+m.exp.Pn = read.csv(file.path(out.dir, paste(family.model.naturalSelection.core, "_out_m.exp.Pn.csv", sep = "")))[, 1:nmodes4]
 mean.exp.Pn = colMeans(m.exp.Pn)
 
-m.exp.dr.squarei = read.csv(file.path(out.dir, paste(family.heme.model.core, "_out_m.exp.dr.squarei.csv", sep = "")))
+exp.Pn.quantile1 = matrix(0, ncol = ncol(m.exp.Pn), nrow = 1)
+exp.Pn.quantile2 = matrix(0, ncol = ncol(m.exp.Pn), nrow = 1)
+
+for (i in (1:ncol(m.exp.Pn))){
+    exp.Pn.quantiles <- as.vector(quantile((m.exp.Pn[, i]), probs = c(0.05, 0.95)))
+    exp.Pn.quantile1[1, i] = exp.Pn.quantiles[1]
+    exp.Pn.quantile2[1, i] = exp.Pn.quantiles[2]
+}
+
+m.exp.dr.squarei = read.csv(file.path(out.dir, paste(family.model.naturalSelection.core, "_out_m.exp.dr.squarei.csv", sep = "")))
 exp.MSDi = colMeans(m.exp.dr.squarei, na.rm = T )
@@
 ### Theoretical ###
-m.theo.va = read.csv(file.path(out.dir, paste(family.heme.model.core, "_out_m.theo.va.csv", sep = "")))[, 1:nmodes4]
+m.theo.va = read.csv(file.path(out.dir, paste(family.model.naturalSelection.core, "_out_m.theo.va.csv", sep = "")))[, 1:nmodes4]
 mean.theo.va = colMeans(m.theo.va)
@@
 
-m.theo.Pn = read.csv(file.path(out.dir, paste(family.heme.model.core, "_out_m.theo.Pn.csv", sep = "")))[, 1:nmodes4]
+m.theo.Pn = read.csv(file.path(out.dir, paste(family.model.naturalSelection.core, "_out_m.theo.Pn.csv", sep = "")))[, 1:nmodes4]
 n.mut = nrow(m.theo.Pn)
 
-m.theo.dr.squarei = read.csv(file.path(out.dir, paste(family.heme.model.core, "_out_m.theo.dr.squarei.csv", sep = "")))
+m.theo.dr.squarei = read.csv(file.path(out.dir, paste(family.model.naturalSelection.core, "_out_m.theo.dr.squarei.csv", sep = "")))
 theo.MSDi = colMeans(m.theo.dr.squarei, na.rm = T)
@@
 ### Conjunto teorico
-`r n.mut` mutantes de `r p.ref` (`r n.sites.p.1` sitios) simuladas con el modelo mutacional `r mut.model` con ANM *R0* = 12 y *Fmax* = 2 (solo para LFENM).
+`r n.mut` mutantes de `r p.ref` (`r n.sites.p.1` sitios) simuladas con el modelo mutacional `r mut.model` con ANM *R0* = `r R0` y *Fmax* = 2 (solo para LFENM).
 Para determinar que sitios mutar, se alineo `r p.ref` con cada una de las proteinas del conjunto, se obtuvieron los indices de los sitios alineados pero mutados y se simularon `r n.mut.p` mutantes por cada par de proteinas, obteniendose un total de `r n.mut.p * n.exp` mutantes.
@@
 # Calculate groups, means and quantiles.
-theo.Pn.group <- CalculateGroupsMeansQuantiles(m.theo.Pn, n.mut.p, n.exp)
-mean.theo.Pn.group <- theo.Pn.group$mean.total
-theo.Pn.group.quantile5 <- theo.Pn.group$quantile[1, ]
-theo.Pn.group.quantile95 <- theo.Pn.group$quantile[2, ] 
-theo.Qn.group <- CalculateGroupsMeansQuantiles(m.theo.Qn, n.mut.p, n.exp)
-mean.theo.Qn.group <- theo.Qn.group$mean.total
-theo.Qn.group.quantile5 <- theo.Qn.group$quantile[1, ]
-theo.Qn.group.quantile95 <- theo.Qn.group$quantile[2, ]
+theo.Pn.group = CalculateGroupsMeansQuantiles(m.theo.Pn, n.mut.p, n.exp)
+mean.theo.Pn.group = theo.Pn.group$mean.mean.group
+theo.Pn.group.quantile1 = theo.Pn.group$mean.quantile1.group
+theo.Pn.group.quantile2 = theo.Pn.group$mean.quantile2.group
 
 # Graphics.
-layout(matrix(1:4, 2, 2, byrow = T))
+layout(matrix(1:2, 1, 2, byrow = T))
 
@@
 plot(y = mean.exp.Pn, x = i.mean.exp.va, ylab = "Pn promedio experimental", xlab = "1/evalue")
+
+layout(matrix(1:1, 1, 1, byrow = T))
 
@@
      type = "l", 
-     ylim = c(0, max(c(theo.Pn.group.quantile95, mean.exp.Pn))))
-lines(theo.Pn.group.quantile5, col = "green")
-lines(theo.Pn.group.quantile95, col = "green")
+     ylim = c(0, max(c(theo.Pn.group.quantile2, mean.exp.Pn))))
+lines(theo.Pn.group.quantile1, col = "green")
+lines(theo.Pn.group.quantile2, col = "green")
 points(mean.exp.Pn, col = "red")
-
-plot(mean.theo.Qn.group, 
-     ylab = "Qn promedio", 
-     xlab = "nmodo", 
-     type = "l", 
-     ylim = c(0, max(c(theo.Qn.group.quantile95, mean.exp.Qn))))
-lines(theo.Qn.group.quantile5, col = "green")
-lines(theo.Qn.group.quantile95, col = "green")
-points(mean.exp.Qn, col = "red")
+lines(as.vector(exp.Pn.quantile1), col = "red")
+lines(as.vector(exp.Pn.quantile2), col = "red")
 
@@
 Rojo: Experimental
-Verdes: Cuartiles 0.05 y 0.95 de `r n.mut.p` grupos de `r n.exp` mutantes teoricas.
+Verdes: Cuartiles 0.01 y 0.99 de `r n.mut.p` grupos de `r n.exp` mutantes teoricas.

### 2016-03-06 FUNCTIONS/GenerateMutants.R

@@ -4,17 +4,17 @@
 #
 #  Args:
 #    family: the family of the protein to mutate.
-#    p.ref: the pdb code (pdbid) of the protein to mutate.
-#    chain: the chain of p.ref to mutate.
+#    exp.chain.p.ref: the chain of p.ref in the pdb file obtained from Homstrad.
 #    mut.model: mutational model. It can be "LFENM" or "MND".
 #    n.mut.p: the number of mutants to generate for each protein of the family.
 #    fmax: argument for "LFENM". It is the maximun value for the forces that model the mutations.
 #    R0: the cut-off for the ANM ("Anisotropic Network Model").
 #    heme: argument for "globins". It can be "TRUE" or "FALSE". If it is "TRUE" the program considers the heme group.
-#    data.dir: directory of the data. It must contain the file "_out_m.aligned.mut.p.ref.index.csv" with indexes to mutate.
-#    This file is generated using AnalyzeFamily().
+#    natural.selection: It can be "TRUE" or "FALSE". If it is "TRUE", the mutants are calculated considering natural 
+#    selection. If it is "FALSE", the mutants are calculated in a random manner.
+#    data.dir: directory of the data.It must contain the output of the function AnalyzeFamily().
 #    out.dir: output directory.
-#    out.name: ID for output filenames.
+#    mut.fname.id: ID for output filenames.
 #    TOLERANCE: 0 tolerance.
 #
 #  Requires:
@@ -28,32 +28,32 @@
 #    File with a matrix of coordinates of the mutants in each column in out.dir.
 
 GenerateMutants <- function(family,
-                            p.ref, 
-                            chain,
+                            exp.chain.p.ref,
                             mut.model,
                             n.mut.p,
                             fmax, 
                             R0,
-                            heme, 
+                            heme,
+                            natural.selection,
                             data.dir,
                             out.dir,
-                            out.name,
+                            mut.fname.id,
[…]

### 2016-03-06 MainMultipleReport.R

@@ -1,0 +1,21 @@
+# Load packages.
+library(knitr)
+library(markdown)
+
+# Read input.
+input.fname <- file.path("input_MainMultipleReport.csv")
+input <- read.csv(input.fname)
+
+for (a in (1:nrow(input))) { 
+  print(a)
+  family <- as.character(input$family)[a]
+  p.ref <- as.character(input$p.ref)[a]
+  mut.model = input$mut.model[a]
+  n.mut.p = input$n.mut.p[a]
+  R0 = input$R0[a]
+  K.analysis = input$K.analysis[a]
+
+  # Generate a report.
+  rmarkdown::render('MultipleReport.Rmd', 
+                    output_file =  paste("report_", family, "_R0_", R0, "_K.analysis_", K.analysis, ".html", sep = ''))
+}

### 2016-03-09 MultipleReport.Rmd
cambios 9/3/16

@@
 layout(matrix(1:4, 2, 2, byrow = T)) 
-plot(rank(nsF.cF.theo.MSDi), main = "MSDi ns = F, c = F", xlab = "site", ylab = "rank MSDi")
-points(rank(cF.exp.MSDi), col = "red")
-plot(rank(nsT.cF.theo.MSDi), main = "MSDi ns = T, c = F", xlab = "site", ylab = "rank MSDi")
-points(rank(cF.exp.MSDi), col = "red")
-plot(rank(nsF.cT.theo.MSDi), main = "MSDi ns = F, c = T", xlab = "site", ylab = "rank MSDi")
-points(rank(cT.exp.MSDi), col = "red")
-plot(rank(nsT.cT.theo.MSDi), main = "MSDi ns = T, c = T", xlab = "site", ylab = "rank MSDi")
-points(rank(cT.exp.MSDi), col = "red")
+plot(rank(nsF.cF.theo.MSDi, na.last = "keep"), main = "MSDi ns = F, c = F", xlab = "site", ylab = "rank MSDi")
+points(rank(cF.exp.MSDi, na.last = "keep"), col = "red")
+plot(rank(nsT.cF.theo.MSDi, na.last = "keep"), main = "MSDi ns = T, c = F", xlab = "site", ylab = "rank MSDi")
+points(rank(cF.exp.MSDi, na.last = "keep"), col = "red")
+plot(rank(nsF.cT.theo.MSDi, na.last = "keep"), main = "MSDi ns = F, c = T", xlab = "site", ylab = "rank MSDi")
+points(rank(cT.exp.MSDi, na.last = "keep"), col = "red")
+plot(rank(nsT.cT.theo.MSDi, na.last = "keep"), main = "MSDi ns = T, c = T", xlab = "site", ylab = "rank MSDi")
+points(rank(cT.exp.MSDi, na.last = "keep"), col = "red")
 ```
@@
 
-*Negro*: Puntos: promedio de promedios teorico. Lineas: promedio de cuartiles 0.05 y 0.95 de `r n.mut.p` grupos de `r n.exp` mutantes teoricas.
-*Rojo*: Experimental. Puntos: promedio. Lineas: cuartiles 0.05 y 0.95.
+*Negro*: Puntos: promedio de promedios teorico. Lineas: promedio de cuantiles 0.05 y 0.95 de `r n.mut.p` grupos de `r n.exp` mutantes teoricas.
+*Rojo*: Experimental. Puntos: promedio. Lineas: cuantiles 0.05 y 0.95.
+
+## R^2 y MSE
+Las comparaciones entre perfines promedio Pn y MSDi teoricos fiteados y experimentales se muestran a continuacion. En cada grafico se muestra la correlacion (R^2) y el error (MSE).
+```{r}
+layout(matrix(1:4, 2, 2, byrow = T))
+
+fit.nsF.cF = lm(mean.cF.exp.Pn ~ mean.nsF.cF.theo.Pn.group)
+Pn.fit.nsF.cF = fitted.values(fit.nsF.cF)
+R2.nsF.cF = cor(mean.cF.exp.Pn, Pn.fit.nsF.cF) ^ 2 
+MSE.nsF.cF = mean((Pn.fit.nsF.cF - mean.cF.exp.Pn) ^ 2)
+plot(Pn.fit.nsF.cF, mean.cF.exp.Pn, xlab = "Pn teorico", ylab = "Pn experimental", main = "ns = F c = F")
+abline(0, 1)
+legend("topleft", paste("R^2", round(R2.nsF.cF, digits = 2)), bty = "n", text.col = "red")
+legend("bottomright", paste("MSE", signif(MSE.nsF.cF, digits = 2)), bty = "n", text.col = "red")
+
+fit.nsT.cF = lm(mean.cF.exp.Pn ~ mean.nsT.cF.theo.Pn.group)
+Pn.fit.nsT.cF = fitted.values(fit.nsT.cF)
+R2.nsT.cF = cor(mean.cF.exp.Pn, Pn.fit.nsT.cF) ^ 2 
+MSE.nsT.cF = mean((Pn.fit.nsT.cF - mean.cF.exp.Pn) ^ 2)
+plot(Pn.fit.nsT.cF, mean.cF.exp.Pn, xlab = "Pn teorico", ylab = "Pn experimental", main = "ns = T c = F")
+abline(0, 1)
+legend("topleft", paste("R^2", round(R2.nsT.cF, digits = 2)), bty = "n", text.col = "red")
+legend("bottomright", paste("MSE", signif(MSE.nsT.cF, digits = 2)), bty = "n", text.col = "red")
+
+fit.nsF.cT = lm(mean.cT.exp.Pn ~ mean.nsF.cT.theo.Pn.group)
+Pn.fit.nsF.cT = fitted.values(fit.nsF.cT)
+R2.nsF.cT = cor(mean.cT.exp.Pn, Pn.fit.nsF.cT) ^ 2 
+MSE.nsF.cT = mean((Pn.fit.nsF.cT - mean.cT.exp.Pn) ^ 2)
+plot(Pn.fit.nsF.cT, mean.cT.exp.Pn, xlab = "Pn teorico", ylab = "Pn experimental", main = "ns = F c = T")
+abline(0, 1)
+legend("topleft", paste("R^2", round(R2.nsF.cT, digits = 2)), bty = "n", text.col = "red") 
+legend("bottomright", paste("MSE", signif(MSE.nsF.cT, digits = 2)), bty = "n", text.col = "red")
+
+fit.nsT.cT = lm(mean.cT.exp.Pn ~ mean.nsT.cT.theo.Pn.group)
+Pn.fit.nsT.cT = fitted.values(fit.nsT.cT)
+R2.nsT.cT = cor(mean.cT.exp.Pn, Pn.fit.nsT.cT) ^ 2 
+MSE.nsT.cT = mean((Pn.fit.nsT.cT - mean.cT.exp.Pn) ^ 2)
+plot(Pn.fit.nsT.cT, mean.cT.exp.Pn, xlab = "Pn teorico", ylab = "Pn experimental", main = "ns = T c = T")
+abline(0, 1)
+legend("topleft", paste("R^2", round(R2.nsT.cT, digits = 2)), bty = "n", text.col = "red")
+legend("bottomright", paste("MSE", signif(MSE.nsT.cT, digits = 2)), bty = "n", text.col = "red")
+
+```
+
+```{r}
+layout(matrix(1:4, 2, 2, byrow = T))
+
+fit.nsF.cF = lm(cF.exp.MSDi ~ nsF.cF.theo.MSDi)
+MSDi.fit.nsF.cF = fitted.values(fit.nsF.cF)
+R2.nsF.cF = cor(cF.exp.MSDi[!is.na(cF.exp.MSDi)], MSDi.fit.nsF.cF) ^ 2 
+MSE.nsF.cF = mean((MSDi.fit.nsF.cF - cF.exp.MSDi[!is.na(cF.exp.MSDi)]) ^ 2)
+plot(MSDi.fit.nsF.cF, cF.exp.MSDi[!is.na(cF.exp.MSDi)], xlab = "MSDi teorico", ylab = "MSDi experimental", main = "ns = F c = F")
+abline(0, 1)
+legend("topleft", paste("R^2", round(R2.nsF.cF, digits = 2)), bty = "n", text.col = "red")
+legend("bottomright", paste("MSE", signif(MSE.nsF.cF, digits = T)), bty = "n", text.col = "red")
+
+fit.nsT.cF = lm(cF.exp.MSDi ~ nsT.cF.theo.MSDi)
+MSDi.fit.nsT.cF = fitted.values(fit.nsT.cF)
+R2.nsT.cF = cor(cF.exp.MSDi[!is.na(cF.exp.MSDi)], MSDi.fit.nsT.cF) ^ 2 
+MSE.nsT.cF = mean((MSDi.fit.nsT.cF - cF.exp.MSDi[!is.na(cF.exp.MSDi)]) ^ 2)
+plot(MSDi.fit.nsT.cF, cF.exp.MSDi[!is.na(cF.exp.MSDi)], xlab = "MSDi teorico", ylab = "MSDi experimental", main = "ns = T c = F")
+abline(0, 1)
+legend("topleft", paste("R^2", round(R2.nsT.cF, digits = 2)), bty = "n", text.col = "red")
+legend("bottomright", paste("MSE", signif(MSE.nsT.cF, digits = 2)), bty = "n", text.col = "red")
+
+fit.nsF.cT = lm(cT.exp.MSDi ~ nsF.cT.theo.MSDi)
+MSDi.fit.nsF.cT = fitted.values(fit.nsF.cT)
+R2.nsF.cT = cor(cT.exp.MSDi[!is.na(cT.exp.MSDi)], MSDi.fit.nsF.cT) ^ 2 
+MSE.nsF.cT = mean((MSDi.fit.nsF.cT - cT.exp.MSDi[!is.na(cT.exp.MSDi)]) ^ 2)
+plot(MSDi.fit.nsF.cT, cT.exp.MSDi[!is.na(cT.exp.MSDi)], xlab = "MSDi teorico", ylab = "MSDi experimental", main = "ns = F c = T")
+abline(0, 1)
+legend("topleft", paste("R^2", round(R2.nsF.cT, digits = 2)), bty = "n", text.col = "red")
+legend("bottomright", paste("MSE", signif(MSE.nsF.cT, digits = 2)), bty = "n", text.col = "red")
+
+fit.nsT.cT = lm(cT.exp.MSDi ~ nsT.cT.theo.MSDi)
+MSDi.fit.nsT.cT = fitted.values(fit.nsT.cT)
+R2.nsT.cT = cor(cT.exp.MSDi[!is.na(cT.exp.MSDi)], MSDi.fit.nsT.cT) ^ 2 
+MSE.nsT.cT = mean((MSDi.fit.nsT.cT - cT.exp.MSDi[!is.na(cT.exp.MSDi)]) ^ 2)
+plot(MSDi.fit.nsT.cT, cT.exp.MSDi[!is.na(cT.exp.MSDi)], xlab = "MSDi teorico", ylab = "MSDi experimental", main = "ns = T c = T")
+abline(0, 1)
+legend("topleft", paste("R^2", round(R2.nsT.cT, digits = 2)), bty = "n", text.col = "red")
+legend("bottomright", paste("MSE", signif(MSE.nsT.cT, digits = 2)), bty = "n", text.col = "red")
+```

### 2016-03-20 AllFamilys.Rmd
cambios 20/03/16

---
title: "AllFamilys"
author: "mlm"
date: "20 de marzo de 2016"
output: html_document
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(warning = FALSE, echo = FALSE, message = FALSE)
```

```{r}

# Create matrix.
theo.MSDi.nsF = c()
theo.MSDi.nsT = c()
theo.MSDi.nsF.s = c()
theo.MSDi.nsT.s = c()

exp.MSDi = c()
exp.MSDi.s = c()

# Dirs.
out.dir <- "OUT"

# Read input.
input.fname <- file.path("input_MainMultipleReport.csv")
input <- read.csv(input.fname)

print(input)

for (a in (1:nrow(input))) { 
  family <- as.character(input$family)[a]
  p.ref <- as.character(input$p.ref)[a]
  mut.model = input$mut.model[a]
  n.mut.p = input$n.mut.p[a]
  R0 = input$R0[a]
  K.analysis = input$K.analysis[a]

  #Read experimental data.
  analysis.fname.id <- paste(family, "_mut.model_", mut.model, "_naturalSelection_", "FALSE", "_R0_", R0, "_core_", "FALSE", "_K.analysis_", K.analysis, sep = "")

  m.cF.exp.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.exp.dr.squarei.csv", sep = "")))
  m.cF.exp.smooth.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.exp.smooth.dr.squarei.csv", sep = "")))

  cF.exp.MSDi = colMeans(m.cF.exp.dr.squarei, na.rm = T )
  cF.exp.MSDi.s = colMeans(m.cF.exp.smooth.dr.squarei, na.rm = T )

  #Read theoretical data#

  # ns = F.
  m.nsF.cF.theo.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.dr.squarei.csv", sep = "")))
  m.nsF.cF.theo.smooth.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.smooth.dr.squarei.csv", sep = "")))
  nsF.cF.theo.MSDi = colMeans(m.nsF.cF.theo.dr.squarei, na.rm = T)
  nsF.cF.theo.smooth.MSDi = colMeans(m.nsF.cF.theo.smooth.dr.squarei, na.rm = T)

  # ns = T.
  analysis.fname.id <- paste(family, "_mut.model_", mut.model, "_naturalSelection_", "TRUE", "_R0_", R0, "_core_", "FALSE", "_K.analysis_", K.analysis, sep = "")

  m.nsT.cF.theo.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.dr.squarei.csv", sep = "")))
  m.nsT.cF.theo.smooth.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.smooth.dr.squarei.csv", sep = "")))
  nsT.cF.theo.MSDi = colMeans(m.nsT.cF.theo.dr.squarei, na.rm = T)
  nsT.cF.theo.smooth.MSDi = colMeans(m.nsT.cF.theo.smooth.dr.squarei, na.rm = T)

  ## Fits.
  fit.nsF.cF = lm(cF.exp.MSDi ~ nsF.cF.theo.MSDi)
  MSDi.fit.nsF.cF = fitted.values(fit.nsF.cF)

  fit.nsT.cF = lm(cF.exp.MSDi ~ nsT.cF.theo.MSDi)
  MSDi.fit.nsT.cF = fitted.values(fit.nsT.cF)

  fit.nsF.cF.s = lm(cF.exp.MSDi.s ~ nsF.cF.theo.smooth.MSDi)
  MSDi.fit.nsF.cF.s = fitted.values(fit.nsF.cF.s)

  fit.nsT.cF.s = lm(cF.exp.MSDi.s ~ nsT.cF.theo.smooth.MSDi)
  MSDi.fit.nsT.cF.s = fitted.values(fit.nsT.cF.s)

  # Concatenate information.
  theo.MSDi.nsF = c(theo.MSDi.nsF, MSDi.fit.nsF.cF)
  theo.MSDi.nsT = c(theo.MSDi.nsT, MSDi.fit.nsT.cF)
  theo.MSDi.nsF.s = c(theo.MSDi.nsF.s, MSDi.fit.nsF.cF.s)
  theo.MSDi.nsT.s = c(theo.MSDi.nsT.s, MSDi.fit.nsT.cF.s)

  cF.exp.MSDi = cF.exp.MSDi[!is.na(cF.exp.MSDi)]
  cF.exp.MSDi.s = cF.exp.MSDi.s[!is.na(cF.exp.MSDi.s)]

  exp.MSDi = c(exp.MSDi, cF.exp.MSDi)
  exp.MSDi.s = c(exp.MSDi.s, cF.exp.MSDi.s)

}

# Caluclate measures.
R2.nsF.cF = cor(theo.MSDi.nsF, exp.MSDi)^2 
R2.nsT.cF = cor(theo.MSDi.nsT, exp.MSDi)^2

R2.nsF.cF.s = cor(theo.MSDi.nsF.s, exp.MSDi.s)^2
R2.nsT.cF.s = cor(theo.MSDi.nsT.s, exp.MSDi.s)^2

MSE.nsF.cF = mean((theo.MSDi.nsF - exp.MSDi) ^ 2)
MSE.nsT.cF = mean((theo.MSDi.nsT - exp.MSDi) ^ 2)

MSE.nsF.cF.s = mean((theo.MSDi.nsF.s - exp.MSDi.s) ^ 2)
MSE.nsT.cF.s = mean((theo.MSDi.nsT.s - exp.MSDi.s) ^ 2)

```

```{r, include = F}
layout(matrix(1:3, 3, 1, byrow = F))

plot(theo.MSDi.nsF, type="l", xlab = "sitio", ylab = "Theoretical")
plot(exp.MSDi, type="l", col ="red", ylab = "Experimental")
plot(theo.MSDi.nsF, type="l", ylab = "both")
points(exp.MSDi, col = "red", type="l")
legend("topleft", paste("R^2", round(R2.nsF.cF, digits = 2)), bty = "n", text.col = "red")

```

```{r, include = F}
layout(matrix(1:3, 3, 1, byrow = F)) 
plot(theo.MSDi.nsT, type="l", xlab = "sitio", ylab = "Theoretical")
plot(exp.MSDi, type="l", col ="red", ylab = "Experimental")
plot(theo.MSDi.nsT, type="l", ylab = "both")
points(exp.MSDi, col = "red", type="l")
legend("topleft", paste("R^2", round(R2.nsT.cF, digits = 2)), bty = "n", text.col = "red")
```
All familys fitted smooth MSD profiles

Without natural selection (ns = F)

```{r}
layout(matrix(1:3, 3, 1, byrow = F)) 
plot(theo.MSDi.nsF.s, type="l", xlab = "sitio", ylab = "Theoretical ns = F")
plot(exp.MSDi.s, type="l", col ="red", ylab = "Experimental")
plot(theo.MSDi.nsF.s, type="l", ylab = "both")
points(exp.MSDi.s, col = "red", type="l")
legend("topleft", paste("R^2", round(R2.nsF.cF.s, digits = 2), " ", "MSE", signif(MSE.nsF.cF.s, digits = 2)), bty = "n", text.col = "red")

```

With natural selection (ns = T)

```{r}
layout(matrix(1:3, 3, 1, byrow = F)) 
plot(theo.MSDi.nsT.s, type="l", xlab = "sitio", ylab = "Theoretical ns = T")
plot(exp.MSDi.s, type="l", col ="red", ylab = "Experimental")
plot(theo.MSDi.nsT.s, type="l", ylab = "both")
points(exp.MSDi.s, col = "red", type="l")
legend("topleft", paste("R^2", round(R2.nsT.cF.s, digits = 2), " ", "MSE", signif(MSE.nsT.cF.s, digits = 2)), bty = "n", text.col = "red")

```

### 2016-03-20 MultipleReport.Rmd
cambios 20/03/16

@@
 m.cF.exp.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.exp.dr.squarei.csv", sep = "")))
+m.cF.exp.smooth.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.exp.smooth.dr.squarei.csv", sep = "")))
+
 cF.exp.MSDi = colMeans(m.cF.exp.dr.squarei, na.rm = T )
+cF.exp.smooth.MSDi = colMeans(m.cF.exp.smooth.dr.squarei, na.rm = T )
+
 cF.exp.MSD = rowMeans(m.cF.exp.dr.squarei, na.rm = T)
@@
 m.nsF.cF.theo.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.dr.squarei.csv", sep = "")))
+m.nsF.cF.theo.smooth.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.smooth.dr.squarei.csv", sep = "")))
 nsF.cF.theo.MSDi = colMeans(m.nsF.cF.theo.dr.squarei, na.rm = T)
+nsF.cF.theo.smooth.MSDi = colMeans(m.nsF.cF.theo.smooth.dr.squarei, na.rm = T)
+
 nsF.cF.theo.MSD = rowMeans(m.nsF.cF.theo.dr.squarei, na.rm = T)
@@
 m.nsT.cF.theo.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.dr.squarei.csv", sep = "")))
+m.nsT.cF.theo.smooth.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.smooth.dr.squarei.csv", sep = "")))
 nsT.cF.theo.MSDi = colMeans(m.nsT.cF.theo.dr.squarei, na.rm = T)
+nsT.cF.theo.smooth.MSDi = colMeans(m.nsT.cF.theo.smooth.dr.squarei, na.rm = T)
+
 nsT.cF.theo.MSD = rowMeans(m.nsT.cF.theo.dr.squarei, na.rm = T)
@@
 m.nsT.cF.theo.Qn = t(apply(m.nsT.cF.theo.Pn, 1, cumsum))
+```
+
+```{r, include = FALSE}
 
@@
 m.cT.exp.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.exp.dr.squarei.csv", sep = "")))
+m.cT.exp.dr.smooth.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.exp.smooth.dr.squarei.csv", sep = "")))
 cT.exp.MSDi = colMeans(m.cT.exp.dr.squarei, na.rm = T )
+cT.exp.smooth.MSDi = colMeans(m.cT.exp.dr.smooth.squarei, na.rm = T )
+
 cT.exp.MSD = rowMeans(m.cT.exp.dr.squarei, na.rm = T)
@@
 m.nsF.cT.theo.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.dr.squarei.csv", sep = "")))
+m.nsF.cT.theo.smooth.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.smooth.dr.squarei.csv", sep = "")))
 nsF.cT.theo.MSDi = colMeans(m.nsF.cT.theo.dr.squarei, na.rm = T)
+nsF.cT.theo.smooth.MSDi = colMeans(m.nsF.cT.theo.smooth.dr.squarei, na.rm = T)
+
 nsF.cT.theo.MSD = rowMeans(m.nsF.cT.theo.dr.squarei, na.rm = T)
@@
 m.nsT.cT.theo.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.dr.squarei.csv", sep = "")))
+m.nsT.cT.theo.smooth.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.dr.squarei.csv", sep = "")))
 nsT.cT.theo.MSDi = colMeans(m.nsT.cT.theo.dr.squarei, na.rm = T)
+nsT.cT.theo.smooth.MSDi = colMeans(m.nsT.cT.theo.smooth.dr.squarei, na.rm = T)
+
 nsT.cT.theo.MSD = rowMeans(m.nsT.cT.theo.dr.squarei, na.rm = T)
@@
 
-Con seleccion natural (ns = T): para determinar que sitios mutar, se alineo `r p.ref` con cada una de las proteinas del conjunto, se obtuvieron los indices de los sitios alineados pero mutados y de los sitios con gaps y se simularon `r n.mut.p` mutantes por cada par de proteinas, obteniendose un total de `r n.mut.p * n.exp` mutantes.
-Luego, para el analisis, se tomaron como alineados los sitios alineados de `r p.ref` para cada par de proteinas.
+Con seleccion natural (ns = T): Para seleccionar cuales sitios mutar, se utilizo el "stress model", mediante el cual se asignaron probabilidades de mutacion a cada sitio:
 
-Sin seleccion natural (ns = F): se mutaron al azar la cantidad de sitios correspondientes al % id del conjunto experimental y luego, para el analisis, se tomaron como alineados todos los sitios.
+prob.mut.i = 1 - (beta * CN.i).
+
+Luego, se selecciono para mutar, a los sitios con mayores probabilidades de mutacion. El numero de sitios seleccionados fue el numero de sitios mutados o con gaps en cada par de alineamientos
+
+Sin seleccion natural (ns = F): para cada par de proteínas se mutaron al azar la cantidad de sitios correspondientes a la identidad secuencial.
 
 ### Conjunto experimental 
-`r n.exp` proteinas de la familia de `r family`. Las proteinas tienen un promedio de identidad secuencial de `r round(mean(identity))`%. El core del alineamiento de la familia es de `r n.core` sitios.
-
-### Analisis
-
-Se realizaron 2 tipos de analisis:
-
-*Core (C = T)*: se analizo solo el core conservado del alinemiento (sitios sin gaps en el alineamiento multiple).
-
-*No Core (C = F)*: no se utilizo el core para el analisis.
+`r n.exp` proteinas de la familia de `r family`. Las proteinas tienen un promedio de identidad secuencial de `r round(mean(identity))`%.
 
@@
 
-layout(matrix(1:6, 3, 2, byrow = T))
+layout(matrix(1:3, 1, 3, byrow = T))
 
-hist(cF.exp.MSD, main = "Experimental MSD C = F", xlab = "MSD")
-hist(cT.exp.MSD, main = "Experimental MSD C = T", xlab = "MSD")
-
-hist(nsF.cF.theo.MSD, main = "Theoretical MSD ns = F, C = F", xlab = "MSD")
-hist(nsT.cF.theo.MSD, main = "Theoretical MSD ns = T, C = F", xlab = "MSD")
-hist(nsF.cT.theo.MSD, main = "Theoretical MSD ns = F, C = T", xlab = "MSD")
-hist(nsT.cT.theo.MSD, main = "Theoretical MSD ns = T, C = T", xlab = "MSD")
+hist(cF.exp.MSD, main = "Experimental MSD", xlab = "MSD", col = "red")
+hist(nsF.cF.theo.MSD, main = "Theoretical MSD ns = F", xlab = "MSD", col = "grey")
+hist(nsT.cF.theo.MSD, main = "Theoretical MSD ns = T", xlab = "MSD", col = "grey")
 
@@
 ### MSDi
-```{r}
+```{r, include = F}
 
 layout(matrix(1:4, 2, 2, byrow = T)) 
-plot(rank(nsF.cF.theo.MSDi, na.last = "keep"), main = "MSDi ns = F, c = F", xlab = "site", ylab = "rank MSDi")
+plot(rank(nsF.cF.theo.MSDi, na.last = "keep"), main = "MSDi ns = F", xlab = "site", ylab = "rank MSDi")
 points(rank(cF.exp.MSDi, na.last = "keep"), col = "red")
-plot(rank(nsT.cF.theo.MSDi, na.last = "keep"), main = "MSDi ns = T, c = F", xlab = "site", ylab = "rank MSDi")
+
+plot(rank(nsT.cF.theo.MSDi, na.last = "keep"), main = "MSDi ns = T", xlab = "site", ylab = "rank MSDi")
 points(rank(cF.exp.MSDi, na.last = "keep"), col = "red")
-plot(rank(nsF.cT.theo.MSDi, na.last = "keep"), main = "MSDi ns = F, c = T", xlab = "site", ylab = "rank MSDi")
-points(rank(cT.exp.MSDi, na.last = "keep"), col = "red")
-plot(rank(nsT.cT.theo.MSDi, na.last = "keep"), main = "MSDi ns = T, c = T", xlab = "site", ylab = "rank MSDi")
-points(rank(cT.exp.MSDi, na.last = "keep"), col = "red")
+
+plot(rank(nsF.cF.theo.smooth.MSDi, na.last = "keep"), main = "MSDi.smooth ns = F", xlab = "site", ylab = "rank MSDi")
+points(rank(cF.exp.smooth.MSDi, na.last = "keep"), col = "red")
+
+plot(rank(nsT.cF.theo.smooth.MSDi, na.last = "keep"), main = "MSDi.smooth ns = T", xlab = "site", ylab = "rank MSDi")
+points(rank(cF.exp.smooth.MSDi, na.last = "keep"), col = "red")
+
 ```
+Los perfiles teoricos de MSDi y smooth.MSDi fueron fiteados con los perfiles exterimentales. Se compararon y se calcularon R^2 y MSE. 
+```{r}
+keep.data = c()
+
+layout(matrix(1:4, 2, 2, byrow = F))
+
+fit.nsF.cF = lm(cF.exp.MSDi ~ nsF.cF.theo.MSDi)
+MSDi.fit.nsF.cF = fitted.values(fit.nsF.cF)
+R2.nsF.cF = cor(cF.exp.MSDi[!is.na(cF.exp.MSDi)], MSDi.fit.nsF.cF) ^ 2 
+MSE.nsF.cF = mean((MSDi.fit.nsF.cF - cF.exp.MSDi[!is.na(cF.exp.MSDi)]) ^ 2)
+
+keep.data = c(keep.data, R2.nsF.cF, MSE.nsF.cF)
+
+plot(MSDi.fit.nsF.cF, main = "MSDi ns = F", xlab = "site", ylab = "MSDi", ylim = c(0, max(cbind(MSDi.fit.nsF.cF, cF.exp.MSDi[!is.na(cF.exp.MSDi)]))))
+points(cF.exp.MSDi[!is.na(cF.exp.MSDi)], col = "red")
+
+plot(MSDi.fit.nsF.cF, cF.exp.MSDi[!is.na(cF.exp.MSDi)], xlab = "MSDi teorico", ylab = "MSDi experimental", main = "ns = F c = F")
+abline(0, 1)
+legend("topleft", paste("R^2", round(R2.nsF.cF, digits = 2)), bty = "n", text.col = "red")
+legend("bottomright", paste("MSE", signif(MSE.nsF.cF, digits = T)), bty = "n", text.col = "red")
+
+fit.nsT.cF = lm(cF.exp.MSDi ~ nsT.cF.theo.MSDi)
+MSDi.fit.nsT.cF = fitted.values(fit.nsT.cF)
+R2.nsT.cF = cor(cF.exp.MSDi[!is.na(cF.exp.MSDi)], MSDi.fit.nsT.cF) ^ 2 
+MSE.nsT.cF = mean((MSDi.fit.nsT.cF - cF.exp.MSDi[!is.na(cF.exp.MSDi)]) ^ 2)
+
+keep.data = c(keep.data, R2.nsT.cF, MSE.nsT.cF)
+
+plot(MSDi.fit.nsT.cF, main = "MSDi ns = T", xlab = "site", ylab = "MSDi", ylim = c(0, max(cbind(MSDi.fit.nsT.cF, cF.exp.MSDi[!is.na(cF.exp.MSDi)]))))
+points(cF.exp.MSDi[!is.na(cF.exp.MSDi)], col = "red")
+
+plot(MSDi.fit.nsT.cF, cF.exp.MSDi[!is.na(cF.exp.MSDi)], xlab = "MSDi teorico", ylab = "MSDi experimental", main = "ns = T c = F")
+abline(0, 1)
+legend("topleft", paste("R^2", round(R2.nsT.cF, digits = 2)), bty = "n", text.col = "red")
+legend("bottomright", paste("MSE", signif(MSE.nsT.cF, digits = 2)), bty = "n", text.col = "red")
+```
+
+```{r}
+layout(matrix(1:4, 2, 2, byrow = F))
+
+fit.nsF.cF = lm(cF.exp.smooth.MSDi ~ nsF.cF.theo.smooth.MSDi)
+MSDi.fit.nsF.cF = fitted.values(fit.nsF.cF)
+R2.nsF.cF = cor(cF.exp.smooth.MSDi[!is.na(cF.exp.smooth.MSDi)], MSDi.fit.nsF.cF) ^ 2 
+MSE.nsF.cF = mean((MSDi.fit.nsF.cF - cF.exp.smooth.MSDi[!is.na(cF.exp.smooth.MSDi)]) ^ 2)
+
+keep.data = c(keep.data, R2.nsF.cF, MSE.nsF.cF)
+
+plot(MSDi.fit.nsF.cF, main = "smooth.MSDi ns = F", xlab = "site", ylab = "MSDi", ylim = c(0, max(cbind(MSDi.fit.nsF.cF, cF.exp.smooth.MSDi[!is.na(cF.exp.smooth.MSDi)])))) 
+points(cF.exp.smooth.MSDi[!is.na(cF.exp.smooth.MSDi)], col = "red")
+
+plot(MSDi.fit.nsF.cF, cF.exp.smooth.MSDi[!is.na(cF.exp.smooth.MSDi)], xlab = "MSDi.smooth teorico", ylab = "MSDi.smooth experimental", main = "ns = F c = F")
+abline(0, 1)
+legend("topleft", paste("R^2", round(R2.nsF.cF, digits = 2)), bty = "n", text.col = "red")
+legend("bottomright", paste("MSE", signif(MSE.nsF.cF, digits = T)), bty = "n", text.col = "red")
+
+fit.nsT.cF = lm(cF.exp.smooth.MSDi ~ nsT.cF.theo.smooth.MSDi)
+MSDi.fit.nsT.cF = fitted.values(fit.nsT.cF)
+R2.nsT.cF = cor(cF.exp.smooth.MSDi[!is.na(cF.exp.smooth.MSDi)], MSDi.fit.nsT.cF) ^ 2 
+MSE.nsT.cF = mean((MSDi.fit.nsT.cF - cF.exp.smooth.MSDi[!is.na(cF.exp.smooth.MSDi)]) ^ 2)
+
+keep.data = c(keep.data, R2.nsT.cF, MSE.nsT.cF)
+
+plot(MSDi.fit.nsT.cF, main = "smooth.MSDi ns = T", xlab = "site", ylab = "MSDi", ylim = c(0, max(cbind(MSDi.fit.nsT.cF, cF.exp.smooth.MSDi[!is.na(cF.exp.smooth.MSDi)])))) 
+points(cF.exp.smooth.MSDi[!is.na(cF.exp.smooth.MSDi)], col = "red")
+
+plot(MSDi.fit.nsT.cF, cF.exp.smooth.MSDi[!is.na(cF.exp.smooth.MSDi)], xlab = "MSDi.smooth teorico", ylab = "MSDi.smooth experimental", main = "ns = T c = F")
+abline(0, 1)
+legend("topleft", paste("R^2", round(R2.nsT.cF, digits = 2)), bty = "n", text.col = "red")
+legend("bottomright", paste("MSE", signif(MSE.nsT.cF, digits = 2)), bty = "n", text.col = "red")
+
+```
+
 rojo: experimental
@@
 
-Los perfiles de MSDi fueron normalizados con la funcion rank().
+## Pn y Qn
+Las distribuciones de *Pn* y *Qn* de los conjuntos son las siguientes:
+
+```{r}
+# Re-ordenate Pn.
+m.theo.index = matrix(ncol = 1, nrow = n.mut)
+for (P in (1:n.exp)) {
+  for (mut in (1:n.mut.p)) {
+    m.theo.index[(P - 1) * n.mut.p + mut, ] = ((mut - 1) * 10 + P)
+  }
+}
+m.nsF.cF.theo.Pn = m.nsF.cF.theo.Pn[as.vector(m.theo.index), ]
+m.nsT.cF.theo.Pn = m.nsT.cF.theo.Pn[as.vector(m.theo.index), ]
+m.nsF.cT.theo.Pn = m.nsF.cT.theo.Pn[as.vector(m.theo.index), ]
+m.nsT.cT.theo.Pn = m.nsT.cT.theo.Pn[as.vector(m.theo.index), ]
+
+# Calculate groups, means and quantiles.
+nsF.cF.theo.Pn.group = CalculateGroupsMeansQuantiles(m.nsF.cF.theo.Pn, n.mut.p, n.exp)
+mean.nsF.cF.theo.Pn.group = nsF.cF.theo.Pn.group$mean.mean.group
+nsF.cF.theo.Pn.group.quantile1 = nsF.cF.theo.Pn.group$mean.quantile1.group
+nsF.cF.theo.Pn.group.quantile2 = nsF.cF.theo.Pn.group$mean.quantile2.group
+
+nsT.cF.theo.Pn.group = CalculateGroupsMeansQuantiles(m.nsT.cF.theo.Pn, n.mut.p, n.exp)
+mean.nsT.cF.theo.Pn.group = nsT.cF.theo.Pn.group$mean.mean.group
+nsT.cF.theo.Pn.group.quantile1 = nsT.cF.theo.Pn.group$mean.quantile1.group
+nsT.cF.theo.Pn.group.quantile2 = nsT.cF.theo.Pn.group$mean.quantile2.group
+```
+
+```{r, inlude = FALSE}
+
+nsF.cT.theo.Pn.group = CalculateGroupsMeansQuantiles(m.nsF.cT.theo.Pn, n.mut.p, n.exp)
+mean.nsF.cT.theo.Pn.group = nsF.cT.theo.Pn.group$mean.mean.group
+nsF.cT.theo.Pn.group.quantile1 = nsF.cT.theo.Pn.group$mean.quantile1.group
+nsF.cT.theo.Pn.group.quantile2 = nsF.cT.theo.Pn.group$mean.quantile2.group
+
+nsT.cT.theo.Pn.group = CalculateGroupsMeansQuantiles(m.nsT.cT.theo.Pn, n.mut.p, n.exp)
+mean.nsT.cT.theo.Pn.group = nsT.cT.theo.Pn.group$mean.mean.group
+nsT.cT.theo.Pn.group.quantile1 = nsT.cT.theo.Pn.group$mean.quantile1.group
+nsT.cT.theo.Pn.group.quantile2 = nsT.cT.theo.Pn.group$mean.quantile2.group
+```
+
+```{r, inlude = FALSE}
+
+nsF.cF.theo.Qn.group = CalculateGroupsMeansQuantiles(m.nsF.cF.theo.Qn, n.mut.p, n.exp)
+mean.nsF.cF.theo.Qn.group = nsF.cF.theo.Qn.group$mean.mean.group
+nsF.cF.theo.Qn.group.quantile1 = nsF.cF.theo.Qn.group$mean.quantile1.group
+nsF.cF.theo.Qn.group.quantile2 = nsF.cF.theo.Qn.group$mean.quantile2.group
+
+nsT.cF.theo.Qn.group = CalculateGroupsMeansQuantiles(m.nsT.cF.theo.Qn, n.mut.p, n.exp)
+mean.nsT.cF.theo.Qn.group = nsT.cF.theo.Qn.group$mean.mean.group
+nsT.cF.theo.Qn.group.quantile1 = nsT.cF.theo.Qn.group$mean.quantile1.group
+nsT.cF.theo.Qn.group.quantile2 = nsT.cF.theo.Qn.group$mean.quantile2.group
+
+nsF.cT.theo.Qn.group = CalculateGroupsMeansQuantiles(m.nsF.cT.theo.Qn, n.mut.p, n.exp)
+mean.nsF.cT.theo.Qn.group = nsF.cT.theo.Qn.group$mean.mean.group
+nsF.cT.theo.Qn.group.quantile1 = nsF.cT.theo.Qn.group$mean.quantile1.group
+nsF.cT.theo.Qn.group.quantile2 = nsF.cT.theo.Qn.group$mean.quantile2.group
+
+nsT.cT.theo.Qn.group = CalculateGroupsMeansQuantiles(m.nsT.cT.theo.Qn, n.mut.p, n.exp)
+mean.nsT.cT.theo.Qn.group = nsT.cT.theo.Qn.group$mean.mean.group
+nsT.cT.theo.Qn.group.quantile1 = nsT.cT.theo.Qn.group$mean.quantile1.group
+nsT.cT.theo.Qn.group.quantile2 = nsT.cT.theo.Qn.group$mean.quantile2.group
+```
+
+```{r}
+
+# Graphics.
+
+layout(matrix(1:2, 1, 2, byrow = T))
+
+plot(mean.nsF.cF.theo.Pn.group, 
+     main = "Pn promedio ns = F", 
+     xlab = "nmodo",
+     ylab = "Pn",
+     ylim = c(0, max(c(nsF.cF.theo.Pn.group.quantile2, mean.cF.exp.Pn))))
+lines(nsF.cF.theo.Pn.group.quantile1)
+lines(nsF.cF.theo.Pn.group.quantile2)
+points(mean.cF.exp.Pn, col = "red")
+lines(as.vector(cF.exp.Pn.quantile1), col = "red")
+lines(as.vector(cF.exp.Pn.quantile2), col = "red")
+
+plot(mean.nsT.cF.theo.Pn.group, 
+     main = "Pn promedio ns = T", 
+     xlab = "nmodo",
+     ylab = "Pn",
+     ylim = c(0, max(c(nsT.cF.theo.Pn.group.quantile2, mean.cF.exp.Pn))))
+lines(nsT.cF.theo.Pn.group.quantile1)
+lines(nsT.cF.theo.Pn.group.quantile2)
+points(mean.cF.exp.Pn, col = "red")
+lines(as.vector(cF.exp.Pn.quantile1), col = "red")
+lines(as.vector(cF.exp.Pn.quantile2), col = "red")
+
+```
+
+*Negro*: Puntos: promedio de promedios teorico. Lineas: promedio de cuantiles 0.05 y 0.95 de `r n.mut.p` grupos de `r n.exp` mutantes teoricas.
+*Rojo*: Experimental. Puntos: promedio. Lineas: cuantiles 0.05 y 0.95.
+
+Posteriormente, los perfiles de Pn teoricos fueron fiteados con los perfiles exterimentales. Se compararon y se calcularon R^2 y MSE.
+
+```{r}
+layout(matrix(1:2, 1, 2, byrow = T))
+
+fit.nsF.cF = lm(mean.cF.exp.Pn ~ mean.nsF.cF.theo.Pn.group)
+Pn.fit.nsF.cF = fitted.values(fit.nsF.cF)
+R2.nsF.cF = cor(mean.cF.exp.Pn, Pn.fit.nsF.cF) ^ 2 
+MSE.nsF.cF = mean((Pn.fit.nsF.cF - mean.cF.exp.Pn) ^ 2)
+plot(Pn.fit.nsF.cF, mean.cF.exp.Pn, xlab = "Pn teorico", ylab = "Pn experimental", main = "ns = F c = F")
+abline(0, 1)
+legend("topleft", paste("R^2", round(R2.nsF.cF, digits = 2)), bty = "n", text.col = "red")
+legend("bottomright", paste("MSE", signif(MSE.nsF.cF, digits = 2)), bty = "n", text.col = "red")
+
+keep.data = c(keep.data, R2.nsF.cF, MSE.nsF.cF)
+
+fit.nsT.cF = lm(mean.cF.exp.Pn ~ mean.nsT.cF.theo.Pn.group)
+Pn.fit.nsT.cF = fitted.values(fit.nsT.cF)
+R2.nsT.cF = cor(mean.cF.exp.Pn, Pn.fit.nsT.cF) ^ 2 
+MSE.nsT.cF = mean((Pn.fit.nsT.cF - mean.cF.exp.Pn) ^ 2)
+plot(Pn.fit.nsT.cF, mean.cF.exp.Pn, xlab = "Pn teorico", ylab = "Pn experimental", main = "ns = T c = F")
+abline(0, 1)
+legend("topleft", paste("R^2", round(R2.nsT.cF, digits = 2)), bty = "n", text.col = "red")
+legend("bottomright", paste("MSE", signif(MSE.nsT.cF, digits = 2)), bty = "n", text.col = "red")
+
+keep.data = c(keep.data, R2.nsT.cF, MSE.nsT.cF)
+
+write.csv(keep.data, file = "cor_MSE.csv", appen = TRUE)
+```
 
@@
 }
+```
+
+```{r, include = FALSE}
 
@@
 
-### RHO y AUC
-Las distribuciones de *auc* y *rho* para cada conjunto se muestran a continuacion (negro = teorico, rojo = experimental)
+### RHO
+Las distribuciones de *rho* para cada conjunto se muestran a continuacion
 
 ```{r}
-layout(matrix(1:4, 2, 2, byrow = T))
-plot(density(nsF.cF.rho.t.1), ylab = "Frecuencia", xlab = "rho", main = "Histograma rho 10 modos ns = F, c = F")
+layout(matrix(1:2, 1, 2, byrow = T))
+plot(density(nsF.cF.rho.t.1), ylab = "Frecuencia", xlab = "rho", main = "Histograma rho 10 modos ns = F")
 points(x = c(cF.rho.e.1), y = rep(0, n.exp), col = "red")
-plot(density(nsT.cF.rho.t.1), ylab = "Frecuencia", xlab = "rho", main = "Histograma rho 10 modos ns = T, c = F")
+plot(density(nsT.cF.rho.t.1), ylab = "Frecuencia", xlab = "rho", main = "Histograma rho 10 modos ns = T")
 points(x = c(cF.rho.e.1), y = rep(0, n.exp), col = "red")
+```
+
+```{r, include = FALSE}
 plot(density(nsF.cT.rho.t.1), ylab = "Frecuencia", xlab = "rho", main = "Histograma rho 10 modos ns = F, c = T")
@@
 ```
+
 ```{r}
-layout(matrix(1:4, 2, 2, byrow = T))
-plot(density(nsF.cF.rho.t.3), ylab = "Frecuencia", xlab = "rho", main = "Histograma rho 50 modos ns = F, c = F")
+layout(matrix(1:2, 1, 2, byrow = T))
+plot(density(nsF.cF.rho.t.3), ylab = "Frecuencia", xlab = "rho", main = "Histograma rho 50 modos ns = F")
 points(x = c(cF.rho.e.3), y = rep(0, n.exp), col = "red")
-plot(density(nsT.cF.rho.t.3), ylab = "Frecuencia", xlab = "rho", main = "Histograma rho 50 modos ns = T, c = F")
+plot(density(nsT.cF.rho.t.3), ylab = "Frecuencia", xlab = "rho", main = "Histograma rho 50 modos ns = T")
 points(x = c(cF.rho.e.3), y = rep(0, n.exp), col = "red")
+```
+
+```{r, include = FALSE}
 plot(density(nsF.cT.rho.t.3), ylab = "Frecuencia", xlab = "rho", main = "Histograma rho 50 modos ns = F, c = T")
@@
 ```
-```{r}
+
+```{r, include = FALSE}
 layout(matrix(1:4, 2, 2, byrow = T))
@@
 
-## Pn y Qn
-Las distribuciones de *Pn* y *Qn* de los conjuntos son las siguientes:
-
-```{r}
-# Re-ordenate Pn and Qn.
-m.theo.index = matrix(ncol = 1, nrow = n.mut)
-for (P in (1:n.exp)) {
-  for (mut in (1:n.mut.p)) {
-    m.theo.index[(P - 1) * n.mut.p + mut, ] = ((mut - 1) * 10 + P)
-  }
-}
-m.nsF.cF.theo.Pn = m.nsF.cF.theo.Pn[as.vector(m.theo.index), ]
-m.nsF.cF.theo.Qn = m.nsF.cF.theo.Qn[as.vector(m.theo.index), ]
-
-m.nsT.cF.theo.Pn = m.nsT.cF.theo.Pn[as.vector(m.theo.index), ]
-m.nsT.cF.theo.Qn = m.nsT.cF.theo.Qn[as.vector(m.theo.index), ]
-
-m.nsF.cT.theo.Pn = m.nsF.cT.theo.Pn[as.vector(m.theo.index), ]
-m.nsF.cT.theo.Qn = m.nsF.cT.theo.Qn[as.vector(m.theo.index), ]
-
-m.nsT.cT.theo.Pn = m.nsT.cT.theo.Pn[as.vector(m.theo.index), ]
-m.nsT.cT.theo.Qn = m.nsT.cT.theo.Qn[as.vector(m.theo.index), ]
-
-# Calculate groups, means and quantiles.
-nsF.cF.theo.Pn.group = CalculateGroupsMeansQuantiles(m.nsF.cF.theo.Pn, n.mut.p, n.exp)
-mean.nsF.cF.theo.Pn.group = nsF.cF.theo.Pn.group$mean.mean.group
-nsF.cF.theo.Pn.group.quantile1 = nsF.cF.theo.Pn.group$mean.quantile1.group
-nsF.cF.theo.Pn.group.quantile2 = nsF.cF.theo.Pn.group$mean.quantile2.group
-
-nsT.cF.theo.Pn.group = CalculateGroupsMeansQuantiles(m.nsT.cF.theo.Pn, n.mut.p, n.exp)
-mean.nsT.cF.theo.Pn.group = nsT.cF.theo.Pn.group$mean.mean.group
-nsT.cF.theo.Pn.group.quantile1 = nsT.cF.theo.Pn.group$mean.quantile1.group
-nsT.cF.theo.Pn.group.quantile2 = nsT.cF.theo.Pn.group$mean.quantile2.group
-
-nsF.cT.theo.Pn.group = CalculateGroupsMeansQuantiles(m.nsF.cT.theo.Pn, n.mut.p, n.exp)
-mean.nsF.cT.theo.Pn.group = nsF.cT.theo.Pn.group$mean.mean.group
-nsF.cT.theo.Pn.group.quantile1 = nsF.cT.theo.Pn.group$mean.quantile1.group
-nsF.cT.theo.Pn.group.quantile2 = nsF.cT.theo.Pn.group$mean.quantile2.group
-
-nsT.cT.theo.Pn.group = CalculateGroupsMeansQuantiles(m.nsT.cT.theo.Pn, n.mut.p, n.exp)
-mean.nsT.cT.theo.Pn.group = nsT.cT.theo.Pn.group$mean.mean.group
-nsT.cT.theo.Pn.group.quantile1 = nsT.cT.theo.Pn.group$mean.quantile1.group
-nsT.cT.theo.Pn.group.quantile2 = nsT.cT.theo.Pn.group$mean.quantile2.group
-
-nsF.cF.theo.Qn.group = CalculateGroupsMeansQuantiles(m.nsF.cF.theo.Qn, n.mut.p, n.exp)
-mean.nsF.cF.theo.Qn.group = nsF.cF.theo.Qn.group$mean.mean.group
-nsF.cF.theo.Qn.group.quantile1 = nsF.cF.theo.Qn.group$mean.quantile1.group
-nsF.cF.theo.Qn.group.quantile2 = nsF.cF.theo.Qn.group$mean.quantile2.group
-
-nsT.cF.theo.Qn.group = CalculateGroupsMeansQuantiles(m.nsT.cF.theo.Qn, n.mut.p, n.exp)
-mean.nsT.cF.theo.Qn.group = nsT.cF.theo.Qn.group$mean.mean.group
-nsT.cF.theo.Qn.group.quantile1 = nsT.cF.theo.Qn.group$mean.quantile1.group
-nsT.cF.theo.Qn.group.quantile2 = nsT.cF.theo.Qn.group$mean.quantile2.group
-
-nsF.cT.theo.Qn.group = CalculateGroupsMeansQuantiles(m.nsF.cT.theo.Qn, n.mut.p, n.exp)
-mean.nsF.cT.theo.Qn.group = nsF.cT.theo.Qn.group$mean.mean.group
-nsF.cT.theo.Qn.group.quantile1 = nsF.cT.theo.Qn.group$mean.quantile1.group
-nsF.cT.theo.Qn.group.quantile2 = nsF.cT.theo.Qn.group$mean.quantile2.group
-
-nsT.cT.theo.Qn.group = CalculateGroupsMeansQuantiles(m.nsT.cT.theo.Qn, n.mut.p, n.exp)
-mean.nsT.cT.theo.Qn.group = nsT.cT.theo.Qn.group$mean.mean.group
-nsT.cT.theo.Qn.group.quantile1 = nsT.cT.theo.Qn.group$mean.quantile1.group
-nsT.cT.theo.Qn.group.quantile2 = nsT.cT.theo.Qn.group$mean.quantile2.group
-
-# Graphics.
-
-layout(matrix(1:4, 2, 2, byrow = T))
-
-plot(mean.nsF.cF.theo.Pn.group, 
-     main = "Pn promedio ns = F, C = F", 
-     xlab = "nmodo",
-     ylab = "Pn",
-     ylim = c(0, max(c(nsF.cF.theo.Pn.group.quantile2, mean.cF.exp.Pn))))
-lines(nsF.cF.theo.Pn.group.quantile1)
-lines(nsF.cF.theo.Pn.group.quantile2)
-points(mean.cF.exp.Pn, col = "red")
-lines(as.vector(cF.exp.Pn.quantile1), col = "red")
-lines(as.vector(cF.exp.Pn.quantile2), col = "red")
-
-plot(mean.nsT.cF.theo.Pn.group, 
-     main = "Pn promedio ns = T, C = F", 
-     xlab = "nmodo",
-     ylab = "Pn",
-     ylim = c(0, max(c(nsT.cF.theo.Pn.group.quantile2, mean.cF.exp.Pn))))
-lines(nsT.cF.theo.Pn.group.quantile1)
-lines(nsT.cF.theo.Pn.group.quantile2)
-points(mean.cF.exp.Pn, col = "red")
-lines(as.vector(cF.exp.Pn.quantile1), col = "red")
-lines(as.vector(cF.exp.Pn.quantile2), col = "red")
+```{r, include = FALSE}
 
@@
 
-```{r}
+```{r, include = FALSE}
 
@@
 
-*Negro*: Puntos: promedio de promedios teorico. Lineas: promedio de cuantiles 0.05 y 0.95 de `r n.mut.p` grupos de `r n.exp` mutantes teoricas.
-*Rojo*: Experimental. Puntos: promedio. Lineas: cuantiles 0.05 y 0.95.
-
-## R^2 y MSE
-Las comparaciones entre perfines promedio Pn y MSDi teoricos fiteados y experimentales se muestran a continuacion. En cada grafico se muestra la correlacion (R^2) y el error (MSE).
-```{r}
-layout(matrix(1:4, 2, 2, byrow = T))
-
-fit.nsF.cF = lm(mean.cF.exp.Pn ~ mean.nsF.cF.theo.Pn.group)
-Pn.fit.nsF.cF = fitted.values(fit.nsF.cF)
-R2.nsF.cF = cor(mean.cF.exp.Pn, Pn.fit.nsF.cF) ^ 2 
-MSE.nsF.cF = mean((Pn.fit.nsF.cF - mean.cF.exp.Pn) ^ 2)
-plot(Pn.fit.nsF.cF, mean.cF.exp.Pn, xlab = "Pn teorico", ylab = "Pn experimental", main = "ns = F c = F")
-abline(0, 1)
-legend("topleft", paste("R^2", round(R2.nsF.cF, digits = 2)), bty = "n", text.col = "red")
-legend("bottomright", paste("MSE", signif(MSE.nsF.cF, digits = 2)), bty = "n", text.col = "red")
-
-fit.nsT.cF = lm(mean.cF.exp.Pn ~ mean.nsT.cF.theo.Pn.group)
-Pn.fit.nsT.cF = fitted.values(fit.nsT.cF)
-R2.nsT.cF = cor(mean.cF.exp.Pn, Pn.fit.nsT.cF) ^ 2 
-MSE.nsT.cF = mean((Pn.fit.nsT.cF - mean.cF.exp.Pn) ^ 2)
-plot(Pn.fit.nsT.cF, mean.cF.exp.Pn, xlab = "Pn teorico", ylab = "Pn experimental", main = "ns = T c = F")
-abline(0, 1)
-legend("topleft", paste("R^2", round(R2.nsT.cF, digits = 2)), bty = "n", text.col = "red")
-legend("bottomright", paste("MSE", signif(MSE.nsT.cF, digits = 2)), bty = "n", text.col = "red")
-
+```{r, include = FALSE}
 fit.nsF.cT = lm(mean.cT.exp.Pn ~ mean.nsF.cT.theo.Pn.group)
@@
 
-```{r}
+```{r, include = F}
 layout(matrix(1:4, 2, 2, byrow = T))
@@
 MSDi.fit.nsF.cF = fitted.values(fit.nsF.cF)
-R2.nsF.cF = cor(cF.exp.MSDi[!is.na(cF.exp.MSDi)], MSDi.fit.nsF.cF) ^ 2 
-MSE.nsF.cF = mean((MSDi.fit.nsF.cF - cF.exp.MSDi[!is.na(cF.exp.MSDi)]) ^ 2)
-plot(MSDi.fit.nsF.cF, cF.exp.MSDi[!is.na(cF.exp.MSDi)], xlab = "MSDi teorico", ylab = "MSDi experimental", main = "ns = F c = F")
+R2.nsF.cF = cor(rank(cF.exp.MSDi[!is.na(cF.exp.MSDi)]), rank(MSDi.fit.nsF.cF)) ^ 2 
+MSE.nsF.cF = mean((rank(MSDi.fit.nsF.cF - cF.exp.MSDi[!is.na(cF.exp.MSDi)])) ^ 2)
+plot(rank(MSDi.fit.nsF.cF), rank(cF.exp.MSDi[!is.na(cF.exp.MSDi)]), xlab = "MSDi teorico", ylab = "MSDi experimental", main = "ns = F c = F")
 abline(0, 1)
@@
 MSDi.fit.nsT.cF = fitted.values(fit.nsT.cF)
-R2.nsT.cF = cor(cF.exp.MSDi[!is.na(cF.exp.MSDi)], MSDi.fit.nsT.cF) ^ 2 
-MSE.nsT.cF = mean((MSDi.fit.nsT.cF - cF.exp.MSDi[!is.na(cF.exp.MSDi)]) ^ 2)
-plot(MSDi.fit.nsT.cF, cF.exp.MSDi[!is.na(cF.exp.MSDi)], xlab = "MSDi teorico", ylab = "MSDi experimental", main = "ns = T c = F")
+R2.nsT.cF = cor(rank(cF.exp.MSDi[!is.na(cF.exp.MSDi)]), rank(MSDi.fit.nsT.cF)) ^ 2 
+MSE.nsT.cF = mean((rank(MSDi.fit.nsT.cF) - rank(cF.exp.MSDi[!is.na(cF.exp.MSDi)])) ^ 2)
+plot(rank(MSDi.fit.nsT.cF), rank(cF.exp.MSDi[!is.na(cF.exp.MSDi)]), xlab = "MSDi teorico", ylab = "MSDi experimental", main = "ns = T c = F")
 abline(0, 1)
@@
 legend("bottomright", paste("MSE", signif(MSE.nsT.cF, digits = 2)), bty = "n", text.col = "red")
+```
+
+```{r, include = FALSE, include = FALSE}
+layout(matrix(1:4, 2, 2, byrow = T))
+
+fit.nsF.cF = lm(cF.exp.smooth.MSDi ~ nsF.cF.theo.smooth.MSDi)
+MSDi.fit.nsF.cF = fitted.values(fit.nsF.cF)
+R2.nsF.cF = cor(rank(cF.exp.smooth.MSDi[!is.na(cF.exp.smooth.MSDi)]), rank(MSDi.fit.nsF.cF)) ^ 2 
+MSE.nsF.cF = mean((rank(MSDi.fit.nsF.cF) - rank(cF.exp.smooth.MSDi[!is.na(cF.exp.smooth.MSDi)])) ^ 2)
+plot(rank(MSDi.fit.nsF.cF), rank(cF.exp.smooth.MSDi[!is.na(cF.exp.smooth.MSDi)]), xlab = "MSDi.smooth teorico", ylab = "MSDi.smooth experimental", main = "ns = F c = F")
+abline(0, 1) 
+legend("topleft", paste("R^2", round(R2.nsF.cF, digits = 2)), bty = "n", text.col = "red")
+legend("bottomright", paste("MSE", signif(MSE.nsF.cF, digits = T)), bty = "n", text.col = "red")
+
+fit.nsT.cF = lm(cF.exp.smooth.MSDi ~ nsT.cF.theo.smooth.MSDi)
+MSDi.fit.nsT.cF = fitted.values(fit.nsT.cF)
+R2.nsT.cF = cor(rank(cF.exp.smooth.MSDi[!is.na(cF.exp.smooth.MSDi)]), rank(MSDi.fit.nsT.cF)) ^ 2 
+MSE.nsT.cF = mean((rank(MSDi.fit.nsT.cF) - rank(cF.exp.smooth.MSDi[!is.na(cF.exp.smooth.MSDi)])) ^ 2)
+plot(rank(MSDi.fit.nsT.cF), rank(cF.exp.smooth.MSDi[!is.na(cF.exp.smooth.MSDi)]), xlab = "MSDi.smooth teorico", ylab = "MSDi.smooth experimental", main = "ns = T c = F")
+abline(0, 1)
+legend("topleft", paste("R^2", round(R2.nsT.cF, digits = 2)), bty = "n", text.col = "red")
+legend("bottomright", paste("MSE", signif(MSE.nsT.cF, digits = 2)), bty = "n", text.col = "red")
+
+```
+
+```{r, include = FALSE}
 
@@
 ```
+
+```{r, include = FALSE}
+fit.nsF.cT = lm(cT.exp.smooth.MSDi ~ nsF.cT.theo.smooth.MSDi)
+MSDi.fit.nsF.cT = fitted.values(fit.nsF.cT)
+R2.nsF.cT = cor(cT.exp.smooth.MSDi[!is.na(cT.exp.smooth.MSDi)], MSDi.fit.nsF.cT) ^ 2 
+MSE.nsF.cT = mean((MSDi.fit.nsF.cT - cT.exp.smooth.MSDi[!is.na(cT.exp.smooth.MSDi)]) ^ 2)
+plot(MSDi.fit.nsF.cT, cT.exp.smooth.MSDi[!is.na(cT.exp.smooth.MSDi)], xlab = "MSDi.smooth teorico", ylab = "MSDi.smooth experimental", main = "ns = F c = T")
+abline(0, 1)
+legend("topleft", paste("R^2", round(R2.nsF.cT, digits = 2)), bty = "n", text.col = "red")
+legend("bottomright", paste("MSE", signif(MSE.nsF.cT, digits = 2)), bty = "n", text.col = "red")
+
+fit.nsT.cT = lm(cT.exp.smooth.MSDi ~ nsT.cT.theo.smooth.MSDi)
+MSDi.fit.nsT.cT = fitted.values(fit.nsT.cT)
+R2.nsT.cT = cor(cT.exp.smooth.MSDi[!is.na(cT.exp.smooth.MSDi)], MSDi.fit.nsT.cT) ^ 2 
+MSE.nsT.cT = mean((MSDi.fit.nsT.cT - cT.exp.smooth.MSDi[!is.na(cT.exp.smooth.MSDi)]) ^ 2)
+plot(MSDi.fit.nsT.cT, cT.exp.smooth.MSDi[!is.na(cT.exp.smooth.MSDi)], xlab = "MSDi.smooth teorico", ylab = "MSDi.smooth experimental", main = "ns = T c = T")
+abline(0, 1)
+legend("topleft", paste("R^2", round(R2.nsT.cT, digits = 2)), bty = "n", text.col = "red")
+legend("bottomright", paste("MSE", signif(MSE.nsT.cT, digits = 2)), bty = "n", text.col = "red")
+```

### 2016-03-20 FUNCTIONS/AnalyzeExperimentalTheoretical.R

@@ -103,10 +103,14 @@ AnalyzeExperimentalTheoretical <- function(family,
   m.exp.Pn = matrix(nrow = n.prot, ncol = 3 * n.sites.p.ref)
   m.exp.va = matrix(nrow = n.prot, ncol = 3 * n.sites.p.ref)
   m.exp.dr.squarei = matrix(nrow = n.prot, ncol = n.sites.p.ref)
+  m.exp.dr.squarei.10.modes = matrix(nrow = n.prot, ncol = n.sites.p.ref)
+  m.exp.smooth.dr.squarei = matrix(nrow = n.prot, ncol = n.sites.p.ref)
   
   m.theo.Pn = matrix(nrow = n.prot * n.mut.p, ncol = 3 * n.sites.p.ref)
   m.theo.va = matrix(nrow = n.prot * n.mut.p, ncol = 3 * n.sites.p.ref)
   m.theo.dr.squarei = matrix(nrow = n.prot * n.mut.p, ncol = n.sites.p.ref)
+  m.theo.dr.squarei.10.modes = matrix(nrow = n.prot * n.mut.p, ncol = n.sites.p.ref)
+  m.theo.smooth.dr.squarei = matrix(nrow = n.prot * n.mut.p, ncol = n.sites.p.ref)
   
   # Start a loop to evaluate each protein of the family.
   for (P in (1:n.prot)) {
@@ -166,27 +170,22 @@ AnalyzeExperimentalTheoretical <- function(family,
     for (i in (1:n.sites.p.ref)) {
       m.exp.dr.squarei[P, i] = matrix(exp.dr.squarei[ aligned.p.ref.index == i], nrow = 1, ncol = 1)
     }
-
+  
+    # Calculate smooth dr.squarei 1
+    kij = CalculateENMK(exp.r.p.ref, CalculateKij, R0, TOLERANCE)$kij
+    m.exp.dr.squarei.0 = m.exp.dr.squarei[P, ]
+    m.exp.dr.squarei.0[is.na(m.exp.dr.squarei.0)] = TOLERANCE
+    m.exp.smooth.dr.squarei[P, ] = (m.exp.dr.squarei[P, ] +  kij %*%  m.exp.dr.squarei.0) / rowSums(kij)
+    
     for (mut in (1:n.mut.p)) {
     print(c(P, mut))
       
+      P.mut = n.mut.p * P - (n.mut.p - mut)
+      
       # Get theo.r.p.2.
[…]

### 2016-03-20 FUNCTIONS/CalculateENMK.R

@@ -45,6 +45,8 @@ CalculateENMK <- function(r, CalculateKij, R0, TOLERANCE) {
   nmodes <- length(va)
   # Calculate covariance matrix of K.
   cov <-  ve %*% ((1 / va) * t(ve))
-  output <- list("K" = K, "kij" = kij, "cov" = cov, "va" = va, "ve" = ve, "nmodes" = nmodes)
+  cov.10.modes <-  ve[, 1:10] %*% ((1 / va[1:10]) * t(ve[, 1:10]))
+  
+  output <- list("K" = K, "kij" = kij, "cov" = cov, "cov.10.modes" = cov.10.modes, "va" = va, "ve" = ve, "nmodes" = nmodes)
   output
 }

### 2016-04-09 AllFamilys.Rmd
cambios 09/04/2016

@@
 ---
-title: "AllFamilys"
-author: "mlm"
-date: "20 de marzo de 2016"
+title: "MSDi for all families together"
+author: "Maria Laura Marcos"
 output: html_document
@@
 
-# Create matrix.
-theo.MSDi.nsF = c()
-theo.MSDi.nsT = c()
-theo.MSDi.nsF.s = c()
-theo.MSDi.nsT.s = c()
+# Directories.
+out.dir <- "OUT"
+
+# Create matrixes.
+nsF.theo.MSDi = c()
+nsT.theo.MSDi = c()
+nsF.theo.MSDi.s = c()
+nsT.theo.MSDi.s = c()
 
@@
 exp.MSDi.s = c()
-
-# Dirs.
-out.dir <- "OUT"
 
@@
 
+# Print the input in the html file.
 print(input)
 
+# Start a loop to read data for each family.
 for (a in (1:nrow(input))) { 
   family <- as.character(input$family)[a]
-  p.ref <- as.character(input$p.ref)[a]
   mut.model = input$mut.model[a]
-  n.mut.p = input$n.mut.p[a]
   R0 = input$R0[a]
@@
 
-  # ns = F.
+  # natural selection (ns) = F.
   m.nsF.cF.theo.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.dr.squarei.csv", sep = "")))
   m.nsF.cF.theo.smooth.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.smooth.dr.squarei.csv", sep = "")))
+
   nsF.cF.theo.MSDi = colMeans(m.nsF.cF.theo.dr.squarei, na.rm = T)
-  nsF.cF.theo.smooth.MSDi = colMeans(m.nsF.cF.theo.smooth.dr.squarei, na.rm = T)
+  nsF.cF.theo.MSDi.s = colMeans(m.nsF.cF.theo.smooth.dr.squarei, na.rm = T)
 
-  # ns = T.
+  # natural selection (ns) = T.
   analysis.fname.id <- paste(family, "_mut.model_", mut.model, "_naturalSelection_", "TRUE", "_R0_", R0, "_core_", "FALSE", "_K.analysis_", K.analysis, sep = "")
@@
   m.nsT.cF.theo.smooth.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.smooth.dr.squarei.csv", sep = "")))
+
   nsT.cF.theo.MSDi = colMeans(m.nsT.cF.theo.dr.squarei, na.rm = T)
-  nsT.cF.theo.smooth.MSDi = colMeans(m.nsT.cF.theo.smooth.dr.squarei, na.rm = T)
+  nsT.cF.theo.MSDi.s = colMeans(m.nsT.cF.theo.smooth.dr.squarei, na.rm = T)
 
-  ## Fits.
+  ## Fit theoretical data with experimental data.
   fit.nsF.cF = lm(cF.exp.MSDi ~ nsF.cF.theo.MSDi)
-  MSDi.fit.nsF.cF = fitted.values(fit.nsF.cF)
+  fit.nsF.cF.MSDi = fitted.values(fit.nsF.cF)
 
   fit.nsT.cF = lm(cF.exp.MSDi ~ nsT.cF.theo.MSDi)
-  MSDi.fit.nsT.cF = fitted.values(fit.nsT.cF)
+  fit.nsT.cF.MSDi = fitted.values(fit.nsT.cF)
 
-  fit.nsF.cF.s = lm(cF.exp.MSDi.s ~ nsF.cF.theo.smooth.MSDi)
-  MSDi.fit.nsF.cF.s = fitted.values(fit.nsF.cF.s)
+  fit.nsF.cF.s = lm(cF.exp.MSDi.s ~ nsF.cF.theo.MSDi.s)
+  fit.nsF.cF.MSDi.s = fitted.values(fit.nsF.cF.s)
 
-  fit.nsT.cF.s = lm(cF.exp.MSDi.s ~ nsT.cF.theo.smooth.MSDi)
-  MSDi.fit.nsT.cF.s = fitted.values(fit.nsT.cF.s)
+  fit.nsT.cF.s = lm(cF.exp.MSDi.s ~ nsT.cF.theo.MSDi.s)
+  fit.nsT.cF.MSDi.s = fitted.values(fit.nsT.cF.s)
 
   # Concatenate information.
-  theo.MSDi.nsF = c(theo.MSDi.nsF, MSDi.fit.nsF.cF)
-  theo.MSDi.nsT = c(theo.MSDi.nsT, MSDi.fit.nsT.cF)
-  theo.MSDi.nsF.s = c(theo.MSDi.nsF.s, MSDi.fit.nsF.cF.s)
-  theo.MSDi.nsT.s = c(theo.MSDi.nsT.s, MSDi.fit.nsT.cF.s)
+  nsF.theo.MSDi = c(nsF.theo.MSDi, fit.nsF.cF.MSDi)
+  nsT.theo.MSDi = c(nsT.theo.MSDi, fit.nsT.cF.MSDi)
+  nsF.theo.MSDi.s = c(nsF.theo.MSDi.s, fit.nsF.cF.MSDi.s)
+  nsT.theo.MSDi.s = c(nsT.theo.MSDi.s, fit.nsT.cF.MSDi.s)
 
@@
   exp.MSDi.s = c(exp.MSDi.s, cF.exp.MSDi.s)
-
 }
@@
 # Caluclate measures.
-R2.nsF.cF = cor(theo.MSDi.nsF, exp.MSDi)^2 
-R2.nsT.cF = cor(theo.MSDi.nsT, exp.MSDi)^2
+R2.nsF.cF = cor(nsF.theo.MSDi, exp.MSDi) ^ 2 
+R2.nsT.cF = cor(nsT.theo.MSDi, exp.MSDi) ^ 2
 
-R2.nsF.cF.s = cor(theo.MSDi.nsF.s, exp.MSDi.s)^2
-R2.nsT.cF.s = cor(theo.MSDi.nsT.s, exp.MSDi.s)^2
+R2.nsF.cF.s = cor(nsF.theo.MSDi.s, exp.MSDi.s) ^ 2
+R2.nsT.cF.s = cor(nsT.theo.MSDi.s, exp.MSDi.s) ^ 2
 
-MSE.nsF.cF = mean((theo.MSDi.nsF - exp.MSDi) ^ 2)
-MSE.nsT.cF = mean((theo.MSDi.nsT - exp.MSDi) ^ 2)
+MSE.nsF.cF = mean((nsF.theo.MSDi - exp.MSDi) ^ 2)
+MSE.nsT.cF = mean((nsT.theo.MSDi - exp.MSDi) ^ 2)
 
-MSE.nsF.cF.s = mean((theo.MSDi.nsF.s - exp.MSDi.s) ^ 2)
-MSE.nsT.cF.s = mean((theo.MSDi.nsT.s - exp.MSDi.s) ^ 2)
+MSE.nsF.cF.s = mean((nsF.theo.MSDi.s - exp.MSDi.s) ^ 2)
+MSE.nsT.cF.s = mean((nsT.theo.MSDi.s - exp.MSDi.s) ^ 2)
 
@@
 
-plot(theo.MSDi.nsF, type="l", xlab = "sitio", ylab = "Theoretical")
-plot(exp.MSDi, type="l", col ="red", ylab = "Experimental")
-plot(theo.MSDi.nsF, type="l", ylab = "both")
-points(exp.MSDi, col = "red", type="l")
+plot(nsF.theo.MSDi, type = "l", xlab = "sitio", ylab = "Theoretical")
+plot(exp.MSDi, type = "l", col = "red", ylab = "Experimental")
+plot(nsF.theo.MSDi, type = "l", ylab = "both")
+points(exp.MSDi, col = "red", type = "l")
 legend("topleft", paste("R^2", round(R2.nsF.cF, digits = 2)), bty = "n", text.col = "red")
@@
 layout(matrix(1:3, 3, 1, byrow = F)) 
-plot(theo.MSDi.nsT, type="l", xlab = "sitio", ylab = "Theoretical")
+plot(nsT.theo.MSDi, type="l", xlab = "sitio", ylab = "Theoretical")
 plot(exp.MSDi, type="l", col ="red", ylab = "Experimental")
-plot(theo.MSDi.nsT, type="l", ylab = "both")
+plot(nsT.theo.MSDi, type="l", ylab = "both")
 points(exp.MSDi, col = "red", type="l")
@@
 ```
-All familys fitted smooth MSD profiles
+All families fitted smooth normalized MSD profiles
 
@@
 ```{r}
-layout(matrix(1:3, 3, 1, byrow = F)) 
-plot(theo.MSDi.nsF.s, type="l", xlab = "sitio", ylab = "Theoretical ns = F")
-plot(exp.MSDi.s, type="l", col ="red", ylab = "Experimental")
-plot(theo.MSDi.nsF.s, type="l", ylab = "both")
-points(exp.MSDi.s, col = "red", type="l")
-legend("topleft", paste("R^2", round(R2.nsF.cF.s, digits = 2), " ", "MSE", signif(MSE.nsF.cF.s, digits = 2)), bty = "n", text.col = "red")
+plot(nsF.theo.MSDi.s, type = "l", xlab = "sitio", ylab = "Theoretical ns = F", ylim = c(0, 0.14))
+```
 
+```{r}
+plot(exp.MSDi.s, type = "l", col = "red", ylab = "Experimental", ylim = c(0, 0.14))
+```
+
+```{r}
+plot(nsF.theo.MSDi.s, type = "l", ylab = "both", ylim = c(0, 0.14))
+points(exp.MSDi.s, col = "red", type = "l")
+legend("topleft", paste("R^2", round(R2.nsF.cF.s, digits = 2), " ", "MSE", signif(MSE.nsF.cF.s, digits = 4)), bty = "n", text.col = "red")
 ```
@@
 ```{r}
-layout(matrix(1:3, 3, 1, byrow = F)) 
-plot(theo.MSDi.nsT.s, type="l", xlab = "sitio", ylab = "Theoretical ns = T")
-plot(exp.MSDi.s, type="l", col ="red", ylab = "Experimental")
-plot(theo.MSDi.nsT.s, type="l", ylab = "both")
-points(exp.MSDi.s, col = "red", type="l")
+plot(nsT.theo.MSDi.s, type="l", xlab = "sitio", ylab = "Theoretical ns = T", ylim = c(0, 0.14))
+```
+
+```{r}
+plot(exp.MSDi.s, type = "l", col = "red", ylab = "Experimental", ylim = c(0, 0.14))
+```
+
+```{r}
+plot(nsT.theo.MSDi.s, type = "l", ylab = "both", ylim = c(0, 0.14))
+points(exp.MSDi.s, col = "red", type = "l")
 legend("topleft", paste("R^2", round(R2.nsT.cF.s, digits = 2), " ", "MSE", signif(MSE.nsT.cF.s, digits = 2)), bty = "n", text.col = "red")
-
 ```

### 2016-04-09 MultipleReport.Rmd
cambios 09/04/2016

@@
 
-m.cF.exp.Qn = t(apply(m.cF.exp.Pn, 1, cumsum))
-mean.cF.exp.Qn = colMeans(m.cF.exp.Qn)
-
-cF.exp.Qn.quantile1 = matrix(0, ncol = ncol(m.cF.exp.Qn), nrow = 1)
-cF.exp.Qn.quantile2 = matrix(0, ncol = ncol(m.cF.exp.Qn), nrow = 1)
-
-for (i in (1:ncol(m.cF.exp.Qn))){
-    cF.exp.Qn.quantiles = as.vector(quantile((m.cF.exp.Qn[, i]), probs = c(0.05, 0.95)))
-    cF.exp.Qn.quantile1[1, i] = cF.exp.Qn.quantiles[1]
-    cF.exp.Qn.quantile2[1, i] = cF.exp.Qn.quantiles[2]
-}
-
 family.data <- data.frame(pdbid, nsites = m.n.sites.p.2, naligned = m.n.aligned, identity, MSD = cF.exp.MSD)
@@
 
-m.nsF.cF.theo.Qn = t(apply(m.nsF.cF.theo.Pn, 1, cumsum))
-
 ### natural_selection = TRUE, core = FALSE ####
@@
 mean.nsT.cF.theo.MSD.group <- nsT.cF.theo.MSD.group$mean.group[,1]
-
-m.nsT.cF.theo.Qn = t(apply(m.nsT.cF.theo.Pn, 1, cumsum))
-```
-
-```{r, include = FALSE}
-
-### natural_selection = FALSE, core = TRUE ####
-
-analysis.fname.id <- paste(family, "_mut.model_", mut.model, "_naturalSelection_", "FALSE", "_R0_", R0, "_core_", "TRUE", "_K.analysis_", K.analysis, sep = "")
-
-m.cT.exp.va = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.exp.va.csv", sep = "")))[, 1:nmodes3]
-i.m.cT.exp.va = 1/m.cT.exp.va
-
-m.cT.exp.Pn = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.exp.Pn.csv", sep = "")))[, 1:nmodes3]
-mean.cT.exp.Pn = colMeans(m.cT.exp.Pn)
-
-cT.exp.Pn.quantile1 = matrix(0, ncol = ncol(m.cT.exp.Pn), nrow = 1)
-cT.exp.Pn.quantile2 = matrix(0, ncol = ncol(m.cT.exp.Pn), nrow = 1)
-
-for (i in (1:ncol(m.cT.exp.Pn))){
-    cT.exp.Pn.quantiles <- as.vector(quantile((m.cT.exp.Pn[, i]), probs = c(0.05, 0.95)))
-    cT.exp.Pn.quantile1[1, i] = cT.exp.Pn.quantiles[1]
-    cT.exp.Pn.quantile2[1, i] = cT.exp.Pn.quantiles[2]
-}
-
-m.cT.exp.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.exp.dr.squarei.csv", sep = "")))
-m.cT.exp.dr.smooth.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.exp.smooth.dr.squarei.csv", sep = "")))
-cT.exp.MSDi = colMeans(m.cT.exp.dr.squarei, na.rm = T )
-cT.exp.smooth.MSDi = colMeans(m.cT.exp.dr.smooth.squarei, na.rm = T )
-
-cT.exp.MSD = rowMeans(m.cT.exp.dr.squarei, na.rm = T)
-
-m.cT.exp.Qn = t(apply(m.cT.exp.Pn, 1, cumsum))
-mean.cT.exp.Qn = colMeans(m.cT.exp.Qn)
-
-cT.exp.Qn.quantile1 = matrix(0, ncol = ncol(m.cT.exp.Qn), nrow = 1)
-cT.exp.Qn.quantile2 = matrix(0, ncol = ncol(m.cT.exp.Qn), nrow = 1)
-
-for (i in (1:ncol(m.cT.exp.Qn))){
-    cT.exp.Qn.quantiles = as.vector(quantile((m.cT.exp.Qn[, i]), probs = c(0.05, 0.95)))
-    cT.exp.Qn.quantile1[1, i] = cT.exp.Qn.quantiles[1]
-    cT.exp.Qn.quantile2[1, i] = cT.exp.Qn.quantiles[2]
-}
-
-### Theoretical ###
-
-m.nsF.cT.theo.va = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.va.csv", sep = "")))[, 1:nmodes3]
-i.m.nsF.cT.theo.va = 1/m.nsF.cT.theo.va
-
-m.nsF.cT.theo.Pn = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.Pn.csv", sep = "")))[, 1:nmodes3]
-n.mut = nrow(m.nsF.cT.theo.Pn)
-
-m.nsF.cT.theo.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.dr.squarei.csv", sep = "")))
-m.nsF.cT.theo.smooth.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.smooth.dr.squarei.csv", sep = "")))
-nsF.cT.theo.MSDi = colMeans(m.nsF.cT.theo.dr.squarei, na.rm = T)
-nsF.cT.theo.smooth.MSDi = colMeans(m.nsF.cT.theo.smooth.dr.squarei, na.rm = T)
-
-nsF.cT.theo.MSD = rowMeans(m.nsF.cT.theo.dr.squarei, na.rm = T)
-nsF.cT.theo.MSD.group <- CalculateGroupsMeansQuantiles(cbind(nsF.cT.theo.MSD,nsF.cT.theo.MSD), n.exp, n.mut.p)
-mean.nsF.cT.theo.MSD.group <- nsF.cT.theo.MSD.group$mean.group[,1]
-
-m.nsF.cT.theo.Qn = t(apply(m.nsF.cT.theo.Pn, 1, cumsum))
-
-### natural_selection = TRUE, core = TRUE ####
-
-analysis.fname.id <- paste(family, "_mut.model_", mut.model, "_naturalSelection_", "TRUE", "_R0_", R0, "_core_", "TRUE", "_K.analysis_", K.analysis, sep = "")
-
-m.nsT.cT.theo.va = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.va.csv", sep = "")))[, 1:nmodes3]
-i.m.nsT.cT.theo.va = 1/m.nsT.cT.theo.va
-
-m.nsT.cT.theo.Pn = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.Pn.csv", sep = "")))[, 1:nmodes3]
-n.mut = nrow(m.nsT.cT.theo.Pn)
-
-m.nsT.cT.theo.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.dr.squarei.csv", sep = "")))
-m.nsT.cT.theo.smooth.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.dr.squarei.csv", sep = "")))
-nsT.cT.theo.MSDi = colMeans(m.nsT.cT.theo.dr.squarei, na.rm = T)
-nsT.cT.theo.smooth.MSDi = colMeans(m.nsT.cT.theo.smooth.dr.squarei, na.rm = T)
-
-nsT.cT.theo.MSD = rowMeans(m.nsT.cT.theo.dr.squarei, na.rm = T)
-
-nsT.cT.theo.MSD.group <- CalculateGroupsMeansQuantiles(cbind(nsT.cT.theo.MSD,nsT.cT.theo.MSD), n.exp, n.mut.p)
-mean.nsT.cT.theo.MSD.group <- nsT.cT.theo.MSD.group$mean.group[,1]
-
-m.nsT.cT.theo.Qn = t(apply(m.nsT.cT.theo.Pn, 1, cumsum))
 
@@
 ### MSDi
-```{r, include = F}
 
-layout(matrix(1:4, 2, 2, byrow = T)) 
-plot(rank(nsF.cF.theo.MSDi, na.last = "keep"), main = "MSDi ns = F", xlab = "site", ylab = "rank MSDi")
-points(rank(cF.exp.MSDi, na.last = "keep"), col = "red")
-
-plot(rank(nsT.cF.theo.MSDi, na.last = "keep"), main = "MSDi ns = T", xlab = "site", ylab = "rank MSDi")
-points(rank(cF.exp.MSDi, na.last = "keep"), col = "red")
-
-plot(rank(nsF.cF.theo.smooth.MSDi, na.last = "keep"), main = "MSDi.smooth ns = F", xlab = "site", ylab = "rank MSDi")
-points(rank(cF.exp.smooth.MSDi, na.last = "keep"), col = "red")
-
-plot(rank(nsT.cF.theo.smooth.MSDi, na.last = "keep"), main = "MSDi.smooth ns = T", xlab = "site", ylab = "rank MSDi")
-points(rank(cF.exp.smooth.MSDi, na.last = "keep"), col = "red")
-
-```
 Los perfiles teoricos de MSDi y smooth.MSDi fueron fiteados con los perfiles exterimentales. Se compararon y se calcularon R^2 y MSE. 
@@
 keep.data = c()
-
-layout(matrix(1:4, 2, 2, byrow = F))
-
-fit.nsF.cF = lm(cF.exp.MSDi ~ nsF.cF.theo.MSDi)
-MSDi.fit.nsF.cF = fitted.values(fit.nsF.cF)
-R2.nsF.cF = cor(cF.exp.MSDi[!is.na(cF.exp.MSDi)], MSDi.fit.nsF.cF) ^ 2 
-MSE.nsF.cF = mean((MSDi.fit.nsF.cF - cF.exp.MSDi[!is.na(cF.exp.MSDi)]) ^ 2)
-
-keep.data = c(keep.data, R2.nsF.cF, MSE.nsF.cF)
-
-plot(MSDi.fit.nsF.cF, main = "MSDi ns = F", xlab = "site", ylab = "MSDi", ylim = c(0, max(cbind(MSDi.fit.nsF.cF, cF.exp.MSDi[!is.na(cF.exp.MSDi)]))))
-points(cF.exp.MSDi[!is.na(cF.exp.MSDi)], col = "red")
-
-plot(MSDi.fit.nsF.cF, cF.exp.MSDi[!is.na(cF.exp.MSDi)], xlab = "MSDi teorico", ylab = "MSDi experimental", main = "ns = F c = F")
-abline(0, 1)
-legend("topleft", paste("R^2", round(R2.nsF.cF, digits = 2)), bty = "n", text.col = "red")
-legend("bottomright", paste("MSE", signif(MSE.nsF.cF, digits = T)), bty = "n", text.col = "red")
-
-fit.nsT.cF = lm(cF.exp.MSDi ~ nsT.cF.theo.MSDi)
-MSDi.fit.nsT.cF = fitted.values(fit.nsT.cF)
-R2.nsT.cF = cor(cF.exp.MSDi[!is.na(cF.exp.MSDi)], MSDi.fit.nsT.cF) ^ 2 
-MSE.nsT.cF = mean((MSDi.fit.nsT.cF - cF.exp.MSDi[!is.na(cF.exp.MSDi)]) ^ 2)
-
-keep.data = c(keep.data, R2.nsT.cF, MSE.nsT.cF)
-
-plot(MSDi.fit.nsT.cF, main = "MSDi ns = T", xlab = "site", ylab = "MSDi", ylim = c(0, max(cbind(MSDi.fit.nsT.cF, cF.exp.MSDi[!is.na(cF.exp.MSDi)]))))
-points(cF.exp.MSDi[!is.na(cF.exp.MSDi)], col = "red")
-
-plot(MSDi.fit.nsT.cF, cF.exp.MSDi[!is.na(cF.exp.MSDi)], xlab = "MSDi teorico", ylab = "MSDi experimental", main = "ns = T c = F")
-abline(0, 1)
-legend("topleft", paste("R^2", round(R2.nsT.cF, digits = 2)), bty = "n", text.col = "red")
-legend("bottomright", paste("MSE", signif(MSE.nsT.cF, digits = 2)), bty = "n", text.col = "red")
 ```
@@
 
+```{r}
+# Write pdb files for MSDi.
+pdbs.fname <- file.path(data.dir, paste(family, "_coordinates.pdb", sep = "")) 
+pdb = ReadCA(pdbs.fname, exp.chain.p.ref)
+xyz.calpha = pdb$xyz.calpha
+
+MSDi.fit.nsF.cF.pdb <- vec2resno(as.vector(MSDi.fit.nsF.cF), sort(rep(1:ncol(xyz.calpha),3)))
+write.pdb(xyz = c(xyz.calpha) ,b = MSDi.fit.nsF.cF.pdb*100, file = file.path(out.dir, paste(p.ref, ".theo.nsF.pdb", sep = "")))
+
+MSDi.fit.nsT.cF.pdb <- vec2resno(as.vector(MSDi.fit.nsT.cF), sort(rep(1:ncol(xyz.calpha),3)))
+write.pdb(xyz = c(xyz.calpha) ,b = MSDi.fit.nsT.cF.pdb*100, file = file.path(out.dir, paste(p.ref, ".theo.nsT.pdb", sep = "")))
+
+cF.exp.smooth.MSDi.pdb <- vec2resno(as.vector(cF.exp.smooth.MSDi[!is.na(cF.exp.smooth.MSDi)]),sort(rep(1:ncol(xyz.calpha),3)))
+write.pdb(xyz = c(xyz.calpha) ,b = cF.exp.smooth.MSDi.pdb*100, file = file.path(out.dir, paste(p.ref, ".exp.pdb", sep = "")))
+
+```
+
 ## Pn y Qn
@@
 m.nsT.cF.theo.Pn = m.nsT.cF.theo.Pn[as.vector(m.theo.index), ]
-m.nsF.cT.theo.Pn = m.nsF.cT.theo.Pn[as.vector(m.theo.index), ]
-m.nsT.cT.theo.Pn = m.nsT.cT.theo.Pn[as.vector(m.theo.index), ]
 
@@
 nsT.cF.theo.Pn.group.quantile2 = nsT.cF.theo.Pn.group$mean.quantile2.group
-```
-
-```{r, inlude = FALSE}
-
-nsF.cT.theo.Pn.group = CalculateGroupsMeansQuantiles(m.nsF.cT.theo.Pn, n.mut.p, n.exp)
-mean.nsF.cT.theo.Pn.group = nsF.cT.theo.Pn.group$mean.mean.group
-nsF.cT.theo.Pn.group.quantile1 = nsF.cT.theo.Pn.group$mean.quantile1.group
-nsF.cT.theo.Pn.group.quantile2 = nsF.cT.theo.Pn.group$mean.quantile2.group
-
-nsT.cT.theo.Pn.group = CalculateGroupsMeansQuantiles(m.nsT.cT.theo.Pn, n.mut.p, n.exp)
-mean.nsT.cT.theo.Pn.group = nsT.cT.theo.Pn.group$mean.mean.group
-nsT.cT.theo.Pn.group.quantile1 = nsT.cT.theo.Pn.group$mean.quantile1.group
-nsT.cT.theo.Pn.group.quantile2 = nsT.cT.theo.Pn.group$mean.quantile2.group
-```
-
-```{r, inlude = FALSE}
-
-nsF.cF.theo.Qn.group = CalculateGroupsMeansQuantiles(m.nsF.cF.theo.Qn, n.mut.p, n.exp)
-mean.nsF.cF.theo.Qn.group = nsF.cF.theo.Qn.group$mean.mean.group
-nsF.cF.theo.Qn.group.quantile1 = nsF.cF.theo.Qn.group$mean.quantile1.group
-nsF.cF.theo.Qn.group.quantile2 = nsF.cF.theo.Qn.group$mean.quantile2.group
-
-nsT.cF.theo.Qn.group = CalculateGroupsMeansQuantiles(m.nsT.cF.theo.Qn, n.mut.p, n.exp)
-mean.nsT.cF.theo.Qn.group = nsT.cF.theo.Qn.group$mean.mean.group
-nsT.cF.theo.Qn.group.quantile1 = nsT.cF.theo.Qn.group$mean.quantile1.group
-nsT.cF.theo.Qn.group.quantile2 = nsT.cF.theo.Qn.group$mean.quantile2.group
-
-nsF.cT.theo.Qn.group = CalculateGroupsMeansQuantiles(m.nsF.cT.theo.Qn, n.mut.p, n.exp)
-mean.nsF.cT.theo.Qn.group = nsF.cT.theo.Qn.group$mean.mean.group
-nsF.cT.theo.Qn.group.quantile1 = nsF.cT.theo.Qn.group$mean.quantile1.group
-nsF.cT.theo.Qn.group.quantile2 = nsF.cT.theo.Qn.group$mean.quantile2.group
-
-nsT.cT.theo.Qn.group = CalculateGroupsMeansQuantiles(m.nsT.cT.theo.Qn, n.mut.p, n.exp)
-mean.nsT.cT.theo.Qn.group = nsT.cT.theo.Qn.group$mean.mean.group
-nsT.cT.theo.Qn.group.quantile1 = nsT.cT.theo.Qn.group$mean.quantile1.group
-nsT.cT.theo.Qn.group.quantile2 = nsT.cT.theo.Qn.group$mean.quantile2.group
 ```
@@
 
-write.csv(keep.data, file = "cor_MSE.csv", appen = TRUE)
 ```
@@
 
-nsF.cT.rho.t.1 <- matrix(0, nrow = n.mut, ncol = 1)
-nsF.cT.rho.t.3 <- matrix(0, nrow = n.mut, ncol = 1)
-for (i in (1:n.mut)) {
-  nsF.cT.rho.t.1[i, ] <- cor(as.numeric(m.nsF.cT.theo.Pn[i, 1:nmodes1] * m.nsF.cT.theo.va[i, 1:nmodes1]), as.numeric(i.m.nsF.cT.theo.va[i, 1:nmodes1]), method = "pearson")	
-  nsF.cT.rho.t.3[i, ] <- cor(as.numeric(m.nsF.cT.theo.Pn[i, 1:nmodes3] * m.nsF.cT.theo.va[i, 1:nmodes3]), as.numeric(i.m.nsF.cT.theo.va[i, 1:nmodes3]), method = "pearson")	
-}
-
-nsT.cT.rho.t.1 <- matrix(0, nrow = n.mut, ncol = 1)
-nsT.cT.rho.t.3 <- matrix(0, nrow = n.mut, ncol = 1)
-for (i in (1:n.mut)) {
-  nsT.cT.rho.t.1[i, ] <- cor(as.numeric(m.nsT.cT.theo.Pn[i, 1:nmodes1] * m.nsT.cT.theo.va[i, 1:nmodes1]), as.numeric(i.m.nsT.cT.theo.va[i, 1:nmodes1]), method = "pearson")	
-  nsT.cT.rho.t.3[i, ] <- cor(as.numeric(m.nsT.cT.theo.Pn[i, 1:nmodes3] * m.nsT.cT.theo.va[i, 1:nmodes3]), as.numeric(i.m.nsT.cT.theo.va[i, 1:nmodes3]), method = "pearson")	
-}
-
 cF.rho.e.1 <- matrix(0, nrow = n.exp, ncol = 1)
@@
 
-cT.rho.e.1 <- matrix(0, nrow = n.exp, ncol = 1)
-cT.rho.e.3 <- matrix(0, nrow = n.exp, ncol = 1) 
-for (i in (1:n.exp)) {
-  cT.rho.e.1[i, ] <- cor(as.numeric(m.cT.exp.Pn[i, 1:nmodes1] * m.cT.exp.va[i, 1:nmodes1]), as.numeric(i.m.cT.exp.va[i, 1:nmodes1]), method = "pearson")
-  cT.rho.e.3[i, ] <- cor(as.numeric(m.cT.exp.Pn[i, 1:nmodes3] * m.cT.exp.va[i, 1:nmodes3]), as.numeric(i.m.cT.exp.va[i, 1:nmodes3]), method = "pearson")
-}
-```
-
-```{r, include = FALSE}
-
-# Calculate auc.
-nsF.cF.auc.t.1 <- matrix(0, nrow = n.mut, ncol = 1)
-nsF.cF.auc.t.3 <- matrix(0, nrow = n.mut, ncol = 1)
-for (i in (1:n.mut)) {
-  nsF.cF.auc.t.1[i, ] <- auc(seq(1:nmodes1), m.nsF.cF.theo.Qn[i,1:nmodes1])
-  nsF.cF.auc.t.3[i, ] <- auc(seq(1:nmodes3), m.nsF.cF.theo.Qn[i,1:nmodes3])
-}
-nsT.cF.auc.t.1 <- matrix(0, nrow = n.mut, ncol = 1)
-nsT.cF.auc.t.3 <- matrix(0, nrow = n.mut, ncol = 1)
-for (i in (1:n.mut)) {
-  nsT.cF.auc.t.1[i, ] <- auc(seq(1:nmodes1), m.nsT.cF.theo.Qn[i,1:nmodes1])
-  nsT.cF.auc.t.3[i, ] <- auc(seq(1:nmodes3), m.nsT.cF.theo.Qn[i,1:nmodes3])
-}
-
-cF.auc.e.1 <- matrix(0, nrow = n.exp, ncol = 1)
-cF.auc.e.3 <- matrix(0, nrow = n.exp, ncol = 1)
-for (i in (1:n.exp)) {
-  cF.auc.e.1[i, ] <- auc(seq(1:nmodes1), m.cF.exp.Qn[i, 1:nmodes1])
-  cF.auc.e.3[i, ] <- auc(seq(1:nmodes3), m.cF.exp.Qn[i, 1:nmodes3])
-}
-
-nsF.cT.auc.t.1 <- matrix(0, nrow = n.mut, ncol = 1)
-nsF.cT.auc.t.3 <- matrix(0, nrow = n.mut, ncol = 1)
-for (i in (1:n.mut)) {
-  nsF.cT.auc.t.1[i, ] <- auc(seq(1:nmodes1), m.nsF.cT.theo.Qn[i,1:nmodes1])
-  nsF.cT.auc.t.3[i, ] <- auc(seq(1:nmodes3), m.nsF.cT.theo.Qn[i,1:nmodes3])
-}
-nsT.cT.auc.t.1 <- matrix(0, nrow = n.mut, ncol = 1)
-nsT.cT.auc.t.3 <- matrix(0, nrow = n.mut, ncol = 1)
-for (i in (1:n.mut)) {
-  nsT.cT.auc.t.1[i, ] <- auc(seq(1:nmodes1), m.nsT.cT.theo.Qn[i,1:nmodes1])
-  nsT.cT.auc.t.3[i, ] <- auc(seq(1:nmodes3), m.nsT.cT.theo.Qn[i,1:nmodes3])
-}
-
-cT.auc.e.1 <- matrix(0, nrow = n.exp, ncol = 1)
-cT.auc.e.3 <- matrix(0, nrow = n.exp, ncol = 1)
-for (i in (1:n.exp)) {
-  cT.auc.e.1[i, ] <- auc(seq(1:nmodes1), m.cT.exp.Qn[i, 1:nmodes1])
-  cT.auc.e.3[i, ] <- auc(seq(1:nmodes3), m.cT.exp.Qn[i, 1:nmodes3])
-}
 ```
@@
 
-```{r, include = FALSE}
-plot(density(nsF.cT.rho.t.1), ylab = "Frecuencia", xlab = "rho", main = "Histograma rho 10 modos ns = F, c = T")
-points(x = c(cT.rho.e.1), y = rep(0, n.exp), col = "red")
-plot(density(nsT.cT.rho.t.1), ylab = "Frecuencia", xlab = "rho", main = "Histograma rho 10 modos ns = T, c = T")
-points(x = c(cT.rho.e.1), y = rep(0, n.exp), col = "red")
-
-```
-
 ```{r}
@@
 ```
-
-```{r, include = FALSE}
-plot(density(nsF.cT.rho.t.3), ylab = "Frecuencia", xlab = "rho", main = "Histograma rho 50 modos ns = F, c = T")
-points(x = c(cT.rho.e.3), y = rep(0, n.exp), col = "red")
-plot(density(nsT.cT.rho.t.3), ylab = "Frecuencia", xlab = "rho", main = "Histograma rho 50 modos ns = T, c = T")
-points(x = c(cT.rho.e.3), y = rep(0, n.exp), col = "red")
-
-```
-
-```{r, include = FALSE}
-layout(matrix(1:4, 2, 2, byrow = T))
-plot(density(nsF.cF.auc.t.1), ylab = "Frecuencia", xlab = "auc", main = "Histograma auc 10 modos ns = F, c = F")
-points(x = c(cF.auc.e.1), y = rep(0, n.exp), col = "red")
-plot(density(nsT.cF.auc.t.1), ylab = "Frecuencia", xlab = "auc", main = "Histograma auc 10 modos ns = T, c = F")
-points(x = c(cF.auc.e.1), y = rep(0, n.exp), col = "red")
-plot(density(nsF.cT.auc.t.1), ylab = "Frecuencia", xlab = "auc", main = "Histograma auc 10 modos ns = F, c = T")
-points(x = c(cT.auc.e.1), y = rep(0, n.exp), col = "red")
-plot(density(nsT.cT.auc.t.1), ylab = "Frecuencia", xlab = "auc", main = "Histograma auc 10 modos ns = T, c = T")
-points(x = c(cT.auc.e.1), y = rep(0, n.exp), col = "red")
-
-```
-
-```{r, include = FALSE}
-layout(matrix(1:4, 2, 2, byrow = T))
-plot(density(nsF.cF.auc.t.3), ylab = "Frecuencia", xlab = "auc", main = "Histograma auc 50 modos ns = F, c = F")
-points(x = c(cF.auc.e.3), y = rep(0, n.exp), col = "red")
-plot(density(nsT.cF.auc.t.3), ylab = "Frecuencia", xlab = "auc", main = "Histograma auc 50 modos ns = T, c = F")
-points(x = c(cF.auc.e.3), y = rep(0, n.exp), col = "red")
-plot(density(nsF.cT.auc.t.3), ylab = "Frecuencia", xlab = "auc", main = "Histograma auc 50 modos ns = F, c = T")
-points(x = c(cT.auc.e.3), y = rep(0, n.exp), col = "red")
-plot(density(nsT.cT.auc.t.3), ylab = "Frecuencia", xlab = "auc", main = "Histograma auc 50 modos ns = T, c = T")
-points(x = c(cT.auc.e.3), y = rep(0, n.exp), col = "red")
-
-```
-
-```{r, include = FALSE}
-
-plot(mean.nsF.cT.theo.Pn.group, 
-     main = "Pn promedio ns = F, C = T", 
-     xlab = "nmodo",
-     ylab = "Pn",
-     ylim = c(0, max(c(nsF.cT.theo.Pn.group.quantile2, mean.cT.exp.Pn))))
-lines(nsF.cT.theo.Pn.group.quantile1)
-lines(nsF.cT.theo.Pn.group.quantile2)
-points(mean.cT.exp.Pn, col = "red")
-lines(as.vector(cT.exp.Pn.quantile1), col = "red")
-lines(as.vector(cT.exp.Pn.quantile2), col = "red")
-
-plot(mean.nsT.cT.theo.Pn.group, 
-     main = "Pn promedio ns = T, C = T", 
-     xlab = "nmodo",
-     ylab = "Pn",
-     ylim = c(0, max(c(nsT.cT.theo.Pn.group.quantile2, mean.cT.exp.Pn))))
-lines(nsT.cT.theo.Pn.group.quantile1)
-lines(nsT.cT.theo.Pn.group.quantile2)
-points(mean.cT.exp.Pn, col = "red")
-lines(as.vector(cT.exp.Pn.quantile1), col = "red")
-lines(as.vector(cT.exp.Pn.quantile2), col = "red")
-```
-
-```{r, include = FALSE}
-
-layout(matrix(1:4, 2, 2, byrow = T))
-
-plot(mean.nsF.cF.theo.Qn.group, 
-     main = "Qn promedio ns = F, C = F", 
-     xlab = "nmodo", 
-     ylab = "Qn",
-     ylim = c(0, max(c(nsF.cF.theo.Qn.group.quantile2, mean.cF.exp.Qn))))
-lines(nsF.cF.theo.Qn.group.quantile1)
-lines(nsF.cF.theo.Qn.group.quantile2)
-points(mean.cF.exp.Qn, col = "red")
-lines(as.vector(cF.exp.Qn.quantile1), col = "red")
-lines(as.vector(cF.exp.Qn.quantile2), col = "red")
-
-plot(mean.nsT.cF.theo.Qn.group, 
-     main = "Qn promedio ns = T, C = F", 
-     xlab = "nmodo",     
-     ylab = "Qn",
-     ylim = c(0, max(c(nsT.cF.theo.Qn.group.quantile2, mean.cF.exp.Qn))))
-lines(nsT.cF.theo.Qn.group.quantile1)
-lines(nsT.cF.theo.Qn.group.quantile2)
-points(mean.cF.exp.Qn, col = "red")
-lines(as.vector(cF.exp.Qn.quantile1), col = "red")
-lines(as.vector(cF.exp.Qn.quantile2), col = "red")
-
-plot(mean.nsF.cT.theo.Qn.group, 
-     main = "Qn promedio ns = F, C = T", 
-     xlab = "nmodo",      
-     ylab = "Qn",
-     ylim = c(0, max(c(nsF.cT.theo.Qn.group.quantile2, mean.cT.exp.Qn))))
-lines(nsF.cT.theo.Qn.group.quantile1)
-lines(nsF.cT.theo.Qn.group.quantile2)
-points(mean.cT.exp.Qn, col = "red")
-lines(as.vector(cT.exp.Qn.quantile1), col = "red")
-lines(as.vector(cT.exp.Qn.quantile2), col = "red")
-
-plot(mean.nsT.cT.theo.Qn.group, 
-     main = "Qn promedio ns = T, C = T", 
-     xlab = "nmodo",     
-     ylab = "Qn",
-     ylim = c(0, max(c(nsT.cT.theo.Qn.group.quantile2, mean.cT.exp.Qn))))
-lines(nsT.cT.theo.Qn.group.quantile1)
-lines(nsT.cT.theo.Qn.group.quantile2)
-points(mean.cT.exp.Qn, col = "red")
-lines(as.vector(cT.exp.Qn.quantile1), col = "red")
-lines(as.vector(cT.exp.Qn.quantile2), col = "red")
-```
-
-```{r, include = FALSE}
-fit.nsF.cT = lm(mean.cT.exp.Pn ~ mean.nsF.cT.theo.Pn.group)
-Pn.fit.nsF.cT = fitted.values(fit.nsF.cT)
-R2.nsF.cT = cor(mean.cT.exp.Pn, Pn.fit.nsF.cT) ^ 2 
-MSE.nsF.cT = mean((Pn.fit.nsF.cT - mean.cT.exp.Pn) ^ 2)
-plot(Pn.fit.nsF.cT, mean.cT.exp.Pn, xlab = "Pn teorico", ylab = "Pn experimental", main = "ns = F c = T")
-abline(0, 1)
-legend("topleft", paste("R^2", round(R2.nsF.cT, digits = 2)), bty = "n", text.col = "red") 
-legend("bottomright", paste("MSE", signif(MSE.nsF.cT, digits = 2)), bty = "n", text.col = "red")
-
-fit.nsT.cT = lm(mean.cT.exp.Pn ~ mean.nsT.cT.theo.Pn.group)
-Pn.fit.nsT.cT = fitted.values(fit.nsT.cT)
-R2.nsT.cT = cor(mean.cT.exp.Pn, Pn.fit.nsT.cT) ^ 2 
-MSE.nsT.cT = mean((Pn.fit.nsT.cT - mean.cT.exp.Pn) ^ 2)
-plot(Pn.fit.nsT.cT, mean.cT.exp.Pn, xlab = "Pn teorico", ylab = "Pn experimental", main = "ns = T c = T")
-abline(0, 1)
-legend("topleft", paste("R^2", round(R2.nsT.cT, digits = 2)), bty = "n", text.col = "red")
-legend("bottomright", paste("MSE", signif(MSE.nsT.cT, digits = 2)), bty = "n", text.col = "red")
-
-```
-
-```{r, include = F}
-layout(matrix(1:4, 2, 2, byrow = T))
-
-fit.nsF.cF = lm(cF.exp.MSDi ~ nsF.cF.theo.MSDi)
-MSDi.fit.nsF.cF = fitted.values(fit.nsF.cF)
-R2.nsF.cF = cor(rank(cF.exp.MSDi[!is.na(cF.exp.MSDi)]), rank(MSDi.fit.nsF.cF)) ^ 2 
-MSE.nsF.cF = mean((rank(MSDi.fit.nsF.cF - cF.exp.MSDi[!is.na(cF.exp.MSDi)])) ^ 2)
-plot(rank(MSDi.fit.nsF.cF), rank(cF.exp.MSDi[!is.na(cF.exp.MSDi)]), xlab = "MSDi teorico", ylab = "MSDi experimental", main = "ns = F c = F")
-abline(0, 1)
-legend("topleft", paste("R^2", round(R2.nsF.cF, digits = 2)), bty = "n", text.col = "red")
-legend("bottomright", paste("MSE", signif(MSE.nsF.cF, digits = T)), bty = "n", text.col = "red")
-
-fit.nsT.cF = lm(cF.exp.MSDi ~ nsT.cF.theo.MSDi)
-MSDi.fit.nsT.cF = fitted.values(fit.nsT.cF)
-R2.nsT.cF = cor(rank(cF.exp.MSDi[!is.na(cF.exp.MSDi)]), rank(MSDi.fit.nsT.cF)) ^ 2 
-MSE.nsT.cF = mean((rank(MSDi.fit.nsT.cF) - rank(cF.exp.MSDi[!is.na(cF.exp.MSDi)])) ^ 2)
-plot(rank(MSDi.fit.nsT.cF), rank(cF.exp.MSDi[!is.na(cF.exp.MSDi)]), xlab = "MSDi teorico", ylab = "MSDi experimental", main = "ns = T c = F")
-abline(0, 1)
-legend("topleft", paste("R^2", round(R2.nsT.cF, digits = 2)), bty = "n", text.col = "red")
-legend("bottomright", paste("MSE", signif(MSE.nsT.cF, digits = 2)), bty = "n", text.col = "red")
-```
-
-```{r, include = FALSE, include = FALSE}
-layout(matrix(1:4, 2, 2, byrow = T))
-
-fit.nsF.cF = lm(cF.exp.smooth.MSDi ~ nsF.cF.theo.smooth.MSDi)
-MSDi.fit.nsF.cF = fitted.values(fit.nsF.cF)
-R2.nsF.cF = cor(rank(cF.exp.smooth.MSDi[!is.na(cF.exp.smooth.MSDi)]), rank(MSDi.fit.nsF.cF)) ^ 2 
-MSE.nsF.cF = mean((rank(MSDi.fit.nsF.cF) - rank(cF.exp.smooth.MSDi[!is.na(cF.exp.smooth.MSDi)])) ^ 2)
-plot(rank(MSDi.fit.nsF.cF), rank(cF.exp.smooth.MSDi[!is.na(cF.exp.smooth.MSDi)]), xlab = "MSDi.smooth teorico", ylab = "MSDi.smooth experimental", main = "ns = F c = F")
-abline(0, 1) 
-legend("topleft", paste("R^2", round(R2.nsF.cF, digits = 2)), bty = "n", text.col = "red")
-legend("bottomright", paste("MSE", signif(MSE.nsF.cF, digits = T)), bty = "n", text.col = "red")
-
-fit.nsT.cF = lm(cF.exp.smooth.MSDi ~ nsT.cF.theo.smooth.MSDi)
-MSDi.fit.nsT.cF = fitted.values(fit.nsT.cF)
-R2.nsT.cF = cor(rank(cF.exp.smooth.MSDi[!is.na(cF.exp.smooth.MSDi)]), rank(MSDi.fit.nsT.cF)) ^ 2 
-MSE.nsT.cF = mean((rank(MSDi.fit.nsT.cF) - rank(cF.exp.smooth.MSDi[!is.na(cF.exp.smooth.MSDi)])) ^ 2)
-plot(rank(MSDi.fit.nsT.cF), rank(cF.exp.smooth.MSDi[!is.na(cF.exp.smooth.MSDi)]), xlab = "MSDi.smooth teorico", ylab = "MSDi.smooth experimental", main = "ns = T c = F")
-abline(0, 1)
-legend("topleft", paste("R^2", round(R2.nsT.cF, digits = 2)), bty = "n", text.col = "red")
-legend("bottomright", paste("MSE", signif(MSE.nsT.cF, digits = 2)), bty = "n", text.col = "red")
-
-```
-
-```{r, include = FALSE}
-
-fit.nsF.cT = lm(cT.exp.MSDi ~ nsF.cT.theo.MSDi)
-MSDi.fit.nsF.cT = fitted.values(fit.nsF.cT)
-R2.nsF.cT = cor(cT.exp.MSDi[!is.na(cT.exp.MSDi)], MSDi.fit.nsF.cT) ^ 2 
-MSE.nsF.cT = mean((MSDi.fit.nsF.cT - cT.exp.MSDi[!is.na(cT.exp.MSDi)]) ^ 2)
-plot(MSDi.fit.nsF.cT, cT.exp.MSDi[!is.na(cT.exp.MSDi)], xlab = "MSDi teorico", ylab = "MSDi experimental", main = "ns = F c = T")
-abline(0, 1)
-legend("topleft", paste("R^2", round(R2.nsF.cT, digits = 2)), bty = "n", text.col = "red")
-legend("bottomright", paste("MSE", signif(MSE.nsF.cT, digits = 2)), bty = "n", text.col = "red")
-
-fit.nsT.cT = lm(cT.exp.MSDi ~ nsT.cT.theo.MSDi)
-MSDi.fit.nsT.cT = fitted.values(fit.nsT.cT)
-R2.nsT.cT = cor(cT.exp.MSDi[!is.na(cT.exp.MSDi)], MSDi.fit.nsT.cT) ^ 2 
-MSE.nsT.cT = mean((MSDi.fit.nsT.cT - cT.exp.MSDi[!is.na(cT.exp.MSDi)]) ^ 2)
-plot(MSDi.fit.nsT.cT, cT.exp.MSDi[!is.na(cT.exp.MSDi)], xlab = "MSDi teorico", ylab = "MSDi experimental", main = "ns = T c = T")
-abline(0, 1)
-legend("topleft", paste("R^2", round(R2.nsT.cT, digits = 2)), bty = "n", text.col = "red")
-legend("bottomright", paste("MSE", signif(MSE.nsT.cT, digits = 2)), bty = "n", text.col = "red")
-```
-
-```{r, include = FALSE}
-fit.nsF.cT = lm(cT.exp.smooth.MSDi ~ nsF.cT.theo.smooth.MSDi)
-MSDi.fit.nsF.cT = fitted.values(fit.nsF.cT)
-R2.nsF.cT = cor(cT.exp.smooth.MSDi[!is.na(cT.exp.smooth.MSDi)], MSDi.fit.nsF.cT) ^ 2 
-MSE.nsF.cT = mean((MSDi.fit.nsF.cT - cT.exp.smooth.MSDi[!is.na(cT.exp.smooth.MSDi)]) ^ 2)
-plot(MSDi.fit.nsF.cT, cT.exp.smooth.MSDi[!is.na(cT.exp.smooth.MSDi)], xlab = "MSDi.smooth teorico", ylab = "MSDi.smooth experimental", main = "ns = F c = T")
-abline(0, 1)
-legend("topleft", paste("R^2", round(R2.nsF.cT, digits = 2)), bty = "n", text.col = "red")
-legend("bottomright", paste("MSE", signif(MSE.nsF.cT, digits = 2)), bty = "n", text.col = "red")
-
-fit.nsT.cT = lm(cT.exp.smooth.MSDi ~ nsT.cT.theo.smooth.MSDi)
-MSDi.fit.nsT.cT = fitted.values(fit.nsT.cT)
-R2.nsT.cT = cor(cT.exp.smooth.MSDi[!is.na(cT.exp.smooth.MSDi)], MSDi.fit.nsT.cT) ^ 2 
-MSE.nsT.cT = mean((MSDi.fit.nsT.cT - cT.exp.smooth.MSDi[!is.na(cT.exp.smooth.MSDi)]) ^ 2)
-plot(MSDi.fit.nsT.cT, cT.exp.smooth.MSDi[!is.na(cT.exp.smooth.MSDi)], xlab = "MSDi.smooth teorico", ylab = "MSDi.smooth experimental", main = "ns = T c = T")
-abline(0, 1)
-legend("topleft", paste("R^2", round(R2.nsT.cT, digits = 2)), bty = "n", text.col = "red")
-legend("bottomright", paste("MSE", signif(MSE.nsT.cT, digits = 2)), bty = "n", text.col = "red")
-```

### 2016-04-09 FUNCTIONS/AnalyzeExperimentalTheoretical.R

@@ -103,13 +103,11 @@ AnalyzeExperimentalTheoretical <- function(family,
   m.exp.Pn = matrix(nrow = n.prot, ncol = 3 * n.sites.p.ref)
   m.exp.va = matrix(nrow = n.prot, ncol = 3 * n.sites.p.ref)
   m.exp.dr.squarei = matrix(nrow = n.prot, ncol = n.sites.p.ref)
-  m.exp.dr.squarei.10.modes = matrix(nrow = n.prot, ncol = n.sites.p.ref)
   m.exp.smooth.dr.squarei = matrix(nrow = n.prot, ncol = n.sites.p.ref)
   
   m.theo.Pn = matrix(nrow = n.prot * n.mut.p, ncol = 3 * n.sites.p.ref)
   m.theo.va = matrix(nrow = n.prot * n.mut.p, ncol = 3 * n.sites.p.ref)
   m.theo.dr.squarei = matrix(nrow = n.prot * n.mut.p, ncol = n.sites.p.ref)
-  m.theo.dr.squarei.10.modes = matrix(nrow = n.prot * n.mut.p, ncol = n.sites.p.ref)
   m.theo.smooth.dr.squarei = matrix(nrow = n.prot * n.mut.p, ncol = n.sites.p.ref)
   
   # Start a loop to evaluate each protein of the family.
@@ -170,13 +168,13 @@ AnalyzeExperimentalTheoretical <- function(family,
     for (i in (1:n.sites.p.ref)) {
       m.exp.dr.squarei[P, i] = matrix(exp.dr.squarei[ aligned.p.ref.index == i], nrow = 1, ncol = 1)
     }
-  
-    # Calculate smooth dr.squarei 1
+    
+    # Calculate smooth dr.squarei.
     kij = CalculateENMK(exp.r.p.ref, CalculateKij, R0, TOLERANCE)$kij
     m.exp.dr.squarei.0 = m.exp.dr.squarei[P, ]
     m.exp.dr.squarei.0[is.na(m.exp.dr.squarei.0)] = TOLERANCE
-    m.exp.smooth.dr.squarei[P, ] = (m.exp.dr.squarei[P, ] +  kij %*%  m.exp.dr.squarei.0) / rowSums(kij)
-    
+    m.exp.smooth.dr.squarei[P, ] = (m.exp.dr.squarei[P, ] +  (kij %*%  m.exp.dr.squarei.0)) / rowSums(kij[, !is.na(m.exp.dr.squarei[P, ])])
[…]

### 2016-04-09 FUNCTIONS/GenerateMutants.R

@@ -64,20 +64,20 @@ GenerateMutants <- function(family,
   # Calculate K of p.ref.
   ENMK.p.ref = CalculateENMK(r.p.ref, CalculateKij, R0, TOLERANCE)
   
-  # Get mutated and not aligned sites of p.ref in the multiple alignment, the % sequence identity between p.ref
-  # and the other proteins, and the number of proteins.
-  m.aligned.mut.p.ref.index = read.csv(m.aligned.mut.p.ref.index.fname)
-  m.not.aligned.p.ref.index = read.csv(m.not.aligned.p.ref.index.fname)
+  # Get mutated and not aligned sites of p.ref in the multiple alignment
+  #m.aligned.mut.p.ref.index = read.csv(m.aligned.mut.p.ref.index.fname)
+  #m.not.aligned.p.ref.index = read.csv(m.not.aligned.p.ref.index.fname)
+  
+  # Get the % sequence identity between p.ref and the other proteins, and the number of proteins.
   m.identity = read.csv(m.identity.fname)$V1
-  n.prot = nrow(m.aligned.mut.p.ref.index)
+  n.prot = length(m.identity)
   
   # Calculate mutants using "LF-ENM".
   if (mut.model == "LFENM") {
     
     # Create a matrix to save coordinates of each generated mutant.
     m.r.mut = matrix(nrow = 3 * n.sites, ncol = n.prot * n.mut.p)
-    m.r.mut.10.modes = matrix(nrow = 3 * n.sites, ncol = n.prot * n.mut.p)
-    
+
     # Start a loop to read mutated sites of p.ref for each P.
     for (P in (1:n.prot)) {
       
@@ -91,7 +91,7 @@ GenerateMutants <- function(family,
       #    
       #      mutated.index = c(aligned.mut.p.ref.index, not.aligned.p.ref.index)
       #    }
-      #   
+         
       # Decide which sites to mutate (natural.selection == TRUE).
       if (natural.selection == "TRUE") {
       
@@ -109,8 +109,8 @@ GenerateMutants <- function(family,
         beta = (1 - prob.mut) / mean.CN
         prob.i = 1 - (beta * CN.i)
       
-        increasing.prob = order(prob.i, decreasing = T)
-        mutated.index = increasing.prob[1:n.sites.mut]
+        decreasing.prob = order(prob.i, decreasing = T)
[…]

### 2016-04-10 INFORMATION/paper.tex
cambios 10/04/2016

\documentclass{article}
\usepackage{lmodern}
\usepackage[T1]{fontenc}

\title{Structural Variability}
\author{Maria Laura Marcos}

\begin{document}

\maketitle

\section{Abstract}
Proteins diverge during biological evolution, which is evident in the variation of the aminoacid sequences and the resulting structural, dynamical and functional changes. At the level of aminoacid sequences, there is a clear evidence of natural selection: different sites evolve at different speeds. These patterns are well reproduced by the recently proposed mechanistic model (``Stress Model''), in which a mutation is accepted at a rate proportional to the probability that the mutant adopts the ``active structure''. At the level of structure, empirical studies show that the structure diverges much more slowly than the sequence, that the structural divergence occurs mainly along the lower energy vibrational modes and that there are structurally conserved cores in families of proteins. Applying a purely mutational model as the ``Linearly Forced - Elastic Network Model'' (LF - ENM) it has been shown that these structural divergence patterns can be well reproduced without resorting to natural selection. However, it is expected that the natural selection restricts, although very slightly, structural divergence. To study this, we deeply analyzed 8 structurally representative families of proteins. We obtained their multiple structural alignment and the structure of each protein of the family. Then, for each family, we used the LF - ENM to generate structures of multiple mutants of the reference ``wilt type'' protein. We did as much mutations as it corresponds to the sequence identity of this protein with each of the other proteins of the family. In the selection of which sites to mutate is where we included or not natural selection. In one case, we mutated sites randomly and, on the other case, we accounted for natural selection mutating sites more likely to mutate according to the ``Stress Model''. Finally, we calculated, for simulated and experimental sets of protein, profiles of structural variability in cartesian coordinates and projected on normal modes and compared them using the Pearson correlation coefficient and the ``Mean Square Error'' (MSE). We obtained that either at the level of cartesian coordinates or at the level of normal modes, there is no clear evidence of natural selection in protein evolution. These results give more evidence of the absence of natural selection in structural evolution.

\section{Introduction}
Proteins diverge during biological evolution, which is evident in the variation of the aminoacid sequences and the resulting structural, dynamical and functional changes. It is known that the structure diverges much more slowly than the sequence and that the  structural divergence occurs mainly along the lower energy vibrational modes of proteins and that there are structurally conserved ``cores'' in families of proteins [1]. These facts are difficult to interpret because most of the studies that have been made are purely empirical. To go forward in this sense, it has been developed the mechanistic model ``Linearly Forced – Elastic Network Model'' (LF - ENM), which predicts the change in the equilibrium position of the sites as a result of random mutations, not subjected to natural selection. Applying this model, it was shown that the patterns of structural change (greater contribution of lower energy normal modes and the existence of a structurally conserved ``core'') can be predicted without resorting to natural selection [3,4]. With regard to the dynamics, this model reproduces well the observed pattern that the normal modes of lower energy are more evolutionarily conserved, even in the absence of natural selection [5]. This implies that such modes are more robust to random mutations, so that they would conserve more even in the absence of natural selection. All these results call into question interpretations based on the assumption that everything that is conserved or that varies is related to the biological function.
While natural selection apparently little affects structural and dynamical divergence patterns, at the level of aminoacid sequences, different sites evolve at different speeds. Purely mutational evolutional models such as the LF-ENM, cannot account for this fact. To explain such patterns of sequence variation, natural selection must be modeled. Recently, we have proposed a mechanistic model (``Stress Model'') in which a mutation is accepted at a rate proportional to the probability that the mutant adopts the ``active structure". This model has been used to account for the average evolutionary variation from site to site [6].
As we said, the LF-ENM model has been successfully used to explain the observed patterns of structural and dynamical divergence in the absence of natural selection. However, it is expected that the selection restricts the structural divergence and / or dynamics. For example if the structure and fluctuations of an enzyme`s active site are important for enzymatic activity, one would expect that the structure and movements are evolutionarily conserved significantly higher than expected for purely mutational patterns. Therefore, no matter how weak, some evidence of natural selection at the level of structural and dynamical divergence would be expected. The aim of this work is to find evidence of natural selection at the structural divergence level.

\section{Methods}

{\bf Experimental dataset:}
We selected 8 families of proteins from the database of multiple structural alignments of homologous HOMSTRAD (http://mizuguchilab.org/homstrad/). In this dataset, there are representatives of the major structural classes: all alpha, all beta, alpha and beta, and small proteins. We looked for families that possess multiple structural alignments with more than 12 proteins and with an alignment length greater than 50 sites. The selected families and their characteristics are shown in Table 1.

{\bf Selection of the reference protein:}
For each family of proteins we selected a reference ``wilt type'' protein, which we consider is the most structurally representative protein of the family. To get this protein, we first calculated the average structure of each multiple alignment. Then, we calculated the ``Mean Square Deviation'' (MSD) between the structure of each protein of the family and the obtained average structure. Finally, we selected as the reference protein the one with the lower value of MSD.

{\bf Alignments analysis:}
For each family of proteins, the reference protein was aligned with each of the other proteins of the family. Then, the aligned and nonaligned sites, their coordinates, and the sequence identity for each pair of proteins were obtained.

{\bf ENM of the reference protein:}

We considered the backbone fluctuations of the reference protein around its equilibrium conformation to be described by a coarse - grained ``Elastic Network Model'' (ENM), which represents a protein as a network of nodes placed at the alpha carbons ($C_{\alpha}$) connected by springs. In general, the ENM potential is of the form:

\begin{equation}
V(r) = 1/2*(r-r_{0})^{T}K(r-r_{0})
\end{equation}

where, for a protein of $N$ sites, $r$ is a column vector with $3N$ elements: the $x$, $y$, $z$ coordinates of the $N$ $C_{\alpha}$, $r_{0}$ is the equilibrium structure, and $K$ is the ``stiffness'' matrix, which represents the network\textsc{\char13} s topology and spring force constants. 
Specifically, we used the ``Anisotropic Network Model'' (ANM). Following this model, we gave a spring force constant of 1 to sites at a distance $\leq$ 10 \AA  and a spring force constant of 0 to sites at a distance > 10 \AA. We selected 10 \AA  as the cut off value after optimization using a range of values form 8 to 12 (data not shown). This cut off value is also the most commonly used.

\section{Conclusion}
Not much of a paper, but it's a start.

\end{document}

### 2016-04-10 FUNCTIONS/AnalyzeExperimentalTheoretical.R

@@ -1,11 +1,13 @@
-# This function analyzes experimental and theoretical data calculating measures of variability 
-# of experimental proteins and simulated mutants respectibly. 
+# This function analyzes experimental and theoretical data calculating measures of variability in cartesian coordinates
+# and projected on normal modes of p.ref. 
 # 
 #  Args:
-#    family: the family of p.ref.
+#    family: the family of the protein to mutate. It can be "globins", "serinProteases", 
+#    "snakesToxin", "sh3", "fabp", "rrm", "phoslip" or "cys".
 #    exp.chain.p.ref: the chain of p.ref in the pdb file obtained from Homstrad.
-#    n.mut.p: the number of simulated mutants generated for each protein of the family.
-#    R0: cut-off for the ANM.
+#    n.mut.p: the number of mutants to generate for each member of the family. For example, if the family has 20 
+#    members, the program generates n.mut.p x 20 mutants.
+#    R0: the cut-off for the "ANM" (Anisotropic Network Model) that represents the proteins.
 #    rotate: it can be "TRUE" or "FALSE". If it is "TRUE", r.p.2 is rotaded in order to minimize RMSD with r.p.ref.
 #    core: it can be "TRUE" or "FALSE". If it is "TRUE", the program only considers the conserved core of 
 #    the alignment. If it is "FALSE", the program analyzes the whole alignment.

### 2016-04-10 FUNCTIONS/GenerateMutants.R

@@ -3,17 +3,21 @@
 # - "MND" (Multivariate Normal Distribution), considering mu = dr expected value = 0 and Sigma = Cov.
 #
 #  Args:
-#    family: the family of the protein to mutate.
+#    family: the family of the protein to mutate. It can be "globins", "serinProteases", 
+#    "snakesToxin", "sh3", "fabp", "rrm", "phoslip" or "cys".
 #    exp.chain.p.ref: the chain of p.ref in the pdb file obtained from Homstrad.
-#    mut.model: mutational model. It can be "LFENM" or "MND".
-#    n.mut.p: the number of mutants to generate for each protein of the family.
+#    mut.model: mutational model. It can be "LFENM" (Linearly Forced - Elastic Network Model) or "MND" 
+#    (Multivariate Normal Distribution).
+#    n.mut.p: the number of mutants to generate for each member of the family. For example, if the family has 20 
+#    members, the program generates n.mut.p x 20 mutants.
 #    fmax: argument for "LFENM". It is the maximun value for the forces that model the mutations.
-#    R0: the cut-off for the ANM ("Anisotropic Network Model").
-#    heme: argument for "globins". It can be "TRUE" or "FALSE". If it is "TRUE" the program considers the heme group.
+#    R0: the cut-off for the "ANM" (Anisotropic Network Model) that represents the proteins.
+#    heme: argument for "globins". It can be "TRUE" or "FALSE". If it is "TRUE", the program considers the heme group.
 #    natural.selection: It can be "TRUE" or "FALSE". If it is "TRUE", the mutants are calculated considering natural 
 #    selection. If it is "FALSE", the mutants are calculated in a random manner.
-#    data.dir: directory of the data.It must contain the output of the function AnalyzeFamily().
-#    out.dir: output directory.
+#    data.dir: directory of the data. It must contain the file the pdb file 
+#    obtained from Homstrad ("data.dir/family_coordinates.csv").
+#    out.dir: output directory. It must contain the output of the function AnalyzeFamily().
 #    mut.fname.id: ID for output filenames.
 #    TOLERANCE: 0 tolerance.
 #
@@ -42,8 +46,6 @@ GenerateMutants <- function(family,
   
   # Filenames.
[…]

### 2016-04-11 INFORMATION/paper.tex
cambios 11/04/2016

@@
 
+{\bf LF-ENM model of mutant proteins:}
+
+To simulate mutants of each reference protein and thus to generate datasets of theoretical proteins, we used the ``Linearly Forced Elastic Network Model'' (LF - ENM).
+This model predicts the effect of a single mutation adding a linear perturbative term to the reference potential:
+
+Agregar formula
+
+where $f$ is a column vector with $3N$ elements that models the mutation.
+The equilibrium structure of the mutant $r^{0}_{mut}$ is the value of $r$ that minimizes $V_{mut}$.
+Using Eqs.
+(1) and (2) we find the structural variation due to the mutation:
+
+Agregar formula
+
+This equation shows that the structural perturbation introduced by a mutation is related to the mutation and to the network of oscillators, via $K^{1}$.
+We should note here that $K^{1}$ is actually the pseudo inverse, because $K$ has six zero eigenvalues, corresponding to translations and rotations, so that it is not invertible.
+
+{\bf Multiple-sites mutants: }
+In order to simulate adequately the experimental data, we did not simulated proteins with a single mutation, we did simulate proteins with multiple mutations.
+To do this, we considered additive mutations by the assumption that $K^{mut}$ \cong $K^{wt}$:
+
+\begin{equation}
+dr^{tot} = dr^{mut1}_{wt} + dr^{mut2}_{wt} + ... + dr^{mutNmut}_{wt} = K^{-1}_{wt} \times (fmut1+fmut2+...+fmutNmut) 
+\end{equation}
+
+Where $dr^{tot}$ is the total structural variation due the M mutations, dr^{mutm}_{wt} is the structural variation produced by the mutation $m$considering $K^{wt}$, and fmutn is the vector of force of $n$.
+
+\section{Results and discussion}
+
 \section{Conclusion}
-Not much of a paper, but it's a start.
 

### 2016-04-12 INFORMATION/paper.tex
cambios 12/04/2016

--- 2016-04-10 INFORMATION/paper.tex
@@
 
+{\bf ENM of a reference protein:}
+
+We considered the backbone fluctuations of the reference ``wilt type'' protein around its equilibrium conformation to be described by a coarse - grained ``Elastic Network Model'' (ENM), which represents a protein as a network of nodes placed at the alpha carbons ($C_{\alpha}$) connected by springs.
+In general, the ENM potential is of the form:
+
+\begin{equation}
+V_{wt}(\mathbf{r}) = 1/2(\mathbf{r}-\mathbf{r}^{0}_{wt})^{T}\mathbf{K}_{wt}(\mathbf{r}-\mathbf{r}^{0}_{wt})
+\end{equation}
+
+where, for a protein of $N$ sites, $\mathbf{r}$ is a column vector with $3N$ elements: the $x$, $y$, $z$ coordinates of the $N$ $C_{\alpha}$, $\mathbf{r}^{0}_{wt}$ is the equilibrium structure of the reference protein, and $\mathbf{K}_{wt}$ is the ``stiffness'' matrix, which represents the network\textsc{\char13} s topology and spring force constants.
+
+{\bf LF-ENM model of mutant proteins:}
+
+To simulate mutants of each reference protein and thus to generate datasets of theoretical proteins, we used the ``Linearly Forced Elastic Network Model'' (LF - ENM).
+This model predicts the effect of a single mutation adding a linear perturbative term to the reference potential:
+
+\begin{equation}
+V_{mut}=V_{wt} - \mathbf{f}^{T}(\mathbf{r}-\mathbf{r}^{0}_{wt})
+\end{equation}
+
+where $\mathbf{f}$ is a column vector with $3N$ elements that models the mutation.
+The equilibrium structure of the mutant $\mathbf{r}^{0}_{mut}$ is the value of $\mathbf{r}$ that minimizes $V_{mut}$.
+Using Eqs.
+(1) and (2) we find the structural variation due to the mutation:
+
+\begin{equation}
+d\mathbf{r}^{0} \equiv  \mathbf{r}^{0}_{mut} - \mathbf{r}^{0}_{wt} = \mathbf{K}^{-1}_{wt}\mathbf{f}
+\end{equation}
+
+This equation shows that the structural perturbation introduced by a mutation is related to the mutation and to the network of oscillators, via $\mathbf{K}^{-1}_{wt}$.
+We should note here that $\mathbf{K}^{-1}_{wt}$ is actually the pseudo inverse, because $\mathbf{K}_{wt}$ has six zero eigenvalues, corresponding to translations and rotations, so that it is not invertible.
+
+{\bf LF-ENM for multiple mutants: }
+To simulate proteins with not one but multiple mutations we considered additive mutations by the assumption that $\mathbf{K}^{mut}$ \cong $\mathbf{K}^{wt}$:
+
+\begin{equation}
+d\mathbf{r}^{tot} = d\mathbf{r}^{mut1}_{wt}+d\mathbf{r}^{mut2}_{wt}+ ...+d\mathbf{r}^{mutm}_{wt}+...+d\mathbf{r}^{mutNmut}_{wt}
+\end{equation}
+
+\begin{equation}
+d\mathbf{r}^{tot} = =\mathbf{K}^{-1}_{wt}\times(\mathbf{fmut1}+\mathbf{fmut2}+...+\mathbf{fmutm}+...+\mathbf{fmutNmut}) 
+\end{equation}
+
+Where $d\mathbf{r}^{tot}$ is the total structural variation due the M mutations, $d\mathbf{r}^{mutm}_{wt}$ is the structural variation produced by the mutation $m$ (considering $\mathbf{K}^{wt}$), and $\mathbf{fmutm}$ is the vector of force of the $m$ mutation.
+
+{\bf Model parameters: }
+To completely specify the model, we must choose $\mathbf{K}_{wt}$ and $\mathbf{f}$.
+There are a number of alternative ENMs.Specifically, we used the ``Anisotropic Network Model'' (ANM).
+Following this model, we gave a spring force constant of 1 to sites at a distance $\leq$ 10 $\AA$ and a spring force constant of 0 to sites at a distance > 10 $\AA$.
+We selected 10 $\AA$ as the cut off value after optimization using a range of values form 8 to 12 (data not shown).
+This cut off value is also the most commonly used.
+To calculate $\mathbf{f}$, given a mutation at a site $l$, each site $i$ in contact with $l$ is assigned a force directed along the $l-i$ contact and site $l$ is assigned a reaction force.
+To simulate random mutations, the magnitudes of $f_{li}$ were randomly picked from a uniform distribution in $[-f_{max},f_{max}]$.
+The forces for different contacts were picked independently.
+Since $f_{max}$ does not affect the results, we set
+$f_{max} = 2$. We can think of the range $[-f_{max}, f_{max}]$ as a continuous approximation of the perturbations introduced by the mutations, covering
+from mutations between physicochemically similar amino acids ($f \approx 0$) up to mutations between very different amino acids ($f \leq f_{max}$).
+
 {\bf Experimental dataset:}
@@
 
-{\bf Selection of the reference protein:}
+{\it Selection of the reference protein:}
 For each family of proteins we selected a reference ``wilt type'' protein, which we consider is the most structurally representative protein of the family.
@@
 
-{\bf Alignments analysis:}
+{\it Alignments analysis:}
 For each family of proteins, the reference protein was aligned with each of the other proteins of the family.
@@
 
-{\bf ENM of the reference protein:}
+{\bf Theoretical datasets:}
+In order to study the effect of natural selection on structural divergence, for each family of proteins, we generated two datasets of simulated mutants.
+In one dataset, we applied natural selection and, on the other dataset, we did not consider natural selection:
 
-We considered the backbone fluctuations of the reference protein around its equilibrium conformation to be described by a coarse - grained ``Elastic Network Model'' (ENM), which represents a protein as a network of nodes placed at the alpha carbons ($C_{\alpha}$) connected by springs.
-In general, the ENM potential is of the form:
+{\it Mutants with natural selection (NS = T):} we applied natural selection at the sequence level.
+To determine which sites to mutate accounting natural selection, we followed the stress model, by which probabilities of mutation are assigned for each site of the reference protein:
 
 \begin{equation}
-V(r) = 1/2*(r-r_{0})^{T}K(r-r_{0})
+p^{mut}_{i} = 1 - (beta \times CN_{i})
 \end{equation}
 
-where, for a protein of $N$ sites, $r$ is a column vector with $3N$ elements: the $x$, $y$, $z$ coordinates of the $N$ $C_{\alpha}$, $r_{0}$ is the equilibrium structure, and $K$ is the ``stiffness'' matrix, which represents the network\textsc{\char13} s topology and spring force constants.
-Specifically, we used the ``Anisotropic Network Model'' (ANM).
-Following this model, we gave a spring force constant of 1 to sites at a distance $\leq$ 10 \AA  and a spring force constant of 0 to sites at a distance > 10 \AA.
-We selected 10 \AA  as the cut off value after optimization using a range of values form 8 to 12 (data not shown).
-This cut off value is also the most commonly used.
+Were $CN_{i}$ is the number of contacts (sites with a distance $\leq$ 10 $\AA$ in this case) of site $i$. 
+To select the number of sites to mutate, we took information from the alignments.
+For each pair comprising the reference protein and one of the other proteins of the family, we obtained the average sequence identity (\% ID) within the aligned region.
+Then, the number of mutated sites for this pair is:
+
+\begin{equation}
+nsites^{mut} = (100 - \% ID) \times naa / 100
+\end{equation}
+
+Being $naa$ the number of aminoacids of the reference protein. 
+Then, for each of these pairs, we generated 10 mutants of $nsites^{mut}$, where the mutated sites are the ones with more probabilities to mutate following the stress model.
+
+In this way, if the family has $P$ proteins (plus the reference protein), we obtained a simulated dataset of $10 \times P$  members.
+
+{\it Mutants without natural selection (NS = F):} For each pair comprising the reference protein and one of the other proteins of the family, we obtained the number of sites to mutate as mentioned before and we mutated randomly this number of sites.
+For each of these pairs, we generated 10 mutants.
+Hence, again, if the family has $P$ proteins plus the reference protein, we obtained a simulated dataset of  $10 \times P$  members.
+
+\section{Results and discussion}
 
 \section{Conclusion}
-Not much of a paper, but it's a start.
 

### 2016-04-13 INFORMATION/paper.tex
cambios 13/04/2016

@@
 {\bf LF-ENM for multiple mutants: }
-To simulate proteins with not one but multiple mutations we considered additive mutations by the assumption that $\mathbf{K}^{mut}$ \cong $\mathbf{K}^{wt}$:
+To simulate proteins with not one but multiple mutations we considered additive mutations by the assumption that $\mathbf{K}_{mut}$ \cong $\mathbf{K}_{wt}$:
 
@@
 \begin{equation}
-d\mathbf{r}^{tot} = =\mathbf{K}^{-1}_{wt}\times(\mathbf{fmut1}+\mathbf{fmut2}+...+\mathbf{fmutm}+...+\mathbf{fmutNmut}) 
+d\mathbf{r}^{tot} =\mathbf{K}^{-1}_{wt}\times(\mathbf{f}_{mut1}+\mathbf{f}_{mut2}+...+\mathbf{f}_{mutm}+...+\mathbf{fmut}_{Nmut}) 
 \end{equation}
@@
 {\it Selection of the reference protein:}
-For each family of proteins we selected a reference ``wilt type'' protein, which we consider is the most structurally representative protein of the family.
+For each family of the dataset we selected a reference ``wilt type'' protein, which we consider is the most structurally representative protein of the family.
 To get this protein, we first calculated the average structure of each multiple alignment.
@@
 {\bf Theoretical datasets:}
-In order to study the effect of natural selection on structural divergence, for each family of proteins, we generated two datasets of simulated mutants.
+In order to study the effect of natural selection on structural divergence we generated two datasets of simulated mutants.
 In one dataset, we applied natural selection and, on the other dataset, we did not consider natural selection:
 
-{\it Mutants with natural selection (NS = T):} we applied natural selection at the sequence level.
+{\it Mutants with natural selection (NS = T):} we applied natural selection at the sequence level of the reference protein of each family.
 To determine which sites to mutate accounting natural selection, we followed the stress model, by which probabilities of mutation are assigned for each site of the reference protein:
@@
 Were $CN_{i}$ is the number of contacts (sites with a distance $\leq$ 10 $\AA$ in this case) of site $i$. 
-To select the number of sites to mutate, we took information from the alignments.
+To select the number of sites to mutate, we took information from the alignment of the correspondent family.
 For each pair comprising the reference protein and one of the other proteins of the family, we obtained the average sequence identity (\% ID) within the aligned region.
@@
 
-{\it Mutants without natural selection (NS = F):} For each pair comprising the reference protein and one of the other proteins of the family, we obtained the number of sites to mutate as mentioned before and we mutated randomly this number of sites.
+{\it Mutants without natural selection (NS = F):} For family and for each pair comprising the reference protein and one of the other proteins of the family, we obtained the number of sites to mutate as mentioned before and we mutated randomly this number of sites.
 For each of these pairs, we generated 10 mutants.
@@
 
+{\bf Structural variability measures:}
+We obtained the coordinates of the aligned sites of each protein.
+For the theoretical dataset we considered that there are not nonaligned sites.
+Then, structural variability measures were calculated in Cartesian coordinates and projected onto the normal modes coordinates:
+
+{\it Cartesian coordinates:}
+Structural variation of each protein was calculated relative to the reference protein into the aligned sites. To do this, for each aligned site, we calculated the square deviation:
+
+\begin{equation}
+\left\|d\mathbf{r}^{0}_{i}\right\|^{2}=d\mathbf{x}^{0}_{i}^{2}+d\mathbf{y}^{0}_{i}^{2}+d\mathbf{z}^{0}_{i}^{2}
+\end{equation}
+
+Were $d\mathbf{r}^{0}_{i}=(d\mathbf{x}^{0}_{i}d\mathbf{y}^{0}_{i}d\mathbf{z}^{0}_{i})^{T}$ is the column vector of cartesian displacements of the $ith$ $C_{\alpha}$ with respect to the reference structure obtained from Eq.
+(4).
+To diminish noisy information, we smoothed these profiles as shown:
+
+Formula
+
+Then, since we are only interested in the relative variability of different sites, deviations obtained using Eq. () were normalize so that they add up to 1.
+
+{\it Normal modes coordinates:}
+Analysis of structural change of normal modes was calculated by projecting structural differences of aligned sites of each protein onto the normal modes of the reference protein.
+The normal modes were obtained by solving the equation:
+
+\begin{equation}
+\mathbf{K}\mathbf{q}_{n} = \lambda_{n}\mathbf{q}_{n} 
+\end{equation}
+
+For proteins that do not align with all the sites of the reference protein instead of $\mathbf{K}$, we used $\mathbf{K}_{eff}$, whose normal modes describe the motions of the aligned sites only (see reference [x]).
+Then, for a protein with structural variation of the aligned sites $d\mathbf{r}^{0}$, the projection onto eigenvectors was calculated as follows:
+
+\begin{equation}
+P_{n} \equiv \frac{(\mathbf{q}^{T}_{n}d\mathbf{r}^{0})^2}{\sum_{n}(\mathbf{q}^{T}_{n}d\mathbf{r}^{0})^2}
+\end{equation}
+
+{\bf Profile comparisons:}
+
+{\it Cartesian coordinates:} For the theoretical datasets and for the experimental dataset we averaged $\left\|d\mathbf{r}^{0}_{i}\right\|^{2}$ over each site $i$ of the reference protein of each family to obtain profiles of $MSD_{i}$.
+Then, the theoretical average profiles were fitted with the experimental profile.
+Lastly, for each dataset, we concatenated the profiles obtained for all of the families to obtain a sole profile.
+
+{\it Normal modes coordinates:} For the theoretical datasets, with or without natural selection, the 10 x M profiles of $P_{n}$ of each family were split in 10 groups so that in all of them there was a simulated mutant that corresponded to an experimental pair of proteins of the family in means of the \% ID.
+Then we calculated, for these 10 groups, the average and 0.05 and 0.95 quantiles.
+Finally, we calculated the average of averages and the average of quantiles.
+For the experimental dataset, the average and 0.05 and 0.95 quantile profiles of each family were calculated.
+
 \section{Results and discussion}
+{\it Cartesian coordinates:}
+In order to analyze the effect of natural selection on the structural variability in cartesian coordinates we calculated unique per dataset $MSD_{i}$ profiles as explained in Methods.
+These profiles contain information of all of the families.
+Then, we calculated the $R^2$ and the $MSE$ between the experimental dataset compared with theoretical datasets (with and without natural selection).
+The results are shown in figure 1.
+Figue 1 shows that the $R^2$ between the experimental dataset and theoretical datasets, with or without natural selection, is high, $\approx 0.8$, and that accounting for natural selection does not seem to improve the agreement.
+
+{\it Normal modes coordinates:}
+In order to analyze the effect of natural selection on the structural variability projected onto normal modes coordinates of the reference protein, we obtained average $P_{n}$ profiles and 0.05 and 0.95 quantiles profiles as explained in Methods.
+To compare the experimental dataset with the theoretical datasets we calculated the $R^2$ and the $MSE$ between them.
+The results are shown in Table 2 and figure 3.
+Table 1 and figure 2 show that, again, the $R^2$ between experimental data and theoretical data, with or without natural selection, is high, $\approx 0.7$ and that natural selection does not seem to improve the agreement with experimental data.
 

### 2016-04-14 AllFamilys.Rmd
cambios 14/04/2016

@@
 ```{r}
-plot(nsF.theo.MSDi.s, type = "l", xlab = "sitio", ylab = "Theoretical ns = F", ylim = c(0, 0.14))
+plot(nsF.theo.MSDi.s, type = "l", xlab = "site", ylab = "Theoretical NS = F", ylim = c(0, 0.14))
 ```
@@
 ```{r}
-plot(exp.MSDi.s, type = "l", col = "red", ylab = "Experimental", ylim = c(0, 0.14))
+plot(exp.MSDi.s, type = "l", col = "red", xlab = "site",  ylab = "Experimental", ylim = c(0, 0.14))
 ```
@@
 ```{r}
-plot(nsF.theo.MSDi.s, type = "l", ylab = "both", ylim = c(0, 0.14))
+plot(nsF.theo.MSDi.s, type = "l", xlab = "site", ylab = "Merge", ylim = c(0, 0.14))
 points(exp.MSDi.s, col = "red", type = "l")
@@
 ```{r}
-plot(nsT.theo.MSDi.s, type="l", xlab = "sitio", ylab = "Theoretical ns = T", ylim = c(0, 0.14))
+plot(nsT.theo.MSDi.s, type="l", xlab = "sitie", ylab = "Theoretical NS = T", ylim = c(0, 0.14))
 ```
@@
 ```{r}
-plot(exp.MSDi.s, type = "l", col = "red", ylab = "Experimental", ylim = c(0, 0.14))
+plot(exp.MSDi.s, type = "l", col = "red", xlab = "sitie", ylab = "Experimental", ylim = c(0, 0.14))
 ```
@@
 ```{r}
-plot(nsT.theo.MSDi.s, type = "l", ylab = "both", ylim = c(0, 0.14))
+plot(nsT.theo.MSDi.s, type = "l", xlab = "sitie", ylab = "Merge", ylim = c(0, 0.14))
 points(exp.MSDi.s, col = "red", type = "l")

### 2016-04-14 INFORMATION/paper.tex
cambios 14/04/2016

@@
 \usepackage[T1]{fontenc}
+\usepackage{multicol}
 
@@
 
+\begin{multicols}{2} 
 \section{Introduction}
@@
 \begin{equation}
-d\mathbf{r}^{tot} = d\mathbf{r}^{mut1}_{wt}+d\mathbf{r}^{mut2}_{wt}+ ...+d\mathbf{r}^{mutm}_{wt}+...+d\mathbf{r}^{mutNmut}_{wt}
+d\mathbf{r}^{0,tot} = d\mathbf{r}^{0,mut1}_{wt}+d\mathbf{r}^{0,mut2}_{wt}+ ...+d\mathbf{r}^{0,mutm}_{wt}+...+d\mathbf{r}^{0,mutNmut}_{wt}
 \end{equation}
@@
 \begin{equation}
-d\mathbf{r}^{tot} =\mathbf{K}^{-1}_{wt}\times(\mathbf{f}_{mut1}+\mathbf{f}_{mut2}+...+\mathbf{f}_{mutm}+...+\mathbf{fmut}_{Nmut}) 
+d\mathbf{r}^{0,tot} =\mathbf{K}^{-1}_{wt}\times(\mathbf{f}_{mut1}+\mathbf{f}_{mut2}+...+\mathbf{f}_{mutm}+...+\mathbf{f}_{mutNmut}) 
 \end{equation}
 
-Where $d\mathbf{r}^{tot}$ is the total structural variation due the M mutations, $d\mathbf{r}^{mutm}_{wt}$ is the structural variation produced by the mutation $m$ (considering $\mathbf{K}^{wt}$), and $\mathbf{fmutm}$ is the vector of force of the $m$ mutation.
+Where $d\mathbf{r}^{0,tot}$ is the total structural variation due the M mutations, $d\mathbf{r}^{0,mutm}_{wt}$ is the structural variation produced by the mutation $m$ (considering $\mathbf{K}_{wt}$), and $\mathbf{f}_mutm}$ is the vector of force of the $m$ mutation.
 
@@
 
-{\it Mutants without natural selection (NS = F):} For family and for each pair comprising the reference protein and one of the other proteins of the family, we obtained the number of sites to mutate as mentioned before and we mutated randomly this number of sites.
+{\it Mutants without natural selection (NS = F):} For each family and for each pair comprising the reference protein and one of the other proteins of the family, we obtained the number of sites to mutate as mentioned before and we mutated randomly this number of sites.
 For each of these pairs, we generated 10 mutants.
-Hence, again, if the family has $P$ proteins plus the reference protein, we obtained a simulated dataset of  $10 \times P$  members.
+Hence, again, if the family has $P$ proteins (plus the reference protein), we obtained a simulated dataset of  $10 \times P$  members.
 
@@
 \begin{equation}
-\left\|d\mathbf{r}^{0}_{i}\right\|^{2}=d\mathbf{x}^{0}_{i}^{2}+d\mathbf{y}^{0}_{i}^{2}+d\mathbf{z}^{0}_{i}^{2}
+\left\|d\mathbf{r}^{0}_{i}\right\|^{2}=dx^{0,2}_{i}+dy^{0,2}_{i}+dz^{0,2}_{i}
 \end{equation}
 
-Were $d\mathbf{r}^{0}_{i}=(d\mathbf{x}^{0}_{i}d\mathbf{y}^{0}_{i}d\mathbf{z}^{0}_{i})^{T}$ is the column vector of cartesian displacements of the $ith$ $C_{\alpha}$ with respect to the reference structure obtained from Eq.
+Were $d\mathbf{r}^{0}_{i}=(d\mathbf{x}^{0}_{i}d\mathbf{y}^{0}_{i}d\mathbf{z}^{0}_{i})^{T}$ is the column vector of cartesian displacements of the $i^{th}$ $C_{\alpha}$ with respect to the reference structure obtained from Eq.
 (4).
@@
 
-{\it Normal modes coordinates:} For the theoretical datasets, with or without natural selection, the 10 x M profiles of $P_{n}$ of each family were split in 10 groups so that in all of them there was a simulated mutant that corresponded to an experimental pair of proteins of the family in means of the \% ID.
+{\it Normal modes coordinates:} For the theoretical datasets, with or without natural selection, the 10 x P profiles of $P_{n}$ of each family were split in 10 groups so that in all of them there was a simulated mutant that corresponded to an experimental pair of proteins of the family in means of the \% ID.
 Then we calculated, for these 10 groups, the average and 0.05 and 0.95 quantiles.
@@
 To compare the experimental dataset with the theoretical datasets we calculated the $R^2$ and the $MSE$ between them.
-The results are shown in Table 2 and figure 3.
+The results are shown in Table 2 and figure 2.
 Table 1 and figure 2 show that, again, the $R^2$ between experimental data and theoretical data, with or without natural selection, is high, $\approx 0.7$ and that natural selection does not seem to improve the agreement with experimental data.
@@
 \section{Conclusion}
+\end{multicols}
 

### 2016-04-14 figure_1.Rmd
cambios 14/04/2016

--- 2016-04-14 AllFamilys.Rmd
@@
 ---
-title: "MSDi for all families together"
-author: "Maria Laura Marcos"
 output: html_document
@@
 
-# Create matrixes.
-nsF.theo.MSDi = c()
-nsT.theo.MSDi = c()
 nsF.theo.MSDi.s = c()
-nsT.theo.MSDi.s = c()
-
-exp.MSDi = c()
 exp.MSDi.s = c()
@@
 input <- read.csv(input.fname)
-
-# Print the input in the html file.
-print(input)
 
@@
 
-  m.cF.exp.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.exp.dr.squarei.csv", sep = "")))
   m.cF.exp.smooth.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.exp.smooth.dr.squarei.csv", sep = "")))
 
-  cF.exp.MSDi = colMeans(m.cF.exp.dr.squarei, na.rm = T )
   cF.exp.MSDi.s = colMeans(m.cF.exp.smooth.dr.squarei, na.rm = T )
@@
   #Read theoretical data#
-
-  # natural selection (ns) = F.
-  m.nsF.cF.theo.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.dr.squarei.csv", sep = "")))
   m.nsF.cF.theo.smooth.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.smooth.dr.squarei.csv", sep = "")))
 
-  nsF.cF.theo.MSDi = colMeans(m.nsF.cF.theo.dr.squarei, na.rm = T)
   nsF.cF.theo.MSDi.s = colMeans(m.nsF.cF.theo.smooth.dr.squarei, na.rm = T)
 
-  # natural selection (ns) = T.
-  analysis.fname.id <- paste(family, "_mut.model_", mut.model, "_naturalSelection_", "TRUE", "_R0_", R0, "_core_", "FALSE", "_K.analysis_", K.analysis, sep = "")
-
-  m.nsT.cF.theo.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.dr.squarei.csv", sep = "")))
-  m.nsT.cF.theo.smooth.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.smooth.dr.squarei.csv", sep = "")))
-
-  nsT.cF.theo.MSDi = colMeans(m.nsT.cF.theo.dr.squarei, na.rm = T)
-  nsT.cF.theo.MSDi.s = colMeans(m.nsT.cF.theo.smooth.dr.squarei, na.rm = T)
-
   ## Fit theoretical data with experimental data.
-  fit.nsF.cF = lm(cF.exp.MSDi ~ nsF.cF.theo.MSDi)
-  fit.nsF.cF.MSDi = fitted.values(fit.nsF.cF)
-
-  fit.nsT.cF = lm(cF.exp.MSDi ~ nsT.cF.theo.MSDi)
-  fit.nsT.cF.MSDi = fitted.values(fit.nsT.cF)
 
@@
 
-  fit.nsT.cF.s = lm(cF.exp.MSDi.s ~ nsT.cF.theo.MSDi.s)
-  fit.nsT.cF.MSDi.s = fitted.values(fit.nsT.cF.s)
+  # Concatenate information.
 
-  # Concatenate information.
-  nsF.theo.MSDi = c(nsF.theo.MSDi, fit.nsF.cF.MSDi)
-  nsT.theo.MSDi = c(nsT.theo.MSDi, fit.nsT.cF.MSDi)
   nsF.theo.MSDi.s = c(nsF.theo.MSDi.s, fit.nsF.cF.MSDi.s)
-  nsT.theo.MSDi.s = c(nsT.theo.MSDi.s, fit.nsT.cF.MSDi.s)
 
-  cF.exp.MSDi = cF.exp.MSDi[!is.na(cF.exp.MSDi)]
   cF.exp.MSDi.s = cF.exp.MSDi.s[!is.na(cF.exp.MSDi.s)]
-
-  exp.MSDi = c(exp.MSDi, cF.exp.MSDi)
   exp.MSDi.s = c(exp.MSDi.s, cF.exp.MSDi.s)
@@
 # Caluclate measures.
-R2.nsF.cF = cor(nsF.theo.MSDi, exp.MSDi) ^ 2 
-R2.nsT.cF = cor(nsT.theo.MSDi, exp.MSDi) ^ 2
 
 R2.nsF.cF.s = cor(nsF.theo.MSDi.s, exp.MSDi.s) ^ 2
-R2.nsT.cF.s = cor(nsT.theo.MSDi.s, exp.MSDi.s) ^ 2
-
-MSE.nsF.cF = mean((nsF.theo.MSDi - exp.MSDi) ^ 2)
-MSE.nsT.cF = mean((nsT.theo.MSDi - exp.MSDi) ^ 2)
 
 MSE.nsF.cF.s = mean((nsF.theo.MSDi.s - exp.MSDi.s) ^ 2)
-MSE.nsT.cF.s = mean((nsT.theo.MSDi.s - exp.MSDi.s) ^ 2)
 
@@
 
-```{r, include = F}
-layout(matrix(1:3, 3, 1, byrow = F))
-
-plot(nsF.theo.MSDi, type = "l", xlab = "sitio", ylab = "Theoretical")
-plot(exp.MSDi, type = "l", col = "red", ylab = "Experimental")
-plot(nsF.theo.MSDi, type = "l", ylab = "both")
-points(exp.MSDi, col = "red", type = "l")
-legend("topleft", paste("R^2", round(R2.nsF.cF, digits = 2)), bty = "n", text.col = "red")
-
-```
-
-```{r, include = F}
-layout(matrix(1:3, 3, 1, byrow = F)) 
-plot(nsT.theo.MSDi, type="l", xlab = "sitio", ylab = "Theoretical")
-plot(exp.MSDi, type="l", col ="red", ylab = "Experimental")
-plot(nsT.theo.MSDi, type="l", ylab = "both")
-points(exp.MSDi, col = "red", type="l")
-legend("topleft", paste("R^2", round(R2.nsT.cF, digits = 2)), bty = "n", text.col = "red")
-```
-All families fitted smooth normalized MSD profiles
-
-Without natural selection (ns = F)
-
 ```{r}
-plot(nsF.theo.MSDi.s, type = "l", xlab = "site", ylab = "Theoretical NS = F", ylim = c(0, 0.14))
+plot(nsF.theo.MSDi.s, type = "l", xlab = "site", ylab = "Theoretical MSDi NS = F", ylim = c(0, 0.14))
 ```
@@
 ```{r}
-plot(exp.MSDi.s, type = "l", col = "red", xlab = "site",  ylab = "Experimental", ylim = c(0, 0.14))
+plot(exp.MSDi.s, type = "l", col = "red", xlab = "site",  ylab = "Experimental MSDi ", ylim = c(0, 0.14))
 ```
@@
 ```
-
-With natural selection (ns = T)
-
-```{r}
-plot(nsT.theo.MSDi.s, type="l", xlab = "sitie", ylab = "Theoretical NS = T", ylim = c(0, 0.14))
-```
-
-```{r}
-plot(exp.MSDi.s, type = "l", col = "red", xlab = "sitie", ylab = "Experimental", ylim = c(0, 0.14))
-```
-
-```{r}
-plot(nsT.theo.MSDi.s, type = "l", xlab = "sitie", ylab = "Merge", ylim = c(0, 0.14))
-points(exp.MSDi.s, col = "red", type = "l")
-legend("topleft", paste("R^2", round(R2.nsT.cF.s, digits = 2), " ", "MSE", signif(MSE.nsT.cF.s, digits = 2)), bty = "n", text.col = "red")
-```

### 2016-04-14 figure_2.Rmd
cambios 14/04/2016

--- 2016-04-14 figure_1.Rmd
@@
 
-nsF.theo.MSDi.s = c()
+nsT.theo.MSDi.s = c()
 exp.MSDi.s = c()
@@
   #Read experimental data.
-  analysis.fname.id <- paste(family, "_mut.model_", mut.model, "_naturalSelection_", "FALSE", "_R0_", R0, "_core_", "FALSE", "_K.analysis_", K.analysis, sep = "")
+  analysis.fname.id <- paste(family, "_mut.model_", mut.model, "_naturalSelection_", "TRUE", "_R0_", R0, "_core_", "FALSE", "_K.analysis_", K.analysis, sep = "")
 
@@
   #Read theoretical data#
-  m.nsF.cF.theo.smooth.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.smooth.dr.squarei.csv", sep = "")))
+  m.nsT.cF.theo.smooth.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.smooth.dr.squarei.csv", sep = "")))
 
-  nsF.cF.theo.MSDi.s = colMeans(m.nsF.cF.theo.smooth.dr.squarei, na.rm = T)
+  nsT.cF.theo.MSDi.s = colMeans(m.nsT.cF.theo.smooth.dr.squarei, na.rm = T)
 
@@
 
-  fit.nsF.cF.s = lm(cF.exp.MSDi.s ~ nsF.cF.theo.MSDi.s)
-  fit.nsF.cF.MSDi.s = fitted.values(fit.nsF.cF.s)
+  fit.nsT.cF.s = lm(cF.exp.MSDi.s ~ nsT.cF.theo.MSDi.s)
+  fit.nsT.cF.MSDi.s = fitted.values(fit.nsT.cF.s)
 
@@
 
-  nsF.theo.MSDi.s = c(nsF.theo.MSDi.s, fit.nsF.cF.MSDi.s)
+  nsT.theo.MSDi.s = c(nsT.theo.MSDi.s, fit.nsT.cF.MSDi.s)
 
@@
 
-R2.nsF.cF.s = cor(nsF.theo.MSDi.s, exp.MSDi.s) ^ 2
+R2.nsT.cF.s = cor(nsT.theo.MSDi.s, exp.MSDi.s) ^ 2
 
-MSE.nsF.cF.s = mean((nsF.theo.MSDi.s - exp.MSDi.s) ^ 2)
+MSE.nsT.cF.s = mean((nsT.theo.MSDi.s - exp.MSDi.s) ^ 2)
 
@@
 ```{r}
-plot(nsF.theo.MSDi.s, type = "l", xlab = "site", ylab = "Theoretical MSDi NS = F", ylim = c(0, 0.14))
+plot(nsT.theo.MSDi.s, type = "l", xlab = "site", ylab = "Theoretical MSDi NS = T", ylim = c(0, 0.14))
 ```
@@
 ```{r}
-plot(nsF.theo.MSDi.s, type = "l", xlab = "site", ylab = "Merge", ylim = c(0, 0.14))
+plot(nsT.theo.MSDi.s, type = "l", xlab = "site", ylab = "Merge", ylim = c(0, 0.14))
 points(exp.MSDi.s, col = "red", type = "l")
-legend("topleft", paste("R^2", round(R2.nsF.cF.s, digits = 2), " ", "MSE", signif(MSE.nsF.cF.s, digits = 4)), bty = "n", text.col = "red")
+legend("topleft", paste("R^2", round(R2.nsT.cF.s, digits = 2), " ", "MSE", signif(MSE.nsT.cF.s, digits = 4)), bty = "n", text.col = "red")
 ```

### 2016-04-25 MultipleReport.Rmd
cambios 25/04/2016

@@
 ```{r}
-# Load library.
-library(flux)
 
@@
 
-# Nmodes to analyze.
-nmodes1 = 10 
-nmodes2 = 25
-nmodes3 = 50
-
 # Read files and calculate measures.
-
 data.dir <- "DATA"
@@
 # Family.
-
 pdbid <- read.csv(file.path(data.dir, paste(family, "_dataset.csv", sep = "")))$pdbid
 n.exp = length(pdbid)
-
 n.sites.p.1 = read.csv(file.path(out.dir, paste(family, "_out_m.n.sites.p.ref.csv", sep = "")))$V1[1]
 m.n.sites.p.2 = read.csv(file.path(out.dir, paste(family, "_out_m.n.sites.p.2.csv", sep = "")))$V1
-
-n.core = read.csv(file.path(out.dir, paste(family, "_out_m.n.core.csv", sep = "")))$V1[1]
 m.n.aligned = read.csv(file.path(out.dir, paste(family, "_out_m.n.aligned.csv", sep = "")))$V1
-
 identity = read.csv(file.path(out.dir, paste(family, "_out_m.identity.csv", sep = "")))$V1
 
-### natural_selection = FALSE, core = FALSE ####
+# Read experimental.
+analysis.fname.id <- paste(family, "_R0_", R0, "_K.analysis_", K.analysis, sep = "")
 
-analysis.fname.id <- paste(family, "_mut.model_", mut.model, "_naturalSelection_", "FALSE", "_R0_", R0, "_core_", "FALSE", "_K.analysis_", K.analysis, sep = "")
+m.exp.Pn = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.exp.Pn.csv", sep = "")))[, 1:100]
+mean.exp.Pn = colMeans(m.exp.Pn)
 
-m.cF.exp.va = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.exp.va.csv", sep = "")))[, 1:nmodes3]
-i.m.cF.exp.va = 1/m.cF.exp.va
+exp.Pn.quantile1 = matrix(0, ncol = ncol(m.exp.Pn), nrow = 1)
+exp.Pn.quantile2 = matrix(0, ncol = ncol(m.exp.Pn), nrow = 1)
 
-m.cF.exp.Pn = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.exp.Pn.csv", sep = "")))[, 1:nmodes3]
-mean.cF.exp.Pn = colMeans(m.cF.exp.Pn)
-
-cF.exp.Pn.quantile1 = matrix(0, ncol = ncol(m.cF.exp.Pn), nrow = 1)
-cF.exp.Pn.quantile2 = matrix(0, ncol = ncol(m.cF.exp.Pn), nrow = 1)
-
-for (i in (1:ncol(m.cF.exp.Pn))){
-    cF.exp.Pn.quantiles = as.vector(quantile((m.cF.exp.Pn[, i]), probs = c(0.05, 0.95)))
-    cF.exp.Pn.quantile1[1, i] = cF.exp.Pn.quantiles[1]
-    cF.exp.Pn.quantile2[1, i] = cF.exp.Pn.quantiles[2]
+for (i in (1:ncol(m.exp.Pn))){
+    exp.Pn.quantiles = as.vector(quantile((m.exp.Pn[, i]), probs = c(0.05, 0.95)))
+    exp.Pn.quantile1[1, i] = exp.Pn.quantiles[1]
+    exp.Pn.quantile2[1, i] = exp.Pn.quantiles[2]
 }
 
-m.cF.exp.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.exp.dr.squarei.csv", sep = "")))
-m.cF.exp.smooth.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.exp.smooth.dr.squarei.csv", sep = "")))
-
-cF.exp.MSDi = colMeans(m.cF.exp.dr.squarei, na.rm = T )
-cF.exp.smooth.MSDi = colMeans(m.cF.exp.smooth.dr.squarei, na.rm = T )
-
-cF.exp.MSD = rowMeans(m.cF.exp.dr.squarei, na.rm = T)
-
-family.data <- data.frame(pdbid, nsites = m.n.sites.p.2, naligned = m.n.aligned, identity, MSD = cF.exp.MSD)
+m.exp.smooth.norm.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.exp.smooth.norm.dr.squarei.csv", sep = "")))
+exp.smooth.norm.MSDi = colMeans(m.exp.smooth.norm.dr.squarei, na.rm = T )
 
 ### Theoretical ###
+  mut.fname.id <- paste(family, "_R0_", R0, sep = "")
 
-m.nsF.cF.theo.va = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.va.csv", sep = "")))[, 1:nmodes3]
-i.m.nsF.cF.theo.va = 1/m.nsF.cF.theo.va
+m.theo.Pn = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.Pn.csv", sep = "")))[, 1:100]
+m.theo.smooth.norm.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.smooth.norm.dr.squarei.csv", sep = "")))
+prob.accept.mut.all.betas = read.csv(file.path(out.dir, paste(mut.fname.id, "_out_prob.accept.mut.all.betas.csv", sep = "")))
 
-m.nsF.cF.theo.Pn = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.Pn.csv", sep = "")))[, 1:nmodes3]
-n.mut = nrow(m.nsF.cF.theo.Pn)
+n.mut = nrow(m.theo.Pn)
 
-m.nsF.cF.theo.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.dr.squarei.csv", sep = "")))
-m.nsF.cF.theo.smooth.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.smooth.dr.squarei.csv", sep = "")))
-nsF.cF.theo.MSDi = colMeans(m.nsF.cF.theo.dr.squarei, na.rm = T)
-nsF.cF.theo.smooth.MSDi = colMeans(m.nsF.cF.theo.smooth.dr.squarei, na.rm = T)
+prob.accept.mut.beta.0.1 = prob.accept.mut.all.betas[1, ]
+prob.accept.mut.beta.0.5 = prob.accept.mut.all.betas[2, ]
+prob.accept.mut.beta.0.9 = prob.accept.mut.all.betas[3, ]
 
-nsF.cF.theo.MSD = rowMeans(m.nsF.cF.theo.dr.squarei, na.rm = T)
+mean.beta.0.theo.Pn = ColMeans(m.theo.Pn)
+mean.beta.0.1.theo.Pn = colSums((m.theo.Pn) * as.numeric(prob.accept.mut.beta.0.1))/ sum(prob.accept.mut.beta.0.1)
+mean.beta.0.5.theo.Pn = colSums(m.theo.Pn * as.numeric(prob.accept.mut.beta.0.5))/ sum(prob.accept.mut.beta.0.5)
+mean.beta.0.9.theo.Pn = colSums(m.theo.Pn * as.numeric(prob.accept.mut.beta.0.9))/ sum(prob.accept.mut.beta.0.9)
 
-nsF.cF.theo.MSD.group <- CalculateGroupsMeansQuantiles(cbind(nsF.cF.theo.MSD,nsF.cF.theo.MSD), n.exp, n.mut.p)
-mean.nsF.cF.theo.MSD.group <- nsF.cF.theo.MSD.group$mean.group[,1]
-
-### natural_selection = TRUE, core = FALSE ####
-
-analysis.fname.id <- paste(family, "_mut.model_", mut.model, "_naturalSelection_", "TRUE", "_R0_", R0, "_core_", "FALSE", "_K.analysis_", K.analysis, sep = "")
-
-m.nsT.cF.theo.va = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.va.csv", sep = "")))[, 1:nmodes3]
-i.m.nsT.cF.theo.va = 1/m.nsT.cF.theo.va
-
-m.nsT.cF.theo.Pn = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.Pn.csv", sep = "")))[, 1:nmodes3]
-n.mut = nrow(m.nsT.cF.theo.Pn)
-
-m.nsT.cF.theo.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.dr.squarei.csv", sep = "")))
-m.nsT.cF.theo.smooth.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.smooth.dr.squarei.csv", sep = "")))
-nsT.cF.theo.MSDi = colMeans(m.nsT.cF.theo.dr.squarei, na.rm = T)
-nsT.cF.theo.smooth.MSDi = colMeans(m.nsT.cF.theo.smooth.dr.squarei, na.rm = T)
-
-nsT.cF.theo.MSD = rowMeans(m.nsT.cF.theo.dr.squarei, na.rm = T)
-
-nsT.cF.theo.MSD.group <- CalculateGroupsMeansQuantiles(cbind(nsT.cF.theo.MSD,nsT.cF.theo.MSD), n.exp, n.mut.p)
-mean.nsT.cF.theo.MSD.group <- nsT.cF.theo.MSD.group$mean.group[,1]
-
+mean.beta.0.theo.smooth.MSDi = colMeans(m.theo.smooth.dr.squarei, na.rm = T)
+mean.beta.0.1.theo.smooth.MSDi = colSums(m.theo.smooth.dr.squarei * as.numeric(prob.accept.mut.beta.0.1), na.rm = T)/ sum(prob.accept.mut.beta.0.1, na.rm = T )
+mean.beta.0.5.theo.smooth.MSDi = colSums(m.theo.smooth.dr.squarei * as.numeric(prob.accept.mut.beta.0.5), na.rm = T)/ sum(prob.accept.mut.beta.0.5, na.rm = T)
+mean.beta.0.9.theo.smooth.MSDi = colSums(m.theo.smooth.dr.squarei * as.numeric(prob.accept.mut.beta.0.9), na.rm = T)/ sum(prob.accept.mut.beta.0.9, na.rm = T)
 ```
 
-## Conjuntos de proteinas
-
-### Conjunto teorico
-`r n.mut` mutantes de `r p.ref` (`r n.sites.p.1` sitios) simuladas con el modelo mutacional `r mut.model` con ANM *R0* = `r R0` y *Fmax* = 2 (solo para LFENM).
-
-Con seleccion natural (ns = T): Para seleccionar cuales sitios mutar, se utilizo el "stress model", mediante el cual se asignaron probabilidades de mutacion a cada sitio:
-
-prob.mut.i = 1 - (beta * CN.i).
-
-Luego, se selecciono para mutar, a los sitios con mayores probabilidades de mutacion. El numero de sitios seleccionados fue el numero de sitios mutados o con gaps en cada par de alineamientos
-
-Sin seleccion natural (ns = F): para cada par de proteínas se mutaron al azar la cantidad de sitios correspondientes a la identidad secuencial.
-
-### Conjunto experimental 
-`r n.exp` proteinas de la familia de `r family`. Las proteinas tienen un promedio de identidad secuencial de `r round(mean(identity))`%.
-
-La caracterizacion del conjunto experimental se muestra a continuacion:
-```{r}
-
-family.data
-```
-## Comparaciones
-
-### MSD
-```{r}
-
-layout(matrix(1:3, 1, 3, byrow = T))
-
-hist(cF.exp.MSD, main = "Experimental MSD", xlab = "MSD", col = "red")
-hist(nsF.cF.theo.MSD, main = "Theoretical MSD ns = F", xlab = "MSD", col = "grey")
-hist(nsT.cF.theo.MSD, main = "Theoretical MSD ns = T", xlab = "MSD", col = "grey")
-
-```
-
-### MSDi
-
-Los perfiles teoricos de MSDi y smooth.MSDi fueron fiteados con los perfiles exterimentales. Se compararon y se calcularon R^2 y MSE. 
+Los perfiles teoricos de  smooth.norm.MSDi fueron fiteados con los perfiles exterimentales. Se compararon y se calcularon R^2 y MSE. 
 ```{r}
@@
 
-fit.nsF.cF = lm(cF.exp.smooth.MSDi ~ nsF.cF.theo.smooth.MSDi)
-MSDi.fit.nsF.cF = fitted.values(fit.nsF.cF)
-R2.nsF.cF = cor(cF.exp.smooth.MSDi[!is.na(cF.exp.smooth.MSDi)], MSDi.fit.nsF.cF) ^ 2 
-MSE.nsF.cF = mean((MSDi.fit.nsF.cF - cF.exp.smooth.MSDi[!is.na(cF.exp.smooth.MSDi)]) ^ 2)
+fit.beta.0 = lm(exp.smooth.norm.MSDi ~ mean.beta.0.theo.smooth.MSDi )
+MSDi.fit.beta.0 = fitted.values(fit.beta.0)
+R2.beta.0 = cor(exp.smooth.norm.MSDi[!is.na(exp.smooth.norm.MSDi)], MSDi.fit.beta.0) ^ 2 
+MSE.beta.0 = mean((MSDi.fit.beta.0 - exp.smooth.norm.MSDi[!is.na(exp.smooth.norm.MSDi)]) ^ 2)
 
-keep.data = c(keep.data, R2.nsF.cF, MSE.nsF.cF)
+fit.beta.0.1 = lm(exp.smooth.norm.MSDi ~ mean.beta.0.1.theo.smooth.MSDi )
+MSDi.fit.beta.0.1 = fitted.values(fit.beta.0.1)
+R2.beta.0.1 = cor(exp.smooth.norm.MSDi[!is.na(exp.smooth.norm.MSDi)], MSDi.fit.beta.0.1) ^ 2 
+MSE.beta.0.1 = mean((MSDi.fit.beta.0.1 - exp.smooth.norm.MSDi[!is.na(exp.smooth.norm.MSDi)]) ^ 2)
 
-plot(MSDi.fit.nsF.cF, main = "smooth.MSDi ns = F", xlab = "site", ylab = "MSDi", ylim = c(0, max(cbind(MSDi.fit.nsF.cF, cF.exp.smooth.MSDi[!is.na(cF.exp.smooth.MSDi)])))) 
-points(cF.exp.smooth.MSDi[!is.na(cF.exp.smooth.MSDi)], col = "red")
+fit.beta.0.5 = lm(exp.smooth.norm.MSDi ~ mean.beta.0.5.theo.smooth.MSDi )
+MSDi.fit.beta.0.5 = fitted.values(fit.beta.0.5)
+R2.beta.0.5 = cor(exp.smooth.norm.MSDi[!is.na(exp.smooth.norm.MSDi)], MSDi.fit.beta.0.5) ^ 2 
+MSE.beta.0.5 = mean((MSDi.fit.beta.0.5 - exp.smooth.norm.MSDi[!is.na(exp.smooth.norm.MSDi)]) ^ 2)
 
-plot(MSDi.fit.nsF.cF, cF.exp.smooth.MSDi[!is.na(cF.exp.smooth.MSDi)], xlab = "MSDi.smooth teorico", ylab = "MSDi.smooth experimental", main = "ns = F c = F")
-abline(0, 1)
-legend("topleft", paste("R^2", round(R2.nsF.cF, digits = 2)), bty = "n", text.col = "red")
-legend("bottomright", paste("MSE", signif(MSE.nsF.cF, digits = T)), bty = "n", text.col = "red")
-
-fit.nsT.cF = lm(cF.exp.smooth.MSDi ~ nsT.cF.theo.smooth.MSDi)
-MSDi.fit.nsT.cF = fitted.values(fit.nsT.cF)
-R2.nsT.cF = cor(cF.exp.smooth.MSDi[!is.na(cF.exp.smooth.MSDi)], MSDi.fit.nsT.cF) ^ 2 
-MSE.nsT.cF = mean((MSDi.fit.nsT.cF - cF.exp.smooth.MSDi[!is.na(cF.exp.smooth.MSDi)]) ^ 2)
-
-keep.data = c(keep.data, R2.nsT.cF, MSE.nsT.cF)
-
-plot(MSDi.fit.nsT.cF, main = "smooth.MSDi ns = T", xlab = "site", ylab = "MSDi", ylim = c(0, max(cbind(MSDi.fit.nsT.cF, cF.exp.smooth.MSDi[!is.na(cF.exp.smooth.MSDi)])))) 
-points(cF.exp.smooth.MSDi[!is.na(cF.exp.smooth.MSDi)], col = "red")
-
-plot(MSDi.fit.nsT.cF, cF.exp.smooth.MSDi[!is.na(cF.exp.smooth.MSDi)], xlab = "MSDi.smooth teorico", ylab = "MSDi.smooth experimental", main = "ns = T c = F")
-abline(0, 1)
-legend("topleft", paste("R^2", round(R2.nsT.cF, digits = 2)), bty = "n", text.col = "red")
-legend("bottomright", paste("MSE", signif(MSE.nsT.cF, digits = 2)), bty = "n", text.col = "red")
+fit.beta.0.9 = lm(exp.smooth.norm.MSDi ~ mean.beta.0.9.theo.smooth.MSDi )
+MSDi.fit.beta.0.9 = fitted.values(fit.beta.0.9)
+R2.beta.0.9 = cor(exp.smooth.norm.MSDi[!is.na(exp.smooth.norm.MSDi)], MSDi.fit.beta.0.9) ^ 2 
+MSE.beta.0.9 = mean((MSDi.fit.beta.0.9 - exp.smooth.norm.MSDi[!is.na(exp.smooth.norm.MSDi)]) ^ 2)
 
@@
 
+```{r}
+lines(as.numeric(MSDi.fit.beta.0), type = "l", xlab = "site", ylab = "Theoretical MSDi BETA = 0", col = "red")
+
+lines(MSDi.fit.beta.0.1, type = "l", xlab = "site", ylab = "Theoretical MSDi BETA = 0.1", col = "red")
+
+lines(MSDi.fit.beta.0.5, type = "l", xlab = "site", ylab = "Theoretical MSDi BETA = 0.5", col = "blue")
+
+lines(MSDi.fit.beta.0.9, type = "l", xlab = "site", ylab = "Theoretical MSDi BETA = 0.9", col = "green")
+
+```
+
+```{r}
+plot(exp.smooth.norm.MSDi[!is.na(exp.smooth.norm.MSDi)], type = "l", xlab = "site", ylab = "Experimental")
+
+```
+
+```{r}
+plot(nsF.theo.MSDi.s, type = "l", xlab = "site", ylab = "Merge", ylim = c(0, 0.14))
+points(exp.MSDi.s, col = "red", type = "l")
+legend("topleft", paste("R^2", round(R2.nsF.cF.s, digits = 2), " ", "MSE", signif(MSE.nsF.cF.s, digits = 4)), bty = "n", text.col = "red")
 rojo: experimental
 negro: teorico
-
-```{r}
-# Write pdb files for MSDi.
-pdbs.fname <- file.path(data.dir, paste(family, "_coordinates.pdb", sep = "")) 
-pdb = ReadCA(pdbs.fname, exp.chain.p.ref)
-xyz.calpha = pdb$xyz.calpha
-
-MSDi.fit.nsF.cF.pdb <- vec2resno(as.vector(MSDi.fit.nsF.cF), sort(rep(1:ncol(xyz.calpha),3)))
-write.pdb(xyz = c(xyz.calpha) ,b = MSDi.fit.nsF.cF.pdb*100, file = file.path(out.dir, paste(p.ref, ".theo.nsF.pdb", sep = "")))
-
-MSDi.fit.nsT.cF.pdb <- vec2resno(as.vector(MSDi.fit.nsT.cF), sort(rep(1:ncol(xyz.calpha),3)))
-write.pdb(xyz = c(xyz.calpha) ,b = MSDi.fit.nsT.cF.pdb*100, file = file.path(out.dir, paste(p.ref, ".theo.nsT.pdb", sep = "")))
-
-cF.exp.smooth.MSDi.pdb <- vec2resno(as.vector(cF.exp.smooth.MSDi[!is.na(cF.exp.smooth.MSDi)]),sort(rep(1:ncol(xyz.calpha),3)))
-write.pdb(xyz = c(xyz.calpha) ,b = cF.exp.smooth.MSDi.pdb*100, file = file.path(out.dir, paste(p.ref, ".exp.pdb", sep = "")))
-
-```
 
@@
 ```{r}
-# Re-ordenate Pn.
-m.theo.index = matrix(ncol = 1, nrow = n.mut)
-for (P in (1:n.exp)) {
-  for (mut in (1:n.mut.p)) {
-    m.theo.index[(P - 1) * n.mut.p + mut, ] = ((mut - 1) * 10 + P)
-  }
-}
-m.nsF.cF.theo.Pn = m.nsF.cF.theo.Pn[as.vector(m.theo.index), ]
-m.nsT.cF.theo.Pn = m.nsT.cF.theo.Pn[as.vector(m.theo.index), ]
 
 # Calculate groups, means and quantiles.
-nsF.cF.theo.Pn.group = CalculateGroupsMeansQuantiles(m.nsF.cF.theo.Pn, n.mut.p, n.exp)
-mean.nsF.cF.theo.Pn.group = nsF.cF.theo.Pn.group$mean.mean.group
-nsF.cF.theo.Pn.group.quantile1 = nsF.cF.theo.Pn.group$mean.quantile1.group
-nsF.cF.theo.Pn.group.quantile2 = nsF.cF.theo.Pn.group$mean.quantile2.group
+theo.Pn.group = CalculateGroupsMeansQuantiles(theo.Pn, n.mut.p, n.exp)
+mean.theo.Pn.group = theo.Pn.group$mean.mean.group
+theo.Pn.group.quantile1 = theo.Pn.group$mean.quantile1.group
+theo.Pn.group.quantile2 = theo.Pn.group$mean.quantile2.group
 
-nsT.cF.theo.Pn.group = CalculateGroupsMeansQuantiles(m.nsT.cF.theo.Pn, n.mut.p, n.exp)
-mean.nsT.cF.theo.Pn.group = nsT.cF.theo.Pn.group$mean.mean.group
-nsT.cF.theo.Pn.group.quantile1 = nsT.cF.theo.Pn.group$mean.quantile1.group
-nsT.cF.theo.Pn.group.quantile2 = nsT.cF.theo.Pn.group$mean.quantile2.group
 ```
@@
 ```
-
-```{r}
-# Calculate rho.
-nsF.cF.rho.t.1 <- matrix(0, nrow = n.mut, ncol = 1)
-nsF.cF.rho.t.3 <- matrix(0, nrow = n.mut, ncol = 1)
-for (i in (1:n.mut)) {
-  nsF.cF.rho.t.1[i, ] <- cor(as.numeric(m.nsF.cF.theo.Pn[i, 1:nmodes1] * m.nsF.cF.theo.va[i, 1:nmodes1]), as.numeric(i.m.nsF.cF.theo.va[i, 1:nmodes1]), method = "pearson")
-
-  nsF.cF.rho.t.3[i, ] <- cor(as.numeric(m.nsF.cF.theo.Pn[i, 1:nmodes3] * m.nsF.cF.theo.va[i, 1:nmodes3]), as.numeric(i.m.nsF.cF.theo.va[i, 1:nmodes3]), method = "pearson")	
-}
-
-nsT.cF.rho.t.1 <- matrix(0, nrow = n.mut, ncol = 1)
-nsT.cF.rho.t.3 <- matrix(0, nrow = n.mut, ncol = 1)
-for (i in (1:n.mut)) {
-  nsT.cF.rho.t.1[i, ] <- cor(as.numeric(m.nsT.cF.theo.Pn[i, 1:nmodes1] * m.nsT.cF.theo.va[i, 1:nmodes1]), as.numeric(i.m.nsT.cF.theo.va[i, 1:nmodes1]), method = "pearson")	
-  nsT.cF.rho.t.3[i, ] <- cor(as.numeric(m.nsT.cF.theo.Pn[i, 1:nmodes3] * m.nsT.cF.theo.va[i, 1:nmodes3]), as.numeric(i.m.nsT.cF.theo.va[i, 1:nmodes3]), method = "pearson")	
-}
-
-cF.rho.e.1 <- matrix(0, nrow = n.exp, ncol = 1)
-cF.rho.e.3 <- matrix(0, nrow = n.exp, ncol = 1) 
-for (i in (1:n.exp)) {
-  cF.rho.e.1[i, ] <- cor(as.numeric(m.cF.exp.Pn[i, 1:nmodes1] * m.cF.exp.va[i, 1:nmodes1]), as.numeric(i.m.cF.exp.va[i, 1:nmodes1]), method = "pearson")
-  cF.rho.e.3[i, ] <- cor(as.numeric(m.cF.exp.Pn[i, 1:nmodes3] * m.cF.exp.va[i, 1:nmodes3]), as.numeric(i.m.cF.exp.va[i, 1:nmodes3]), method = "pearson")
-}
-
-```
-
-### RHO
-Las distribuciones de *rho* para cada conjunto se muestran a continuacion
-
-```{r}
-layout(matrix(1:2, 1, 2, byrow = T))
-plot(density(nsF.cF.rho.t.1), ylab = "Frecuencia", xlab = "rho", main = "Histograma rho 10 modos ns = F")
-points(x = c(cF.rho.e.1), y = rep(0, n.exp), col = "red")
-plot(density(nsT.cF.rho.t.1), ylab = "Frecuencia", xlab = "rho", main = "Histograma rho 10 modos ns = T")
-points(x = c(cF.rho.e.1), y = rep(0, n.exp), col = "red")
-```
-
-```{r}
-layout(matrix(1:2, 1, 2, byrow = T))
-plot(density(nsF.cF.rho.t.3), ylab = "Frecuencia", xlab = "rho", main = "Histograma rho 50 modos ns = F")
-points(x = c(cF.rho.e.3), y = rep(0, n.exp), col = "red")
-plot(density(nsT.cF.rho.t.3), ylab = "Frecuencia", xlab = "rho", main = "Histograma rho 50 modos ns = T")
-points(x = c(cF.rho.e.3), y = rep(0, n.exp), col = "red")
-```

### 2016-04-25 MultipleReport2.Rmd
cambios 25/04/2016

---
title: "Estudio variabilidad estructural proteica"
output: html_document
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(warning = FALSE, echo = FALSE, message = FALSE)
```

```{r}
# Load library.
library(flux)

# Source functions.
source("FUNCTIONS/CalculateGroupsMeansQuantiles.R")

# Read files and calculate measures.
data.dir <- "DATA"
out.dir <- "OUT"

# Family.

pdbid <- read.csv(file.path(data.dir, paste(family, "_dataset.csv", sep = "")))$pdbid
n.exp = length(pdbid)

n.sites.p.1 = read.csv(file.path(out.dir, paste(family, "_out_m.n.sites.p.ref.csv", sep = "")))$V1[1]
m.n.sites.p.2 = read.csv(file.path(out.dir, paste(family, "_out_m.n.sites.p.2.csv", sep = "")))$V1

n.core = read.csv(file.path(out.dir, paste(family, "_out_m.n.core.csv", sep = "")))$V1[1]
m.n.aligned = read.csv(file.path(out.dir, paste(family, "_out_m.n.aligned.csv", sep = "")))$V1

identity = read.csv(file.path(out.dir, paste(family, "_out_m.identity.csv", sep = "")))$V1

# Read experimental.
analysis.fname.id <- paste(family, "_R0_", R0, "_K.analysis_", K.analysis, sep = "")

m.exp.Pn = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.exp.Pn.csv", sep = "")))[, 1:100]
mean.exp.Pn = colMeans(m.exp.Pn)

exp.Pn.quantile1 = matrix(0, ncol = ncol(m.exp.Pn), nrow = 1)
exp.Pn.quantile2 = matrix(0, ncol = ncol(m.exp.Pn), nrow = 1)

for (i in (1:ncol(m.exp.Pn))){
    exp.Pn.quantiles = as.vector(quantile((m.exp.Pn[, i]), probs = c(0.05, 0.95)))
    exp.Pn.quantile1[1, i] = exp.Pn.quantiles[1]
    exp.Pn.quantile2[1, i] = exp.Pn.quantiles[2]
}

m.exp.smooth.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.exp.smooth.dr.squarei.csv", sep = "")))
exp.smooth.MSDi = colMeans(m.exp.smooth.dr.squarei, na.rm = T )

### Theoretical ###

m.theo.Pn = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.Pn.csv", sep = "")))[, 1:nmodes3]
m.theo.smooth.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.smooth.dr.squarei.csv", sep = "")))
prob.accept.mut.all.betas = read.csv(file.path(out.dir, paste(mut.fname.id, "_out_prob.accept.mut.all.betas.csv", sep = "")), row.names = FALSE)

n.mut = nrow(m.nsF.cF.theo.Pn)

prob.accept.mut.beta.0.1 = prob.accept.mut.all.betas[1, ]
prob.accept.mut.beta.0.5 = prob.accept.mut.all.betas[2, ]
prob.accept.mut.beta.0.9 = prob.accept.mut.all.betas[3, ]

mean.beta.0.theo.Pn = ColMeans(m.theo.Pn)
mean.beta.0.1.theo.Pn = colSums(m.theo.Pn * prob.accept.mut.beta.0.1)/ sum(prob.accept.mut.beta.0.1)
mean.beta.0.5.theo.Pn = colSums(m.theo.Pn * prob.accept.mut.beta.0.5)/ sum(prob.accept.mut.beta.0.5)
mean.beta.0.9.theo.Pn = colSums(m.theo.Pn * prob.accept.mut.beta.0.9)/ sum(prob.accept.mut.beta.0.9)

mean.beta.0.theo.smooth.dr.squarei = ColMeans(m.theo.smooth.dr.squarei)
mean.beta.0.1.theo.smooth.dr.squarei = colSums(m.theo.smooth.dr.squarei * prob.accept.mut.beta.0.1)/ sum(prob.accept.mut.beta.0.1)
mean.beta.0.5.theo.smooth.dr.squarei = colSums(m.theo.smooth.dr.squarei * prob.accept.mut.beta.0.5)/ sum(prob.accept.mut.beta.0.5)
mean.beta.0.9.theo.smooth.dr.squarei = colSums(m.theo.smooth.dr.squarei * prob.accept.mut.beta.0.9)/ sum(prob.accept.mut.beta.0.9)
```

## Conjuntos de proteinas

### Conjunto teorico
`r n.mut` mutantes de `r p.ref` (`r n.sites.p.1` sitios) simuladas con el modelo mutacional `r mut.model` con ANM *R0* = `r R0` y *Fmax* = 2 (solo para LFENM).

Con seleccion natural (ns = T): Para seleccionar cuales sitios mutar, se utilizo el "stress model", mediante el cual se asignaron probabilidades de mutacion a cada sitio:

prob.mut.i = 1 - (beta * CN.i).

Luego, se selecciono para mutar, a los sitios con mayores probabilidades de mutacion. El numero de sitios seleccionados fue el numero de sitios mutados o con gaps en cada par de alineamientos

Sin seleccion natural (ns = F): para cada par de proteínas se mutaron al azar la cantidad de sitios correspondientes a la identidad secuencial.

### Conjunto experimental 
`r n.exp` proteinas de la familia de `r family`. Las proteinas tienen un promedio de identidad secuencial de `r round(mean(identity))`%.

La caracterizacion del conjunto experimental se muestra a continuacion:
```{r}

family.data
```
## Comparaciones

### MSDi

Los perfiles teoricos de  smooth.MSDi fueron fiteados con los perfiles exterimentales. Se compararon y se calcularon R^2 y MSE. 
```{r}
keep.data = c()
```

```{r}
layout(matrix(1:4, 2, 2, byrow = F))

fit.nsF.cF = lm(cF.exp.smooth.MSDi ~ theo.smooth.MSDi)
MSDi.fit.nsF.cF = fitted.values(fit.nsF.cF)
R2.nsF.cF = cor(cF.exp.smooth.MSDi[!is.na(cF.exp.smooth.MSDi)], MSDi.fit.nsF.cF) ^ 2 
MSE.nsF.cF = mean((MSDi.fit.nsF.cF - cF.exp.smooth.MSDi[!is.na(cF.exp.smooth.MSDi)]) ^ 2)

keep.data = c(keep.data, R2.nsF.cF, MSE.nsF.cF)

plot(MSDi.fit.nsF.cF, main = "smooth.MSDi ns = F", xlab = "site", ylab = "MSDi", ylim = c(0, max(cbind(MSDi.fit.nsF.cF, cF.exp.smooth.MSDi[!is.na(cF.exp.smooth.MSDi)])))) 
points(cF.exp.smooth.MSDi[!is.na(cF.exp.smooth.MSDi)], col = "red")

plot(MSDi.fit.nsF.cF, cF.exp.smooth.MSDi[!is.na(cF.exp.smooth.MSDi)], xlab = "MSDi.smooth teorico", ylab = "MSDi.smooth experimental", main = "ns = F c = F")
abline(0, 1)
legend("topleft", paste("R^2", round(R2.nsF.cF, digits = 2)), bty = "n", text.col = "red")
legend("bottomright", paste("MSE", signif(MSE.nsF.cF, digits = T)), bty = "n", text.col = "red")

fit.nsT.cF = lm(cF.exp.smooth.MSDi ~ nsT.cF.theo.smooth.MSDi)
MSDi.fit.nsT.cF = fitted.values(fit.nsT.cF)
R2.nsT.cF = cor(cF.exp.smooth.MSDi[!is.na(cF.exp.smooth.MSDi)], MSDi.fit.nsT.cF) ^ 2 
MSE.nsT.cF = mean((MSDi.fit.nsT.cF - cF.exp.smooth.MSDi[!is.na(cF.exp.smooth.MSDi)]) ^ 2)

keep.data = c(keep.data, R2.nsT.cF, MSE.nsT.cF)

plot(MSDi.fit.nsT.cF, main = "smooth.MSDi ns = T", xlab = "site", ylab = "MSDi", ylim = c(0, max(cbind(MSDi.fit.nsT.cF, cF.exp.smooth.MSDi[!is.na(cF.exp.smooth.MSDi)])))) 
points(cF.exp.smooth.MSDi[!is.na(cF.exp.smooth.MSDi)], col = "red")

plot(MSDi.fit.nsT.cF, cF.exp.smooth.MSDi[!is.na(cF.exp.smooth.MSDi)], xlab = "MSDi.smooth teorico", ylab = "MSDi.smooth experimental", main = "ns = T c = F")
abline(0, 1)
legend("topleft", paste("R^2", round(R2.nsT.cF, digits = 2)), bty = "n", text.col = "red")
legend("bottomright", paste("MSE", signif(MSE.nsT.cF, digits = 2)), bty = "n", text.col = "red")

```

rojo: experimental
negro: teorico

```{r}
# Write pdb files for MSDi.
pdbs.fname <- file.path(data.dir, paste(family, "_coordinates.pdb", sep = "")) 
pdb = ReadCA(pdbs.fname, exp.chain.p.ref)
xyz.calpha = pdb$xyz.calpha

MSDi.fit.nsF.cF.pdb <- vec2resno(as.vector(MSDi.fit.nsF.cF), sort(rep(1:ncol(xyz.calpha),3)))
write.pdb(xyz = c(xyz.calpha) ,b = MSDi.fit.nsF.cF.pdb*100, file = file.path(out.dir, paste(p.ref, ".theo.nsF.pdb", sep = "")))

MSDi.fit.nsT.cF.pdb <- vec2resno(as.vector(MSDi.fit.nsT.cF), sort(rep(1:ncol(xyz.calpha),3)))
write.pdb(xyz = c(xyz.calpha) ,b = MSDi.fit.nsT.cF.pdb*100, file = file.path(out.dir, paste(p.ref, ".theo.nsT.pdb", sep = "")))

cF.exp.smooth.MSDi.pdb <- vec2resno(as.vector(cF.exp.smooth.MSDi[!is.na(cF.exp.smooth.MSDi)]),sort(rep(1:ncol(xyz.calpha),3)))
write.pdb(xyz = c(xyz.calpha) ,b = cF.exp.smooth.MSDi.pdb*100, file = file.path(out.dir, paste(p.ref, ".exp.pdb", sep = "")))

```

## Pn y Qn
Las distribuciones de *Pn* y *Qn* de los conjuntos son las siguientes:

```{r}
# Re-ordenate Pn.
m.theo.index = matrix(ncol = 1, nrow = n.mut)
for (P in (1:n.exp)) {
  for (mut in (1:n.mut.p)) {
    m.theo.index[(P - 1) * n.mut.p + mut, ] = ((mut - 1) * 10 + P)
  }
}
m.nsF.cF.theo.Pn = m.nsF.cF.theo.Pn[as.vector(m.theo.index), ]
m.nsT.cF.theo.Pn = m.nsT.cF.theo.Pn[as.vector(m.theo.index), ]

# Calculate groups, means and quantiles.
nsF.cF.theo.Pn.group = CalculateGroupsMeansQuantiles(m.nsF.cF.theo.Pn, n.mut.p, n.exp)
mean.nsF.cF.theo.Pn.group = nsF.cF.theo.Pn.group$mean.mean.group
nsF.cF.theo.Pn.group.quantile1 = nsF.cF.theo.Pn.group$mean.quantile1.group
nsF.cF.theo.Pn.group.quantile2 = nsF.cF.theo.Pn.group$mean.quantile2.group

nsT.cF.theo.Pn.group = CalculateGroupsMeansQuantiles(m.nsT.cF.theo.Pn, n.mut.p, n.exp)
mean.nsT.cF.theo.Pn.group = nsT.cF.theo.Pn.group$mean.mean.group
nsT.cF.theo.Pn.group.quantile1 = nsT.cF.theo.Pn.group$mean.quantile1.group
nsT.cF.theo.Pn.group.quantile2 = nsT.cF.theo.Pn.group$mean.quantile2.group
```

```{r}

# Graphics.

layout(matrix(1:2, 1, 2, byrow = T))

plot(mean.nsF.cF.theo.Pn.group, 
     main = "Pn promedio ns = F", 
     xlab = "nmodo",
     ylab = "Pn",
     ylim = c(0, max(c(nsF.cF.theo.Pn.group.quantile2, mean.cF.exp.Pn))))
lines(nsF.cF.theo.Pn.group.quantile1)
lines(nsF.cF.theo.Pn.group.quantile2)
points(mean.cF.exp.Pn, col = "red")
lines(as.vector(cF.exp.Pn.quantile1), col = "red")
lines(as.vector(cF.exp.Pn.quantile2), col = "red")

plot(mean.nsT.cF.theo.Pn.group, 
     main = "Pn promedio ns = T", 
     xlab = "nmodo",
     ylab = "Pn",
     ylim = c(0, max(c(nsT.cF.theo.Pn.group.quantile2, mean.cF.exp.Pn))))
lines(nsT.cF.theo.Pn.group.quantile1)
lines(nsT.cF.theo.Pn.group.quantile2)
points(mean.cF.exp.Pn, col = "red")
lines(as.vector(cF.exp.Pn.quantile1), col = "red")
lines(as.vector(cF.exp.Pn.quantile2), col = "red")

```

*Negro*: Puntos: promedio de promedios teorico. Lineas: promedio de cuantiles 0.05 y 0.95 de `r n.mut.p` grupos de `r n.exp` mutantes teoricas.
*Rojo*: Experimental. Puntos: promedio. Lineas: cuantiles 0.05 y 0.95.

Posteriormente, los perfiles de Pn teoricos fueron fiteados con los perfiles exterimentales. Se compararon y se calcularon R^2 y MSE.

```{r}
layout(matrix(1:2, 1, 2, byrow = T))

fit.nsF.cF = lm(mean.cF.exp.Pn ~ mean.nsF.cF.theo.Pn.group)
Pn.fit.nsF.cF = fitted.values(fit.nsF.cF)
R2.nsF.cF = cor(mean.cF.exp.Pn, Pn.fit.nsF.cF) ^ 2 
MSE.nsF.cF = mean((Pn.fit.nsF.cF - mean.cF.exp.Pn) ^ 2)
plot(Pn.fit.nsF.cF, mean.cF.exp.Pn, xlab = "Pn teorico", ylab = "Pn experimental", main = "ns = F c = F")
abline(0, 1)
legend("topleft", paste("R^2", round(R2.nsF.cF, digits = 2)), bty = "n", text.col = "red")
legend("bottomright", paste("MSE", signif(MSE.nsF.cF, digits = 2)), bty = "n", text.col = "red")

keep.data = c(keep.data, R2.nsF.cF, MSE.nsF.cF)

fit.nsT.cF = lm(mean.cF.exp.Pn ~ mean.nsT.cF.theo.Pn.group)
Pn.fit.nsT.cF = fitted.values(fit.nsT.cF)
R2.nsT.cF = cor(mean.cF.exp.Pn, Pn.fit.nsT.cF) ^ 2 
MSE.nsT.cF = mean((Pn.fit.nsT.cF - mean.cF.exp.Pn) ^ 2)
plot(Pn.fit.nsT.cF, mean.cF.exp.Pn, xlab = "Pn teorico", ylab = "Pn experimental", main = "ns = T c = F")
abline(0, 1)
legend("topleft", paste("R^2", round(R2.nsT.cF, digits = 2)), bty = "n", text.col = "red")
legend("bottomright", paste("MSE", signif(MSE.nsT.cF, digits = 2)), bty = "n", text.col = "red")

keep.data = c(keep.data, R2.nsT.cF, MSE.nsT.cF)

```

```{r}
# Calculate rho.
nsF.cF.rho.t.1 <- matrix(0, nrow = n.mut, ncol = 1)
nsF.cF.rho.t.3 <- matrix(0, nrow = n.mut, ncol = 1)
for (i in (1:n.mut)) {
  nsF.cF.rho.t.1[i, ] <- cor(as.numeric(m.nsF.cF.theo.Pn[i, 1:nmodes1] * m.nsF.cF.theo.va[i, 1:nmodes1]), as.numeric(i.m.nsF.cF.theo.va[i, 1:nmodes1]), method = "pearson")

  nsF.cF.rho.t.3[i, ] <- cor(as.numeric(m.nsF.cF.theo.Pn[i, 1:nmodes3] * m.nsF.cF.theo.va[i, 1:nmodes3]), as.numeric(i.m.nsF.cF.theo.va[i, 1:nmodes3]), method = "pearson")	
}

nsT.cF.rho.t.1 <- matrix(0, nrow = n.mut, ncol = 1)
nsT.cF.rho.t.3 <- matrix(0, nrow = n.mut, ncol = 1)
for (i in (1:n.mut)) {
  nsT.cF.rho.t.1[i, ] <- cor(as.numeric(m.nsT.cF.theo.Pn[i, 1:nmodes1] * m.nsT.cF.theo.va[i, 1:nmodes1]), as.numeric(i.m.nsT.cF.theo.va[i, 1:nmodes1]), method = "pearson")	
  nsT.cF.rho.t.3[i, ] <- cor(as.numeric(m.nsT.cF.theo.Pn[i, 1:nmodes3] * m.nsT.cF.theo.va[i, 1:nmodes3]), as.numeric(i.m.nsT.cF.theo.va[i, 1:nmodes3]), method = "pearson")	
}

cF.rho.e.1 <- matrix(0, nrow = n.exp, ncol = 1)
cF.rho.e.3 <- matrix(0, nrow = n.exp, ncol = 1) 
for (i in (1:n.exp)) {
  cF.rho.e.1[i, ] <- cor(as.numeric(m.cF.exp.Pn[i, 1:nmodes1] * m.cF.exp.va[i, 1:nmodes1]), as.numeric(i.m.cF.exp.va[i, 1:nmodes1]), method = "pearson")
  cF.rho.e.3[i, ] <- cor(as.numeric(m.cF.exp.Pn[i, 1:nmodes3] * m.cF.exp.va[i, 1:nmodes3]), as.numeric(i.m.cF.exp.va[i, 1:nmodes3]), method = "pearson")
}

```

### RHO
Las distribuciones de *rho* para cada conjunto se muestran a continuacion

```{r}
layout(matrix(1:2, 1, 2, byrow = T))
plot(density(nsF.cF.rho.t.1), ylab = "Frecuencia", xlab = "rho", main = "Histograma rho 10 modos ns = F")
points(x = c(cF.rho.e.1), y = rep(0, n.exp), col = "red")
plot(density(nsT.cF.rho.t.1), ylab = "Frecuencia", xlab = "rho", main = "Histograma rho 10 modos ns = T")
points(x = c(cF.rho.e.1), y = rep(0, n.exp), col = "red")
```

```{r}
layout(matrix(1:2, 1, 2, byrow = T))
plot(density(nsF.cF.rho.t.3), ylab = "Frecuencia", xlab = "rho", main = "Histograma rho 50 modos ns = F")
points(x = c(cF.rho.e.3), y = rep(0, n.exp), col = "red")
plot(density(nsT.cF.rho.t.3), ylab = "Frecuencia", xlab = "rho", main = "Histograma rho 50 modos ns = T")
points(x = c(cF.rho.e.3), y = rep(0, n.exp), col = "red")
```

### 2016-04-25 FUNCTIONS/AnalyzeExperimentalTheoretical.R

@@ -1,22 +1,25 @@
+# Description:
+#
 # This function analyzes experimental and theoretical data calculating measures of variability in cartesian coordinates
-# and projected on normal modes of p.ref. 
+# and projected onto normal modes of p.ref. 
 # 
+# Usage:
+#
+# AnalyzeExperimentalTheoretical <- function(family, chain.p.ref, n.mut.p, R0,  rotate = TRUE/FALSE,
+# heme = TRUE/FALSE, K.analysis, data.dir, out.dir, mut.fname.id,  analysis.fname.id, TOLERANCE)
+#
 #  Args:
 #    family: the family of the protein to mutate. It can be "globins", "serinProteases", 
 #    "snakesToxin", "sh3", "fabp", "rrm", "phoslip" or "cys".
-#    exp.chain.p.ref: the chain of p.ref in the pdb file obtained from Homstrad.
+#    chain.p.ref: the chain of p.ref in the pdb file obtained from Homstrad.
 #    n.mut.p: the number of mutants to generate for each member of the family. For example, if the family has 20 
 #    members, the program generates n.mut.p x 20 mutants.
-#    R0: the cut-off for the "ANM" (Anisotropic Network Model) that represents the proteins.
+#    R0: the cut-off for the ANM ("Anisotropic Network Model") that represents the proteins.
 #    rotate: it can be "TRUE" or "FALSE". If it is "TRUE", r.p.2 is rotaded in order to minimize RMSD with r.p.ref.
-#    core: it can be "TRUE" or "FALSE". If it is "TRUE", the program only considers the conserved core of 
-#    the alignment. If it is "FALSE", the program analyzes the whole alignment.
 #    heme: argument for globins. It can be "TRUE" or "FALSE". If it is "TRUE", the program considers the heme group. 
-#    natural.selection: It can be "TRUE" or "FALSE". If it is "TRUE" the mutants are calculated considering natural 
-#    selection. If it is "FALSE" the mutants are calculated in a random manner.
 #    K.analysis: It can be "K" or "Keff". For "K" or "Keff", the analysis is based on normal modes of "K" or "Keff"
 #    respectibly.
[…]

### 2016-05-01 AllFamilys.Rmd
cambios 01/05/2016

--- 2016-04-09 AllFamilys.Rmd
@@
 
-# Create matrixes.
-nsF.theo.MSDi = c()
-nsT.theo.MSDi = c()
-nsF.theo.MSDi.s = c()
-nsT.theo.MSDi.s = c()
-
-exp.MSDi = c()
-exp.MSDi.s = c()
+# Create vectors to keep data.
+v.theo.MSDi.s.n = c()
+v.exp.MSDi.s.n = c()
 
@@
   family <- as.character(input$family)[a]
-  mut.model = input$mut.model[a]
   R0 = input$R0[a]
@@
   #Read experimental data.
-  analysis.fname.id <- paste(family, "_mut.model_", mut.model, "_naturalSelection_", "FALSE", "_R0_", R0, "_core_", "FALSE", "_K.analysis_", K.analysis, sep = "")
+  analysis.fname.id <- paste(family, "_R0_", R0,  "_beta_", beta, "_K.analysis_", K.analysis, sep = "")
 
-  m.cF.exp.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.exp.dr.squarei.csv", sep = "")))
-  m.cF.exp.smooth.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.exp.smooth.dr.squarei.csv", sep = "")))
+  m.exp.smooth.norm.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.exp.smooth.norm.dr.squarei.csv", sep = "")))
 
-  cF.exp.MSDi = colMeans(m.cF.exp.dr.squarei, na.rm = T )
-  cF.exp.MSDi.s = colMeans(m.cF.exp.smooth.dr.squarei, na.rm = T )
+ exp.MSDi.s.n = colMeans(m.exp.smooth.norm.dr.squarei, na.rm = T )
 
-  #Read theoretical data#
+  # Read theoretical data#
+  m.theo.smooth.norm.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.smooth.norm.dr.squarei.csv", sep = "")))
 
-  # natural selection (ns) = F.
-  m.nsF.cF.theo.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.dr.squarei.csv", sep = "")))
-  m.nsF.cF.theo.smooth.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.smooth.dr.squarei.csv", sep = "")))
-
-  nsF.cF.theo.MSDi = colMeans(m.nsF.cF.theo.dr.squarei, na.rm = T)
-  nsF.cF.theo.MSDi.s = colMeans(m.nsF.cF.theo.smooth.dr.squarei, na.rm = T)
-
-  # natural selection (ns) = T.
-  analysis.fname.id <- paste(family, "_mut.model_", mut.model, "_naturalSelection_", "TRUE", "_R0_", R0, "_core_", "FALSE", "_K.analysis_", K.analysis, sep = "")
-
-  m.nsT.cF.theo.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.dr.squarei.csv", sep = "")))
-  m.nsT.cF.theo.smooth.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.smooth.dr.squarei.csv", sep = "")))
-
-  nsT.cF.theo.MSDi = colMeans(m.nsT.cF.theo.dr.squarei, na.rm = T)
-  nsT.cF.theo.MSDi.s = colMeans(m.nsT.cF.theo.smooth.dr.squarei, na.rm = T)
+ theo.MSDi.s.n = colMeans(m.theo.smooth.norm.dr.squarei, na.rm = T)
 
   ## Fit theoretical data with experimental data.
-  fit.nsF.cF = lm(cF.exp.MSDi ~ nsF.cF.theo.MSDi)
-  fit.nsF.cF.MSDi = fitted.values(fit.nsF.cF)
 
-  fit.nsT.cF = lm(cF.exp.MSDi ~ nsT.cF.theo.MSDi)
-  fit.nsT.cF.MSDi = fitted.values(fit.nsT.cF)
-
-  fit.nsF.cF.s = lm(cF.exp.MSDi.s ~ nsF.cF.theo.MSDi.s)
-  fit.nsF.cF.MSDi.s = fitted.values(fit.nsF.cF.s)
-
-  fit.nsT.cF.s = lm(cF.exp.MSDi.s ~ nsT.cF.theo.MSDi.s)
-  fit.nsT.cF.MSDi.s = fitted.values(fit.nsT.cF.s)
+  fit.s.n = lm(exp.MSDi.s.n ~ theo.MSDi.s.n)
+  fit.MSDi.s.n = fitted.values(fit.s.n)
 
   # Concatenate information.
-  nsF.theo.MSDi = c(nsF.theo.MSDi, fit.nsF.cF.MSDi)
-  nsT.theo.MSDi = c(nsT.theo.MSDi, fit.nsT.cF.MSDi)
-  nsF.theo.MSDi.s = c(nsF.theo.MSDi.s, fit.nsF.cF.MSDi.s)
-  nsT.theo.MSDi.s = c(nsT.theo.MSDi.s, fit.nsT.cF.MSDi.s)
+  v.theo.MSDi.s.n = c(v.theo.MSDi.s.n, fit.MSDi.s.n)
 
-  cF.exp.MSDi = cF.exp.MSDi[!is.na(cF.exp.MSDi)]
-  cF.exp.MSDi.s = cF.exp.MSDi.s[!is.na(cF.exp.MSDi.s)]
-
-  exp.MSDi = c(exp.MSDi, cF.exp.MSDi)
-  exp.MSDi.s = c(exp.MSDi.s, cF.exp.MSDi.s)
+  exp.MSDi.s.n = exp.MSDi.s.n[!is.na(exp.MSDi.s.n)]
+  v.exp.MSDi.s.n = c(v.exp.MSDi.s.n, exp.MSDi.s.n)
 }
@@
 # Caluclate measures.
-R2.nsF.cF = cor(nsF.theo.MSDi, exp.MSDi) ^ 2 
-R2.nsT.cF = cor(nsT.theo.MSDi, exp.MSDi) ^ 2
-
-R2.nsF.cF.s = cor(nsF.theo.MSDi.s, exp.MSDi.s) ^ 2
-R2.nsT.cF.s = cor(nsT.theo.MSDi.s, exp.MSDi.s) ^ 2
-
-MSE.nsF.cF = mean((nsF.theo.MSDi - exp.MSDi) ^ 2)
-MSE.nsT.cF = mean((nsT.theo.MSDi - exp.MSDi) ^ 2)
-
-MSE.nsF.cF.s = mean((nsF.theo.MSDi.s - exp.MSDi.s) ^ 2)
-MSE.nsT.cF.s = mean((nsT.theo.MSDi.s - exp.MSDi.s) ^ 2)
+R2.s.n = cor(theo.MSDi.s.n, exp.MSDi.s.n) ^ 2  
+MSE.s.n = mean((theo.MSDi.s.n - exp.MSDi.s.n) ^ 2)
 
@@
 
-```{r, include = F}
-layout(matrix(1:3, 3, 1, byrow = F))
-
-plot(nsF.theo.MSDi, type = "l", xlab = "sitio", ylab = "Theoretical")
-plot(exp.MSDi, type = "l", col = "red", ylab = "Experimental")
-plot(nsF.theo.MSDi, type = "l", ylab = "both")
-points(exp.MSDi, col = "red", type = "l")
-legend("topleft", paste("R^2", round(R2.nsF.cF, digits = 2)), bty = "n", text.col = "red")
-
-```
-
-```{r, include = F}
-layout(matrix(1:3, 3, 1, byrow = F)) 
-plot(nsT.theo.MSDi, type="l", xlab = "sitio", ylab = "Theoretical")
-plot(exp.MSDi, type="l", col ="red", ylab = "Experimental")
-plot(nsT.theo.MSDi, type="l", ylab = "both")
-points(exp.MSDi, col = "red", type="l")
-legend("topleft", paste("R^2", round(R2.nsT.cF, digits = 2)), bty = "n", text.col = "red")
-```
-All families fitted smooth normalized MSD profiles
-
-Without natural selection (ns = F)
+All families fitted smooth and normalized MSD profiles
 
 ```{r}
-plot(nsF.theo.MSDi.s, type = "l", xlab = "sitio", ylab = "Theoretical ns = F", ylim = c(0, 0.14))
+plot(theo.MSDi.s.n, type = "l", xlab = "site", ylab = "Theoretical")
 ```
@@
 ```{r}
-plot(exp.MSDi.s, type = "l", col = "red", ylab = "Experimental", ylim = c(0, 0.14))
+plot(exp.MSDi.s.n, type = "l", col = "red", xlab = "site",  ylab = "Experimental")
 ```
@@
 ```{r}
-plot(nsF.theo.MSDi.s, type = "l", ylab = "both", ylim = c(0, 0.14))
-points(exp.MSDi.s, col = "red", type = "l")
-legend("topleft", paste("R^2", round(R2.nsF.cF.s, digits = 2), " ", "MSE", signif(MSE.nsF.cF.s, digits = 4)), bty = "n", text.col = "red")
+plot(theo.MSDi.s.n, type = "l", xlab = "site", ylab = "Merge")
+points(exp.MSDi.s.n, col = "red", type = "l")
+legend("topleft", paste("R^2", round(R2.s.n, digits = 2), " ", "MSE", signif(MSE.s.n, digits = 4)), bty = "n", text.col = "red")
 ```
-
-With natural selection (ns = T)
-
-```{r}
-plot(nsT.theo.MSDi.s, type="l", xlab = "sitio", ylab = "Theoretical ns = T", ylim = c(0, 0.14))
-```
-
-```{r}
-plot(exp.MSDi.s, type = "l", col = "red", ylab = "Experimental", ylim = c(0, 0.14))
-```
-
-```{r}
-plot(nsT.theo.MSDi.s, type = "l", ylab = "both", ylim = c(0, 0.14))
-points(exp.MSDi.s, col = "red", type = "l")
-legend("topleft", paste("R^2", round(R2.nsT.cF.s, digits = 2), " ", "MSE", signif(MSE.nsT.cF.s, digits = 2)), bty = "n", text.col = "red")
-```

### 2016-05-01 MultipleReport.Rmd
cambios 01/05/2016

@@
 
-# Read files and calculate measures.
+# Set directories.
 data.dir <- "DATA"
@@
 
-# Family.
-pdbid <- read.csv(file.path(data.dir, paste(family, "_dataset.csv", sep = "")))$pdbid
-n.exp = length(pdbid)
-n.sites.p.1 = read.csv(file.path(out.dir, paste(family, "_out_m.n.sites.p.ref.csv", sep = "")))$V1[1]
-m.n.sites.p.2 = read.csv(file.path(out.dir, paste(family, "_out_m.n.sites.p.2.csv", sep = "")))$V1
-m.n.aligned = read.csv(file.path(out.dir, paste(family, "_out_m.n.aligned.csv", sep = "")))$V1
-identity = read.csv(file.path(out.dir, paste(family, "_out_m.identity.csv", sep = "")))$V1
-
-# Read experimental.
-analysis.fname.id <- paste(family, "_R0_", R0, "_K.analysis_", K.analysis, sep = "")
+### Experimental ###
+analysis.fname.id <- paste(family, "_R0_", R0, "_beta_", beta, "_K.analysis_", K.analysis, sep = "")
 
@@
 
-exp.Pn.quantile1 = matrix(0, ncol = ncol(m.exp.Pn), nrow = 1)
-exp.Pn.quantile2 = matrix(0, ncol = ncol(m.exp.Pn), nrow = 1)
+n.prot = nrow(m.exp.Pn)
 
-for (i in (1:ncol(m.exp.Pn))){
+exp.Pn.quantile1 = matrix(ncol = ncol(m.exp.Pn), nrow = 1)
+exp.Pn.quantile2 = matrix(ncol = ncol(m.exp.Pn), nrow = 1)
+
+for (i in (1:ncol(m.exp.Pn))) {
     exp.Pn.quantiles = as.vector(quantile((m.exp.Pn[, i]), probs = c(0.05, 0.95)))
@@
 ### Theoretical ###
-  mut.fname.id <- paste(family, "_R0_", R0, sep = "")
 
 m.theo.Pn = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.Pn.csv", sep = "")))[, 1:100]
+
 m.theo.smooth.norm.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.smooth.norm.dr.squarei.csv", sep = "")))
-prob.accept.mut.all.betas = read.csv(file.path(out.dir, paste(mut.fname.id, "_out_prob.accept.mut.all.betas.csv", sep = "")))
+theo.smooth.norm.MSDi = colMeans(m.theo.smooth.norm.dr.squarei, na.rm = T )
 
@@
 
-prob.accept.mut.beta.0.1 = prob.accept.mut.all.betas[1, ]
-prob.accept.mut.beta.0.5 = prob.accept.mut.all.betas[2, ]
-prob.accept.mut.beta.0.9 = prob.accept.mut.all.betas[3, ]
-
-mean.beta.0.theo.Pn = ColMeans(m.theo.Pn)
-mean.beta.0.1.theo.Pn = colSums((m.theo.Pn) * as.numeric(prob.accept.mut.beta.0.1))/ sum(prob.accept.mut.beta.0.1)
-mean.beta.0.5.theo.Pn = colSums(m.theo.Pn * as.numeric(prob.accept.mut.beta.0.5))/ sum(prob.accept.mut.beta.0.5)
-mean.beta.0.9.theo.Pn = colSums(m.theo.Pn * as.numeric(prob.accept.mut.beta.0.9))/ sum(prob.accept.mut.beta.0.9)
-
-mean.beta.0.theo.smooth.MSDi = colMeans(m.theo.smooth.dr.squarei, na.rm = T)
-mean.beta.0.1.theo.smooth.MSDi = colSums(m.theo.smooth.dr.squarei * as.numeric(prob.accept.mut.beta.0.1), na.rm = T)/ sum(prob.accept.mut.beta.0.1, na.rm = T )
-mean.beta.0.5.theo.smooth.MSDi = colSums(m.theo.smooth.dr.squarei * as.numeric(prob.accept.mut.beta.0.5), na.rm = T)/ sum(prob.accept.mut.beta.0.5, na.rm = T)
-mean.beta.0.9.theo.smooth.MSDi = colSums(m.theo.smooth.dr.squarei * as.numeric(prob.accept.mut.beta.0.9), na.rm = T)/ sum(prob.accept.mut.beta.0.9, na.rm = T)
 ```
 
+### MSDi
+
 Los perfiles teoricos de  smooth.norm.MSDi fueron fiteados con los perfiles exterimentales. Se compararon y se calcularon R^2 y MSE.
-```{r}
-keep.data = c()
-```
 
 ```{r}
-layout(matrix(1:4, 2, 2, byrow = F))
 
-fit.beta.0 = lm(exp.smooth.norm.MSDi ~ mean.beta.0.theo.smooth.MSDi )
-MSDi.fit.beta.0 = fitted.values(fit.beta.0)
-R2.beta.0 = cor(exp.smooth.norm.MSDi[!is.na(exp.smooth.norm.MSDi)], MSDi.fit.beta.0) ^ 2 
-MSE.beta.0 = mean((MSDi.fit.beta.0 - exp.smooth.norm.MSDi[!is.na(exp.smooth.norm.MSDi)]) ^ 2)
-
-fit.beta.0.1 = lm(exp.smooth.norm.MSDi ~ mean.beta.0.1.theo.smooth.MSDi )
-MSDi.fit.beta.0.1 = fitted.values(fit.beta.0.1)
-R2.beta.0.1 = cor(exp.smooth.norm.MSDi[!is.na(exp.smooth.norm.MSDi)], MSDi.fit.beta.0.1) ^ 2 
-MSE.beta.0.1 = mean((MSDi.fit.beta.0.1 - exp.smooth.norm.MSDi[!is.na(exp.smooth.norm.MSDi)]) ^ 2)
-
-fit.beta.0.5 = lm(exp.smooth.norm.MSDi ~ mean.beta.0.5.theo.smooth.MSDi )
-MSDi.fit.beta.0.5 = fitted.values(fit.beta.0.5)
-R2.beta.0.5 = cor(exp.smooth.norm.MSDi[!is.na(exp.smooth.norm.MSDi)], MSDi.fit.beta.0.5) ^ 2 
-MSE.beta.0.5 = mean((MSDi.fit.beta.0.5 - exp.smooth.norm.MSDi[!is.na(exp.smooth.norm.MSDi)]) ^ 2)
-
-fit.beta.0.9 = lm(exp.smooth.norm.MSDi ~ mean.beta.0.9.theo.smooth.MSDi )
-MSDi.fit.beta.0.9 = fitted.values(fit.beta.0.9)
-R2.beta.0.9 = cor(exp.smooth.norm.MSDi[!is.na(exp.smooth.norm.MSDi)], MSDi.fit.beta.0.9) ^ 2 
-MSE.beta.0.9 = mean((MSDi.fit.beta.0.9 - exp.smooth.norm.MSDi[!is.na(exp.smooth.norm.MSDi)]) ^ 2)
+fit = lm(exp.smooth.norm.MSDi ~ theo.smooth.norm.MSDi )
+MSDi.fit = fitted.values(fit)
+R2 = cor(exp.smooth.norm.MSDi[!is.na(exp.smooth.norm.MSDi)], MSDi.fit) ^ 2 
+MSE = mean((MSDi.fit - exp.smooth.norm.MSDi[!is.na(exp.smooth.norm.MSDi)]) ^ 2)
 
@@
 ```{r}
-lines(as.numeric(MSDi.fit.beta.0), type = "l", xlab = "site", ylab = "Theoretical MSDi BETA = 0", col = "red")
-
-lines(MSDi.fit.beta.0.1, type = "l", xlab = "site", ylab = "Theoretical MSDi BETA = 0.1", col = "red")
-
-lines(MSDi.fit.beta.0.5, type = "l", xlab = "site", ylab = "Theoretical MSDi BETA = 0.5", col = "blue")
-
-lines(MSDi.fit.beta.0.9, type = "l", xlab = "site", ylab = "Theoretical MSDi BETA = 0.9", col = "green")
-
+plot(as.numeric(MSDi.fit), xlab = "site", ylab = "Experimental", ylim = c(0,3))
+points(exp.smooth.norm.MSDi[!is.na(exp.smooth.norm.MSDi)], col = "red")
+legend("topleft", paste("R^2", round(R2, digits = 2), " ", "MSE", signif(MSE, digits = 4)), bty = "n", text.col = "red")
 ```
 
-```{r}
-plot(exp.smooth.norm.MSDi[!is.na(exp.smooth.norm.MSDi)], type = "l", xlab = "site", ylab = "Experimental")
+*negro:* teorico
 
-```
+*rojo:* experimental
 
-```{r}
-plot(nsF.theo.MSDi.s, type = "l", xlab = "site", ylab = "Merge", ylim = c(0, 0.14))
-points(exp.MSDi.s, col = "red", type = "l")
-legend("topleft", paste("R^2", round(R2.nsF.cF.s, digits = 2), " ", "MSE", signif(MSE.nsF.cF.s, digits = 4)), bty = "n", text.col = "red")
-rojo: experimental
-negro: teorico
-
-## Pn y Qn
+### Pn y Qn
 Las distribuciones de *Pn* y *Qn* de los conjuntos son las siguientes:
@@
 ```{r}
+# Re-ordenate Pn.
+m.theo.index = matrix(ncol = 1, nrow = n.mut)
+for (P in (1:n.prot)) {
+  for (mut in (1:n.mut.p)) {
+    m.theo.index[(P - 1) * n.mut.p + mut, ] = ((mut - 1) * 10 + P)
+  }
+}
+m.theo.Pn = m.theo.Pn[as.vector(m.theo.index), ]
 
 # Calculate groups, means and quantiles.
-theo.Pn.group = CalculateGroupsMeansQuantiles(theo.Pn, n.mut.p, n.exp)
+theo.Pn.group = CalculateGroupsMeansQuantiles(m.theo.Pn, n.mut.p, n.prot)
 mean.theo.Pn.group = theo.Pn.group$mean.mean.group
@@
 
-layout(matrix(1:2, 1, 2, byrow = T))
-
-plot(mean.nsF.cF.theo.Pn.group, 
-     main = "Pn promedio ns = F", 
+plot(mean.theo.Pn.group, 
+     main = "Pn promedio", 
      xlab = "nmodo",
      ylab = "Pn",
-     ylim = c(0, max(c(nsF.cF.theo.Pn.group.quantile2, mean.cF.exp.Pn))))
-lines(nsF.cF.theo.Pn.group.quantile1)
-lines(nsF.cF.theo.Pn.group.quantile2)
-points(mean.cF.exp.Pn, col = "red")
-lines(as.vector(cF.exp.Pn.quantile1), col = "red")
-lines(as.vector(cF.exp.Pn.quantile2), col = "red")
-
-plot(mean.nsT.cF.theo.Pn.group, 
-     main = "Pn promedio ns = T", 
-     xlab = "nmodo",
-     ylab = "Pn",
-     ylim = c(0, max(c(nsT.cF.theo.Pn.group.quantile2, mean.cF.exp.Pn))))
-lines(nsT.cF.theo.Pn.group.quantile1)
-lines(nsT.cF.theo.Pn.group.quantile2)
-points(mean.cF.exp.Pn, col = "red")
-lines(as.vector(cF.exp.Pn.quantile1), col = "red")
-lines(as.vector(cF.exp.Pn.quantile2), col = "red")
+     ylim = c(0, max(c(theo.Pn.group.quantile2, mean.exp.Pn))))
+lines(theo.Pn.group.quantile1)
+lines(theo.Pn.group.quantile2)
+points(mean.exp.Pn, col = "red")
+lines(as.vector(exp.Pn.quantile1), col = "red")
+lines(as.vector(exp.Pn.quantile2), col = "red")
 
@@
 
-*Negro*: Puntos: promedio de promedios teorico. Lineas: promedio de cuantiles 0.05 y 0.95 de `r n.mut.p` grupos de `r n.exp` mutantes teoricas.
+*Negro*: Puntos: promedio de promedios teorico. Lineas: promedio de cuantiles 0.05 y 0.95 de `r n.mut.p` grupos de `r n.prot` mutantes teoricas.
+
 *Rojo*: Experimental. Puntos: promedio. Lineas: cuantiles 0.05 y 0.95.
@@
 
-fit.nsF.cF = lm(mean.cF.exp.Pn ~ mean.nsF.cF.theo.Pn.group)
-Pn.fit.nsF.cF = fitted.values(fit.nsF.cF)
-R2.nsF.cF = cor(mean.cF.exp.Pn, Pn.fit.nsF.cF) ^ 2 
-MSE.nsF.cF = mean((Pn.fit.nsF.cF - mean.cF.exp.Pn) ^ 2)
-plot(Pn.fit.nsF.cF, mean.cF.exp.Pn, xlab = "Pn teorico", ylab = "Pn experimental", main = "ns = F c = F")
+fit = lm(mean.exp.Pn ~ mean.theo.Pn.group)
+Pn.fit = fitted.values(fit)
+R2 = cor(mean.exp.Pn, Pn.fit) ^ 2 
+MSE = mean((Pn.fit - mean.exp.Pn) ^ 2)
+plot(Pn.fit, mean.exp.Pn, xlab = "Pn teorico", ylab = "Pn experimental", main = "Pn")
 abline(0, 1)
-legend("topleft", paste("R^2", round(R2.nsF.cF, digits = 2)), bty = "n", text.col = "red")
-legend("bottomright", paste("MSE", signif(MSE.nsF.cF, digits = 2)), bty = "n", text.col = "red")
-
-keep.data = c(keep.data, R2.nsF.cF, MSE.nsF.cF)
-
-fit.nsT.cF = lm(mean.cF.exp.Pn ~ mean.nsT.cF.theo.Pn.group)
-Pn.fit.nsT.cF = fitted.values(fit.nsT.cF)
-R2.nsT.cF = cor(mean.cF.exp.Pn, Pn.fit.nsT.cF) ^ 2 
-MSE.nsT.cF = mean((Pn.fit.nsT.cF - mean.cF.exp.Pn) ^ 2)
-plot(Pn.fit.nsT.cF, mean.cF.exp.Pn, xlab = "Pn teorico", ylab = "Pn experimental", main = "ns = T c = F")
-abline(0, 1)
-legend("topleft", paste("R^2", round(R2.nsT.cF, digits = 2)), bty = "n", text.col = "red")
-legend("bottomright", paste("MSE", signif(MSE.nsT.cF, digits = 2)), bty = "n", text.col = "red")
-
-keep.data = c(keep.data, R2.nsT.cF, MSE.nsT.cF)
+legend("topleft", paste("R^2", round(R2, digits = 2)), bty = "n", text.col = "red")
+legend("bottomright", paste("MSE", signif(MSE, digits = 2)), bty = "n", text.col = "red")
 

### 2016-05-01 FUNCTIONS/AnalyzeExperimentalTheoretical.R

@@ -49,9 +49,7 @@ AnalyzeExperimentalTheoretical <- function(family,
                                            mut.fname.id, 
                                            analysis.fname.id,
                                            TOLERANCE) {
-  ### EXPERIMENTAL ###
-  
-  # Filenames.
+  # General Filenames.
   dataset.fname <- file.path(data.dir, paste(family, "_dataset.csv", sep = ""))
   pdbs.fname <- file.path(data.dir, paste(family, "_coordinates.pdb", sep = "")) 
   
@@ -60,12 +58,67 @@ AnalyzeExperimentalTheoretical <- function(family,
   m.aligned.p.2.index.fname <- file.path(out.dir, paste(family, "_out_m.aligned.p.2.index.csv", sep = ""))
   m.not.aligned.p.ref.index.fname <- file.path(out.dir, paste(family, "_out_m.not.aligned.p.ref.index.csv", sep = ""))
   m.not.aligned.p.2.index.fname <- file.path(out.dir, paste(family, "_out_m.not.aligned.p.2.index.csv", sep = ""))
-
+  
   # Read dataset.
   dataset <- read.csv(dataset.fname)
   pdbid.dataset <- as.character(dataset$pdbid)
   chain <- as.character(dataset$chain)
   n.prot = length(pdbid.dataset)
+  
+  ### THEORETICAL ###
+  
+  # Filenames.
+  theo.r.p.ref.fname <- file.path(out.dir, paste(mut.fname.id, "_out_r.p.ref.csv", sep = ""))
+  m.r.mut.fname <- file.path(out.dir, paste(mut.fname.id, "_out_m.r.mut.csv", sep = ""))
+  
+  # Read theo.p.ref and the simulated mutants.
+  theo.r.p.ref = read.csv(theo.r.p.ref.fname)$x
+  m.r.mut = read.csv(m.r.mut.fname)
+  n.sites.p.ref = length(theo.r.p.ref)/3
+  n.mut = ncol(m.r.mut)
+  
+  # Create matrices to save measures of variability of each mutant.
+  m.theo.Pn = matrix(nrow = n.mut, ncol = 3 * n.sites.p.ref)
+  m.theo.va = matrix(nrow = n.mut, ncol = 3 * n.sites.p.ref)
+  m.theo.dr.squarei = matrix(nrow = n.mut, ncol = n.sites.p.ref)
[…]

### 2016-05-01 FUNCTIONS/CalculateBetas.R

@@ -36,6 +36,8 @@ CalculateBetas <- function(chain.p.ref,
                           betas.fname.id,
                           TOLERANCE) {
   
+  print("calculating betas...")
+  
   ### READ EXPERIMENTAL DATA ###
   
   # Filenames.
@@ -69,10 +71,10 @@ CalculateBetas <- function(chain.p.ref,
   f2 = mean((fmax * runif(1e6, -1, 1)) ^ 2)
   
   # Caculate betas for differente selection regimes.
-  beta.0.2 = - log(0.2) / (f2 * mean.CN) # Strong selection.
-  beta.0.5 = - log(0.5) / (f2 * mean.CN) # Medium.
-  beta.0.8 = - log(0.8) / (f2 * mean.CN) # Weak selection.
-  beta.1 = - log(1) / (f2 * mean.CN) # No selection.
+  beta.0.2 = round(- log(0.2) / (f2 * mean.CN), digits = 3) # Strong selection.
+  beta.0.5 = round(- log(0.5) / (f2 * mean.CN), digits = 3) # Medium.
+  beta.0.8 = round(- log(0.8) / (f2 * mean.CN), digits = 3) # Weak selection.
+  beta.1 = round(- log(1) / (f2 * mean.CN), digits = 3) # No selection.
   
   # Build a list with betas.
   all.betas = list("strong.sel" = beta.0.2, "medium.sel" = beta.0.5, "weak.sel" = beta.0.8, "no.sel" = beta.1) 

### 2016-05-01 MainMultipleReport.R

@@ -6,17 +6,25 @@ library(markdown)
 input.fname <- file.path("input_MainMultipleReport.csv")
 input <- read.csv(input.fname)
 
+# Satart a loop for each family.
 for (a in (1:nrow(input))) { 
   print(a)
   family <- as.character(input$family)[a]
   p.ref <- as.character(input$p.ref)[a]
-  mut.model = input$mut.model[a]
+  chain.p.ref = input$chain.p.ref[a]
   n.mut.p = input$n.mut.p[a]
   R0 = input$R0[a]
   K.analysis = input$K.analysis[a]
-  exp.chain.p.ref = input$exp.chain.p.ref[a]
-
-  # Generate a report.
-  rmarkdown::render('MultipleReport.Rmd', 
-                    output_file =  paste("report_", family, "_R0_", R0, "_K.analysis_", K.analysis, ".html", sep = ''))
+  
+  # Read betas.
+  betas.fname.id <- paste(family, "_", p.ref, "_R0_", R0, sep = "")
+  all.betas <- read.csv(file.path(out.dir, paste(betas.fname.id, "_out_all.betas.csv", sep = "")))
+  
+  # Start a loop for each beta.
+  for (beta in all.betas)  {
+    
+    # Generate a report.
+    rmarkdown::render('MultipleReport.Rmd', 
+                      output_file =  paste("report_", family, "_R0_", R0, "_beta_", beta, "_K.analysis_", K.analysis, ".html", sep = ''))
+  }
 }

### 2016-05-05 INFORMATION/paper.tex
cambios 05/05/2016

@@
 
-{\bf ENM of a reference protein:}
+{\subsection* {ENM of a reference protein:}
 
@@
 
-{\bf LF-ENM model of mutant proteins:}
+\subsection*{LF-ENM model of mutant proteins:}
 
@@
 
-{\bf LF-ENM for multiple mutants: }
-To simulate proteins with not one but multiple mutations we considered additive mutations by the assumption that $\mathbf{K}_{mut}$ \cong $\mathbf{K}_{wt}$:
+\subsection*{Stress Model}
+The stress model is based on an Elastic Netowork Model in which mutations are modeled as perturbations to the spring lengths that connect the mutated site with its neighbors.
 
-\begin{equation}
-d\mathbf{r}^{0,tot} = d\mathbf{r}^{0,mut1}_{wt}+d\mathbf{r}^{0,mut2}_{wt}+ ...+d\mathbf{r}^{0,mutm}_{wt}+...+d\mathbf{r}^{0,mutNmut}_{wt}
+Let the ENM potential energy of the wild-type protein be:
+\begin{equation} \label{eq:Vwt}
+V_{wt} = \frac{1}{2} \sum_{i<j} k_{ij} (d_{ij}-d^0_{ij})^2
+\end{equation}
+We model the mutation by replacing perturbing the equilibrium lengths of the ENM springs: $d^0_{ij} \to d^0_{ij} + \Delta_{ij}$, where $\Delta_{ij}$ are picked independently for each of the contacts of the mutated site, from the same distribution, e.g.
+a uniform distribution, which satisfies $<\Delta_{ij}> = 0$ and $Var(\Delta_ij) = \sigma^2$, independent of $ij$.
+The mutant's potential is:
+\begin{equation} \label{eq:Vmut}
+V_{mut} = \frac{1}{2} \sum_{i<j} k_{ij} [d_{ij}-(d^0_{ij}+\Delta_{ij})]^2
+\end{equation}
+When the mutant adopts the wild-type structure $\mathbf{r^0}_{wt}$, $d_{ij} = d_{ij}^0$, and the mutant's energy is:
+\begin{equation} \label{eq:Vmut0}
+V_{mut}(\mathbf{r^0}_{wt}) = \frac{1}{2} \sum_{i<j} k_{ij} \Delta_{ij}^2
+\end{equation}
+The stress model poses that the probability of accepting such a mutant is:
+\begin{equation} \label{eq:Paccept}
+P_{accept} = e^{-\beta \frac{1}{2} \sum_{i<j} k_{ij} \Delta_{ij}^2}
 \end{equation}
 
-\begin{equation}
-d\mathbf{r}^{0,tot} =\mathbf{K}^{-1}_{wt}\times(\mathbf{f}_{mut1}+\mathbf{f}_{mut2}+...+\mathbf{f}_{mutm}+...+\mathbf{f}_{mutNmut}) 
+\subsection*{Linearly Forced Elastic Network Model with Stress Model}
+The linearly forced elastic network model is obtained from expanding Eq.
+\ref{eq:Vmut} up to second order.
+The potential is expressed in terms of "forces" directed along the contacts of the mutated site with lengths:
+\begin{equation} \label{eq:fij}
+f_{ij} = k_{ij} \Delta_{ij}
+\end{equation}
+Therefore, from Eq. \ref{eq:Paccept} and \ref{eq:fij} we find:
+\begin{equation} \label{eq:PacceptFij}
+P_{accept} = e^{-\beta \frac{1}{2} \sum_{i<j}  f_{ij}^2/k_{ij}}
 \end{equation}
 
-Where $d\mathbf{r}^{0,tot}$ is the total structural variation due the M mutations, $d\mathbf{r}^{0,mutm}_{wt}$ is the structural variation produced by the mutation $m$ (considering $\mathbf{K}_{wt}$), and $\mathbf{f}_mutm}$ is the vector of force of the $m$ mutation.
+For the ANM, $k_{ij}$ are either 0 or 1, and we get:
+\begin{equation} \label{eq:PacceptANM}
+P_{accept} = e^{-\beta \frac{1}{2} \sum_{j\sim i}  f_{ij}^2}
+\end{equation}
+Where the sum $j \sim i$ is over all $j$ that are in contact with the mutated site $i$ (i.e. for which $k_{ij} \ne 0$.
 
-{\bf Model parameters: }
+\subsection*{Evolutionary Simulation}
+
+\subsubsection*{One evolutionary step}
+Let us define a time-step such that the time-step when there is a single substitution event for the whole protein (a substitution is an accepted mutation).
+To simulate such an event we did the following:
+\begin{enumerate}
+\item We picked one random site $l$
+\item We introduced a "trial" mutation by obtaining a set of ${f_{lj}}$ for each of the contacts of site $l$
+\item We calculated the probability of accepting this trial mutation: $P_{accept} = e^{-\beta \frac{1}{2} \sum_{j\sim i}  f_{lj}^2}$
+\item We calculated the logical variable $\text{Accept} = P_{accept} \ge \text{runif(1,0,1)}$; Accept will be TRUE with probability $P_{accept}$, this is a way of implementing accepting mutations with this probability.
+\item If Accept is TRUE, we accepted the mutation (i.e.
+the new wild-type is the mutant) and the evolutionary step was finished (i.e.
+we found an accepted mutation: one substitution).
+Else, we rejected the trial mutation and tried again (i.e.
+went back to Step 1: picked a random site, etc.).
+\end{enumerate}
+For future reference, let's assume that we implement this single-step using a function oneSubstitution(sites) that returns the mutated site $l$, and the force that simulates the mutation ${f_{lj}}$ (or alternatively the force-vector $\mathbf{f}_l$).
+
+\subsubsection*{An evolutionary path of N substitution at N different sites}
+We want to simulate a lineage (an evolutionary path) such that it starts at a known ancestor (our reference protein) and it ends when $N$ sites have accepted mutations.
+($N \le L$, where $L$ is the sequence length).
+Briefly, we need to repeat the single evolutionary step of the previous paragraph $N$ times, making sure that the set of sites where we try mutations does not include sites that previously accepted mutations (this corresponds to sampling without replacement).
+The process would be, using pseudocode:
+
+\section*{Star tree}
+Our "experimental" data are sets of proteins one of which we consider as the "reference" protein.
+In principle, we should infer the phylogenetic tree and try to simulate structures with our model following a tree with the same topology.
+However, we assume that the results are not too sensitive with respect to tree topology so that we can approximate the tree by a "star tree".
+The common ancestor of all lineages of our star tree is our reference protein.
+Then, each lineage corresponds to a pair alignment of each protein with the reference.
+Thus, different lineages have different "branch lengths", were we assume the branch lengh is the number of sites in which the sequence of the (common) ancestor and the tip of the lineage differ.
+
+\section*{Model parameters}
 To completely specify the model, we must choose $\mathbf{K}_{wt}$ and $\mathbf{f}$.
@@
 
-{\bf Experimental dataset:}
+\subsection*{Experimental dataset:}
 We selected 8 families of proteins from the database of multiple structural alignments of homologous HOMSTRAD (http://mizuguchilab.org/homstrad/).
@@
 
-{\it Selection of the reference protein:}
+\subsubsection*{Selection of the reference protein:}
 For each family of the dataset we selected a reference ``wilt type'' protein, which we consider is the most structurally representative protein of the family.
@@
 
-{\it Alignments analysis:}
+\subsubsection*{Alignments analysis:}
 For each family of proteins, the reference protein was aligned with each of the other proteins of the family.
@@
 
-{\bf Theoretical datasets:}
-In order to study the effect of natural selection on structural divergence we generated two datasets of simulated mutants.
-In one dataset, we applied natural selection and, on the other dataset, we did not consider natural selection:
-
-{\it Mutants with natural selection (NS = T):} we applied natural selection at the sequence level of the reference protein of each family.
-To determine which sites to mutate accounting natural selection, we followed the stress model, by which probabilities of mutation are assigned for each site of the reference protein:
-
-\begin{equation}
-p^{mut}_{i} = 1 - (beta \times CN_{i})
-\end{equation}
-
-Were $CN_{i}$ is the number of contacts (sites with a distance $\leq$ 10 $\AA$ in this case) of site $i$. 
-To select the number of sites to mutate, we took information from the alignment of the correspondent family.
-For each pair comprising the reference protein and one of the other proteins of the family, we obtained the average sequence identity (\% ID) within the aligned region.
-Then, the number of mutated sites for this pair is:
-
-\begin{equation}
-nsites^{mut} = (100 - \% ID) \times naa / 100
-\end{equation}
-
-Being $naa$ the number of aminoacids of the reference protein. 
-Then, for each of these pairs, we generated 10 mutants of $nsites^{mut}$, where the mutated sites are the ones with more probabilities to mutate following the stress model.
-
-In this way, if the family has $P$ proteins (plus the reference protein), we obtained a simulated dataset of $10 \times P$  members.
-
-{\it Mutants without natural selection (NS = F):} For each family and for each pair comprising the reference protein and one of the other proteins of the family, we obtained the number of sites to mutate as mentioned before and we mutated randomly this number of sites.
-For each of these pairs, we generated 10 mutants.
-Hence, again, if the family has $P$ proteins (plus the reference protein), we obtained a simulated dataset of  $10 \times P$  members.
-
-{\bf Structural variability measures:}
+\subsection*{ Structural variability measures:}
 We obtained the coordinates of the aligned sites of each protein.
@@
 
-{\it Cartesian coordinates:}
+\subsubsection*{ Cartesian coordinates:}
 Structural variation of each protein was calculated relative to the reference protein into the aligned sites. To do this, for each aligned site, we calculated the square deviation:
@@
 
-{\it Normal modes coordinates:}
+\subsubsection*{Normal modes coordinates:}
 Analysis of structural change of normal modes was calculated by projecting structural differences of aligned sites of each protein onto the normal modes of the reference protein.
@@
 
-{\bf Profile comparisons:}
+\subsection*{ Profile comparisons:}
 
-{\it Cartesian coordinates:} For the theoretical datasets and for the experimental dataset we averaged $\left\|d\mathbf{r}^{0}_{i}\right\|^{2}$ over each site $i$ of the reference protein of each family to obtain profiles of $MSD_{i}$.
+\subsubsection*{Cartesian coordinates:} For the theoretical datasets and for the experimental dataset we averaged $\left\|d\mathbf{r}^{0}_{i}\right\|^{2}$ over each site $i$ of the reference protein of each family to obtain profiles of $MSD_{i}$.
 Then, the theoretical average profiles were fitted with the experimental profile.
@@
 
-{\it Normal modes coordinates:} For the theoretical datasets, with or without natural selection, the 10 x P profiles of $P_{n}$ of each family were split in 10 groups so that in all of them there was a simulated mutant that corresponded to an experimental pair of proteins of the family in means of the \% ID.
+\subsubsection*{Normal modes coordinates:} For the theoretical datasets, with or without natural selection, the 10 x P profiles of $P_{n}$ of each family were split in 10 groups so that in all of them there was a simulated mutant that corresponded to an experimental pair of proteins of the family in means of the \% ID.
 Then we calculated, for these 10 groups, the average and 0.05 and 0.95 quantiles.
@@
 \section{Results and discussion}
-{\it Cartesian coordinates:}
+\subsection*{Cartesian coordinates:}
 In order to analyze the effect of natural selection on the structural variability in cartesian coordinates we calculated unique per dataset $MSD_{i}$ profiles as explained in Methods.
@@
 
-{\it Normal modes coordinates:}
+\subsection*{Normal modes coordinates:}
 In order to analyze the effect of natural selection on the structural variability projected onto normal modes coordinates of the reference protein, we obtained average $P_{n}$ profiles and 0.05 and 0.95 quantiles profiles as explained in Methods.

### 2016-05-05 MultipleReport.Rmd
cambios 05/05/2016

@@
 
-*negro:* teorico
+*negro:* Promedio teorico.
 
-*rojo:* experimental
+*rojo:* Promedio experimental.
 
@@
 theo.Pn.group.quantile2 = theo.Pn.group$mean.quantile2.group
-
+theo.Pn.quantile1.mean = theo.Pn.group$quantile1.mean
+theo.Pn.quantile2.mean = theo.Pn.group$quantile2.mean
 ```
@@
 
-*Rojo*: Experimental. Puntos: promedio. Lineas: cuantiles 0.05 y 0.95.
+*Rojo*: Puntos: promedio experimental. Lineas: cuantiles 0.05 y 0.95 experimentales.
 
-Posteriormente, los perfiles de Pn teoricos fueron fiteados con los perfiles exterimentales. Se compararon y se calcularon R^2 y MSE.
+```{r}
+
+# Graphics.
+
+plot(mean.theo.Pn.group, 
+     main = "Pn promedio", 
+     xlab = "nmodo",
+     ylab = "Pn",
+     ylim = c(0, max(c(theo.Pn.group.quantile2, mean.exp.Pn))))
+lines(as.vector(theo.Pn.quantile1.mean))
+lines(as.vector(theo.Pn.quantile2.mean))
+points(mean.exp.Pn, col = "red")
+
+```
+
+*Negro*: Puntos: promedio de promedios teorico. Lineas:  cuantiles 0.05 y 0.95 de promedios de `r n.mut.p` grupos de `r n.prot` mutantes teoricas.
+
+*Rojo*: Promedio experimental.
 
@@
 MSE = mean((Pn.fit - mean.exp.Pn) ^ 2)
-plot(Pn.fit, mean.exp.Pn, xlab = "Pn teorico", ylab = "Pn experimental", main = "Pn")
+plot(Pn.fit, mean.exp.Pn, xlab = "Pn promedio de promedios teorico", ylab = "Pn promedio experimental", main = "Pn")
 abline(0, 1)

### 2016-05-05 MultipleReportAllBetas.Rmd
cambios 05/05/2016

---
title: "Estudio variabilidad estructural proteica"
output: html_document
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(warning = FALSE, echo = FALSE, message = FALSE)
```

```{r}

# Source functions.
source("FUNCTIONS/CalculateGroupsMeansQuantiles.R")

# Set directories.
data.dir <- "DATA"
out.dir <- "OUT"

# p.ref.
n.sites.p.ref = read.csv(file.path(out.dir, paste(family, "_out_m.n.sites.p.ref.csv", sep = "")))$V1[1]

# Create matrices to save data.
m.MSDi.fit = matrix(nrow = 4, ncol = n.sites.p.ref)
m.exp.MSDi = matrix(nrow = 4, ncol = n.sites.p.ref)
m.MSDi.R2 = matrix(nrow = 4, ncol = 1)
m.MSDi.MSE = matrix(nrow = 4, ncol = 1)

m.Pn.fit = matrix(nrow = 4, ncol = 3 * n.sites.p.ref)
m.exp.Pn = matrix(nrow = 4, ncol = 3 * n.sites.p.ref)
m.Pn.R2 = matrix(nrow = 4, ncol = 1)
m.Pn.MSE = matrix(nrow = 4, ncol = 1)

m.mean.theo.Pn.group = matrix(nrow = 4, ncol = 3 * n.sites.p.ref)
m.theo.Pn.group.quantile1 = matrix(nrow = 4, ncol = 3 * n.sites.p.ref)
m.theo.Pn.group.quantile2 = matrix(nrow = 4, ncol = 3 * n.sites.p.ref)
m.theo.Pn.quantile1.mean = matrix(nrow = 4, ncol = 3 * n.sites.p.ref)
m.theo.Pn.quantile2.mean = matrix(nrow = 4, ncol = 3 * n.sites.p.ref)

m.mean.exp.Pn = matrix(nrow = 4, ncol = 3 * n.sites.p.ref)
m.exp.Pn.quantile1 = matrix(nrow = 4, ncol = 3 * n.sites.p.ref)
m.exp.Pn.quantile2 = matrix(nrow = 4, ncol = 3 * n.sites.p.ref)

# Read betas.
betas.fname.id <- paste(family, "_", p.ref, "_R0_", R0, sep = "")
all.betas <- read.csv(file.path(out.dir, paste(betas.fname.id, "_out_all.betas.csv", sep = "")))

  # Start a loop for each beta.
  for (beta in all.betas)  {

  ### Experimental ###
  analysis.fname.id <- paste(family, "_R0_", R0, "_beta_", beta, "_K.analysis_", K.analysis, sep = "")

  m.exp.Pn = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.exp.Pn.csv", sep = "")))[, 1:100]
  mean.exp.Pn = colMeans(m.exp.Pn)

  n.prot = nrow(m.exp.Pn)

  exp.Pn.quantile1 = matrix(ncol = ncol(m.exp.Pn), nrow = 1)
  exp.Pn.quantile2 = matrix(ncol = ncol(m.exp.Pn), nrow = 1)

  for (i in (1:ncol(m.exp.Pn))) {
      exp.Pn.quantiles = as.vector(quantile((m.exp.Pn[, i]), probs = c(0.05, 0.95)))
      exp.Pn.quantile1[1, i] = exp.Pn.quantiles[1]
      exp.Pn.quantile2[1, i] = exp.Pn.quantiles[2]
  }

  m.mean.exp.Pn[as.vector(all.betas == beta), 1:length(mean.exp.Pn)] = mean.exp.Pn
  m.exp.Pn.quantile1[as.vector(all.betas == beta), 1:length(exp.Pn.quantile1)] = exp.Pn.quantile1
  m.exp.Pn.quantile2[as.vector(all.betas == beta), 1:length(exp.Pn.quantile2)] = exp.Pn.quantile2

  m.exp.smooth.norm.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.exp.smooth.norm.dr.squarei.csv", sep = "")))
  exp.smooth.norm.MSDi = colMeans(m.exp.smooth.norm.dr.squarei, na.rm = T )

  ### Theoretical ###

  m.theo.Pn = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.Pn.csv", sep = "")))[, 1:100]

  m.theo.smooth.norm.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.smooth.norm.dr.squarei.csv", sep = "")))
  theo.smooth.norm.MSDi = colMeans(m.theo.smooth.norm.dr.squarei, na.rm = T )

 n.mut = nrow(m.theo.Pn)

fit = lm(exp.smooth.norm.MSDi ~ theo.smooth.norm.MSDi )
MSDi.fit = fitted.values(fit)
MSDi.R2 = cor(exp.smooth.norm.MSDi[!is.na(exp.smooth.norm.MSDi)], MSDi.fit) ^ 2 
MSDi.MSE = mean((MSDi.fit - exp.smooth.norm.MSDi[!is.na(exp.smooth.norm.MSDi)]) ^ 2)
exp.smooth.norm.MSDi = exp.smooth.norm.MSDi[!is.na(exp.smooth.norm.MSDi)]

m.MSDi.fit[as.vector(all.betas == beta), ] = MSDi.fit
m.MSDi.R2[as.vector(all.betas == beta), ] = MSDi.R2
m.MSDi.MSE[as.vector(all.betas == beta), ] = MSDi.MSE
m.exp.MSDi[as.vector(all.betas == beta), ] = exp.smooth.norm.MSDi

  ### Pn ###

  # Re-ordenate Pn.
  m.theo.index = matrix(ncol = 1, nrow = n.mut)
  for (P in (1:n.prot)) {
    for (mut in (1:n.mut.p)) {
      m.theo.index[(P - 1) * n.mut.p + mut, ] = ((mut - 1) * 10 + P)
    }
  }
  m.theo.Pn = m.theo.Pn[as.vector(m.theo.index), ]

  # Calculate groups, means and quantiles.
  theo.Pn.group = CalculateGroupsMeansQuantiles(m.theo.Pn, n.mut.p, n.prot)
  mean.theo.Pn.group = theo.Pn.group$mean.mean.group
  theo.Pn.group.quantile1 = theo.Pn.group$mean.quantile1.group
  theo.Pn.group.quantile2 = theo.Pn.group$mean.quantile2.group
  theo.Pn.quantile1.mean = theo.Pn.group$quantile1.mean
  theo.Pn.quantile2.mean = theo.Pn.group$quantile2.mean

  m.mean.theo.Pn.group[as.vector(all.betas == beta), 1:length(mean.theo.Pn.group)] = mean.theo.Pn.group
  m.theo.Pn.group.quantile1[as.vector(all.betas == beta), 1:length(theo.Pn.group.quantile1)] = theo.Pn.group.quantile1
  m.theo.Pn.group.quantile2[as.vector(all.betas == beta), 1:length(theo.Pn.group.quantile2)] = theo.Pn.group.quantile2
  m.theo.Pn.quantile1.mean[as.vector(all.betas == beta), 1:length(theo.Pn.quantile1.mean)] = theo.Pn.quantile1.mean
  m.theo.Pn.quantile2.mean[as.vector(all.betas == beta), 1:length(theo.Pn.quantile2.mean)] = theo.Pn.quantile2.mean

Pn.fit = lm(mean.exp.Pn ~  mean.theo.Pn.group)
Pn.fit = fitted.values(Pn.fit)
Pn.R2 = cor(mean.exp.Pn, Pn.fit) ^ 2 
Pn.MSE = mean((Pn.fit - mean.exp.Pn) ^ 2)

m.Pn.fit[as.vector(all.betas == beta), 1:(length(Pn.fit))] = Pn.fit
m.Pn.R2[as.vector(all.betas == beta), ] = Pn.R2
m.Pn.MSE[as.vector(all.betas == beta), ] = Pn.MSE
m.mean.exp.Pn[as.vector(all.betas == beta), 1:(length(mean.exp.Pn))] = mean.exp.Pn

}

```

### MSDi

Los perfiles teoricos suavizados y normalizados de MSDi fueron fiteados con los perfiles exterimentales. Se compararon y se calcularon R^2 y MSE. Se indica el regimen de selección usada.

```{r}

layout(matrix(1:4, 2, 2, byrow = T))

plot(as.numeric(m.MSDi.fit[1, ]), xlab = "site", main = "MSDi strong selection", ylab = "MSDi", ylim = c(0,5))
points(m.exp.MSDi[1, ], col = "red")
legend("topleft", paste("R^2", round(m.MSDi.R2[1, ], digits = 2), " ", "MSE", signif(m.MSDi.MSE[1, ], digits = 4)), bty = "n", text.col = "red")

plot(as.numeric(m.MSDi.fit[2, ]), xlab = "site", main = "MSDi medium selection", ylab = "MSDi", ylim = c(0,5))
points(m.exp.MSDi[2, ], col = "red")
legend("topleft", paste("R^2", round(m.MSDi.R2[2, ], digits = 2), " ", "MSE", signif(m.MSDi.MSE[2, ], digits = 4)), bty = "n", text.col = "red")

plot(as.numeric(m.MSDi.fit[3, ]), xlab = "site", main = "MSDi weak selection", ylab = "MSDi", ylim = c(0,5))
points(m.exp.MSDi[3, ], col = "red")
legend("topleft", paste("R^2", round(m.MSDi.R2[3, ], digits = 2), " ", "MSE", signif(m.MSDi.MSE[3, ], digits = 4)), bty = "n", text.col = "red")

plot(as.numeric(m.MSDi.fit[4, ]), xlab = "site", main = "MSDi no selection", ylab = "MSDi", ylim = c(0,5))
points(m.exp.MSDi[4, ], col = "red")
legend("topleft", paste("R^2", round(m.MSDi.R2[4, ], digits = 2), " ", "MSE", signif(m.MSDi.MSE[4, ], digits = 4)), bty = "n", text.col = "red")
```

*negro:* Promedio teorico.

*rojo:* Promedio experimental.

### Pn y Qn
Las distribuciones de *Pn* y *Qn* de los conjuntos son las siguientes:

```{r}
layout(matrix(1:4, 2, 2, byrow = T))

plot(m.mean.theo.Pn.group[1, 1:100], 
     main = "Pn strong selection", 
     xlab = "mode",
     ylab = "Pn",
     ylim = c(0, max(c(m.theo.Pn.group.quantile2[1, 1:100], m.mean.exp.Pn[1, 1:100]))))
lines(m.theo.Pn.group.quantile1[1, ])
lines(m.theo.Pn.group.quantile2[1, ])
points(m.mean.exp.Pn[1, ], col = "red")
lines(as.vector(m.exp.Pn.quantile1[1, ]), col = "red")
lines(as.vector(m.exp.Pn.quantile2[1, ]), col = "red")

plot(m.mean.theo.Pn.group[2, 1:100], 
     main = "Pn medium selection", 
     xlab = "mode",
     ylab = "Pn",
     ylim = c(0, max(c(m.theo.Pn.group.quantile2[2, 1:100], m.mean.exp.Pn[2, 1:100]))))
lines(m.theo.Pn.group.quantile1[2, ])
lines(m.theo.Pn.group.quantile2[2, ])
points(m.mean.exp.Pn[2, ], col = "red")
lines(as.vector(m.exp.Pn.quantile1[2, ]), col = "red")
lines(as.vector(m.exp.Pn.quantile2[2, ]), col = "red")

plot(m.mean.theo.Pn.group[3, 1:100], 
     main = "Pn weak selection", 
     xlab = "mode",
     ylab = "Pn",
     ylim = c(0, max(c(m.theo.Pn.group.quantile2[3, 1:100], m.mean.exp.Pn[3, 1:100]))))
lines(m.theo.Pn.group.quantile1[3, ])
lines(m.theo.Pn.group.quantile2[3, ])
points(m.mean.exp.Pn[3, ], col = "red")
lines(as.vector(m.exp.Pn.quantile1[3, ]), col = "red")
lines(as.vector(m.exp.Pn.quantile2[3, ]), col = "red")

plot(m.mean.theo.Pn.group[4, 1:100], 
     main = "Pn no selection", 
     xlab = "mode",
     ylab = "Pn",
     ylim = c(0, max(c(m.theo.Pn.group.quantile2[4, 1:100], m.mean.exp.Pn[4, 1:100]))))
lines(m.theo.Pn.group.quantile1[4, ])
lines(m.theo.Pn.group.quantile2[4, ])
points(m.mean.exp.Pn[4, ], col = "red")
lines(as.vector(m.exp.Pn.quantile1[4, ]), col = "red")
lines(as.vector(m.exp.Pn.quantile2[4, ]), col = "red")

```

*Negro*: Puntos: promedio de promedios teorico. Lineas: promedio de cuantiles 0.05 y 0.95 de `r n.mut.p` grupos de `r n.prot` mutantes teoricas.

*Rojo*: Puntos: promedio experimental. Lineas: cuantiles 0.05 y 0.95 experimentales.

```{r}
layout(matrix(1:4, 2, 2, byrow = T))

plot(m.mean.theo.Pn.group[1, 1:100], 
     main = "Pn strong selection", 
     xlab = "mode",
     ylab = "Pn",
     ylim = c(0, max(c(m.theo.Pn.group.quantile2[1, 1:100], m.mean.exp.Pn[1, 1:100]))))
lines(as.vector(m.theo.Pn.quantile1.mean[1, ]))
lines(as.vector(m.theo.Pn.quantile2.mean[1, ]))
points(m.mean.exp.Pn[1, ], col = "red")

plot(m.mean.theo.Pn.group[2, 1:100], 
     main = "Pn medium selection", 
     xlab = "mode",
     ylab = "Pn",
     ylim = c(0, max(c(m.theo.Pn.group.quantile2[2, 1:100], m.mean.exp.Pn[2, 1:100]))))
lines(as.vector(m.theo.Pn.quantile1.mean[2, ]))
lines(as.vector(m.theo.Pn.quantile2.mean[2, ]))
points(m.mean.exp.Pn[2, ], col = "red")

plot(m.mean.theo.Pn.group[3, 1:100], 
     main = "Pn weak selection", 
     xlab = "mode",
     ylab = "Pn",
     ylim = c(0, max(c(m.theo.Pn.group.quantile2[3, 1:100], m.mean.exp.Pn[3, 1:100]))))
lines(as.vector(m.theo.Pn.quantile1.mean[3, ]))
lines(as.vector(m.theo.Pn.quantile2.mean[3, ]))
points(m.mean.exp.Pn[3, ], col = "red")

plot(m.mean.theo.Pn.group[4, 1:100], 
     main = "Pn no selection", 
     xlab = "mode",
     ylab = "Pn",
     ylim = c(0, max(c(m.theo.Pn.group.quantile2[4, 1:100], m.mean.exp.Pn[4, 1:100]))))
lines(as.vector(m.theo.Pn.quantile1.mean[4, ]))
lines(as.vector(m.theo.Pn.quantile2.mean[4, ]))
points(m.mean.exp.Pn[4, ], col = "red")

```

*Negro*: Puntos: promedio de promedios teorico. Lineas:  cuantiles 0.05 y 0.95 de promedios de `r n.mut.p` grupos de `r n.prot` mutantes teoricas.

*Rojo*: Promedio experimental.

```{r}
layout(matrix(1:4, 2, 2, byrow = T)) 
plot(m.mean.theo.Pn.group[1, ], m.mean.exp.Pn[1, ], xlab = "<<Pn>> teorico", ylab = "<Pn> experimental", main = "Pn strong selection")
abline(0, 1)
legend("topleft", paste("R^2", round(m.Pn.R2[1, ], digits = 2)), bty = "n", text.col = "red")
legend("bottomright", paste("MSE", signif(m.Pn.MSE[1, ], digits = 2)), bty = "n", text.col = "red")

plot(m.mean.theo.Pn.group[2, ], m.mean.exp.Pn[2, ], xlab = "<<Pn>> teorico", ylab = "<Pn> experimental", main = "Pn medium selection")
abline(0, 1)
legend("topleft", paste("R^2", round(m.Pn.R2[2, ], digits = 2)), bty = "n", text.col = "red")
legend("bottomright", paste("MSE", signif(m.Pn.MSE[2, ], digits = 2)), bty = "n", text.col = "red")

plot(m.mean.theo.Pn.group[3, ], m.mean.exp.Pn[3, ], xlab = "<<Pn>> teorico", ylab = "<Pn> experimental", main = "Pn weak selection")
abline(0, 1)
legend("topleft", paste("R^2", round(m.Pn.R2[3, ], digits = 2)), bty = "n", text.col = "red")
legend("bottomright", paste("MSE", signif(m.Pn.MSE[3, ], digits = 2)), bty = "n", text.col = "red")

plot(m.mean.theo.Pn.group[4, ], m.mean.exp.Pn[4, ], xlab = "<<Pn>> teorico", ylab = "<Pn> experimental", main = "Pn no selection")
abline(0, 1)
legend("topleft", paste("R^2", round(m.Pn.R2[4, ], digits = 2)), bty = "n", text.col = "red")
legend("bottomright", paste("MSE", signif(m.Pn.MSE[4, ], digits = 2)), bty = "n", text.col = "red")

```

### 2016-05-09 AllFamilys.Rmd
cambios 09/05/2016

@@
 # Create vectors to keep data.
-v.theo.MSDi.s.n = c()
-v.exp.MSDi.s.n = c()
+v.v.theo.MSDi = c()
+v.v.exp.MSDi = c()
+v.R2 = c()
+v.MSE = c()
 
@@
 print(input)
+
+# Create a list of selection regimens.
+all.betas <- list("strong.sel", "medium.sel", "weak.sel", "no.sel")
+
+# Start a loop for each beta.
+for (beta in (all.betas)) {
+
+  # Create vectors to keep data.
+  v.theo.MSDi = c()
+  v.exp.MSDi = c()
 
@@
 
-  m.exp.smooth.norm.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.exp.smooth.norm.dr.squarei.csv", sep = "")))
-
- exp.MSDi.s.n = colMeans(m.exp.smooth.norm.dr.squarei, na.rm = T )
+    m.exp.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.exp.smooth.norm.dr.squarei.csv", sep = "")))
+    exp.MSDi = colMeans(m.exp.dr.squarei, na.rm = T)
 
     # Read theoretical data#
-  m.theo.smooth.norm.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.smooth.norm.dr.squarei.csv", sep = "")))
+    m.theo.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.smooth.norm.dr.squarei.csv", sep = "")))
+    theo.MSDi = colMeans(m.theo.dr.squarei, na.rm = T)
 
- theo.MSDi.s.n = colMeans(m.theo.smooth.norm.dr.squarei, na.rm = T)
+    # Fit theoretical data with experimental data.
+    fit = lm(exp.MSDi ~ theo.MSDi)
+    fit.MSDi = fitted.values(fit)
 
-  ## Fit theoretical data with experimental data.
+    # Save and concatenale information.
+    v.theo.MSDi = c(v.theo.MSDi, fit.MSDi)
+    exp.MSDi = exp.MSDi[!is.na(exp.MSDi)]
+    v.exp.MSDi = c(v.exp.MSDi, exp.MSDi)
 
-  fit.s.n = lm(exp.MSDi.s.n ~ theo.MSDi.s.n)
-  fit.MSDi.s.n = fitted.values(fit.s.n)
-
-  # Concatenate information.
-  v.theo.MSDi.s.n = c(v.theo.MSDi.s.n, fit.MSDi.s.n)
-
-  exp.MSDi.s.n = exp.MSDi.s.n[!is.na(exp.MSDi.s.n)]
-  v.exp.MSDi.s.n = c(v.exp.MSDi.s.n, exp.MSDi.s.n)
   }
@@
   # Caluclate measures.
-R2.s.n = cor(theo.MSDi.s.n, exp.MSDi.s.n) ^ 2  
-MSE.s.n = mean((theo.MSDi.s.n - exp.MSDi.s.n) ^ 2)
+  R2 = cor(v.theo.MSDi, v.exp.MSDi) ^ 2  
+  MSE = mean((v.theo.MSDi - v.exp.MSDi) ^ 2)
 
+  v.v.theo.MSDi = c(v.v.theo.MSDi, v.theo.MSDi)
+  v.v.exp.MSDi = c(v.v.exp.MSDi, v.exp.MSDi)
+
+  v.R2 = c(v.R2, R2)
+  v.MSE = c(v.MSE, MSE)
+}
+
+n.sites.all.families = length(v.v.theo.MSDi)/4
 ```
 
-All families fitted smooth and normalized MSD profiles
+All families fitted smoothed and normalized MSD profiles with different selection regimens:
 
 ```{r}
-plot(theo.MSDi.s.n, type = "l", xlab = "site", ylab = "Theoretical")
+plot(v.v.theo.MSDi[1:n.sites.all.families], type = "l", main = " Strong selection", xlab = "site", ylab = "Merge")
+points(v.v.exp.MSDi[1:n.sites.all.families], col = "red", type = "l")
+legend("topleft", paste("R ^ 2", round(v.R2[1], digits = 3), "MSE", signif(v.MSE[1], digits = 4)), bty = "n", text.col = "red")
 ```
@@
 ```{r}
-plot(exp.MSDi.s.n, type = "l", col = "red", xlab = "site",  ylab = "Experimental")
+plot(v.v.theo.MSDi[(n.sites.all.families + 1):(2 * n.sites.all.families)], type = "l", main = " Medium selection", xlab = "site", ylab = "Merge")
+points(v.v.exp.MSDi[(n.sites.all.families + 1):(2 * n.sites.all.families)], col = "red", type = "l")
+legend("topleft", paste("R^2", round(v.R2[2], digits = 3), "MSE", signif(v.MSE[2], digits = 4)), bty = "n", text.col = "red")
 ```
@@
 ```{r}
-plot(theo.MSDi.s.n, type = "l", xlab = "site", ylab = "Merge")
-points(exp.MSDi.s.n, col = "red", type = "l")
-legend("topleft", paste("R^2", round(R2.s.n, digits = 2), " ", "MSE", signif(MSE.s.n, digits = 4)), bty = "n", text.col = "red")
+plot(v.v.theo.MSDi[((2 * n.sites.all.families) + 1):(3 * n.sites.all.families)], type = "l", main = " Weak selection", xlab = "site", ylab = "Merge")
+points(v.v.exp.MSDi[((2 * n.sites.all.families) + 1):(3 * n.sites.all.families)], col = "red", type = "l")
+legend("topleft", paste("R^2", round(v.R2[3], digits = 3), "MSE", signif(v.MSE[3], digits = 4)), bty = "n", text.col = "red")
 ```
+
+```{r}
+plot(v.v.theo.MSDi[((3 * n.sites.all.families) + 1):(4 * n.sites.all.families)], type = "l", main = " No selection", xlab = "site", ylab = "Merge")
+points(v.v.exp.MSDi[((3 * n.sites.all.families) + 1):(4 * n.sites.all.families)], col = "red", type = "l")
+legend("topleft", paste("R^2", round(v.R2[4], digits = 3), "MSE", signif(v.MSE[4], digits = 4)), bty = "n", text.col = "red")
+```
+
+*Black:* Theoretical mean.
+
+*Red:* Experimental mean.

### 2016-05-09 MultipleReportAllBetas.Rmd
cambios 09/05/2016

@@
 ```{r}
-
 # Source functions.
@@
 # Read betas.
-betas.fname.id <- paste(family, "_", p.ref, "_R0_", R0, sep = "")
-all.betas <- read.csv(file.path(out.dir, paste(betas.fname.id, "_out_all.betas.csv", sep = "")))
+all.betas <- list("strong.sel", "medium.sel", "weak.sel", "no.sel")
 
@@
 
-Los perfiles teoricos suavizados y normalizados de MSDi fueron fiteados con los perfiles exterimentales. Se compararon y se calcularon R^2 y MSE. Se indica el regimen de selección usada.
+Los perfiles teoricos suavizados y normalizados de MSDi fueron fiteados con los perfiles exterimentales. Se compararon y se calcularon R^2 y MSE. Se indica el regimen de selecci?n usada.
 

### 2016-05-09 MainProgram.R

@@ -1,9 +1,10 @@
 # Description:
 #
-# This is the main program of the project. The program simulates mutants of a given protein using different selection regimens 
-# , following the Stress Model, analyzes the multiple alignment of the family to which the protein belongs and calculates measures 
+# This is the main program of the project. The program simulates multiple mutants of a given protein using the "Linearly Forced - 
+# Elastic Network Model" (LFENM) and with different selection regimens according to the Stress Model. Then, the program
+# analyzes the multiple alignment of the family to which the protein belongs and calculates measures 
 # of variabilty of theoretical and experimental data.
-# To run the program it is necessary to fill the input file ("input_MainProgram.csv") with the following information:
+# To run the program it is necessary to fill the input ("input_MainProgram.csv") with the following information:
 #
 #    - family: The family of the protein to mutate. It can be "globins", "serinProteases", 
 #    "snakesToxin", "sh3", "fabp", "rrm", "phoslip" or "cys".
@@ -11,7 +12,7 @@
 #    the selected family. This pdbid must not be included in the dataset ("DATA/family_dataset.csv").
 #    - chain.p.ref: The chain of p.ref in the pdb file obtained from Homstrad.
 #    - n.mut.p: The number of mutants to generate for each member of the family. For example, if the family has 20 
-#    members, The program generates n.mut.p x 20 mutants.
+#    members, the program generates n.mut.p x 20 mutants.
 #    - fmax: Argument for "LFENM". It is the maximun value for the forces that model the mutations. 
 #    - R0: the Cut-off for the "ANM" (Anisotropic Network Model) that represents the proteins.
 #    - rotate: It can be "TRUE" or "FALSE". If it is "TRUE", r.p.2 is rotated in order to minimize RMSD with r.p.ref.
@@ -114,12 +115,13 @@ for (a in (1:nrow(input))) {
   
   # Read betas.
   all.betas <- read.csv(file.path(out.dir, paste(betas.fname.id, "_out_all.betas.csv", sep = "")))
+  regimens <- list("strong.sel", "medium.sel", "weak.sel", "no.sel")
   
   # Start a loop for each beta.
   for (beta in all.betas)  {
     
     # Generate ids for output filenames.
-    mut.fname.id <- paste(family, "_R0_", R0, "_beta_", beta, sep = "")
+    mut.fname.id <- paste(family, "_R0_", R0, "_beta_", regimens[all.betas == beta], sep = "")
[…]

### 2016-05-13 MultipleReportAllBetas.Rmd
cambios 13/05/2016

@@
 ```{r}
+# Load packages.
+library(bio3d)
+
 # Source functions.
@@
 
+# Write pdb files for MSDi.
+pdbs.fname <- file.path(data.dir, paste(family, "_coordinates.pdb", sep = ""))
+pdb = ReadCA(pdbs.fname, as.character(chain.p.ref))
+xyz.calpha = pdb$xyz.calpha
+
+MSDi.fit.pdb <- vec2resno(as.vector(MSDi.fit), sort(rep(1:ncol(xyz.calpha),3)))
+write.pdb(xyz = c(xyz.calpha), b = MSDi.fit.pdb * 100, file = file.path(out.dir, paste(family, "_", p.ref, "_beta_", beta, ".pdb", sep = "")))
+
+MSDi.exp.pdb <- vec2resno(as.vector(exp.smooth.norm.MSDi), sort(rep(1:ncol(xyz.calpha),3)))
+write.pdb(xyz = c(xyz.calpha), b = MSDi.exp.pdb * 100, file = file.path(out.dir, paste(family, "_", p.ref, "_exp", ".pdb", sep = "")))
 }

### 2016-05-13 MultipleReportAllBetas2.Rmd
cambios 13/05/2016

---
title: "Estudio variabilidad estructural proteica"
output: html_document
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(warning = FALSE, echo = FALSE, message = FALSE)
```

```{r}
# Source functions.
source("FUNCTIONS/CalculateGroupsMeansQuantiles.R")

# Set directories.
data.dir <- "DATA"
out.dir <- "OUT"

# p.ref.
n.sites.p.ref = read.csv(file.path(out.dir, paste(family, "_out_m.n.sites.p.ref.csv", sep = "")))$V1[1]

# Create matrices to save data.

# MSDi #
m.MSDi.fit = matrix(nrow = 4, ncol = n.sites.p.ref)
m.exp.MSDi = matrix(nrow = 4, ncol = n.sites.p.ref)
m.MSDi.R2 = matrix(nrow = 4, ncol = 1)
m.MSDi.MSE = matrix(nrow = 4, ncol = 1)

m.mean.theo.MSDi.group = matrix(nrow = 4, ncol = n.sites.p.ref)
m.theo.MSDi.group.quantile1 = matrix(nrow = 4, ncol = n.sites.p.ref)
m.theo.MSDi.group.quantile2 = matrix(nrow = 4, ncol = n.sites.p.ref)
m.theo.MSDi.quantile1.mean = matrix(nrow = 4, ncol = n.sites.p.ref)
m.theo.MSDi.quantile2.mean = matrix(nrow = 4, ncol = n.sites.p.ref)

m.mean.exp.MSDi = matrix(nrow = 4, ncol = n.sites.p.ref)
m.exp.MSDi.quantile1 = matrix(nrow = 4, ncol = n.sites.p.ref)
m.exp.MSDi.quantile2 = matrix(nrow = 4, ncol = n.sites.p.ref)

# Pn # 
m.Pn.fit = matrix(nrow = 4, ncol = 3 * n.sites.p.ref)
m.exp.Pn = matrix(nrow = 4, ncol = 3 * n.sites.p.ref)
m.Pn.R2 = matrix(nrow = 4, ncol = 1)
m.Pn.MSE = matrix(nrow = 4, ncol = 1)

m.mean.theo.Pn.group = matrix(nrow = 4, ncol = 3 * n.sites.p.ref)
m.theo.Pn.group.quantile1 = matrix(nrow = 4, ncol = 3 * n.sites.p.ref)
m.theo.Pn.group.quantile2 = matrix(nrow = 4, ncol = 3 * n.sites.p.ref)
m.theo.Pn.quantile1.mean = matrix(nrow = 4, ncol = 3 * n.sites.p.ref)
m.theo.Pn.quantile2.mean = matrix(nrow = 4, ncol = 3 * n.sites.p.ref)

m.mean.exp.Pn = matrix(nrow = 4, ncol = 3 * n.sites.p.ref)
m.exp.Pn.quantile1 = matrix(nrow = 4, ncol = 3 * n.sites.p.ref)
m.exp.Pn.quantile2 = matrix(nrow = 4, ncol = 3 * n.sites.p.ref)

# Read betas.
all.betas <- list("strong.sel", "medium.sel", "weak.sel", "no.sel")

  # Start a loop for each beta.
  for (beta in all.betas)  {

  ### Experimental ###
  analysis.fname.id <- paste(family, "_R0_", R0, "_beta_", beta, "_K.analysis_", K.analysis, sep = "")

  m.exp.Pn = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.exp.Pn.csv", sep = "")))[, 1:100]
  mean.exp.Pn = colMeans(m.exp.Pn)

  n.prot = nrow(m.exp.Pn)

  exp.Pn.quantile1 = matrix(ncol = ncol(m.exp.Pn), nrow = 1)
  exp.Pn.quantile2 = matrix(ncol = ncol(m.exp.Pn), nrow = 1)

  for (i in (1:ncol(m.exp.Pn))) {
      exp.Pn.quantiles = as.vector(quantile((m.exp.Pn[, i]), probs = c(0.05, 0.95)))
      exp.Pn.quantile1[1, i] = exp.Pn.quantiles[1]
      exp.Pn.quantile2[1, i] = exp.Pn.quantiles[2]
  }

  m.mean.exp.Pn[as.vector(all.betas == beta), 1:length(mean.exp.Pn)] = mean.exp.Pn
  m.exp.Pn.quantile1[as.vector(all.betas == beta), 1:length(exp.Pn.quantile1)] = exp.Pn.quantile1
  m.exp.Pn.quantile2[as.vector(all.betas == beta), 1:length(exp.Pn.quantile2)] = exp.Pn.quantile2

  m.exp.smooth.norm.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.exp.smooth.norm.dr.squarei.csv", sep = "")))
  exp.smooth.norm.MSDi = colMeans(m.exp.smooth.norm.dr.squarei, na.rm = T )

  exp.MSDi.quantile1 = matrix(ncol = ncol(m.exp.smooth.norm.MSDi), nrow = 1)
  exp.MSDi.quantile2 = matrix(ncol = ncol(m.exp.smooth.norm.MSDi), nrow = 1)

  for (i in (1:ncol(m.exp.smooth.norm.dr.squarei))) {
      exp.smooth.norm.dr.squarei.quantiles = as.vector(quantile((m.exp.smooth.norm.dr.squarei[, i]), probs = c(0.05, 0.95)))
      exp.smooth.norm.dr.squarei.quantile1[1, i] = exp.smooth.norm.dr.squarei.quantiles[1]
      exp.smooth.norm.dr.squarei.quantile2[1, i] = exp.smooth.norm.dr.squarei.quantiles[2]
  }

  m.mean.exp.MSDi[as.vector(all.betas == beta), 1:length(mean.exp.MSDi)] = mean.exp.MSDi
  m.exp.MSDi.quantile1[as.vector(all.betas == beta), 1:length(exp.smooth.norm.dr.squarei.quantile1)] = exp.MSDi.quantile1
  m.exp.smooth.norm.dr.squarei.quantile2[as.vector(all.betas == beta), 1:length(exp.smooth.norm.dr.squarei.quantile2)] = exp.smooth.norm.dr.squarei.quantile2

  ### Theoretical ###

  m.theo.Pn = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.Pn.csv", sep = "")))[, 1:100]

  n.mut = nrow(m.theo.Pn)

  m.theo.smooth.norm.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.smooth.norm.dr.squarei.csv", sep = "")))

  theo.smooth.norm.MSDi = colMeans(m.theo.smooth.norm.dr.squarei, na.rm = T )

  for (i in (1:n.sites.p.ref)) {
    fit = lm(exp.smooth.norm.MSDi ~ theo.smooth.norm.dr.squarei[i, 1:n.sites.p.ref] )
    MSDi.fit = fitted.values(fit)
    theo.smooth.norm.dr.squarei[i, 1:n.sites.p.ref] = MSDi.fit
  }

  # Re-ordenate m.theo.smooth.norm.dr.squarei.
  m.theo.index = matrix(ncol = 1, nrow = n.mut)
  for (P in (1:n.prot)) {
    for (mut in (1:n.mut.p)) {
      m.theo.index[(P - 1) * n.mut.p + mut, ] = ((mut - 1) * 10 + P)
    }
  }
  m.theo.smooth.norm.dr.squarei = m.theo.smooth.norm.dr.squarei[as.vector(m.theo.index), ]

  # Calculate groups, means and quantiles.
  theo.MSDi.group = CalculateGroupsMeansQuantiles(m.theo.smooth.norm.dr.squarei, n.mut.p, n.prot)
  mean.theo.MSDi.group = theo.MSDi.group$mean.mean.group
  theo.MSDi.group.quantile1 = theo.MSDi.group$mean.quantile1.group
  theo.MSDi.group.quantile2 = theo.MSDi.group$mean.quantile2.group
  theo.MSDi.quantile1.mean = theo.MSDi.group$quantile1.mean
  theo.MSDi.quantile2.mean = theo.MSDi.group$quantile2.mean

  m.mean.theo.MSDi.group[as.vector(all.betas == beta), 1:length(mean.theo.MSDi.group)] = mean.theo.MSDi.group
  m.theo.MSDi.group.quantile1[as.vector(all.betas == beta), 1:length(theo.MSDi.group.quantile1)] = theo.MSDi.group.quantile1
  m.theo.MSDi.group.quantile2[as.vector(all.betas == beta), 1:length(theo.MSDi.group.quantile2)] = theo.MSDi.group.quantile2
  m.theo.MSDi.quantile1.mean[as.vector(all.betas == beta), 1:length(theo.MSDi.quantile1.mean)] = theo.MSDi.quantile1.mean
  m.theo.MSDi.quantile2.mean[as.vector(all.betas == beta), 1:length(theo.MSDi.quantile2.mean)] = theo.MSDi.quantile2.mean

  MSDi.R2 = cor(exp.smooth.norm.MSDi[!is.na(exp.smooth.norm.MSDi)], mean.theo.MSDi.group) ^ 2 
    MSDi.MSE = mean((mean.theo.MSDi.group - exp.smooth.norm.MSDi[!is.na(exp.smooth.norm.MSDi)]) ^ 2)
  exp.smooth.norm.MSDi = exp.smooth.norm.MSDi[!is.na(exp.smooth.norm.MSDi)]

  m.MSDi.fit[as.vector(all.betas == beta), ] = mean.theo.MSDi.group
  m.MSDi.R2[as.vector(all.betas == beta), ] = MSDi.R2
  m.MSDi.MSE[as.vector(all.betas == beta), ] = MSDi.MSE
  m.exp.MSDi[as.vector(all.betas == beta), ] = exp.smooth.norm.MSDi

  ### Pn ###

  # Re-ordenate Pn.
  m.theo.index = matrix(ncol = 1, nrow = n.mut)
  for (P in (1:n.prot)) {
    for (mut in (1:n.mut.p)) {
      m.theo.index[(P - 1) * n.mut.p + mut, ] = ((mut - 1) * 10 + P)
    }
  }
  m.theo.Pn = m.theo.Pn[as.vector(m.theo.index), ]

  # Calculate groups, means and quantiles.
  theo.Pn.group = CalculateGroupsMeansQuantiles(m.theo.Pn, n.mut.p, n.prot)
  mean.theo.Pn.group = theo.Pn.group$mean.mean.group
  theo.Pn.group.quantile1 = theo.Pn.group$mean.quantile1.group
  theo.Pn.group.quantile2 = theo.Pn.group$mean.quantile2.group
  theo.Pn.quantile1.mean = theo.Pn.group$quantile1.mean
  theo.Pn.quantile2.mean = theo.Pn.group$quantile2.mean

  m.mean.theo.Pn.group[as.vector(all.betas == beta), 1:length(mean.theo.Pn.group)] = mean.theo.Pn.group
  m.theo.Pn.group.quantile1[as.vector(all.betas == beta), 1:length(theo.Pn.group.quantile1)] = theo.Pn.group.quantile1
  m.theo.Pn.group.quantile2[as.vector(all.betas == beta), 1:length(theo.Pn.group.quantile2)] = theo.Pn.group.quantile2
  m.theo.Pn.quantile1.mean[as.vector(all.betas == beta), 1:length(theo.Pn.quantile1.mean)] = theo.Pn.quantile1.mean
  m.theo.Pn.quantile2.mean[as.vector(all.betas == beta), 1:length(theo.Pn.quantile2.mean)] = theo.Pn.quantile2.mean

Pn.fit = lm(mean.exp.Pn ~  mean.theo.Pn.group)
Pn.fit = fitted.values(Pn.fit)
Pn.R2 = cor(mean.exp.Pn, Pn.fit) ^ 2 
Pn.MSE = mean((Pn.fit - mean.exp.Pn) ^ 2)

m.Pn.fit[as.vector(all.betas == beta), 1:(length(Pn.fit))] = Pn.fit
m.Pn.R2[as.vector(all.betas == beta), ] = Pn.R2
m.Pn.MSE[as.vector(all.betas == beta), ] = Pn.MSE
m.mean.exp.Pn[as.vector(all.betas == beta), 1:(length(mean.exp.Pn))] = mean.exp.Pn
}

```

### MSDi

Los perfiles teoricos suavizados y normalizados de MSDi fueron fiteados con los perfiles exterimentales. Se compararon y se calcularon R^2 y MSE. Se indica el regimen de selecci?n usada.

```{r}
layout(matrix(1:4, 2, 2, byrow = T))

plot(m.mean.theo.MSDi.group[1, 1:100], 
     main = "MSDi strong selection", 
     xlab = "mode",
     ylab = "MSDi",
     ylim = c(0, max(c(m.theo.MSDi.group.quantile2[1, 1:100], m.mean.exp.MSDi[1, 1:100]))))
lines(m.theo.MSDi.group.quantile1[1, ])
lines(m.theo.MSDi.group.quantile2[1, ])
points(m.mean.exp.MSDi[1, ], col = "red")
lines(as.vector(m.exp.MSDi.quantile1[1, ]), col = "red")
lines(as.vector(m.exp.MSDi.quantile2[1, ]), col = "red")

plot(m.mean.theo.MSDi.group[2, 1:100], 
     main = "MSDi medium selection", 
     xlab = "mode",
     ylab = "MSDi",
     ylim = c(0, max(c(m.theo.MSDi.group.quantile2[2, 1:100], m.mean.exp.MSDi[2, 1:100]))))
lines(m.theo.MSDi.group.quantile1[2, ])
lines(m.theo.MSDi.group.quantile2[2, ])
points(m.mean.exp.MSDi[2, ], col = "red")
lines(as.vector(m.exp.MSDi.quantile1[2, ]), col = "red")
lines(as.vector(m.exp.MSDi.quantile2[2, ]), col = "red")

plot(m.mean.theo.MSDi.group[3, 1:100], 
     main = "MSDi weak selection", 
     xlab = "mode",
     ylab = "MSDi",
     ylim = c(0, max(c(m.theo.MSDi.group.quantile2[3, 1:100], m.mean.exp.MSDi[3, 1:100]))))
lines(m.theo.MSDi.group.quantile1[3, ])
lines(m.theo.MSDi.group.quantile2[3, ])
points(m.mean.exp.MSDi[3, ], col = "red")
lines(as.vector(m.exp.MSDi.quantile1[3, ]), col = "red")
lines(as.vector(m.exp.MSDi.quantile2[3, ]), col = "red")

plot(m.mean.theo.MSDi.group[4, 1:100], 
     main = "MSDi no selection", 
     xlab = "mode",
     ylab = "MSDi",
     ylim = c(0, max(c(m.theo.MSDi.group.quantile2[4, 1:100], m.mean.exp.MSDi[4, 1:100]))))
lines(m.theo.MSDi.group.quantile1[4, ])
lines(m.theo.MSDi.group.quantile2[4, ])
points(m.mean.exp.MSDi[4, ], col = "red")
lines(as.vector(m.exp.MSDi.quantile1[4, ]), col = "red")
lines(as.vector(m.exp.MSDi.quantile2[4, ]), col = "red")

```

*Negro*: Puntos: promedio de promedios teorico. Lineas: promedio de cuantiles 0.05 y 0.95 de `r n.mut.p` grupos de `r n.prot` mutantes teoricas.

*Rojo*: Puntos: promedio experimental. Lineas: cuantiles 0.05 y 0.95 experimentales.

```{r}
layout(matrix(1:4, 2, 2, byrow = T))

plot(m.mean.theo.MSDi.group[1, 1:100], 
     main = "MSDi strong selection", 
     xlab = "mode",
     ylab = "MSDi",
     ylim = c(0, max(c(m.theo.MSDi.group.quantile2[1, 1:100], m.mean.exp.MSDi[1, 1:100]))))
lines(as.vector(m.theo.MSDi.quantile1.mean[1, ]))
lines(as.vector(m.theo.MSDi.quantile2.mean[1, ]))
points(m.mean.exp.MSDi[1, ], col = "red")

plot(m.mean.theo.MSDi.group[2, 1:100], 
     main = "MSDi medium selection", 
     xlab = "mode",
     ylab = "MSDi",
     ylim = c(0, max(c(m.theo.MSDi.group.quantile2[2, 1:100], m.mean.exp.MSDi[2, 1:100]))))
lines(as.vector(m.theo.MSDi.quantile1.mean[2, ]))
lines(as.vector(m.theo.MSDi.quantile2.mean[2, ]))
points(m.mean.exp.MSDi[2, ], col = "red")

plot(m.mean.theo.MSDi.group[3, 1:100], 
     main = "MSDi weak selection", 
     xlab = "mode",
     ylab = "MSDi",
     ylim = c(0, max(c(m.theo.MSDi.group.quantile2[3, 1:100], m.mean.exp.MSDi[3, 1:100]))))
lines(as.vector(m.theo.MSDi.quantile1.mean[3, ]))
lines(as.vector(m.theo.MSDi.quantile2.mean[3, ]))
points(m.mean.exp.MSDi[3, ], col = "red")

plot(m.mean.theo.MSDi.group[4, 1:100], 
     main = "MSDi no selection", 
     xlab = "mode",
     ylab = "MSDi",
     ylim = c(0, max(c(m.theo.MSDi.group.quantile2[4, 1:100], m.mean.exp.MSDi[4, 1:100]))))
lines(as.vector(m.theo.MSDi.quantile1.mean[4, ]))
lines(as.vector(m.theo.MSDi.quantile2.mean[4, ]))
points(m.mean.exp.MSDi[4, ], col = "red")

```

*Negro*: Puntos: promedio de promedios teorico. Lineas:  cuantiles 0.05 y 0.95 de promedios de `r n.mut.p` grupos de `r n.prot` mutantes teoricas.

*Rojo*: Promedio experimental.

```{r}
layout(matrix(1:4, 2, 2, byrow = T)) 
plot(m.mean.theo.MSDi.group[1, ], m.mean.exp.MSDi[1, ], xlab = "<<MSDi>> teorico", ylab = "<MSDi> experimental", main = "MSDi strong selection")
abline(0, 1)
legend("topleft", paste("R^2", round(m.MSDi.R2[1, ], digits = 2)), bty = "n", text.col = "red")
legend("bottomright", paste("MSE", signif(m.MSDi.MSE[1, ], digits = 2)), bty = "n", text.col = "red")

plot(m.mean.theo.MSDi.group[2, ], m.mean.exp.MSDi[2, ], xlab = "<<MSDi>> teorico", ylab = "<MSDi> experimental", main = "MSDi medium selection")
abline(0, 1)
legend("topleft", paste("R^2", round(m.MSDi.R2[2, ], digits = 2)), bty = "n", text.col = "red")
legend("bottomright", paste("MSE", signif(m.MSDi.MSE[2, ], digits = 2)), bty = "n", text.col = "red")

plot(m.mean.theo.MSDi.group[3, ], m.mean.exp.MSDi[3, ], xlab = "<<MSDi>> teorico", ylab = "<MSDi> experimental", main = "MSDi weak selection")
abline(0, 1)
legend("topleft", paste("R^2", round(m.MSDi.R2[3, ], digits = 2)), bty = "n", text.col = "red")
legend("bottomright", paste("MSE", signif(m.MSDi.MSE[3, ], digits = 2)), bty = "n", text.col = "red")

plot(m.mean.theo.MSDi.group[4, ], m.mean.exp.MSDi[4, ], xlab = "<<MSDi>> teorico", ylab = "<MSDi> experimental", main = "MSDi no selection")
abline(0, 1)
legend("topleft", paste("R^2", round(m.MSDi.R2[4, ], digits = 2)), bty = "n", text.col = "red")
legend("bottomright", paste("MSE", signif(m.MSDi.MSE[4, ], digits = 2)), bty = "n", text.col = "red")

```

### Pn y Qn
Las distribuciones de *Pn* y *Qn* de los conjuntos son las siguientes:

```{r}
layout(matrix(1:4, 2, 2, byrow = T))

plot(m.mean.theo.Pn.group[1, 1:100], 
     main = "Pn strong selection", 
     xlab = "site",
     ylab = "Pn",
     ylim = c(0, max(c(m.theo.Pn.group.quantile2[1, 1:100], m.mean.exp.Pn[1, 1:100]))))
lines(m.theo.Pn.group.quantile1[1, ])
lines(m.theo.Pn.group.quantile2[1, ])
points(m.mean.exp.Pn[1, ], col = "red")
lines(as.vector(m.exp.Pn.quantile1[1, ]), col = "red")
lines(as.vector(m.exp.Pn.quantile2[1, ]), col = "red")

plot(m.mean.theo.Pn.group[2, 1:100], 
     main = "Pn medium selection", 
     xlab = "site",
     ylab = "Pn",
     ylim = c(0, max(c(m.theo.Pn.group.quantile2[2, 1:100], m.mean.exp.Pn[2, 1:100]))))
lines(m.theo.Pn.group.quantile1[2, ])
lines(m.theo.Pn.group.quantile2[2, ])
points(m.mean.exp.Pn[2, ], col = "red")
lines(as.vector(m.exp.Pn.quantile1[2, ]), col = "red")
lines(as.vector(m.exp.Pn.quantile2[2, ]), col = "red")

plot(m.mean.theo.Pn.group[3, 1:100], 
     main = "Pn weak selection", 
     xlab = "site",
     ylab = "Pn",
     ylim = c(0, max(c(m.theo.Pn.group.quantile2[3, 1:100], m.mean.exp.Pn[3, 1:100]))))
lines(m.theo.Pn.group.quantile1[3, ])
lines(m.theo.Pn.group.quantile2[3, ])
points(m.mean.exp.Pn[3, ], col = "red")
lines(as.vector(m.exp.Pn.quantile1[3, ]), col = "red")
lines(as.vector(m.exp.Pn.quantile2[3, ]), col = "red")

plot(m.mean.theo.Pn.group[4, 1:100], 
     main = "Pn no selection", 
     xlab = "site",
     ylab = "Pn",
     ylim = c(0, max(c(m.theo.Pn.group.quantile2[4, 1:100], m.mean.exp.Pn[4, 1:100]))))
lines(m.theo.Pn.group.quantile1[4, ])
lines(m.theo.Pn.group.quantile2[4, ])
points(m.mean.exp.Pn[4, ], col = "red")
lines(as.vector(m.exp.Pn.quantile1[4, ]), col = "red")
lines(as.vector(m.exp.Pn.quantile2[4, ]), col = "red")

```

*Negro*: Puntos: promedio de promedios teorico. Lineas: promedio de cuantiles 0.05 y 0.95 de `r n.mut.p` grupos de `r n.prot` mutantes teoricas.

*Rojo*: Puntos: promedio experimental. Lineas: cuantiles 0.05 y 0.95 experimentales.

```{r}
layout(matrix(1:4, 2, 2, byrow = T))

plot(m.mean.theo.Pn.group[1, 1:100], 
     main = "Pn strong selection", 
     xlab = "site",
     ylab = "Pn",
     ylim = c(0, max(c(m.theo.Pn.group.quantile2[1, 1:100], m.mean.exp.Pn[1, 1:100]))))
lines(as.vector(m.theo.Pn.quantile1.mean[1, ]))
lines(as.vector(m.theo.Pn.quantile2.mean[1, ]))
points(m.mean.exp.Pn[1, ], col = "red")

plot(m.mean.theo.Pn.group[2, 1:100], 
     main = "Pn medium selection", 
     xlab = "site",
     ylab = "Pn",
     ylim = c(0, max(c(m.theo.Pn.group.quantile2[2, 1:100], m.mean.exp.Pn[2, 1:100]))))
lines(as.vector(m.theo.Pn.quantile1.mean[2, ]))
lines(as.vector(m.theo.Pn.quantile2.mean[2, ]))
points(m.mean.exp.Pn[2, ], col = "red")

plot(m.mean.theo.Pn.group[3, 1:100], 
     main = "Pn weak selection", 
     xlab = "site",
     ylab = "Pn",
     ylim = c(0, max(c(m.theo.Pn.group.quantile2[3, 1:100], m.mean.exp.Pn[3, 1:100]))))
lines(as.vector(m.theo.Pn.quantile1.mean[3, ]))
lines(as.vector(m.theo.Pn.quantile2.mean[3, ]))
points(m.mean.exp.Pn[3, ], col = "red")

plot(m.mean.theo.Pn.group[4, 1:100], 
     main = "Pn no selection", 
     xlab = "site",
     ylab = "Pn",
     ylim = c(0, max(c(m.theo.Pn.group.quantile2[4, 1:100], m.mean.exp.Pn[4, 1:100]))))
lines(as.vector(m.theo.Pn.quantile1.mean[4, ]))
lines(as.vector(m.theo.Pn.quantile2.mean[4, ]))
points(m.mean.exp.Pn[4, ], col = "red")

```

*Negro*: Puntos: promedio de promedios teorico. Lineas:  cuantiles 0.05 y 0.95 de promedios de `r n.mut.p` grupos de `r n.prot` mutantes teoricas.

*Rojo*: Promedio experimental.

```{r}
layout(matrix(1:4, 2, 2, byrow = T)) 
plot(m.mean.theo.Pn.group[1, ], m.mean.exp.Pn[1, ], xlab = "<<Pn>> teorico", ylab = "<Pn> experimental", main = "Pn strong selection")
abline(0, 1)
legend("topleft", paste("R^2", round(m.Pn.R2[1, ], digits = 2)), bty = "n", text.col = "red")
legend("bottomright", paste("MSE", signif(m.Pn.MSE[1, ], digits = 2)), bty = "n", text.col = "red")

plot(m.mean.theo.Pn.group[2, ], m.mean.exp.Pn[2, ], xlab = "<<Pn>> teorico", ylab = "<Pn> experimental", main = "Pn medium selection")
abline(0, 1)
legend("topleft", paste("R^2", round(m.Pn.R2[2, ], digits = 2)), bty = "n", text.col = "red")
legend("bottomright", paste("MSE", signif(m.Pn.MSE[2, ], digits = 2)), bty = "n", text.col = "red")

plot(m.mean.theo.Pn.group[3, ], m.mean.exp.Pn[3, ], xlab = "<<Pn>> teorico", ylab = "<Pn> experimental", main = "Pn weak selection")
abline(0, 1)
legend("topleft", paste("R^2", round(m.Pn.R2[3, ], digits = 2)), bty = "n", text.col = "red")
legend("bottomright", paste("MSE", signif(m.Pn.MSE[3, ], digits = 2)), bty = "n", text.col = "red")

plot(m.mean.theo.Pn.group[4, ], m.mean.exp.Pn[4, ], xlab = "<<Pn>> teorico", ylab = "<Pn> experimental", main = "Pn no selection")
abline(0, 1)
legend("topleft", paste("R^2", round(m.Pn.R2[4, ], digits = 2)), bty = "n", text.col = "red")
legend("bottomright", paste("MSE", signif(m.Pn.MSE[4, ], digits = 2)), bty = "n", text.col = "red")

```

### 2016-05-13 MultipleReportAllBetas3.Rmd
cambios 13/05/2016

--- 2016-05-13 MultipleReportAllBetas2.Rmd
@@
 
-  exp.MSDi.quantile1 = matrix(ncol = ncol(m.exp.smooth.norm.MSDi), nrow = 1)
-  exp.MSDi.quantile2 = matrix(ncol = ncol(m.exp.smooth.norm.MSDi), nrow = 1)
+  exp.MSDi.quantile1 = matrix(ncol = ncol(m.exp.MSDi), nrow = 1)
+  exp.MSDi.quantile2 = matrix(ncol = ncol(m.exp.MSDi), nrow = 1)
 
-  for (i in (1:ncol(m.exp.smooth.norm.dr.squarei))) {
-      exp.smooth.norm.dr.squarei.quantiles = as.vector(quantile((m.exp.smooth.norm.dr.squarei[, i]), probs = c(0.05, 0.95)))
-      exp.smooth.norm.dr.squarei.quantile1[1, i] = exp.smooth.norm.dr.squarei.quantiles[1]
-      exp.smooth.norm.dr.squarei.quantile2[1, i] = exp.smooth.norm.dr.squarei.quantiles[2]
+  for (i in (1:n.sites.p.ref)) {
+      exp.smooth.norm.dr.squarei.quantiles = as.vector(quantile((m.exp.smooth.norm.dr.squarei[, i]), probs = c(0.05, 0.95), na.rm = T))
+      exp.MSDi.quantile1[1, i] = exp.smooth.norm.dr.squarei.quantiles[1]
+      exp.MSDi.quantile2[1, i] = exp.smooth.norm.dr.squarei.quantiles[2]
   }
 
-  m.mean.exp.MSDi[as.vector(all.betas == beta), 1:length(mean.exp.MSDi)] = mean.exp.MSDi
-  m.exp.MSDi.quantile1[as.vector(all.betas == beta), 1:length(exp.smooth.norm.dr.squarei.quantile1)] = exp.MSDi.quantile1
-  m.exp.smooth.norm.dr.squarei.quantile2[as.vector(all.betas == beta), 1:length(exp.smooth.norm.dr.squarei.quantile2)] = exp.smooth.norm.dr.squarei.quantile2
+  m.mean.exp.MSDi[as.vector(all.betas == beta), 1:n.sites.p.ref] = exp.smooth.norm.MSDi[1:n.sites.p.ref]
+  m.exp.MSDi.quantile1[as.vector(all.betas == beta), 1:length(exp.MSDi.quantile1)] = exp.MSDi.quantile1
+  m.exp.MSDi.quantile2[as.vector(all.betas == beta), 1:length(exp.MSDi.quantile2)] = exp.MSDi.quantile2
 
@@
   for (i in (1:n.sites.p.ref)) {
-    fit = lm(exp.smooth.norm.MSDi ~ theo.smooth.norm.dr.squarei[i, 1:n.sites.p.ref] )
+    fit = lm(exp.smooth.norm.MSDi[1:n.sites.p.ref] ~ as.numeric(m.theo.smooth.norm.dr.squarei[i, 1:n.sites.p.ref]))
     MSDi.fit = fitted.values(fit)
-    theo.smooth.norm.dr.squarei[i, 1:n.sites.p.ref] = MSDi.fit
+    m.theo.smooth.norm.dr.squarei[i, 1:n.sites.p.ref] = MSDi.fit
   }
@@
   theo.MSDi.group = CalculateGroupsMeansQuantiles(m.theo.smooth.norm.dr.squarei, n.mut.p, n.prot)
-  mean.theo.MSDi.group = theo.MSDi.group$mean.mean.group
-  theo.MSDi.group.quantile1 = theo.MSDi.group$mean.quantile1.group
-  theo.MSDi.group.quantile2 = theo.MSDi.group$mean.quantile2.group
-  theo.MSDi.quantile1.mean = theo.MSDi.group$quantile1.mean
-  theo.MSDi.quantile2.mean = theo.MSDi.group$quantile2.mean
+  mean.theo.MSDi.group = theo.MSDi.group$mean.mean.group[1:n.sites.p.ref]
+  theo.MSDi.group.quantile1 = theo.MSDi.group$mean.quantile1.group[1:n.sites.p.ref]
+  theo.MSDi.group.quantile2 = theo.MSDi.group$mean.quantile2.group[1:n.sites.p.ref]
+  theo.MSDi.quantile1.mean = theo.MSDi.group$quantile1.mean[1:n.sites.p.ref]
+  theo.MSDi.quantile2.mean = theo.MSDi.group$quantile2.mean[1:n.sites.p.ref]
 
@@
 
-plot(m.mean.theo.MSDi.group[1, 1:100], 
+plot(m.mean.theo.MSDi.group[1, ], 
      main = "MSDi strong selection", 
@@
      ylab = "MSDi",
-     ylim = c(0, max(c(m.theo.MSDi.group.quantile2[1, 1:100], m.mean.exp.MSDi[1, 1:100]))))
+     ylim = c(0, max(c(m.theo.MSDi.group.quantile2, m.mean.exp.MSDi))))
 lines(m.theo.MSDi.group.quantile1[1, ])
@@
 
-plot(m.mean.theo.MSDi.group[2, 1:100], 
+plot(m.mean.theo.MSDi.group[2, ], 
      main = "MSDi medium selection", 
@@
      ylab = "MSDi",
-     ylim = c(0, max(c(m.theo.MSDi.group.quantile2[2, 1:100], m.mean.exp.MSDi[2, 1:100]))))
+     ylim = c(0, max(c(m.theo.MSDi.group.quantile2[2,], m.mean.exp.MSDi[2,]))))
 lines(m.theo.MSDi.group.quantile1[2, ])
@@
 
-plot(m.mean.theo.MSDi.group[3, 1:100], 
+plot(m.mean.theo.MSDi.group[3, ], 
      main = "MSDi weak selection", 
@@
      ylab = "MSDi",
-     ylim = c(0, max(c(m.theo.MSDi.group.quantile2[3, 1:100], m.mean.exp.MSDi[3, 1:100]))))
+     ylim = c(0, max(c(m.theo.MSDi.group.quantile2[3, ], m.mean.exp.MSDi[3, ]))))
 lines(m.theo.MSDi.group.quantile1[3, ])
@@
 
-plot(m.mean.theo.MSDi.group[4, 1:100], 
+plot(m.mean.theo.MSDi.group[4, ], 
      main = "MSDi no selection", 
@@
      ylab = "MSDi",
-     ylim = c(0, max(c(m.theo.MSDi.group.quantile2[4, 1:100], m.mean.exp.MSDi[4, 1:100]))))
+     ylim = c(0, max(c(m.theo.MSDi.group.quantile2[4, ], m.mean.exp.MSDi[4, ]))))
 lines(m.theo.MSDi.group.quantile1[4, ])
@@
      ylab = "MSDi",
-     ylim = c(0, max(c(m.theo.MSDi.group.quantile2[1, 1:100], m.mean.exp.MSDi[1, 1:100]))))
+     ylim = c(0, max(c(m.theo.MSDi.group.quantile2[1, ], m.mean.exp.MSDi[1, ]))))
 lines(as.vector(m.theo.MSDi.quantile1.mean[1, ]))
@@
      ylab = "MSDi",
-     ylim = c(0, max(c(m.theo.MSDi.group.quantile2[2, 1:100], m.mean.exp.MSDi[2, 1:100]))))
+     ylim = c(0, max(c(m.theo.MSDi.group.quantile2[2, ], m.mean.exp.MSDi[2, ]))))
 lines(as.vector(m.theo.MSDi.quantile1.mean[2, ]))
@@
      ylab = "MSDi",
-     ylim = c(0, max(c(m.theo.MSDi.group.quantile2[3, 1:100], m.mean.exp.MSDi[3, 1:100]))))
+     ylim = c(0, max(c(m.theo.MSDi.group.quantile2[3, ], m.mean.exp.MSDi[3, ]))))
 lines(as.vector(m.theo.MSDi.quantile1.mean[3, ]))
@@
      ylab = "MSDi",
-     ylim = c(0, max(c(m.theo.MSDi.group.quantile2[4, 1:100], m.mean.exp.MSDi[4, 1:100]))))
+     ylim = c(0, max(c(m.theo.MSDi.group.quantile2[4, ], m.mean.exp.MSDi[4, ]))))
 lines(as.vector(m.theo.MSDi.quantile1.mean[4, ]))

### 2016-05-13 MainMultipleReport.R

@@ -1,30 +1,0 @@
-# Load packages.
-library(knitr)
-library(markdown)
-
-# Read input.
-input.fname <- file.path("input_MainMultipleReport.csv")
-input <- read.csv(input.fname)
-
-# Satart a loop for each family.
-for (a in (1:nrow(input))) { 
-  print(a)
-  family <- as.character(input$family)[a]
-  p.ref <- as.character(input$p.ref)[a]
-  chain.p.ref = input$chain.p.ref[a]
-  n.mut.p = input$n.mut.p[a]
-  R0 = input$R0[a]
-  K.analysis = input$K.analysis[a]
-  
-  # Read betas.
-  betas.fname.id <- paste(family, "_", p.ref, "_R0_", R0, sep = "")
-  all.betas <- read.csv(file.path(out.dir, paste(betas.fname.id, "_out_all.betas.csv", sep = "")))
-  
-  # Start a loop for each beta.
-  for (beta in all.betas)  {
-    
-    # Generate a report.
-    rmarkdown::render('MultipleReport.Rmd', 
-                      output_file =  paste("report_", family, "_R0_", R0, "_beta_", beta, "_K.analysis_", K.analysis, ".html", sep = ''))
-  }
-}

### 2016-05-23 AllFamilys.Rmd
cambios 23/05/2016

@@
 author: "Maria Laura Marcos"
-output: html_document
+output: pdf_document
 ---

### 2016-05-23 MultipleReportAllBetas.Rmd
cambios 23/05/2016

--- 2016-05-09 MultipleReportAllBetas.Rmd
@@
 
+# Write pdb files for MSDi.
+pdbs.fname <- file.path(data.dir, paste(family, "_coordinates.pdb", sep = ""))
+pdb = ReadCA(pdbs.fname, as.character(chain.p.ref))
+xyz.calpha = pdb$xyz.calpha
+
+MSDi.fit.pdb <- vec2resno(as.vector(MSDi.fit), sort(rep(1:ncol(xyz.calpha),3)))
+write.pdb(xyz = c(xyz.calpha), b = MSDi.fit.pdb, file = file.path(out.dir, paste(family, "_", p.ref, "_beta_", beta, ".pdb", sep = "")))
+
+MSDi.exp.pdb <- vec2resno(as.vector(exp.smooth.norm.MSDi), sort(rep(1:ncol(xyz.calpha),3)))
+write.pdb(xyz = c(xyz.calpha), b = MSDi.exp.pdb, file = file.path(out.dir, paste(family, "_", p.ref, "_exp", ".pdb", sep = "")))
 }

### 2016-06-05 MultipleReportAllBetas.Rmd
cambios 05/06/2016

@@
 m.exp.MSDi = matrix(nrow = 4, ncol = n.sites.p.ref)
+m.exp.MSDi.sd = matrix(nrow = 4, ncol = n.sites.p.ref)
 m.MSDi.R2 = matrix(nrow = 4, ncol = 1)
@@
 m.mean.theo.Pn.group = matrix(nrow = 4, ncol = 3 * n.sites.p.ref)
-m.theo.Pn.group.quantile1 = matrix(nrow = 4, ncol = 3 * n.sites.p.ref)
-m.theo.Pn.group.quantile2 = matrix(nrow = 4, ncol = 3 * n.sites.p.ref)
-m.theo.Pn.quantile1.mean = matrix(nrow = 4, ncol = 3 * n.sites.p.ref)
-m.theo.Pn.quantile2.mean = matrix(nrow = 4, ncol = 3 * n.sites.p.ref)
-
 m.mean.exp.Pn = matrix(nrow = 4, ncol = 3 * n.sites.p.ref)
-m.exp.Pn.quantile1 = matrix(nrow = 4, ncol = 3 * n.sites.p.ref)
-m.exp.Pn.quantile2 = matrix(nrow = 4, ncol = 3 * n.sites.p.ref)
+m.exp.Pn.sd = matrix(nrow = 4, ncol = 3 * n.sites.p.ref)
 
@@
     m.exp.Pn = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.exp.Pn.csv", sep = "")))[, 1:100]
-  mean.exp.Pn = colMeans(m.exp.Pn)
-
     n.prot = nrow(m.exp.Pn)
 
-  exp.Pn.quantile1 = matrix(ncol = ncol(m.exp.Pn), nrow = 1)
-  exp.Pn.quantile2 = matrix(ncol = ncol(m.exp.Pn), nrow = 1)
-
-  for (i in (1:ncol(m.exp.Pn))) {
-      exp.Pn.quantiles = as.vector(quantile((m.exp.Pn[, i]), probs = c(0.05, 0.95)))
-      exp.Pn.quantile1[1, i] = exp.Pn.quantiles[1]
-      exp.Pn.quantile2[1, i] = exp.Pn.quantiles[2]
-  }
+    mean.exp.Pn = colMeans(m.exp.Pn)
+    exp.Pn.sd = apply(m.exp.Pn, 2, sd, na.rm = T)
 
     m.mean.exp.Pn[as.vector(all.betas == beta), 1:length(mean.exp.Pn)] = mean.exp.Pn
-  m.exp.Pn.quantile1[as.vector(all.betas == beta), 1:length(exp.Pn.quantile1)] = exp.Pn.quantile1
-  m.exp.Pn.quantile2[as.vector(all.betas == beta), 1:length(exp.Pn.quantile2)] = exp.Pn.quantile2
 
@@
     exp.smooth.norm.MSDi = colMeans(m.exp.smooth.norm.dr.squarei, na.rm = T )
+    exp.smooth.norm.MSDi.sd = apply(m.exp.smooth.norm.dr.squarei, 2, sd, na.rm = T)
 
@@
     m.exp.MSDi[as.vector(all.betas == beta), ] = exp.smooth.norm.MSDi
+    m.exp.MSDi.sd[as.vector(all.betas == beta), ] = exp.smooth.norm.MSDi.sd[!is.na(exp.smooth.norm.MSDi.sd)]
 
     ### Pn ###
-
-  # Re-ordenate Pn.
-  m.theo.index = matrix(ncol = 1, nrow = n.mut)
-  for (P in (1:n.prot)) {
-    for (mut in (1:n.mut.p)) {
-      m.theo.index[(P - 1) * n.mut.p + mut, ] = ((mut - 1) * 10 + P)
-    }
-  }
-  m.theo.Pn = m.theo.Pn[as.vector(m.theo.index), ]
 
@@
   mean.theo.Pn.group = theo.Pn.group$mean.mean.group
-  theo.Pn.group.quantile1 = theo.Pn.group$mean.quantile1.group
-  theo.Pn.group.quantile2 = theo.Pn.group$mean.quantile2.group
-  theo.Pn.quantile1.mean = theo.Pn.group$quantile1.mean
-  theo.Pn.quantile2.mean = theo.Pn.group$quantile2.mean
 
   m.mean.theo.Pn.group[as.vector(all.betas == beta), 1:length(mean.theo.Pn.group)] = mean.theo.Pn.group
-  m.theo.Pn.group.quantile1[as.vector(all.betas == beta), 1:length(theo.Pn.group.quantile1)] = theo.Pn.group.quantile1
-  m.theo.Pn.group.quantile2[as.vector(all.betas == beta), 1:length(theo.Pn.group.quantile2)] = theo.Pn.group.quantile2
-  m.theo.Pn.quantile1.mean[as.vector(all.betas == beta), 1:length(theo.Pn.quantile1.mean)] = theo.Pn.quantile1.mean
-  m.theo.Pn.quantile2.mean[as.vector(all.betas == beta), 1:length(theo.Pn.quantile2.mean)] = theo.Pn.quantile2.mean
 
@@
   m.mean.exp.Pn[as.vector(all.betas == beta), 1:(length(mean.exp.Pn))] = mean.exp.Pn
+  m.exp.Pn.sd[as.vector(all.betas == beta), 1:(length(exp.Pn.sd))] = exp.Pn.sd
 
@@
   MSDi.exp.pdb <- vec2resno(as.vector(exp.smooth.norm.MSDi), sort(rep(1:ncol(xyz.calpha),3)))
-write.pdb(xyz = c(xyz.calpha), b = MSDi.exp.pdb, file = file.path(out.dir, paste(family, "_", p.ref, "_exp", ".pdb", sep = "")))
+  write.pdb(xyz = c(xyz.calpha), b = MSDi.exp.pdb, file = file.path(out.dir, paste(family, "_", p.ref, "_exp", ".pdb", sep ="")))
 }
@@
 
-Los perfiles teoricos suavizados y normalizados de MSDi fueron fiteados con los perfiles exterimentales. Se compararon y se calcularon R^2 y MSE. Se indica el regimen de selecci?n usada.
+Los perfiles teoricos suavizados y normalizados de MSDi fueron fiteados con los perfiles exterimentales. Se compararon y se calcularon R^2 y MSE. Se indica el regimen de seleccion usada.
 
@@
 
-plot(as.numeric(m.MSDi.fit[1, ]), xlab = "site", main = "MSDi strong selection", ylab = "MSDi", ylim = c(0,5))
-points(m.exp.MSDi[1, ], col = "red")
-legend("topleft", paste("R^2", round(m.MSDi.R2[1, ], digits = 2), " ", "MSE", signif(m.MSDi.MSE[1, ], digits = 4)), bty = "n", text.col = "red")
+MSDi.exp = m.exp.MSDi[1, ]
+MSDi.theo = m.MSDi.fit[1, ]
+MSDi.exp.sd = m.exp.MSDi.sd[1, ]
 
-plot(as.numeric(m.MSDi.fit[2, ]), xlab = "site", main = "MSDi medium selection", ylab = "MSDi", ylim = c(0,5))
-points(m.exp.MSDi[2, ], col = "red")
-legend("topleft", paste("R^2", round(m.MSDi.R2[2, ], digits = 2), " ", "MSE", signif(m.MSDi.MSE[2, ], digits = 4)), bty = "n", text.col = "red")
+data.MSDi = data.frame("MSDi.exp" = MSDi.exp, "MSDi.theo" = MSDi.theo, "sites" = seq(1:length(MSDi.exp)), "MSDi.exp.sd" = MSDi.exp.sd)
+ggplot(data = data.MSDi, aes(x = sites)) + 
+  geom_point(aes(y = MSDi.exp, colour = "MSDi.exp")) + 
+  geom_line(aes(y = MSDi.theo, colour = "MSDi.theo"), col = "black") +
+  ylab("MSDi strong selecion") + 
+  geom_errorbar(aes(y = MSDi.exp, ymin = MSDi.exp - MSDi.exp.sd, ymax = MSDi.exp + MSDi.exp.sd), width = 0, col = "red")
 
-plot(as.numeric(m.MSDi.fit[3, ]), xlab = "site", main = "MSDi weak selection", ylab = "MSDi", ylim = c(0,5))
-points(m.exp.MSDi[3, ], col = "red")
-legend("topleft", paste("R^2", round(m.MSDi.R2[3, ], digits = 2), " ", "MSE", signif(m.MSDi.MSE[3, ], digits = 4)), bty = "n", text.col = "red")
+MSDi.exp = m.exp.MSDi[2, ]
+MSDi.theo = m.MSDi.fit[2, ]
+MSDi.exp.sd = m.exp.MSDi.sd[2, ]
 
-plot(as.numeric(m.MSDi.fit[4, ]), xlab = "site", main = "MSDi no selection", ylab = "MSDi", ylim = c(0,5))
-points(m.exp.MSDi[4, ], col = "red")
-legend("topleft", paste("R^2", round(m.MSDi.R2[4, ], digits = 2), " ", "MSE", signif(m.MSDi.MSE[4, ], digits = 4)), bty = "n", text.col = "red")
+data.MSDi = data.frame("MSDi.exp" = MSDi.exp, "MSDi.theo" = MSDi.theo, "sites" = seq(1:length(MSDi.exp)), "MSDi.exp.sd" = MSDi.exp.sd)
+ggplot(data = data.MSDi, aes(x = sites)) + 
+  geom_point(aes(y = MSDi.exp, colour = "MSDi.exp")) + 
+  geom_line(aes(y = MSDi.theo, colour = "MSDi.theo"), col = "black") +
+  ylab("MSDi medium selecion") + 
+  geom_errorbar(aes(y = MSDi.exp, ymin = MSDi.exp - MSDi.exp.sd, ymax = MSDi.exp + MSDi.exp.sd), width = 0, col = "red")
+
+MSDi.exp = m.exp.MSDi[3, ]
+MSDi.theo = m.MSDi.fit[3, ]
+MSDi.exp.sd = m.exp.MSDi.sd[3, ]
+
+data.MSDi = data.frame("MSDi.exp" = MSDi.exp, "MSDi.theo" = MSDi.theo, "sites" = seq(1:length(MSDi.exp)), "MSDi.exp.sd" = MSDi.exp.sd)
+ggplot(data = data.MSDi, aes(x = sites)) + 
+  geom_point(aes(y = MSDi.exp, colour = "MSDi.exp")) + 
+  geom_line(aes(y = MSDi.theo, colour = "MSDi.theo"), col = "black") +
+  ylab("MSDi weak selecion") + 
+  geom_errorbar(aes(y = MSDi.exp, ymin = MSDi.exp - MSDi.exp.sd, ymax = MSDi.exp + MSDi.exp.sd), width = 0, col = "red")
+
+MSDi.exp = m.exp.MSDi[4, ]
+MSDi.theo = m.MSDi.fit[4, ]
+MSDi.exp.sd = m.exp.MSDi.sd[4, ]
+
+data.MSDi = data.frame("MSDi.exp" = MSDi.exp, "MSDi.theo" = MSDi.theo, "sites" = seq(1:length(MSDi.exp)), "MSDi.exp.sd" = MSDi.exp.sd)
+ggplot(data = data.MSDi, aes(x = sites)) + 
+  geom_point(aes(y = MSDi.exp, colour = "MSDi.exp")) + 
+  geom_line(aes(y = MSDi.theo, colour = "MSDi.theo"), col = "black") +
+  ylab("MSDi no selecion") + 
+  geom_errorbar(aes(y = MSDi.exp, ymin = MSDi.exp - MSDi.exp.sd, ymax = MSDi.exp + MSDi.exp.sd), width = 0, col = "red")
 ```
 
-*negro:* Promedio teorico.
+*Linea negra:* Promedio teorico.
+*Puntos rojos:* Promedio experimental.
 
-*rojo:* Promedio experimental.
+```{r}
+layout(matrix(1:4, 2, 2, byrow = T))
 
+plot(m.MSDi.fit[1, ], m.exp.MSDi[1, ], xlab = "MSDi teorico", ylab = "MSDi experimental", main = "MSDi strong selection")
+abline(0, 1)
+legend("topleft", paste("R^2", round(m.MSDi.R2[1, ], digits = 2)), bty = "n", text.col = "red")
+legend("bottomright", paste("MSE", signif(m.MSDi.MSE[1, ], digits = 2)), bty = "n", text.col = "red")
+
+plot(m.MSDi.fit[2, ], m.exp.MSDi[2, ], xlab = "MSDi teorico", ylab = "MSDi experimental", main = "MSDi medium selection")
+abline(0, 1)
+legend("topleft", paste("R^2", round(m.MSDi.R2[2, ], digits = 2)), bty = "n", text.col = "red")
+legend("bottomright", paste("MSE", signif(m.MSDi.MSE[2, ], digits = 2)), bty = "n", text.col = "red")
+
+plot(m.MSDi.fit[3, ], m.exp.MSDi[3, ], xlab = "MSDi teorico", ylab = "MSDi experimental", main = "MSDi weak selection")
+abline(0, 1)
+legend("topleft", paste("R^2", round(m.MSDi.R2[3, ], digits = 2)), bty = "n", text.col = "red")
+legend("bottomright", paste("MSE", signif(m.MSDi.MSE[3, ], digits = 2)), bty = "n", text.col = "red")
+
+plot(m.MSDi.fit[4, ], m.exp.MSDi[4, ], xlab = "MSDi teorico", ylab = "MSDi experimental", main = "MSDi no selection")
+abline(0, 1)
+legend("topleft", paste("R^2", round(m.MSDi.R2[4, ], digits = 2)), bty = "n", text.col = "red")
+legend("bottomright", paste("MSE", signif(m.MSDi.MSE[4, ], digits = 2)), bty = "n", text.col = "red")
+
+```
 ### Pn y Qn
@@
 
-plot(m.mean.theo.Pn.group[1, 1:100], 
-     main = "Pn strong selection", 
-     xlab = "mode",
-     ylab = "Pn",
-     ylim = c(0, max(c(m.theo.Pn.group.quantile2[1, 1:100], m.mean.exp.Pn[1, 1:100]))))
-lines(m.theo.Pn.group.quantile1[1, ])
-lines(m.theo.Pn.group.quantile2[1, ])
-points(m.mean.exp.Pn[1, ], col = "red")
-lines(as.vector(m.exp.Pn.quantile1[1, ]), col = "red")
-lines(as.vector(m.exp.Pn.quantile2[1, ]), col = "red")
+Pn.exp = m.mean.exp.Pn[1, 1:100]
+Pn.theo = m.mean.theo.Pn.group[1, 1:100]
+Pn.exp.sd = m.exp.Pn.sd[1, 1:100]
 
-plot(m.mean.theo.Pn.group[2, 1:100], 
-     main = "Pn medium selection", 
-     xlab = "mode",
-     ylab = "Pn",
-     ylim = c(0, max(c(m.theo.Pn.group.quantile2[2, 1:100], m.mean.exp.Pn[2, 1:100]))))
-lines(m.theo.Pn.group.quantile1[2, ])
-lines(m.theo.Pn.group.quantile2[2, ])
-points(m.mean.exp.Pn[2, ], col = "red")
-lines(as.vector(m.exp.Pn.quantile1[2, ]), col = "red")
-lines(as.vector(m.exp.Pn.quantile2[2, ]), col = "red")
+data.Pn = data.frame("Pn.exp" = Pn.exp, "Pn.theo" = Pn.theo, "modes" = seq(1:length(Pn.exp)), "Pn.exp.sd" = Pn.exp.sd)
+ggplot(data = data.Pn, aes(x = modes)) + 
+  geom_point(aes(y = Pn.exp, colour = "Pn.exp")) + 
+  geom_line(aes(y = Pn.theo, colour = "Pn.theo"), col = "black") +
+  ylab("Pn strong selecion") + 
+  geom_errorbar(aes(y = Pn.exp, ymin = Pn.exp - Pn.exp.sd, ymax = Pn.exp + Pn.exp.sd), width = 0, col = "red")
 
-plot(m.mean.theo.Pn.group[3, 1:100], 
-     main = "Pn weak selection", 
-     xlab = "mode",
-     ylab = "Pn",
-     ylim = c(0, max(c(m.theo.Pn.group.quantile2[3, 1:100], m.mean.exp.Pn[3, 1:100]))))
-lines(m.theo.Pn.group.quantile1[3, ])
-lines(m.theo.Pn.group.quantile2[3, ])
-points(m.mean.exp.Pn[3, ], col = "red")
-lines(as.vector(m.exp.Pn.quantile1[3, ]), col = "red")
-lines(as.vector(m.exp.Pn.quantile2[3, ]), col = "red")
+Pn.exp = m.mean.exp.Pn[2, 1:100]
+Pn.theo = m.mean.theo.Pn.group[2, 1:100]
+Pn.exp.sd = m.exp.Pn.sd[2, 1:100]
 
-plot(m.mean.theo.Pn.group[4, 1:100], 
-     main = "Pn no selection", 
-     xlab = "mode",
-     ylab = "Pn",
-     ylim = c(0, max(c(m.theo.Pn.group.quantile2[4, 1:100], m.mean.exp.Pn[4, 1:100]))))
-lines(m.theo.Pn.group.quantile1[4, ])
-lines(m.theo.Pn.group.quantile2[4, ])
-points(m.mean.exp.Pn[4, ], col = "red")
-lines(as.vector(m.exp.Pn.quantile1[4, ]), col = "red")
-lines(as.vector(m.exp.Pn.quantile2[4, ]), col = "red")
+data.Pn = data.frame("Pn.exp" = Pn.exp, "Pn.theo" = Pn.theo, "modes" = seq(1:length(Pn.exp)), "Pn.exp.sd" = Pn.exp.sd)
+ggplot(data = data.Pn, aes(x = modes)) + 
+  geom_point(aes(y = Pn.exp, colour = "Pn.exp")) + 
+  geom_line(aes(y = Pn.theo, colour = "Pn.theo"), col = "black") +
+  ylab("Pn medium selecion") + 
+  geom_errorbar(aes(y = Pn.exp, ymin = Pn.exp - Pn.exp.sd, ymax = Pn.exp + Pn.exp.sd), width = 0, col = "red")
+
+Pn.exp = m.mean.exp.Pn[3, 1:100]
+Pn.theo = m.mean.theo.Pn.group[3, 1:100]
+Pn.exp.sd = m.exp.Pn.sd[3, 1:100]
+
+data.Pn = data.frame("Pn.exp" = Pn.exp, "Pn.theo" = Pn.theo, "modes" = seq(1:length(Pn.exp)), "Pn.exp.sd" = Pn.exp.sd)
+ggplot(data = data.Pn, aes(x = modes)) + 
+  geom_point(aes(y = Pn.exp, colour = "Pn.exp")) + 
+  geom_line(aes(y = Pn.theo, colour = "Pn.theo"), col = "black") +
+  ylab("Pn weak selecion") + 
+  geom_errorbar(aes(y = Pn.exp, ymin = Pn.exp - Pn.exp.sd, ymax = Pn.exp + Pn.exp.sd), width = 0, col = "red")
+
+Pn.exp = m.mean.exp.Pn[4, 1:100]
+Pn.theo = m.mean.theo.Pn.group[4, 1:100]
+Pn.exp.sd = m.exp.Pn.sd[4, 1:100]
+
+data.Pn = data.frame("Pn.exp" = Pn.exp, "Pn.theo" = Pn.theo, "modes" = seq(1:length(Pn.exp)), "Pn.exp.sd" = Pn.exp.sd)
+ggplot(data = data.Pn, aes(x = modes)) + 
+  geom_point(aes(y = Pn.exp, colour = "Pn.exp")) + 
+  geom_line(aes(y = Pn.theo, colour = "Pn.theo"), col = "black") +
+  ylab("Pn no selecion") + 
+  geom_errorbar(aes(y = Pn.exp, ymin = Pn.exp - Pn.exp.sd, ymax = Pn.exp + Pn.exp.sd), width = 0, col = "red")
 
@@
 
-*Negro*: Puntos: promedio de promedios teorico. Lineas: promedio de cuantiles 0.05 y 0.95 de `r n.mut.p` grupos de `r n.prot` mutantes teoricas.
-
-*Rojo*: Puntos: promedio experimental. Lineas: cuantiles 0.05 y 0.95 experimentales.
-
-```{r}
-layout(matrix(1:4, 2, 2, byrow = T))
-
-plot(m.mean.theo.Pn.group[1, 1:100], 
-     main = "Pn strong selection", 
-     xlab = "mode",
-     ylab = "Pn",
-     ylim = c(0, max(c(m.theo.Pn.group.quantile2[1, 1:100], m.mean.exp.Pn[1, 1:100]))))
-lines(as.vector(m.theo.Pn.quantile1.mean[1, ]))
-lines(as.vector(m.theo.Pn.quantile2.mean[1, ]))
-points(m.mean.exp.Pn[1, ], col = "red")
-
-plot(m.mean.theo.Pn.group[2, 1:100], 
-     main = "Pn medium selection", 
-     xlab = "mode",
-     ylab = "Pn",
-     ylim = c(0, max(c(m.theo.Pn.group.quantile2[2, 1:100], m.mean.exp.Pn[2, 1:100]))))
-lines(as.vector(m.theo.Pn.quantile1.mean[2, ]))
-lines(as.vector(m.theo.Pn.quantile2.mean[2, ]))
-points(m.mean.exp.Pn[2, ], col = "red")
-
-plot(m.mean.theo.Pn.group[3, 1:100], 
-     main = "Pn weak selection", 
-     xlab = "mode",
-     ylab = "Pn",
-     ylim = c(0, max(c(m.theo.Pn.group.quantile2[3, 1:100], m.mean.exp.Pn[3, 1:100]))))
-lines(as.vector(m.theo.Pn.quantile1.mean[3, ]))
-lines(as.vector(m.theo.Pn.quantile2.mean[3, ]))
-points(m.mean.exp.Pn[3, ], col = "red")
-
-plot(m.mean.theo.Pn.group[4, 1:100], 
-     main = "Pn no selection", 
-     xlab = "mode",
-     ylab = "Pn",
-     ylim = c(0, max(c(m.theo.Pn.group.quantile2[4, 1:100], m.mean.exp.Pn[4, 1:100]))))
-lines(as.vector(m.theo.Pn.quantile1.mean[4, ]))
-lines(as.vector(m.theo.Pn.quantile2.mean[4, ]))
-points(m.mean.exp.Pn[4, ], col = "red")
-
-```
-
-*Negro*: Puntos: promedio de promedios teorico. Lineas:  cuantiles 0.05 y 0.95 de promedios de `r n.mut.p` grupos de `r n.prot` mutantes teoricas.
-
-*Rojo*: Promedio experimental.
+*Linea negra*: Promedio teorico.
+*Puntos rojos*: Promedio experimental.
 

### 2016-06-05 INFORMATION/practica_ggplot.R

@@ -1,0 +1,31 @@
+library("ggplot2")
+
+data = data.frame("x.c" = c(1, 2, 3),
+                  "y.c" = c(10, 20, 30),
+                  "s.d" = c(0.5, 0.8, 1.4),
+                  "names" = c(1,2,3))
+
+ggplot(data, aes(x = names)) +
+geom_point(aes(y = x.c, colour = "x.c")) + 
+geom_point(aes(y = y.c, colour = "y.c")) + 
+geom_errorbar(aes(y = y.c, ymin = y.c - s.d, ymax = y.c + s.d), width = 0, col = "blue") +
+ylim(c(0,40))
+
+library("ggplot2")
+
+data = data.frame("x.c" = c(1, 2, 3),
+                  "y.c" = c(10, 20, 30),
+                  "s.d" = c(0.5, 0.8, 1.4),
+                  "names" = c(1, 2, 3))
+
+MSDi.exp = matrix(runif(151, 1, 151), 151, 1)
+MSDi.theo = matrix(runif(151, 1, 151), 151, 1)
+error = runif(151, 0, 1)
+sites = seq(1:151)
+
+data.MSDi = data.frame("MSDi.exp" = MSDi.exp, "MSDi.theo" = MSDi.theo, "sites" = sites, "error" = error)
+ggplot(data = data.MSDi, aes(x = sites)) + 
+  geom_point(aes(y = MSDi.exp, colour = "MSDi.exp")) + 
+  geom_line(aes(y = MSDi.theo, colour = "MSDi.theo"), col = "black") +
+  ylab("MSDi.theo") + 
+  geom_errorbar(aes(y = MSDi.exp, ymin = MSDi.exp - error, ymax = MSDi.exp + error), width = 0, col = "red") 

### 2016-07-27 MultipleReportAllBetasZscore.Rmd
cambios 27/07/2016

--- 2016-06-05 MultipleReportAllBetas.Rmd
@@
     exp.smooth.norm.MSDi = colMeans(m.exp.smooth.norm.dr.squarei, na.rm = T )
+
+    exp.smooth.norm.MSDi = scale(sqrt(exp.smooth.norm.MSDi))[, 1]
+
+    exp.smooth.norm.MSDi = exp.smooth.norm.MSDi[!is.na(exp.smooth.norm.MSDi)]                                                                    
     exp.smooth.norm.MSDi.sd = apply(m.exp.smooth.norm.dr.squarei, 2, sd, na.rm = T)
@@
 
+    n.mut = nrow(m.theo.Pn)
+
     m.theo.smooth.norm.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.smooth.norm.dr.squarei.csv", sep = "")))
     theo.smooth.norm.MSDi = colMeans(m.theo.smooth.norm.dr.squarei, na.rm = T )
+    MSDi.fit = scale(sqrt(theo.smooth.norm.MSDi))[, 1]               
+    MSDi.fit = MSDi.fit[1:length(exp.smooth.norm.MSDi)]
 
-    n.mut = nrow(m.theo.Pn)
-
-    fit = lm(exp.smooth.norm.MSDi ~ theo.smooth.norm.MSDi )
-    MSDi.fit = fitted.values(fit)
     MSDi.R2 = cor(exp.smooth.norm.MSDi[!is.na(exp.smooth.norm.MSDi)], MSDi.fit) ^ 2 
     MSDi.MSE = mean((MSDi.fit - exp.smooth.norm.MSDi[!is.na(exp.smooth.norm.MSDi)]) ^ 2)
-    exp.smooth.norm.MSDi = exp.smooth.norm.MSDi[!is.na(exp.smooth.norm.MSDi)]
 

### 2016-07-27 OUT/analysis-structure-CA.Rmd
cambios 27/07/2016

---
title: "Structural Divergence Analysis"
author: "María Laura Marcos, Julian Echave"
date: "25 de julio de 2016"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, cache = 2, autodep = T)
```

```{r load_libraries}
library(ggplot2)
library(reshape2)
library(plyr)
library(quantreg)
library(bio3d)

setwd("C:/Users/Usuario/Desktop/VariabilidadEstructuralProteica")

source("OUT/out_subset_CA/multiplot.R")
source("OUT/out_subset_CA/my-functions.R")
```

```{r set_my_colors, eval = T}
myColors = c("blue", "darkgreen", "red", "red")
names(myColors) <- c("exp", "mut", "strong", "mut+sel")

setwd("C:/Users/Usuario/Desktop/VariabilidadEstructuralProteica/OUT")

```
# Introduction
We study the evolutionary divergence of proteins using the LFENM and compare with experimental data.

```{r set_run_variables}
# Set options
family = "globins"
R0 = 10
enm = "ANM"

# significance factors
f95 = 1.96
f99 = 2.6
f999 = 3.3
data.dir = paste("out_subset_CA", sep = "")
```

```{r set_file_names}
## Input and pre-processing of data
# Set up input filenames

reference.fname = file.path(data.dir, paste(family, "_ref.txt", sep = ""))
site.info.fname = file.path(data.dir, paste(family, "_out_m.da.csv", sep = ""))
protein_list.fname = file.path(data.dir, paste(family, "_list.txt", sep = ""))

dri2.exp.fname = file.path(data.dir, paste(family, "_R0_10_beta_strong.sel_K.analysis_Keff_out_m.exp.norm.dr.squarei.csv", sep = ""))
Pn.exp.fname = file.path(data.dir, paste(family,"_R0_10_beta_strong.sel_K.analysis_Keff_out_m.exp.Pn.csv", sep = ""))
energy.exp.fname = file.path(data.dir, paste(family, "_R0_10_beta_strong.sel_K.analysis_Keff_out_m.exp.va.csv", sep = ""))

dri2.strong.fname = file.path(data.dir, paste(family, "_R0_10_beta_strong.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
Pn.strong.fname = file.path(data.dir, paste(family, "_R0_10_beta_strong.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
energy.strong.fname = file.path(data.dir, paste(family, "_R0_10_beta_strong.sel_K.analysis_Keff_out_m.theo.va.csv", sep = ""))

dri2.mut.fname = file.path(data.dir,paste(family, "_R0_10_beta_no.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
Pn.mut.fname = file.path(data.dir, paste(family, "_R0_10_beta_no.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
energy.mut.fname = file.path(data.dir, paste(family, "_R0_10_beta_no.sel_K.analysis_Keff_out_m.theo.va.csv", sep = ""))

```

```{r set_reference_protein}
## which is the reference protein?
reference = as.character(read.table(reference.fname, header = F)[1, 1])
```

We use the `r enm` Elastic Network Model with `R0 =` `r R0` for the `r family` family. 
We use as reference for the ENM the protein with pdb code `r reference`.
The `r family` family consists of the following proteins:

```{r set_experimental_protein_names}
## Experimental protein names
protein.exp = read.table(protein_list.fname, header = F, stringsAsFactors = F)[, 1]
protein.exp = protein.exp[protein.exp != reference]
print(protein.exp)
```

[//]: Prepare site.info data frame

```{r set_up_site_info, eval = T}

## read site information of reference protein
site.info = read.csv(site.info.fname, header = T, sep = ";")

## add info to site.info
d = ddply(site.info, "site", .fun = function(x) data.frame("da" = min(x[, c(-1, -2)])))

## Define shells of active site neighborhood (first shell is from 2.5 to 7.5, second from 7.5 to 12.5, etc)
d$shell = cut(d$da, breaks = c(-.1, 2.5, 7.5, 12.5, 17.5, 22.5, 27.5, 32.5, 37.5, 42.5, 47.5, 52.5, max(d$da)))
levels(d$shell) = seq(length(levels(d$shell))) - 1 # rename shell levels
site.info = merge(site.info, d, by = "site")

## Read reference pdb and calculate resno, AA, and CN
reference.pdb.fname = file.path(data.dir,paste(reference, ".pdb", sep = ""))
ref.pdb = read.pdb(reference.pdb.fname)
inds = atom.select(ref.pdb, elety = "CA")
ref.pdb.ca = ref.pdb$atom[inds$atom,]
cmap.ca = cmap(ref.pdb$xyz[inds$xyz], dcut = R0, scut = 0, mask.lower = F)
CN = rowSums(cmap.ca, na.rm = T) - 1 # diag(cmap.ca) returned by cmap is 1!
AA = ref.pdb.ca$resid
resno = ref.pdb.ca$resno
pdb.info = data.frame(resno, AA, CN)
names(pdb.info) = c("resno", "AA", paste("CN", as.character(R0), sep = ""))

## Add pdb.info to site.info
site.info = cbind(site.info, pdb.info)
```

[//]: Prepare experimental data

```{r read_experimental_data}
# read experimental data
dri2.exp = read.csv(dri2.exp.fname, header = T)
site = site.info$site
dri2.exp = dri2.exp[, site]
rownames(dri2.exp) = protein.exp

Pn.exp = read.csv(Pn.exp.fname, header = T)
rownames(Pn.exp) = protein.exp

energy.exp = read.csv(energy.exp.fname, header = T)
rownames(energy.exp) = protein.exp

```

[//]: Prepare data for no selection (mut)

```{r read_and_set_data_mut}
# read simulated data

dri2.mut = read.csv(dri2.mut.fname, header = T)
site = site.info$site
dri2.mut = dri2.mut[, site]
rownames(dri2.mut) = paste("mut", rownames(dri2.mut), sep = "")

Pn.mut = read.csv(Pn.mut.fname, header = T)
rownames(Pn.mut) = paste("mut", rownames(Pn.mut), sep = "")

energy.mut = read.csv(energy.mut.fname, header = T)
rownames(energy.mut) = paste("mut", rownames(energy.mut), sep = "")
```

[//]: Prepare data for strong selection

```{r read_and_set_data_strong}
# read simulated data

dri2.strong = read.csv(dri2.strong.fname, header = T)
site = site.info$site
dri2.strong = dri2.strong[, site]
rownames(dri2.strong) = paste("strong", rownames(dri2.strong), sep = "")

Pn.strong = read.csv(Pn.strong.fname, header = T)
rownames(Pn.strong) = paste("strong", rownames(Pn.strong), sep = "")

energy.strong = read.csv(energy.strong.fname, header = T)
rownames(energy.strong) = paste("strong", rownames(energy.strong), sep = "")
```

# Structural divergence along sites

Here we study how structural divergence varies from site to site. We will compare simulated data and empirical data.

```{r prepare-site-data}
# Prepare my data.frame
# rows of dri2 are proteins, columns are sites

tdri2.strong = as.data.frame(t(as.matrix(dri2.strong)))
tdri2.strong = cbind(site.info, tdri2.strong)
siteComparison.strong = melt(tdri2.strong, id.vars = names(site.info), variable.name = "protein", value.name = "dri2")

tdri2.mut = as.data.frame(t(as.matrix(dri2.mut)))
tdri2.mut = cbind(site.info, tdri2.mut)
siteComparison.mut = melt(tdri2.mut, id.vars = names(site.info), variable.name = "protein", value.name = "dri2")

tdri2.exp = as.data.frame(t(as.matrix(dri2.exp)))
tdri2.exp = cbind(site.info, tdri2.exp)
siteComparison.exp = melt(tdri2.exp, id.vars = names(site.info), variable.name = "protein", value.name = "dri2")

siteComparison.all.datasets = rbind(
  data.frame("dataset" = "exp", siteComparison.exp),
  data.frame("dataset" = "mut", siteComparison.mut),
  data.frame("dataset" = "strong", siteComparison.strong))

siteComparison.all.datasets = ddply(siteComparison.all.datasets, c("dataset", "protein"), mutate,
          "n.SD" = dri2/mean(dri2, na.rm = T),
          "z.SD" = vscale(dri2),
          "RSD" = sqrt(dri2),
          "n.RSD" = RSD/mean(RSD, na.rm = T),
          "z.RSD" = vscale(RSD))
```

### Mean z.RSD vs site

To measure structural divergence we use z.RSD profiles, which are the best (most similar distributions and profiles w.r.t experimental).

The following plot compares the mean z.RSD profiles, including standard errors (with .999 confidence level for the mean)
*Warning: the effective number of data should be smaller than the actual data, especially for the experimental dataset because of several factors, including smoothing of the profiles, phylogenetic relationships, etc. We need to deal with this for quantitative analysis. Probably we'll need to use bootstrapping to calculate standard errors non-parametrically*

```{r mean-z-RSD-vs-site}
# Comparison of z.RSD profiles annotated with functional information (reported active sites).
dat = siteComparison.all.datasets
dat$dataset = revalue(dat$dataset, c("strong" = "mut+sel"))

# dat.with.means and standard errors
d = ddply(dat,c("dataset","site","AA","shell"), function(x) {
                mean.z.RSD = mean(x$z.RSD, na.rm = T)
                ndata = sum(!is.na(x$z.RSD))
                se.z.RSD = sd(x$z.RSD, na.rm = T) / sqrt(ndata)
                data.frame(mean.z.RSD, ndata, se.z.RSD)
})

##

z.RSD.exp = d$mean.z.RSD[d$dataset == "exp"]
z.RSD.strong = d$mean.z.RSD[d$dataset == "mut+sel"]
z.RSD.mut = d$mean.z.RSD[d$dataset == "mut"]

m.min.da.CM.ca = read.csv(file.path(data.dir, "min.da.CM.ca.csv", sep = ""))[, 2:4]

data.csv = data.frame(m.min.da.CM.ca[1:151, ], "mean.z.RSD.exp" = z.RSD.exp, "mean.z.RSD.strong" = z.RSD.strong, "mean.z.RSD.mut" = z.RSD.mut)

write.csv(data.csv, file.path(data.dir, "data.da.csv", sep = ""))

m.min.da.CM = m.min.da.CM.ca$min.da.CM[1:151]

data.plot = data.frame("d.exp.mut" = z.RSD.mut - z.RSD.exp, "d.exp.strong" = z.RSD.mut - z.RSD.strong, "m.min.da.CM" = m.min.da.CM)

r = round(cor(data.plot$d.exp.mut, data.plot$m.min.da.CM), 2)

ggplot(data.plot, aes(y = d.exp.mut, x = m.min.da.CM)) +
  geom_point()+
  geom_smooth(method = "lm") +
  geom_label(aes(x = 5, y = 2, label = paste("R =", as.character(r)))) +
    labs(y = "mean.z.RSD.mut - mean.z.RSD.exp", x = "min.da.CM")

r = round(cor(data.plot$d.exp.strong, data.plot$m.min.da.CM), 2)

ggplot(data.plot, aes(y = d.exp.strong, x = m.min.da.CM)) +
  geom_point()+
  geom_smooth(method = "lm") +
  geom_label(aes(x = 5, y = 0.5, label = paste("R =", as.character(r)))) +
    labs(y = "mean.z.RSD.strong - mean.z.RSD.exp", x = "min.da.CM")

##

m.min.da.ca = m.min.da.CM.ca$min.da.ca[1:151]

data.plot = data.frame("d.exp.mut" = z.RSD.mut - z.RSD.exp, "d.exp.strong" = z.RSD.strong - z.RSD.exp, "m.min.da.ca" = m.min.da.ca)

r = round(cor(data.plot$d.exp.mut, data.plot$m.min.da.ca), 2)

ggplot(data.plot, aes(y = d.exp.mut, x = m.min.da.ca)) +
  geom_point()+
  geom_smooth(method = "lm") +
  geom_label(aes(x = 5, y = 2, label = paste("R =", as.character(r)))) +
    labs(y = "mean.z.RSD.mut - mean.z.RSD.exp", x = "min.da.ca")

r = round(cor(data.plot$d.exp.strong, data.plot$m.min.da.ca), 2)

ggplot(data.plot, aes(y = d.exp.strong, x = m.min.da.ca)) +
  geom_point()+
  geom_smooth(method = "lm") +
  geom_label(aes(x = 5, y = 2, label = paste("R =", as.character(r)))) +
    labs(y = "mean.z.RSD.strong - mean.z.RSD.exp", x = "min.da.ca")

#d$dataset = factor(d$dataset, levels = c("exp", "mut", "strong"))
d$label = as.character(d$site)
active.sites = d$site[d$shell == 0]

p = ggplot(d,aes(x = site, y = mean.z.RSD, col = dataset, fill = dataset)) +
    geom_line() +
    geom_ribbon(aes(ymin = mean.z.RSD - f95 * se.z.RSD, ymax = mean.z.RSD + se.z.RSD), alpha = .4, show.legend = F) +
    geom_vline(xintercept = active.sites, col = "grey", show.legend = F) +
    labs(x = "site", y = "structural divergence(mean z.RSD)") +
    coord_cartesian(ylim = c(-1.5, 2.8)) +
    scale_colour_manual(name = NULL, values = myColors) + 
    scale_fill_manual(name=NULL, values = myColors)

# Plot separate and comparative plots
p.facet = p + facet_grid(dataset~., switch = "y") + theme(legend.position = "none")

p.facet %+% subset(d, dataset == "exp") 
p.facet %+% subset(d, dataset == "mut")
p.facet %+% subset(d, dataset == "mut+sel") 
p.facet
#p + theme(legend.position = "bottom", legend.title = element_blank())
p + theme(legend.position = "bottom")

```

VAL107 and its neighbors (including site 32) are more structurally conserved than predicted.

### Correlation between site profiles

```{r}
dat = siteComparison.all.datasets

# dat.with.means and standard errors
dat = ddply(dat,c("dataset", "site", "AA", "shell"), function(x) {
                mean.z.RSD = mean(x$z.RSD, na.rm = T)
                ndata = sum(!is.na(x$z.RSD))
                se.z.RSD = sd(x$z.RSD, na.rm = T) / sqrt(ndata)
                data.frame(mean.z.RSD, ndata, se.z.RSD)
})

dat.exp = subset(dat, dataset == "exp")
dat.mut = subset(dat, dataset == "mut")
dat.strong = subset(dat, dataset == "strong")

ggplot(dat, aes(x = site, y = mean.z.RSD, col = dataset)) + geom_line() +
    geom_text(data = subset(dat, dataset == "exp" & mean.z.RSD < -.5), aes(x = site, y = mean.z.RSD, label = site), nudge_y = -.1, size = 2)

d = dat.exp
d$d.exp.mut = dat.exp$mean.z.RSD - dat.mut$mean.z.RSD
d$d.exp.strong = dat.exp$mean.z.RSD - dat.strong$mean.z.RSD
d$d.strong.mut = dat.strong$mean.z.RSD - dat.mut$mean.z.RSD
dd = melt(data = d[, c("site", "se.z.RSD", "d.exp.mut", "d.strong.mut")], c("site", "se.z.RSD"))

ggplot(dd, aes(x = site, y = value, col = variable)) +
    geom_line() 
r = round(cor(d$d.strong.mut, d$d.exp.mut), 2)

ggplot(d, aes(x = scale(d.strong.mut), y = scale(d.exp.mut))) + 
    geom_point(aes(col = shell == 0)) +
    geom_smooth(method = "lm") +
    geom_label(aes(x = 0, y = 3, label = paste("R =", as.character(r)))) +
    labs(x = "predicted selection vs mutation (RSD change)",y="empirical vs mutation (RSD change)")

r.exp.mut = cor(dat.exp$mean.z.RSD, dat.mut$mean.z.RSD)
r.exp.strong = cor(dat.exp$mean.z.RSD, dat.strong$mean.z.RSD)
r.mut.strong = cor(dat.mut$mean.z.RSD, dat.strong$mean.z.RSD)
cor.df = data.frame("comparison" = c("exp vs mut", "exp vs strong", "mut vs strong"),
                    "R" = c(r.exp.mut, r.exp.strong, r.mut.strong))
knitr::kable(cor.df, digits = 2)
write.csv(dat, "structure-comparison-profiles.csv")

```

# Structural divergence along normal modes
In this section we consider structural divergence using normal mode coordinates.
Pn is the square divergence along a normal mode relative to the mean.

[//]: Prepare mode data

```{r prepare-mode-data}
mode = seq(ncol(Pn.strong))

# Prepare modeComparison.strong
tPn.strong = as.data.frame(t(as.matrix(Pn.strong)))
tPn.strong = cbind(data.frame("mode" = mode), tPn.strong)
Pn.strong.long = melt(tPn.strong, "mode", variable.name = "protein", value.name = "Pn")

tenergy.strong = as.data.frame(t(as.matrix(energy.strong)))
tenergy.strong = cbind(data.frame("mode" = mode), tenergy.strong)
energy.strong.long = melt(tenergy.strong, "mode", variable.name = "protein", value.name = "energy")
energy.strong.long$sn2 = 1/energy.strong.long$energy

modeComparison.strong = merge(energy.strong.long, Pn.strong.long, by = c("mode", "protein"))

modeComparison.strong = ddply(modeComparison.strong, "protein", mutate, "Pn" = Pn / mean(Pn, na.rm = T))

# Prepare modeComparison.mut
tPn.mut = as.data.frame(t(as.matrix(Pn.mut)))
tPn.mut = cbind(data.frame("mode" = mode), tPn.mut)
Pn.mut.long = melt(tPn.mut, "mode", variable.name = "protein", value.name = "Pn")

tenergy.mut = as.data.frame(t(as.matrix(energy.mut)))
tenergy.mut = cbind(data.frame("mode" = mode), tenergy.mut)
energy.mut.long = melt(tenergy.mut, "mode", variable.name = "protein", value.name = "energy")
energy.mut.long$sn2 = 1/energy.mut.long$energy

modeComparison.mut = merge(energy.mut.long, Pn.mut.long, by = c("mode", "protein"))
modeComparison.mut = ddply(modeComparison.mut, "protein", mutate, "Pn" = Pn / mean(Pn, na.rm = T))

# Prepare modeComparison.exp
tPn.exp = as.data.frame(t(as.matrix(Pn.exp)))
tPn.exp = cbind(data.frame("mode" = mode), tPn.exp)
Pn.exp.long = melt(tPn.exp, "mode", variable.name = "protein", value.name = "Pn")

tenergy.exp = as.data.frame(t(as.matrix(energy.exp)))
tenergy.exp = cbind(data.frame("mode" = mode), tenergy.exp)
energy.exp.long = melt(tenergy.exp, "mode", variable.name = "protein", value.name = "energy")
energy.exp.long$sn2 = 1/energy.exp.long$energy

modeComparison.exp = merge(energy.exp.long,Pn.exp.long,by=c("mode", "protein"))

# renormalize Pn
modeComparison.exp = ddply(modeComparison.exp, "protein", mutate, "Pn" = Pn / mean(Pn, na.rm = T))

# modeComparison.exp has NA's because for proteins with gaps when using Keff there're less modes
#print("Warning: modeComparison.exp <- na.omit(modeComparison.exp)")
modeComparison.exp <- na.omit(modeComparison.exp)
modeComparison.strong <- na.omit(modeComparison.strong)
modeComparison.mut <- na.omit(modeComparison.mut)

```

[//]: Add quantile regression data

```{r}
## Quantile regression

# fit median and quantiles to simulated data and add them to data.frames
fit.strong.rq.5 <- rq(Pn ~ sn2, tau = .5, data = modeComparison.strong, method = "fn")
fit.strong.rq.05 <- rq(Pn ~ sn2, tau = .05, data = modeComparison.strong, method = "fn")
fit.strong.rq.95 <- rq(Pn ~ sn2, tau = .95, data = modeComparison.strong, method = "fn")
modeComparison.strong$rq.5 = fit.strong.rq.5$fitted.values
modeComparison.strong$rq.05 = fit.strong.rq.05$fitted.values
modeComparison.strong$rq.95 = fit.strong.rq.95$fitted.values

# fit median and quantiles to simulated data and add them to data.frames
fit.mut.rq.5 <- rq(Pn ~ sn2, tau = .5, data = modeComparison.mut, method = "fn")
fit.mut.rq.05 <- rq(Pn ~ sn2, tau = .05, data = modeComparison.mut, method = "fn")
fit.mut.rq.95 <- rq(Pn ~ sn2, tau = .95, data = modeComparison.mut, method = "fn")
modeComparison.mut$rq.5 = fit.mut.rq.5$fitted.values
modeComparison.mut$rq.05 = fit.mut.rq.05$fitted.values
modeComparison.mut$rq.95 = fit.mut.rq.95$fitted.values

# fit median and quantiles to experimental data
fit.exp.rq.5 <- rq(Pn ~ sn2, tau = .5, data = modeComparison.exp, method = "fn")
fit.exp.rq.05 <- rq(Pn ~ sn2, tau = .05, data = modeComparison.exp, method = "fn")
fit.exp.rq.95 <- rq(Pn ~ sn2, tau = .95, data = modeComparison.exp, method = "fn")
modeComparison.exp$rq.5 = fit.exp.rq.5$fitted.values
modeComparison.exp$rq.05 = fit.exp.rq.05$fitted.values
modeComparison.exp$rq.95 = fit.exp.rq.95$fitted.values

# put simulated and experimental data together

modeComparison.all.datasets = rbind(data.frame("dataset" = "exp", modeComparison.exp),
                                    data.frame("dataset" = "mut", modeComparison.mut),
                                    data.frame("dataset" = "strong", modeComparison.strong))

modeComparison.all.datasets$dataset = factor(modeComparison.all.datasets$dataset, levels = c("exp", "mut", "strong"))
```

### Pn vs. mode energy

Note: lines are the median, 0.05 and 0.95 quantiles fit using rq(Pn ~ sn2).
sn2 = 1/energy is the expected MSD of along mode n. 
The mean value of Pn should be a linear function of sn2 (Pn is normalized, sn2 is not).

Here we show the square deviation along each normal mode (normalized so that <Pn> = 1) vs. the normal-mode's energy. For the empirical data, we use the actual energy obtained from Keff for the given comparison. It is this energy the one that should be used, since it's inverse is the expected value of Pn. Lines are the .5 (median), .05, and .95 quantiles obtained using `rq()`
- Upper panel: simulated vs empirical data, shown separately.
- Lower panel: simulated vs empirical overlaped and zoomed to better see the pattern.

```{r Pn-vs-mode-energy,cache = 2}
# Plot Pn vs energy
dat = modeComparison.all.datasets
dat$dataset = revalue(dat$dataset,c("strong" = "mut+sel"))

# p is just the median and quantiles
p.points.rq = ggplot(dat, aes(x = energy, y = Pn, col = dataset)) + 
    geom_point(alpha = .4, size = .2) +
    geom_line(aes(y = rq.5)) +
    geom_line(aes(y = rq.05)) +
    geom_line(aes(y = rq.95)) 
p = p.points.rq +  
    labs(x = "mode energy", y = "structural divergence") +
    coord_cartesian(xlim = c(0,2.5)) +
    scale_colour_manual(name = NULL, values = myColors) + 
    scale_fill_manual(name=NULL, values = myColors)

p.facet = p + facet_grid(dataset~., switch = "y") + theme(legend.position = "none")
p.facet %+% subset(dat, dataset == "exp")
p.facet %+% subset(dat, dataset == "mut")
p.facet %+% subset(dat, dataset == "mut+sel")
p.facet
```

### median(Pn) vs mode energy

```{r median-Pn-vs-mode-energy, cache = 2}
dat = modeComparison.all.datasets
dat$dataset = revalue(dat$dataset,c("strong" = "mut+sel"))

# calculate dataset of medians

dat = ddply(dat,c("dataset", "mode"), function(x) {
    energy.mean = mean(x$energy)
    Pn.median = median(x$Pn)
    Pn.median.ci = sort(x$Pn)[qbinom(c(.025, .975), length(x$Pn), 0.5)]
    Pn.median.min = Pn.median.ci[1]
    Pn.median.max = Pn.median.ci[2]
    rq.5 = mean(x$rq.5)
    data.frame(energy.mean, Pn.median.min, Pn.median.max, Pn.median, rq.5)
})

p = ggplot(dat,aes(x=energy.mean,y=Pn.median,col=dataset,fill=dataset)) +
    geom_pointrange(aes(ymin=Pn.median.min,ymax = Pn.median.max),size=.2,alpha=.4) +
    geom_line(aes(y=rq.5))  +
    labs(x="mode energy",y="structural divergence (median Pn) ") +
    scale_colour_manual(name = NULL,values = myColors) + 
    scale_fill_manual(name=NULL,values=myColors)+
    coord_cartesian(xlim=c(0,1))

p.facet = p + facet_grid(dataset~.,switch="y") + theme(legend.position="none")
p.facet %+% subset(dat,dataset =="exp")
p.facet %+% subset(dat,dataset == "mut")
p.facet %+% subset(dat,dataset == "mut+sel")
p.facet
p + theme(legend.position = "bottom")

```

### Correlation between mode profiles

```{r}
dat = modeComparison.all.datasets
#dat$dataset = revalue(dat$dataset,c("strong" = "mut+sel"))

# calculate dataset of medians
dat = ddply(dat, c("dataset", "mode"), function(x) {
    energy.mean = mean(x$energy)
    Pn.median = median(x$Pn)
    data.frame(energy.mean, Pn.median)
})

dat = subset(dat, mode < 101)
dat.exp = subset(dat, dataset == "exp")
dat.mut = subset(dat,dataset == "mut")
dat.strong = subset(dat,dataset == "strong")

r.exp.mut = cor(dat.exp$Pn.median, dat.mut$Pn.median)
r.exp.strong = cor(dat.exp$Pn.median, dat.strong$Pn.median)
r.mut.strong = cor(dat.mut$Pn.median, dat.strong$Pn.median)
cor.df = data.frame("comparison" = c("exp vs mut", "exp vs strong", "mut vs strong"),
                    "R" = c(r.exp.mut, r.exp.strong, r.mut.strong))
knitr::kable(cor.df, digits = 2)

```

[//]: Write output for further analysis with other programs

```{r write-data-to-output}
write.csv(siteComparison.exp, "site-structure-comparison-exp.csv",row.names=F)
write.csv(modeComparison.exp, "mode-structure-comparison-exp.csv",row.names=F)
```

### 2016-07-27 OUT/analysis-structure-CM.Rmd
cambios 27/07/2016

--- 2016-07-27 OUT/analysis-structure-CA.Rmd
@@
 
-source("OUT/out_subset_CA/multiplot.R")
-source("OUT/out_subset_CA/my-functions.R")
+source("OUT/out_subset_CM/multiplot.R")
+source("OUT/out_subset_CM/my-functions.R")
 ```
@@
 family = "globins"
-R0 = 10
+R0 = 7.5
 enm = "ANM"
@@
 f999 = 3.3
-data.dir = paste("out_subset_CA", sep = "")
+data.dir = paste("out_subset_CM", sep = "")
 ```
@@
 
-dri2.exp.fname = file.path(data.dir, paste(family, "_R0_10_beta_strong.sel_K.analysis_Keff_out_m.exp.norm.dr.squarei.csv", sep = ""))
-Pn.exp.fname = file.path(data.dir, paste(family,"_R0_10_beta_strong.sel_K.analysis_Keff_out_m.exp.Pn.csv", sep = ""))
-energy.exp.fname = file.path(data.dir, paste(family, "_R0_10_beta_strong.sel_K.analysis_Keff_out_m.exp.va.csv", sep = ""))
+dri2.exp.fname = file.path(data.dir, paste(family, "_R0_7.5_beta_strong.sel_K.analysis_Keff_out_m.exp.norm.dr.squarei.csv", sep = ""))
+Pn.exp.fname = file.path(data.dir, paste(family,"_R0_7.5_beta_strong.sel_K.analysis_Keff_out_m.exp.Pn.csv", sep = ""))
+energy.exp.fname = file.path(data.dir, paste(family, "_R0_7.5_beta_strong.sel_K.analysis_Keff_out_m.exp.va.csv", sep = ""))
 
-dri2.strong.fname = file.path(data.dir, paste(family, "_R0_10_beta_strong.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
-Pn.strong.fname = file.path(data.dir, paste(family, "_R0_10_beta_strong.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
-energy.strong.fname = file.path(data.dir, paste(family, "_R0_10_beta_strong.sel_K.analysis_Keff_out_m.theo.va.csv", sep = ""))
+dri2.strong.fname = file.path(data.dir, paste(family, "_R0_7.5_beta_strong.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
+Pn.strong.fname = file.path(data.dir, paste(family, "_R0_7.5_beta_strong.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
+energy.strong.fname = file.path(data.dir, paste(family, "_R0_7.5_beta_strong.sel_K.analysis_Keff_out_m.theo.va.csv", sep = ""))
 
-dri2.mut.fname = file.path(data.dir,paste(family, "_R0_10_beta_no.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
-Pn.mut.fname = file.path(data.dir, paste(family, "_R0_10_beta_no.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
-energy.mut.fname = file.path(data.dir, paste(family, "_R0_10_beta_no.sel_K.analysis_Keff_out_m.theo.va.csv", sep = ""))
+dri2.mut.fname = file.path(data.dir,paste(family, "_R0_7.5_beta_no.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
+Pn.mut.fname = file.path(data.dir, paste(family, "_R0_7.5_beta_no.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
+energy.mut.fname = file.path(data.dir, paste(family, "_R0_7.5_beta_no.sel_K.analysis_Keff_out_m.theo.va.csv", sep = ""))
 
@@
 })
-
-##
-
-z.RSD.exp = d$mean.z.RSD[d$dataset == "exp"]
-z.RSD.strong = d$mean.z.RSD[d$dataset == "mut+sel"]
-z.RSD.mut = d$mean.z.RSD[d$dataset == "mut"]
-
-m.min.da.CM.ca = read.csv(file.path(data.dir, "min.da.CM.ca.csv", sep = ""))[, 2:4]
-
-data.csv = data.frame(m.min.da.CM.ca[1:151, ], "mean.z.RSD.exp" = z.RSD.exp, "mean.z.RSD.strong" = z.RSD.strong, "mean.z.RSD.mut" = z.RSD.mut)
-
-write.csv(data.csv, file.path(data.dir, "data.da.csv", sep = ""))
-
-m.min.da.CM = m.min.da.CM.ca$min.da.CM[1:151]
-
-data.plot = data.frame("d.exp.mut" = z.RSD.mut - z.RSD.exp, "d.exp.strong" = z.RSD.mut - z.RSD.strong, "m.min.da.CM" = m.min.da.CM)
-
-r = round(cor(data.plot$d.exp.mut, data.plot$m.min.da.CM), 2)
-
-ggplot(data.plot, aes(y = d.exp.mut, x = m.min.da.CM)) +
-  geom_point()+
-  geom_smooth(method = "lm") +
-  geom_label(aes(x = 5, y = 2, label = paste("R =", as.character(r)))) +
-    labs(y = "mean.z.RSD.mut - mean.z.RSD.exp", x = "min.da.CM")
-
-r = round(cor(data.plot$d.exp.strong, data.plot$m.min.da.CM), 2)
-
-ggplot(data.plot, aes(y = d.exp.strong, x = m.min.da.CM)) +
-  geom_point()+
-  geom_smooth(method = "lm") +
-  geom_label(aes(x = 5, y = 0.5, label = paste("R =", as.character(r)))) +
-    labs(y = "mean.z.RSD.strong - mean.z.RSD.exp", x = "min.da.CM")
-
-##
-
-m.min.da.ca = m.min.da.CM.ca$min.da.ca[1:151]
-
-data.plot = data.frame("d.exp.mut" = z.RSD.mut - z.RSD.exp, "d.exp.strong" = z.RSD.strong - z.RSD.exp, "m.min.da.ca" = m.min.da.ca)
-
-r = round(cor(data.plot$d.exp.mut, data.plot$m.min.da.ca), 2)
-
-ggplot(data.plot, aes(y = d.exp.mut, x = m.min.da.ca)) +
-  geom_point()+
-  geom_smooth(method = "lm") +
-  geom_label(aes(x = 5, y = 2, label = paste("R =", as.character(r)))) +
-    labs(y = "mean.z.RSD.mut - mean.z.RSD.exp", x = "min.da.ca")
-
-r = round(cor(data.plot$d.exp.strong, data.plot$m.min.da.ca), 2)
-
-ggplot(data.plot, aes(y = d.exp.strong, x = m.min.da.ca)) +
-  geom_point()+
-  geom_smooth(method = "lm") +
-  geom_label(aes(x = 5, y = 2, label = paste("R =", as.character(r)))) +
-    labs(y = "mean.z.RSD.strong - mean.z.RSD.exp", x = "min.da.ca")
-
 #d$dataset = factor(d$dataset, levels = c("exp", "mut", "strong"))

### 2016-07-27 OUT/analysis-structure-smooth-CA.Rmd
cambios 27/07/2016

--- 2016-07-27 OUT/analysis-structure-CM.Rmd
@@
 
-source("OUT/out_subset_CM/multiplot.R")
-source("OUT/out_subset_CM/my-functions.R")
+source("OUT/out_subset_CA/multiplot.R")
+source("OUT/out_subset_CA/my-functions.R")
 ```
@@
 family = "globins"
-R0 = 7.5
+R0 = 10
 enm = "ANM"
@@
 f999 = 3.3
-data.dir = paste("out_subset_CM", sep = "")
+data.dir = paste("out_subset_CA", sep = "")
 ```
@@
 
-dri2.exp.fname = file.path(data.dir, paste(family, "_R0_7.5_beta_strong.sel_K.analysis_Keff_out_m.exp.norm.dr.squarei.csv", sep = ""))
-Pn.exp.fname = file.path(data.dir, paste(family,"_R0_7.5_beta_strong.sel_K.analysis_Keff_out_m.exp.Pn.csv", sep = ""))
-energy.exp.fname = file.path(data.dir, paste(family, "_R0_7.5_beta_strong.sel_K.analysis_Keff_out_m.exp.va.csv", sep = ""))
+dri2.exp.fname = file.path(data.dir, paste(family, "_R0_10_beta_strong.sel_K.analysis_Keff_out_m.exp.smooth.norm.dr.squarei.csv", sep = ""))
+Pn.exp.fname = file.path(data.dir, paste(family,"_R0_10_beta_strong.sel_K.analysis_Keff_out_m.exp.Pn.csv", sep = ""))
+energy.exp.fname = file.path(data.dir, paste(family, "_R0_10_beta_strong.sel_K.analysis_Keff_out_m.exp.va.csv", sep = ""))
 
-dri2.strong.fname = file.path(data.dir, paste(family, "_R0_7.5_beta_strong.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
-Pn.strong.fname = file.path(data.dir, paste(family, "_R0_7.5_beta_strong.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
-energy.strong.fname = file.path(data.dir, paste(family, "_R0_7.5_beta_strong.sel_K.analysis_Keff_out_m.theo.va.csv", sep = ""))
+dri2.strong.fname = file.path(data.dir, paste(family, "_R0_10_beta_strong.sel_K.analysis_Keff_out_m.theo.smooth.norm.dr.squarei.csv", sep = ""))
+Pn.strong.fname = file.path(data.dir, paste(family, "_R0_10_beta_strong.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
+energy.strong.fname = file.path(data.dir, paste(family, "_R0_10_beta_strong.sel_K.analysis_Keff_out_m.theo.va.csv", sep = ""))
 
-dri2.mut.fname = file.path(data.dir,paste(family, "_R0_7.5_beta_no.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
-Pn.mut.fname = file.path(data.dir, paste(family, "_R0_7.5_beta_no.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
-energy.mut.fname = file.path(data.dir, paste(family, "_R0_7.5_beta_no.sel_K.analysis_Keff_out_m.theo.va.csv", sep = ""))
+dri2.mut.fname = file.path(data.dir,paste(family, "_R0_10_beta_no.sel_K.analysis_Keff_out_m.theo.smooth.norm.dr.squarei.csv", sep = ""))
+Pn.mut.fname = file.path(data.dir, paste(family, "_R0_10_beta_no.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
+energy.mut.fname = file.path(data.dir, paste(family, "_R0_10_beta_no.sel_K.analysis_Keff_out_m.theo.va.csv", sep = ""))
 

### 2016-07-27 OUT/analysis-structure.Rmd
cambios 27/07/2016

--- 2016-07-27 OUT/analysis-structure-CM.Rmd
@@
 date: "25 de julio de 2016"
-output: html_document
+output: pdf_document
 ---
@@
 
-dri2.exp.fname = file.path(data.dir, paste(family, "_R0_7.5_beta_strong.sel_K.analysis_Keff_out_m.exp.norm.dr.squarei.csv", sep = ""))
+dri2.exp.fname = file.path(data.dir, paste(family, "_R0_7.5_beta_strong.sel_K.analysis_Keff_out_m.exp.smooth.norm.dr.squarei.csv", sep = ""))
 Pn.exp.fname = file.path(data.dir, paste(family,"_R0_7.5_beta_strong.sel_K.analysis_Keff_out_m.exp.Pn.csv", sep = ""))
@@
 
-dri2.strong.fname = file.path(data.dir, paste(family, "_R0_7.5_beta_strong.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
+dri2.strong.fname = file.path(data.dir, paste(family, "_R0_7.5_beta_strong.sel_K.analysis_Keff_out_m.theo.smooth.norm.dr.squarei.csv", sep = ""))
 Pn.strong.fname = file.path(data.dir, paste(family, "_R0_7.5_beta_strong.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
@@
 
-dri2.mut.fname = file.path(data.dir,paste(family, "_R0_7.5_beta_no.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
+dri2.mut.fname = file.path(data.dir,paste(family, "_R0_7.5_beta_no.sel_K.analysis_Keff_out_m.theo.smooth.norm.dr.squarei.csv", sep = ""))
 Pn.mut.fname = file.path(data.dir, paste(family, "_R0_7.5_beta_no.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))

### 2016-07-27 other_programs/MultipleReportAllBetasGlobinsZscore2.Rmd
cambios 27/07/2016

---
title: "Estudio variabilidad estructural proteica"
output: html_document
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(warning = FALSE, echo = FALSE, message = FALSE)
```

```{r}
# Load packages.
library(bio3d)
library(ggplot2)

# Source functions.
source("FUNCTIONS/CalculateGroupsMeansQuantiles.R")

# Set directories.
data.dir <- "DATA"
out.dir <- "OUT/out_subset_CM"

# p.ref.
n.sites.p.ref = 156

# Create matrices to save data.
m.MSDi.fit = matrix(nrow = 4, ncol = n.sites.p.ref)
m.exp.MSDi = matrix(nrow = 4, ncol = n.sites.p.ref)
m.exp.MSDi.sd = matrix(nrow = 4, ncol = n.sites.p.ref)
m.MSDi.R2 = matrix(nrow = 4, ncol = 1)
m.MSDi.MSE = matrix(nrow = 4, ncol = 1)

m.Pn.fit = matrix(nrow = 4, ncol = 3 * n.sites.p.ref)
m.exp.Pn = matrix(nrow = 4, ncol = 3 * n.sites.p.ref)
m.Pn.R2 = matrix(nrow = 4, ncol = 1)
m.Pn.MSE = matrix(nrow = 4, ncol = 1)

m.mean.theo.Pn.group = matrix(nrow = 4, ncol = 3 * n.sites.p.ref)
m.mean.exp.Pn = matrix(nrow = 4, ncol = 3 * n.sites.p.ref)
m.exp.Pn.sd = matrix(nrow = 4, ncol = 3 * n.sites.p.ref)

# Read betas.
all.betas <- list("strong.sel", "medium.sel", "weak.sel", "no.sel")

# Information of sites.
gaps = c(18, 19, 51, 52, 53, 54, 55, 148, 149, 150, 151)
active = c(28, 29, 32, 64, 68, 93, 107)
heme = c(152, 153, 154, 155, 156)

# Start a loop for each beta.
  for (beta in all.betas)  {

    ### Experimental ###

    analysis.fname.id <- paste(family, "_R0_", R0, "_beta_", beta, "_K.analysis_", K.analysis, sep = "")

    # Pn.
    m.exp.Pn = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.exp.Pn.csv", sep = "")))[, 1:100]
    mean.exp.Pn = colMeans(m.exp.Pn)
    m.mean.exp.Pn[as.vector(all.betas == beta), 1:length(mean.exp.Pn)] = mean.exp.Pn
    n.prot = nrow(m.exp.Pn)

    # MSDi.
    m.exp.smooth.norm.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.exp.norm.dr.squarei.csv", sep = "")))

    m.exp.smooth.norm.dr.squarei = m.exp.smooth.norm.dr.squarei[-c(6, 7, 9, 29, 31), ] # Saqué proteínas que Julian no usó

    n.prot = nrow(m.exp.smooth.norm.dr.squarei)
    exp.smooth.norm.MSDi = colMeans(m.exp.smooth.norm.dr.squarei, na.rm = T)
    exp.smooth.norm.MSDi.sd = apply(m.exp.smooth.norm.dr.squarei, 2, sd, na.rm = T)/sqrt(no.gaps) * 1.96 # Ver si no hay que hacer sd dp

    exp.smooth.norm.MSDi.sd = exp.smooth.norm.MSDi.sd[!is.na(exp.smooth.norm.MSDi.sd)]

    exp.smooth.norm.MSDi = scale(sqrt(exp.smooth.norm.MSDi))[, 1]

    exp.smooth.norm.MSDi = exp.smooth.norm.MSDi[!is.na(exp.smooth.norm.MSDi)]

    ### Theoretical ###

    # Pn.
    m.theo.Pn = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.Pn.csv", sep = "")))[, 1:100]

    n.mut = nrow(m.theo.Pn)

    # MSDi.
    m.theo.smooth.norm.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.norm.dr.squarei.csv", sep = "")))

    theo.smooth.norm.MSDi = colMeans(m.theo.smooth.norm.dr.squarei, na.rm = T)

    MSDi.fit = scale(sqrt(theo.smooth.norm.MSDi))[, 1]

    MSDi.fit = MSDi.fit[1:length(exp.smooth.norm.MSDi)]

    ### COMPARE EXPERIMENTAL AND THEORETICAL ###
    MSDi.R2 = cor(exp.smooth.norm.MSDi, MSDi.fit) ^ 2

    MSDi.MSE = mean((MSDi.fit - exp.smooth.norm.MSDi) ^ 2)

    ### SAVE DATA IN MATRICES ###
    m.exp.MSDi[as.vector(all.betas == beta), ] = exp.smooth.norm.MSDi
    m.exp.MSDi.sd[as.vector(all.betas == beta), ] = exp.smooth.norm.MSDi.sd
    m.MSDi.fit[as.vector(all.betas == beta), ] = MSDi.fit
    m.MSDi.R2[as.vector(all.betas == beta), ] = MSDi.R2
    m.MSDi.MSE[as.vector(all.betas == beta), ] = MSDi.MSE

    ### Pn ###

    # Calculate groups, means and quantiles.
    theo.Pn.group = CalculateGroupsMeansQuantiles(m.theo.Pn, n.mut.p, n.prot)
    mean.theo.Pn.group = theo.Pn.group$mean.mean.group

    m.mean.theo.Pn.group[as.vector(all.betas == beta), 1:length(mean.theo.Pn.group)] = mean.theo.Pn.group

    Pn.fit = lm(mean.exp.Pn ~  mean.theo.Pn.group)
    Pn.fit = fitted.values(Pn.fit)
    Pn.R2 = cor(mean.exp.Pn, Pn.fit) ^ 2 
    Pn.MSE = mean((Pn.fit - mean.exp.Pn) ^ 2)

    m.mean.exp.Pn[as.vector(all.betas == beta), 1:(length(mean.exp.Pn))] = mean.exp.Pn
    m.Pn.fit[as.vector(all.betas == beta), 1:(length(Pn.fit))] = Pn.fit
    m.Pn.R2[as.vector(all.betas == beta), ] = Pn.R2
    m.Pn.MSE[as.vector(all.betas == beta), ] = Pn.MSE

    # Write pdb files for MSDi.
    pdbs.fname <- file.path(data.dir, paste("1a6m.pdb", sep = ""))

    pdb <- read.pdb(pdbs.fname, ATOM.only = "TRUE")
    sel <- atom.select(pdb)
    b.factor <- pdb$atom$b
    site = as.numeric(pdb$atom[sel$atom, c("resno")])[1:1203]
    MSDi.fit.pdb <- vec2resno(as.vector(MSDi.fit[1:151]), site)
    exp.MSDi.pdb <- vec2resno(as.vector(exp.smooth.norm.MSDi[1:151]), site)
    b.factor.fit = b.factor
    b.factor.exp = b.factor

    b.factor.fit[1:1203] = MSDi.fit.pdb * 100
    b.factor.exp[1:1203] = exp.MSDi.pdb * 100

    write.pdb(pdb = pdb, b = b.factor.fit, file = file.path(out.dir, paste(family, "_", p.ref, "_beta_", beta, ".pdb", sep = "")))

    write.pdb(pdb = pdb, b = b.factor.exp, file = file.path(out.dir, paste(family, "_", p.ref, "_exp", ".pdb", sep = "")))
}

```

### MSDi

Los perfiles teoricos suavizados y normalizados de MSDi fueron fiteados con los perfiles exterimentales. Se compararon y se calcularon R^2 y MSE. Se indica el regimen de seleccion usada.

```{r}

layout(matrix(1:4, 2, 2, byrow = T))

MSDi.exp = m.exp.MSDi[1, 1:151]
MSDi.theo = m.MSDi.fit[1, 1:151]
MSDi.exp.sd = m.exp.MSDi.sd[1, 1:151]

data.MSDi = data.frame("MSDi.exp" = MSDi.exp, "MSDi.theo" = MSDi.theo, "sites" = seq(1:length(MSDi.exp)), "MSDi.exp.sd" = MSDi.exp.sd, "type" = active.sites$type)

ggplot(data = data.MSDi, aes(x = sites)) + 
  geom_errorbar(aes(y = MSDi.exp, ymin = MSDi.exp - MSDi.exp.sd, ymax = MSDi.exp + MSDi.exp.sd), width = 0, col = gray(0.5)) +
  geom_line(aes(y = MSDi.theo, colour = "MSDi.theo"), col = "black") +
  geom_point(aes(y = MSDi.exp, colour = type), size = 1.5) + 
  ylab("MSDi strong selection")

MSDi.exp = m.exp.MSDi[2, ]
MSDi.theo = m.MSDi.fit[2, ]
MSDi.exp.sd = m.exp.MSDi.sd[2, ]

data.MSDi = data.frame("MSDi.exp" = MSDi.exp, "MSDi.theo" = MSDi.theo, "sites" = seq(1:length(MSDi.exp)), "MSDi.exp.sd" = MSDi.exp.sd, "type" = active.sites$type)

ggplot(data = data.MSDi, aes(x = sites)) + 
  geom_errorbar(aes(y = MSDi.exp, ymin = MSDi.exp - MSDi.exp.sd, ymax = MSDi.exp + MSDi.exp.sd), width = 0, col = gray(0.5)) +
  geom_line(aes(y = MSDi.theo, colour = "MSDi.theo"), col = "black") +
  geom_point(aes(y = MSDi.exp, colour = type), size = 1.5) + 
  ylab("MSDi medium selection")

MSDi.exp = m.exp.MSDi[3, ]
MSDi.theo = m.MSDi.fit[3, ]
MSDi.exp.sd = m.exp.MSDi.sd[3, ]

data.MSDi = data.frame("MSDi.exp" = MSDi.exp, "MSDi.theo" = MSDi.theo, "sites" = seq(1:length(MSDi.exp)), "MSDi.exp.sd" = MSDi.exp.sd, "type" = active.sites$type)

ggplot(data = data.MSDi, aes(x = sites)) + 
  geom_errorbar(aes(y = MSDi.exp, ymin = MSDi.exp - MSDi.exp.sd, ymax = MSDi.exp + MSDi.exp.sd), width = 0, col = gray(0.5)) +
  geom_line(aes(y = MSDi.theo, colour = "MSDi.theo"), col = "black") +
  geom_point(aes(y = MSDi.exp, colour = type), size = 1.5) + 
  ylab("MSDi weak selection")

MSDi.exp = m.exp.MSDi[4, ]
MSDi.theo = m.MSDi.fit[4, ]
MSDi.exp.sd = m.exp.MSDi.sd[4, ]

data.MSDi = data.frame("MSDi.exp" = MSDi.exp, "MSDi.theo" = MSDi.theo, "sites" = seq(1:length(MSDi.exp)), "MSDi.exp.sd" = MSDi.exp.sd, "type" = active.sites$type)

ggplot(data = data.MSDi, aes(x = sites)) + 
  geom_errorbar(aes(y = MSDi.exp, ymin = MSDi.exp - MSDi.exp.sd, ymax = MSDi.exp + MSDi.exp.sd), width = 0, col = gray(0.5)) +
  geom_line(aes(y = MSDi.theo, colour = "MSDi.theo"), col = "black") +
  geom_point(aes(y = MSDi.exp, colour = type), size = 1.5) + 
  ylab("MSDi no selection") +
```

*Linea negra:* Promedio teorico.
*Puntos rojos:* Promedio experimental gaps. 
*Puntos verdes:* Promedio experimental sitio activo.
*Puntos amarillos:* Promedio experimental sitios en contacto con el sitio activo.
*Puntos negros:* Promedio experimental otros sitios.
*Barras grises:* intervalo Sd/sqrt(n.prot)*1.96.

```{r}
layout(matrix(1:2, 1, 2, byrow = T)) 
par(pty = "s")
plot(m.MSDi.fit[1, ], m.exp.MSDi[1, ], xlab = "MSDi teorico", ylab = "MSDi experimental", main = "MSDi strong selection", xlim = c(0.3, 3.5), ylim = c(0.3, 3.5), cex.main = 1, cex.lab = 1)
abline(0, 1)
legend("topleft", paste("R^2", round(m.MSDi.R2[1, ], digits = 2)), bty = "n", cex = 0.7)
legend("bottomright", paste("MSE", signif(m.MSDi.MSE[1, ], digits = 2)), bty = "n", cex = 0.7)
points(m.MSDi.fit[1, contacts.active],m.exp.MSDi[1, contacts.active], col = "yellow")
points(m.MSDi.fit[1, gaps],m.exp.MSDi[1, gaps], col = "red")
points(m.MSDi.fit[1, active],m.exp.MSDi[1, active], col = "green")

plot(m.MSDi.fit[2, ], m.exp.MSDi[2, ], xlab = "MSDi teorico", ylab = "MSDi experimental", main = "MSDi medium selection", xlim = c(0.3, 3.5), ylim = c(0.3, 3.5), cex.main = 1, cex.lab = 1)
abline(0, 1)
legend("topleft", paste("R^2", round(m.MSDi.R2[2, ], digits = 2)), bty = "n", cex = 0.7)
legend("bottomright", paste("MSE", signif(m.MSDi.MSE[2, ], digits = 2)), bty = "n", cex = 0.7)
points(m.MSDi.fit[2, contacts.active],m.exp.MSDi[2, contacts.active], col = "yellow")
points(m.MSDi.fit[2, gaps],m.exp.MSDi[2, gaps], col = "red")
points(m.MSDi.fit[2, active],m.exp.MSDi[2, active], col = "green")

plot(m.MSDi.fit[3, ], m.exp.MSDi[3, ], xlab = "MSDi teorico", ylab = "MSDi experimental", main = "MSDi weak selection", xlim = c(0.3, 3.5), ylim = c(0.3, 3.5), cex.main = 1, cex.lab = 1)
abline(0, 1)
legend("topleft", paste("R^2", round(m.MSDi.R2[3, ], digits = 2)), bty = "n", cex = 0.7)
legend("bottomright", paste("MSE", signif(m.MSDi.MSE[3, ], digits = 2)), bty = "n", cex = 0.7)
points(m.MSDi.fit[3, contacts.active],m.exp.MSDi[3, contacts.active], col = "yellow")
points(m.MSDi.fit[3, gaps],m.exp.MSDi[3, gaps] , col = "red") 
points(m.MSDi.fit[3, active],m.exp.MSDi[3, active] , col = "green")

plot(m.MSDi.fit[4, ], m.exp.MSDi[4, ], xlab = "MSDi teorico", ylab = "MSDi experimental", main = "MSDi no selection", xlim = c(0.3, 3.5), ylim = c(0.3, 3.5), cex.main = 1, cex.lab = 1)
abline(0, 1)
legend("topleft", paste("R^2", round(m.MSDi.R2[4, ], digits = 2)), bty = "n", cex = 0.7)
legend("bottomright", paste("MSE", signif(m.MSDi.MSE[4, ], digits = 2)), bty = "n", cex = 0.7)
points(m.MSDi.fit[4, contacts.active],m.exp.MSDi[4, contacts.active], col = "yellow")
points(m.MSDi.fit[4, gaps],m.exp.MSDi[4, gaps] , col = "red")
points(m.MSDi.fit[4, active],m.exp.MSDi[4, active] , col = "green")
```

```{r}
layout(matrix(1:2, 1, 2, byrow = T))

par(pty = "s")
plot(m.MSDi.fit[1, ], m.MSDi.fit[2, ], xlab = "MSDi strong selection", ylab = "MSDi medium selection", xlim = c(0.3, 3.5), ylim = c(0.3, 3.5), cex.main = 1, cex.lab = 1)
abline(0, 1)
legend("topleft", paste("R^2", round(cor(m.MSDi.fit[1, ], m.MSDi.fit[2, ]), digits = 4)), bty = "n", cex = 0.7)
legend("bottomright", paste("MSE", signif(mean((m.MSDi.fit[1, ] - m.MSDi.fit[2, ])^2), digits = 2)), bty = "n", cex = 0.7)
points(m.MSDi.fit[1, contacts.active],m.MSDi.fit[2, contacts.active], col = "yellow")
points(m.MSDi.fit[1, gaps],m.MSDi.fit[2, gaps], col = "red")
points(m.MSDi.fit[1, active],m.MSDi.fit[2, active], col = "green")

plot(m.MSDi.fit[1, ], m.MSDi.fit[3, ], xlab = "MSDi strong selection", ylab = "MSDi weak selection", xlim = c(0.3, 3.5), ylim = c(0.3, 3.5), cex.main = 1, cex.lab = 1)
abline(0, 1)
legend("topleft", paste("R^2", round(cor(m.MSDi.fit[1, ], m.MSDi.fit[3, ]), digits = 4)), bty = "n", cex = 0.7)
legend("bottomright", paste("MSE", signif(mean((m.MSDi.fit[1, ] - m.MSDi.fit[3, ])^2), digits = 2)), bty = "n", cex = 0.7)
points(m.MSDi.fit[1, contacts.active],m.MSDi.fit[3, contacts.active], col = "yellow")
points(m.MSDi.fit[1, gaps],m.MSDi.fit[3, gaps], col = "red")
points(m.MSDi.fit[1, active],m.MSDi.fit[3, active], col = "green")

plot(m.MSDi.fit[1, ], m.MSDi.fit[4, ], xlab = "MSDi strong selection", ylab = "MSDi no selection", xlim = c(0.3, 3.5), ylim = c(0.3, 3.5), cex.main = 1, cex.lab = 1)
abline(0, 1)
legend("topleft", paste("R^2", round(cor(m.MSDi.fit[1, ], m.MSDi.fit[4, ]), digits = 4)), bty = "n", cex = 0.7)
legend("bottomright", paste("MSE", signif(mean((m.MSDi.fit[1, ] - m.MSDi.fit[4, ])^2), digits = 2)), bty = "n", cex = 0.7)
points(m.MSDi.fit[1, contacts.active],m.MSDi.fit[4, contacts.active], col = "yellow")
points(m.MSDi.fit[1, gaps],m.MSDi.fit[4, gaps], col = "red")
points(m.MSDi.fit[1, active],m.MSDi.fit[4, active], col = "green")

plot(m.MSDi.fit[2, ], m.MSDi.fit[3, ], xlab = "MSDi medium selection", ylab = "MSDi weak selection", xlim = c(0.3, 3.5), ylim = c(0.3, 3.5), cex.main = 1, cex.lab = 1)
abline(0, 1)
legend("topleft", paste("R^2", round(cor(m.MSDi.fit[2, ], m.MSDi.fit[3, ]), digits = 4)), bty = "n", cex = 0.7)
legend("bottomright", paste("MSE", signif(mean((m.MSDi.fit[2, ] - m.MSDi.fit[3, ])^2), digits = 2)), bty = "n", cex = 0.7)
points(m.MSDi.fit[2, contacts.active],m.MSDi.fit[3, contacts.active], col = "yellow")
points(m.MSDi.fit[2, gaps],m.MSDi.fit[3, gaps], col = "red")
points(m.MSDi.fit[2, active],m.MSDi.fit[3, active], col = "green")

plot(m.MSDi.fit[2, ], m.MSDi.fit[4, ], xlab = "MSDi medium selection", ylab = "MSDi no selection", xlim = c(0.3, 3.5), ylim = c(0.3, 3.5), cex.main = 1, cex.lab = 1)
abline(0, 1)
legend("topleft", paste("R^2", round(cor(m.MSDi.fit[2, ], m.MSDi.fit[4, ]), digits = 4)), bty = "n", cex = 0.7)
legend("bottomright", paste("MSE", signif(mean((m.MSDi.fit[2, ] - m.MSDi.fit[4, ])^2), digits = 2)), bty = "n", cex = 0.7)
points(m.MSDi.fit[2, contacts.active],m.MSDi.fit[4, contacts.active], col = "yellow")
points(m.MSDi.fit[2, gaps],m.MSDi.fit[4, gaps], col = "red")
points(m.MSDi.fit[2, active],m.MSDi.fit[4, active], col = "green")

plot(m.MSDi.fit[3, ], m.MSDi.fit[4, ], xlab = "MSDi weak selection", ylab = "MSDi no selection", xlim = c(0.3, 3.5), ylim = c(0.3, 3.5), cex.main = 1, cex.lab = 1)
abline(0, 1)
legend("topleft", paste("R^2", round(cor(m.MSDi.fit[3, ], m.MSDi.fit[4, ]), digits = 4)), bty = "n", cex = 0.7)
legend("bottomright", paste("MSE", signif(mean((m.MSDi.fit[3, ] - m.MSDi.fit[4, ])^2), digits = 2)), bty = "n", cex = 0.7)
points(m.MSDi.fit[3, contacts.active],m.MSDi.fit[4, contacts.active], col = "yellow")
points(m.MSDi.fit[3, gaps],m.MSDi.fit[4, gaps], col = "red")
points(m.MSDi.fit[3, active],m.MSDi.fit[4, active], col = "green")
```

*Rojo:* Gaps. 
*Verde:* Sitio activo.
*Amarillo:* Sitios en contacto con el sitio activo.
*Negro:* Otros sitios.

### Pn y Qn
Las distribuciones de *Pn* y *Qn* de los conjuntos son las siguientes:

```{r}
layout(matrix(1:4, 2, 2, byrow = T))

Pn.exp = m.mean.exp.Pn[1, 1:100]
Pn.theo = m.mean.theo.Pn.group[1, 1:100]
Pn.exp.sd = m.exp.Pn.sd[1, 1:100]

data.Pn = data.frame("Pn.exp" = Pn.exp, "Pn.theo" = Pn.theo, "modes" = seq(1:length(Pn.exp)), "Pn.exp.sd" = Pn.exp.sd)
ggplot(data = data.Pn, aes(x = modes)) + 
  geom_point(aes(y = Pn.exp, colour = "Pn.exp")) + 
  geom_line(aes(y = Pn.theo, colour = "Pn.theo"), col = "black") +
  ylab("Pn strong selecion") + 
  geom_errorbar(aes(y = Pn.exp, ymin = Pn.exp - Pn.exp.sd, ymax = Pn.exp + Pn.exp.sd), width = 0, col = "red") +
geom_smooth(aes(y = Pn.exp), colour = "red", span = 0.4)

Pn.exp = m.mean.exp.Pn[2, 1:100]
Pn.theo = m.mean.theo.Pn.group[2, 1:100]
Pn.exp.sd = m.exp.Pn.sd[2, 1:100]

data.Pn = data.frame("Pn.exp" = Pn.exp, "Pn.theo" = Pn.theo, "modes" = seq(1:length(Pn.exp)), "Pn.exp.sd" = Pn.exp.sd)
ggplot(data = data.Pn, aes(x = modes)) + 
  geom_point(aes(y = Pn.exp, colour = "Pn.exp")) + 
  geom_line(aes(y = Pn.theo, colour = "Pn.theo"), col = "black") +
  ylab("Pn medium selecion") + 
  geom_errorbar(aes(y = Pn.exp, ymin = Pn.exp - Pn.exp.sd, ymax = Pn.exp + Pn.exp.sd), width = 0, col = "red") +
geom_smooth(aes(y = Pn.exp), colour = "red", span = 0.4)

Pn.exp = m.mean.exp.Pn[3, 1:100]
Pn.theo = m.mean.theo.Pn.group[3, 1:100]
Pn.exp.sd = m.exp.Pn.sd[3, 1:100]

data.Pn = data.frame("Pn.exp" = Pn.exp, "Pn.theo" = Pn.theo, "modes" = seq(1:length(Pn.exp)), "Pn.exp.sd" = Pn.exp.sd)
ggplot(data = data.Pn, aes(x = modes)) + 
  geom_point(aes(y = Pn.exp, colour = "Pn.exp")) + 
  geom_line(aes(y = Pn.theo, colour = "Pn.theo"), col = "black") +
  ylab("Pn weak selecion") + 
  geom_errorbar(aes(y = Pn.exp, ymin = Pn.exp - Pn.exp.sd, ymax = Pn.exp + Pn.exp.sd), width = 0, col = "red") +
  geom_smooth(aes(y = Pn.exp), colour = "red", span = 0.4)

Pn.exp = m.mean.exp.Pn[4, 1:100]
Pn.theo = m.mean.theo.Pn.group[4, 1:100]
Pn.exp.sd = m.exp.Pn.sd[4, 1:100]

data.Pn = data.frame("Pn.exp" = Pn.exp, "Pn.theo" = Pn.theo, "modes" = seq(1:length(Pn.exp)), "Pn.exp.sd" = Pn.exp.sd)
ggplot(data = data.Pn, aes(x = modes)) + 
  geom_point(aes(y = Pn.exp, colour = "Pn.exp")) + 
  geom_line(aes(y = Pn.theo, colour = "Pn.theo"), col = "black") +
  ylab("Pn no selecion") + 
  geom_errorbar(aes(y = Pn.exp, ymin = Pn.exp - Pn.exp.sd, ymax = Pn.exp + Pn.exp.sd), width = 0, col = "red") + 
  geom_smooth(aes(y = Pn.exp), colour = "red", span = 0.4)

```

*Linea negra*: Promedio teorico.
*Puntos rojos*: Promedio experimental.
*Barras rojas:* intervalo Sd/sqrt(n.prot)*1.96.
*Liena roja y banda gris:* geom_smooth experimental con span = 0.4

```{r}
layout(matrix(1:2, 1, 2, byrow = T)) 
par(pty = "s")

plot(m.mean.theo.Pn.group[1, ], m.mean.exp.Pn[1, ], xlab = "<<Pn>> teorico", ylab = "<Pn> experimental", main = "Pn strong selection", xlim = c(0, 0.04), ylim = c(0, 0.04), cex.main = 1, cex.lab = 1)
abline(0, 1)
legend("topleft", paste("R^2", round(m.Pn.R2[1, ], digits = 2)), bty = "n", cex = 0.7)
legend("bottomright", paste("MSE", signif(m.Pn.MSE[1, ], digits = 2)), bty = "n", cex = 0.7)

plot(m.mean.theo.Pn.group[2, ], m.mean.exp.Pn[2, ], xlab = "<<Pn>> teorico", ylab = "<Pn> experimental", main = "Pn medium selection", xlim = c(0, 0.04), ylim = c(0, 0.04), cex.main = 1, cex.lab = 1)
abline(0, 1)
legend("topleft", paste("R^2", round(m.Pn.R2[2, ], digits = 2)), bty = "n", cex = 0.7)
legend("bottomright", paste("MSE", signif(m.Pn.MSE[2, ], digits = 2)), bty = "n", cex = 0.7)

plot(m.mean.theo.Pn.group[3, ], m.mean.exp.Pn[3, ], xlab = "<<Pn>> teorico", ylab = "<Pn> experimental", main = "Pn weak selection", xlim = c(0, 0.04), ylim = c(0, 0.04), cex.main = 1, cex.lab = 1)
abline(0, 1)
legend("topleft", paste("R^2", round(m.Pn.R2[3, ], digits = 2)), bty = "n", cex = 0.7)
legend("bottomright", paste("MSE", signif(m.Pn.MSE[3, ], digits = 2)), bty = "n", cex = 0.7)

plot(m.mean.theo.Pn.group[4, ], m.mean.exp.Pn[4, ], xlab = "<<Pn>> teorico", ylab = "<Pn> experimental", main = "Pn no selection", xlim = c(0, 0.04), ylim = c(0, 0.04), cex.main = 1, cex.lab = 1)
abline(0, 1)
legend("topleft", paste("R^2", round(m.Pn.R2[4, ], digits = 2)), bty = "n", cex = 0.7)
legend("bottomright", paste("MSE", signif(m.Pn.MSE[4, ], digits = 2)), bty = "n", cex = 0.7)

```

### 2016-07-27 other_programs/MultipleReportAllBetasGlobinsZscoreGenerico.Rmd
cambios 27/07/2016

---
title: "Estudio variabilidad estructural proteica"
output: html_document
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(warning = FALSE, echo = FALSE, message = FALSE)
```

```{r}
# Load packages.
library(bio3d)
library(ggplot2)

# Source functions.
source("FUNCTIONS/CalculateGroupsMeansQuantiles.R")

# Set directories.
data.dir <- "DATA"

# p.ref.
n.sites.p.ref = 156

# Create matrices to save data.
m.MSDi.fit = matrix(nrow = 4, ncol = n.sites.p.ref)
m.exp.MSDi = matrix(nrow = 4, ncol = n.sites.p.ref)
m.exp.MSDi.sd = matrix(nrow = 4, ncol = n.sites.p.ref)
m.MSDi.R2 = matrix(nrow = 4, ncol = 1)
m.MSDi.MSE = matrix(nrow = 4, ncol = 1)

m.Pn.fit = matrix(nrow = 4, ncol = 3 * n.sites.p.ref)
m.exp.Pn = matrix(nrow = 4, ncol = 3 * n.sites.p.ref)
m.Pn.R2 = matrix(nrow = 4, ncol = 1)
m.Pn.MSE = matrix(nrow = 4, ncol = 1)

m.mean.theo.Pn.group = matrix(nrow = 4, ncol = 3 * n.sites.p.ref)
m.mean.exp.Pn = matrix(nrow = 4, ncol = 3 * n.sites.p.ref)
m.exp.Pn.sd = matrix(nrow = 4, ncol = 3 * n.sites.p.ref)

# Read betas.
all.betas <- list("strong.sel", "medium.sel", "weak.sel", "no.sel")

# Information of sites.
gaps = c(18, 19, 51, 52, 53, 54, 55, 148, 149, 150, 151)
active = c(28, 29, 32, 64, 68, 93, 107)
contacts.active = c(24, 25, 26, 27, 28, 29, 30, 31, 32, 33, 34, 35, 36, 39, 60,  61, 62, 63, 64, 65, 66, 67, 68, 69, 70, 71, 72, 89,  90, 91,  92, 94, 95, 96, 97, 98, 99, 103, 104, 105, 106, 107, 108, 109, 110, 111, 114, 152, 153, 154, 155, 156)
heme = c(152, 153, 154, 155, 156)

type = rep("else", n.sites.p.ref)
type[contacts.active] = "contacts.active"
type[active] = "active"
type[gaps] = "gap"
type[heme] = "heme"

# Start a loop for each beta.
  for (beta in all.betas)  {

    ### Experimental ###

    analysis.fname.id <- paste(family, "_R0_", R0, "_beta_", beta, "_K.analysis_", K.analysis, sep = "")

    # Pn.
    m.exp.Pn = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.exp.Pn.csv", sep = "")))[, 1:100]
    mean.exp.Pn = colMeans(m.exp.Pn)
    m.mean.exp.Pn[as.vector(all.betas == beta), 1:length(mean.exp.Pn)] = mean.exp.Pn

    # MSDi.
    m.exp.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.exp.norm.dr.squarei.csv", sep = "")))
    m.exp.dr.squarei = m.exp.dr.squarei[-c(6, 7, 9, 29, 31), ]  # Saqué proteínas que Julian no usó
    n.prot = nrow(m.exp.dr.squarei)
    for (p in (1:n.prot)) {
      m.exp.dr.squarei[p, ] = scale(sqrt(as.numeric(m.exp.dr.squarei[p, ])))[, 1]
    }

    no.gaps = colSums(matrix(as.numeric(!is.na(m.exp.dr.squarei)), nrow = n.prot))
    exp.MSDi = colMeans(m.exp.dr.squarei, na.rm = T)
    exp.MSDi = exp.MSDi[!is.na(exp.MSDi)]

    exp.MSDi.sd = apply(m.exp.dr.squarei, 2, sd, na.rm = T)/sqrt(no.gaps) * 1.96 # Ver si no hay que calcular sd dp
    exp.MSDi.sd = exp.MSDi.sd[!is.na(exp.MSDi.sd)]

    ### Theoretical ###

    # Pn
    m.theo.Pn = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.Pn.csv", sep = "")))[, 1:100]
    n.mut = nrow(m.theo.Pn)

    # MSDi
    m.theo.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.norm.dr.squarei.csv", sep = "")))
    theo.MSDi = colMeans(m.theo.dr.squarei, na.rm = T)
    MSDi.fit = scale(sqrt(theo.MSDi))
    MSDi.fit = MSDi.fit[1:length(exp.MSDi)]

    ### COMPARE EXPERIMENTAL AND THEORETICAL ###
    MSDi.R2 = cor(exp.MSDi, MSDi.fit) ^ 2 
    MSDi.MSE = mean((MSDi.fit - exp.MSDi) ^ 2)

    ### SAVE DATA IN MATRICES ###
    m.exp.MSDi[as.vector(all.betas == beta), ] = exp.MSDi
    m.exp.MSDi.sd[as.vector(all.betas == beta), ] = exp.MSDi.sd
    m.MSDi.fit[as.vector(all.betas == beta), ] = MSDi.fit
    m.MSDi.R2[as.vector(all.betas == beta), ] = MSDi.R2
    m.MSDi.MSE[as.vector(all.betas == beta), ] = MSDi.MSE

    ### Pn ###

    # Calculate groups, means and quantiles.
    theo.Pn.group = CalculateGroupsMeansQuantiles(m.theo.Pn, n.mut.p, n.prot)
    mean.theo.Pn.group = theo.Pn.group$mean.mean.group

    m.mean.theo.Pn.group[as.vector(all.betas == beta), 1:length(mean.theo.Pn.group)] = mean.theo.Pn.group

    Pn.fit = lm(mean.exp.Pn ~  mean.theo.Pn.group)
    Pn.fit = fitted.values(Pn.fit)
    Pn.R2 = cor(mean.exp.Pn, Pn.fit) ^ 2 
    Pn.MSE = mean((Pn.fit - mean.exp.Pn) ^ 2)

    m.mean.exp.Pn[as.vector(all.betas == beta), 1:(length(mean.exp.Pn))] = mean.exp.Pn
    m.Pn.fit[as.vector(all.betas == beta), 1:(length(Pn.fit))] = Pn.fit
    m.Pn.R2[as.vector(all.betas == beta), ] = Pn.R2
    m.Pn.MSE[as.vector(all.betas == beta), ] = Pn.MSE

    # Write pdb files for MSDi
    pdbs.fname <- file.path(data.dir, paste("1a6m.pdb", sep = ""))

    pdb <- read.pdb(pdbs.fname, ATOM.only = "TRUE")
    sel <- atom.select(pdb)
    b.factor <- pdb$atom$b
    site = as.numeric(pdb$atom[sel$atom, c("resno")])[1:1213]
    MSDi.fit.pdb <- vec2resno(as.vector(MSDi.fit[1:151]), site)
    exp.MSDi.pdb <- vec2resno(as.vector(exp.MSDi[1:151]), site)
    b.factor.fit = b.factor
    b.factor.exp = b.factor

    b.factor.fit[1:1213] = MSDi.fit.pdb * 100
    b.factor.exp[1:1213] = exp.MSDi.pdb * 100

    write.pdb(pdb = pdb, b = b.factor.fit, file = file.path(out.dir, paste(family, "_", p.ref, "_CM_smooth_beta_", beta, ".pdb", sep = "")))

    write.pdb(pdb = pdb, b = b.factor.exp, file = file.path(out.dir, paste(family, "_", p.ref, "_CM_smooth_exp", ".pdb", sep = "")))
}

```

### MSDi

Los perfiles normalizados de MSDi se compararon cualitativamente y cuantitativamente mediante el calculo de R^2 y MSE. En cada caso se indica el regimen de seleccion usado, correspondiendo "strong sel", "medium sel", "weak sel" y "no sel" a beta = 0.2, 0.5, 0.8 y 1 respectivamente.

```{r}

layout(matrix(1:4, 2, 2, byrow = T))

MSDi.exp = m.exp.MSDi[1, ]
MSDi.theo = m.MSDi.fit[1, ]
MSDi.exp.sd = m.exp.MSDi.sd[1, ]

data.MSDi = data.frame("MSDi.exp" = MSDi.exp, "MSDi.theo" = MSDi.theo, "sites" = seq(1:length(MSDi.exp)), "MSDi.exp.sd" = MSDi.exp.sd, "type" = type)

ggplot(data = data.MSDi, aes(x = sites)) + 
  geom_errorbar(aes(y = MSDi.exp, ymin = MSDi.exp - MSDi.exp.sd, ymax = MSDi.exp + MSDi.exp.sd), width = 0, col = gray(0.5)) +
  geom_line(aes(y = MSDi.theo, colour = "MSDi.theo"), col = "black") +
  geom_point(aes(y = MSDi.exp, colour = type), size = 1.5) + 
  ylab("MSDi strong selection") +
  scale_color_manual(values = c("green", "yellow","black", "red", "blue"))

MSDi.exp = m.exp.MSDi[2, ]
MSDi.theo = m.MSDi.fit[2, ]
MSDi.exp.sd = m.exp.MSDi.sd[2, ]

data.MSDi = data.frame("MSDi.exp" = MSDi.exp, "MSDi.theo" = MSDi.theo, "sites" = seq(1:length(MSDi.exp)), "MSDi.exp.sd" = MSDi.exp.sd, "type" = type)

ggplot(data = data.MSDi, aes(x = sites)) + 
  geom_errorbar(aes(y = MSDi.exp, ymin = MSDi.exp - MSDi.exp.sd, ymax = MSDi.exp + MSDi.exp.sd), width = 0, col = gray(0.5)) +
  geom_line(aes(y = MSDi.theo, colour = "MSDi.theo"), col = "black") +
  geom_point(aes(y = MSDi.exp, colour = type), size = 1.5) + 
  ylab("MSDi medium selection") +
  scale_color_manual(values = c("green", "yellow","black", "red", "blue"))

MSDi.exp = m.exp.MSDi[3, ]
MSDi.theo = m.MSDi.fit[3, ]
MSDi.exp.sd = m.exp.MSDi.sd[3, ]

data.MSDi = data.frame("MSDi.exp" = MSDi.exp, "MSDi.theo" = MSDi.theo, "sites" = seq(1:length(MSDi.exp)), "MSDi.exp.sd" = MSDi.exp.sd, "type" = type)

ggplot(data = data.MSDi, aes(x = sites)) + 
  geom_errorbar(aes(y = MSDi.exp, ymin = MSDi.exp - MSDi.exp.sd, ymax = MSDi.exp + MSDi.exp.sd), width = 0, col = gray(0.5)) +
  geom_line(aes(y = MSDi.theo, colour = "MSDi.theo"), col = "black") +
  geom_point(aes(y = MSDi.exp, colour = type), size = 1.5) + 
  ylab("MSDi weak selection") +
  scale_color_manual(values = c("green", "yellow","black", "red", "blue"))

MSDi.exp = m.exp.MSDi[4, ]
MSDi.theo = m.MSDi.fit[4, ]
MSDi.exp.sd = m.exp.MSDi.sd[4, ]

data.MSDi = data.frame("MSDi.exp" = MSDi.exp, "MSDi.theo" = MSDi.theo, "sites" = seq(1:length(MSDi.exp)), "MSDi.exp.sd" = MSDi.exp.sd, "type" = type)

ggplot(data = data.MSDi, aes(x = sites)) + 
  geom_errorbar(aes(y = MSDi.exp, ymin = MSDi.exp - MSDi.exp.sd, ymax = MSDi.exp + MSDi.exp.sd), width = 0, col = gray(0.5)) +
  geom_line(aes(y = MSDi.theo, colour = "MSDi.theo"), col = "black") +
  geom_point(aes(y = MSDi.exp, colour = type), size = 1.5) + 
  ylab("MSDi no selection") +
  scale_color_manual(values = c("green", "yellow","black", "red", "blue"))

```

*Linea negra:* Promedio teorico.
*Puntos rojos:* Promedio experimental gaps. 
*Puntos verdes:* Promedio experimental sitio activo.
*Puntos amarillos:* Promedio experimental sitios en contacto con el sitio activo.
*Puntos azules:* Promedio experimental Hemo.
*Puntos negros:* Promedio experimental otros sitios.
*Barras grises:* intervalo Sd/sqrt(n.prot) * 1.96 conjunto experimental.

```{r}
layout(matrix(1:2, 1, 2, byrow = T)) 
par(pty = "s")
plot(m.MSDi.fit[1, ], m.exp.MSDi[1, ], xlab = "MSDi teorico", ylab = "MSDi experimental", main = "MSDi strong selection", cex.main = 1, cex.lab = 1)
abline(0, 1)
legend("topleft", paste("R^2", round(m.MSDi.R2[1, ], digits = 2)), bty = "n", cex = 0.7)
legend("bottomright", paste("MSE", signif(m.MSDi.MSE[1, ], digits = 2)), bty = "n", cex = 0.7)
points(m.MSDi.fit[1, contacts.active],m.exp.MSDi[1, contacts.active], col = "yellow")
points(m.MSDi.fit[1, gaps],m.exp.MSDi[1, gaps], col = "red")
points(m.MSDi.fit[1, active],m.exp.MSDi[1, active], col = "green")
points(m.MSDi.fit[1, heme],m.exp.MSDi[1, heme], col = "blue")

plot(m.MSDi.fit[2, ], m.exp.MSDi[2, ], xlab = "MSDi teorico", ylab = "MSDi experimental", main = "MSDi medium selection", cex.main = 1, cex.lab = 1)
abline(0, 1)
legend("topleft", paste("R^2", round(m.MSDi.R2[2, ], digits = 2)), bty = "n", cex = 0.7)
legend("bottomright", paste("MSE", signif(m.MSDi.MSE[2, ], digits = 2)), bty = "n", cex = 0.7)
points(m.MSDi.fit[2, contacts.active],m.exp.MSDi[2, contacts.active], col = "yellow")
points(m.MSDi.fit[2, gaps],m.exp.MSDi[2, gaps], col = "red")
points(m.MSDi.fit[2, active],m.exp.MSDi[2, active], col = "green")
points(m.MSDi.fit[2, heme],m.exp.MSDi[2, heme], col = "blue")

plot(m.MSDi.fit[3, ], m.exp.MSDi[3, ], xlab = "MSDi teorico", ylab = "MSDi experimental", main = "MSDi weak selection", cex.main = 1, cex.lab = 1)
abline(0, 1)
legend("topleft", paste("R^2", round(m.MSDi.R2[3, ], digits = 2)), bty = "n", cex = 0.7)
legend("bottomright", paste("MSE", signif(m.MSDi.MSE[3, ], digits = 2)), bty = "n", cex = 0.7)
points(m.MSDi.fit[3, contacts.active],m.exp.MSDi[3, contacts.active], col = "yellow")
points(m.MSDi.fit[3, gaps],m.exp.MSDi[3, gaps] , col = "red") 
points(m.MSDi.fit[3, active],m.exp.MSDi[3, active] , col = "green") 
points(m.MSDi.fit[3, heme],m.exp.MSDi[3, heme], col = "blue")

plot(m.MSDi.fit[4, ], m.exp.MSDi[4, ], xlab = "MSDi teorico", ylab = "MSDi experimental", main = "MSDi no selection", cex.main = 1, cex.lab = 1)
abline(0, 1)
legend("topleft", paste("R^2", round(m.MSDi.R2[4, ], digits = 2)), bty = "n", cex = 0.7)
legend("bottomright", paste("MSE", signif(m.MSDi.MSE[4, ], digits = 2)), bty = "n", cex = 0.7)
points(m.MSDi.fit[4, contacts.active],m.exp.MSDi[4, contacts.active], col = "yellow")
points(m.MSDi.fit[4, gaps],m.exp.MSDi[4, gaps] , col = "red")
points(m.MSDi.fit[4, active],m.exp.MSDi[4, active] , col = "green")
points(m.MSDi.fit[4, heme],m.exp.MSDi[4, heme], col = "blue")

```

```{r}
layout(matrix(1:2, 1, 2, byrow = T))

par(pty = "s")
plot(m.MSDi.fit[1, ], m.MSDi.fit[2, ], xlab = "MSDi strong selection", ylab = "MSDi medium selection", cex.main = 1, cex.lab = 1)
abline(0, 1)
legend("topleft", paste("R^2", round(cor(m.MSDi.fit[1, ], m.MSDi.fit[2, ]), digits = 4)), bty = "n", cex = 0.7)
legend("bottomright", paste("MSE", signif(mean((m.MSDi.fit[1, ] - m.MSDi.fit[2, ])^2), digits = 2)), bty = "n", cex = 0.7)
points(m.MSDi.fit[1, contacts.active],m.MSDi.fit[2, contacts.active], col = "yellow")
points(m.MSDi.fit[1, gaps],m.MSDi.fit[2, gaps], col = "red")
points(m.MSDi.fit[1, active],m.MSDi.fit[2, active], col = "green")
points(m.MSDi.fit[1, heme],m.MSDi.fit[2, heme], col = "blue")

plot(m.MSDi.fit[1, ], m.MSDi.fit[3, ], xlab = "MSDi strong selection", ylab = "MSDi weak selection", cex.main = 1, cex.lab = 1)
abline(0, 1)
legend("topleft", paste("R^2", round(cor(m.MSDi.fit[1, ], m.MSDi.fit[3, ]), digits = 4)), bty = "n", cex = 0.7)
legend("bottomright", paste("MSE", signif(mean((m.MSDi.fit[1, ] - m.MSDi.fit[3, ])^2), digits = 2)), bty = "n", cex = 0.7)
points(m.MSDi.fit[1, contacts.active],m.MSDi.fit[3, contacts.active], col = "yellow")
points(m.MSDi.fit[1, gaps],m.MSDi.fit[3, gaps], col = "red")
points(m.MSDi.fit[1, active],m.MSDi.fit[3, active], col = "green")
points(m.MSDi.fit[1, heme],m.MSDi.fit[3, heme], col = "blue")

plot(m.MSDi.fit[1, ], m.MSDi.fit[4, ], xlab = "MSDi strong selection", ylab = "MSDi no selection", cex.main = 1, cex.lab = 1)
abline(0, 1)
legend("topleft", paste("R^2", round(cor(m.MSDi.fit[1, ], m.MSDi.fit[4, ]), digits = 4)), bty = "n", cex = 0.7)
legend("bottomright", paste("MSE", signif(mean((m.MSDi.fit[1, ] - m.MSDi.fit[4, ])^2), digits = 2)), bty = "n", cex = 0.7)
points(m.MSDi.fit[1, contacts.active],m.MSDi.fit[4, contacts.active], col = "yellow")
points(m.MSDi.fit[1, gaps],m.MSDi.fit[4, gaps], col = "red")
points(m.MSDi.fit[1, active],m.MSDi.fit[4, active], col = "green")
points(m.MSDi.fit[1, heme],m.MSDi.fit[4, heme], col = "blue")

plot(m.MSDi.fit[2, ], m.MSDi.fit[3, ], xlab = "MSDi medium selection", ylab = "MSDi weak selection", cex.main = 1, cex.lab = 1)
abline(0, 1)
legend("topleft", paste("R^2", round(cor(m.MSDi.fit[2, ], m.MSDi.fit[3, ]), digits = 4)), bty = "n", cex = 0.7)
legend("bottomright", paste("MSE", signif(mean((m.MSDi.fit[2, ] - m.MSDi.fit[3, ])^2), digits = 2)), bty = "n", cex = 0.7)
points(m.MSDi.fit[2, contacts.active],m.MSDi.fit[3, contacts.active], col = "yellow")
points(m.MSDi.fit[2, gaps],m.MSDi.fit[3, gaps], col = "red")
points(m.MSDi.fit[2, active],m.MSDi.fit[3, active], col = "green")
points(m.MSDi.fit[2, heme],m.MSDi.fit[3, heme], col = "blue")

plot(m.MSDi.fit[2, ], m.MSDi.fit[4, ], xlab = "MSDi medium selection", ylab = "MSDi no selection", cex.main = 1, cex.lab = 1)
abline(0, 1)
legend("topleft", paste("R^2", round(cor(m.MSDi.fit[2, ], m.MSDi.fit[4, ]), digits = 4)), bty = "n", cex = 0.7)
legend("bottomright", paste("MSE", signif(mean((m.MSDi.fit[2, ] - m.MSDi.fit[4, ])^2), digits = 2)), bty = "n", cex = 0.7)
points(m.MSDi.fit[2, contacts.active],m.MSDi.fit[4, contacts.active], col = "yellow")
points(m.MSDi.fit[2, gaps],m.MSDi.fit[4, gaps], col = "red")
points(m.MSDi.fit[2, active],m.MSDi.fit[4, active], col = "green")
points(m.MSDi.fit[2, heme],m.MSDi.fit[4, heme], col = "blue")

plot(m.MSDi.fit[3, ], m.MSDi.fit[4, ], xlab = "MSDi weak selection", ylab = "MSDi no selection", cex.main = 1, cex.lab = 1)
abline(0, 1)
legend("topleft", paste("R^2", round(cor(m.MSDi.fit[3, ], m.MSDi.fit[4, ]), digits = 4)), bty = "n", cex = 0.7)
legend("bottomright", paste("MSE", signif(mean((m.MSDi.fit[3, ] - m.MSDi.fit[4, ])^2), digits = 2)), bty = "n", cex = 0.7)
points(m.MSDi.fit[3, contacts.active],m.MSDi.fit[4, contacts.active], col = "yellow")
points(m.MSDi.fit[3, gaps],m.MSDi.fit[4, gaps], col = "red")
points(m.MSDi.fit[3, active],m.MSDi.fit[4, active], col = "green")
points(m.MSDi.fit[3, heme],m.MSDi.fit[4, heme], col = "blue")

```

*Rojo:* Gaps. 
*Verde:* Sitio activo.
*Amarillo:* Sitios en contacto con el sitio activo.
*Azul:* Hemo.
*Negro:* Otros sitios.

### Pn y Qn
Las distribuciones de *Pn* y *Qn* de los conjuntos son las siguientes:

```{r}
layout(matrix(1:4, 2, 2, byrow = T))

Pn.exp = m.mean.exp.Pn[1, 1:100]
Pn.theo = m.mean.theo.Pn.group[1, 1:100]
Pn.exp.sd = m.exp.Pn.sd[1, 1:100]

data.Pn = data.frame("Pn.exp" = Pn.exp, "Pn.theo" = Pn.theo, "modes" = seq(1:length(Pn.exp)), "Pn.exp.sd" = Pn.exp.sd)
ggplot(data = data.Pn, aes(x = modes)) + 
  geom_point(aes(y = Pn.exp, colour = "Pn.exp")) + 
  geom_line(aes(y = Pn.theo, colour = "Pn.theo"), col = "black") +
  ylab("Pn strong selecion") + 
  geom_errorbar(aes(y = Pn.exp, ymin = Pn.exp - Pn.exp.sd, ymax = Pn.exp + Pn.exp.sd), width = 0, col = "red") +
geom_smooth(aes(y = Pn.exp), colour = "red", span = 0.4)

Pn.exp = m.mean.exp.Pn[2, 1:100]
Pn.theo = m.mean.theo.Pn.group[2, 1:100]
Pn.exp.sd = m.exp.Pn.sd[2, 1:100]

data.Pn = data.frame("Pn.exp" = Pn.exp, "Pn.theo" = Pn.theo, "modes" = seq(1:length(Pn.exp)), "Pn.exp.sd" = Pn.exp.sd)
ggplot(data = data.Pn, aes(x = modes)) + 
  geom_point(aes(y = Pn.exp, colour = "Pn.exp")) + 
  geom_line(aes(y = Pn.theo, colour = "Pn.theo"), col = "black") +
  ylab("Pn medium selecion") + 
  geom_errorbar(aes(y = Pn.exp, ymin = Pn.exp - Pn.exp.sd, ymax = Pn.exp + Pn.exp.sd), width = 0, col = "red") +
geom_smooth(aes(y = Pn.exp), colour = "red", span = 0.4)

Pn.exp = m.mean.exp.Pn[3, 1:100]
Pn.theo = m.mean.theo.Pn.group[3, 1:100]
Pn.exp.sd = m.exp.Pn.sd[3, 1:100]

data.Pn = data.frame("Pn.exp" = Pn.exp, "Pn.theo" = Pn.theo, "modes" = seq(1:length(Pn.exp)), "Pn.exp.sd" = Pn.exp.sd)
ggplot(data = data.Pn, aes(x = modes)) + 
  geom_point(aes(y = Pn.exp, colour = "Pn.exp")) + 
  geom_line(aes(y = Pn.theo, colour = "Pn.theo"), col = "black") +
  ylab("Pn weak selecion") + 
  geom_errorbar(aes(y = Pn.exp, ymin = Pn.exp - Pn.exp.sd, ymax = Pn.exp + Pn.exp.sd), width = 0, col = "red") +
  geom_smooth(aes(y = Pn.exp), colour = "red", span = 0.4)

Pn.exp = m.mean.exp.Pn[4, 1:100]
Pn.theo = m.mean.theo.Pn.group[4, 1:100]
Pn.exp.sd = m.exp.Pn.sd[4, 1:100]

data.Pn = data.frame("Pn.exp" = Pn.exp, "Pn.theo" = Pn.theo, "modes" = seq(1:length(Pn.exp)), "Pn.exp.sd" = Pn.exp.sd)
ggplot(data = data.Pn, aes(x = modes)) + 
  geom_point(aes(y = Pn.exp, colour = "Pn.exp")) + 
  geom_line(aes(y = Pn.theo, colour = "Pn.theo"), col = "black") +
  ylab("Pn no selecion") + 
  geom_errorbar(aes(y = Pn.exp, ymin = Pn.exp - Pn.exp.sd, ymax = Pn.exp + Pn.exp.sd), width = 0, col = "red") + 
  geom_smooth(aes(y = Pn.exp), colour = "red", span = 0.4)

```

*Linea negra*: Promedio teorico.
*Puntos rojos*: Promedio experimental.
*Barras rojas:* intervalo Sd/sqrt(n.prot)*1.96.
*Liena roja y banda gris:* geom_smooth experimental con span = 0.4

```{r}
layout(matrix(1:2, 1, 2, byrow = T)) 
par(pty = "s")

plot(m.mean.theo.Pn.group[1, ], m.mean.exp.Pn[1, ], xlab = "<Pn> teorico", ylab = "<Pn> experimental", main = "Pn strong selection", xlim = c(0, 0.04), ylim = c(0, 0.04), cex.main = 1, cex.lab = 1)
abline(0, 1)
legend("topleft", paste("R^2", round(m.Pn.R2[1, ], digits = 2)), bty = "n", cex = 0.7)
legend("bottomright", paste("MSE", signif(m.Pn.MSE[1, ], digits = 2)), bty = "n", cex = 0.7)

plot(m.mean.theo.Pn.group[2, ], m.mean.exp.Pn[2, ], xlab = "<Pn> teorico", ylab = "<Pn> experimental", main = "Pn medium selection", xlim = c(0, 0.04), ylim = c(0, 0.04), cex.main = 1, cex.lab = 1)
abline(0, 1)
legend("topleft", paste("R^2", round(m.Pn.R2[2, ], digits = 2)), bty = "n", cex = 0.7)
legend("bottomright", paste("MSE", signif(m.Pn.MSE[2, ], digits = 2)), bty = "n", cex = 0.7)

plot(m.mean.theo.Pn.group[3, ], m.mean.exp.Pn[3, ], xlab = "<Pn> teorico", ylab = "<Pn> experimental", main = "Pn weak selection", xlim = c(0, 0.04), ylim = c(0, 0.04), cex.main = 1, cex.lab = 1)
abline(0, 1)
legend("topleft", paste("R^2", round(m.Pn.R2[3, ], digits = 2)), bty = "n", cex = 0.7)
legend("bottomright", paste("MSE", signif(m.Pn.MSE[3, ], digits = 2)), bty = "n", cex = 0.7)

plot(m.mean.theo.Pn.group[4, ], m.mean.exp.Pn[4, ], xlab = "<Pn> teorico", ylab = "<Pn> experimental", main = "Pn no selection", xlim = c(0, 0.04), ylim = c(0, 0.04), cex.main = 1, cex.lab = 1)
abline(0, 1)
legend("topleft", paste("R^2", round(m.Pn.R2[4, ], digits = 2)), bty = "n", cex = 0.7)
legend("bottomright", paste("MSE", signif(m.Pn.MSE[4, ], digits = 2)), bty = "n", cex = 0.7)

```

### 2016-07-27 FIGURES/create_images_globins.py

@@ -1,0 +1,29 @@
+# importar de Chimera
+import os
+from chimera import runCommand as rc # use 'rc' as shorthand for runCommand
+from chimera import replyobj # for emitting status messages
+
+# change to folder with data files
+os.chdir("C:\Users\Usuario\Desktop\VariabilidadEstructuralProteica\pdbs_globins")
+
+# gather the names of .pdb files in the folder
+file_names = [fn for fn in os.listdir(".") if fn.endswith(".pdb")]
+
+# loop through the files, opening, processing, and closing each in turn
+for fn in file_names:
+	replyobj.status("Processing " + fn) # show what file we're working on
+	rc("open " + fn)
+	rc("preset apply publication 1") # make everything look nice
+	rc("focus")
+	rc("color white")
+        rc("preset apply pub 1")
+	# save image to a file that ends in .png rather than .pdb
+	png_name = fn[:-3] + "png"
+	rc("copy file " + png_name + " supersample 3")
+	rc("close all")
+# uncommenting the line below will cause Chimera to exit when the script is done
+# rc("stop now")
+# note that indentation is significant in Python; the fact that
+# the above command is exdented means that it is executed after
+# the loop completes, whereas the indented commands that 
+# preceded it are executed as part of the loop.

### 2016-07-27 FUNCTIONS/AnalyzeAlignment.R

@@ -1,14 +1,13 @@
+# Description:
+#
 # This function calculates aligned and not aligned sites of two proteins p.ref and p.2 in a 
-# multiple alignment. It does two types of analysis:
-#  - CORE = FALSE: all aligned and not aligned sites of p.ref and p.2.
-#  - CORE = TRUE: aligned and not aligned sites of p.ref and p.2 that are in the 
-# conserved core of the alignment: positions with no gaps in the whole alignemnt.
+# multiple alignment.
 #
 #  Args:
-#      alignment: multiple alignment.
-#      pdbid: pdbidS of proteins in the rows of the alignment.
-#      p.ref: pdbid of the reference protein.
-#      p.2: pdbid of the other protein to analyze.
+#   - alignment: multiple alignment.
+#   - pdbid: pdbidS of proteins in the rows of the alignment.
+#   - p.ref: pdbid of the reference protein.
+#   - p.2: pdbid of the other protein to analyze.
 #
 #  Returns:
 #    n.sites.p.ref: n sites of p.ref.
@@ -20,26 +19,20 @@
 #    not.aligned.p.2.index: not aligned sites of p.2.
 #    n.aligned.mut.p.ref: n aligned but mutated sites of p.ref.
 #    aligned.mut.p.ref.index: aligned but mutated sites of p.ref.
-#    n.core: n core sites.
-#    core.p.ref.index: core sites of p.ref.
-#    core.p.2.index: core sites of p.2.
-#    no.core.p.ref.index: no core sites of p.ref.
-#    no.core.p.2.index: no core sites of p.2.
-#    identity: % sequence identity between p.ref and p.2.
 
 AnalyzeAlignment <- function(alignment, pdbid, p.ref, p.2) {
   
-  # Extract data form the alignment.
+  # Extract data form the alignment
   l.alignment = ncol(alignment)
   n.prot = nrow(alignment)
   alignment.p.ref = alignment[which(grepl(p.ref, pdbid)), ]
   alignment.p.2 = alignment[which(grepl(p.2, pdbid)), ]
 
-  # Get aa indexes in the alignment.
-  p.ref.index = c()
-  p.2.index = c()
+  # Get aa indexes in the alignment
   aa.p.ref = 0
   aa.p.2 = 0
+  p.ref.index = c()
+  p.2.index = c()
   
[…]

### 2016-07-27 FUNCTIONS/AnalyzeExperimentalTheoreticalCM.R

@@ -1,0 +1,234 @@
+# Description:
+#
+# This function analyzes experimental and theoretical proteins calculating measures of structural variability in cartesian 
+# coordinates and projected on the normal modes of a reference protein. 
+# 
+# Usage:
+#
+# AnalyzeExperimentalTheoretical <- function(family, p.ref, chain.p.ref, n.mut.p, R0, rotate = TRUE/FALSE,
+# heme = TRUE/FALSE, K.analysis, data.dir, out.dir, mut.fname.id, analysis.fname.id, tolerance)
+#
+#  Args:
+#    - family: the family of the protein to mutate. It can be "globins", "serinProteases", 
+#    "snakesToxin", "sh3", "fabp", "rrm", "phoslip" or "cys".
+#    - p.ref: the reference protein of the family.
+#    - chain.p.ref: the chain of p.ref in the pdb file obtained from Homstrad.
+#    - n.mut.p: the number of mutants to generate for each member of the family. For example, if the family has 20 
+#    members, the program generates n.mut.p x 20 mutants.
+#    - R0: the cut-off for the ANM ("Anisotropic Network Model") that represents the proteins.
+#    - rotate: it can be "TRUE" or "FALSE". If it is "TRUE", r.p.2 is rotaded in order to minimize RMSD with r.p.ref.
+#    - heme: argument for globins. It can be "TRUE" or "FALSE". If it is "TRUE", the program considers the heme group. 
+#    - K.analysis: It can be "K" or "Keff". For "K" or "Keff", the analysis is based on normal modes of "K" or "Keff"
+#    respectibly.
+#    - data.dir: directory of the data. It must contain the dataset ("data.dir/family_dataset.csv") and the pdb file 
+#    obtained from Homstrad ("data.dir/family_coordinates.csv").
+#    - out.dir: directory of the output. It must contain output files generated with AnalyzeFamily() and GenerateMutants().
+#    The output of this function is also saved in out.dir.
+#    - mut.fname.id: ID of filnames of mutant proteins.
+#    - analysis.fname.id: ID of output filenames.
+#    - tolerance: 0 tolerance.
+#
[…]

### 2016-07-27 FUNCTIONS/CalculateBetas.R

@@ -6,7 +6,7 @@
 # Usage:
 #
 # CalculateBetas(chain.p.ref, fmax, R0, heme = TRUE/FALSE, data.dir, out.dir,
-# betas.fname.id, TOLERANCE)
+# betas.fname.id, tolerance)
 #
 #  Args:
 #    - chain.p.ref: The chain of p.ref in the pdb file obtained from Homstrad.
@@ -16,12 +16,12 @@
 #    - data.dir: Directory of the data. It must contain the pdb file obtained from Homstrad ("data.dir/family_coordinates.csv").
 #    - out.dir: Output directory. It must contain the output generated by the function AnalyzeFamily().
 #    - betas.fname.id: ID for output filenames.
-#    - TOLERANCE: 0 tolerance.
+#    - tolerance: 0 tolerance.
 #
 #  Required libraries:
 #    {Bio3d}
 #
-#  Required function:
+#  Required functions:
 #    ReadCA()
 #    ReadHeme()
 #    CalculateENMK()
@@ -34,21 +34,21 @@ CalculateBetas <- function(chain.p.ref,
                            data.dir,
                            out.dir,
                            betas.fname.id,
-                           TOLERANCE) {
+                           tolerance) {
   
   print("calculating betas...")
   
   ### READ EXPERIMENTAL DATA ###
   
-  # Filenames.
+  # Filenames
   pdbs.fname <- file.path(data.dir, paste(family, "_coordinates.pdb", sep = "")) 
   
-  # Read PDB of p.ref.
+  # Read PDB of p.ref
   pdb = ReadCA(pdbs.fname, chain.p.ref)
   r.p.ref = pdb$xyz.calpha
   n.aa = pdb$n.sites
   
-  # Get heme coordinates, add them to CA´s coordinates and calculate the new number of sites.
+  # Get heme coordinates, add them to CA´s coordinates and calculate the new number of sites
   if (heme == "TRUE") {
     r.heme = ReadHeme(pdbs.fname, chain.p.ref)
     r.p.ref = cbind(r.p.ref, r.heme)
@@ -59,15 +59,15 @@ CalculateBetas <- function(chain.p.ref,
   
   ### CALCULATE ENM OF THE REFERENCE PROTEIN ###
   
-  # Calculate ENM of p.ref.
-  ENMK.p.ref = CalculateENMK(r.p.ref, CalculateKij, R0, TOLERANCE) 
[…]

### 2016-07-27 FUNCTIONS/GenerateMutantsCM.R

@@ -1,0 +1,202 @@
+# Description:
+#
+# This function generates multiple mutants of a given protein using the LF-ENM ("Linearly Forced - Elastic Network Model")
+# and considering additive single mutations. It calculates the probability of acceptance of each single mutation
+# following the "Stress Model" and given value of the parameter "beta". The function accepts each mutation according to the 
+# calculated probability. 
+# The program only mutates CMs, but considers both CAs and CMs.
+# For each protein of the family of the given protein, the program calculates a lineage of simulated mutants with the same
+# % of sequence identity.
+#
+# Usage:
+# 
+# GenerateMutants(family, chain.p.ref, n.mut.p, fmax, R0, beta, heme = TRUE/FALSE, data.dir, out.dir,
+# mut.fname.id, tolerance)
+#
+#  Args:
+#    - family: the family of the protein to mutate. It can be "globins", "serinProteases", 
+#    "snakesToxin", "sh3", "fabp", "rrm", "phoslip" or "cys".
+#    - chain.p.ref: the chain of p.ref in the pdb file obtained from Homstrad.
+#    - n.mut.p: the number of mutants to generate for each member of the family. For example, if the family has 20 
+#    members, the function generates n.mut.p x 20 mutants.
+#    - fmax: It is the maximun value for the forces that model the mutations.
+#    - R0: the cut-off for the ANM ("Anisotropic Network Model") that represents the proteins.
+#    - beta: parameter for the selection following the Stress Model.
+#    - heme: argument for "globins". It can be "TRUE" or "FALSE". If it is "TRUE", the program considers the heme group.
+#    - data.dir: directory of the data. It must contain the pdb file obtained from Homstrad ("data.dir/family_coordinates.csv").
+#    - out.dir: output directory. It must contain the output generated by the function AnalyzeFamily().
+#    - mut.fname.id: ID for output filenames.
+#    - tolerance: 0 tolerance.
+#
+#  Required libraries:
+#    {Bio3d}
+#
+#  Required function:
+#    ReadCA()
+#    ReadHeme()
+#    CalculateSideChainCM()
+#    CalculateENMK()
+#    CalculateKij()
[…]

### 2016-07-27 MainProgramCM.R

@@ -1,0 +1,168 @@
+# Description:
+#
+# This is the main program of the project. The program simulates multiple mutants of a given protein using the "Linearly Forced - 
+# Elastic Network Model" (LF-ENM) with different selection regimens according to the "Stress Model". The program also
+# analyzes the multiple alignment of the family to which the protein belongs and calculates measures 
+# of variabilty of theoretical and experimental data.
+#
+# To run the program it is necessary to previously fill the input ("input_MainProgram.csv") with the following information:
+#
+#    - family: The family of the protein to mutate. It can be "globins", "serinProteases", 
+#    "snakesToxin", "sh3", "fabp", "rrm", "phoslip" or "cys".
+#    - p.ref: The pdb code (pdbid) of the protein to mutate (example: "1a6m"). The protein must be a member of
+#    the selected family. This pdbid must not be included in the dataset ("DATA/family_dataset.csv").
+#    - chain.p.ref: The chain of p.ref in the pdb file obtained from Homstrad.
+#    - n.mut.p: The number of mutants to generate for each member of the family. For example, if the family has 20 
+#    members, the program generates n.mut.p x 20 mutants.
+#    - fmax: Argument for "LFENM". It is the maximun value for the forces that model the mutations. 
+#    - R0: the Cut-off for the "ANM" (Anisotropic Network Model) that represents the proteins.
+#    - rotate: It can be "TRUE" or "FALSE". If it is "TRUE", r.p.2 is rotated in order to minimize RMSD with r.p.ref.
+#    - heme: Argument for "globins". It can be "TRUE" or "FALSE". If it is "TRUE", the program considers the heme group.
+#    - calculate.betas: It can be "TRUE" or "FALSE". If it is "TRUE", the program calculates betas of the "Stress Model".
+#    - analyze.family: It can be "TRUE" or "FALSE". If it is "TRUE", the program analyzes the family.
+#    - generate.mutants: It can be "TRUE" or "FALSE". If it is "TRUE", the program generates new mutants.
+#    - K.analysis: It can be "K" or "Keff". For "K" or "Keff", the analysis is based on normal modes of "K" or "Keff"
+#    respectibly.
+
+# Remove objects from the workspace
+rm(list = ls())
+
+# Load packages
[…]

### 2016-07-27 other_programs/min.da.CM.R

@@ -1,0 +1,43 @@
+# Filenames
+pdb.fname <- file.path(data.dir, paste(p.ref, ".pdb", sep = "")) 
+
+r.CM.p.ref = CalculateSideChainCM(pdb.fname, chain.p.ref)
+r.ca.p.ref = ReadCA(pdb.fname, chain.p.ref)$xyz
+
+# Get heme coordinates, add them to CM´s coordinates and calculate the new number of sites
+r.heme = ReadHeme(pdb.fname, chain.p.ref)
+r.CM.p.ref = cbind(r.CM.p.ref, r.heme)
+r.ca.p.ref = cbind(r.ca.p.ref, r.heme)
+n.sites = ncol(r.CM.p.ref)
+
+# Active sites
+active = c(28, 29, 32, 64, 68, 93, 107, 152, 153, 154, 155, 156)
+
+# Calculate distance of each center of mass 
+m.da.CM = matrix(nrow = n.sites, ncol = length(active))
+m.da.ca = matrix(nrow = n.sites, ncol = length(active))
+
+for (i in (active)) {
+  print(i)
+  for (j in (1:n.sites)) {
+    m.da.CM[j, which(active == i)] = sqrt(sum((r.CM.p.ref[, j] - r.CM.p.ref[, i]) ^ 2))
+    m.da.ca[j, which(active == i)] = sqrt(sum((r.ca.p.ref[, j] - r.ca.p.ref[, i]) ^ 2))
+  }
+}
+
+# Calculate the minimum distance
+m.min.da.CM = matrix(nrow = n.sites, ncol = 1)
+m.min.da.ca = matrix(nrow = n.sites, ncol = 1)
+
+for (i in (1:n.sites)) {
+  m.min.da.CM[i, ] = min(m.da.CM[i, ])
+  m.min.da.ca[i, ] = min(m.da.ca[i, ])
+}
+
+data = data.frame("site" = seq(1:156), "min.da.CM" = as.vector(m.min.da.CM), "min.da.ca" = as.vector(m.min.da.ca))
+setwd("C:/Users/Usuario/Desktop/VariabilidadEstructuralProteica")
+out.dir = "OUT/out_subset_CA"
+write.csv(data, file.path(out.dir, "min.da.CM.ca.csv", sep = ""))
+out.dir = "OUT/out_subset_CM"
+write.csv(data, file.path(out.dir, "min.da.CM.ca.csv", sep = ""))
+

### 2016-08-15 OUT/analysis-structure-CA-ANM.Rmd
cambios 15/08/2016

--- 2016-07-27 OUT/analysis-structure-CA.Rmd
@@
 
-setwd("C:/Users/Usuario/Desktop/VariabilidadEstructuralProteica")
+setwd("C:/Users/Usuario/Desktop/VariabilidadEstructuralProteica/OUT")
 
-source("OUT/out_subset_CA/multiplot.R")
-source("OUT/out_subset_CA/my-functions.R")
+source("out_subset_CA_ANM/multiplot.R")
+source("out_subset_CA_ANM/my-functions.R")
 ```
@@
 names(myColors) <- c("exp", "mut", "strong", "mut+sel")
-
-setwd("C:/Users/Usuario/Desktop/VariabilidadEstructuralProteica/OUT")
 
@@
 f999 = 3.3
-data.dir = paste("out_subset_CA", sep = "")
+data.dir = paste("out_subset_CA_ANM", sep = "")
 ```
@@
 rownames(energy.strong) = paste("strong", rownames(energy.strong), sep = "")
+```
+
+```{r calculate MSD}
+MSD.exp = mean(rowMeans(as.matrix(dri2.exp), na.rm = T), na.rm = T) 
+MSD.mut = mean(rowMeans(as.matrix(dri2.mut)))
+MSD.strong = mean(rowMeans(as.matrix(dri2.strong)))
+
+df.MSD = data.frame(MSD.exp = MSD.exp, MSD.mut = MSD.mut, MSD.strong = MSD.strong)
+knitr::kable(df.MSD, digits = 4)
+
 ```

### 2016-08-15 OUT/analysis-structure-CA-pfANM.Rmd
cambios 15/08/2016

--- 2016-08-15 OUT/analysis-structure-CA-ANM.Rmd
@@
 author: "María Laura Marcos, Julian Echave"
-date: "25 de julio de 2016"
+date: "02 de julio de 2016"
 output: html_document
@@
 
-source("out_subset_CA_ANM/multiplot.R")
-source("out_subset_CA_ANM/my-functions.R")
+source("out_subset_CA_pfANM/multiplot.R")
+source("out_subset_CA_pfANM/my-functions.R")
 ```
@@
 family = "globins"
-R0 = 10
-enm = "ANM"
+R0 = "NC"
+enm = "pfANM"
 
-# significance factors
+# Significance factors
 f95 = 1.96
@@
 f999 = 3.3
-data.dir = paste("out_subset_CA_ANM", sep = "")
+data.dir = paste("out_subset_CA_pfANM", sep = "")
 ```
@@
 
-dri2.exp.fname = file.path(data.dir, paste(family, "_R0_10_beta_strong.sel_K.analysis_Keff_out_m.exp.norm.dr.squarei.csv", sep = ""))
-Pn.exp.fname = file.path(data.dir, paste(family,"_R0_10_beta_strong.sel_K.analysis_Keff_out_m.exp.Pn.csv", sep = ""))
-energy.exp.fname = file.path(data.dir, paste(family, "_R0_10_beta_strong.sel_K.analysis_Keff_out_m.exp.va.csv", sep = ""))
+dri2.exp.fname = file.path(data.dir, paste(family, "_R0_NC_beta_no.sel_K.analysis_Keff_out_m.exp.norm.dr.squarei.csv", sep = ""))
+Pn.exp.fname = file.path(data.dir, paste(family,"_R0_NC_beta_no.sel_K.analysis_Keff_out_m.exp.Pn.csv", sep = ""))
+energy.exp.fname = file.path(data.dir, paste(family, "_R0_NC_beta_no.sel_K.analysis_Keff_out_m.exp.va.csv", sep = ""))
 
-dri2.strong.fname = file.path(data.dir, paste(family, "_R0_10_beta_strong.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
-Pn.strong.fname = file.path(data.dir, paste(family, "_R0_10_beta_strong.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
-energy.strong.fname = file.path(data.dir, paste(family, "_R0_10_beta_strong.sel_K.analysis_Keff_out_m.theo.va.csv", sep = ""))
+dri2.strong.fname = file.path(data.dir, paste(family, "_R0_NC_beta_strong.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
+Pn.strong.fname = file.path(data.dir, paste(family, "_R0_NC_beta_strong.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
+energy.strong.fname = file.path(data.dir, paste(family, "_R0_NC_beta_strong.sel_K.analysis_Keff_out_m.theo.va.csv", sep = ""))
 
-dri2.mut.fname = file.path(data.dir,paste(family, "_R0_10_beta_no.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
-Pn.mut.fname = file.path(data.dir, paste(family, "_R0_10_beta_no.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
-energy.mut.fname = file.path(data.dir, paste(family, "_R0_10_beta_no.sel_K.analysis_Keff_out_m.theo.va.csv", sep = ""))
+dri2.mut.fname = file.path(data.dir,paste(family, "_R0_NC_beta_no.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
+Pn.mut.fname = file.path(data.dir, paste(family, "_R0_NC_beta_no.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
+energy.mut.fname = file.path(data.dir, paste(family, "_R0_NC_beta_no.sel_K.analysis_Keff_out_m.theo.va.csv", sep = ""))
 
@@
 ```{r set_reference_protein}
-## which is the reference protein?
+## Which is the reference protein?
 reference = as.character(read.table(reference.fname, header = F)[1, 1])
@@
 
-## read site information of reference protein
+## Read site information of reference protein
 site.info = read.csv(site.info.fname, header = T, sep = ";")
@@
 ```{r read_experimental_data}
-# read experimental data
+# Read experimental data
 dri2.exp = read.csv(dri2.exp.fname, header = T)
@@
 knitr::kable(df.MSD, digits = 4)
-
 ```
@@
 
+##
+
 #d$dataset = factor(d$dataset, levels = c("exp", "mut", "strong"))
@@
 p.facet
+
 #p + theme(legend.position = "bottom", legend.title = element_blank())
@@
 })
+
+##
 
@@
     labs(x = "mode energy", y = "structural divergence") +
-    coord_cartesian(xlim = c(0,2.5)) +
+    coord_cartesian(xlim = c(0,0.5)) +
     scale_colour_manual(name = NULL, values = myColors) + 
@@
     scale_fill_manual(name=NULL,values=myColors)+
-    coord_cartesian(xlim=c(0,1))
+    coord_cartesian(xlim=c(0,0.5))
 

### 2016-08-15 OUT/analysis-structure-CM-ANM.Rmd
cambios 15/08/2016

--- 2016-08-15 OUT/analysis-structure-CA-ANM.Rmd
@@
 
-source("out_subset_CA_ANM/multiplot.R")
-source("out_subset_CA_ANM/my-functions.R")
+source("out_subset_CM_ANM/multiplot.R")
+source("out_subset_CM_ANM/my-functions.R")
 ```
@@
 f999 = 3.3
-data.dir = paste("out_subset_CA_ANM", sep = "")
+data.dir = paste("out_subset_CM_ANM", sep = "")
 ```
@@
     labs(x = "mode energy", y = "structural divergence") +
-    coord_cartesian(xlim = c(0,2.5)) +
+    coord_cartesian(xlim = c(0,10)) +
     scale_colour_manual(name = NULL, values = myColors) + 
@@
     scale_fill_manual(name=NULL,values=myColors)+
-    coord_cartesian(xlim=c(0,1))
+    coord_cartesian(xlim=c(0,10))
 

### 2016-08-15 OUT/analysis-structure-CM-pfANM.Rmd
cambios 15/08/2016

--- 2016-08-15 OUT/analysis-structure-CA-pfANM.Rmd
@@
 
-source("out_subset_CA_pfANM/multiplot.R")
-source("out_subset_CA_pfANM/my-functions.R")
+source("out_subset_CM_pfANM/multiplot.R")
+source("out_subset_CM_pfANM/my-functions.R")
 ```
@@
 f999 = 3.3
-data.dir = paste("out_subset_CA_pfANM", sep = "")
+data.dir = paste("out_subset_CM_pfANM", sep = "")
 ```
@@
 knitr::kable(df.MSD, digits = 4)
+
 ```

### 2016-08-15 FUNCTIONS/AnalyzeExperimentalTheoretical.R

@@ -128,9 +128,13 @@ AnalyzeExperimentalTheoretical <- function(family,
   ### EXPERIMENTAL ###
   
   # Read pdb of exp.p.ref
-  exp.pdb.p.ref = ReadCA(pdbs.fname, chain.p.ref)
-  exp.r.p.ref = exp.pdb.p.ref$xyz.calpha
-  n.aa.p.ref = exp.pdb.p.ref$n.sites
+  exp.r.p.ref = theo.r.p.ref
+  
+  if(heme == "TRUE") {
+    n.aa.p.ref = n.sites.p.ref - 5 
+  } else {
+    n.aa.p.ref = n.sites.p.ref
+  }
   
   # Read indexes files
   m.n.aligned = read.csv(m.n.aligned.fname)
@@ -166,11 +170,6 @@ AnalyzeExperimentalTheoretical <- function(family,
     
     # Calculate heme coordinates, add them to CA´s coordinates and calculate the number of sites and not aligned indexes
     if (heme == "TRUE") {
-      if (P == 1) {
-        exp.r.heme.p.ref = ReadHeme(pdbs.fname, chain.p.ref)
-        exp.r.p.ref = cbind(exp.r.p.ref, exp.r.heme.p.ref)
-        n.sites.p.ref = ncol(exp.r.p.ref)
-      }
       exp.r.heme.p.2 = ReadHeme(pdbs.fname, chain.p.2)
       exp.r.p.2 = cbind(exp.r.p.2, exp.r.heme.p.2)
       exp.n.sites.p.2 = ncol(exp.r.p.2)
@@ -179,7 +178,7 @@ AnalyzeExperimentalTheoretical <- function(family,
       aligned.p.2.index <- c(aligned.p.2.index, t(seq((exp.n.aa.p.2 + 1), exp.n.sites.p.2)))
     }
     
-    # Calculate measures of variavility
+    # Calculate measures of variability
     exp.variability = CalculateVariability(as.vector(exp.r.p.ref), 
                                            as.vector(exp.r.p.2), 
                                            aligned.p.ref.index, 
@@ -202,7 +201,6 @@ AnalyzeExperimentalTheoretical <- function(family,
     m.exp.norm.dr.squarei[P, ] = m.exp.dr.squarei[P, ]/ mean(m.exp.dr.squarei[P, ], na.rm = T)
     
[…]

### 2016-08-15 FUNCTIONS/CalculateENMKeff.R

@@ -1,106 +1,113 @@
 # This function calculates K effective of r, its eigenvalues and eigenvectors.
 #
 #  Args:
-#    r: 3 x nsites matrix containing the equilibrium coordinates of each site.
-#    aligned.index: aligned sites
+#    r: 3 x n.sites matrix containing the equilibrium coordinates of each site.
+#    aligned.index: aligned sites.
 #    not.aligned.index: not aligned sites.
 #    R0: cut-off for ANM.
-#    TOLERANCE: 0 tolerance.
+#    tolerance: 0 tolerance.
 #
 #  Requires:
 #    CalculateENMK
 #
 #  Returns:
-#    KEFF: 3*naligned x 3*naligned KEFF matrix.
-#    va: eigenvalues > TOLERANCE of KEFF.
-#    ve: eigenvectors > TOLERANCE of KEFF.
+#    KEFF: 3 * n.aligned x 3 * n.aligned KEFF matrix.
+#    va: ordered eigenvalues > tolerance of KEFF.
+#    ve: ordered eigenvectors > tolerance of KEFF.
 
-CalculateENMKeff <- function(r, aligned.index, not.aligned.index, R0, TOLERANCE, K.analysis) {
+CalculateENMKeff <- function(r, 
+                             aligned.index, 
+                             not.aligned.index, 
+                             R0, 
+                             tolerance, 
+                             K.analysis) {
   
-  naligned = length(aligned.index)
+  n.aligned = length(aligned.index)
   n.not.aligned = length(not.aligned.index)
-  nsites = ncol(r)
+  n.sites = ncol(r)
   
-  # Bind aligned and not aligned index.
-  aligned.not.aligned.index <- c(aligned.index, not.aligned.index)
+  # Bind aligned and not aligned index
+  aligned.not.aligned.index = c(aligned.index, not.aligned.index)
   
-  # Calculate K.
-  ENMK = CalculateENMK(r, CalculateKij, R0, TOLERANCE)
+  # Calculate K
+  ENMK = CalculateENMK(r, CalculateKij, R0, tolerance)
   K = ENMK$K
   
-  # K.analysis = "K".
+  # K.analysis = "K"
[…]

### 2016-08-15 FUNCTIONS/GenerateMutantsCM.R

@@ -84,6 +84,10 @@ GenerateMutantsCM <- function(family,
   # Bind CA and CM coorrdinates
   r.p.ref = cbind(r.ca.p.ref, r.CM.p.ref)
   n.sites.tot = ncol(r.p.ref)
+
+  # Get the minimun sequence identity 
+  identity = min(m.identity)
+  n.sites.mut = as.integer((100 - (identity)) * n.aa / 100)
   
   ### CALCULATE ENM OF THE REFERENCE PROTEIN ###
   
@@ -107,12 +111,8 @@ GenerateMutantsCM <- function(family,
   # Sart a counter for simulated proteins
   run = 0
   
-  # Start a loop for each protein of the family to crate a lineage
+  # Start a loop for each protein of the family
   for (P in (1:n.prot)) {
-    
-    # Get de sequence identity and the number of mutated sites of "p.ref" for "P"
-    identity = m.identity[P]
-    n.sites.mut = as.integer((100 - (identity)) * n.aa / 100)
       
     # Start a loop to generate "n.mut.p" mutants for P
     for(mut in seq(1:n.mut.p)) {

### 2016-08-15 MainProgramCM.R

@@ -31,11 +31,15 @@ rm(list = ls())
 library(bio3d) 
 library(seqinr) 
 
+# Set Elastic Network Model: "ANM" or "pfANM"
+model <- "pfANM"
+
 # Data dir
 data.dir <- "DATA"
 
 # Output dir
-out.dir <- "OUT/out_subset_CM"
+if (model == "ANM") out.dir <- "OUT/out_subset_CM_ANM"
+if (model == "pfANM") out.dir <- "OUT/out_subset_CM_pfANM"
 
 # General parameters
 tolerance = 1e-10
@@ -48,13 +52,22 @@ GenerateMutantsCM.fname <- "FUNCTIONS/GenerateMutantsCM.R"
 ReadFasta.fname <- "FUNCTIONS/ReadFasta.R"
 ReadCA.fname <- "FUNCTIONS/ReadCA.R"
 ReadHeme.fname <- "FUNCTIONS/ReadHeme.R"
-CalculateBetasCM.fname <- "FUNCTIONS/CalculateBetasCM.R"
 CalculateSideChainCM.fname <- "FUNCTIONS/CalculateSideChainCM.R"
 CalculateENMKeff.fname <- "FUNCTIONS/CalculateENMKeff.R"
 CalculateENMK.fname <- "FUNCTIONS/CalculateENMK.R"
-CalculateKij.fname <- "FUNCTIONS/CalculateKij.R"
-CalculateForce.fname <- "FUNCTIONS/CalculateForce.R"
 CalculateVariability.fname <- "FUNCTIONS/CalculateVariability.R"
+
+if (model == "ANM") {
+  CalculateBetasCM.fname <- "FUNCTIONS/CalculateBetasCM.R"
+  CalculateKij.fname <- "FUNCTIONS/CalculateKij.R"
+  CalculateForce.fname <- "FUNCTIONS/CalculateForce.R"
+}
+
+if (model == "pfANM") {
+  CalculateBetasCM.fname <- "FUNCTIONS/CalculateBetasCMPFANM.R"
+  CalculateKij.fname <- "FUNCTIONS/CalculateKijPFANM.R"
+  CalculateForce.fname <- "FUNCTIONS/CalculateForcePFANM.R"
+}
 
 # Source functions
 source(AnalyzeExperimentalTheoreticalCM.fname)
@@ -65,12 +78,13 @@ source(ReadFasta.fname)
 source(ReadCA.fname) 
 source(ReadHeme.fname)
 source(CalculateSideChainCM.fname)
[…]

### 2016-09-16 OUT/analysis-structure-CA.Rmd
cambios 16/09/2016

@@
 author: "María Laura Marcos, Julian Echave"
-date: "25 de julio de 2016"
+date: "10 de septiembre de 2016"
 output: html_document
@@
 
-setwd("C:/Users/Usuario/Desktop/VariabilidadEstructuralProteica")
-
-source("OUT/out_subset_CA/multiplot.R")
-source("OUT/out_subset_CA/my-functions.R")
+source(file.path(data.dir, "multiplot.R"))
+source(file.path(data.dir, "my-functions.R")) 
 ```
@@
 names(myColors) <- c("exp", "mut", "strong", "mut+sel")
-
-setwd("C:/Users/Usuario/Desktop/VariabilidadEstructuralProteica/OUT")
-
 ```
@@
 ```{r set_run_variables}
-# Set options
-family = "globins"
-R0 = 10
-enm = "ANM"
-
 # significance factors
@@
 f999 = 3.3
-data.dir = paste("out_subset_CA", sep = "")
 ```
@@
 reference.fname = file.path(data.dir, paste(family, "_ref.txt", sep = ""))
-site.info.fname = file.path(data.dir, paste(family, "_out_m.da.csv", sep = ""))
 protein_list.fname = file.path(data.dir, paste(family, "_list.txt", sep = ""))
+site.info.fname = file.path(data.dir, paste(p.ref, "_m.da.csv", sep = ""))
 
@@
 
-##
+m.min.da.CM = read.csv(file.path(data.dir, "min.da.CM.csv", sep = ""))$x[1:151]
 
 z.RSD.exp = d$mean.z.RSD[d$dataset == "exp"]
-z.RSD.strong = d$mean.z.RSD[d$dataset == "mut+sel"]
+z.RSD.strong = d$mean.z.RSD[d$dataset == "strong"]
 z.RSD.mut = d$mean.z.RSD[d$dataset == "mut"]
 
-m.min.da.CM.ca = read.csv(file.path(data.dir, "min.da.CM.ca.csv", sep = ""))[, 2:4]
-
-data.csv = data.frame(m.min.da.CM.ca[1:151, ], "mean.z.RSD.exp" = z.RSD.exp, "mean.z.RSD.strong" = z.RSD.strong, "mean.z.RSD.mut" = z.RSD.mut)
-
-write.csv(data.csv, file.path(data.dir, "data.da.csv", sep = ""))
-
-m.min.da.CM = m.min.da.CM.ca$min.da.CM[1:151]
-
-data.plot = data.frame("d.exp.mut" = z.RSD.mut - z.RSD.exp, "d.exp.strong" = z.RSD.mut - z.RSD.strong, "m.min.da.CM" = m.min.da.CM)
-
-r = round(cor(data.plot$d.exp.mut, data.plot$m.min.da.CM), 2)
-
-ggplot(data.plot, aes(y = d.exp.mut, x = m.min.da.CM)) +
-  geom_point()+
-  geom_smooth(method = "lm") +
-  geom_label(aes(x = 5, y = 2, label = paste("R =", as.character(r)))) +
-    labs(y = "mean.z.RSD.mut - mean.z.RSD.exp", x = "min.da.CM")
-
-r = round(cor(data.plot$d.exp.strong, data.plot$m.min.da.CM), 2)
-
-ggplot(data.plot, aes(y = d.exp.strong, x = m.min.da.CM)) +
-  geom_point()+
-  geom_smooth(method = "lm") +
-  geom_label(aes(x = 5, y = 0.5, label = paste("R =", as.character(r)))) +
-    labs(y = "mean.z.RSD.strong - mean.z.RSD.exp", x = "min.da.CM")
-
-##
-
-m.min.da.ca = m.min.da.CM.ca$min.da.ca[1:151]
-
-data.plot = data.frame("d.exp.mut" = z.RSD.mut - z.RSD.exp, "d.exp.strong" = z.RSD.strong - z.RSD.exp, "m.min.da.ca" = m.min.da.ca)
-
-r = round(cor(data.plot$d.exp.mut, data.plot$m.min.da.ca), 2)
-
-ggplot(data.plot, aes(y = d.exp.mut, x = m.min.da.ca)) +
-  geom_point()+
-  geom_smooth(method = "lm") +
-  geom_label(aes(x = 5, y = 2, label = paste("R =", as.character(r)))) +
-    labs(y = "mean.z.RSD.mut - mean.z.RSD.exp", x = "min.da.ca")
-
-r = round(cor(data.plot$d.exp.strong, data.plot$m.min.da.ca), 2)
-
-ggplot(data.plot, aes(y = d.exp.strong, x = m.min.da.ca)) +
-  geom_point()+
-  geom_smooth(method = "lm") +
-  geom_label(aes(x = 5, y = 2, label = paste("R =", as.character(r)))) +
-    labs(y = "mean.z.RSD.strong - mean.z.RSD.exp", x = "min.da.ca")
+plot(y = z.RSD.exp-z.RSD.strong, x = m.min.da.CM)
+abline(0,0, col = "red")
+plot(y = (z.RSD.exp-z.RSD.mut), x = m.min.da.CM)
+abline(0,0, col = "red")
 

### 2016-09-16 OUT/analysis-structure.Rmd
cambios 16/09/2016

--- 2016-07-27 OUT/analysis-structure-CA.Rmd
@@
 author: "María Laura Marcos, Julian Echave"
-date: "25 de julio de 2016"
 output: html_document
@@
 ```{r set_file_names}
-## Input and pre-processing of data
-# Set up input filenames
+## input and pre-processing of data
+# set up input filenames
 
 reference.fname = file.path(data.dir, paste(family, "_ref.txt", sep = ""))
-site.info.fname = file.path(data.dir, paste(family, "_out_m.da.csv", sep = ""))
 protein_list.fname = file.path(data.dir, paste(family, "_list.txt", sep = ""))
+site.info.fname = file.path(data.dir, paste(p.ref, "_m.da.ca.csv", sep = ""))
 
@@
 ## read site information of reference protein
-site.info = read.csv(site.info.fname, header = T, sep = ";")
+site.info = read.csv(site.info.fname, header = T, sep = ",")[1:151, ]
 
@@
 
-##
+m.min.da.CM = read.csv(file.path(data.dir, paste(p.ref, "_min.da.CM.ca.csv", sep = "")))
 
@@
 
-m.min.da.CM.ca = read.csv(file.path(data.dir, "min.da.CM.ca.csv", sep = ""))[, 2:4]
-
-data.csv = data.frame(m.min.da.CM.ca[1:151, ], "mean.z.RSD.exp" = z.RSD.exp, "mean.z.RSD.strong" = z.RSD.strong, "mean.z.RSD.mut" = z.RSD.mut)
-
-write.csv(data.csv, file.path(data.dir, "data.da.csv", sep = ""))
-
-m.min.da.CM = m.min.da.CM.ca$min.da.CM[1:151]
-
-data.plot = data.frame("d.exp.mut" = z.RSD.mut - z.RSD.exp, "d.exp.strong" = z.RSD.mut - z.RSD.strong, "m.min.da.CM" = m.min.da.CM)
-
-r = round(cor(data.plot$d.exp.mut, data.plot$m.min.da.CM), 2)
-
-ggplot(data.plot, aes(y = d.exp.mut, x = m.min.da.CM)) +
-  geom_point()+
-  geom_smooth(method = "lm") +
-  geom_label(aes(x = 5, y = 2, label = paste("R =", as.character(r)))) +
-    labs(y = "mean.z.RSD.mut - mean.z.RSD.exp", x = "min.da.CM")
-
-r = round(cor(data.plot$d.exp.strong, data.plot$m.min.da.CM), 2)
-
-ggplot(data.plot, aes(y = d.exp.strong, x = m.min.da.CM)) +
-  geom_point()+
-  geom_smooth(method = "lm") +
-  geom_label(aes(x = 5, y = 0.5, label = paste("R =", as.character(r)))) +
-    labs(y = "mean.z.RSD.strong - mean.z.RSD.exp", x = "min.da.CM")
-
-##
-
-m.min.da.ca = m.min.da.CM.ca$min.da.ca[1:151]
-
-data.plot = data.frame("d.exp.mut" = z.RSD.mut - z.RSD.exp, "d.exp.strong" = z.RSD.strong - z.RSD.exp, "m.min.da.ca" = m.min.da.ca)
-
-r = round(cor(data.plot$d.exp.mut, data.plot$m.min.da.ca), 2)
-
-ggplot(data.plot, aes(y = d.exp.mut, x = m.min.da.ca)) +
-  geom_point()+
-  geom_smooth(method = "lm") +
-  geom_label(aes(x = 5, y = 2, label = paste("R =", as.character(r)))) +
-    labs(y = "mean.z.RSD.mut - mean.z.RSD.exp", x = "min.da.ca")
-
-r = round(cor(data.plot$d.exp.strong, data.plot$m.min.da.ca), 2)
-
-ggplot(data.plot, aes(y = d.exp.strong, x = m.min.da.ca)) +
-  geom_point()+
-  geom_smooth(method = "lm") +
-  geom_label(aes(x = 5, y = 2, label = paste("R =", as.character(r)))) +
-    labs(y = "mean.z.RSD.strong - mean.z.RSD.exp", x = "min.da.ca")
+plot(y = z.RSD.exp-z.RSD.strong, x = m.min.da.CM$min.da.ca[1:151])
+plot(y = (z.RSD.exp-z.RSD.mut), x = m.min.da.CM$min.da.CM[1:151])
 
@@
 ggplot(dat, aes(x = site, y = mean.z.RSD, col = dataset)) + geom_line() +
-    geom_text(data = subset(dat, dataset == "exp" & mean.z.RSD < -.5), aes(x = site, y = mean.z.RSD, label = site), nudge_y = -.1, size = 2)
+    geom_text(data = subset(dat, dataset == "exp" & mean.z.RSD < -.5), aes(x = site, y = mean.z.RSD, label = site), nudge_y = -.1, size = 1.8)
 
@@
 
+# Write pdb files for MSDi.
+
+  pdb = ReadCA(reference.pdb.fname, chain.p.ref)$xyz
+
+  mean.exp.z.RSD.pdb <- vec2resno(as.vector(dat.exp$mean.z.RSD), sort(rep(1:ncol(pdb),3)))
+  write.pdb(xyz = c(pdb), b = mean.exp.z.RSD.pdb, file = paste(p.ref, "_exp.pdb", sep = ""))
+
+  mean.mut.z.RSD.pdb <- vec2resno(as.vector(dat.mut$mean.z.RSD), sort(rep(1:ncol(pdb),3)))
+  write.pdb(xyz = c(pdb), b = mean.mut.z.RSD.pdb, file = paste(p.ref, "_mut.pdb", sep = ""))
+
+  mean.strong.z.RSD.pdb <- vec2resno(as.vector(dat.strong$mean.z.RSD), sort(rep(1:ncol(pdb),3)))
+  write.pdb(xyz = c(pdb), b = mean.strong.z.RSD.pdb, file = paste(p.ref, "_strong.pdb", sep = ""))
 ```

### 2016-09-16 other_programs_files/MultipleReportAllBetasGlobins.Rmd
cambios 16/09/2016

--- 2016-07-27 other_programs/MultipleReportAllBetasGlobinsZscore2.Rmd
@@
 data.dir <- "DATA"
-out.dir <- "OUT/out_subset_CM"
+out.dir <- "OUT"
 
 # p.ref.
-n.sites.p.ref = 156
+n.sites.p.ref = read.csv(file.path(out.dir, paste(family, "_out_m.n.sites.p.ref.csv", sep = "")))$V1[1]
 
@@
 
-# Information of sites.
-gaps = c(18, 19, 51, 52, 53, 54, 55, 148, 149, 150, 151)
-active = c(28, 29, 32, 64, 68, 93, 107)
-heme = c(152, 153, 154, 155, 156)
-
   # Start a loop for each beta.
@@
 
+    gaps = c(18, 19, 47, 48, 49, 50, 51, 52, 53, 54, 55, 148, 149, 150, 151)
+    active = c(28, 29, 32, 64, 68, 93, 107)
+
     analysis.fname.id <- paste(family, "_R0_", R0, "_beta_", beta, "_K.analysis_", K.analysis, sep = "")
 
-    # Pn.
     m.exp.Pn = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.exp.Pn.csv", sep = "")))[, 1:100]
-    mean.exp.Pn = colMeans(m.exp.Pn)
-    m.mean.exp.Pn[as.vector(all.betas == beta), 1:length(mean.exp.Pn)] = mean.exp.Pn
     n.prot = nrow(m.exp.Pn)
 
-    # MSDi.
-    m.exp.smooth.norm.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.exp.norm.dr.squarei.csv", sep = "")))
+    mean.exp.Pn = colMeans(m.exp.Pn)
+    exp.Pn.sd = apply(m.exp.Pn, 2, sd, na.rm = T)/sqrt(n.prot) * 1.96
+    m.mean.exp.Pn[as.vector(all.betas == beta), 1:length(mean.exp.Pn)] = mean.exp.Pn
 
-    m.exp.smooth.norm.dr.squarei = m.exp.smooth.norm.dr.squarei[-c(6, 7, 9, 29, 31), ] # Saqué proteínas que Julian no usó
-
-    n.prot = nrow(m.exp.smooth.norm.dr.squarei)
-    exp.smooth.norm.MSDi = colMeans(m.exp.smooth.norm.dr.squarei, na.rm = T)
-    exp.smooth.norm.MSDi.sd = apply(m.exp.smooth.norm.dr.squarei, 2, sd, na.rm = T)/sqrt(no.gaps) * 1.96 # Ver si no hay que hacer sd dp
-
-    exp.smooth.norm.MSDi.sd = exp.smooth.norm.MSDi.sd[!is.na(exp.smooth.norm.MSDi.sd)]
-
-    exp.smooth.norm.MSDi = scale(sqrt(exp.smooth.norm.MSDi))[, 1]
-
-    exp.smooth.norm.MSDi = exp.smooth.norm.MSDi[!is.na(exp.smooth.norm.MSDi)]
+    m.exp.smooth.norm.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.exp.smooth.norm.dr.squarei.csv", sep = "")))
+    no.gaps = colSums(matrix(as.numeric(!is.na(m.exp.smooth.norm.dr.squarei)), nrow = n.prot))
+    exp.smooth.norm.MSDi = colMeans(m.exp.smooth.norm.dr.squarei, na.rm = T )
+    exp.smooth.norm.MSDi.sd = apply(m.exp.smooth.norm.dr.squarei, 2, sd, na.rm = T)/sqrt(no.gaps) * 1.96
 
@@
 
-    # Pn.
     m.theo.Pn = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.Pn.csv", sep = "")))[, 1:100]
+
+    m.theo.smooth.norm.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.smooth.norm.dr.squarei.csv", sep = "")))
+
+    theo.smooth.norm.MSDi = colMeans(m.theo.smooth.norm.dr.squarei, na.rm = T )
 
@@
 
-    # MSDi.
-    m.theo.smooth.norm.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.norm.dr.squarei.csv", sep = "")))
+    fit = lm(exp.smooth.norm.MSDi ~ theo.smooth.norm.MSDi )
+    MSDi.fit = fitted.values(fit)
+    MSDi.R2 = cor(exp.smooth.norm.MSDi[!is.na(exp.smooth.norm.MSDi)], MSDi.fit) ^ 2 
+    MSDi.MSE = mean((MSDi.fit - exp.smooth.norm.MSDi[!is.na(exp.smooth.norm.MSDi)]) ^ 2)
+    exp.smooth.norm.MSDi = exp.smooth.norm.MSDi[!is.na(exp.smooth.norm.MSDi)]
 
-    theo.smooth.norm.MSDi = colMeans(m.theo.smooth.norm.dr.squarei, na.rm = T)
-
-    MSDi.fit = scale(sqrt(theo.smooth.norm.MSDi))[, 1]
-
-    MSDi.fit = MSDi.fit[1:length(exp.smooth.norm.MSDi)]
-
-    ### COMPARE EXPERIMENTAL AND THEORETICAL ###
-    MSDi.R2 = cor(exp.smooth.norm.MSDi, MSDi.fit) ^ 2
-
-    MSDi.MSE = mean((MSDi.fit - exp.smooth.norm.MSDi) ^ 2)
-
-    ### SAVE DATA IN MATRICES ###
-    m.exp.MSDi[as.vector(all.betas == beta), ] = exp.smooth.norm.MSDi
-    m.exp.MSDi.sd[as.vector(all.betas == beta), ] = exp.smooth.norm.MSDi.sd
     m.MSDi.fit[as.vector(all.betas == beta), ] = MSDi.fit
@@
     m.MSDi.MSE[as.vector(all.betas == beta), ] = MSDi.MSE
+    m.exp.MSDi[as.vector(all.betas == beta), ] = exp.smooth.norm.MSDi
+    m.exp.MSDi.sd[as.vector(all.betas == beta), ] = exp.smooth.norm.MSDi.sd[!is.na(exp.smooth.norm.MSDi.sd)]
 
@@
 
-    m.mean.exp.Pn[as.vector(all.betas == beta), 1:(length(mean.exp.Pn))] = mean.exp.Pn
   m.Pn.fit[as.vector(all.betas == beta), 1:(length(Pn.fit))] = Pn.fit
@@
   m.Pn.MSE[as.vector(all.betas == beta), ] = Pn.MSE
+  m.mean.exp.Pn[as.vector(all.betas == beta), 1:(length(mean.exp.Pn))] = mean.exp.Pn
+  m.exp.Pn.sd[as.vector(all.betas == beta), 1:(length(exp.Pn.sd))] = exp.Pn.sd
 
@@
 
-    pdb <- read.pdb(pdbs.fname, ATOM.only = "TRUE")
+  pdb <- read.pdb(pdbs.fname, ATOM.only = T)
   sel <- atom.select(pdb)
@@
   site = as.numeric(pdb$atom[sel$atom, c("resno")])[1:1203]
-    MSDi.fit.pdb <- vec2resno(as.vector(MSDi.fit[1:151]), site)
-    exp.MSDi.pdb <- vec2resno(as.vector(exp.smooth.norm.MSDi[1:151]), site)
+  MSDi.fit.pdb <- vec2resno(as.vector(MSDi.fit), site)
+  exp.MSDi.pdb <- vec2resno(as.vector(exp.smooth.norm.MSDi), site)
   b.factor.fit = b.factor
@@
   write.pdb(pdb = pdb, b = b.factor.exp, file = file.path(out.dir, paste(family, "_", p.ref, "_exp", ".pdb", sep = "")))
+
 }
@@
 
-MSDi.exp = m.exp.MSDi[1, 1:151]
-MSDi.theo = m.MSDi.fit[1, 1:151]
-MSDi.exp.sd = m.exp.MSDi.sd[1, 1:151]
+MSDi.exp = m.exp.MSDi[1, ]
+MSDi.theo = m.MSDi.fit[1, ]
+MSDi.exp.sd = m.exp.MSDi.sd[1, ]
 
@@
   geom_point(aes(y = MSDi.exp, colour = type), size = 1.5) + 
-  ylab("MSDi strong selection")
+  ylab("MSDi strong selection") +
+  scale_color_manual(values=c("green", "yellow", "red", "black"))
 
@@
   geom_point(aes(y = MSDi.exp, colour = type), size = 1.5) + 
-  ylab("MSDi medium selection")
+  ylab("MSDi medium selection") +
+  scale_color_manual(values=c("green", "yellow", "red", "black"))
 
@@
   geom_point(aes(y = MSDi.exp, colour = type), size = 1.5) + 
-  ylab("MSDi weak selection")
+  ylab("MSDi weak selection") +
+  scale_color_manual(values=c("green", "yellow", "red", "black"))
 
@@
   ylab("MSDi no selection") +
+  scale_color_manual(values=c("green", "yellow", "red", "black"))
+
 ```

### 2016-09-16 FUNCTIONS/AnalyzeAlignment.R

@@ -1,51 +1,52 @@
 # Description:
+# This function compares two proteins, "p.ref" and "p.2", in a multiple sequence alignment
 #
-# This function calculates aligned and not aligned sites of two proteins p.ref and p.2 in a 
-# multiple alignment.
+# Usage:
+# AnalyzeAlignment(alignment, pdbid, p.ref, p.2)
 #
 #  Args:
-#   - alignment: multiple alignment.
-#   - pdbid: pdbidS of proteins in the rows of the alignment.
-#   - p.ref: pdbid of the reference protein.
-#   - p.2: pdbid of the other protein to analyze.
+#   - alignment: multiple sequence alignment in FASTA format as obtained with ReadFasta()
+#   - pdbid: ordered pdbids of the proteins in the rows of the alignment
+#   - p.ref: pdbid of the reference protein
+#   - p.2: pdbid of the protein to compare with "p.ref"
 #
 #  Returns:
-#    n.sites.p.ref: n sites of p.ref.
-#    n.sites.p.2: n sites of p.2.
-#    n.aligned: n aligned sites of p.ref.
-#    aligned.p.ref.index: aligned sites of p.ref.
-#    aligned.p.2.index: aligned sites of p.2.
-#    not.aligned.p.ref.index: not aligned sites of p.ref.
-#    not.aligned.p.2.index: not aligned sites of p.2.
-#    n.aligned.mut.p.ref: n aligned but mutated sites of p.ref.
-#    aligned.mut.p.ref.index: aligned but mutated sites of p.ref.
+#    n.sites.p.ref: n sites of p.ref
+#    n.sites.p.2: n sites of p.2
+#    n.aligned: n aligned sites of p.ref
+#    aligned.p.ref.index: aligned sites of p.ref
+#    aligned.p.2.index: aligned sites of p.2
+#    not.aligned.p.ref.index: not aligned sites of p.ref
+#    not.aligned.p.2.index: not aligned sites of p.2
+#    n.aligned.mut.p.ref: n aligned but mutated sites of p.ref
+#    aligned.mut.p.ref.index: aligned but mutated sites of p.ref
 
 AnalyzeAlignment <- function(alignment, pdbid, p.ref, p.2) {
   
-  # Extract data form the alignment
+  # extract data form the multiple sequence alignment
   l.alignment = ncol(alignment)
   n.prot = nrow(alignment)
[…]

### 2016-09-16 MainReport.R

@@ -1,0 +1,36 @@
+setwd("C:/Users/Usuario/Desktop/VariabilidadEstructuralProteica")
+
+# load libraries
+library(knitr)
+library(markdown)
+
+# set output directory
+data.dir <- "OUT/out_subset_CA_ANM"
+
+# set options
+enm = "ANM"
+
+# read input
+input.fname <- "input_MainReport.csv"
+input <- read.csv(input.fname)
+
+# satart a loop for each family
+for (f in (1:nrow(input))) { 
+  print(f)
+  family <- as.character(input$family)[f]
+  R0 = input$R0[f]
+  p.ref <- as.character(input$p.ref)[f]
+  chain.p.ref <- as.character(input$chain.p.ref)[f]
+
+  # generate reports
+  setwd("C:/Users/Usuario/Desktop/VariabilidadEstructuralProteica/OUT")
+  data.dir <- paste("out_subset_CA_ANM", sep = "")
+  
+  rmarkdown::render('analysis-structure.Rmd', 
+                      output_file =  paste("report_structure_CA", family, "_", enm, "_R0_", R0, ".html", sep = ''))
+}
+
+  data.dir <- paste("out_subset_CM_ANM", sep = "")
+  rmarkdown::render('analysis-structure.Rmd', 
+                    output_file =  paste("report_structure_CM", family, "_", enm, "_R0_", R0, ".html", sep = ''))
+}

### 2016-09-16 OUT/min.da.CM.ca.R

@@ -1,0 +1,80 @@
+# This program calculates distances between functional sites of proteins and the other sites of the protein.
+# It calculates distances between CAs and CMs.
+
+# read input
+input.fname <- file.path("input_MainProgram.csv")
+input <- read.csv(input.fname)
+
+# data dir
+data.dir <- "DATA"
+
+# start a loop to analyze each family
+for (f in (1:nrow(input))) { 
+  family <- as.character(input$family)[f]
+  p.ref <- as.character(input$p.ref)[f]
+  chain.p.ref <- as.character(input$chain.p.ref)[f]
+  heme <- input$heme[f]
+  
+  # read functional sites
+  active = read.csv(file.path(data.dir, paste(p.ref, "_functionalSites.csv", sep = "")), sep = ";")$functional.sites
+  active = active[!is.na(active)]
+  
+  # pdb filename
+  pdb.fname <- file.path(data.dir, paste(p.ref, ".pdb", sep = ""))
+
+  # get coordinates of p.ref
+  r.ca.p.ref = ReadCA(pdb.fname, chain.p.ref)$xyz
+  r.CM.p.ref = CalculateSideChainCM(pdb.fname, chain.p.ref)
+
+  if (heme == "TRUE") {
+    r.heme = ReadHeme(pdb.fname, chain.p.ref)
+    r.ca.p.ref = cbind(r.ca.p.ref, r.heme)
+    r.CM.p.ref = cbind(r.CM.p.ref, r.heme)
+  }
+  
+  # calculate the number of sites
+  n.sites = ncol(r.ca.p.ref)
+
+  # calculate the distances between each site and each functional site (CA or CM)
+  m.da.ca = matrix(nrow = n.sites, ncol = length(active))
+  m.da.CM = matrix(nrow = n.sites, ncol = length(active))
+  
+  for (i in (active)) {
+    print(i)
+    for (j in (1:n.sites)) {
+      m.da.ca[j, which(active == i)] = sqrt(sum((r.ca.p.ref[, j] - r.ca.p.ref[, i]) ^ 2))
+      m.da.CM[j, which(active == i)] = sqrt(sum((r.CM.p.ref[, j] - r.CM.p.ref[, i]) ^ 2))
+    }
+  }
+  
+  m.da.ca = cbind(seq(1:n.sites), m.da.ca)
[…]

### 2016-09-16 other_programs_files/alignments.R

@@ -1,0 +1,53 @@
+# Download "muscle"
+source("https://bioconductor.org/biocLite.R")
+biocLite("muscle")
+
+# Library
+library(muscle)
+
+# Get sequences
+alignment.p.ref = alignment.p.ref[alignment.p.ref != "-"]
+alignment.p.2 = alignment.p.2[alignment.p.2 != "-"]
+
+# Create a string set
+AAstring <- AAStringSet(c("VLSEGEWQLVLHVWAKVEADVAGHGQDILIRLFKSHPE
+              TLEKFDRFKHLKTEAEMKASEDLKKHGVTVLTALGAILKKKGHH
+              EAELKPLAQSHATKHKIPIKYLEFISEAIIHVLHSRHPGDFGADAQG
+              AMNKALELFRKDIAAKYKELGY"
+              , "GLSDGEWHLVLNVWGKVETDLAGHGQEVLIRLFKSHPE
+TLEKFDKFK-HLKSEDDMRRSEDLRKHGNTVLTALGGILKKKGHH
+              EAELKPLAQSHATKHKIPIKYLEFISEAIIHVLHSKHPAEFGADAQA
+              AMKKALELFRNDIAAKYKELGFHG
+              "))
+
+# Align
+align = muscle(AAstring)
+align.p.ref <- as.vector(align@unmasked[1])
+align.p.2 <- as.vector(align@unmasked[2])
+
+alignment.p.ref <- strsplit(align.p.ref, split = "")[[1]]
+alignment.p.2 <- strsplit(align.p.2, split = "")[[1]]
+
+# Run AnalyzeFamily.
+
+# Calculate 3N indexes
+aligned.p.ref.index.3N = sort(c(aligned.p.ref.index * 3, aligned.p.ref.index * 3 - 2, aligned.p.ref.index * 3 - 1))
+aligned.p.2.index.3N = sort(c(aligned.p.2.index * 3, aligned.p.2.index * 3 - 2, aligned.p.2.index * 3 - 1))
+
+# Structures
+pdb.p.ref <- read.pdb(get.pdb("1a6m"))
+pdb.p.2 <- read.pdb(get.pdb("1mbs"))
+
+p.ref.inds <- atom.select(pdb.p.ref, chain = "A", elety = "CA")
+p.2.inds <- atom.select(pdb.p.2, chain = "A", elety = "CA")
+
[…]

### 2016-09-29 OUT/analysis-structure.Rmd
cambios 29-09-2016

@@
 ```{r load_libraries}
+# Load packages
 library(ggplot2)
@@
 
+# Source functions
 source(file.path(data.dir, "multiplot.R"))
@@
 ```
+
 # Introduction
-We study the evolutionary divergence of proteins using the LFENM and compare with experimental data.
+We study the evolutionary divergence of proteins using the LF-ENM and comparing simulated mutants with experimental data.
 
@@
 ```{r set_file_names}
-## input and pre-processing of data
-# set up input filenames
+# input and pre-processing of data
 
+## set up input filenames
 reference.fname = file.path(data.dir, paste(family, "_ref.txt", sep = ""))
@@
 
-dri2.exp.fname = file.path(data.dir, paste(family, "_R0_10_beta_strong.sel_K.analysis_Keff_out_m.exp.norm.dr.squarei.csv", sep = ""))
-Pn.exp.fname = file.path(data.dir, paste(family,"_R0_10_beta_strong.sel_K.analysis_Keff_out_m.exp.Pn.csv", sep = ""))
-energy.exp.fname = file.path(data.dir, paste(family, "_R0_10_beta_strong.sel_K.analysis_Keff_out_m.exp.va.csv", sep = ""))
+dri2.exp.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_strong.sel_K.analysis_Keff_out_m.exp.norm.dr.squarei.csv", sep = ""))
+Pn.exp.fname = file.path(data.dir, paste(family,"_R0_", R0, "_beta_strong.sel_K.analysis_Keff_out_m.exp.Pn.csv", sep = ""))
+energy.exp.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_strong.sel_K.analysis_Keff_out_m.exp.va.csv", sep = ""))
 
-dri2.strong.fname = file.path(data.dir, paste(family, "_R0_10_beta_strong.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
-Pn.strong.fname = file.path(data.dir, paste(family, "_R0_10_beta_strong.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
-energy.strong.fname = file.path(data.dir, paste(family, "_R0_10_beta_strong.sel_K.analysis_Keff_out_m.theo.va.csv", sep = ""))
+dri2.strong.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_strong.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
+Pn.strong.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_strong.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
+energy.strong.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_strong.sel_K.analysis_Keff_out_m.theo.va.csv", sep = ""))
 
-dri2.mut.fname = file.path(data.dir,paste(family, "_R0_10_beta_no.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
-Pn.mut.fname = file.path(data.dir, paste(family, "_R0_10_beta_no.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
-energy.mut.fname = file.path(data.dir, paste(family, "_R0_10_beta_no.sel_K.analysis_Keff_out_m.theo.va.csv", sep = ""))
+dri2.mut.fname = file.path(data.dir,paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
+Pn.mut.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
+energy.mut.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.va.csv", sep = ""))
 
@@
 ```{r set_reference_protein}
-## which is the reference protein?
+# which is the reference protein?
 reference = as.character(read.table(reference.fname, header = F)[1, 1])
@@
 
-We use the `r enm` Elastic Network Model with `R0 =` `r R0` for the `r family` family. 
+We use the ```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = TRUE)
+``` Elastic Network Model with `R0 =` `r R0` for the `r family` family. 
 We use as reference for the ENM the protein with pdb code `r reference`.
@@
 ```{r set_experimental_protein_names}
-## Experimental protein names
+# experimental protein names
 protein.exp = read.table(protein_list.fname, header = F, stringsAsFactors = F)[, 1]
@@
 ```{r set_up_site_info, eval = T}
+# read site information of reference protein
+site.info = read.csv(site.info.fname, header = T, sep = ",")
 
-## read site information of reference protein
-site.info = read.csv(site.info.fname, header = T, sep = ",")[1:151, ]
-
-## add info to site.info
+# add info to site.info
 d = ddply(site.info, "site", .fun = function(x) data.frame("da" = min(x[, c(-1, -2)])))
 
-## Define shells of active site neighborhood (first shell is from 2.5 to 7.5, second from 7.5 to 12.5, etc)
+# define shells of active site neighborhood (first shell is from 2.5 to 7.5, second from 7.5 to 12.5, etc)
 d$shell = cut(d$da, breaks = c(-.1, 2.5, 7.5, 12.5, 17.5, 22.5, 27.5, 32.5, 37.5, 42.5, 47.5, 52.5, max(d$da)))
@@
 
-## Read reference pdb and calculate resno, AA, and CN
+# read reference pdb and calculate resno, AA, and CN
 reference.pdb.fname = file.path(data.dir,paste(reference, ".pdb", sep = ""))
@@
 
-## Add pdb.info to site.info
+# add pdb.info to site.info
 site.info = cbind(site.info, pdb.info)
@@
 ```{r read_experimental_data}
+
 # read experimental data
@@
 rownames(energy.exp) = protein.exp
-
 ```
@@
 ```{r read_and_set_data_mut}
+
 # read simulated data
-
 dri2.mut = read.csv(dri2.mut.fname, header = T)
@@
 ```{r read_and_set_data_strong}
+
 # read simulated data
-
 dri2.strong = read.csv(dri2.strong.fname, header = T)
@@
 ```{r prepare-site-data}
-# Prepare my data.frame
-# rows of dri2 are proteins, columns are sites
+# prepare my data.frame
+# note: rows of dri2 are proteins, columns are sites
 
@@
 ```{r mean-z-RSD-vs-site}
-# Comparison of z.RSD profiles annotated with functional information (reported active sites).
+# comparison of z.RSD profiles annotated with functional information (reported active sites).
 dat = siteComparison.all.datasets
@@
 
-# dat.with.means and standard errors
+## dat.with.means and standard errors
 d = ddply(dat,c("dataset","site","AA","shell"), function(x) {
@@
 
-plot(y = z.RSD.exp-z.RSD.strong, x = m.min.da.CM$min.da.ca[1:151])
-plot(y = (z.RSD.exp-z.RSD.mut), x = m.min.da.CM$min.da.CM[1:151])
+plot(y = z.RSD.exp-z.RSD.strong, x = m.min.da.CM$min.da.ca)
+plot(y = (z.RSD.exp-z.RSD.mut), x = m.min.da.CM$min.da.CM)
 
@@
 
-# Plot separate and comparative plots
+## plot separate and comparative plots
 p.facet = p + facet_grid(dataset~., switch = "y") + theme(legend.position = "none")
@@
 p.facet
+
 #p + theme(legend.position = "bottom", legend.title = element_blank())
+
 p + theme(legend.position = "bottom")
@@
 ```
-
-VAL107 and its neighbors (including site 32) are more structurally conserved than predicted.
 
@@
 write.csv(dat, "structure-comparison-profiles.csv")
+```
 
-# Write pdb files for MSDi.
+```{r write-pdb-files}
+# write pdb files with mean.z.RSDi as b-factor for building images
 
-  pdb = ReadCA(reference.pdb.fname, chain.p.ref)$xyz
+## read pdb CAs
+pdb.xyz.ca = ReadCA(reference.pdb.fname, chain.p.ref)$xyz
 
-  mean.exp.z.RSD.pdb <- vec2resno(as.vector(dat.exp$mean.z.RSD), sort(rep(1:ncol(pdb),3)))
-  write.pdb(xyz = c(pdb), b = mean.exp.z.RSD.pdb, file = paste(p.ref, "_exp.pdb", sep = ""))
+## experimental
+exp.mean.z.RSD.vec <- vec2resno(as.vector(dat.exp$mean.z.RSD), sort(rep(1:ncol(pdb.xyz.ca),3)))
+write.pdb(xyz = c(pdb.xyz.ca), b = exp.mean.z.RSD.vec, file = paste(p.ref, "_exp.pdb", sep = ""))
 
-  mean.mut.z.RSD.pdb <- vec2resno(as.vector(dat.mut$mean.z.RSD), sort(rep(1:ncol(pdb),3)))
-  write.pdb(xyz = c(pdb), b = mean.mut.z.RSD.pdb, file = paste(p.ref, "_mut.pdb", sep = ""))
+## mut
+mut.mean.z.RSD.vec <- vec2resno(as.vector(dat.mut$mean.z.RSD), sort(rep(1:ncol(pdb.xyz.ca),3)))
+write.pdb(xyz = c(pdb.xyz.ca), b = mut.mean.z.RSD.vec, file = paste(p.ref, "_mut.pdb", sep = ""))
 
-  mean.strong.z.RSD.pdb <- vec2resno(as.vector(dat.strong$mean.z.RSD), sort(rep(1:ncol(pdb),3)))
-  write.pdb(xyz = c(pdb), b = mean.strong.z.RSD.pdb, file = paste(p.ref, "_strong.pdb", sep = ""))
+## mut + sel / strong
+strong.mean.z.RSD.vec <- vec2resno(as.vector(dat.strong$mean.z.RSD), sort(rep(1:ncol(pdb.xyz.ca),3)))
+write.pdb(xyz = c(pdb.xyz.ca), b = strong.mean.z.RSD.vec, file = paste(p.ref, "_strong.pdb", sep = ""))
 ```
@@
 
-# Prepare modeComparison.strong
+# prepare modeComparison.strong
 tPn.strong = as.data.frame(t(as.matrix(Pn.strong)))
@@
 
-# Prepare modeComparison.mut
+# prepare modeComparison.mut
 tPn.mut = as.data.frame(t(as.matrix(Pn.mut)))
@@
 
-# Prepare modeComparison.exp
+# prepare modeComparison.exp
 tPn.exp = as.data.frame(t(as.matrix(Pn.exp)))
@@
 # modeComparison.exp has NA's because for proteins with gaps when using Keff there're less modes
-#print("Warning: modeComparison.exp <- na.omit(modeComparison.exp)")
+# print("Warning: modeComparison <- na.omit(modeComparison)")
+
 modeComparison.exp <- na.omit(modeComparison.exp)
@@
 modeComparison.mut <- na.omit(modeComparison.mut)
-
 ```
@@
 ```{r}
-## Quantile regression
+# quantile regression
 
-# fit median and quantiles to simulated data and add them to data.frames
+## fit median and quantiles to simulated data and add them to data.frames
 fit.strong.rq.5 <- rq(Pn ~ sn2, tau = .5, data = modeComparison.strong, method = "fn")
@@
 fit.strong.rq.95 <- rq(Pn ~ sn2, tau = .95, data = modeComparison.strong, method = "fn")
+
 modeComparison.strong$rq.5 = fit.strong.rq.5$fitted.values
@@
 
-# fit median and quantiles to simulated data and add them to data.frames
+## fit median and quantiles to simulated data and add them to data.frames
 fit.mut.rq.5 <- rq(Pn ~ sn2, tau = .5, data = modeComparison.mut, method = "fn")
@@
 fit.mut.rq.95 <- rq(Pn ~ sn2, tau = .95, data = modeComparison.mut, method = "fn")
+
 modeComparison.mut$rq.5 = fit.mut.rq.5$fitted.values
@@
 
-# fit median and quantiles to experimental data
+## fit median and quantiles to experimental data
 fit.exp.rq.5 <- rq(Pn ~ sn2, tau = .5, data = modeComparison.exp, method = "fn")
@@
 fit.exp.rq.95 <- rq(Pn ~ sn2, tau = .95, data = modeComparison.exp, method = "fn")
+
 modeComparison.exp$rq.5 = fit.exp.rq.5$fitted.values
@@
 
-# put simulated and experimental data together
+## put simulated and experimental data together
 
@@
 ```{r Pn-vs-mode-energy,cache = 2}
-# Plot Pn vs energy
+# plot Pn vs energy
 dat = modeComparison.all.datasets
@@
     labs(x = "mode energy", y = "structural divergence") +
-    coord_cartesian(xlim = c(0,2.5)) +
     scale_colour_manual(name = NULL, values = myColors) + 
-    scale_fill_manual(name=NULL, values = myColors)
+    scale_fill_manual(name = NULL, values = myColors)
 
@@
 p = ggplot(dat,aes(x=energy.mean,y=Pn.median,col=dataset,fill=dataset)) +
-    geom_pointrange(aes(ymin=Pn.median.min,ymax = Pn.median.max),size=.2,alpha=.4) +
-    geom_line(aes(y=rq.5))  +
-    labs(x="mode energy",y="structural divergence (median Pn) ") +
-    scale_colour_manual(name = NULL,values = myColors) + 
-    scale_fill_manual(name=NULL,values=myColors)+
-    coord_cartesian(xlim=c(0,1))
+    geom_pointrange(aes(ymin = Pn.median.min,ymax = Pn.median.max), size = .2, alpha = .4) +
+    geom_line(aes(y = rq.5))  +
+    labs(x = "mode energy", y = "structural divergence (median Pn) ") +
+    scale_colour_manual(name = NULL, values = myColors) + 
+    scale_fill_manual(name = NULL, values = myColors)
 
-p.facet = p + facet_grid(dataset~.,switch="y") + theme(legend.position="none")
-p.facet %+% subset(dat,dataset =="exp")
+p.facet = p + facet_grid(dataset~., switch = "y") + theme(legend.position = "none")
+p.facet %+% subset(dat,dataset == "exp")
 p.facet %+% subset(dat,dataset == "mut")
@@
 dat = modeComparison.all.datasets
+
 #dat$dataset = revalue(dat$dataset,c("strong" = "mut+sel"))
@@
 knitr::kable(cor.df, digits = 2)
-
 ```
-
-[//]: Write output for further analysis with other programs
-
-```{r write-data-to-output}
-write.csv(siteComparison.exp, "site-structure-comparison-exp.csv",row.names=F)
-write.csv(modeComparison.exp, "mode-structure-comparison-exp.csv",row.names=F)
-```

### 2016-09-29 FUNCTIONS/CalculateMinDaCMCA.R

@@ -1,0 +1,106 @@
+# Description:
+#
+# This function calculates distances between functional sites of proteins and the other sites of the protein.
+# It calculates distances between CAs and CMs.
+#
+# Usage:
+#
+# CalculateMinDaCMCA(family,
+#                    p.ref,
+#                    chain.p.ref,
+#                    heme,
+#                    data.dir)
+#
+#  Args:
+#    - family: The family of the protein to mutate. It can be "globins", "serinProteases", 
+#    "snakesToxin", "sh3", "fabp", "rrm", "phoslip" or "cys".
+#    - p.ref: The pdb code (pdbid) of the protein to mutate (example: "1a6m"). The protein must be a member of
+#    the selected family. This pdbid must not be included in the dataset ("DATA/family_dataset.csv").
+#    - chain.p.ref: The chain of p.ref in the pdb file obtained from Homstrad.
+#    - heme: argument for "globins". It can be "TRUE" or "FALSE". If it is "TRUE", the program considers the heme group.
+#    - data.dir: Directory of the data. It must contain the pdb file obtained from Homstrad ("data.dir/family_coordinates.csv").
+#
+#  Required libraries:
+#    {Bio3d}
+#
+#  Required functions:
+#    ReadCA()
+#    ReadHeme()
+#    CalculateSideChainCM()
+
+  CalculateMinDaCMCA <- function(family,
+                                 p.ref,
+                                 chain.p.ref,
+                                 heme,
+                                 data.dir) {
+  
+  # read functional sites
+  active = read.csv(file.path(data.dir, paste(p.ref, "_functionalSites.csv", sep = "")), sep = ";")$functional.sites
+  active = active[!is.na(active)]
+  
+  # pdb filename
+  pdb.fname <- file.path(data.dir, paste(p.ref, ".pdb", sep = ""))
+
+  # get coordinates of p.ref
+  r.ca.p.ref = ReadCA(pdb.fname, chain.p.ref)$xyz
+  r.CM.p.ref = CalculateSideChainCM(pdb.fname, chain.p.ref)
[…]

### 2016-09-29 MainProgram.R

@@ -31,11 +31,11 @@ rm(list = ls())
 library(bio3d) 
 library(seqinr) 
 
-# Set Elastic Network Model: "ANM" or "pfANM"
-model <- "ANM"
-
 # Data dir
 data.dir <- "DATA"
+
+# Set Elastic Network Model: "ANM" or "pfANM"
+model <- "ANM"
 
 # Output dir
 if (model == "ANM") out.dir <- "OUT/out_subset_CA_ANM"

### 2016-09-29 MainProgramCM.R

@@ -4,6 +4,9 @@
 # Elastic Network Model" (LF-ENM) with different selection regimens according to the "Stress Model". The program also
 # analyzes the multiple alignment of the family to which the protein belongs and calculates measures 
 # of variabilty of theoretical and experimental data.
+# The difference between this program and "MainProgram.R" is that, in this case, the model considers two sites per
+# aminoacid, the CA and the center of mass of the side chain (CM).
+# For the LF - ENM, only CMs are mutated.
 #
 # To run the program it is necessary to previously fill the input ("input_MainProgram.csv") with the following information:
 #

### 2016-09-30 MY-FILES/OTHER FILES/MultipleReportAllBetas.Rmd
cambios 30/09/2016

--- 2016-06-05 MultipleReportAllBetas.Rmd
@@
     exp.smooth.norm.MSDi = colMeans(m.exp.smooth.norm.dr.squarei, na.rm = T )
+
+    exp.smooth.norm.MSDi = (exp.smooth.norm.MSDi - mean(sqrt(exp.smooth.norm.MSDi)))/sd(sqrt(exp.smooth.norm.MSDi))
+
     exp.smooth.norm.MSDi.sd = apply(m.exp.smooth.norm.dr.squarei, 2, sd, na.rm = T)
@@
     theo.smooth.norm.MSDi = colMeans(m.theo.smooth.norm.dr.squarei, na.rm = T )
+    theo.smooth.norm.MSDi = (theo.smooth.norm.MSDi - mean(sqrt(theo.smooth.norm.MSDi)))/sd(sqrt(theo.smooth.norm.MSDi))
 

### 2016-09-30 MY-FILES/OTHER FILES/MultipleReportAllBetasGlobinsZscore.Rmd
cambios 30/09/2016

--- 2016-07-27 other_programs/MultipleReportAllBetasGlobinsZscore2.Rmd
@@
     # MSDi.
-    m.exp.smooth.norm.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.exp.norm.dr.squarei.csv", sep = "")))
+    m.exp.smooth.norm.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.exp.smooth.norm.dr.squarei.csv", sep = "")))
 
-    m.exp.smooth.norm.dr.squarei = m.exp.smooth.norm.dr.squarei[-c(6, 7, 9, 29, 31), ] # Saqué proteínas que Julian no usó
+    m.exp.smooth.norm.dr.squarei = m.exp.smooth.norm.dr.squarei[-c(6, 7, 9, 29, 31), ]
 
     n.prot = nrow(m.exp.smooth.norm.dr.squarei)
+
     exp.smooth.norm.MSDi = colMeans(m.exp.smooth.norm.dr.squarei, na.rm = T)
-    exp.smooth.norm.MSDi.sd = apply(m.exp.smooth.norm.dr.squarei, 2, sd, na.rm = T)/sqrt(no.gaps) * 1.96 # Ver si no hay que hacer sd dp
+
+    exp.smooth.norm.MSDi.sd = apply(m.exp.smooth.norm.dr.squarei, 2, sd, na.rm = T)/sqrt(no.gaps) * 1.96
 
@@
     exp.smooth.norm.MSDi = exp.smooth.norm.MSDi[!is.na(exp.smooth.norm.MSDi)]                                           
+    no.gaps = colSums(matrix(as.numeric(!is.na(m.exp.smooth.norm.dr.squarei)), nrow = n.prot))
 
@@
     # MSDi.
-    m.theo.smooth.norm.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.norm.dr.squarei.csv", sep = "")))
+    m.theo.smooth.norm.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.smooth.norm.dr.squarei.csv", sep = "")))
 

### 2016-09-30 MY-FILES/OTHER FILES/MultipleReportAllBetasGlobinsZscoreCM.Rmd
cambios 30/09/2016

--- 2016-07-27 other_programs/MultipleReportAllBetasGlobinsZscoreGenerico.Rmd
@@
 data.dir <- "DATA"
+out.dir <- "OUT/out_subset_CM"
 
@@
     n.prot = nrow(m.exp.dr.squarei)
-    for (p in (1:n.prot)) {
-      m.exp.dr.squarei[p, ] = scale(sqrt(as.numeric(m.exp.dr.squarei[p, ])))[, 1]
-    }
-
     no.gaps = colSums(matrix(as.numeric(!is.na(m.exp.dr.squarei)), nrow = n.prot))
     exp.MSDi = colMeans(m.exp.dr.squarei, na.rm = T)
+    exp.MSDi = scale(sqrt(exp.MSDi))[, 1]
     exp.MSDi = exp.MSDi[!is.na(exp.MSDi)]
@@
     theo.MSDi = colMeans(m.theo.dr.squarei, na.rm = T)
-    MSDi.fit = scale(sqrt(theo.MSDi))
+    MSDi.fit = scale(sqrt(theo.MSDi))[, 1]
     MSDi.fit = MSDi.fit[1:length(exp.MSDi)]
@@
     b.factor <- pdb$atom$b
-    site = as.numeric(pdb$atom[sel$atom, c("resno")])[1:1213]
+    site = as.numeric(pdb$atom[sel$atom, c("resno")])[1:1203]
     MSDi.fit.pdb <- vec2resno(as.vector(MSDi.fit[1:151]), site)
@@
 
-    b.factor.fit[1:1213] = MSDi.fit.pdb * 100
-    b.factor.exp[1:1213] = exp.MSDi.pdb * 100
+    b.factor.fit[1:1203] = MSDi.fit.pdb * 100
+    b.factor.exp[1:1203] = exp.MSDi.pdb * 100
 
-    write.pdb(pdb = pdb, b = b.factor.fit, file = file.path(out.dir, paste(family, "_", p.ref, "_CM_smooth_beta_", beta, ".pdb", sep = "")))
+    write.pdb(pdb = pdb, b = b.factor.fit, file = file.path(out.dir, paste(family, "_", p.ref, "_beta_", beta, ".pdb", sep = "")))
 
-    write.pdb(pdb = pdb, b = b.factor.exp, file = file.path(out.dir, paste(family, "_", p.ref, "_CM_smooth_exp", ".pdb", sep = "")))
+    write.pdb(pdb = pdb, b = b.factor.exp, file = file.path(out.dir, paste(family, "_", p.ref, "_exp", ".pdb", sep = "")))
 }
@@
 
-Los perfiles normalizados de MSDi se compararon cualitativamente y cuantitativamente mediante el calculo de R^2 y MSE.
-En cada caso se indica el regimen de seleccion usado, correspondiendo "strong sel", "medium sel", "weak sel" y "no sel" a beta = 0.2, 0.5, 0.8 y 1 respectivamente.
+Los perfiles teoricos suavizados y normalizados de MSDi fueron fiteados con los perfiles exterimentales. Se compararon y se calcularon R^2 y MSE. Se indica el regimen de seleccion usada.
 
@@
 *Puntos negros:* Promedio experimental otros sitios.
-*Barras grises:* intervalo Sd/sqrt(n.prot) * 1.96 conjunto experimental.
+*Barras grises:* intervalo Sd/sqrt(n.prot)*1.96.
 
@@
 
-plot(m.mean.theo.Pn.group[1, ], m.mean.exp.Pn[1, ], xlab = "<Pn> teorico", ylab = "<Pn> experimental", main = "Pn strong selection", xlim = c(0, 0.04), ylim = c(0, 0.04), cex.main = 1, cex.lab = 1)
+plot(m.mean.theo.Pn.group[1, ], m.mean.exp.Pn[1, ], xlab = "<<Pn>> teorico", ylab = "<Pn> experimental", main = "Pn strong selection", xlim = c(0, 0.04), ylim = c(0, 0.04), cex.main = 1, cex.lab = 1)
 abline(0, 1)
@@
 
-plot(m.mean.theo.Pn.group[2, ], m.mean.exp.Pn[2, ], xlab = "<Pn> teorico", ylab = "<Pn> experimental", main = "Pn medium selection", xlim = c(0, 0.04), ylim = c(0, 0.04), cex.main = 1, cex.lab = 1)
+plot(m.mean.theo.Pn.group[2, ], m.mean.exp.Pn[2, ], xlab = "<<Pn>> teorico", ylab = "<Pn> experimental", main = "Pn medium selection", xlim = c(0, 0.04), ylim = c(0, 0.04), cex.main = 1, cex.lab = 1)
 abline(0, 1)
@@
 
-plot(m.mean.theo.Pn.group[3, ], m.mean.exp.Pn[3, ], xlab = "<Pn> teorico", ylab = "<Pn> experimental", main = "Pn weak selection", xlim = c(0, 0.04), ylim = c(0, 0.04), cex.main = 1, cex.lab = 1)
+plot(m.mean.theo.Pn.group[3, ], m.mean.exp.Pn[3, ], xlab = "<<Pn>> teorico", ylab = "<Pn> experimental", main = "Pn weak selection", xlim = c(0, 0.04), ylim = c(0, 0.04), cex.main = 1, cex.lab = 1)
 abline(0, 1)
@@
 
-plot(m.mean.theo.Pn.group[4, ], m.mean.exp.Pn[4, ], xlab = "<Pn> teorico", ylab = "<Pn> experimental", main = "Pn no selection", xlim = c(0, 0.04), ylim = c(0, 0.04), cex.main = 1, cex.lab = 1)
+plot(m.mean.theo.Pn.group[4, ], m.mean.exp.Pn[4, ], xlab = "<<Pn>> teorico", ylab = "<Pn> experimental", main = "Pn no selection", xlim = c(0, 0.04), ylim = c(0, 0.04), cex.main = 1, cex.lab = 1)
 abline(0, 1)

### 2016-09-30 MY-FILES/paper.tex
cambios 30/09/2016

--- 2016-05-05 INFORMATION/paper.tex
@@
 We obtained their multiple structural alignment and the structure of each protein of the family.
-Then, for each family, we used the LF - ENM to generate structures of multiple mutants of the reference ``wilt type'' protein.
+Then, for each family, we used the LF - ENM to generate structures of multiple mutants of the reference ``ancestor'' protein.
 We did as much mutations as it corresponds to the sequence identity of this protein with each of the other proteins of the family.
@@
 
-We considered the backbone fluctuations of the reference ``wilt type'' protein around its equilibrium conformation to be described by a coarse - grained ``Elastic Network Model'' (ENM), which represents a protein as a network of nodes placed at the alpha carbons ($C_{\alpha}$) connected by springs.
+We considered the backbone fluctuations of the reference ``ancestor'' protein around its equilibrium conformation to be described by a coarse - grained ``Elastic Network Model'' (ENM), which represents a protein as a network of nodes placed at its alpha carbons ($C_{\alpha}$) connected by springs.
 In general, the ENM potential is of the form:
 
-\begin{equation}
-V_{wt}(\mathbf{r}) = 1/2(\mathbf{r}-\mathbf{r}^{0}_{wt})^{T}\mathbf{K}_{wt}(\mathbf{r}-\mathbf{r}^{0}_{wt})
+\begin{equation} \label{eq:Vwt}
+V_{wt} = \frac{1}{2} \sum_{i < j} k_{ij} (d_{ij} - d ^ 0_{ij}) ^ 2
 \end{equation}
 
-where, for a protein of $N$ sites, $\mathbf{r}$ is a column vector with $3N$ elements: the $x$, $y$, $z$ coordinates of the $N$ $C_{\alpha}$, $\mathbf{r}^{0}_{wt}$ is the equilibrium structure of the reference protein, and $\mathbf{K}_{wt}$ is the ``stiffness'' matrix, which represents the network\textsc{\char13} s topology and spring force constants.
+where $k_{ij}$ is the force constant of the spring connecting nodes $i$ and $j$, $d_{ij}$ is the distance between sites $i$ and $j$ and $d ^ 0_{ij}$ is the equilibrium (native) distance between these sites.
+These distances are calculates as the modules of $\mathbf{d}_{ij} = \mathbf{r}_{i} - \mathbf{r}_{j}$ and  $\mathbf{d} ^ {0}_{ij} = \mathbf{r}^{0}_{i} - \mathbf{r}^{0}_{j}$ respectively, being $\mathbf{r}$ the position of a given site and $\mathbf{r}_{0}$ the equilibrium position of the site.
 
-\subsection*{LF-ENM model of mutant proteins:}
+{\subsection* {LF - ENM}
+To simulate mutants of the reference protein we used the ``Linearly Forced - Elastic Network Model'' (LF - ENM).
+This model simulates the effect of a single mutation by perturbing the equilibrium lengths of the ENM springs: $d^0_{ij} \to d^0_{ij} + \Delta_{ij}$, where $\Delta_{ij}$ are picked independently for each of the contacts of the mutated site from the same uniform distribution, which satisfies $<\Delta_{ij}> = 0$ and $Var(\Delta_ij) = \sigma^2$.
+Following this, the mutant's potential is of the form:
 
-To simulate mutants of each reference protein and thus to generate datasets of theoretical proteins, we used the ``Linearly Forced Elastic Network Model'' (LF - ENM).
-This model predicts the effect of a single mutation adding a linear perturbative term to the reference potential:
-
-\begin{equation}
-V_{mut}=V_{wt} - \mathbf{f}^{T}(\mathbf{r}-\mathbf{r}^{0}_{wt})
+\begin{equation} \label{eq:Vmut}
+V_{mut} = \frac{1}{2} \sum_{i<j} k_{ij} [d_{ij}-(d^0_{ij}+\Delta_{ij})]^2
 \end{equation}
 
-where $\mathbf{f}$ is a column vector with $3N$ elements that models the mutation.
-The equilibrium structure of the mutant $\mathbf{r}^{0}_{mut}$ is the value of $\mathbf{r}$ that minimizes $V_{mut}$.
+Then, the LF - ENM is obtained from expanding Eq.
+\ref{eq:Vmut} up to second order.
+The potential is expressed in terms of ``forces'' directed along the contacts of the mutated site with lengths of the form:
+
+\begin{equation} \label{eq:fij}
+f_{ij} = k_{ij} \Delta_{ij}
+\end{equation}
+
+Finally, the equilibrium structure of the mutant $\mathbf{r}^{0}_{mut}$ is the value of $\mathbf{r}$ that minimizes $V_{mut}$.
 Using Eqs.
-(1) and (2) we find the structural variation due to the mutation:
+\ref{eq:Vwt} and \ref{eq:Vmut} and after some algebra we find the structural variation due to the mutation of a reference protein of $N$ sites:
 
-\begin{equation}
+\begin{equation} \label{eq:dr}
 d\mathbf{r}^{0} \equiv  \mathbf{r}^{0}_{mut} - \mathbf{r}^{0}_{wt} = \mathbf{K}^{-1}_{wt}\mathbf{f}
@@
 
+being $\mathbf{r}$ a $3 \times N $ vector of coordinates and $\mathbf{K}$ the stiffness matrix, which represents
+the network s topology and spring force constants.
 This equation shows that the structural perturbation introduced by a mutation is related to the mutation and to the network of oscillators, via $\mathbf{K}^{-1}_{wt}$.
@@
 
-\subsection*{Stress Model}
-The stress model is based on an Elastic Netowork Model in which mutations are modeled as perturbations to the spring lengths that connect the mutated site with its neighbors.
+\subsection*{Stress Model of protein evolution}
+We have described how to model mutations, but we have not described yet the way we select them.
+The stress model of protein evolution predicts the probability of acceptance of mutations.
+As the LF - ENM, it is based on an Elastic Netowork Model in which mutations of an ancestor protein are modeled as perturbations to the spring lengths that connect the mutated site with its neighbors.
 
-Let the ENM potential energy of the wild-type protein be:
-\begin{equation} \label{eq:Vwt}
-V_{wt} = \frac{1}{2} \sum_{i<j} k_{ij} (d_{ij}-d^0_{ij})^2
-\end{equation}
-We model the mutation by replacing perturbing the equilibrium lengths of the ENM springs: $d^0_{ij} \to d^0_{ij} + \Delta_{ij}$, where $\Delta_{ij}$ are picked independently for each of the contacts of the mutated site, from the same distribution, e.g.
-a uniform distribution, which satisfies $<\Delta_{ij}> = 0$ and $Var(\Delta_ij) = \sigma^2$, independent of $ij$.
-The mutant's potential is:
-\begin{equation} \label{eq:Vmut}
-V_{mut} = \frac{1}{2} \sum_{i<j} k_{ij} [d_{ij}-(d^0_{ij}+\Delta_{ij})]^2
-\end{equation}
-When the mutant adopts the wild-type structure $\mathbf{r^0}_{wt}$, $d_{ij} = d_{ij}^0$, and the mutant's energy is:
-\begin{equation} \label{eq:Vmut0}
-V_{mut}(\mathbf{r^0}_{wt}) = \frac{1}{2} \sum_{i<j} k_{ij} \Delta_{ij}^2
-\end{equation}
-The stress model poses that the probability of accepting such a mutant is:
+The stress model predicts that the probability of accepting such a mutant is:
 \begin{equation} \label{eq:Paccept}
@@
 
-\subsection*{Linearly Forced Elastic Network Model with Stress Model}
-The linearly forced elastic network model is obtained from expanding Eq.
-\ref{eq:Vmut} up to second order.
-The potential is expressed in terms of "forces" directed along the contacts of the mutated site with lengths:
-\begin{equation} \label{eq:fij}
-f_{ij} = k_{ij} \Delta_{ij}
-\end{equation}
 Therefore, from Eq. \ref{eq:Paccept} and \ref{eq:fij} we find:
@@
 
-For the ANM, $k_{ij}$ are either 0 or 1, and we get:
+For the special case of ENM ``Anisotropic Network Model'' (ANM), $k_{ij}$ are either 0 or 1, as we explain later, and we get:
 \begin{equation} \label{eq:PacceptANM}
@@
 Where the sum $j \sim i$ is over all $j$ that are in contact with the mutated site $i$ (i.e. for which $k_{ij} \ne 0$.
-
-\subsection*{Evolutionary Simulation}
-
-\subsubsection*{One evolutionary step}
-Let us define a time-step such that the time-step when there is a single substitution event for the whole protein (a substitution is an accepted mutation).
-To simulate such an event we did the following:
-\begin{enumerate}
-\item We picked one random site $l$
-\item We introduced a "trial" mutation by obtaining a set of ${f_{lj}}$ for each of the contacts of site $l$
-\item We calculated the probability of accepting this trial mutation: $P_{accept} = e^{-\beta \frac{1}{2} \sum_{j\sim i}  f_{lj}^2}$
-\item We calculated the logical variable $\text{Accept} = P_{accept} \ge \text{runif(1,0,1)}$; Accept will be TRUE with probability $P_{accept}$, this is a way of implementing accepting mutations with this probability.
-\item If Accept is TRUE, we accepted the mutation (i.e.
-the new wild-type is the mutant) and the evolutionary step was finished (i.e.
-we found an accepted mutation: one substitution).
-Else, we rejected the trial mutation and tried again (i.e.
-went back to Step 1: picked a random site, etc.).
-\end{enumerate}
-For future reference, let's assume that we implement this single-step using a function oneSubstitution(sites) that returns the mutated site $l$, and the force that simulates the mutation ${f_{lj}}$ (or alternatively the force-vector $\mathbf{f}_l$).
-
-\subsubsection*{An evolutionary path of N substitution at N different sites}
-We want to simulate a lineage (an evolutionary path) such that it starts at a known ancestor (our reference protein) and it ends when $N$ sites have accepted mutations.
-($N \le L$, where $L$ is the sequence length).
-Briefly, we need to repeat the single evolutionary step of the previous paragraph $N$ times, making sure that the set of sites where we try mutations does not include sites that previously accepted mutations (this corresponds to sampling without replacement).
-The process would be, using pseudocode:
-
-\section*{Star tree}
-Our "experimental" data are sets of proteins one of which we consider as the "reference" protein.
-In principle, we should infer the phylogenetic tree and try to simulate structures with our model following a tree with the same topology.
-However, we assume that the results are not too sensitive with respect to tree topology so that we can approximate the tree by a "star tree".
-The common ancestor of all lineages of our star tree is our reference protein.
-Then, each lineage corresponds to a pair alignment of each protein with the reference.
-Thus, different lineages have different "branch lengths", were we assume the branch lengh is the number of sites in which the sequence of the (common) ancestor and the tip of the lineage differ.
-
-\section*{Model parameters}
-To completely specify the model, we must choose $\mathbf{K}_{wt}$ and $\mathbf{f}$.
-There are a number of alternative ENMs.Specifically, we used the ``Anisotropic Network Model'' (ANM).
-Following this model, we gave a spring force constant of 1 to sites at a distance $\leq$ 10 $\AA$ and a spring force constant of 0 to sites at a distance > 10 $\AA$.
-We selected 10 $\AA$ as the cut off value after optimization using a range of values form 8 to 12 (data not shown).
-This cut off value is also the most commonly used.
-To calculate $\mathbf{f}$, given a mutation at a site $l$, each site $i$ in contact with $l$ is assigned a force directed along the $l-i$ contact and site $l$ is assigned a reaction force.
-To simulate random mutations, the magnitudes of $f_{li}$ were randomly picked from a uniform distribution in $[-f_{max},f_{max}]$.
-The forces for different contacts were picked independently.
-Since $f_{max}$ does not affect the results, we set
-$f_{max} = 2$. We can think of the range $[-f_{max}, f_{max}]$ as a continuous approximation of the perturbations introduced by the mutations, covering
-from mutations between physicochemically similar amino acids ($f \approx 0$) up to mutations between very different amino acids ($f \leq f_{max}$).
 
@@
 \subsubsection*{Selection of the reference protein:}
-For each family of the dataset we selected a reference ``wilt type'' protein, which we consider is the most structurally representative protein of the family.
+For each family of the dataset we selected a reference ``ancestor'' protein, which we consider is the most structurally representative protein of the family.
 To get this protein, we first calculated the average structure of each multiple alignment.
@@
 
+\subsection*{Theoretical dataset:}
+
+To generate a theoretical dataset that is comparable with the experimental dataset, for each family, we aligned the ancestor with the other proteins, we calculated the number of mutated sites $n$ and we created, for each of the pairs, a lineage of 100 simulated mutants following a path of substitutions until we had mutated $n$ sites.
+This path is composed of various evolutionary steps each of them comprising a single substitution.
+
+\subsubsection*{One evolutionary step:}
+Let us define a time-step such the time-step when there is a single substitution event (an accepted mutation) for the whole protein. To simulate such an event we did the following:
+\begin{enumerate}
+\item We picked one random site $l$ of the reference protein.
+\item We introduced a "trial" mutation by obtaining a set of forces ${f_{lj}}$ for each of the $j$ contacts of site $l$ and the reaction force over site $l$.
+\item We calculated the probability of accepting this trial mutation: $P_{accept} = e^{-\beta \frac{1}{2} \sum_{j\sim i}  f_{lj}^2}$
+\item We calculated the logical variable $\text{Accept} = P_{accept} \ge \text{runif(1,0,1)}$; Accept will be TRUE with probability $P_{accept}$.
+\item If Accept was TRUE, we accepted the mutation (i.e.
+the new ancestor was the generated mutant) and the evolutionary step was finished (i.e.
+we found an accepted mutation: one substitution).
+Else, we rejected the trial mutation and tried again (i.e.
+went back to Step 1).
+\end{enumerate}
+
+\subsubsection*{An evolutionary path of substitution at different sites:}
+We wanted to simulate a lineage (an evolutionary path) such that it started at a known ancestor (the reference protein) and it ended when $n$ sites had accepted mutations.
+($n \le N$, where $N$ is the sequence length).
+$n$ corresponds to the number of mutated sites of the ancestor compared with one of the other proteins of the dataset.
+To do this, for each pair of proteins, we repeated the single evolutionary step of the previous paragraph $n$ times, making sure that the set of sites where we tried mutations did not include sites that had previously accepted mutations.
+We calculated 100 proteins of each lineage.
+
+\subsubsection*{Regimens of selection:}
+To account for different regimens of selection we gave $\beta$ different values. This differente regimens corresponds to:
+
+\item No selection: Paccept \approx 1
+
+\item Weak selection: Paccept \approx 0.9
+
+\item Medium selection: Paccept \approx 0.5
+
+\item Strong selection: Paccept \approx 0.1
+
+To gel the $\beta$ values for each regimen we did as follows:
+
+\begin{equation} \label{eq:PacceptFij}
+\beta^{reg} = \frac{- log(Paccept^{reg})}{(<f_{ij}^2> \times <CN>)} 
+\end{equation}
+
+being $<CN>$ the average number of contacts of the reference protein.
+
+\subsubsection*{Star tree}
+Our experimental data are sets of proteins, one of which we consider as the reference ``ancestor'' protein.
+In principle, we should infer the phylogenetic tree and try to simulate structures with our model following a tree with the same topology.
+However, we assume that the results are not too sensitive with respect to tree topology so that we can approximate the tree by a ``star tree''.
+The common ancestor of all lineages of our star tree is our ``reference'' protein.
+Then, each lineage corresponds to a pair alignment of each protein with this protein.
+Thus, different lineages have different ``branch lengths'', were we assume the branch length is the number of sites in which the sequence of the ancestor and the tip of the lineage differ.
+
+\section*{Model parameters}
+To completely specify the model, we must specify parameters for $\mathbf{K}_{wt}$ and $\mathbf{f}$.
+As we mentioned before, we used the ``Anisotropic Network Model'' (ANM).
+Following this model, we gave a spring force constant of 1 to sites at a distance $\leq$ 10 $\AA$ and a spring force constant of 0 to sites at a distance > 10 $\AA$.
+We selected 10 $\AA$ as the cut off value after optimization using a range of values form 8 to 12 (data not shown).
+This cut off value is also the most commonly used.
+To calculate $\mathbf{f}_{lj}$, given a mutation at a site $l$, each site $j$ in contact with $l$ is assigned a force directed along the $l-j$ contact and site $i$ is assigned a reaction force.
+To simulate random mutations, the magnitudes of $\mathbf{f}_{lj}$ were randomly picked from a uniform distribution of $\Delta_{lj}$ in the interval $[- f_{max},f_{max}]$.
+The forces for different contacts were picked independently.
+Since $f_{max}$ does not affect the results, we set $f_{max} = 2$.
+We can think of the range $[-f_{max}, f_{max}]$ as a continuous approximation of the perturbations introduced by the mutations, covering from mutations between physicochemically similar amino acids ($f \approx 0$) up to mutations between very different amino acids ($f \leq f_{max}$).
+
 \subsection*{ Structural variability measures:}
@@
 For the theoretical dataset we considered that there are not nonaligned sites.
-Then, structural variability measures were calculated in Cartesian coordinates and projected onto the normal modes coordinates:
+Then, structural variability measures were calculated in cartesian coordinates and projected onto the normal modes coordinates:
 
@@
 
-\begin{equation}
+\begin{equation} \label{eq:drSquarei}
 \left\|d\mathbf{r}^{0}_{i}\right\|^{2}=dx^{0,2}_{i}+dy^{0,2}_{i}+dz^{0,2}_{i}
@@
 
-Were $d\mathbf{r}^{0}_{i}=(d\mathbf{x}^{0}_{i}d\mathbf{y}^{0}_{i}d\mathbf{z}^{0}_{i})^{T}$ is the column vector of cartesian displacements of the $i^{th}$ $C_{\alpha}$ with respect to the reference structure obtained from Eq.
-(4).
+Were $d\mathbf{r}^{0}_{i}=(d\mathbf{x}^{0}_{i}d\mathbf{y}^{0}_{i}d\mathbf{z}^{0}_{i})^{T}$ is the column vector of cartesian displacements of the $i^{th}$ $C_{\alpha}$ with respect to the reference structure.
 To diminish noisy information, we smoothed these profiles as shown:
 
-Formula
+\begin{equation} \label{eq:SmoothdrSquarei}
+\left\|d\mathbf{r}^{0}_{i}\right\|^{2}_{smooth} = \frac{(mathbf{C} \times \left\|d\mathbf{r}^{0}_{i}\right\|^{2})}{\sum_{i} \mathbf{C}}
 
-Then, since we are only interested in the relative variability of different sites, deviations obtained using Eq. () were normalize so that they add up to 1.
+\end{equation}
+
+Being $\mathbf{C}$ a $N \times N$ matrix with $1$ in the diagonal and in the contacts and $0$ elsewhere. 
+Finally, since we are only interested in the relative variability of different sites, deviations obtained using Eq. \ref{eq:SmoothdrSquarei} were normalize so that they add up to 1.
 
@@
 
-For proteins that do not align with all the sites of the reference protein instead of $\mathbf{K}$, we used $\mathbf{K}_{eff}$, whose normal modes describe the motions of the aligned sites only (see reference [x]).
-Then, for a protein with structural variation of the aligned sites $d\mathbf{r}^{0}$, the projection onto eigenvectors was calculated as follows:
+Being $\mathbf{q}_{n}$ the eigenvectors and  $\lambda_{n}$ their eigenvalues.
+For proteins that do not align with all the sites of the reference protein, instead of $\mathbf{K}$, we used $\mathbf{K}_{eff}$, whose normal modes describe the motions of the aligned sites only (see reference [x]).
+Then, for a protein with structural variation of the aligned sites $d\mathbf{r}^{0}$, the projection onto the normal modes was calculated as follows:
 
@@
 
-\subsubsection*{Cartesian coordinates:} For the theoretical datasets and for the experimental dataset we averaged $\left\|d\mathbf{r}^{0}_{i}\right\|^{2}$ over each site $i$ of the reference protein of each family to obtain profiles of $MSD_{i}$.
-Then, the theoretical average profiles were fitted with the experimental profile.
+\subsubsection*{Cartesian coordinates:} For the theoretical datasets and for the experimental dataset we averaged $\left\|d\mathbf{r}^{0}_{i}\right\|^{2}$ over each site $i$ of the reference protein to obtain profiles of $MSD_{i}$.
+Then, the theoretical average profiles were fitted with the experimental profiles.
 Lastly, for each dataset, we concatenated the profiles obtained for all of the families to obtain a sole profile.
 
-\subsubsection*{Normal modes coordinates:} For the theoretical datasets, with or without natural selection, the 10 x P profiles of $P_{n}$ of each family were split in 10 groups so that in all of them there was a simulated mutant that corresponded to an experimental pair of proteins of the family in means of the \% ID.
-Then we calculated, for these 10 groups, the average and 0.05 and 0.95 quantiles.
+\subsubsection*{Normal modes coordinates:} For the theoretical datasets, the 100 x P profiles of $P_{n}$were split in 100 groups so that in all of them there was a member of each lineage.
+Then we calculated, for these 100 groups, the average and 0.05 and 0.95 quantiles.
 Finally, we calculated the average of averages and the average of quantiles.
@@
 The results are shown in figure 1.
-Figue 1 shows that the $R^2$ between the experimental dataset and theoretical datasets, with or without natural selection, is high, $\approx 0.8$, and that accounting for natural selection does not seem to improve the agreement.
+Figue 1 shows that the $R^2$ between the experimental dataset and theoretical datasets, with or without natural selection, is high, $\approx 0.5$, and that accounting for natural selection does not seem to improve the agreement.
 

### 2016-09-30 OUT/analysis-structure.Rmd
cambios 30/09/2016

@@
 energy.mut.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.va.csv", sep = ""))
-
 ```
@@
 
-We use the ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
-``` Elastic Network Model with `R0 =` `r R0` for the `r family` family. 
+We use the Elastic Network Model with R0 = `r R0` for the `r family` family. 
 We use as reference for the ENM the protein with pdb code `r reference`.
-The `r family` family consists of the following proteins:
+The `r family` family is of the type of `r type` and consists of the following proteins:
 
@@
 ```{r read_experimental_data}
-
 # read experimental data
@@
 ```{r read_and_set_data_mut}
-
 # read simulated data
@@
 ```{r read_and_set_data_strong}
-
 # read simulated data
@@
 
-To measure structural divergence we use z.RSD profiles, which are the best (most similar distributions and profiles w.r.t experimental).
+To measure structural divergence we use z.RSD profiles, which are the best, at least for globins (most similar distributions and profiles w.r.t experimental).
 
@@
 
+## read information about minimal active site distances
 m.min.da.CM = read.csv(file.path(data.dir, paste(p.ref, "_min.da.CM.ca.csv", sep = "")))
@@
 
-plot(y = z.RSD.exp-z.RSD.strong, x = m.min.da.CM$min.da.ca)
-plot(y = (z.RSD.exp-z.RSD.mut), x = m.min.da.CM$min.da.CM)
+plot(y = z.RSD.exp - z.RSD.strong, x = m.min.da.CM$min.da.ca, xlab = "minimal distance to active site (between CAs)")
+plot(y = z.RSD.exp - z.RSD.mut, x = m.min.da.CM$min.da.CM, xlab = "minimal distance to active site (between CMs)")
+
+print("agregar correlación")
 
@@
     scale_colour_manual(name = NULL, values = myColors) + 
-    scale_fill_manual(name=NULL, values = myColors)
+    scale_fill_manual(name = NULL, values = myColors)
 
@@
 knitr::kable(cor.df, digits = 2)
-write.csv(dat, "structure-comparison-profiles.csv")
 ```

### 2016-09-30 FUNCTIONS/CalculateGroupsMeansQuantiles.R

@@ -1,46 +1,0 @@
-# This function partitionates data into "ngroups" of "length" members and calculates
-# means of means and quantiles of means
-#
-#  Args:
-#    data: The matrix of data to partitionate. nrow(data) must be ngroups*length.
-#    ngroups: Number of groups to partitionate the data.
-#    length: Number of members for each group. 
-#
-#  Returns:
-#    mean.group: ngroups x ncol(data) matrix with the mean of each group in each row.
-#    mean.total: 1 x ncol(data) matrix with colMeans(mean.groups).
-#    quantile: 2 x ncol(data) matrix with quantile 0.05 of each column of mean.groups in the first row 
-#    and quantile 0.95 of each column of mean.groups in the second row.
-CalculateGroupsMeansQuantiles <- function(data, ngroups, length) {
-  mean.group = matrix(0, ncol = ncol(data), nrow = ngroups)
-  quantile1.group = matrix(0, ncol = ncol(data), nrow = ngroups)
-  quantile2.group = matrix(0, ncol = ncol(data), nrow = ngroups)
-  quantile1.mean = matrix(0, ncol = ncol(data), nrow = 1)
-  quantile2.mean = matrix(0, ncol = ncol(data), nrow = 1)
-  
-  for (i in (1:ngroups)) {
-    mean.group[i, ] = colMeans(data[((i * length) - (length - 1)):(i * length), ])
-    for (j in (1:ncol(data))) {
-      quantiles = as.vector(quantile((data[((i * length) - (length - 1)):(i * length), j]), probs = c(0.05, 0.95)))
-      quantile1.group[i, j] = quantiles[1]
-      quantile2.group[i, j] = quantiles[2]
-    }
-  }
-  mean.mean.group = colMeans(mean.group)
-  mean.quantile1.group = colMeans(quantile1.group)
-  mean.quantile2.group = colMeans(quantile2.group)
-  
-  for (k in (1:ncol(data))){
-      quantiles.mean = as.vector(quantile(mean.group[, k], probs = c(0.05, 0.95)))
-      quantile1.mean[1, k] = quantiles.mean[1]
-      quantile2.mean[1, k] = quantiles.mean[2]
-  }
-  
-  output <- list("mean.group" = mean.group, 
-                 "mean.mean.group" = mean.mean.group, 
-                 "mean.quantile1.group" = mean.quantile1.group, 
-                 "mean.quantile2.group" = mean.quantile2.group,
[…]

### 2016-10-01 analysis-structure.Rmd
cambios 01-10-2016

--- 2016-09-30 OUT/analysis-structure.Rmd
@@
 ```{r setup, include = FALSE}
-knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, cache = 2, autodep = T)
+knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, autodep = T)
 ```
@@
 
-We use the Elastic Network Model with R0 = `r R0` for the `r family` family. 
-We use as reference for the ENM the protein with pdb code `r reference`.
-The `r family` family is of the type of `r type` and consists of the following proteins:
+We studied the `r family` family. 
+We used the ENM `r enm` with R0 = `r R0` to generate mutants.
+We used as reference for the ENM the protein with pdb code `r reference`. 
+We simulated `r n.mut.p` mutants of this reference for each protein of the family.
+The `r family` family is of the type `r type` and consists of the following proteins:
 
@@
 
-print("agregar correlación")
+print("agregar correlacion")
 
@@
 exp.mean.z.RSD.vec <- vec2resno(as.vector(dat.exp$mean.z.RSD), sort(rep(1:ncol(pdb.xyz.ca),3)))
-write.pdb(xyz = c(pdb.xyz.ca), b = exp.mean.z.RSD.vec, file =  paste(p.ref, "_exp.pdb", sep = ""))
+write.pdb(xyz = c(pdb.xyz.ca), b = exp.mean.z.RSD.vec, file =  file.path(data.dir, paste(p.ref, "_exp.pdb", sep = "")))
 
@@
 mut.mean.z.RSD.vec <- vec2resno(as.vector(dat.mut$mean.z.RSD), sort(rep(1:ncol(pdb.xyz.ca),3)))
-write.pdb(xyz = c(pdb.xyz.ca), b = mut.mean.z.RSD.vec, file = paste(p.ref, "_mut.pdb", sep = ""))
+write.pdb(xyz = c(pdb.xyz.ca), b = mut.mean.z.RSD.vec, file = file.path(data.dir, paste(p.ref, "_mut.pdb", sep = "")))
 
@@
 strong.mean.z.RSD.vec <- vec2resno(as.vector(dat.strong$mean.z.RSD), sort(rep(1:ncol(pdb.xyz.ca),3)))
-write.pdb(xyz = c(pdb.xyz.ca), b = strong.mean.z.RSD.vec, file = paste(p.ref, "_strong.pdb", sep = ""))
+write.pdb(xyz = c(pdb.xyz.ca), b = strong.mean.z.RSD.vec, file = file.path(data.dir, paste(p.ref, "_strong.pdb", sep = "")))
 ```
@@
 
-```{r Pn-vs-mode-energy,cache = 2}
+```{r Pn-vs-mode-energy}
 # plot Pn vs energy
@@
 
-```{r median-Pn-vs-mode-energy, cache = 2}
+```{r median-Pn-vs-mode-energy}
 dat = modeComparison.all.datasets

### 2016-10-01 MainProgram.R

@@ -24,6 +24,8 @@
 #    - K.analysis: It can be "K" or "Keff". For "K" or "Keff", the analysis is based on normal modes of "K" or "Keff"
 #    respectibly.
 
+### PROGRAM ###
+
 # Remove objects from the workspace
 rm(list = ls())
 

### 2016-10-01 MainProgramCM.R

@@ -27,6 +27,8 @@
 #    - K.analysis: It can be "K" or "Keff". For "K" or "Keff", the analysis is based on normal modes of "K" or "Keff"
 #    respectibly.
 
+### PROGRAM ###
+
 # Remove objects from the workspace
 rm(list = ls())
 

### 2016-11-04 analysis-structure-local-enviroment.Rmd
cambios 04/11/16

---
title: "Structural Divergence Analysis"
author: "María Laura Marcos, Julian Echave"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, autodep = T)
```

```{r load_packages}

# Load packages
library(ggplot2)
library(reshape2)
library(plyr)
library(quantreg)
library(bio3d)

# Load functions
source(file.path(data.dir, "multiplot.R"))
source(file.path(data.dir, "my-functions.R")) 
```

```{r set_my_colors, eval = T}
myColors = c("blue", "darkgreen", "red", "red") 
names(myColors) <- c("exp", "mut", "strong", "mut+sel")
```

# Introduction
We study the evolutionary divergence of proteins using the LF-ENM and comparing simulated mutants with experimental data.

```{r set_run_variables}
# significance factors
f95 = 1.96
f99 = 2.6
f999 = 3.3
```

```{r set_file_names}
# input and pre-processing of data

## set up input filenames
reference.fname = file.path(data.dir, paste(family, "_ref.txt", sep = ""))
protein_list.fname = file.path(data.dir, paste(family, "_list.txt", sep = ""))
site.info.fname = file.path(data.dir, paste(p.ref, "_m.da.ca.csv", sep = ""))
min.da.CM.ca.fname = file.path(data.dir, paste(p.ref, "_min.da.CM.ca.csv", sep = ""))

dri2.exp.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.exp.sum.dif.dist.csv", sep = ""))

dri2.strong.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_strong.sel_K.analysis_Keff_out_m.theo.sum.dif.dist.csv", sep = "")) #cambiar

dri2.mut.fname = file.path(data.dir,paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.sum.dif.dist.csv", sep = ""))
```

```{r set_reference_protein}
# which is the reference protein?
reference = as.character(read.table(reference.fname, header = F)[1, 1])
```

We studied the `r family` family. 
We used the ENM `r enm` with R0 = `r R0` to generate mutants.
We used as reference for the ENM the protein with pdb code `r reference`. 
We simulated `r n.mut.p` mutants of this reference for each protein of the family.
The `r family` family is of the type `r type` and consists of the following proteins:

```{r set_experimental_protein_names}
# experimental protein names
protein.exp = read.table(protein_list.fname, header = F, stringsAsFactors = F)[, 1]
protein.exp = protein.exp[protein.exp != reference]
print(protein.exp)
```

[//]: Prepare site.info data frame

```{r set_site_info, eval = T}
# read site information of reference protein
site.info = read.csv(site.info.fname, header = T, sep = ",")
m.min.da.CM.ca = read.csv(min.da.CM.ca.fname)

# add info to site.info
d = ddply(site.info, "site", .fun = function(x) data.frame("da" = min(x[, c(-1, -2)])))

# define shells of active site neighborhood (first shell is from 2.5 to 7.5, second from 7.5 to 12.5, etc)
d$shell = cut(d$da, breaks = c(-.1, 2.5, 7.5, 12.5, 17.5, 22.5, 27.5, 32.5, 37.5, 42.5, 47.5, 52.5, max(d$da)))
levels(d$shell) = seq(length(levels(d$shell))) - 1 # rename shell levels
site.info = merge(site.info, d, by = "site")

# read reference pdb and calculate resno, AA, and CN
reference.pdb.fname = file.path(data.dir,paste(reference, ".pdb", sep = ""))
ref.pdb = read.pdb(reference.pdb.fname)
inds = atom.select(ref.pdb, elety = "CA")
ref.pdb.ca = ref.pdb$atom[inds$atom,]
cmap.ca = cmap(ref.pdb$xyz[inds$xyz], dcut = R0, scut = 0, mask.lower = F)
CN = rowSums(cmap.ca, na.rm = T) - 1 # diag(cmap.ca) returned by cmap is 1!
AA = ref.pdb.ca$resid
resno = ref.pdb.ca$resno
pdb.info = data.frame(resno, AA, CN)
names(pdb.info) = c("resno", "AA", paste("CN", as.character(R0), sep = ""))

# add pdb.info to site.info
site.info = cbind(site.info, pdb.info)
```

[//]: Prepare experimental data

```{r read_experimental_data}
# read experimental data
dri2.exp = read.csv(dri2.exp.fname, header = T)
site = site.info$site
dri2.exp = dri2.exp[1:length(protein.exp), site]
rownames(dri2.exp) = protein.exp

```

[//]: Prepare data for no selection (mut)

```{r read_and_set_data_mut}
# read simulated data
dri2.mut = read.csv(dri2.mut.fname, header = T)
site = site.info$site
dri2.mut = dri2.mut[1:length(protein.exp), site]
rownames(dri2.mut) = paste("mut", rownames(dri2.mut), sep = "")

```

[//]: Prepare data for strong selection

```{r read_and_set_data_strong}
# read simulated data
dri2.strong = read.csv(dri2.strong.fname, header = T)
site = site.info$site
dri2.strong = dri2.strong[1:length(protein.exp), site]
rownames(dri2.strong) = paste("strong", rownames(dri2.strong), sep = "")

```

# Structural divergence along sites

Here we study how structural divergence varies from site to site. We will compare simulated data and empirical data.

```{r prepare_site_data}
# prepare my data.frame

tdri2.strong = as.data.frame(t(as.matrix(dri2.strong)))
tdri2.strong = cbind(site.info, tdri2.strong)
siteComparison.strong = melt(tdri2.strong, id.vars = names(site.info), variable.name = "protein", value.name = "dri2")

tdri2.mut = as.data.frame(t(as.matrix(dri2.mut)))
tdri2.mut = cbind(site.info, tdri2.mut)
siteComparison.mut = melt(tdri2.mut, id.vars = names(site.info), variable.name = "protein", value.name = "dri2")

tdri2.exp = as.data.frame(t(as.matrix(dri2.exp)))
tdri2.exp = cbind(site.info, tdri2.exp)
siteComparison.exp = melt(tdri2.exp, id.vars = names(site.info), variable.name = "protein", value.name = "dri2")

siteComparison.all.datasets = rbind(
  data.frame("dataset" = "exp", siteComparison.exp),
  data.frame("dataset" = "mut", siteComparison.mut),
  data.frame("dataset" = "strong", siteComparison.strong))

siteComparison.all.datasets = ddply(siteComparison.all.datasets, c("dataset", "protein"), mutate,
          "n.SD" = dri2/mean(dri2, na.rm = T),
          "z.SD" = vscale(dri2),
          "RSD" = (dri2),
          "n.RSD" = RSD/mean(RSD, na.rm = T),
          "z.RSD" = vscale(RSD))
```

### Mean z.RSD vs site

To measure structural divergence we use z.RSD profiles, which are the best, at least for globins (most similar distributions and profiles w.r.t experimental).

The following plot compares the mean z.RSD profiles, including standard errors (with .999 confidence level for the mean)
*Warning: the effective number of data should be smaller than the actual data, especially for the experimental dataset because of several factors, including smoothing of the profiles, phylogenetic relationships, etc. We need to deal with this for quantitative analysis. Probably we'll need to use bootstrapping to calculate standard errors non-parametrically*

```{r mean_z_RSD_vs_site}
# comparison of z.RSD profiles with functional sites

## prepare dat
dat = siteComparison.all.datasets
dat$dataset = revalue(dat$dataset, c("strong" = "mut+sel"))

## dat with means and standard errors
d = ddply(dat,c("dataset","site","AA","shell"), function(x) {
                mean.z.RSD = mean(x$z.RSD, na.rm = T)
                ndata = sum(!is.na(x$z.RSD))
                se.z.RSD = sd(x$z.RSD, na.rm = T) / sqrt(ndata)
                data.frame(mean.z.RSD, ndata, se.z.RSD)
})

## comparison of means with the minimum distance to the functional sites
z.RSD.exp = d$mean.z.RSD[d$dataset == "exp"]
z.RSD.strong = d$mean.z.RSD[d$dataset == "mut+sel"]
z.RSD.mut = d$mean.z.RSD[d$dataset == "mut"]

plot(y = z.RSD.exp - z.RSD.mut, x = m.min.da.CM.ca$min.da.ca, xlab = "minimal distance to active site (between CAs)")
plot(y = z.RSD.exp - z.RSD.mut, x = m.min.da.CM.ca$min.da.CM, xlab = "minimal distance to active site (between CMs)")

r.min.da.CA = cor((z.RSD.exp - z.RSD.mut), m.min.da.CM.ca$min.da.ca)
r.min.da.CM = cor((z.RSD.exp - z.RSD.mut), m.min.da.CM.ca$min.da.CM)

cor.df = data.frame("comparison" = c("(exp - mut) vs min.da.CA", "(exp - mut) vs min.da.CM"),
                    "R" = c(r.min.da.CA, r.min.da.CM)) 
knitr::kable(cor.df, digits = 2)

## find active sites
d$label = as.character(d$site)
active.sites = d$site[d$shell == 0]

## start with a print of smoothed profiles
plot(smooth(z.RSD.exp), col = "blue", type = "l")
lines(smooth(z.RSD.strong), col = "red")
lines(smooth(z.RSD.mut), col = "green")
abline(v = active.sites, col = "grey")

## plot mean profiles with deviations
p = ggplot(d,aes(x = site, y = mean.z.RSD, col = dataset, fill = dataset)) +
    geom_line() +
    geom_ribbon(aes(ymin = mean.z.RSD - f95 * se.z.RSD, ymax = mean.z.RSD + se.z.RSD), alpha = .4, show.legend = F) +
    geom_vline(xintercept = active.sites, col = "grey", show.legend = F) +
    labs(x = "site", y = "structural divergence(mean z.RSD)") +
    coord_cartesian(ylim = c(-1.5, 2.8)) +
    scale_colour_manual(name = NULL, values = myColors) + 
    scale_fill_manual(name = NULL, values = myColors)

## plot separate and comparative plots
p.facet = p + facet_grid(dataset~., switch = "y") + theme(legend.position = "none")

p.facet %+% subset(d, dataset == "exp") 
p.facet %+% subset(d, dataset == "mut")
p.facet %+% subset(d, dataset == "mut+sel") 
p.facet

## p + theme(legend.position = "bottom", legend.title = element_blank())
p + theme(legend.position = "bottom")

```

```{r mean-n-RSD-vs-site}
# comparison of n.RSD profiles with functional sites

## prepare dat
dat = siteComparison.all.datasets
dat$dataset = revalue(dat$dataset, c("strong" = "mut+sel"))

## dat with means and standard errors
d = ddply(dat,c("dataset","site","AA","shell"), function(x) {
                mean.n.RSD = mean(x$n.RSD, na.rm = T)
                ndata = sum(!is.na(x$n.RSD))
                se.n.RSD = sd(x$n.RSD, na.rm = T) / sqrt(ndata)
                data.frame(mean.n.RSD, ndata, se.n.RSD)
})

## comparison of means with the minimum distance to the functional sites
n.RSD.exp = d$mean.n.RSD[d$dataset == "exp"]
n.RSD.strong = d$mean.n.RSD[d$dataset == "mut+sel"]
n.RSD.mut = d$mean.n.RSD[d$dataset == "mut"]

plot(y = n.RSD.exp - n.RSD.mut, x = m.min.da.CM.ca$min.da.ca, xlab = "minimal distance to active site (between CAs)")
plot(y = n.RSD.exp - n.RSD.mut, x = m.min.da.CM.ca$min.da.CM, xlab = "minimal distance to active site (between CMs)")

r.min.da.CA = cor((n.RSD.exp - n.RSD.mut), m.min.da.CM.ca$min.da.ca)
r.min.da.CM = cor((n.RSD.exp - n.RSD.mut), m.min.da.CM.ca$min.da.CM)

cor.df = data.frame("comparison" = c("(exp - mut) vs min.da.CA", "(exp - mut) vs min.da.CM"),
                    "R" = c(r.min.da.CA, r.min.da.CM)) 
knitr::kable(cor.df, digits = 2)

## start with a print of smoothed profiles
plot(smooth(n.RSD.exp), col = "blue", type = "l")
lines(smooth(n.RSD.strong), col = "red")
lines(smooth(n.RSD.mut), col = "green")
abline(v = active.sites)

## plot mean profiles with deviations
p = ggplot(d,aes(x = site, y = mean.n.RSD, col = dataset, fill = dataset)) +
    geom_line() +
    geom_ribbon(aes(ymin = mean.n.RSD - f95 * se.n.RSD, ymax = mean.n.RSD + se.n.RSD), alpha = .4, show.legend = F) +
    geom_vline(xintercept = active.sites, col = "grey", show.legend = F) +
    labs(x = "site", y = "structural divergence(mean n.RSD)") +
    coord_cartesian(ylim = c(-1.5, 2.8)) +
    scale_colour_manual(name = NULL, values = myColors) + 
    scale_fill_manual(name = NULL, values = myColors)

## plot separate and comparative plots
p.facet = p + facet_grid(dataset~., switch = "y") + theme(legend.position = "none")

p.facet %+% subset(d, dataset == "exp") 
p.facet %+% subset(d, dataset == "mut")
p.facet %+% subset(d, dataset == "mut+sel") 
p.facet

## p + theme(legend.position = "bottom", legend.title = element_blank())
p + theme(legend.position = "bottom")

```

### Correlation between site profiles

```{r}
# z-score
dat = siteComparison.all.datasets

## dat with means and standard errors
dat = ddply(dat,c("dataset", "site", "AA", "shell"), function(x) {
                mean.z.RSD = mean(x$z.RSD, na.rm = T)
                ndata = sum(!is.na(x$z.RSD))
                se.z.RSD = sd(x$z.RSD, na.rm = T) / sqrt(ndata)
                data.frame(mean.z.RSD, ndata, se.z.RSD)
})

dat.exp = subset(dat, dataset == "exp")
dat.mut = subset(dat, dataset == "mut")
dat.strong = subset(dat, dataset == "strong")

ggplot(dat, aes(x = site, y = mean.z.RSD, col = dataset)) + geom_line() +
    geom_text(data = subset(dat, dataset == "exp" & mean.z.RSD < -.5), aes(x = site, y = mean.z.RSD, label = site), nudge_y = -.1, size = 1.8)+
    geom_vline(xintercept = active.sites, col = "grey", show.legend = F)

## calculate correlations
r.exp.mut = cor(dat.exp$mean.z.RSD, dat.mut$mean.z.RSD)
r.exp.strong = cor(dat.exp$mean.z.RSD, dat.strong$mean.z.RSD)
r.mut.strong = cor(dat.mut$mean.z.RSD, dat.strong$mean.z.RSD)
cor.df = data.frame("comparison" = c("exp vs mut", "exp vs strong", "mut vs strong"),
                    "R" = c(r.exp.mut, r.exp.strong, r.mut.strong))
knitr::kable(cor.df, digits = 2)

# norm
dat = siteComparison.all.datasets

## dat with means and standard errors
dat = ddply(dat,c("dataset", "site", "AA", "shell"), function(x) {
                mean.n.RSD = mean(x$n.RSD, na.rm = T)
                ndata = sum(!is.na(x$n.RSD))
                se.n.RSD = sd(x$n.RSD, na.rm = T) / sqrt(ndata)
                data.frame(mean.n.RSD, ndata, se.n.RSD)
})

dat.exp = subset(dat, dataset == "exp")
dat.mut = subset(dat, dataset == "mut")
dat.strong = subset(dat, dataset == "strong")

ggplot(dat, aes(x = site, y = mean.n.RSD, col = dataset)) + geom_line() +
    geom_text(data = subset(dat, dataset == "exp" & mean.n.RSD < -.5), aes(x = site, y = mean.n.RSD, label = site), nudge_y = -.1, size = 1.8)+
    geom_vline(xintercept = active.sites, col = "grey", show.legend = F)

## calculate correlations
r.exp.mut = cor(dat.exp$mean.n.RSD, dat.mut$mean.n.RSD)
r.exp.strong = cor(dat.exp$mean.n.RSD, dat.strong$mean.n.RSD)
r.mut.strong = cor(dat.mut$mean.n.RSD, dat.strong$mean.n.RSD)
cor.df = data.frame("comparison" = c("exp vs mut", "exp vs strong", "mut vs strong"),
                    "R" = c(r.exp.mut, r.exp.strong, r.mut.strong))
knitr::kable(cor.df, digits = 2)
```

### 2016-11-04 analysis-structure-local-enviroment3.Rmd
cambios 04/11/16

---
title: "Structural Divergence Analysis"
author: "Maria Laura Marcos, Julian Echave"
output: html_document
---

# Introduction
We study the evolutionary divergence of proteins using the LF-ENM and comparing simulated mutants with experimental data.

```{r setup, include = FALSE}
# set chunk options
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r load_packages}
# load packages
library(ggplot2)
library(reshape2)
library(plyr)
library(quantreg)
library(bio3d)

# load functions
source(file.path(data.dir, "multiplot.R"))
source(file.path(data.dir, "my-functions.R")) 
```

```{r set_my_colors}
# set my colors
myColors = c("blue", "darkgreen", "red", "red") 
names(myColors) <- c("exp", "mut", "strong", "mut+sel")
```

```{r set_run_variables}
# set significance factors
f95 = 1.96
f99 = 2.6
f999 = 3.3
```

```{r set_file_names}
# set input filenames
## data
reference.fname = file.path(data.dir, paste(family, "_ref.txt", sep = ""))
protein_list.fname = file.path(data.dir, paste(family, "_list.txt", sep = ""))
site.info.fname = file.path(data.dir, paste(p.ref, "_m.da.ca.csv", sep = ""))
min.da.CM.CA.fname = file.path(data.dir, paste(p.ref, "_min.da.CM.ca.csv", sep = ""))

## profiles to compare
local.score.exp.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.exp.local.score.csv", sep = ""))
local.score.strong.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_strong.sel_K.analysis_Keff_out_m.theo.local.score.csv", sep = ""))
local.score.mut.fname = file.path(data.dir,paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.local.score.csv", sep = ""))
```

```{r set_reference_protein}
# which is the reference protein?
reference = as.character(read.table(reference.fname, header = F)[1, 1])
if (reference != p.ref) {
  print("Warning: different references")
}
```

We studied the `r family` family. 
We used the ENM `r enm` with R0 = `r R0` to generate mutants.
We used as reference for the ENM the protein with pdb code `r reference`. 
We simulated `r n.mut.p` mutants of this reference for each protein of the family.
The `r family` family is of the type `r type` and consists of the following proteins:

```{r set_experimental_protein_names, comment = ""}
# experimental protein names
protein.exp = read.table(protein_list.fname, header = F, stringsAsFactors = F)[, 1]
protein.exp = protein.exp[protein.exp != reference]
print(protein.exp)
```

```{r set_site_info}
# read site information of the reference protein
site.info = read.csv(site.info.fname, header = T, sep = ",")
m.min.da.CM.CA = read.csv(min.da.CM.CA.fname)

# add info to site.info
d = ddply(site.info, "site", .fun = function(x) data.frame("da" = min(x[, c(-1, -2)])))

# define shells of active site neighborhood
d$shell = cut(d$da, breaks = c(-.1, 2.5, 7.5, 12.5, 17.5, 22.5, 27.5, 32.5, 37.5, 42.5, 47.5, 52.5, max(d$da)))
levels(d$shell) = seq(length(levels(d$shell))) - 1 # rename shell levels
site.info = merge(site.info, d, by = "site")

# read reference pdb and calculate resno, AA, and CN
reference.pdb.fname = file.path(data.dir,paste(reference, ".pdb", sep = ""))
ref.pdb = read.pdb(reference.pdb.fname)
inds = atom.select(ref.pdb, elety = "CA")
ref.pdb.ca = ref.pdb$atom[inds$atom,]
cmap.ca = cmap(ref.pdb$xyz[inds$xyz], dcut = R0, scut = 0, mask.lower = F)
CN = rowSums(cmap.ca, na.rm = T) - 1 # diag(cmap.ca) returned by cmap is 1!
AA = ref.pdb.ca$resid
resno = ref.pdb.ca$resno
pdb.info = data.frame(resno, AA, CN)
names(pdb.info) = c("resno", "AA", paste("CN", as.character(R0), sep = ""))

# add pdb.info to site.info
site.info = cbind(site.info, pdb.info)
```

```{r read_data}
# read data
## exp
local.score.exp = read.csv(local.score.exp.fname, header = T)
site = site.info$site
local.score.exp = local.score.exp[1:length(protein.exp), site]
rownames(local.score.exp) = protein.exp

## mut
local.score.mut = read.csv(local.score.mut.fname, header = T)
site = site.info$site
local.score.mut = local.score.mut[1:length(protein.exp), site]
rownames(local.score.mut) = paste("mut", rownames(local.score.mut), sep = "")

## strong
local.score.strong = read.csv(local.score.strong.fname, header = T)
site = site.info$site
local.score.strong = local.score.strong[1:length(protein.exp), site]
rownames(local.score.strong) = paste("strong", rownames(local.score.strong), sep = "")
```

# Structural divergence along sites

Here we study how structural divergence varies from site to site. We compare simulated data with empirical data.

```{r prepare_site_data}
# prepare the data
## exp
tlocal.score.exp = as.data.frame(t(as.matrix(local.score.exp)))
tlocal.score.exp = cbind(site.info, tlocal.score.exp)
siteComparison.exp = melt(tlocal.score.exp, id.vars = names(site.info), variable.name = "protein", value.name = "local.score")

## mut
tlocal.score.mut = as.data.frame(t(as.matrix(local.score.mut)))
tlocal.score.mut = cbind(site.info, tlocal.score.mut)
siteComparison.mut = melt(tlocal.score.mut, id.vars = names(site.info), variable.name = "protein", value.name = "local.score")

## strong
tlocal.score.strong = as.data.frame(t(as.matrix(local.score.strong)))
tlocal.score.strong = cbind(site.info, tlocal.score.strong)
siteComparison.strong = melt(tlocal.score.strong, id.vars = names(site.info), variable.name = "protein", value.name = "local.score")

# bluild the data.frame
siteComparison.all.datasets = rbind(data.frame("dataset" = "exp", siteComparison.exp),
                                    data.frame("dataset" = "mut", siteComparison.mut),
                                    data.frame("dataset" = "strong", siteComparison.strong))

siteComparison.all.datasets = ddply(siteComparison.all.datasets, c("dataset", "protein"), mutate,
          "local.score" = (local.score), 
          "n.local.score" = local.score/mean(local.score, na.rm = T),
          "z.local.score" = vscale(local.score))
```

### Mean z.local.score vs site

To measure structural divergence we use z.local.score profiles, which are the best for most families.

The following plot compares the mean z.local.score profiles, including standard errors (with .999 confidence level for the mean)
*Warning: the effective number of data should be smaller than the actual data, especially for the experimental dataset because of several factors. We need to deal with this for quantitative analysis. Probably we'll need to use bootstrapping to calculate standard errors non-parametrically*

```{r mean_se_z.local.score_vs_site, fig.cap = "Black lines are the active sites and grey lines are their contacts"}
# comparison of z.local.score profiles with functional sites
## prepare dat
dat = siteComparison.all.datasets
dat$dataset = revalue(dat$dataset, c("strong" = "mut+sel"))

## dat with means and standard errors
d = ddply(dat,c("dataset", "site", "AA", "shell"), function(x) {
                mean.z.local.score = mean(x$z.local.score, na.rm = T)
                ndata = sum(!is.na(x$z.local.score))
                se.z.local.score = sd(x$z.local.score, na.rm = T) / sqrt(ndata)
                data.frame(mean.z.local.score, ndata, se.z.local.score)
})

## find the active site and its contacts
active.sites = d$site[d$shell == 0]
contacts.active.sites = d$site[d$shell == 1]

## prepare plots with mean profiles and deviations
p = ggplot(d, aes(x = site, y = mean.z.local.score, col = dataset, fill = dataset)) +
    geom_line() +
    geom_ribbon(aes(ymin = mean.z.local.score - f95 * se.z.local.score, ymax = mean.z.local.score + se.z.local.score), alpha = .4, show.legend = F) +
    geom_vline(xintercept = active.sites, show.legend = F) +
    geom_vline(xintercept = contacts.active.sites, col = "grey", show.legend = F) +
    labs(x = "site", y = "structural divergence(mean z.local.score)") +
    coord_cartesian(ylim = c(-1.5, 2.8)) +
    scale_colour_manual(name = NULL, values = myColors) + 
    scale_fill_manual(name = NULL, values = myColors)

## plot separate and comparative plots
p.facet = p + facet_grid(dataset~., switch = "y") + theme(legend.position = "bottom")

p.facet %+% subset(d, dataset == "exp") 
p.facet %+% subset(d, dataset == "mut")
p.facet %+% subset(d, dataset == "mut+sel") 
p.facet

## plot superimposed plots
p + theme(legend.position = "bottom")
```

### Correlation between site profiles

```{r_comparison_mean_z.local.score_vs_site, fig.cap = "Black lines are the active sites and grey lines are their contacts"}
# comparison of z.local.score profiles
ggplot(d, aes(x = site, y = mean.z.local.score, col = dataset)) +
  geom_line() +
  geom_text(data = subset(d, dataset == "exp" & mean.z.local.score < -.5), aes(x = site, y = mean.z.local.score, label = site), nudge_y = -.1, size = 1.8)+
  geom_vline(xintercept = active.sites, show.legend = F) +
  geom_vline(xintercept = contacts.active.sites, col = "grey", show.legend = F) + 
  scale_colour_manual(name = NULL, values = myColors)

# calculate correlations berween profiles
d.exp = subset(d, dataset == "exp")
d.mut = subset(d, dataset == "mut")
d.strong = subset(d, dataset == "mut+sel")

r.exp.mut = cor(d.exp$mean.z.local.score, d.mut$mean.z.local.score)
r.exp.strong = cor(d.exp$mean.z.local.score, d.strong$mean.z.local.score)
r.mut.strong = cor(d.mut$mean.z.local.score, d.strong$mean.z.local.score)

cor.df = data.frame("comparison" = c("exp vs mut", "exp vs strong", "mut vs strong"),
                    "R" = c(r.exp.mut, r.exp.strong, r.mut.strong))

knitr::kable(cor.df, digits = 2, caption = "Correlation between <Z-scores> profiles")
```

### Distances to the active sites

```{r_comparison_da}

# comparison of means.z.scores with the minimum distance to the functional sites
plot(y = d.exp$mean.z.local.score - d.mut$mean.z.local.score, x = m.min.da.CM.CA$min.da.ca, xlab = "minimal distance to active site (between CAs)", ylab = "exp.mean.z.local.score - mut.mean.z.local.score")
plot(y = d.exp$mean.z.local.score - d.mut$mean.z.local.score, x = m.min.da.CM.CA$min.da.CM, xlab = "minimal distance to active site (between CMs)", ylab = "exp.mean.z.local.score - mut.mean.z.local.score")

## calculate correlations between profiles
r.min.da.CA = cor((d.exp$mean.z.local.score - d.mut$mean.z.local.score), m.min.da.CM.CA$min.da.ca)
r.min.da.CM = cor((d.exp$mean.z.local.score - d.mut$mean.z.local.score), m.min.da.CM.CA$min.da.CM)

cor.df = data.frame("comparison" = c("(exp - mut) vs min.da.CA", "(exp - mut) vs min.da.CM"), "R" = c(r.min.da.CA, r.min.da.CM))

knitr::kable(cor.df, digits = 2, caption = "Correlation between differences in <Z-scores> profiles and the minimal distance to the active site")
```

### 2016-11-04 analysis-structure-window.Rmd
cambios 04/11/16

--- 2016-11-04 analysis-structure-local-enviroment.Rmd
@@
 
-dri2.exp.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.exp.sum.dif.dist.csv", sep = ""))
+dri2.exp.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.exp.norm.dr.squarei.windows.rot.csv", sep = ""))
 
-dri2.strong.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_strong.sel_K.analysis_Keff_out_m.theo.sum.dif.dist.csv", sep = "")) #cambiar
+dri2.strong.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_strong.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.windows.rot.csv", sep = "")) #cambiar
 
-dri2.mut.fname = file.path(data.dir,paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.sum.dif.dist.csv", sep = ""))
+dri2.mut.fname = file.path(data.dir,paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.windows.rot.csv", sep = ""))
 ```
@@
           "z.SD" = vscale(dri2),
-          "RSD" = (dri2),
+          "RSD" = sqrt(dri2), 
           "n.RSD" = RSD/mean(RSD, na.rm = T),

### 2016-11-04 analysis-structure-window2.Rmd
cambios 04/11/16

--- 2016-11-04 analysis-structure-window.Rmd
@@
 
+## find active sites
+d$label = as.character(d$site)
+active.sites = d$site[d$shell == 0]
+contacts.active.sites = d$site[d$shell == 1]
+
+## prepare plots with mean profiles and deviations
+p = ggplot(d,aes(x = site, y = mean.z.RSD, col = dataset, fill = dataset)) +
+    geom_line() +
+    geom_ribbon(aes(ymin = mean.z.RSD - f95 * se.z.RSD, ymax = mean.z.RSD + se.z.RSD), alpha = .4, show.legend = F) +
+    geom_vline(xintercept = active.sites, show.legend = F) +
+    labs(x = "site", y = "structural divergence(mean z.RSD)") +
+    coord_cartesian(ylim = c(-1.5, 2.8)) +
+    scale_colour_manual(name = NULL, values = myColors) + 
+    scale_fill_manual(name = NULL, values = myColors)
+
+## plot separate and comparative plots
+p.facet = p + facet_grid(dataset~., switch = "y") + theme(legend.position = "none")
+
+p.facet %+% subset(d, dataset == "exp") 
+p.facet %+% subset(d, dataset == "mut")
+p.facet %+% subset(d, dataset == "mut+sel") 
+p.facet
+
+## plot superimposed plots
+p + theme(legend.position = "bottom")
+
 ## comparison of means with the minimum distance to the functional sites
@@
 knitr::kable(cor.df, digits = 2)
-
-## find active sites
-d$label = as.character(d$site)
-active.sites = d$site[d$shell == 0]
-
-## start with a print of smoothed profiles
-plot(smooth(z.RSD.exp), col = "blue", type = "l")
-lines(smooth(z.RSD.strong), col = "red")
-lines(smooth(z.RSD.mut), col = "green")
-abline(v = active.sites, col = "grey")
-
-## plot mean profiles with deviations
-p = ggplot(d,aes(x = site, y = mean.z.RSD, col = dataset, fill = dataset)) +
-    geom_line() +
-    geom_ribbon(aes(ymin = mean.z.RSD - f95 * se.z.RSD, ymax = mean.z.RSD + se.z.RSD), alpha = .4, show.legend = F) +
-    geom_vline(xintercept = active.sites, col = "grey", show.legend = F) +
-    labs(x = "site", y = "structural divergence(mean z.RSD)") +
-    coord_cartesian(ylim = c(-1.5, 2.8)) +
-    scale_colour_manual(name = NULL, values = myColors) + 
-    scale_fill_manual(name = NULL, values = myColors)
-
-## plot separate and comparative plots
-p.facet = p + facet_grid(dataset~., switch = "y") + theme(legend.position = "none")
-
-p.facet %+% subset(d, dataset == "exp") 
-p.facet %+% subset(d, dataset == "mut")
-p.facet %+% subset(d, dataset == "mut+sel") 
-p.facet
-
-## p + theme(legend.position = "bottom", legend.title = element_blank())
-p + theme(legend.position = "bottom")
-
-```
-
-```{r mean-n-RSD-vs-site}
-# comparison of n.RSD profiles with functional sites
-
-## prepare dat
-dat = siteComparison.all.datasets
-dat$dataset = revalue(dat$dataset, c("strong" = "mut+sel"))
-
-## dat with means and standard errors
-d = ddply(dat,c("dataset","site","AA","shell"), function(x) {
-                mean.n.RSD = mean(x$n.RSD, na.rm = T)
-                ndata = sum(!is.na(x$n.RSD))
-                se.n.RSD = sd(x$n.RSD, na.rm = T) / sqrt(ndata)
-                data.frame(mean.n.RSD, ndata, se.n.RSD)
-})
-
-## comparison of means with the minimum distance to the functional sites
-n.RSD.exp = d$mean.n.RSD[d$dataset == "exp"]
-n.RSD.strong = d$mean.n.RSD[d$dataset == "mut+sel"]
-n.RSD.mut = d$mean.n.RSD[d$dataset == "mut"]
-
-plot(y = n.RSD.exp - n.RSD.mut, x = m.min.da.CM.ca$min.da.ca, xlab = "minimal distance to active site (between CAs)")
-plot(y = n.RSD.exp - n.RSD.mut, x = m.min.da.CM.ca$min.da.CM, xlab = "minimal distance to active site (between CMs)")
-
-r.min.da.CA = cor((n.RSD.exp - n.RSD.mut), m.min.da.CM.ca$min.da.ca)
-r.min.da.CM = cor((n.RSD.exp - n.RSD.mut), m.min.da.CM.ca$min.da.CM)
-
-cor.df = data.frame("comparison" = c("(exp - mut) vs min.da.CA", "(exp - mut) vs min.da.CM"),
-                    "R" = c(r.min.da.CA, r.min.da.CM)) 
-knitr::kable(cor.df, digits = 2)
-
-## start with a print of smoothed profiles
-plot(smooth(n.RSD.exp), col = "blue", type = "l")
-lines(smooth(n.RSD.strong), col = "red")
-lines(smooth(n.RSD.mut), col = "green")
-abline(v = active.sites)
-
-## plot mean profiles with deviations
-p = ggplot(d,aes(x = site, y = mean.n.RSD, col = dataset, fill = dataset)) +
-    geom_line() +
-    geom_ribbon(aes(ymin = mean.n.RSD - f95 * se.n.RSD, ymax = mean.n.RSD + se.n.RSD), alpha = .4, show.legend = F) +
-    geom_vline(xintercept = active.sites, col = "grey", show.legend = F) +
-    labs(x = "site", y = "structural divergence(mean n.RSD)") +
-    coord_cartesian(ylim = c(-1.5, 2.8)) +
-    scale_colour_manual(name = NULL, values = myColors) + 
-    scale_fill_manual(name = NULL, values = myColors)
-
-## plot separate and comparative plots
-p.facet = p + facet_grid(dataset~., switch = "y") + theme(legend.position = "none")
-
-p.facet %+% subset(d, dataset == "exp") 
-p.facet %+% subset(d, dataset == "mut")
-p.facet %+% subset(d, dataset == "mut+sel") 
-p.facet
-
-## p + theme(legend.position = "bottom", legend.title = element_blank())
-p + theme(legend.position = "bottom")
-
 ```
@@
     geom_text(data = subset(dat, dataset == "exp" & mean.z.RSD < -.5), aes(x = site, y = mean.z.RSD, label = site), nudge_y = -.1, size = 1.8)+
-    geom_vline(xintercept = active.sites, col = "grey", show.legend = F)
+    geom_vline(xintercept = active.sites, col = "grey", show.legend = F) +
+    geom_vline(xintercept = contacts.active.sites, col = "black", show.legend = F)
 
@@
 knitr::kable(cor.df, digits = 2)
-
-# norm
-dat = siteComparison.all.datasets
-
-## dat with means and standard errors
-dat = ddply(dat,c("dataset", "site", "AA", "shell"), function(x) {
-                mean.n.RSD = mean(x$n.RSD, na.rm = T)
-                ndata = sum(!is.na(x$n.RSD))
-                se.n.RSD = sd(x$n.RSD, na.rm = T) / sqrt(ndata)
-                data.frame(mean.n.RSD, ndata, se.n.RSD)
-})
-
-dat.exp = subset(dat, dataset == "exp")
-dat.mut = subset(dat, dataset == "mut")
-dat.strong = subset(dat, dataset == "strong")
-
-ggplot(dat, aes(x = site, y = mean.n.RSD, col = dataset)) + geom_line() +
-    geom_text(data = subset(dat, dataset == "exp" & mean.n.RSD < -.5), aes(x = site, y = mean.n.RSD, label = site), nudge_y = -.1, size = 1.8)+
-    geom_vline(xintercept = active.sites, col = "grey", show.legend = F)
-
-## calculate correlations
-r.exp.mut = cor(dat.exp$mean.n.RSD, dat.mut$mean.n.RSD)
-r.exp.strong = cor(dat.exp$mean.n.RSD, dat.strong$mean.n.RSD)
-r.mut.strong = cor(dat.mut$mean.n.RSD, dat.strong$mean.n.RSD)
-cor.df = data.frame("comparison" = c("exp vs mut", "exp vs strong", "mut vs strong"),
-                    "R" = c(r.exp.mut, r.exp.strong, r.mut.strong))
-knitr::kable(cor.df, digits = 2)
 ```

### 2016-11-04 analysis-structure-window3.Rmd
cambios 04/11/16

--- 2016-11-04 analysis-structure-local-enviroment3.Rmd
@@
 ## profiles to compare
-local.score.exp.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.exp.local.score.csv", sep = ""))
-local.score.strong.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_strong.sel_K.analysis_Keff_out_m.theo.local.score.csv", sep = ""))
-local.score.mut.fname = file.path(data.dir,paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.local.score.csv", sep = ""))
+dri2.exp.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.exp.norm.dr.squarei.windows.rot.csv", sep = ""))
+dri2.strong.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_strong.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.windows.rot.csv", sep = ""))
+dri2.mut.fname = file.path(data.dir,paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.windows.rot.csv", sep = ""))
 ```
@@
 ## exp
-local.score.exp = read.csv(local.score.exp.fname, header = T)
+dri2.exp = read.csv(dri2.exp.fname, header = T)
 site = site.info$site
-local.score.exp = local.score.exp[1:length(protein.exp), site]
-rownames(local.score.exp) = protein.exp
+dri2.exp = dri2.exp[1:length(protein.exp), site]
+rownames(dri2.exp) = protein.exp
 
 ## mut
-local.score.mut = read.csv(local.score.mut.fname, header = T)
+dri2.mut = read.csv(dri2.mut.fname, header = T)
 site = site.info$site
-local.score.mut = local.score.mut[1:length(protein.exp), site]
-rownames(local.score.mut) = paste("mut", rownames(local.score.mut), sep = "")
+dri2.mut = dri2.mut[1:length(protein.exp), site]
+rownames(dri2.mut) = paste("mut", rownames(dri2.mut), sep = "")
 
 ## strong
-local.score.strong = read.csv(local.score.strong.fname, header = T)
+dri2.strong = read.csv(dri2.strong.fname, header = T)
 site = site.info$site
-local.score.strong = local.score.strong[1:length(protein.exp), site]
-rownames(local.score.strong) = paste("strong", rownames(local.score.strong), sep = "")
+dri2.strong = dri2.strong[1:length(protein.exp), site]
+rownames(dri2.strong) = paste("strong", rownames(dri2.strong), sep = "")
 ```
@@
 ## exp
-tlocal.score.exp = as.data.frame(t(as.matrix(local.score.exp)))
-tlocal.score.exp = cbind(site.info, tlocal.score.exp)
-siteComparison.exp = melt(tlocal.score.exp, id.vars = names(site.info), variable.name = "protein", value.name = "local.score")
+tdri2.exp = as.data.frame(t(as.matrix(dri2.exp)))
+tdri2.exp = cbind(site.info, tdri2.exp)
+siteComparison.exp = melt(tdri2.exp, id.vars = names(site.info), variable.name = "protein", value.name = "dri2")
 
 ## mut
-tlocal.score.mut = as.data.frame(t(as.matrix(local.score.mut)))
-tlocal.score.mut = cbind(site.info, tlocal.score.mut)
-siteComparison.mut = melt(tlocal.score.mut, id.vars = names(site.info), variable.name = "protein", value.name = "local.score")
+tdri2.mut = as.data.frame(t(as.matrix(dri2.mut)))
+tdri2.mut = cbind(site.info, tdri2.mut)
+siteComparison.mut = melt(tdri2.mut, id.vars = names(site.info), variable.name = "protein", value.name = "dri2")
 
 ## strong
-tlocal.score.strong = as.data.frame(t(as.matrix(local.score.strong)))
-tlocal.score.strong = cbind(site.info, tlocal.score.strong)
-siteComparison.strong = melt(tlocal.score.strong, id.vars = names(site.info), variable.name = "protein", value.name = "local.score")
+tdri2.strong = as.data.frame(t(as.matrix(dri2.strong)))
+tdri2.strong = cbind(site.info, tdri2.strong)
+siteComparison.strong = melt(tdri2.strong, id.vars = names(site.info), variable.name = "protein", value.name = "dri2")
 
@@
 siteComparison.all.datasets = ddply(siteComparison.all.datasets, c("dataset", "protein"), mutate,
-          "local.score" = (local.score), 
-          "n.local.score" = local.score/mean(local.score, na.rm = T),
-          "z.local.score" = vscale(local.score))
+          "n.SD" = dri2/mean(dri2, na.rm = T),
+          "z.SD" = vscale(dri2),
+          "RSD" = sqrt(dri2), 
+          "n.RSD" = RSD/mean(RSD, na.rm = T),
+          "z.RSD" = vscale(RSD))
 ```
 
-### Mean z.local.score vs site
+### Mean z.RSD vs site
 
-To measure structural divergence we use z.local.score profiles, which are the best for most families.
+To measure structural divergence we use z.RSD profiles, which are the best for most families.
 
-The following plot compares the mean z.local.score profiles, including standard errors (with .999 confidence level for the mean)
+The following plot compares the mean z.RSD profiles, including standard errors (with .999 confidence level for the mean)
 *Warning: the effective number of data should be smaller than the actual data, especially for the experimental dataset because of several factors.
@@
 
-```{r mean_se_z.local.score_vs_site, fig.cap = "Black lines are the active sites and grey lines are their contacts"}
-# comparison of z.local.score profiles with functional sites
+```{r mean_se_z.RSD_vs_site, fig.cap = "Black lines are the active sites and grey lines are their contacts"}
+# comparison of z.RSD profiles with functional sites
 ## prepare dat
@@
 d = ddply(dat,c("dataset", "site", "AA", "shell"), function(x) {
-                mean.z.local.score = mean(x$z.local.score, na.rm = T)
-                ndata = sum(!is.na(x$z.local.score))
-                se.z.local.score = sd(x$z.local.score, na.rm = T) / sqrt(ndata)
-                data.frame(mean.z.local.score, ndata, se.z.local.score)
+                mean.z.RSD = mean(x$z.RSD, na.rm = T)
+                ndata = sum(!is.na(x$z.RSD))
+                se.z.RSD = sd(x$z.RSD, na.rm = T) / sqrt(ndata)
+                data.frame(mean.z.RSD, ndata, se.z.RSD)
 })
@@
 ## prepare plots with mean profiles and deviations
-p = ggplot(d, aes(x = site, y = mean.z.local.score, col = dataset, fill = dataset)) +
+p = ggplot(d, aes(x = site, y = mean.z.RSD, col = dataset, fill = dataset)) +
     geom_line() +
-    geom_ribbon(aes(ymin = mean.z.local.score - f95 * se.z.local.score, ymax = mean.z.local.score + se.z.local.score), alpha = .4, show.legend = F) +
+    geom_ribbon(aes(ymin = mean.z.RSD - f95 * se.z.RSD, ymax = mean.z.RSD + se.z.RSD), alpha = .4, show.legend = F) +
     geom_vline(xintercept = active.sites, show.legend = F) +
     geom_vline(xintercept = contacts.active.sites, col = "grey", show.legend = F) +
-    labs(x = "site", y = "structural divergence(mean z.local.score)") +
+    labs(x = "site", y = "structural divergence(mean z.RSD)") +
     coord_cartesian(ylim = c(-1.5, 2.8)) +
@@
 
-```{r_comparison_mean_z.local.score_vs_site, fig.cap = "Black lines are the active sites and grey lines are their contacts"}
-# comparison of z.local.score profiles
-ggplot(d, aes(x = site, y = mean.z.local.score, col = dataset)) +
+```{r_comparison_mean_z.RSD_vs_site, fig.cap = "Black lines are the active sites and grey lines are their contacts"}
+# comparison of z.RSD profiles
+ggplot(d, aes(x = site, y = mean.z.RSD, col = dataset)) +
   geom_line() +
-  geom_text(data = subset(d, dataset == "exp" & mean.z.local.score < -.5), aes(x = site, y = mean.z.local.score, label = site), nudge_y = -.1, size = 1.8)+
+  geom_text(data = subset(d, dataset == "exp" & mean.z.RSD < -.5), aes(x = site, y = mean.z.RSD, label = site), nudge_y = -.1, size = 1.8)+
   geom_vline(xintercept = active.sites, show.legend = F) +
@@
 
-r.exp.mut = cor(d.exp$mean.z.local.score, d.mut$mean.z.local.score)
-r.exp.strong = cor(d.exp$mean.z.local.score, d.strong$mean.z.local.score)
-r.mut.strong = cor(d.mut$mean.z.local.score, d.strong$mean.z.local.score)
+r.exp.mut = cor(d.exp$mean.z.RSD, d.mut$mean.z.RSD)
+r.exp.strong = cor(d.exp$mean.z.RSD, d.strong$mean.z.RSD)
+r.mut.strong = cor(d.mut$mean.z.RSD, d.strong$mean.z.RSD)
 
@@
 # comparison of means.z.scores with the minimum distance to the functional sites
-plot(y = d.exp$mean.z.local.score - d.mut$mean.z.local.score, x = m.min.da.CM.CA$min.da.ca, xlab = "minimal distance to active site (between CAs)", ylab = "exp.mean.z.local.score - mut.mean.z.local.score")
-plot(y = d.exp$mean.z.local.score - d.mut$mean.z.local.score, x = m.min.da.CM.CA$min.da.CM, xlab = "minimal distance to active site (between CMs)", ylab = "exp.mean.z.local.score - mut.mean.z.local.score")
+plot(y = d.exp$mean.z.RSD - d.mut$mean.z.RSD, x = m.min.da.CM.CA$min.da.ca, xlab = "minimal distance to active site (between CAs)", ylab = "exp.mean.z.RSD - mut.mean.z.RSD")
+plot(y = d.exp$mean.z.RSD - d.mut$mean.z.RSD, x = m.min.da.CM.CA$min.da.CM, xlab = "minimal distance to active site (between CMs)", ylab = "exp.mean.z.RSD - mut.mean.z.RSD")
 
 ## calculate correlations between profiles
-r.min.da.CA = cor((d.exp$mean.z.local.score - d.mut$mean.z.local.score), m.min.da.CM.CA$min.da.ca)
-r.min.da.CM = cor((d.exp$mean.z.local.score - d.mut$mean.z.local.score), m.min.da.CM.CA$min.da.CM)
+r.min.da.CA = cor((d.exp$mean.z.RSD - d.mut$mean.z.RSD), m.min.da.CM.CA$min.da.ca)
+r.min.da.CM = cor((d.exp$mean.z.RSD - d.mut$mean.z.RSD), m.min.da.CM.CA$min.da.CM)
 

### 2016-11-04 analysis-structure3.Rmd
cambios 04/11/16

--- 2016-11-04 analysis-structure-window3.Rmd
@@
 ## profiles to compare
-dri2.exp.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.exp.norm.dr.squarei.windows.rot.csv", sep = ""))
-dri2.strong.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_strong.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.windows.rot.csv", sep = ""))
-dri2.mut.fname = file.path(data.dir,paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.windows.rot.csv", sep = ""))
+dri2.exp.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.exp.norm.dr.squarei.csv", sep = ""))
+dri2.strong.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_strong.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
+dri2.mut.fname = file.path(data.dir,paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
 ```

### 2016-11-04 FUNCTIONS/AnalyzeExperimentalTheoreticalCM.R

@@ -38,6 +38,7 @@
 #    CalculateVariability()
 #    CalculateENMKeff()
 #    CalculateENMK()
+#    WindowsRMSD()
 
 AnalyzeExperimentalTheoreticalCM <- function(family,
                                              p.ref,
@@ -54,7 +55,7 @@ AnalyzeExperimentalTheoreticalCM <- function(family,
                                              tolerance) {
   ### GENERAL ###
   
-  # Filenames
+  # filenames
   dataset.fname <- file.path(data.dir, paste(family, "_dataset.csv", sep = ""))
   pdb.fname <- file.path(data.dir, paste(p.ref, ".pdb", sep = "")) 
   pdbs.fname <- file.path(data.dir, paste(family, "_coordinates.pdb", sep = "")) 
@@ -65,19 +66,20 @@ AnalyzeExperimentalTheoreticalCM <- function(family,
   m.not.aligned.p.ref.index.fname <- file.path(out.dir, paste(family, "_out_m.not.aligned.p.ref.index.csv", sep = ""))
   m.not.aligned.p.2.index.fname <- file.path(out.dir, paste(family, "_out_m.not.aligned.p.2.index.csv", sep = ""))
   
-  # Read the dataset
+  # read the dataset
   dataset <- read.csv(dataset.fname)
   pdbid.dataset <- as.character(dataset$pdbid)
   chain <- as.character(dataset$chain)
   n.prot = length(pdbid.dataset)
   
   ### THEORETICAL ###
+  print("analysing theoretical...")
   
-  # Filenames
+  # filenames
   theo.r.p.ref.fname <- file.path(out.dir, paste(mut.fname.id, "_out_r.p.ref.csv", sep = ""))
   m.r.mut.fname <- file.path(out.dir, paste(mut.fname.id, "_out_m.r.mut.csv", sep = ""))
   
-  # Read coordinates
+  # read coordinates
   theo.r.p.ref = read.csv(theo.r.p.ref.fname)$x
   m.r.mut = read.csv(m.r.mut.fname)
   n.sites.p.ref = length(theo.r.p.ref)/3
@@ -89,24 +91,29 @@ AnalyzeExperimentalTheoreticalCM <- function(family,
   theo.r.p.ref = c(theo.r.p.ref, as.vector(r.CM.p.ref))
   n.sites.tot = length(theo.r.p.ref)/3
   
-  # Create matrices to save measures of variability of each mutant
[…]

### 2016-11-04 FUNCTIONS/CalculateENMKeff.R

@@ -103,10 +103,12 @@ CalculateENMKeff <- function(r,
     veKEFF = veKEFF[, modes]
     vaKEFF = vaKEFF[modes]
     n.modes = length(vaKEFF)
+    covKEFF = veKEFF %*% ((1 / vaKEFF) * t(veKEFF))
+    
   }
   
   # Create a list for the output 
-  output = list("KEFF" = KEFF, "ve" = veKEFF, "va" = vaKEFF, "n.modes" = n.modes)
+  output = list("KEFF" = KEFF, "ve" = veKEFF, "va" = vaKEFF, "n.modes" = n.modes, "covKEFF" = covKEFF)
   output
 }
 

### 2016-11-04 FUNCTIONS/MakeBlast.R

@@ -1,0 +1,32 @@
+# input
+# n.seq = 10
+# p.ref = "1a6m"
+# chain = "A"
+
+# libraries
+# bio3d
+
+# get the pdb file of coordinates of p.ref
+get.pdb(p.ref)
+
+# read the file
+pdb <- read.pdb(paste(p.ref, ".pdb", sep = ""))    
+sel <- atom.select(pdb, chain = chain, elety = "CA")    
+seq <- pdb$atom[sel$atom, c("resid")]
+
+# make a blast
+blast.info <- blast.pdb(seq, database = "pdb")
+score = blast.info$mlog.evalue
+pdbid = blast.info$pdb.id
+identity = blast.info$hit.tbl[, 3]
+
+# filter
+filter = (pdbid != p.ref)
+pdbid = pdbid[filter][1:n.seq]
+score = score[filter][1:n.seq]
+
+# align with muscle
+
+# get indeces
+
+# write output

### 2016-11-04 FUNCTIONS/WindowsRMSD.R

@@ -1,0 +1,38 @@
+WindowsRMSD <- function(length.windows,
+                        r.p.1,
+                        r.p.2,
+                        aligned.p.1.index.3N,
+                        aligned.p.2.index.3N) {
+        
+  # select aligned sites          
+  r.p.1 = r.p.1[aligned.p.1.index.3N]
+  r.p.2 = r.p.2[aligned.p.2.index.3N] 
+
+  # calculate the number of aligned sites
+  n.aligned = length(r.p.1)/3
+  
+  # calculate the number of windows and the legth of the last window)
+  n.windows = as.integer(n.aligned/length.windows)
+  resid.last.window = n.aligned - (n.windows * length.windows)
+  
+  # sart a loop to aligne each window 
+  for (i in (1:n.windows)) {
+    
+    # set resid value
+    if (i == n.windows) {
+      resid = resid.last.window
+    } else {
+      resid = 0
+    }
+    
+    index.windows.i = seq(((length.windows * i) - (length.windows - 1)), ((length.windows * i) + resid))
+    index.windows.i.3N = sort(c(index.windows.i * 3, index.windows.i * 3 - 2,  index.windows.i * 3 - 1))
+
+    r.p.2[index.windows.i.3N] = as.vector(fit.xyz(fixed = r.p.1[index.windows.i.3N],
+                                          mobile = r.p.2[index.windows.i.3N],
+                                          fixed.inds = (1:length(index.windows.i.3N)),
+                                          mobile.inds = (1:length(index.windows.i.3N))))
+                                        
+  }
+  r.p.2
+}

### 2016-11-04 MainReport.R

@@ -31,14 +31,28 @@ for (f in (1:nrow(input))) {
   # generate reports
   
   ## CA
-  data.dir <- paste("OUT/out_subset_CA_ANM", sep = "")
-  R0 = R0.CA
-  rmarkdown::render('analysis-structure.Rmd', 
-                      output_file =  paste("OUT/report_structure_CA_", family, "_", enm, "_R0_", R0, ".html", sep = ''))
+  #data.dir <- paste("OUT/out_subset_CA_ANM", sep = "")
+  #R0 = R0.CA
+  #rmarkdown::render('analysis-structure3.Rmd', 
+  #                    output_file =  paste("OUT/report_structure_CA_", family, "_", enm, "_R0_", R0, ".html", sep = ''))
 
   ## CM
   data.dir <- paste("OUT/out_subset_CM_ANM", sep = "")
   R0 = R0.CM
-  rmarkdown::render('analysis-structure.Rmd', 
+  
+  ### RMSD
+  rmarkdown::render('analysis-structure3.Rmd', 
                     output_file =  paste("OUT/report_structure_CM_", family, "_", enm, "_R0_", R0, ".html", sep = ''))
-}
+  
+  ### RMSD windows rot
+  rmarkdown::render('analysis-structure-window3.Rmd', 
+                    output_file =  paste("OUT/report_structure_window_CM_", family, "_", enm, "_R0_", R0, ".html", sep = ''))
+  
+  ### RMSD windows contacts rot
+  rmarkdown::render('analysis-structure-window-contacts3.Rmd', 
+                    output_file =  paste("OUT/report_structure_window_contacts_CM_", family, "_", enm, "_R0_", R0, ".html", sep = ''))
+  
+  ### local enviroment 
+  rmarkdown::render('analysis-structure-local-enviroment3.Rmd', 
+                    output_file =  paste("OUT/report_structure_local_enviroment_CM_", family, "_", enm, "_R0_", R0, ".html", sep = ''))
+  }

### 2016-12-11 analysis-structure3-core.Rmd
cambios 11/12/16

--- 2016-11-04 analysis-structure3.Rmd
@@
 site.info.fname = file.path(data.dir, paste(p.ref, "_m.da.ca.csv", sep = ""))
-min.da.CM.CA.fname = file.path(data.dir, paste(p.ref, "_min.da.CM.ca.csv", sep = ""))
+min.da.CM.CA.fname = file.path(data.dir, paste(p.ref, "_m.da.ca.csv", sep = ""))
 
@@
 
+```{r read_the_core, comment = ""}
+# indexes.core
+indexes.core = as.numeric(read.csv(file.path("DATA", paste("indexes.core.2", "_", family, ".csv", sep = "")))[1, -1])
+```
+
 ```{r set_site_info}
@@
 # add pdb.info to site.info
-site.info = cbind(site.info, pdb.info)
+site.info = cbind(site.info[indexes.core, ], pdb.info[indexes.core, ])
 ```
@@
 ## exp
-dri2.exp = read.csv(dri2.exp.fname, header = T)
-site = site.info$site
-dri2.exp = dri2.exp[1:length(protein.exp), site]
+dri2.exp = read.csv(dri2.exp.fname, header = T)[, indexes.core]
 rownames(dri2.exp) = protein.exp
@@
 ## mut
-dri2.mut = read.csv(dri2.mut.fname, header = T)
-site = site.info$site
-dri2.mut = dri2.mut[1:length(protein.exp), site]
+dri2.mut = read.csv(dri2.mut.fname, header = T)[, indexes.core]
 rownames(dri2.mut) = paste("mut", rownames(dri2.mut), sep = "")
@@
 ## strong
-dri2.strong = read.csv(dri2.strong.fname, header = T)
-site = site.info$site
-dri2.strong = dri2.strong[1:length(protein.exp), site]
+dri2.strong = read.csv(dri2.strong.fname, header = T)[, indexes.core]
 rownames(dri2.strong) = paste("strong", rownames(dri2.strong), sep = "")
@@
 
+# calculate cors
 r.exp.mut = cor(d.exp$mean.z.RSD, d.mut$mean.z.RSD)
@@
 
-# comparison of means.z.scores with the minimum distance to the functional sites
-plot(y = d.exp$mean.z.RSD - d.mut$mean.z.RSD, x = m.min.da.CM.CA$min.da.ca, xlab = "minimal distance to active site (between CAs)", ylab = "exp.mean.z.RSD - mut.mean.z.RSD")
-plot(y = d.exp$mean.z.RSD - d.mut$mean.z.RSD, x = m.min.da.CM.CA$min.da.CM, xlab = "minimal distance to active site (between CMs)", ylab = "exp.mean.z.RSD - mut.mean.z.RSD")
+```
 
-## calculate correlations between profiles
-r.min.da.CA = cor((d.exp$mean.z.RSD - d.mut$mean.z.RSD), m.min.da.CM.CA$min.da.ca)
-r.min.da.CM = cor((d.exp$mean.z.RSD - d.mut$mean.z.RSD), m.min.da.CM.CA$min.da.CM)
+```{r_comparison_vs_plots}
 
-cor.df = data.frame("comparison" = c("(exp - mut) vs min.da.CA", "(exp - mut) vs min.da.CM"), "R" = c(r.min.da.CA, r.min.da.CM))
+# plot exp vs simulated profiles 
+par(pty = "s")
 
-knitr::kable(cor.df, digits = 2, caption = "Correlation between differences in <Z-scores> profiles and the minimal distance to the active site")
+plot(x = d.exp$mean.z.RSD, 
+     y = d.mut$mean.z.RSD, 
+     xlab = "exp.mean.z.RSD", 
+     ylab = "mut.mean.z.RSD", 
+     xlim = c(min(c(d.exp$mean.z.RSD, d.mut$mean.z.RSD)), max(c(d.exp$mean.z.RSD, d.mut$mean.z.RSD))),
+     ylim = c(min(c(d.exp$mean.z.RSD, d.mut$mean.z.RSD)), max(c(d.exp$mean.z.RSD, d.mut$mean.z.RSD))))
+points(x = as.numeric(d.exp$mean.z.RSD)[active.sites], y = as.numeric(d.mut$mean.z.RSD)[active.sites], col = "yellow")
+points(x = as.numeric(d.exp$mean.z.RSD)[contacts.active.sites], y = as.numeric(d.mut$mean.z.RSD)[contacts.active.sites], col = "green")
+abline(0, 1)
+
+plot(x = d.exp$mean.z.RSD, 
+     y = d.strong$mean.z.RSD, 
+     xlab = "exp.mean.z.RSD", 
+     ylab = "strong.mean.z.RSD", 
+     xlim = c(min(c(d.exp$mean.z.RSD, d.strong$mean.z.RSD)), max(c(d.exp$mean.z.RSD, d.strong$mean.z.RSD))),
+     ylim = c(min(c(d.exp$mean.z.RSD, d.strong$mean.z.RSD)), max(c(d.exp$mean.z.RSD, d.strong$mean.z.RSD))))
+points(x = as.numeric(d.exp$mean.z.RSD)[contacts.active.sites], y = as.numeric(d.strong$mean.z.RSD)[contacts.active.sites], col = "green")
+points(x = as.numeric(d.exp$mean.z.RSD)[active.sites], y = as.numeric(d.strong$mean.z.RSD)[active.sites], col = "yellow")
+abline(0, 1)
+
+plot(x = d.mut$mean.z.RSD, 
+     y = d.strong$mean.z.RSD, 
+     xlab = "mut.mean.z.RSD", 
+     ylab = "strong.mean.z.RSD", 
+     xlim = c(min(c(d.mut$mean.z.RSD, d.strong$mean.z.RSD)), max(c(d.mut$mean.z.RSD, d.strong$mean.z.RSD))),
+     ylim = c(min(c(d.mut$mean.z.RSD, d.strong$mean.z.RSD)), max(c(d.mut$mean.z.RSD, d.strong$mean.z.RSD))))
+points(x = as.numeric(d.mut$mean.z.RSD)[contacts.active.sites], y = as.numeric(d.strong$mean.z.RSD)[contacts.active.sites], col = "green")
+points(x = as.numeric(d.mut$mean.z.RSD)[active.sites], y = as.numeric(d.strong$mean.z.RSD)[active.sites], col = "yellow")
+abline(0, 1)
 ```

### 2016-12-11 analysis-structure3.Rmd
cambios 11/12/16

@@
 ```
+
+```{r_comparison_vs_plots}
+
+# plot exp vs simulated profiles 
+par(pty = "s")
+
+plot(x = d.exp$mean.z.RSD, 
+     y = d.mut$mean.z.RSD, 
+     xlab = "exp.mean.z.RSD", 
+     ylab = "mut.mean.z.RSD", 
+     xlim = c(min(c(d.exp$mean.z.RSD, d.mut$mean.z.RSD)), max(c(d.exp$mean.z.RSD, d.mut$mean.z.RSD))),
+     ylim = c(min(c(d.exp$mean.z.RSD, d.mut$mean.z.RSD)), max(c(d.exp$mean.z.RSD, d.mut$mean.z.RSD))))
+points(x = as.numeric(d.exp$mean.z.RSD)[active.sites], y = as.numeric(d.mut$mean.z.RSD)[active.sites], col = "yellow")
+points(x = as.numeric(d.exp$mean.z.RSD)[contacts.active.sites], y = as.numeric(d.mut$mean.z.RSD)[contacts.active.sites], col = "green")
+abline(0, 1)
+
+plot(x = d.exp$mean.z.RSD, 
+     y = d.strong$mean.z.RSD, 
+     xlab = "exp.mean.z.RSD", 
+     ylab = "strong.mean.z.RSD", 
+     xlim = c(min(c(d.exp$mean.z.RSD, d.strong$mean.z.RSD)), max(c(d.exp$mean.z.RSD, d.strong$mean.z.RSD))),
+     ylim = c(min(c(d.exp$mean.z.RSD, d.strong$mean.z.RSD)), max(c(d.exp$mean.z.RSD, d.strong$mean.z.RSD))))
+points(x = as.numeric(d.exp$mean.z.RSD)[contacts.active.sites], y = as.numeric(d.strong$mean.z.RSD)[contacts.active.sites], col = "green")
+points(x = as.numeric(d.exp$mean.z.RSD)[active.sites], y = as.numeric(d.strong$mean.z.RSD)[active.sites], col = "yellow")
+abline(0, 1)
+
+plot(x = d.mut$mean.z.RSD, 
+     y = d.strong$mean.z.RSD, 
+     xlab = "mut.mean.z.RSD", 
+     ylab = "strong.mean.z.RSD", 
+     xlim = c(min(c(d.mut$mean.z.RSD, d.strong$mean.z.RSD)), max(c(d.mut$mean.z.RSD, d.strong$mean.z.RSD))),
+     ylim = c(min(c(d.mut$mean.z.RSD, d.strong$mean.z.RSD)), max(c(d.mut$mean.z.RSD, d.strong$mean.z.RSD))))
+points(x = as.numeric(d.mut$mean.z.RSD)[contacts.active.sites], y = as.numeric(d.strong$mean.z.RSD)[contacts.active.sites], col = "green")
+points(x = as.numeric(d.mut$mean.z.RSD)[active.sites], y = as.numeric(d.strong$mean.z.RSD)[active.sites], col = "yellow")
+abline(0, 1)
+```

### 2016-12-11 MainProgram.R

@@ -57,6 +57,7 @@ ReadHeme.fname <- "FUNCTIONS/ReadHeme.R"
 CalculateENMKeff.fname <- "FUNCTIONS/CalculateENMKeff.R"
 CalculateENMK.fname <- "FUNCTIONS/CalculateENMK.R"
 CalculateVariability.fname <- "FUNCTIONS/CalculateVariability.R"
+GetCore.fname <- "FUNCTIONS/GetCore.R"
 
 if (model == "ANM") {
   CalculateBetas.fname <- "FUNCTIONS/CalculateBetas.R"
@@ -81,6 +82,7 @@ source(ReadHeme.fname)
 source(CalculateENMKeff.fname)
 source(CalculateENMK.fname)
 source(CalculateVariability.fname)
+source(GetCore.fname)
 
 source(CalculateBetas.fname)
 source(CalculateKij.fname)
@@ -115,7 +117,12 @@ for (f in (1:nrow(input))) {
                   data.dir,
                   out.dir)
   }
-
+  
+  # Get the core
+  GetCore(family,
+          data.dir,
+          p.ref)
+  
   # Generate id for betas output filename
   betas.fname.id <- paste(family, "_", p.ref, "_R0_", R0, sep = "")
   

### 2016-12-11 analysis-structure3-core.Rmd
cambios 2 11/12/16

@@
 ```{r_comparison_mean_z.RSD_vs_site, fig.cap = "Black lines are the active sites and grey lines are their contacts"}
-# comparison of z.RSD profiles
-ggplot(d, aes(x = site, y = mean.z.RSD, col = dataset)) +
-  geom_line() +
-  geom_text(data = subset(d, dataset == "exp" & mean.z.RSD < -.5), aes(x = site, y = mean.z.RSD, label = site), nudge_y = -.1, size = 1.8)+
-  geom_vline(xintercept = active.sites, show.legend = F) +
-  geom_vline(xintercept = contacts.active.sites, col = "grey", show.legend = F) + 
-  scale_colour_manual(name = NULL, values = myColors)
 
@@
 knitr::kable(cor.df, digits = 2, caption = "Correlation between <Z-scores> profiles")
-```
-
-### Distances to the active sites
-
-```{r_comparison_da}
-
-```
-
-```{r_comparison_vs_plots}
 
@@
      ylim = c(min(c(d.exp$mean.z.RSD, d.mut$mean.z.RSD)), max(c(d.exp$mean.z.RSD, d.mut$mean.z.RSD))))
-points(x = as.numeric(d.exp$mean.z.RSD)[active.sites], y = as.numeric(d.mut$mean.z.RSD)[active.sites], col = "yellow")
-points(x = as.numeric(d.exp$mean.z.RSD)[contacts.active.sites], y = as.numeric(d.mut$mean.z.RSD)[contacts.active.sites], col = "green")
 abline(0, 1)
@@
      ylim = c(min(c(d.exp$mean.z.RSD, d.strong$mean.z.RSD)), max(c(d.exp$mean.z.RSD, d.strong$mean.z.RSD))))
-points(x = as.numeric(d.exp$mean.z.RSD)[contacts.active.sites], y = as.numeric(d.strong$mean.z.RSD)[contacts.active.sites], col = "green")
-points(x = as.numeric(d.exp$mean.z.RSD)[active.sites], y = as.numeric(d.strong$mean.z.RSD)[active.sites], col = "yellow")
 abline(0, 1)
@@
      ylim = c(min(c(d.mut$mean.z.RSD, d.strong$mean.z.RSD)), max(c(d.mut$mean.z.RSD, d.strong$mean.z.RSD))))
-points(x = as.numeric(d.mut$mean.z.RSD)[contacts.active.sites], y = as.numeric(d.strong$mean.z.RSD)[contacts.active.sites], col = "green")
-points(x = as.numeric(d.mut$mean.z.RSD)[active.sites], y = as.numeric(d.strong$mean.z.RSD)[active.sites], col = "yellow")
 abline(0, 1)

### 2016-12-11 MainReport.R

@@ -35,7 +35,7 @@ for (f in (1:nrow(input))) {
   data.dir <- paste("OUT/out_subset_CA_ANM", sep = "")
   R0 = R0.CA
   rmarkdown::render('analysis-structure3-core.Rmd', 
-                    output_file =  paste("OUT/report_structure_CA_", family, "_", enm, "_R0_", R0, ".html", sep = ''))
+                    output_file =  paste("OUT/report_structure_CA_core_", family, "_", enm, "_R0_", R0, ".html", sep = ''))
 
   ## CM
   data.dir <- paste("OUT/out_subset_CM_ANM", sep = "")

### 2016-12-11 min.da.CM.CA.R

@@ -1,3 +1,4 @@
+# WARNING: run the functions of "MainProgramCM.R".
 # This program calculates distances between functional sites of proteins and the other sites of the protein.
 # It calculates distances between CAs and CMs.
 
@@ -64,8 +65,8 @@ for (f in (1:nrow(input))) {
   m.min.da.CM = matrix(nrow = n.aa, ncol = 1)
   
   for (i in (1:n.aa)) {
-    m.min.da.ca[i, ] = min(m.da.ca[i, ])
-    m.min.da.CM[i, ] = min(m.da.CM[i, ])
+    m.min.da.ca[i, ] = min(m.da.ca[i, 2:ncol(m.da.ca)])
+    m.min.da.CM[i, ] = min(m.da.CM[i, 2:ncol(m.da.ca)])
   }
 
   # build a dataframe with minimum distances

### 2017-01-08 analysis-structure-core.Rmd
cambios 08/01/2017

--- 2016-12-11 analysis-structure3.Rmd
@@
 We study the evolutionary divergence of proteins using the LF-ENM and comparing simulated mutants with experimental data. 
+For the core we considered sites with no gaps in the whole multiple alignment.
 
@@
 
+```{r read_the_core, comment = ""}
+# indexes.core
+indexes.core = as.numeric(read.csv(file.path("DATA", paste("indexes.core", "_", family, ".csv", sep = "")))[1, -1])
+```
+
 ```{r set_site_info}
@@
 p = ggplot(d, aes(x = site, y = mean.z.RSD, col = dataset, fill = dataset)) +
-    geom_line() +
-    geom_ribbon(aes(ymin = mean.z.RSD - f95 * se.z.RSD, ymax = mean.z.RSD + se.z.RSD), alpha = .4, show.legend = F) +
+    geom_point() +
+    geom_errorbar(aes(ymin = mean.z.RSD - f95 * se.z.RSD, ymax = mean.z.RSD + se.z.RSD), alpha = .4, show.legend = F) +
     geom_vline(xintercept = active.sites, show.legend = F) +
@@
 
-```{r_comparison_mean_z.RSD_vs_site, fig.cap = "Black lines are the active sites and grey lines are their contacts"}
-# comparison of z.RSD profiles
-ggplot(d, aes(x = site, y = mean.z.RSD, col = dataset)) +
-  geom_line() +
-  geom_text(data = subset(d, dataset == "exp" & mean.z.RSD < -.5), aes(x = site, y = mean.z.RSD, label = site), nudge_y = -.1, size = 1.8)+
-  geom_vline(xintercept = active.sites, show.legend = F) +
-  geom_vline(xintercept = contacts.active.sites, col = "grey", show.legend = F) + 
-  scale_colour_manual(name = NULL, values = myColors)
+```{r-comparison-mean-z.RSD-vs-site, fig.cap = "Black lines are the active sites and grey lines are their contacts"}
 
@@
 d.strong = subset(d, dataset == "mut+sel")
+
+# eliminate duplicates
+active.sites = active.sites[!duplicated(active.sites)]
+contacts.active.sites = contacts.active.sites[!duplicated(active.sites)]
+
+# new.indexes
+new.active.index = c()
+for (i in (1:(length(active.sites)))){
+  new.active.index[i] = which(indexes.core == active.sites[i])
+}
+
+new.contacts.active.index = c()
+for (i in (1:(length(contacts.active.sites)))){
+  new.contacts.active.index[i] = which(indexes.core == contacts.active.sites[i])
+}
+
+active.sites = new.active.index
+contacts.active.sites = new.contacts.active.index
 
@@
 knitr::kable(cor.df, digits = 2, caption = "Correlation between <Z-scores> profiles")
-```
-
-### Distances to the active sites
-
-```{r_comparison_da}
-
-# comparison of means.z.scores with the minimum distance to the functional sites
-plot(y = d.exp$mean.z.RSD - d.mut$mean.z.RSD, x = m.min.da.CM.CA$min.da.ca, xlab = "minimal distance to active site (between CAs)", ylab = "exp.mean.z.RSD - mut.mean.z.RSD")
-plot(y = d.exp$mean.z.RSD - d.mut$mean.z.RSD, x = m.min.da.CM.CA$min.da.CM, xlab = "minimal distance to active site (between CMs)", ylab = "exp.mean.z.RSD - mut.mean.z.RSD")
-
-## calculate correlations between profiles
-r.min.da.CA = cor((d.exp$mean.z.RSD - d.mut$mean.z.RSD), m.min.da.CM.CA$min.da.ca)
-r.min.da.CM = cor((d.exp$mean.z.RSD - d.mut$mean.z.RSD), m.min.da.CM.CA$min.da.CM)
-
-cor.df = data.frame("comparison" = c("(exp - mut) vs min.da.CA", "(exp - mut) vs min.da.CM"), "R" = c(r.min.da.CA, r.min.da.CM))
-
-knitr::kable(cor.df, digits = 2, caption = "Correlation between differences in <Z-scores> profiles and the minimal distance to the active site")
-```
-
-```{r_comparison_vs_plots}
 

### 2017-01-08 analysis-structure-normal-modes.Rmd
cambios 08/01/2017

--- 2016-07-27 OUT/analysis-structure-CA.Rmd
@@
 title: "Structural Divergence Analysis"
-author: "María Laura Marcos, Julian Echave"
-date: "25 de julio de 2016"
+author: "Maria Laura Marcos, Julian Echave"
 output: html_document
@@
 
+# Introduction
+We study the evolutionary divergence of proteins using the LF-ENM and comparing simulated mutants with experimental data.
+
 ```{r setup, include = FALSE}
-knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, cache = 2, autodep = T)
+# set chunk options
+knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
 ```
 
-```{r load_libraries}
+```{r load_packages}
+# load packages
 library(ggplot2)
@@
 
-setwd("C:/Users/Usuario/Desktop/VariabilidadEstructuralProteica")
-
-source("OUT/out_subset_CA/multiplot.R")
-source("OUT/out_subset_CA/my-functions.R")
+# load functions
+source(file.path(data.dir, "multiplot.R"))
+source(file.path(data.dir, "my-functions.R")) 
 ```
 
-```{r set_my_colors, eval = T}
+```{r set_my_colors}
+# set my colors
 myColors = c("blue", "darkgreen", "red", "red") 
 names(myColors) <- c("exp", "mut", "strong", "mut+sel")
-
-setwd("C:/Users/Usuario/Desktop/VariabilidadEstructuralProteica/OUT")
-
 ```
-# Introduction
-We study the evolutionary divergence of proteins using the LFENM and compare with experimental data.
 
 ```{r set_run_variables}
-# Set options
-family = "globins"
-R0 = 10
-enm = "ANM"
-
-# significance factors
+# set significance factors
 f95 = 1.96
@@
 ```{r set_file_names}
-## Input and pre-processing of data
-# Set up input filenames
+# set input filenames
+## data
+reference.fname = file.path(data.dir, paste(family, "_ref.txt", sep = ""))
+protein_list.fname = file.path(data.dir, paste(family, "_list.txt", sep = ""))
+site.info.fname = file.path(data.dir, paste(p.ref, "_m.da.ca.csv", sep = ""))
+min.da.CM.CA.fname = file.path(data.dir, paste(p.ref, "_min.da.CM.ca.csv", sep = ""))
 
-reference.fname = file.path(data.dir, paste(family, "_ref.txt", sep = ""))
-site.info.fname = file.path(data.dir, paste(family, "_out_m.da.csv", sep = ""))
-protein_list.fname = file.path(data.dir, paste(family, "_list.txt", sep = ""))
+## profiles to compare
+### Pn
+Pn.exp.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.exp.Pn.csv", sep = ""))
+Pn.strong.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_strong.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
+Pn.mut.fname = file.path(data.dir,paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
 
-dri2.exp.fname = file.path(data.dir, paste(family, "_R0_10_beta_strong.sel_K.analysis_Keff_out_m.exp.norm.dr.squarei.csv", sep = ""))
-Pn.exp.fname = file.path(data.dir, paste(family,"_R0_10_beta_strong.sel_K.analysis_Keff_out_m.exp.Pn.csv", sep = ""))
-energy.exp.fname = file.path(data.dir, paste(family, "_R0_10_beta_strong.sel_K.analysis_Keff_out_m.exp.va.csv", sep = ""))
-
-dri2.strong.fname = file.path(data.dir, paste(family, "_R0_10_beta_strong.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
-Pn.strong.fname = file.path(data.dir, paste(family, "_R0_10_beta_strong.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
-energy.strong.fname = file.path(data.dir, paste(family, "_R0_10_beta_strong.sel_K.analysis_Keff_out_m.theo.va.csv", sep = ""))
-
-dri2.mut.fname = file.path(data.dir,paste(family, "_R0_10_beta_no.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
-Pn.mut.fname = file.path(data.dir, paste(family, "_R0_10_beta_no.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
-energy.mut.fname = file.path(data.dir, paste(family, "_R0_10_beta_no.sel_K.analysis_Keff_out_m.theo.va.csv", sep = ""))
+### energy
+energy.exp.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.exp.va.csv", sep = ""))
+energy.strong.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_strong.sel_K.analysis_Keff_out_m.theo.va.csv", sep = ""))
+energy.mut.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.va.csv", sep = ""))
 
@@
 ```{r set_reference_protein}
-## which is the reference protein?
+# which is the reference protein?
 reference = as.character(read.table(reference.fname, header = F)[1, 1])
+if (reference != p.ref) {
+  print("Warning: different references")
+}
 ```
 
-We use the `r enm` Elastic Network Model with `R0 =` `r R0` for the `r family` family. 
-We use as reference for the ENM the protein with pdb code `r reference`.
-The `r family` family consists of the following proteins:
+We studied the `r family` family. 
+We used the ENM `r enm` with R0 = `r R0` to generate mutants.
+We used as reference for the ENM the protein with pdb code `r reference`. 
+We simulated `r n.mut.p` mutants of this reference for each protein of the family.
+The `r family` family is of the type `r type` and consists of the following proteins:
 
-```{r set_experimental_protein_names}
-## Experimental protein names
+```{r set_experimental_protein_names, comment = ""}
+# experimental protein names
 protein.exp = read.table(protein_list.fname, header = F, stringsAsFactors = F)[, 1]
@@
 
-[//]: Prepare site.info data frame
-
-```{r set_up_site_info, eval = T}
-
-## read site information of reference protein
-site.info = read.csv(site.info.fname, header = T, sep = ";")
-
-## add info to site.info
-d = ddply(site.info, "site", .fun = function(x) data.frame("da" = min(x[, c(-1, -2)])))
-
-## Define shells of active site neighborhood (first shell is from 2.5 to 7.5, second from 7.5 to 12.5, etc)
-d$shell = cut(d$da, breaks = c(-.1, 2.5, 7.5, 12.5, 17.5, 22.5, 27.5, 32.5, 37.5, 42.5, 47.5, 52.5, max(d$da)))
-levels(d$shell) = seq(length(levels(d$shell))) - 1 # rename shell levels
-site.info = merge(site.info, d, by = "site")
-
-## Read reference pdb and calculate resno, AA, and CN
-reference.pdb.fname = file.path(data.dir,paste(reference, ".pdb", sep = ""))
-ref.pdb = read.pdb(reference.pdb.fname)
-inds = atom.select(ref.pdb, elety = "CA")
-ref.pdb.ca = ref.pdb$atom[inds$atom,]
-cmap.ca = cmap(ref.pdb$xyz[inds$xyz], dcut = R0, scut = 0, mask.lower = F)
-CN = rowSums(cmap.ca, na.rm = T) - 1 # diag(cmap.ca) returned by cmap is 1!
-AA = ref.pdb.ca$resid
-resno = ref.pdb.ca$resno
-pdb.info = data.frame(resno, AA, CN)
-names(pdb.info) = c("resno", "AA", paste("CN", as.character(R0), sep = ""))
-
-## Add pdb.info to site.info
-site.info = cbind(site.info, pdb.info)
-```
-
-[//]: Prepare experimental data
-
-```{r read_experimental_data}
-# read experimental data
-dri2.exp = read.csv(dri2.exp.fname, header = T)
-site = site.info$site
-dri2.exp = dri2.exp[, site]
-rownames(dri2.exp) = protein.exp
-
+```{r prepare_site_data}
+# prepare the data
 Pn.exp = read.csv(Pn.exp.fname, header = T)
 rownames(Pn.exp) = protein.exp
-
 energy.exp = read.csv(energy.exp.fname, header = T)
@@
 
-```
-
-[//]: Prepare data for no selection (mut)
-
-```{r read_and_set_data_mut}
-# read simulated data
-
-dri2.mut = read.csv(dri2.mut.fname, header = T)
-site = site.info$site
-dri2.mut = dri2.mut[, site]
-rownames(dri2.mut) = paste("mut", rownames(dri2.mut), sep = "")
-
 Pn.mut = read.csv(Pn.mut.fname, header = T)
 rownames(Pn.mut) = paste("mut", rownames(Pn.mut), sep = "")
-
 energy.mut = read.csv(energy.mut.fname, header = T)
 rownames(energy.mut) = paste("mut", rownames(energy.mut), sep = "")
-```
-
-[//]: Prepare data for strong selection
-
-```{r read_and_set_data_strong}
-# read simulated data
-
-dri2.strong = read.csv(dri2.strong.fname, header = T)
-site = site.info$site
-dri2.strong = dri2.strong[, site]
-rownames(dri2.strong) = paste("strong", rownames(dri2.strong), sep = "")
 
@@
 rownames(Pn.strong) = paste("strong", rownames(Pn.strong), sep = "")
-
 energy.strong = read.csv(energy.strong.fname, header = T)
 rownames(energy.strong) = paste("strong", rownames(energy.strong), sep = "")
-```
 
-# Structural divergence along sites
+## exp
+tdri2.exp = as.data.frame(t(as.matrix(dri2.exp)))
+tdri2.exp = cbind(site.info, tdri2.exp)
+siteComparison.exp = melt(tdri2.exp, id.vars = names(site.info), variable.name = "protein", value.name = "dri2")
 
-Here we study how structural divergence varies from site to site. We will compare simulated data and empirical data.
+## mut
+tdri2.mut = as.data.frame(t(as.matrix(dri2.mut)))
+tdri2.mut = cbind(site.info, tdri2.mut)
+siteComparison.mut = melt(tdri2.mut, id.vars = names(site.info), variable.name = "protein", value.name = "dri2")
 
-```{r prepare-site-data}
-# Prepare my data.frame
-# rows of dri2 are proteins, columns are sites
-
+## strong
 tdri2.strong = as.data.frame(t(as.matrix(dri2.strong)))
@@
 
-tdri2.mut = as.data.frame(t(as.matrix(dri2.mut)))
-tdri2.mut = cbind(site.info, tdri2.mut)
-siteComparison.mut = melt(tdri2.mut, id.vars = names(site.info), variable.name = "protein", value.name = "dri2")
-
-tdri2.exp = as.data.frame(t(as.matrix(dri2.exp)))
-tdri2.exp = cbind(site.info, tdri2.exp)
-siteComparison.exp = melt(tdri2.exp, id.vars = names(site.info), variable.name = "protein", value.name = "dri2")
-
-siteComparison.all.datasets = rbind(
-  data.frame("dataset" = "exp", siteComparison.exp),
+# bluild the data.frame
+siteComparison.all.datasets = rbind(data.frame("dataset" = "exp", siteComparison.exp),
                                     data.frame("dataset" = "mut", siteComparison.mut),
@@
 
-### Mean z.RSD vs site
+### Structural divergence along normal modes
 
-To measure structural divergence we use z.RSD profiles, which are the best (most similar distributions and profiles w.r.t experimental).
+In this section we consider structural divergence using normal mode coordinates. Pn is the square divergence along a normal mode relative to the mean.
 
-The following plot compares the mean z.RSD profiles, including standard errors (with .999 confidence level for the mean)
-*Warning: the effective number of data should be smaller than the actual data, especially for the experimental dataset because of several factors, including smoothing of the profiles, phylogenetic relationships, etc.
-We need to deal with this for quantitative analysis.
-Probably we'll need to use bootstrapping to calculate standard errors non-parametrically*
-
-```{r mean-z-RSD-vs-site}
-# Comparison of z.RSD profiles annotated with functional information (reported active sites).
-dat = siteComparison.all.datasets
-dat$dataset = revalue(dat$dataset, c("strong" = "mut+sel"))
-
-# dat.with.means and standard errors
-d = ddply(dat,c("dataset","site","AA","shell"), function(x) {
-                mean.z.RSD = mean(x$z.RSD, na.rm = T)
-                ndata = sum(!is.na(x$z.RSD))
-                se.z.RSD = sd(x$z.RSD, na.rm = T) / sqrt(ndata)
-                data.frame(mean.z.RSD, ndata, se.z.RSD)
-})
-
-##
-
-z.RSD.exp = d$mean.z.RSD[d$dataset == "exp"]
-z.RSD.strong = d$mean.z.RSD[d$dataset == "mut+sel"]
-z.RSD.mut = d$mean.z.RSD[d$dataset == "mut"]
-
-m.min.da.CM.ca = read.csv(file.path(data.dir, "min.da.CM.ca.csv", sep = ""))[, 2:4]
-
-data.csv = data.frame(m.min.da.CM.ca[1:151, ], "mean.z.RSD.exp" = z.RSD.exp, "mean.z.RSD.strong" = z.RSD.strong, "mean.z.RSD.mut" = z.RSD.mut)
-
-write.csv(data.csv, file.path(data.dir, "data.da.csv", sep = ""))
-
-m.min.da.CM = m.min.da.CM.ca$min.da.CM[1:151]
-
-data.plot = data.frame("d.exp.mut" = z.RSD.mut - z.RSD.exp, "d.exp.strong" = z.RSD.mut - z.RSD.strong, "m.min.da.CM" = m.min.da.CM)
-
-r = round(cor(data.plot$d.exp.mut, data.plot$m.min.da.CM), 2)
-
-ggplot(data.plot, aes(y = d.exp.mut, x = m.min.da.CM)) +
-  geom_point()+
-  geom_smooth(method = "lm") +
-  geom_label(aes(x = 5, y = 2, label = paste("R =", as.character(r)))) +
-    labs(y = "mean.z.RSD.mut - mean.z.RSD.exp", x = "min.da.CM")
-
-r = round(cor(data.plot$d.exp.strong, data.plot$m.min.da.CM), 2)
-
-ggplot(data.plot, aes(y = d.exp.strong, x = m.min.da.CM)) +
-  geom_point()+
-  geom_smooth(method = "lm") +
-  geom_label(aes(x = 5, y = 0.5, label = paste("R =", as.character(r)))) +
-    labs(y = "mean.z.RSD.strong - mean.z.RSD.exp", x = "min.da.CM")
-
-##
-
-m.min.da.ca = m.min.da.CM.ca$min.da.ca[1:151]
-
-data.plot = data.frame("d.exp.mut" = z.RSD.mut - z.RSD.exp, "d.exp.strong" = z.RSD.strong - z.RSD.exp, "m.min.da.ca" = m.min.da.ca)
-
-r = round(cor(data.plot$d.exp.mut, data.plot$m.min.da.ca), 2)
-
-ggplot(data.plot, aes(y = d.exp.mut, x = m.min.da.ca)) +
-  geom_point()+
-  geom_smooth(method = "lm") +
-  geom_label(aes(x = 5, y = 2, label = paste("R =", as.character(r)))) +
-    labs(y = "mean.z.RSD.mut - mean.z.RSD.exp", x = "min.da.ca")
-
-r = round(cor(data.plot$d.exp.strong, data.plot$m.min.da.ca), 2)
-
-ggplot(data.plot, aes(y = d.exp.strong, x = m.min.da.ca)) +
-  geom_point()+
-  geom_smooth(method = "lm") +
-  geom_label(aes(x = 5, y = 2, label = paste("R =", as.character(r)))) +
-    labs(y = "mean.z.RSD.strong - mean.z.RSD.exp", x = "min.da.ca")
-
-#d$dataset = factor(d$dataset, levels = c("exp", "mut", "strong"))
-d$label = as.character(d$site)
-active.sites = d$site[d$shell == 0]
-
-p = ggplot(d,aes(x = site, y = mean.z.RSD, col = dataset, fill = dataset)) +
-    geom_line() +
-    geom_ribbon(aes(ymin = mean.z.RSD - f95 * se.z.RSD, ymax = mean.z.RSD + se.z.RSD), alpha = .4, show.legend = F) +
-    geom_vline(xintercept = active.sites, col = "grey", show.legend = F) +
-    labs(x = "site", y = "structural divergence(mean z.RSD)") +
-    coord_cartesian(ylim = c(-1.5, 2.8)) +
-    scale_colour_manual(name = NULL, values = myColors) + 
-    scale_fill_manual(name=NULL, values = myColors)
-
-# Plot separate and comparative plots
-p.facet = p + facet_grid(dataset~., switch = "y") + theme(legend.position = "none")
-
-p.facet %+% subset(d, dataset == "exp") 
-p.facet %+% subset(d, dataset == "mut")
-p.facet %+% subset(d, dataset == "mut+sel") 
-p.facet
-#p + theme(legend.position = "bottom", legend.title = element_blank())
-p + theme(legend.position = "bottom")
-
-```
-
-VAL107 and its neighbors (including site 32) are more structurally conserved than predicted.
-
-### Correlation between site profiles
-
-```{r}
-dat = siteComparison.all.datasets
-
-# dat.with.means and standard errors
-dat = ddply(dat,c("dataset", "site", "AA", "shell"), function(x) {
-                mean.z.RSD = mean(x$z.RSD, na.rm = T)
-                ndata = sum(!is.na(x$z.RSD))
-                se.z.RSD = sd(x$z.RSD, na.rm = T) / sqrt(ndata)
-                data.frame(mean.z.RSD, ndata, se.z.RSD)
-})
-
-dat.exp = subset(dat, dataset == "exp")
-dat.mut = subset(dat, dataset == "mut")
-dat.strong = subset(dat, dataset == "strong")
-
-ggplot(dat, aes(x = site, y = mean.z.RSD, col = dataset)) + geom_line() +
-    geom_text(data = subset(dat, dataset == "exp" & mean.z.RSD < -.5), aes(x = site, y = mean.z.RSD, label = site), nudge_y = -.1, size = 2)
-
-d = dat.exp
-d$d.exp.mut = dat.exp$mean.z.RSD - dat.mut$mean.z.RSD
-d$d.exp.strong = dat.exp$mean.z.RSD - dat.strong$mean.z.RSD
-d$d.strong.mut = dat.strong$mean.z.RSD - dat.mut$mean.z.RSD
-dd = melt(data = d[, c("site", "se.z.RSD", "d.exp.mut", "d.strong.mut")], c("site", "se.z.RSD"))
-
-ggplot(dd, aes(x = site, y = value, col = variable)) +
-    geom_line() 
-r = round(cor(d$d.strong.mut, d$d.exp.mut), 2)
-
-ggplot(d, aes(x = scale(d.strong.mut), y = scale(d.exp.mut))) + 
-    geom_point(aes(col = shell == 0)) +
-    geom_smooth(method = "lm") +
-    geom_label(aes(x = 0, y = 3, label = paste("R =", as.character(r)))) +
-    labs(x = "predicted selection vs mutation (RSD change)",y="empirical vs mutation (RSD change)")
-
-r.exp.mut = cor(dat.exp$mean.z.RSD, dat.mut$mean.z.RSD)
-r.exp.strong = cor(dat.exp$mean.z.RSD, dat.strong$mean.z.RSD)
-r.mut.strong = cor(dat.mut$mean.z.RSD, dat.strong$mean.z.RSD)
-cor.df = data.frame("comparison" = c("exp vs mut", "exp vs strong", "mut vs strong"),
-                    "R" = c(r.exp.mut, r.exp.strong, r.mut.strong))
-knitr::kable(cor.df, digits = 2)
-write.csv(dat, "structure-comparison-profiles.csv")
-
-```
-
-# Structural divergence along normal modes
-In this section we consider structural divergence using normal mode coordinates.
-Pn is the square divergence along a normal mode relative to the mean.
-
-[//]: Prepare mode data
-
-```{r prepare-mode-data}
+```{r-prepare-mode-data}
 mode = seq(ncol(Pn.strong))
@@
 modeComparison.strong = merge(energy.strong.long, Pn.strong.long, by = c("mode", "protein"))
-
 modeComparison.strong = ddply(modeComparison.strong, "protein", mutate, "Pn" = Pn / mean(Pn, na.rm = T))
@@
 modeComparison.exp = merge(energy.exp.long,Pn.exp.long,by=c("mode", "protein"))
-
 # renormalize Pn
@@
 modeComparison.mut <- na.omit(modeComparison.mut)
-
 ```
 
-[//]: Add quantile regression data
+```{r-add-quantile-regression-data}
 
-```{r}
 ## Quantile regression
@@
 ```
-
 ### Pn vs. mode energy
@@
 
-Here we show the square deviation along each normal mode (normalized so that <Pn> = 1) vs.
+Here we show the square deviation along each normal mode (normalized so that = 1) vs.
 the normal-mode's energy.
@@
 It is this energy the one that should be used, since it's inverse is the expected value of Pn.
-Lines are the .5 (median), .05, and .95 quantiles obtained using `rq()`
-- Upper panel: simulated vs empirical data, shown separately.
-- Lower panel: simulated vs empirical overlaped and zoomed to better see the pattern.
+Lines are the .5 (median), .05, and .95 quantiles obtained using rq()
 
-```{r Pn-vs-mode-energy,cache = 2}
+Upper panel: simulated vs empirical data, shown separately.
+Lower panel: simulated vs empirical overlaped and zoomed to better see the pattern.
+
+```{r-Pn-vs-energy}
+
 # Plot Pn vs energy
@@
 
-```{r median-Pn-vs-mode-energy, cache = 2}
+```{r-median-vs-mode-energy}
+
 dat = modeComparison.all.datasets
@@
 
-### Correlation between mode profiles
+### correlaction between mode profiles
 
-```{r}
+```{r-correlation-mode-profiles}
 dat = modeComparison.all.datasets
@@
 
+# plot exp vs simulated profiles 
+par(pty = "s")
+
+plot(x = dat.exp$Pn.median, 
+     y = dat.mut$Pn.median, 
+     xlab = "exp.Pn.median", 
+     ylab = "mut.Pn.median", 
+     xlim = c(min(c(dat.exp$Pn.median, dat.mut$Pn.median)), max(c(dat.exp$Pn.median, dat.mut$Pn.median))),
+     ylim = c(min(c(dat.exp$Pn.median, dat.mut$Pn.median)), max(c(dat.exp$Pn.median, dat.mut$Pn.median))))
+abline(0, 1)
+
+plot(x = dat.exp$Pn.median, 
+     y = dat.strong$Pn.median, 
+     xlab = "exp.Pn.median", 
+     ylab = "strong.Pn.median", 
+     xlim = c(min(c(dat.exp$Pn.median, dat.strong$Pn.median)), max(c(dat.exp$Pn.median, dat.strong$Pn.median))),
+     ylim = c(min(c(dat.exp$Pn.median, dat.strong$Pn.median)), max(c(dat.exp$Pn.median, dat.strong$Pn.median))))
+abline(0, 1)
+
+plot(x = dat.mut$Pn.median, 
+     y = dat.strong$Pn.median, 
+     xlab = "mut.Pn.median", 
+     ylab = "strong.Pn.median", 
+     xlim = c(min(c(dat.mut$Pn.median, dat.strong$Pn.median)), max(c(dat.mut$Pn.median, dat.strong$Pn.median))),
+     ylim = c(min(c(dat.mut$Pn.median, dat.strong$Pn.median)), max(c(dat.mut$Pn.median, dat.strong$Pn.median))))
+abline(0, 1)
 ```
-
-[//]: Write output for further analysis with other programs
-
-```{r write-data-to-output}
-write.csv(siteComparison.exp, "site-structure-comparison-exp.csv",row.names=F)
-write.csv(modeComparison.exp, "mode-structure-comparison-exp.csv",row.names=F)
-```

### 2017-01-08 analysis-structure-window-contacts.Rmd
cambios 08/01/2017

--- 2016-11-04 analysis-structure-window3.Rmd
@@
 ## profiles to compare
-dri2.exp.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.exp.norm.dr.squarei.windows.rot.csv", sep = ""))
-dri2.strong.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_strong.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.windows.rot.csv", sep = ""))
-dri2.mut.fname = file.path(data.dir,paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.windows.rot.csv", sep = ""))
+dri2.exp.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.exp.norm.dr.squarei.windows.contacts.rot.csv", sep = ""))
+dri2.strong.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_strong.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.windows.contacts.rot.csv", sep = ""))
+dri2.mut.fname = file.path(data.dir,paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.windows.contacts.rot.csv", sep = ""))
 ```

### 2017-01-08 analysis-structure.Rmd
cambios 08/01/2017

@@
 title: "Structural Divergence Analysis"
-author: "María Laura Marcos, Julian Echave"
+author: "Maria Laura Marcos, Julian Echave"
 output: html_document
@@
 
+# Introduction
+We study the evolutionary divergence of proteins using the LF-ENM and comparing simulated mutants with experimental data.
+
 ```{r setup, include = FALSE}
-knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, autodep = T)
+# set chunk options
+knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
 ```
 
-```{r load_libraries}
-# Load packages
+```{r load_packages}
+# load packages
 library(ggplot2)
@@
 
-# Source functions
+# load functions
 source(file.path(data.dir, "multiplot.R"))
@@
 
-```{r set_my_colors, eval = T}
+```{r set_my_colors}
+# set my colors
 myColors = c("blue", "darkgreen", "red", "red") 
@@
 
-# Introduction
-We study the evolutionary divergence of proteins using the LF-ENM and comparing simulated mutants with experimental data.
-
 ```{r set_run_variables}
-# significance factors
+# set significance factors
 f95 = 1.96
@@
 ```{r set_file_names}
-# input and pre-processing of data
-
-## set up input filenames
+# set input filenames
+## data
 reference.fname = file.path(data.dir, paste(family, "_ref.txt", sep = ""))
@@
 site.info.fname = file.path(data.dir, paste(p.ref, "_m.da.ca.csv", sep = ""))
+min.da.CM.CA.fname = file.path(data.dir, paste(p.ref, "_min.da.CM.ca.csv", sep = ""))
 
-dri2.exp.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_strong.sel_K.analysis_Keff_out_m.exp.norm.dr.squarei.csv", sep = ""))
-Pn.exp.fname = file.path(data.dir, paste(family,"_R0_", R0, "_beta_strong.sel_K.analysis_Keff_out_m.exp.Pn.csv", sep = ""))
-energy.exp.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_strong.sel_K.analysis_Keff_out_m.exp.va.csv", sep = ""))
-
+## profiles to compare
+dri2.exp.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.exp.norm.dr.squarei.csv", sep = ""))
 dri2.strong.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_strong.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
-Pn.strong.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_strong.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
-energy.strong.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_strong.sel_K.analysis_Keff_out_m.theo.va.csv", sep = ""))
-
 dri2.mut.fname = file.path(data.dir,paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
-Pn.mut.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
-energy.mut.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.va.csv", sep = ""))
 ```
@@
 reference = as.character(read.table(reference.fname, header = F)[1, 1])
+if (reference != p.ref) {
+  print("Warning: different references")
+}
 ```
@@
 
-```{r set_experimental_protein_names}
+```{r set_experimental_protein_names, comment = ""}
 # experimental protein names
@@
 
-[//]: Prepare site.info data frame
-
-```{r set_up_site_info, eval = T}
-# read site information of reference protein
+```{r set_site_info}
+# read site information of the reference protein
 site.info = read.csv(site.info.fname, header = T, sep = ",")
+m.min.da.CM.CA = read.csv(min.da.CM.CA.fname)
 
@@
 
-# define shells of active site neighborhood (first shell is from 2.5 to 7.5, second from 7.5 to 12.5, etc)
+# define shells of active site neighborhood
 d$shell = cut(d$da, breaks = c(-.1, 2.5, 7.5, 12.5, 17.5, 22.5, 27.5, 32.5, 37.5, 42.5, 47.5, 52.5, max(d$da)))
@@
 
-[//]: Prepare experimental data
-
-```{r read_experimental_data}
-# read experimental data
+```{r read_data}
+# read data
+## exp
 dri2.exp = read.csv(dri2.exp.fname, header = T)
 site = site.info$site
-dri2.exp = dri2.exp[, site]
+dri2.exp = dri2.exp[1:length(protein.exp), site]
 rownames(dri2.exp) = protein.exp
 
-Pn.exp = read.csv(Pn.exp.fname, header = T)
-rownames(Pn.exp) = protein.exp
-
-energy.exp = read.csv(energy.exp.fname, header = T)
-rownames(energy.exp) = protein.exp
-```
-
-[//]: Prepare data for no selection (mut)
-
-```{r read_and_set_data_mut}
-# read simulated data
+## mut
 dri2.mut = read.csv(dri2.mut.fname, header = T)
 site = site.info$site
-dri2.mut = dri2.mut[, site]
+dri2.mut = dri2.mut[1:length(protein.exp), site]
 rownames(dri2.mut) = paste("mut", rownames(dri2.mut), sep = "")
 
-Pn.mut = read.csv(Pn.mut.fname, header = T)
-rownames(Pn.mut) = paste("mut", rownames(Pn.mut), sep = "")
-
-energy.mut = read.csv(energy.mut.fname, header = T)
-rownames(energy.mut) = paste("mut", rownames(energy.mut), sep = "")
-```
-
-[//]: Prepare data for strong selection
-
-```{r read_and_set_data_strong}
-# read simulated data
+## strong
 dri2.strong = read.csv(dri2.strong.fname, header = T)
 site = site.info$site
-dri2.strong = dri2.strong[, site]
+dri2.strong = dri2.strong[1:length(protein.exp), site]
 rownames(dri2.strong) = paste("strong", rownames(dri2.strong), sep = "")
-
-Pn.strong = read.csv(Pn.strong.fname, header = T)
-rownames(Pn.strong) = paste("strong", rownames(Pn.strong), sep = "")
-
-energy.strong = read.csv(energy.strong.fname, header = T)
-rownames(energy.strong) = paste("strong", rownames(energy.strong), sep = "")
 ```
@@
 
-Here we study how structural divergence varies from site to site. We will compare simulated data and empirical data.
+Here we study how structural divergence varies from site to site. We compare simulated data with empirical data.
 
-```{r prepare-site-data}
-# prepare my data.frame
-# note: rows of dri2 are proteins, columns are sites
+```{r prepare_site_data}
+# prepare the data
+## exp
+tdri2.exp = as.data.frame(t(as.matrix(dri2.exp)))
+tdri2.exp = cbind(site.info, tdri2.exp)
+siteComparison.exp = melt(tdri2.exp, id.vars = names(site.info), variable.name = "protein", value.name = "dri2")
 
+## mut
+tdri2.mut = as.data.frame(t(as.matrix(dri2.mut)))
+tdri2.mut = cbind(site.info, tdri2.mut)
+siteComparison.mut = melt(tdri2.mut, id.vars = names(site.info), variable.name = "protein", value.name = "dri2")
+
+## strong
 tdri2.strong = as.data.frame(t(as.matrix(dri2.strong)))
@@
 
-To measure structural divergence we use z.RSD profiles, which are the best, at least for globins (most similar distributions and profiles w.r.t experimental).
+To measure structural divergence we use z.RSD profiles, which are the best for most families.
 
 The following plot compares the mean z.RSD profiles, including standard errors (with .999 confidence level for the mean)
-*Warning: the effective number of data should be smaller than the actual data, especially for the experimental dataset because of several factors, including smoothing of the profiles, phylogenetic relationships, etc.
+*Warning: the effective number of data should be smaller than the actual data, especially for the experimental dataset because of several factors.
 We need to deal with this for quantitative analysis.
@@
 
-```{r mean-z-RSD-vs-site}
-# comparison of z.RSD profiles annotated with functional information (reported active sites).
+```{r-mean_se_z.RSD_vs_site, fig.cap = "Black lines are the active sites and grey lines are their contacts"}
+# comparison of z.RSD profiles with functional sites
+## prepare dat
 dat = siteComparison.all.datasets
@@
 
-## dat.with.means and standard errors
-d = ddply(dat,c("dataset","site","AA","shell"), function(x) {
+## dat with means and standard errors
+d = ddply(dat,c("dataset", "site", "AA", "shell"), function(x) {
                 mean.z.RSD = mean(x$z.RSD, na.rm = T)
@@
 
-## read information about minimal active site distances
-m.min.da.CM = read.csv(file.path(data.dir, paste(p.ref, "_min.da.CM.ca.csv", sep = "")))
+## find the active site and its contacts
+active.sites = d$site[d$shell == 0]
+contacts.active.sites = d$site[d$shell == 1]
 
-z.RSD.exp = d$mean.z.RSD[d$dataset == "exp"]
-z.RSD.strong = d$mean.z.RSD[d$dataset == "mut+sel"]
-z.RSD.mut = d$mean.z.RSD[d$dataset == "mut"]
-
-plot(y = z.RSD.exp - z.RSD.strong, x = m.min.da.CM$min.da.ca, xlab = "minimal distance to active site (between CAs)")
-plot(y = z.RSD.exp - z.RSD.mut, x = m.min.da.CM$min.da.CM, xlab = "minimal distance to active site (between CMs)")
-
-print("agregar correlacion")
-
-#d$dataset = factor(d$dataset, levels = c("exp", "mut", "strong"))
-d$label = as.character(d$site)
-active.sites = d$site[d$shell == 0]
-
-p = ggplot(d,aes(x = site, y = mean.z.RSD, col = dataset, fill = dataset)) +
+## prepare plots with mean profiles and deviations
+p = ggplot(d, aes(x = site, y = mean.z.RSD, col = dataset, fill = dataset)) +
     geom_line() +
     geom_ribbon(aes(ymin = mean.z.RSD - f95 * se.z.RSD, ymax = mean.z.RSD + se.z.RSD), alpha = .4, show.legend = F) +
-    geom_vline(xintercept = active.sites, col = "grey", show.legend = F) +
+    geom_vline(xintercept = active.sites, show.legend = F) +
+    geom_vline(xintercept = contacts.active.sites, col = "grey", show.legend = F) +
     labs(x = "site", y = "structural divergence(mean z.RSD)") +
@@
 ## plot separate and comparative plots
-p.facet = p + facet_grid(dataset~., switch = "y") + theme(legend.position = "none")
+p.facet = p + facet_grid(dataset~., switch = "y") + theme(legend.position = "bottom")
 
@@
 
-#p + theme(legend.position = "bottom", legend.title = element_blank())
-
+## plot superimposed plots
 p + theme(legend.position = "bottom")
-
 ```
@@
 
-```{r}
-dat = siteComparison.all.datasets
+```{r-comparison_mean_z.RSD_vs_site}
 
-# dat.with.means and standard errors
-dat = ddply(dat,c("dataset", "site", "AA", "shell"), function(x) {
-                mean.z.RSD = mean(x$z.RSD, na.rm = T)
-                ndata = sum(!is.na(x$z.RSD))
-                se.z.RSD = sd(x$z.RSD, na.rm = T) / sqrt(ndata)
-                data.frame(mean.z.RSD, ndata, se.z.RSD)
-})
+# comparison of z.RSD profiles
 
-dat.exp = subset(dat, dataset == "exp")
-dat.mut = subset(dat, dataset == "mut")
-dat.strong = subset(dat, dataset == "strong")
+ggplot(d, aes(x = site, y = mean.z.RSD, col = dataset)) +
+  geom_line() +
+  geom_text(data = subset(d, dataset == "exp" & mean.z.RSD < -.5), aes(x = site, y = mean.z.RSD, label = site), nudge_y = -.1, size = 1.8)+
+  geom_vline(xintercept = active.sites, show.legend = F) +
+  geom_vline(xintercept = contacts.active.sites, col = "grey", show.legend = F) + 
+  scale_colour_manual(name = NULL, values = myColors)
 
-ggplot(dat, aes(x = site, y = mean.z.RSD, col = dataset)) + geom_line() +
-    geom_text(data = subset(dat, dataset == "exp" & mean.z.RSD < -.5), aes(x = site, y = mean.z.RSD, label = site), nudge_y = -.1, size = 1.8)
+# calculate correlations berween profiles
+d.exp = subset(d, dataset == "exp")
+d.mut = subset(d, dataset == "mut")
+d.strong = subset(d, dataset == "mut+sel")
 
-d = dat.exp
-d$d.exp.mut = dat.exp$mean.z.RSD - dat.mut$mean.z.RSD
-d$d.exp.strong = dat.exp$mean.z.RSD - dat.strong$mean.z.RSD
-d$d.strong.mut = dat.strong$mean.z.RSD - dat.mut$mean.z.RSD
-dd = melt(data = d[, c("site", "se.z.RSD", "d.exp.mut", "d.strong.mut")], c("site", "se.z.RSD"))
+# calculate cors
+r.exp.mut = cor(d.exp$mean.z.RSD, d.mut$mean.z.RSD)
+r.exp.strong = cor(d.exp$mean.z.RSD, d.strong$mean.z.RSD)
+r.mut.strong = cor(d.mut$mean.z.RSD, d.strong$mean.z.RSD)
 
-ggplot(dd, aes(x = site, y = value, col = variable)) +
-    geom_line() 
-r = round(cor(d$d.strong.mut, d$d.exp.mut), 2)
-
-ggplot(d, aes(x = scale(d.strong.mut), y = scale(d.exp.mut))) + 
-    geom_point(aes(col = shell == 0)) +
-    geom_smooth(method = "lm") +
-    geom_label(aes(x = 0, y = 3, label = paste("R =", as.character(r)))) +
-    labs(x = "predicted selection vs mutation (RSD change)",y="empirical vs mutation (RSD change)")
-
-r.exp.mut = cor(dat.exp$mean.z.RSD, dat.mut$mean.z.RSD)
-r.exp.strong = cor(dat.exp$mean.z.RSD, dat.strong$mean.z.RSD)
-r.mut.strong = cor(dat.mut$mean.z.RSD, dat.strong$mean.z.RSD)
 cor.df = data.frame("comparison" = c("exp vs mut", "exp vs strong", "mut vs strong"),
                     "R" = c(r.exp.mut, r.exp.strong, r.mut.strong))
-knitr::kable(cor.df, digits = 2)
+
+knitr::kable(cor.df, digits = 2, caption = "Correlation between <Z-scores> profiles")
 ```
 
-```{r write-pdb-files}
-# write pdb files with mean.z.RSDi as b-factor for building images
+### Distances to the active sites
 
-## read pdb CAs
-pdb.xyz.ca = ReadCA(reference.pdb.fname, chain.p.ref)$xyz
+```{r-comparison-da}
 
-## experimental
-exp.mean.z.RSD.vec <- vec2resno(as.vector(dat.exp$mean.z.RSD), sort(rep(1:ncol(pdb.xyz.ca),3)))
-write.pdb(xyz = c(pdb.xyz.ca), b = exp.mean.z.RSD.vec, file =  file.path(data.dir, paste(p.ref, "_exp.pdb", sep = "")))
+# comparison of means.z.scores with the minimum distance to the functional sites
+plot(y = d.exp$mean.z.RSD - d.mut$mean.z.RSD, x = m.min.da.CM.CA$min.da.ca, xlab = "minimal distance to active site (between CAs)", ylab = "exp.mean.z.RSD - mut.mean.z.RSD")
+plot(y = d.exp$mean.z.RSD - d.mut$mean.z.RSD, x = m.min.da.CM.CA$min.da.CM, xlab = "minimal distance to active site (between CMs)", ylab = "exp.mean.z.RSD - mut.mean.z.RSD")
 
-## mut
-mut.mean.z.RSD.vec <- vec2resno(as.vector(dat.mut$mean.z.RSD), sort(rep(1:ncol(pdb.xyz.ca),3)))
-write.pdb(xyz = c(pdb.xyz.ca), b = mut.mean.z.RSD.vec, file = file.path(data.dir, paste(p.ref, "_mut.pdb", sep = "")))
+## calculate correlations between profiles
+r.min.da.CA = cor((d.exp$mean.z.RSD - d.mut$mean.z.RSD), m.min.da.CM.CA$min.da.ca)
+r.min.da.CM = cor((d.exp$mean.z.RSD - d.mut$mean.z.RSD), m.min.da.CM.CA$min.da.CM)
 
-## mut + sel / strong
-strong.mean.z.RSD.vec <- vec2resno(as.vector(dat.strong$mean.z.RSD), sort(rep(1:ncol(pdb.xyz.ca),3)))
-write.pdb(xyz = c(pdb.xyz.ca), b = strong.mean.z.RSD.vec, file = file.path(data.dir, paste(p.ref, "_strong.pdb", sep = "")))
+cor.df = data.frame("comparison" = c("(exp - mut) vs min.da.CA", "(exp - mut) vs min.da.CM"), "R" = c(r.min.da.CA, r.min.da.CM))
+
+knitr::kable(cor.df, digits = 2, caption = "Correlation between differences in <Z-scores> profiles and the minimal distance to the active site")
 ```
 
-# Structural divergence along normal modes
-In this section we consider structural divergence using normal mode coordinates.
-Pn is the square divergence along a normal mode relative to the mean.
+```{r-comparisons-between-plots}
 
-[//]: Prepare mode data
+# plot exp vs simulated profiles 
+par(pty = "s")
 
-```{r prepare-mode-data}
-mode = seq(ncol(Pn.strong))
+plot(x = d.exp$mean.z.RSD, 
+     y = d.mut$mean.z.RSD, 
+     xlab = "exp.mean.z.RSD", 
+     ylab = "mut.mean.z.RSD", 
+     xlim = c(min(c(d.exp$mean.z.RSD, d.mut$mean.z.RSD)), max(c(d.exp$mean.z.RSD, d.mut$mean.z.RSD))),
+     ylim = c(min(c(d.exp$mean.z.RSD, d.mut$mean.z.RSD)), max(c(d.exp$mean.z.RSD, d.mut$mean.z.RSD))))
+points(x = as.numeric(d.exp$mean.z.RSD)[active.sites], y = as.numeric(d.mut$mean.z.RSD)[active.sites], col = "yellow")
+points(x = as.numeric(d.exp$mean.z.RSD)[contacts.active.sites], y = as.numeric(d.mut$mean.z.RSD)[contacts.active.sites], col = "green")
+abline(0, 1)
 
-# prepare modeComparison.strong
-tPn.strong = as.data.frame(t(as.matrix(Pn.strong)))
-tPn.strong = cbind(data.frame("mode" = mode), tPn.strong)
-Pn.strong.long = melt(tPn.strong, "mode", variable.name = "protein", value.name = "Pn")
+plot(x = d.exp$mean.z.RSD, 
+     y = d.strong$mean.z.RSD, 
+     xlab = "exp.mean.z.RSD", 
+     ylab = "strong.mean.z.RSD", 
+     xlim = c(min(c(d.exp$mean.z.RSD, d.strong$mean.z.RSD)), max(c(d.exp$mean.z.RSD, d.strong$mean.z.RSD))),
+     ylim = c(min(c(d.exp$mean.z.RSD, d.strong$mean.z.RSD)), max(c(d.exp$mean.z.RSD, d.strong$mean.z.RSD))))
+points(x = as.numeric(d.exp$mean.z.RSD)[contacts.active.sites], y = as.numeric(d.strong$mean.z.RSD)[contacts.active.sites], col = "green")
+points(x = as.numeric(d.exp$mean.z.RSD)[active.sites], y = as.numeric(d.strong$mean.z.RSD)[active.sites], col = "yellow")
+abline(0, 1)
 
-tenergy.strong = as.data.frame(t(as.matrix(energy.strong)))
-tenergy.strong = cbind(data.frame("mode" = mode), tenergy.strong)
-energy.strong.long = melt(tenergy.strong, "mode", variable.name = "protein", value.name = "energy")
-energy.strong.long$sn2 = 1/energy.strong.long$energy
-
-modeComparison.strong = merge(energy.strong.long, Pn.strong.long, by = c("mode", "protein"))
-
-modeComparison.strong = ddply(modeComparison.strong, "protein", mutate, "Pn" = Pn / mean(Pn, na.rm = T))
-
-# prepare modeComparison.mut
-tPn.mut = as.data.frame(t(as.matrix(Pn.mut)))
-tPn.mut = cbind(data.frame("mode" = mode), tPn.mut)
-Pn.mut.long = melt(tPn.mut, "mode", variable.name = "protein", value.name = "Pn")
-
-tenergy.mut = as.data.frame(t(as.matrix(energy.mut)))
-tenergy.mut = cbind(data.frame("mode" = mode), tenergy.mut)
-energy.mut.long = melt(tenergy.mut, "mode", variable.name = "protein", value.name = "energy")
-energy.mut.long$sn2 = 1/energy.mut.long$energy
-
-modeComparison.mut = merge(energy.mut.long, Pn.mut.long, by = c("mode", "protein"))
-modeComparison.mut = ddply(modeComparison.mut, "protein", mutate, "Pn" = Pn / mean(Pn, na.rm = T))
-
-# prepare modeComparison.exp
-tPn.exp = as.data.frame(t(as.matrix(Pn.exp)))
-tPn.exp = cbind(data.frame("mode" = mode), tPn.exp)
-Pn.exp.long = melt(tPn.exp, "mode", variable.name = "protein", value.name = "Pn")
-
-tenergy.exp = as.data.frame(t(as.matrix(energy.exp)))
-tenergy.exp = cbind(data.frame("mode" = mode), tenergy.exp)
-energy.exp.long = melt(tenergy.exp, "mode", variable.name = "protein", value.name = "energy")
-energy.exp.long$sn2 = 1/energy.exp.long$energy
-
-modeComparison.exp = merge(energy.exp.long,Pn.exp.long,by=c("mode", "protein"))
-
-# renormalize Pn
-modeComparison.exp = ddply(modeComparison.exp, "protein", mutate, "Pn" = Pn / mean(Pn, na.rm = T))
-
-# modeComparison.exp has NA's because for proteins with gaps when using Keff there're less modes
-# print("Warning: modeComparison <- na.omit(modeComparison)")
-
-modeComparison.exp <- na.omit(modeComparison.exp)
-modeComparison.strong <- na.omit(modeComparison.strong)
-modeComparison.mut <- na.omit(modeComparison.mut)
+plot(x = d.mut$mean.z.RSD, 
+     y = d.strong$mean.z.RSD, 
+     xlab = "mut.mean.z.RSD", 
+     ylab = "strong.mean.z.RSD", 
+     xlim = c(min(c(d.mut$mean.z.RSD, d.strong$mean.z.RSD)), max(c(d.mut$mean.z.RSD, d.strong$mean.z.RSD))),
+     ylim = c(min(c(d.mut$mean.z.RSD, d.strong$mean.z.RSD)), max(c(d.mut$mean.z.RSD, d.strong$mean.z.RSD))))
+points(x = as.numeric(d.mut$mean.z.RSD)[contacts.active.sites], y = as.numeric(d.strong$mean.z.RSD)[contacts.active.sites], col = "green")
+points(x = as.numeric(d.mut$mean.z.RSD)[active.sites], y = as.numeric(d.strong$mean.z.RSD)[active.sites], col = "yellow")
+abline(0, 1)
 ```
-
-[//]: Add quantile regression data
-
-```{r}
-# quantile regression
-
-## fit median and quantiles to simulated data and add them to data.frames
-fit.strong.rq.5 <- rq(Pn ~ sn2, tau = .5, data = modeComparison.strong, method = "fn")
-fit.strong.rq.05 <- rq(Pn ~ sn2, tau = .05, data = modeComparison.strong, method = "fn")
-fit.strong.rq.95 <- rq(Pn ~ sn2, tau = .95, data = modeComparison.strong, method = "fn")
-
-modeComparison.strong$rq.5 = fit.strong.rq.5$fitted.values
-modeComparison.strong$rq.05 = fit.strong.rq.05$fitted.values
-modeComparison.strong$rq.95 = fit.strong.rq.95$fitted.values
-
-## fit median and quantiles to simulated data and add them to data.frames
-fit.mut.rq.5 <- rq(Pn ~ sn2, tau = .5, data = modeComparison.mut, method = "fn")
-fit.mut.rq.05 <- rq(Pn ~ sn2, tau = .05, data = modeComparison.mut, method = "fn")
-fit.mut.rq.95 <- rq(Pn ~ sn2, tau = .95, data = modeComparison.mut, method = "fn")
-
-modeComparison.mut$rq.5 = fit.mut.rq.5$fitted.values
-modeComparison.mut$rq.05 = fit.mut.rq.05$fitted.values
-modeComparison.mut$rq.95 = fit.mut.rq.95$fitted.values
-
-## fit median and quantiles to experimental data
-fit.exp.rq.5 <- rq(Pn ~ sn2, tau = .5, data = modeComparison.exp, method = "fn")
-fit.exp.rq.05 <- rq(Pn ~ sn2, tau = .05, data = modeComparison.exp, method = "fn")
-fit.exp.rq.95 <- rq(Pn ~ sn2, tau = .95, data = modeComparison.exp, method = "fn")
-
-modeComparison.exp$rq.5 = fit.exp.rq.5$fitted.values
-modeComparison.exp$rq.05 = fit.exp.rq.05$fitted.values
-modeComparison.exp$rq.95 = fit.exp.rq.95$fitted.values
-
-## put simulated and experimental data together
-
-modeComparison.all.datasets = rbind(data.frame("dataset" = "exp", modeComparison.exp),
-                                    data.frame("dataset" = "mut", modeComparison.mut),
-                                    data.frame("dataset" = "strong", modeComparison.strong))
-
-modeComparison.all.datasets$dataset = factor(modeComparison.all.datasets$dataset, levels = c("exp", "mut", "strong"))
-```
-
-### Pn vs. mode energy
-
-Note: lines are the median, 0.05 and 0.95 quantiles fit using rq(Pn ~ sn2).
-sn2 = 1/energy is the expected MSD of along mode n. 
-The mean value of Pn should be a linear function of sn2 (Pn is normalized, sn2 is not).
-
-Here we show the square deviation along each normal mode (normalized so that <Pn> = 1) vs.
-the normal-mode's energy.
-For the empirical data, we use the actual energy obtained from Keff for the given comparison.
-It is this energy the one that should be used, since it's inverse is the expected value of Pn.
-Lines are the .5 (median), .05, and .95 quantiles obtained using `rq()`
-- Upper panel: simulated vs empirical data, shown separately.
-- Lower panel: simulated vs empirical overlaped and zoomed to better see the pattern.
-
-```{r Pn-vs-mode-energy}
-# plot Pn vs energy
-dat = modeComparison.all.datasets
-dat$dataset = revalue(dat$dataset,c("strong" = "mut+sel"))
-
-# p is just the median and quantiles
-p.points.rq = ggplot(dat, aes(x = energy, y = Pn, col = dataset)) + 
-    geom_point(alpha = .4, size = .2) +
-    geom_line(aes(y = rq.5)) +
-    geom_line(aes(y = rq.05)) +
-    geom_line(aes(y = rq.95)) 
-p = p.points.rq +  
-    labs(x = "mode energy", y = "structural divergence") +
-    scale_colour_manual(name = NULL, values = myColors) + 
-    scale_fill_manual(name = NULL, values = myColors)
-
-p.facet = p + facet_grid(dataset~., switch = "y") + theme(legend.position = "none")
-p.facet %+% subset(dat, dataset == "exp")
-p.facet %+% subset(dat, dataset == "mut")
-p.facet %+% subset(dat, dataset == "mut+sel")
-p.facet
-```
-
-### median(Pn) vs mode energy
-
-```{r median-Pn-vs-mode-energy}
-dat = modeComparison.all.datasets
-dat$dataset = revalue(dat$dataset,c("strong" = "mut+sel"))
-
-# calculate dataset of medians
-
-dat = ddply(dat,c("dataset", "mode"), function(x) {
-    energy.mean = mean(x$energy)
-    Pn.median = median(x$Pn)
-    Pn.median.ci = sort(x$Pn)[qbinom(c(.025, .975), length(x$Pn), 0.5)]
-    Pn.median.min = Pn.median.ci[1]
-    Pn.median.max = Pn.median.ci[2]
-    rq.5 = mean(x$rq.5)
-    data.frame(energy.mean, Pn.median.min, Pn.median.max, Pn.median, rq.5)
-})
-
-p = ggplot(dat,aes(x=energy.mean,y=Pn.median,col=dataset,fill=dataset)) +
-    geom_pointrange(aes(ymin = Pn.median.min,ymax = Pn.median.max), size = .2, alpha = .4) +
-    geom_line(aes(y = rq.5))  +
-    labs(x = "mode energy", y = "structural divergence (median Pn) ") +
-    scale_colour_manual(name = NULL, values = myColors) + 
-    scale_fill_manual(name = NULL, values = myColors)
-
-p.facet = p + facet_grid(dataset~., switch = "y") + theme(legend.position = "none")
-p.facet %+% subset(dat,dataset == "exp")
-p.facet %+% subset(dat,dataset == "mut")
-p.facet %+% subset(dat,dataset == "mut+sel")
-p.facet
-p + theme(legend.position = "bottom")
-
-```
-
-### Correlation between mode profiles
-
-```{r}
-dat = modeComparison.all.datasets
-
-#dat$dataset = revalue(dat$dataset,c("strong" = "mut+sel"))
-
-# calculate dataset of medians
-dat = ddply(dat, c("dataset", "mode"), function(x) {
-    energy.mean = mean(x$energy)
-    Pn.median = median(x$Pn)
-    data.frame(energy.mean, Pn.median)
-})
-
-dat = subset(dat, mode < 101)
-dat.exp = subset(dat, dataset == "exp")
-dat.mut = subset(dat,dataset == "mut")
-dat.strong = subset(dat,dataset == "strong")
-
-r.exp.mut = cor(dat.exp$Pn.median, dat.mut$Pn.median)
-r.exp.strong = cor(dat.exp$Pn.median, dat.strong$Pn.median)
-r.mut.strong = cor(dat.mut$Pn.median, dat.strong$Pn.median)
-cor.df = data.frame("comparison" = c("exp vs mut", "exp vs strong", "mut vs strong"),
-                    "R" = c(r.exp.mut, r.exp.strong, r.mut.strong))
-knitr::kable(cor.df, digits = 2)
-```

### 2017-01-08 FUNCTIONS/CalculateDynamicalVariability.R

@@ -32,22 +32,27 @@ CalculateDynamicalVariability <- function(r.p.1,
   ## get eigen vectors
   ve.p.1 = ENMK.p.1$ve
   ve.p.2 = ENMK.p.2$ve
+  
+  # calculate nH and nR
+  overlap = t(ve.p.1) %*% ve.p.2
+  nH = exp( - rowSums(overlap ^ 2 * log(overlap ^ 2 + tolerance)))
+  nR = 1 / rowSums(overlap ^ 4)
 
   # calculate Mean Square Fluctuation
   ## get the diagonal of the cov matrix
   diag.p.1 = diag(cov.p.1)
   diag.p.2 = diag(cov.p.2)
 
-  ## calculate the factor to divide the diagonal
+  ## calculate the factor to split the diagonal
   factor = sort(rep(seq(1:n.aligned), 3))
 
-  ## separate the diagonal
+  ## split the diagonal
   s.diag.p.1 = split(diag.p.1, factor)
   s.diag.p.2 = split(diag.p.2, factor)
 
-  ## create matrices to save data
-  MSF.p.1 = matrix(rnow = 1, ncol = n.aligned)
-  MSF.p.2 = matrix(rnow = 1, ncol = n.aligned)
+  ## create matrices to save the data
+  MSF.p.1 = matrix(nrow = 1, ncol = n.aligned)
+  MSF.p.2 = matrix(nrow = 1, ncol = n.aligned)
 
   ## start a loop to calculate sums for each site
   for (i in (1:n.aligned)) {
@@ -57,11 +62,6 @@ CalculateDynamicalVariability <- function(r.p.1,
  
   ## calculate the difference
   square.dif.MSF = (MSF.p.1 - MSF.p.2) ^ 2
-  
-  # calculate nH and nR
-  overlap = t(ve.p.1) %*% ve.p.2
-  nH = exp( - rowSums(overlap ^ 2 * log(overlap ^ 2 + tolerance)))
-  nR = 1 / rowSums(overlap ^ 4)
   
   # create a list for the output
   out = list("MSF.p.1" = MSF.p.1,

### 2017-01-08 FUNCTIONS/CalculateSideChainCM.R

@@ -14,45 +14,84 @@ CalculateSideChainCM <- function(pdb.fname, chain) {
   # Read pdb
   pdb <- read.pdb(file = pdb.fname)
   
-  # Get n.aa of the chain
-  sel.ca <- atom.select(pdb, chain = chain, elety = "CA")    
+  # get information from de pdb
+  sel.ca <- atom.select(pdb, chain = chain, elety = "CA")
   site.ca = as.numeric(pdb$atom[sel.ca$atom, c("resno")])    
-  n.aa = length(site.ca)    
-
-  # Create a matrix to the save the centers of mass
+  n.aa = length(site.ca)  
+  
+  # create a matrix to the save the centers of mass
   xyz.side.chain.CM = matrix(nrow = 3, ncol = n.aa)
   
-  # Star a loop to analyze each residue
-  for (i in (site.ca)) { 
-    
-    # Extract information of the chain
-    sel <- atom.select(pdb, chain = chain, strain = "protein", resno = i)    
-    site.elety <- pdb$atom[sel$atom, c("elety")]     
-    n.atoms = length(site.elety) 
-    xyz.site <- matrix(pdb$xyz[sel$xyz], nrow = 3, byrow = F)     
+  # start to count sites
+  site = 0
   
-    # Get weights
-    weights = matrix(nrow = n.atoms)
-
-    index.C = which(grepl("C", site.elety))
-    index.O = which(grepl("O", site.elety))
-    index.N = which(grepl("N", site.elety))
-    index.S = which(grepl("S", site.elety))
+  # key for run
+  key = 1
+  # star a loop to analyze each residue
+  for (i in (site.ca)) { 
+    if (key == 1) {
+      
+      # count a site
+      site = site + 1
+      print(site)
+  
+      # Extract information of the resid
+      sel <- atom.select(pdb, chain = chain, strain = "protein", resno = i)    
+      site.elety <- pdb$atom[sel$atom, c("elety")] 
+      site.resid <- pdb$atom[sel$atom, c("resid")]     
+      n.atoms = length(site.elety) 
+      xyz.site <- matrix(pdb$xyz[sel$xyz], nrow = 3, byrow = F)     
+  
+      # Get weights
+      weights = matrix(nrow = n.atoms)
+  
+      index.C = which(grepl("C", site.elety))
+      index.O = which(grepl("O", site.elety))
[…]

### 2017-01-08 FUNCTIONS/MakeBlast.R

@@ -1,32 +1,42 @@
 # input
-# n.seq = 10
-# p.ref = "1a6m"
-# chain = "A"
+ n.seq = 10
+ p.ref = "1a6m"
+ chain = "A"
 
 # libraries
-# bio3d
+library("bio3d")
 
-# get the pdb file of coordinates of p.ref
+# get the pdb file of p.ref
 get.pdb(p.ref)
 
 # read the file
-pdb <- read.pdb(paste(p.ref, ".pdb", sep = ""))    
-sel <- atom.select(pdb, chain = chain, elety = "CA")    
+pdb <- read.pdb(paste(p.ref, ".pdb", sep = "")) 
+sel <- atom.select(pdb, chain = chain, elety = "CA")  
 seq <- pdb$atom[sel$atom, c("resid")]
+
+# code maps
+code3 <- c("Ala", "Arg", "Asn", "Asp", "Cys", "Glu", "Gln", "Gly", "His", 
+           "Ile", "Leu", "Lys", "Met", "Phe", "Pro", "Ser", "Thr", "Trp", 
+           "Tyr", "Val")
+code1 <- c("A", "R", "N", "D", "C", "E", "Q", "G", "H", "I", "L", "K", 
+           "M", "F", "P", "S", "T", "W", "Y", "V")
+
+# for each code replace 3letter code by 1letter code:
+for (i in 1:length(code3)) {
+  seq <- gsub(code3[i], code1[i], seq, ignore.case = TRUE)
+}
 
 # make a blast
 blast.info <- blast.pdb(seq, database = "pdb")
-score = blast.info$mlog.evalue
-pdbid = blast.info$pdb.id
-identity = blast.info$hit.tbl[, 3]
+score = blast.info$hit.tbl$bitscore
+pdbid = blast.info$hit.tbl$pdb.id
+identity = blast.info$hit.tbl$identity
 
-# filter
-filter = (pdbid != p.ref)
-pdbid = pdbid[filter][1:n.seq]
-score = score[filter][1:n.seq]
+# filter too similar proteins
+filter = (pdbid != paste(toupper(p.ref), "_", toupper(chain), sep = ""))
+pdbid = pdbid[filter]
+identity = identity[filter]
 
-# align with muscle
-
-# get indeces
-
-# write output
+filter2 = (identity < 90)
+pdbid = pdbid[filter2]
+identity = identity[filter2]

### 2017-01-08 MainProgram.R

@@ -26,27 +26,27 @@
 
 ### PROGRAM ###
 
-# Remove objects from the workspace
+# remove objects from the workspace
 rm(list = ls())
 
-# Load packages
+# load packages
 library(bio3d) 
 library(seqinr) 
 
-# Data dir
+# data dir
 data.dir <- "DATA"
 
-# Set Elastic Network Model: "ANM" or "pfANM"
+# set Elastic Network Model: "ANM" or "pfANM"
 model <- "ANM"
 
-# Output dir
+# output dir
 if (model == "ANM") out.dir <- "OUT/out_subset_CA_ANM"
 if (model == "pfANM") out.dir <- "OUT/out_subset_CA_pfANM"
 
-# General parameters
+# general parameters
 tolerance = 1e-10
 
-# Function filenames
+# function filenames
 AnalyzeExperimentalTheoretical.fname <- "FUNCTIONS/AnalyzeExperimentalTheoretical.R"
 AnalyzeFamily.fname <- "FUNCTIONS/AnalyzeFamily.R"
 AnalyzeAlignment.fname <- "FUNCTIONS/AnalyzeAlignment.R"
@@ -58,6 +58,8 @@ CalculateENMKeff.fname <- "FUNCTIONS/CalculateENMKeff.R"
 CalculateENMK.fname <- "FUNCTIONS/CalculateENMK.R"
 CalculateVariability.fname <- "FUNCTIONS/CalculateVariability.R"
 GetCore.fname <- "FUNCTIONS/GetCore.R"
+WindowsRMSD.fname <- "FUNCTIONS/WindowsRMSD.R"
+WindowsRMSDcontacts.fname <- "FUNCTIONS/WindowsRMSDcontacts.R"
 
 if (model == "ANM") {
   CalculateBetas.fname <- "FUNCTIONS/CalculateBetas.R"
@@ -71,7 +73,7 @@ if (model == "pfANM") {
   CalculateForce.fname <- "FUNCTIONS/CalculateForcePFANM.R"
 }
 
-# Source functions
+# source functions
 source(AnalyzeExperimentalTheoretical.fname)
 source(AnalyzeFamily.fname)
 source(AnalyzeAlignment.fname)
@@ -83,16 +85,18 @@ source(CalculateENMKeff.fname)
 source(CalculateENMK.fname)
 source(CalculateVariability.fname)
 source(GetCore.fname)
+source(WindowsRMSD.fname)
[…]

### 2017-01-19 analysis-structure-core.Rmd
cambios 19/01/17

@@
 site.info.fname = file.path(data.dir, paste(p.ref, "_m.da.ca.csv", sep = ""))
-min.da.CM.CA.fname = file.path(data.dir, paste(p.ref, "_m.da.ca.csv", sep = ""))
+min.da.CM.CA.fname = file.path(data.dir, paste(p.ref, "_min.da.CM.ca.csv", sep = ""))
 
@@
 ```
+### Distance to the active site
+
+```{r-comparison-da}
+
+# comparison of means.z.scores with the minimum distance to the functional sites
+plot(y = d.exp$mean.z.RSD - d.mut$mean.z.RSD, x = m.min.da.CM.CA$min.da.ca[indexes.core], xlab = "minimal distance to active site (between CAs)", ylab = "exp.mean.z.RSD - mut.mean.z.RSD")
+plot(y = d.exp$mean.z.RSD - d.mut$mean.z.RSD, x = m.min.da.CM.CA$min.da.CM[indexes.core], xlab = "minimal distance to active site (between CMs)", ylab = "exp.mean.z.RSD - mut.mean.z.RSD")
+
+## calculate correlations between profiles
+r.min.da.CA = cor((d.exp$mean.z.RSD - d.mut$mean.z.RSD), m.min.da.CM.CA$min.da.ca[indexes.core])
+r.min.da.CM = cor((d.exp$mean.z.RSD - d.mut$mean.z.RSD), m.min.da.CM.CA$min.da.CM[indexes.core])
+
+cor.df = data.frame("comparison" = c("(exp - mut) vs min.da.CA", "(exp - mut) vs min.da.CM"), "R" = c(r.min.da.CA, r.min.da.CM))
+
+knitr::kable(cor.df, digits = 2, caption = "Correlation between differences in <Z-scores> profiles and the minimal distance to the active site")
+```

### 2017-01-19 analysis-structure-normal-modes.Rmd
cambios 19/01/17

@@
 
-## exp
-tdri2.exp = as.data.frame(t(as.matrix(dri2.exp)))
-tdri2.exp = cbind(site.info, tdri2.exp)
-siteComparison.exp = melt(tdri2.exp, id.vars = names(site.info), variable.name = "protein", value.name = "dri2")
-
-## mut
-tdri2.mut = as.data.frame(t(as.matrix(dri2.mut)))
-tdri2.mut = cbind(site.info, tdri2.mut)
-siteComparison.mut = melt(tdri2.mut, id.vars = names(site.info), variable.name = "protein", value.name = "dri2")
-
-## strong
-tdri2.strong = as.data.frame(t(as.matrix(dri2.strong)))
-tdri2.strong = cbind(site.info, tdri2.strong)
-siteComparison.strong = melt(tdri2.strong, id.vars = names(site.info), variable.name = "protein", value.name = "dri2")
-
-# bluild the data.frame
-siteComparison.all.datasets = rbind(data.frame("dataset" = "exp", siteComparison.exp),
-                                    data.frame("dataset" = "mut", siteComparison.mut),
-                                    data.frame("dataset" = "strong", siteComparison.strong))
-
-siteComparison.all.datasets = ddply(siteComparison.all.datasets, c("dataset", "protein"), mutate,
-          "n.SD" = dri2/mean(dri2, na.rm = T),
-          "z.SD" = vscale(dri2),
-          "RSD" = sqrt(dri2), 
-          "n.RSD" = RSD/mean(RSD, na.rm = T),
-          "z.RSD" = vscale(RSD))
 ```
@@
 
-```{r-prepare-mode-data}
+```{r prepare-mode-data}
 mode = seq(ncol(Pn.strong))
@@
 
-```{r-add-quantile-regression-data}
+```{r add-quantile-regression-data}
 
@@
 
-```{r-Pn-vs-energy}
+```{r Pn-vs-energy}
 
@@
 
-```{r-median-vs-mode-energy}
+```{r median-vs-mode-energy}
 
@@
 
-p.facet = p + facet_grid(dataset~.,switch="y") + theme(legend.position="none")
-p.facet %+% subset(dat,dataset =="exp")
+p.facet = p + facet_grid(dataset~., switch = "y") + theme(legend.position = "none")
+p.facet %+% subset(dat,dataset == "exp")
 p.facet %+% subset(dat,dataset == "mut")
@@
 
-```{r-correlation-mode-profiles}
+```{r correlation-mode-profiles}
 dat = modeComparison.all.datasets

### 2017-01-19 analysis-structure.Rmd
cambios 19/01/17

@@
 source(file.path(data.dir, "my-functions.R"))
+source("FUNCTIONS/readCA.R") 
 ```
@@
 min.da.CM.CA.fname = file.path(data.dir, paste(p.ref, "_min.da.CM.ca.csv", sep = ""))
+functional.sites.fname = file.path("DATA", paste(p.ref, "_functionalSites.csv", sep = ""))
 
@@
 
+```{r read_functional_sites}
+# which are the functional sites?
+functional.sites = read.csv(functional.sites.fname, sep = ";")
+active.site.index = functional.sites$index
+description = functional.sites$description
+function.info = data.frame(active.site.index, description)
+```
+
 We studied the `r family` family. 
@@
 We used as reference for the ENM the protein with pdb code `r reference`. 
+The active.sites sites of the reference are:
+```{r}
+print(function.info)
+```
+
 We simulated `r n.mut.p` mutants of this reference for each protein of the family.
@@
 
-# define shells of active site neighborhood
+# define shells of active.sites site neighborhood
 d$shell = cut(d$da, breaks = c(-.1, 2.5, 7.5, 12.5, 17.5, 22.5, 27.5, 32.5, 37.5, 42.5, 47.5, 52.5, max(d$da)))
@@
 
-```{r-comparison_mean_z.RSD_vs_site}
+```{r-comparison-mean-z.RSD-vs-site}
 
@@
 knitr::kable(cor.df, digits = 2, caption = "Correlation between <Z-scores> profiles")
-```
-
-### Distances to the active sites
-
-```{r-comparison-da}
-
-# comparison of means.z.scores with the minimum distance to the functional sites
-plot(y = d.exp$mean.z.RSD - d.mut$mean.z.RSD, x = m.min.da.CM.CA$min.da.ca, xlab = "minimal distance to active site (between CAs)", ylab = "exp.mean.z.RSD - mut.mean.z.RSD")
-plot(y = d.exp$mean.z.RSD - d.mut$mean.z.RSD, x = m.min.da.CM.CA$min.da.CM, xlab = "minimal distance to active site (between CMs)", ylab = "exp.mean.z.RSD - mut.mean.z.RSD")
-
-## calculate correlations between profiles
-r.min.da.CA = cor((d.exp$mean.z.RSD - d.mut$mean.z.RSD), m.min.da.CM.CA$min.da.ca)
-r.min.da.CM = cor((d.exp$mean.z.RSD - d.mut$mean.z.RSD), m.min.da.CM.CA$min.da.CM)
-
-cor.df = data.frame("comparison" = c("(exp - mut) vs min.da.CA", "(exp - mut) vs min.da.CM"), "R" = c(r.min.da.CA, r.min.da.CM))
-
-knitr::kable(cor.df, digits = 2, caption = "Correlation between differences in <Z-scores> profiles and the minimal distance to the active site")
 ```
@@
 ```
+
+### Distances to the active sites
+
+```{r-comparison-da}
+
+# comparison of means.z.scores with the minimum distance to the functional sites
+plot(y = d.exp$mean.z.RSD - d.mut$mean.z.RSD, x = m.min.da.CM.CA$min.da.ca, xlab = "minimal distance to active site (between CAs)", ylab = "exp.mean.z.RSD - mut.mean.z.RSD")
+plot(y = d.exp$mean.z.RSD - d.mut$mean.z.RSD, x = m.min.da.CM.CA$min.da.CM, xlab = "minimal distance to active site (between CMs)", ylab = "exp.mean.z.RSD - mut.mean.z.RSD")
+
+## calculate correlations between profiles
+r.min.da.CA = cor((d.exp$mean.z.RSD - d.mut$mean.z.RSD), m.min.da.CM.CA$min.da.ca)
+r.min.da.CM = cor((d.exp$mean.z.RSD - d.mut$mean.z.RSD), m.min.da.CM.CA$min.da.CM)
+
+cor.df = data.frame("comparison" = c("(exp - mut) vs min.da.CA", "(exp - mut) vs min.da.CM"), "R" = c(r.min.da.CA, r.min.da.CM))
+
+knitr::kable(cor.df, digits = 2, caption = "Correlation between differences in <Z-scores> profiles and the minimal distance to the active site")
+```
+
+```{r-write-pdbs} 
+# write pdb files with mean.z.RSDi as b-factor for building images
+
+## read pdb CAs
+pdb.xyz.ca = ReadCA(reference.pdb.fname, chain.p.ref)$xyz
+
+## experimental
+exp.mean.z.RSD.vec <- vec2resno(as.vector(d.exp$mean.z.RSD), sort(rep(1:ncol(pdb.xyz.ca),3)))
+write.pdb(xyz = c(pdb.xyz.ca), b = exp.mean.z.RSD.vec, file =  file.path(data.dir, paste(p.ref, "_exp.pdb", sep = "")))
+
+## mut
+mut.mean.z.RSD.vec <- vec2resno(as.vector(d.mut$mean.z.RSD), sort(rep(1:ncol(pdb.xyz.ca),3)))
+write.pdb(xyz = c(pdb.xyz.ca), b = mut.mean.z.RSD.vec, file = file.path(data.dir, paste(p.ref, "_mut.pdb", sep = "")))
+
+## mut + sel / strong
+strong.mean.z.RSD.vec <- vec2resno(as.vector(d.strong$mean.z.RSD), sort(rep(1:ncol(pdb.xyz.ca),3)))
+write.pdb(xyz = c(pdb.xyz.ca), b = strong.mean.z.RSD.vec, file = file.path(data.dir, paste(p.ref, "_strong.pdb", sep = "")))
+```

### 2017-01-19 FUNCTIONS/CalculateBetas.R

@@ -71,13 +71,13 @@ CalculateBetas <- function(chain.p.ref,
   f2 = mean((fmax * runif(1e6, -1, 1)) ^ 2)
   
   # Caculate betas for differente selection regimes.
-  beta.0.2 = round(- log(0.1) / (f2 * mean.CN), digits = 3) # Strong selection
+  beta.0.1 = round(- log(0.1) / (f2 * mean.CN), digits = 3) # Strong selection
   beta.0.5 = round(- log(0.5) / (f2 * mean.CN), digits = 3) # Medium selection
-  beta.0.8 = round(- log(0.9) / (f2 * mean.CN), digits = 3) # Weak selection
+  beta.0.9 = round(- log(0.9) / (f2 * mean.CN), digits = 3) # Weak selection
   beta.1 = round(- log(1) / (f2 * mean.CN), digits = 3) # No selection
   
   # Build a list with betas
-  all.betas = list("strong.sel" = beta.0.2, "medium.sel" = beta.0.5, "weak.sel" = beta.0.8, "no.sel" = beta.1) 
+  all.betas = list("strong.sel" = beta.0.1, "medium.sel" = beta.0.5, "weak.sel" = beta.0.9, "no.sel" = beta.1) 
   
   # Create a file to save the data
   write.csv(all.betas, file = file.path(out.dir, paste(betas.fname.id, "_out_all.betas.csv", sep = "")), row.names = FALSE)

### 2017-02-20 analysis-structure-core.Rmd
cambios 20/2/2017

@@
 
-```{r load_packages}
+```{r load-packages}
 # load packages
@@
 
-```{r set_my_colors}
+```{r set-my-colors}
 # set my colors
@@
 
-```{r set_run_variables}
+```{r set-run-variables}
 # set significance factors
@@
 
-```{r set_file_names}
+```{r set-file-names}
 # set input filenames
@@
 
-```{r set_reference_protein}
+```{r set-reference-protein}
 # which is the reference protein?
@@
 
-```{r set_experimental_protein_names, comment = ""}
+```{r set-experimental-protein-names, comment = ""}
 # experimental protein names
@@
 
-```{r read_the_core, comment = ""}
+```{r read-the-core, comment = ""}
 # indexes.core
@@
 
-```{r set_site_info}
+```{r set-site-info}
 # read site information of the reference protein
@@
 CN = rowSums(cmap.ca, na.rm = T) - 1 # diag(cmap.ca) returned by cmap is 1!
+n.sites = length(CN)
 AA = ref.pdb.ca$resid
@@
 
-```{r read_data}
+```{r read-data}
 # read data
@@
 
-```{r prepare_site_data}
+```{r prepare-site-data}
 # prepare the data
@@
 
-```{r mean_se_z.RSD_vs_site, fig.cap = "Black lines are the active sites and grey lines are their contacts"}
+```{r mean-se-z.RSD-vs-site, fig.cap = "Black lines are the active sites and grey lines are their contacts"}
 # comparison of z.RSD profiles with functional sites
@@
 
-```{r-comparison-mean-z.RSD-vs-site, fig.cap = "Black lines are the active sites and grey lines are their contacts"}
+```{r comparison-mean-z.RSD-vs-site, fig.cap = "Black lines are the active sites and grey lines are their contacts"}
 
@@
 
-```{r-comparison-da}
+```{r comparison-min.da}
 
 # comparison of means.z.scores with the minimum distance to the functional sites
-plot(y = d.exp$mean.z.RSD - d.mut$mean.z.RSD, x = m.min.da.CM.CA$min.da.ca[indexes.core], xlab = "minimal distance to active site (between CAs)", ylab = "exp.mean.z.RSD - mut.mean.z.RSD")
+plot(y = d.exp$mean.z.RSD - d.mut$mean.z.RSD, x = m.min.da.CM.CA$min.da.CA[indexes.core], xlab = "minimal distance to active site (between CAs)", ylab = "exp.mean.z.RSD - mut.mean.z.RSD")
 plot(y = d.exp$mean.z.RSD - d.mut$mean.z.RSD, x = m.min.da.CM.CA$min.da.CM[indexes.core], xlab = "minimal distance to active site (between CMs)", ylab = "exp.mean.z.RSD - mut.mean.z.RSD")
@@
 ## calculate correlations between profiles
-r.min.da.CA = cor((d.exp$mean.z.RSD - d.mut$mean.z.RSD), m.min.da.CM.CA$min.da.ca[indexes.core])
+r.min.da.CA = cor((d.exp$mean.z.RSD - d.mut$mean.z.RSD), m.min.da.CM.CA$min.da.CA[indexes.core])
 r.min.da.CM = cor((d.exp$mean.z.RSD - d.mut$mean.z.RSD), m.min.da.CM.CA$min.da.CM[indexes.core])

### 2017-02-20 analysis-structure.Rmd
cambios 20/2/2017

@@
 min.da.CM.CA.fname = file.path(data.dir, paste(p.ref, "_min.da.CM.ca.csv", sep = ""))
+sum.inv.da.CM.CA.fname = file.path(data.dir, paste(p.ref, "_sum.inv.da.CM.ca.csv", sep = ""))
 functional.sites.fname = file.path("DATA", paste(p.ref, "_functionalSites.csv", sep = ""))
@@
 dri2.mut.fname = file.path(data.dir,paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
+
+## consurf
+score.fname = file.path(data.dir, paste(p.ref, "_consurf.csv", sep = ""))
+sim.data.no.sel.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_out_df.data.csv", sep = ""))
+sim.data.strong.sel.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_strong.sel_out_df.data.csv", sep = ""))
+
 ```
 
-```{r set_reference_protein}
+```{r set-reference-protein}
 # which is the reference protein?
@@
 
-```{r read_functional_sites}
+```{r read-functional-sites}
 # which are the functional sites?
@@
 
-We studied the `r family` family. 
+In this case we studied the `r family` family. 
 We used the ENM `r enm` with R0 = `r R0` to generate mutants.
 We used as reference for the ENM the protein with pdb code `r reference`. 
-The active.sites sites of the reference are:
-```{r}
+The active/functional sites of the reference are:
+
+```{r print-info}
 print(function.info)
@@
 
-```{r set_experimental_protein_names, comment = ""}
+```{r set-experimental-protein-names}
 # experimental protein names
@@
 m.min.da.CM.CA = read.csv(min.da.CM.CA.fname)
+m.sum.inv.da.CM.CA = read.csv(sum.inv.da.CM.CA.fname)
 
@@
 
-```{r-mean_se_z.RSD_vs_site, fig.cap = "Black lines are the active sites and grey lines are their contacts"}
+```{r-mean-se-z.RSD-vs-site, fig.cap = "Black lines are the active sites and grey lines are their contacts"}
 # comparison of z.RSD profiles with functional sites
@@
 
-### Correlation between site profiles
+### Correlation between profiles
 
-```{r-comparison-mean-z.RSD-vs-site}
+```{r comparison-mean-z.RSD-vs-site}
 
@@
 
-```{r-comparisons-between-plots}
+### Comparison between profiles
+
+```{r comparisons-between-plots}
 
@@
 
-```{r-comparison-da}
+```{r comparison-min.da}
 
 # comparison of means.z.scores with the minimum distance to the functional sites
-plot(y = d.exp$mean.z.RSD - d.mut$mean.z.RSD, x = m.min.da.CM.CA$min.da.ca, xlab = "minimal distance to active site (between CAs)", ylab = "exp.mean.z.RSD - mut.mean.z.RSD")
+plot(y = d.exp$mean.z.RSD - d.mut$mean.z.RSD, x = m.min.da.CM.CA$min.da.CA, xlab = "minimal distance to active site (between CAs)", ylab = "exp.mean.z.RSD - mut.mean.z.RSD")
 plot(y = d.exp$mean.z.RSD - d.mut$mean.z.RSD, x = m.min.da.CM.CA$min.da.CM, xlab = "minimal distance to active site (between CMs)", ylab = "exp.mean.z.RSD - mut.mean.z.RSD")
@@
 ## calculate correlations between profiles
-r.min.da.CA = cor((d.exp$mean.z.RSD - d.mut$mean.z.RSD), m.min.da.CM.CA$min.da.ca)
+r.min.da.CA = cor((d.exp$mean.z.RSD - d.mut$mean.z.RSD), m.min.da.CM.CA$min.da.CA)
 r.min.da.CM = cor((d.exp$mean.z.RSD - d.mut$mean.z.RSD), m.min.da.CM.CA$min.da.CM)
@@
 
-```{r-write-pdbs} 
+```{r comparison-sum.inv.da}
+
+# comparison of means.z.scores with the sum.inv distance to the functional sites
+plot(y = d.exp$mean.z.RSD - d.mut$mean.z.RSD, x = m.sum.inv.da.CM.CA$sum.inv.da.CA, xlab = "sum.inv distance to active site (between CAs)", ylab = "exp.mean.z.RSD - mut.mean.z.RSD")
+plot(y = d.exp$mean.z.RSD - d.mut$mean.z.RSD, x = m.sum.inv.da.CM.CA$sum.inv.da.CM, xlab = "sum.inv distance to active site (between CMs)", ylab = "exp.mean.z.RSD - mut.mean.z.RSD")
+
+## calculate correlations between profiles
+r.sum.inv.da.CA = cor((d.exp$mean.z.RSD - d.mut$mean.z.RSD), m.sum.inv.da.CM.CA$sum.inv.da.CA)
+r.sum.inv.da.CM = cor((d.exp$mean.z.RSD - d.mut$mean.z.RSD), m.sum.inv.da.CM.CA$sum.inv.da.CM)
+
+cor.df = data.frame("comparison" = c("(exp - mut) vs sum.inv.da.CA", "(exp - mut) vs sum.inv.da.CM"), "R" = c(r.sum.inv.da.CA, r.sum.inv.da.CM))
+
+knitr::kable(cor.df, digits = 2, caption = "Correlation between differences in <Z-scores> profiles and the sum.inv distance to the active site")
+```
+
+```{r correlation-da-CN} 
+## calculate correlations between profiles
+r.min.da.CA.CN = cor(CN, m.min.da.CM.CA$min.da.CA)
+r.min.da.CM.CN = cor(CN, m.min.da.CM.CA$min.da.CM)
+
+cor.df = data.frame("comparison" = c("CN vs min.da.CA", "CN vs min.da.CM"), "R" = c(r.min.da.CA.CN, r.min.da.CM.CN))
+
+knitr::kable(cor.df, digits = 2, caption = "Correlation between CN and the minimal distance to the active site")
+
+## calculate correlations between profiles
+r.sum.inv.da.CA.CN = cor(CN, m.sum.inv.da.CM.CA$sum.inv.da.CA)
+r.sum.inv.da.CM.CN = cor(CN, m.sum.inv.da.CM.CA$sum.inv.da.CM)
+
+cor.df = data.frame("comparison" = c("CN vs sum.inv.da.CA", "CN vs sum.inv.da.CM"), "R" = c(r.sum.inv.da.CA.CN, r.sum.inv.da.CM.CN))
+
+knitr::kable(cor.df, digits = 2, caption = "Correlation between CN and the sum.inv distance to the active site")
+```
+
+```{r write-pdbs} 
 # write pdb files with mean.z.RSDi as b-factor for building images
@@
 ```
+
+### sequence comparison
+```{r}
+consurf = read.csv(score.fname, sep = ";")
+score = consurf$SCORE
+
+sim.data.no.sel = read.csv(sim.data.no.sel.fname)
+mut.site.no.sel = sim.data.no.sel$site
+p.accept.no.sel = sim.data.no.sel$p.accept
+
+sim.data.strong.sel = read.csv(sim.data.strong.sel.fname)
+mut.site.strong.sel = sim.data.strong.sel$site
+p.accept.strong.sel = sim.data.strong.sel$p.accept
+
+mean.p.accept.no.sel = c()
+mean.p.accept.strong.sel = c()
+
+if (data.dir == "OUT/out_subset_CM_ANM") {
+  mut.site.no.sel = mut.site.no.sel - n.sites
+  mut.site.strong.sel = mut.site.strong.sel - n.sites
+  }
+
+for (i in (1:n.sites)) {
+  p.accept.no.sel.i = p.accept.no.sel[which(mut.site.no.sel == i)]
+  mean.p.accept.no.sel.i = mean(p.accept.no.sel.i)
+  mean.p.accept.no.sel[i] = mean.p.accept.no.sel.i
+
+  p.accept.strong.sel.i = p.accept.strong.sel[which(mut.site.strong.sel == i)]
+  mean.p.accept.strong.sel.i = mean(p.accept.strong.sel.i)
+  mean.p.accept.strong.sel[i] = mean.p.accept.strong.sel.i
+}
+
+par(pty = "s")
+
+plot(x = mean.p.accept.no.sel, y = CN)
+plot(x = mean.p.accept.no.sel, y = score)
+plot(x = score, y = CN)
+
+r.mean.p.accept.no.sel.CN = cor(mean.p.accept.no.sel, CN)
+r.mean.p.accept.no.sel.score = cor(mean.p.accept.no.sel, score)
+r.score.CN = cor(score, CN)
+
+cor.df = data.frame("comparison" = c("p.accept.no.sel vs CN", "p.accept.no.sel vs score", "score vs CN"),
+                    "R" = c(r.mean.p.accept.no.sel.CN , r.mean.p.accept.no.sel.score, r.score.CN))
+
+knitr::kable(cor.df, digits = 2, caption = "Correlation between sequence profiles")
+
+par(pty = "s")
+
+plot(x = log(mean.p.accept.strong.sel), y = CN)
+plot(x = log(mean.p.accept.strong.sel), y = score)
+plot(x = score, y = CN)
+
+r.mean.p.accept.strong.sel.CN = cor(log(mean.p.accept.strong.sel), CN)
+r.mean.p.accept.strong.sel.score = cor(log(mean.p.accept.strong.sel), score)
+r.score.CN = cor(score, CN)
+
+cor.df = data.frame("comparison" = c("log(p.accept.strong.sel) vs CN", "log(p.accept.strong.sel) vs score", "score vs CN"),
+                    "R" = c(r.mean.p.accept.strong.sel.CN , r.mean.p.accept.strong.sel.score, r.score.CN))
+
+knitr::kable(cor.df, digits = 2, caption = "Correlation between sequence profiles")
+
+```

### 2017-02-20 FUNCTIONS/CalculateVariability.R

@@ -55,14 +55,11 @@ CalculateVariability <- function(r.p.1,
   dr.squarei = colSums(matrix(dr, nrow = 3) ^ 2) 
   
   # transform r.p.2 using an aa seq based windows and calculate dr.squarei.windows.rot
-  r.p.2.window.rot = WindowsRMSD(15,
-                                 r.p.1,
-                                 r.p.2,
-                                 aligned.p.1.index.3N,
-                                 aligned.p.2.index.3N)
-  
-  dr.windows.rot = r.p.2.window.rot - r.p.1[aligned.p.1.index.3N]
-  dr.squarei.windows.rot = colSums(matrix(dr.windows.rot, nrow = 3) ^ 2)
+  dr.squarei.windows.rot = WindowsRMSD(10,
+                                       r.p.1,
+                                       r.p.2,
+                                       aligned.p.1.index.3N,
+                                       aligned.p.2.index.3N)
   
   # transform r.p.2 using contacts based windows and calculate a score (dr.squarei.windows.contacts.rot) in each window
   # the score of each window is mean(di^2), being i the sites inside the window
@@ -77,12 +74,12 @@ CalculateVariability <- function(r.p.1,
   dr.squarei.windows.contacts.rot = WindowsRMSDcontacts(ENMK.p.1$kij,
                                                         r.p.1,
                                                         r.p.2,
-                                                        aligned.p.1.index,
-                                                        aligned.p.2.index)
+                                                        aligned.p.1.index.3N,
+                                                        aligned.p.2.index.3N)
   
   # similarity of local enviroment - local score without transformating coordinates
   ## set R0 for local score
-  R0.local.score = 10
+  R0.local.score = R0
   
   ## calculate ENMK of aligned sites of p.1
   ENMK.p.1 = CalculateENMK(matrix(r.p.1, nrow = 3)[, aligned.p.1.index],
@@ -147,7 +144,6 @@ CalculateVariability <- function(r.p.1,
   
   # create a list for the output
   output = list(             "dr" = dr,
-                 "dr.windows.rot" = dr.windows.rot,
                              "va" = va,
                              "ve" = ve,
                              "Pn" = Pn,

### 2017-02-20 FUNCTIONS/GenerateMutants.R

@@ -67,7 +67,7 @@ GenerateMutants <- function(family,
   r.p.ref = pdb$xyz.calpha
   n.aa = pdb$n.sites
   
-  # Get heme coordinates, add them to CA´s coordinates and calculate the new number of sites
+  # Get heme coordinates, add them to CAB4s coordinates and calculate the new number of sites
   if (heme == "TRUE") {
     r.heme = ReadHeme(pdbs.fname, chain.p.ref)
     r.p.ref = cbind(r.p.ref, r.heme)
@@ -77,7 +77,7 @@ GenerateMutants <- function(family,
   }
   
   # Get the minimun sequence identity 
-  identity = min(m.identity)
+  identity = mean(m.identity)
   n.sites.mut = as.integer((100 - (identity)) * n.aa / 100)
   
   ### CALCULATE ENM OF THE REFERENCE PROTEIN ###

### 2017-02-20 FUNCTIONS/GenerateMutantsCM.R

@@ -72,7 +72,7 @@ GenerateMutantsCM <- function(family,
   r.CM.p.ref = CalculateSideChainCM(pdb.fname, chain.p.ref)
   n.CM = ncol(r.CM.p.ref)
 
-  # Get heme coordinates, add them to CA´s coordinates and calculate the new number of sites
+  # Get heme coordinates, add them to CAB4s coordinates and calculate the new number of sites
   if (heme == "TRUE") {
     r.heme = ReadHeme(pdb.fname, chain.p.ref)
     r.ca.p.ref = cbind(r.ca.p.ref, r.heme)
@@ -85,8 +85,8 @@ GenerateMutantsCM <- function(family,
   r.p.ref = cbind(r.ca.p.ref, r.CM.p.ref)
   n.sites.tot = ncol(r.p.ref)
 
-  # Get the minimun sequence identity 
-  identity = min(m.identity)
+  # Get the mean sequence identity 
+  identity = mean(m.identity)
   n.sites.mut = as.integer((100 - (identity)) * n.aa / 100)
   
   ### CALCULATE ENM OF THE REFERENCE PROTEIN ###

### 2017-02-20 FUNCTIONS/WindowsRMSDcontacts.R

@@ -1,33 +1,33 @@
 WindowsRMSDcontacts <- function(kij,
                                 r.p.1,
                                 r.p.2,
-                                aligned.p.1.index,
-                                aligned.p.2.index) {
-  # prepare r.p.1 and r.p.2
-  r.p.1 = matrix(r.p.1, nrow = 3)[, aligned.p.1.index]
-  r.p.2 = matrix(r.p.2, nrow = 3)[, aligned.p.2.index]
+                                aligned.p.1.index.3N,
+                                aligned.p.2.index.3N) {
+  # select aligned sites          
+  r.p.1 = r.p.1[aligned.p.1.index.3N]
+  r.p.2 = r.p.2[aligned.p.2.index.3N] 
+  
+  # calculate the number of aligned sites
+  n.aligned = length(r.p.1)/3
   
   # change kij
   diag(kij) = 1
-  
-  # calculate the number of windows
-  n.windows = length(aligned.p.1.index)
 
   # build a vector to save the data
   score.windows = c()
   
   # sart a loop to aligne each window and calculate the score
-  for (i in (1:n.windows)) {
+  for (i in (1:n.aligned)) {
     
-    index.windows.i = which(kij[i, ] == 1)
-    index.windows.i.3N = sort(c(index.windows.i * 3, index.windows.i * 3 - 2,  index.windows.i * 3 - 1))
+    indexes.window.i = which(kij[i, ] == 1)
+    indexes.window.i.3N = sort(c(indexes.window.i * 3, indexes.window.i * 3 - 2,  indexes.window.i * 3 - 1))
 
-    r.p.2.window = matrix(fit.xyz(fixed = as.vector(r.p.1),
-                                 mobile = as.vector(r.p.2),
-                             fixed.inds = index.windows.i.3N,
-                            mobile.inds = index.windows.i.3N)[index.windows.i.3N], nrow = 3)
+    r.p.2.window = fit.xyz(fixed = r.p.1[indexes.window.i.3N],
+                          mobile = r.p.2[indexes.window.i.3N],
+                      fixed.inds = (1:length(indexes.window.i.3N)),
+                     mobile.inds = (1:length(indexes.window.i.3N)))
     
-    score.windows.i = mean(colSums((r.p.2.window - r.p.1[, index.windows.i]) ^ 2)) 
[…]

### 2017-02-20 MainProgram.R

@@ -3,19 +3,20 @@
 # This is the main program of the project. The program simulates multiple mutants of a given protein using the "Linearly Forced - 
 # Elastic Network Model" (LF-ENM) with different selection regimens according to the "Stress Model". The program also
 # analyzes the multiple alignment of the family to which the protein belongs and calculates measures 
-# of variabilty of theoretical and experimental data.
+# of variabilty of theoretical and experimental structures.
+# Experimental structures and the multiple alignment must be obtained from Homstrad.
 #
 # To run the program it is necessary to previously fill the input ("input_MainProgram.csv") with the following information:
 #
-#    - family: The family of the protein to mutate. It can be "globins", "serinProteases", 
-#    "snakesToxin", "sh3", "fabp", "rrm", "phoslip" or "cys".
+#    - family: The family of the protein to mutate.
 #    - p.ref: The pdb code (pdbid) of the protein to mutate (example: "1a6m"). The protein must be a member of
 #    the selected family. This pdbid must not be included in the dataset ("DATA/family_dataset.csv").
 #    - chain.p.ref: The chain of p.ref in the pdb file obtained from Homstrad.
 #    - n.mut.p: The number of mutants to generate for each member of the family. For example, if the family has 20 
 #    members, the program generates n.mut.p x 20 mutants.
-#    - fmax: Argument for "LFENM". It is the maximun value for the forces that model the mutations. 
-#    - R0: the Cut-off for the "ANM" (Anisotropic Network Model) that represents the proteins.
+#    - fmax: Argument for the "LF-ENM". It is the maximun value for the forces that model the mutations. 
+#    - R0.CA: The Cut-off for the "ANM" (Anisotropic Network Model) that represents the proteins for the CA model.
+#    - R0.CM: The Cut-off for the "ANM" (Anisotropic Network Model) that represents the proteins for the two nodes per site model.
 #    - rotate: It can be "TRUE" or "FALSE". If it is "TRUE", r.p.2 is rotated in order to minimize RMSD with r.p.ref.
[…]

### 2017-02-20 MainProgramCM.R

@@ -3,22 +3,23 @@
 # This is the main program of the project. The program simulates multiple mutants of a given protein using the "Linearly Forced - 
 # Elastic Network Model" (LF-ENM) with different selection regimens according to the "Stress Model". The program also
 # analyzes the multiple alignment of the family to which the protein belongs and calculates measures 
-# of variabilty of theoretical and experimental data.
-# The difference between this program and "MainProgram.R" is that, in this case, the model considers two sites per
-# aminoacid, the CA and the center of mass of the side chain (CM).
-# For the LF - ENM, only CMs are mutated.
+# of variabilty of theoretical and experimental structures.
+# Experimental structures and the multiple alignment must be obtained from Homstrad.
+# The difference between this program and "MainProgram.R" is that, in this case, the model considers two nodes per
+# aminoacid, the alpha carbon (CA) and the center of mass of the side chain (CM).
+# For the simulations using the LF-ENM, only CMs are mutated.
 #
 # To run the program it is necessary to previously fill the input ("input_MainProgram.csv") with the following information:
 #
-#    - family: The family of the protein to mutate. It can be "globins", "serinProteases", 
-#    "snakesToxin", "sh3", "fabp", "rrm", "phoslip" or "cys".
+#    - family: The family of the protein to mutate.
 #    - p.ref: The pdb code (pdbid) of the protein to mutate (example: "1a6m"). The protein must be a member of
 #    the selected family. This pdbid must not be included in the dataset ("DATA/family_dataset.csv").
 #    - chain.p.ref: The chain of p.ref in the pdb file obtained from Homstrad.
 #    - n.mut.p: The number of mutants to generate for each member of the family. For example, if the family has 20 
 #    members, the program generates n.mut.p x 20 mutants.
-#    - fmax: Argument for "LFENM". It is the maximun value for the forces that model the mutations. 
-#    - R0: the Cut-off for the "ANM" (Anisotropic Network Model) that represents the proteins.
[…]

### 2017-02-20 MainReport.R

@@ -1,5 +1,4 @@
-# Description: This program generates reports with the output of "MainProgram.R", "MainProgramCM.R" and "mean.da.CM.CA.R".
-# It works with the program "analysis-structure.Rmd" and its analogous. 
+# Description: This program generates reports with the output of "MainProgram.R" and "MainProgramCM.R".
 # To run the program it is neccessary to fill the input file "input_MainReport.csv".
 # Files needed for each family in data.dir are:
 #  "famiy_list.txt": with all of the proteins of the family (including p.ref).
@@ -8,7 +7,7 @@
 
 ### PROGRAM ###
 
-# Load packages
+# load packages
 library(knitr)
 library(markdown)
 

### 2017-02-28 analysis-structure-core.Rmd
cambios 28/02/17

@@
 min.da.CM.CA.fname = file.path(data.dir, paste(p.ref, "_min.da.CM.ca.csv", sep = ""))
+sum.inv.da.CM.CA.fname = file.path(data.dir, paste(p.ref, "_sum.inv.da.CM.ca.csv", sep = ""))
 
@@
 dri2.mut.fname = file.path(data.dir,paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
+
+## consurf
+score.fname = file.path(data.dir, paste(p.ref, "_consurf.csv", sep = ""))
+sim.data.no.sel.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_out_df.data.csv", sep = ""))
+sim.data.strong.sel.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_strong.sel_out_df.data.csv", sep = ""))
 ```
@@
 ```
+
+```{r comparison-sum.inv.da}
+
+# comparison of means.z.scores with the sum.inv distance to the functional sites
+plot(y = d.exp$mean.z.RSD - d.mut$mean.z.RSD, x = m.sum.inv.da.CM.CA$sum.inv.da.CA[indexes.core], xlab = "sum.inv distance to active site (between CAs)", ylab = "exp.mean.z.RSD - mut.mean.z.RSD")
+plot(y = d.exp$mean.z.RSD - d.mut$mean.z.RSD, x = m.sum.inv.da.CM.CA$sum.inv.da.CM[indexes.core], xlab = "sum.inv distance to active site (between CMs)", ylab = "exp.mean.z.RSD - mut.mean.z.RSD")
+
+## calculate correlations between profiles
+r.sum.inv.da.CA = cor((d.exp$mean.z.RSD - d.mut$mean.z.RSD), m.sum.inv.da.CM.CA$sum.inv.da.CA[indexes.core])
+r.sum.inv.da.CM = cor((d.exp$mean.z.RSD - d.mut$mean.z.RSD), m.sum.inv.da.CM.CA$sum.inv.da.CM[indexes.core])
+
+cor.df = data.frame("comparison" = c("(exp - mut) vs sum.inv.da.CA", "(exp - mut) vs sum.inv.da.CM"), "R" = c(r.sum.inv.da.CA, r.sum.inv.da.CM))
+
+knitr::kable(cor.df, digits = 2, caption = "Correlation between differences in <Z-scores> profiles and the sum.inv distance to the active site")
+```
+
+```{r correlation-da-CN} 
+## CN core
+CN = CN[indexes.core]
+
+## calculate correlations between profiles
+r.min.da.CA.CN = cor(CN, m.min.da.CM.CA$min.da.CA[indexes.core])
+r.min.da.CM.CN = cor(CN, m.min.da.CM.CA$min.da.CM[indexes.core])
+
+cor.df = data.frame("comparison" = c("CN vs min.da.CA", "CN vs min.da.CM"), "R" = c(r.min.da.CA.CN, r.min.da.CM.CN))
+
+knitr::kable(cor.df, digits = 2, caption = "Correlation between CN and the minimal distance to the active site")
+
+## calculate correlations between profiles
+r.sum.inv.da.CA.CN = cor(CN, m.sum.inv.da.CM.CA$sum.inv.da.CA[indexes.core])
+r.sum.inv.da.CM.CN = cor(CN, m.sum.inv.da.CM.CA$sum.inv.da.CM[indexes.core])
+
+cor.df = data.frame("comparison" = c("CN vs sum.inv.da.CA", "CN vs sum.inv.da.CM"), "R" = c(r.sum.inv.da.CA.CN, r.sum.inv.da.CM.CN))
+
+knitr::kable(cor.df, digits = 2, caption = "Correlation between CN and the sum.inv distance to the active site")
+```
+
+```{r}
+# read experimental data obtained from ConsurfDB
+consurf = read.csv(score.fname, sep = ";")
+score = consurf$SCORE[indexes.core]
+
+# read simulated data
+## no sel
+sim.data.no.sel = read.csv(sim.data.no.sel.fname)
+mut.site.no.sel = sim.data.no.sel$site
+p.accept.no.sel = sim.data.no.sel$p.accept
+
+## strong sel
+sim.data.strong.sel = read.csv(sim.data.strong.sel.fname)
+mut.site.strong.sel = sim.data.strong.sel$site
+p.accept.strong.sel = sim.data.strong.sel$p.accept
+
+# calculate de mean.p.accept of simulated data
+mean.p.accept.no.sel = c()
+mean.p.accept.strong.sel = c()
+
+if (data.dir == "OUT/out_subset_CM_ANM") {
+  mut.site.no.sel = mut.site.no.sel - n.sites
+  mut.site.strong.sel = mut.site.strong.sel - n.sites
+  CN.CM = sim.data.no.sel$CN
+  CN = c()
+
+  for (i in (1:n.sites)) {
+    CN[i] = CN.CM[which(mut.site.no.sel == i)][1]
+  }
+  CN = CN[indexes.core]
+}
+
+# core n.sites
+
+for (i in (1:n.sites)) {
+  p.accept.no.sel.i = p.accept.no.sel[which(mut.site.no.sel == i)]
+  mean.p.accept.no.sel.i = mean(p.accept.no.sel.i)
+  mean.p.accept.no.sel[i] = mean.p.accept.no.sel.i
+
+  p.accept.strong.sel.i = p.accept.strong.sel[which(mut.site.strong.sel == i)]
+  mean.p.accept.strong.sel.i = mean(p.accept.strong.sel.i)
+  mean.p.accept.strong.sel[i] = mean.p.accept.strong.sel.i
+}
+mean.p.accept.no.sel = mean.p.accept.no.sel[indexes.core]
+mean.p.accept.strong.sel = mean.p.accept.strong.sel[indexes.core]
+
+# compare exp vs no sel profiles
+## plot
+par(pty = "s")
+
+plot(x = mean.p.accept.no.sel, y = CN)
+plot(x = mean.p.accept.no.sel, y = score)
+plot(x = score, y = CN)
+
+## calculate corelations
+r.mean.p.accept.no.sel.CN = cor(mean.p.accept.no.sel, CN)
+r.mean.p.accept.no.sel.score = cor(mean.p.accept.no.sel, score)
+r.score.CN = cor(score, CN)
+
+cor.df = data.frame("comparison" = c("p.accept.no.sel vs CN", "p.accept.no.sel vs score", "score vs CN"),
+                    "R" = c(r.mean.p.accept.no.sel.CN , r.mean.p.accept.no.sel.score, r.score.CN))
+
+knitr::kable(cor.df, digits = 2, caption = "Correlation between sequence profiles")
+
+# compare exp vs strong sel profiles
+## plot
+par(pty = "s")
+
+plot(x = log(mean.p.accept.strong.sel), y = CN)
+plot(x = log(mean.p.accept.strong.sel), y = score)
+plot(x = score, y = CN)
+
+## calculate corelations
+r.mean.p.accept.strong.sel.CN = cor(log(mean.p.accept.strong.sel), CN)
+r.mean.p.accept.strong.sel.score = cor(log(mean.p.accept.strong.sel), score)
+r.score.CN = cor(score, CN)
+
+cor.df = data.frame("comparison" = c("log(p.accept.strong.sel) vs CN", "log(p.accept.strong.sel) vs score", "score vs CN"),
+                    "R" = c(r.mean.p.accept.strong.sel.CN , r.mean.p.accept.strong.sel.score, r.score.CN))
+
+knitr::kable(cor.df, digits = 2, caption = "Correlation between sequence profiles")
+
+```

### 2017-02-28 analysis-structure.Rmd
cambios 28/02/17

@@
 ### sequence comparison
-```{r}
+```{r sequence-profiles-comparison}
+# read experimental data obtained from ConsurfDB
 consurf = read.csv(score.fname, sep = ";")
@@
 
+# read simulated data
+## no sel
 sim.data.no.sel = read.csv(sim.data.no.sel.fname)
@@
 
+## strong sel
 sim.data.strong.sel = read.csv(sim.data.strong.sel.fname)
@@
 
+# calculate de mean.p.accept of simulated data
 mean.p.accept.no.sel = c()
@@
   mut.site.strong.sel = mut.site.strong.sel - n.sites
+  CN.CM = sim.data.no.sel$CN
+  CN = c()
+
+  for (i in (1:n.sites)) {
+    CN[i] = CN.CM[which(mut.site.no.sel == i)][1]
+  }
 }
@@
 
+# compare exp vs no sel profiles
+## plot
 par(pty = "s")
@@
 
+## calculate corelations
 r.mean.p.accept.no.sel.CN = cor(mean.p.accept.no.sel, CN)
@@
 
+# compare exp vs strong sel profiles
+## plot
 par(pty = "s")
@@
 
+## calculate corelations
 r.mean.p.accept.strong.sel.CN = cor(log(mean.p.accept.strong.sel), CN)

### 2017-03-20 analysis-structure.Rmd
cambios 20/3/17

@@
 # set my colors
-myColors = c("blue", "darkgreen", "red", "red") 
-names(myColors) <- c("exp", "mut", "strong", "mut+sel")
+myColors = c("blue", "darkgreen", "darkgreen", "red", "red") 
+names(myColors) <- c("exp", "mut", "no-sel", "strong", "strong-sel")
 ```
@@
 dat = siteComparison.all.datasets
-dat$dataset = revalue(dat$dataset, c("strong" = "mut+sel"))
+dat$dataset = revalue(dat$dataset, c("strong" = "strong-sel"))
+dat$dataset = revalue(dat$dataset, c("mut" = "no-sel"))
 
@@
     geom_vline(xintercept = contacts.active.sites, col = "grey", show.legend = F) +
-    labs(x = "site", y = "structural divergence(mean z.RSD)") +
+    labs(x = "site", y = "<zRSDi>") +
     coord_cartesian(ylim = c(-1.5, 2.8)) +
@@
 p.facet %+% subset(d, dataset == "exp") 
-p.facet %+% subset(d, dataset == "mut")
-p.facet %+% subset(d, dataset == "mut+sel") 
+p.facet %+% subset(d, dataset == "no-sel")
+p.facet %+% subset(d, dataset == "strong-sel") 
 p.facet
@@
 d.exp = subset(d, dataset == "exp")
-d.mut = subset(d, dataset == "mut")
-d.strong = subset(d, dataset == "mut+sel")
+d.mut = subset(d, dataset == "no-sel")
+d.strong = subset(d, dataset == "strong-sel")
 
@@
 ```
+```{r structure-profiles-comparison}
+
+# compare profiles
+## plot
+par(pty = "s")
+plot(x = d.exp$mean.z.RSD, y = CN, xlab = "experimental <zRSDi>")
+plot(x = d.mut$mean.z.RSD, y = CN, xlab = "theoretical with no selection <zRSDi>")
+plot(x = d.strong$mean.z.RSD, y = CN, xlab = "theoretical with strong selection <zRSDi>")
+
+## calculate corelations
+r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, CN)
+r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, CN)
+r.strong.mean.z.RSD.CN = cor(d.strong$mean.z.RSD, CN)
+
+cor.df = data.frame("comparison" = c("exp.mean.z.RSD vs CN", "mut.mean.z.RSD vs CN", "strong.mean.z.RSD vs CN"),
+                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.strong.mean.z.RSD.CN))
+
+knitr::kable(cor.df, digits = 2, caption = "Correlation between sequence profiles")
+```

### 2017-03-26 analysis-structure.Rmd
paper actualizado

@@
 myColors = c("blue", "darkgreen", "darkgreen", "red", "red") 
-names(myColors) <- c("exp", "mut", "no-sel", "strong", "strong-sel")
+names(myColors) <- c("exp", "mut", "no-selection", "strong", "selection")
 ```
@@
 dat = siteComparison.all.datasets
-dat$dataset = revalue(dat$dataset, c("strong" = "strong-sel"))
-dat$dataset = revalue(dat$dataset, c("mut" = "no-sel"))
+dat$dataset = revalue(dat$dataset, c("strong" = "selection"))
+dat$dataset = revalue(dat$dataset, c("mut" = "no-selection"))
 
@@
 p.facet %+% subset(d, dataset == "exp") 
-p.facet %+% subset(d, dataset == "no-sel")
-p.facet %+% subset(d, dataset == "strong-sel") 
+p.facet %+% subset(d, dataset == "no-selection")
+p.facet %+% subset(d, dataset == "selection") 
 p.facet
@@
 d.exp = subset(d, dataset == "exp")
-d.mut = subset(d, dataset == "no-sel")
-d.strong = subset(d, dataset == "strong-sel")
+d.mut = subset(d, dataset == "no-selection")
+d.strong = subset(d, dataset == "selection")
 
@@
 
-# calculate de mean.p.accept of simulated data
+# calculate mean.p.accept of simulated data
 mean.p.accept.no.sel = c()
@@
 
+# correct indexes
 if (data.dir == "OUT/out_subset_CM_ANM") {
@@
 ```
-```{r structure-profiles-comparison}
+```{r structure-profiles-CN-comparison}
 
@@
 
-knitr::kable(cor.df, digits = 2, caption = "Correlation between sequence profiles")
+knitr::kable(cor.df, digits = 2, caption = "Correlation structure - sequence")
 ```

### 2017-03-26 FUNCTIONS/AnalyzeExperimentalTheoretical.R

@@ -91,6 +91,9 @@ AnalyzeExperimentalTheoretical <- function(family,
   m.theo.norm.dr.squarei.windows.rot = matrix(nrow = n.mut, ncol = n.sites.p.ref)
   m.theo.norm.dr.squarei.windows.contacts.rot = matrix(nrow = n.mut, ncol = n.sites.p.ref)
   m.theo.local.score = matrix(nrow = n.mut, ncol = n.sites.p.ref)
+  m.theo.square.dif.MSF = matrix(nrow = n.mut, ncol = n.sites.p.ref)
+  m.theo.nH = matrix(nrow = n.mut, ncol = 3 * n.sites.p.ref)
+  m.theo.nR = matrix(nrow = n.mut, ncol = 3 * n.sites.p.ref)
   
   # start a loop to analyze each mutant
   for (mut in (1:(n.mut))) {
@@ -119,6 +122,9 @@ AnalyzeExperimentalTheoretical <- function(family,
     m.theo.dr.squarei.windows.rot[mut, 1:length(theo.variability$dr.squarei)] = theo.variability$dr.squarei.windows.rot
     m.theo.dr.squarei.windows.contacts.rot[mut, 1:length(theo.variability$dr.squarei)] = theo.variability$dr.squarei.windows.contacts.rot
     m.theo.local.score[mut, 1:length(theo.variability$local.score)] = theo.variability$local.score
+    m.theo.square.dif.MSF[mut, 1:length(theo.variability$square.dif.MSF)] = theo.variability$square.dif.MSF
+    m.theo.nH[mut, 1:length(theo.variability$nH)] = theo.variability$nH
+    m.theo.nR[mut, 1:length(theo.variability$nR)] = theo.variability$nR
     
     # calculate norm.dr.squarei
     m.theo.norm.dr.squarei[mut, ] = m.theo.dr.squarei[mut, ]/ mean(m.theo.dr.squarei[mut, ], na.rm = T)
@@ -133,6 +139,9 @@ AnalyzeExperimentalTheoretical <- function(family,
   write.csv(m.theo.norm.dr.squarei.windows.rot, file = file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.norm.dr.squarei.windows.rot.csv", sep = "")), row.names = FALSE)
[…]

### 2017-03-26 FUNCTIONS/CalculateVariability.R

@@ -19,6 +19,7 @@
 #    CalculateKij
 #    WindowsRMSD
 #    LocalEnviroment
+#    CalculateDynamicalVariability
 #
 #  Returns:
 #    Pn
@@ -142,6 +143,21 @@ CalculateVariability <- function(r.p.1,
   ## calculate measures of variability between p.1 and p.2
   Pn = ((t(ve) %*% dr) ^ 2) / (sum((t(ve) %*% dr) ^ 2))
   
+  ## dynamical variability
+  
+  dynamical.variability = CalculateDynamicalVariability(r.p.1,
+                                                        r.p.2,
+                                                        aligned.p.1.index,
+                                                        aligned.p.2.index,
+                                                        not.aligned.p.1.index,
+                                                        not.aligned.p.2.index,
+                                                        R0, 
+                                                        tolerance, 
+                                                        K.analysis)
+  square.dif.MSF = dynamical.variability$square.dif.MSF
+  nH = dynamical.variability$nH
+  nR = dynamical.variability$nR
+  
   # create a list for the output
   output = list(             "dr" = dr,
                              "va" = va,
@@ -150,7 +166,10 @@ CalculateVariability <- function(r.p.1,
                      "dr.squarei" = dr.squarei,
          "dr.squarei.windows.rot" = dr.squarei.windows.rot,
 "dr.squarei.windows.contacts.rot" = dr.squarei.windows.contacts.rot,
-                    "local.score" = local.score)
+                    "local.score" = local.score,
+                 "square.dif.MSF" = square.dif.MSF,
+                             "nH" = nH,
+                             "nR" = nR)
   output
 }
 

### 2017-03-26 MainProgramCM.R

@@ -62,6 +62,7 @@ CalculateSideChainCM.fname <- "FUNCTIONS/CalculateSideChainCM.R"
 CalculateENMKeff.fname <- "FUNCTIONS/CalculateENMKeff.R"
 CalculateENMK.fname <- "FUNCTIONS/CalculateENMK.R"
 CalculateVariability.fname <- "FUNCTIONS/CalculateVariability.R"
+CalculateDynamicalVariability.fname <- "FUNCTIONS/CalculateDynamicalVariability.R"
 CalculateDaCMCA.fname <- "FUNCTIONS/CalculateDaCMCA.R"
 GetCore.fname <- "FUNCTIONS/GetCore.R"
 WindowsRMSD.fname <- "FUNCTIONS/WindowsRMSD.R"
@@ -89,6 +90,7 @@ source(CalculateSideChainCM.fname)
 source(CalculateENMKeff.fname)
 source(CalculateENMK.fname)
 source(CalculateVariability.fname)
+source(CalculateDynamicalVariability.fname)
 source(CalculateDaCMCA.fname)
 source(GetCore.fname)
 source(WindowsRMSD.fname)
@@ -163,8 +165,8 @@ for (f in (1:nrow(input))) {
   for (b in all.betas)  {
     
     # filter regimens
-    if (regimens[all.betas == b] != "medium.sel") {
-      if (regimens[all.betas == b] != "weak.sel") {
+    if (regimens[all.betas == b] != "weak.sel") {
+      if (regimens[all.betas == b] != "strong.sel") {
         
         # generate ids for output filenames
         mut.fname.id <- paste(family, "_R0_", R0, "_beta_", regimens[all.betas == b], sep = "")

### 2017-04-01 analysis-dynamical-MSF.Rmd
dinamica

---
title: "Structural Divergence Analysis"
author: "Maria Laura Marcos, Julian Echave"
output: html_document
---

# Introduction
We study the evolutionary divergence of proteins using the LF-ENM and comparing simulated mutants with experimental data.

```{r setup, include = FALSE}
# set chunk options
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r load_packages}
# load packages
library(ggplot2)
library(reshape2)
library(plyr)
library(quantreg)
library(bio3d)

# load functions
source(file.path(data.dir, "multiplot.R"))
source(file.path(data.dir, "my-functions.R")) 
```

```{r set_my_colors}
# set my colors
myColors = c("blue", "darkgreen", "red", "red") 
names(myColors) <- c("exp", "mut", "medium", "mut+sel")
```

```{r set_run_variables}
# set significance factors
f95 = 1.96
f99 = 2.6
f999 = 3.3
```

```{r set_file_names}
# set input filenames
## data
reference.fname = file.path(data.dir, paste(family, "_ref.txt", sep = ""))
protein_list.fname = file.path(data.dir, paste(family, "_list.txt", sep = ""))
site.info.fname = file.path(data.dir, paste(p.ref, "_m.da.ca.csv", sep = ""))
min.da.CM.CA.fname = file.path(data.dir, paste(p.ref, "_min.da.CM.ca.csv", sep = ""))

## profiles to compare
### square.dif.MSF
square.dif.MSF.exp.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.exp.square.dif.MSF.csv", sep = ""))
square.dif.MSF.medium.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_medium.sel_K.analysis_Keff_out_m.theo.square.dif.MSF.csv", sep = ""))
square.dif.MSF.mut.fname = file.path(data.dir,paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.square.dif.MSF.csv", sep = ""))

```

```{r set_reference_protein}
# which is the reference protein?
reference = as.character(read.table(reference.fname, header = F)[1, 1])
if (reference != p.ref) {
  print("Warning: different references")
}
```

We studied the `r family` family. 
We used the ENM `r enm` with R0 = `r R0` to generate mutants.
We used as reference for the ENM the protein with pdb code `r reference`. 
We simulated `r n.mut.p` mutants of this reference for each protein of the family.
The `r family` family is of the type `r type` and consists of the following proteins:

```{r set_experimental_protein_names, comment = ""}
# experimental protein names
protein.exp = read.table(protein_list.fname, header = F, stringsAsFactors = F)[, 1]
protein.exp = protein.exp[protein.exp != reference]
print(protein.exp)
```

```{r prepare_site_data}
# prepare the data
square.dif.MSF.exp = read.csv(square.dif.MSF.exp.fname, header = T)

square.dif.MSF.mut = read.csv(square.dif.MSF.mut.fname, header = T)

square.dif.MSF.medium = read.csv(square.dif.MSF.medium.fname, header = T)
```

### Dynamical divergence along sites

In this section we consider dynamical divergence using Cartessian coordinates. square.dif.MSF is the square diference between MSF of the proteins relative to the reference protein.

```{r comparisson-of-means}
# calculate means
mean.square.dif.MSF.exp = colMeans(square.dif.MSF.exp, na.rm = T)
mean.square.dif.MSF.mut = colMeans(square.dif.MSF.mut)
mean.square.dif.MSF.medium = colMeans(square.dif.MSF.medium)

# remove too divergent sites 
n.sites = length(mean.square.dif.MSF.exp)
mean.square.dif.MSF.exp = mean.square.dif.MSF.exp[-c(1,2,3,4,(n.sites-3), (n.sites-2), (n.sites-1), n.sites)]
mean.square.dif.MSF.mut = mean.square.dif.MSF.mut[-c(1,2,3,4,(n.sites-3), (n.sites-2), (n.sites-1), n.sites)]
mean.square.dif.MSF.medium = mean.square.dif.MSF.medium[-c(1,2,3,4,(n.sites-3), (n.sites-2), (n.sites-1), n.sites)]

# scale profiles
mean.square.dif.MSF.exp = rank(mean.square.dif.MSF.exp)
mean.square.dif.MSF.mut = rank(mean.square.dif.MSF.mut)
mean.square.dif.MSF.medium = rank(mean.square.dif.MSF.medium)

plot(mean.square.dif.MSF.exp, ylab = "Square dif MSF", xlab = "site", col = "blue")
points(mean.square.dif.MSF.mut, col = "green")
points(mean.square.dif.MSF.medium, col = "red")

r.exp.mut = cor(mean.square.dif.MSF.exp, mean.square.dif.MSF.mut)
r.exp.medium = cor(mean.square.dif.MSF.exp, mean.square.dif.MSF.medium)
r.mut.medium = cor(mean.square.dif.MSF.mut, mean.square.dif.MSF.medium)

cor.df = data.frame("comparison" = c("exp vs mut", "exp vs medium", "mut vs medium"),
                    "R" = c(r.exp.mut, r.exp.medium, r.mut.medium))
knitr::kable(cor.df, digits = 2)

# plot exp vs simulated profiles 
par(pty = "s")

plot(x = mean.square.dif.MSF.exp, 
     y = mean.square.dif.MSF.mut, 
     xlab = "exp.mean.square.dif.MSF", 
     ylab = "mut.mean.square.dif.MSF")
abline(0, 1)

plot(x = mean.square.dif.MSF.exp, 
     y = mean.square.dif.MSF.medium, 
     xlab = "exp.mean.square.dif.MSF", 
     ylab = "medium.mean.square.dif.MSF")
abline(0, 1)

plot(x = mean.square.dif.MSF.mut, 
     y = mean.square.dif.MSF.medium, 
     xlab = "mut.mean.square.dif.MSF", 
     ylab = "medium.mean.square.dif.MSF")
abline(0, 1)
```

### 2017-04-01 analysis-dynamical-nH.Rmd
dinamica

--- 2017-04-01 analysis-dynamical-MSF.Rmd
@@
 ## profiles to compare
-### square.dif.MSF
-square.dif.MSF.exp.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.exp.square.dif.MSF.csv", sep = ""))
-square.dif.MSF.medium.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_medium.sel_K.analysis_Keff_out_m.theo.square.dif.MSF.csv", sep = ""))
-square.dif.MSF.mut.fname = file.path(data.dir,paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.square.dif.MSF.csv", sep = ""))
+### nH
+nH.exp.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.exp.nH.csv", sep = ""))
+nH.medium.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_medium.sel_K.analysis_Keff_out_m.theo.nH.csv", sep = ""))
+nH.mut.fname = file.path(data.dir,paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.nH.csv", sep = ""))
 
@@
 # prepare the data
-square.dif.MSF.exp = read.csv(square.dif.MSF.exp.fname, header = T)
+nH.exp = read.csv(nH.exp.fname, header = T)
 
-square.dif.MSF.mut = read.csv(square.dif.MSF.mut.fname, header = T)
+nH.mut = read.csv(nH.mut.fname, header = T)
 
-square.dif.MSF.medium = read.csv(square.dif.MSF.medium.fname, header = T)
+nH.medium = read.csv(nH.medium.fname, header = T)
 ```
 
-### Dynamical divergence along sites
+### Dynamical divergence along normal modes
 
-In this section we consider dynamical divergence using Cartessian coordinates. square.dif.MSF is the square diference between MSF of the proteins relative to the reference protein.
+In this section we consider dynamical divergence using normal modes coordinates.
 
@@
 # calculate means
-mean.square.dif.MSF.exp = colMeans(square.dif.MSF.exp, na.rm = T)
-mean.square.dif.MSF.mut = colMeans(square.dif.MSF.mut)
-mean.square.dif.MSF.medium = colMeans(square.dif.MSF.medium)
-
-# remove too divergent sites 
-n.sites = length(mean.square.dif.MSF.exp)
-mean.square.dif.MSF.exp = mean.square.dif.MSF.exp[-c(1,2,3,4,(n.sites-3), (n.sites-2), (n.sites-1), n.sites)]
-mean.square.dif.MSF.mut = mean.square.dif.MSF.mut[-c(1,2,3,4,(n.sites-3), (n.sites-2), (n.sites-1), n.sites)]
-mean.square.dif.MSF.medium = mean.square.dif.MSF.medium[-c(1,2,3,4,(n.sites-3), (n.sites-2), (n.sites-1), n.sites)]
+mean.nH.exp = colMeans(nH.exp, na.rm = T)
+mean.nH.mut = colMeans(nH.mut)
+mean.nH.medium = colMeans(nH.medium)
 
 # scale profiles
-mean.square.dif.MSF.exp = rank(mean.square.dif.MSF.exp)
-mean.square.dif.MSF.mut = rank(mean.square.dif.MSF.mut)
-mean.square.dif.MSF.medium = rank(mean.square.dif.MSF.medium)
+mean.nH.exp = rank(mean.nH.exp)
+mean.nH.mut = rank(mean.nH.mut)
+mean.nH.medium = rank(mean.nH.medium)
 
-plot(mean.square.dif.MSF.exp, ylab = "Square dif MSF", xlab = "site", col = "blue")
-points(mean.square.dif.MSF.mut, col = "green")
-points(mean.square.dif.MSF.medium, col = "red")
+plot(mean.nH.exp, ylab = "nH", xlab = "site", col = "blue")
+points(mean.nH.mut, col = "green")
+points(mean.nH.medium, col = "red")
 
-r.exp.mut = cor(mean.square.dif.MSF.exp, mean.square.dif.MSF.mut)
-r.exp.medium = cor(mean.square.dif.MSF.exp, mean.square.dif.MSF.medium)
-r.mut.medium = cor(mean.square.dif.MSF.mut, mean.square.dif.MSF.medium)
+r.exp.mut = cor(mean.nH.exp, mean.nH.mut)
+r.exp.medium = cor(mean.nH.exp, mean.nH.medium)
+r.mut.medium = cor(mean.nH.mut, mean.nH.medium)
 
@@
 
-plot(x = mean.square.dif.MSF.exp, 
-     y = mean.square.dif.MSF.mut, 
-     xlab = "exp.mean.square.dif.MSF", 
-     ylab = "mut.mean.square.dif.MSF")
+plot(x = mean.nH.exp, 
+     y = mean.nH.mut, 
+     xlab = "exp.mean.nH", 
+     ylab = "mut.mean.nH")
 abline(0, 1)
 
-plot(x = mean.square.dif.MSF.exp, 
-     y = mean.square.dif.MSF.medium, 
-     xlab = "exp.mean.square.dif.MSF", 
-     ylab = "medium.mean.square.dif.MSF")
+plot(x = mean.nH.exp, 
+     y = mean.nH.medium, 
+     xlab = "exp.mean.nH", 
+     ylab = "medium.mean.nH")
 abline(0, 1)
 
-plot(x = mean.square.dif.MSF.mut, 
-     y = mean.square.dif.MSF.medium, 
-     xlab = "mut.mean.square.dif.MSF", 
-     ylab = "medium.mean.square.dif.MSF")
+plot(x = mean.nH.mut, 
+     y = mean.nH.medium, 
+     xlab = "mut.mean.nH", 
+     ylab = "medium.mean.nH")
 abline(0, 1)

### 2017-04-01 analysis-dynamical-nR.Rmd
dinamica

--- 2017-04-01 analysis-dynamical-nH.Rmd
@@
 ## profiles to compare
-### nH
-nH.exp.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.exp.nH.csv", sep = ""))
-nH.medium.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_medium.sel_K.analysis_Keff_out_m.theo.nH.csv", sep = ""))
-nH.mut.fname = file.path(data.dir,paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.nH.csv", sep = ""))
+### nR
+nR.exp.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.exp.nR.csv", sep = ""))
+nR.medium.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_medium.sel_K.analysis_Keff_out_m.theo.nR.csv", sep = ""))
+nR.mut.fname = file.path(data.dir,paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.nR.csv", sep = ""))
 
@@
 # prepare the data
-nH.exp = read.csv(nH.exp.fname, header = T)
+nR.exp = read.csv(nR.exp.fname, header = T)
 
-nH.mut = read.csv(nH.mut.fname, header = T)
+nR.mut = read.csv(nR.mut.fname, header = T)
 
-nH.medium = read.csv(nH.medium.fname, header = T)
+nR.medium = read.csv(nR.medium.fname, header = T)
 ```
@@
 # calculate means
-mean.nH.exp = colMeans(nH.exp, na.rm = T)
-mean.nH.mut = colMeans(nH.mut)
-mean.nH.medium = colMeans(nH.medium)
+mean.nR.exp = colMeans(nR.exp, na.rm = T)
+mean.nR.mut = colMeans(nR.mut)
+mean.nR.medium = colMeans(nR.medium)
 
 # scale profiles
-mean.nH.exp = rank(mean.nH.exp)
-mean.nH.mut = rank(mean.nH.mut)
-mean.nH.medium = rank(mean.nH.medium)
+mean.nR.exp = rank(mean.nR.exp)
+mean.nR.mut = rank(mean.nR.mut)
+mean.nR.medium = rank(mean.nR.medium)
 
-plot(mean.nH.exp, ylab = "nH", xlab = "site", col = "blue")
-points(mean.nH.mut, col = "green")
-points(mean.nH.medium, col = "red")
+plot(mean.nR.exp, ylab = "nR", xlab = "site", col = "blue")
+points(mean.nR.mut, col = "green")
+points(mean.nR.medium, col = "red")
 
-r.exp.mut = cor(mean.nH.exp, mean.nH.mut)
-r.exp.medium = cor(mean.nH.exp, mean.nH.medium)
-r.mut.medium = cor(mean.nH.mut, mean.nH.medium)
+r.exp.mut = cor(mean.nR.exp, mean.nR.mut)
+r.exp.medium = cor(mean.nR.exp, mean.nR.medium)
+r.mut.medium = cor(mean.nR.mut, mean.nR.medium)
 
@@
 
-plot(x = mean.nH.exp, 
-     y = mean.nH.mut, 
-     xlab = "exp.mean.nH", 
-     ylab = "mut.mean.nH")
+plot(x = mean.nR.exp, 
+     y = mean.nR.mut, 
+     xlab = "exp.mean.nR", 
+     ylab = "mut.mean.nR")
 abline(0, 1)
 
-plot(x = mean.nH.exp, 
-     y = mean.nH.medium, 
-     xlab = "exp.mean.nH", 
-     ylab = "medium.mean.nH")
+plot(x = mean.nR.exp, 
+     y = mean.nR.medium, 
+     xlab = "exp.mean.nR", 
+     ylab = "medium.mean.nR")
 abline(0, 1)
 
-plot(x = mean.nH.mut, 
-     y = mean.nH.medium, 
-     xlab = "mut.mean.nH", 
-     ylab = "medium.mean.nH")
+plot(x = mean.nR.mut, 
+     y = mean.nR.medium, 
+     xlab = "mut.mean.nR", 
+     ylab = "medium.mean.nR")
 abline(0, 1)

### 2017-04-01 FUNCTIONS/AnalyzeExperimentalTheoretical.R

@@ -165,15 +165,15 @@ AnalyzeExperimentalTheoretical <- function(family,
   m.exp.Pn = matrix(nrow = n.prot, ncol = 3 * (n.sites.p.ref)) 
   m.exp.va = matrix(nrow = n.prot, ncol = 3 * (n.sites.p.ref))
   m.exp.dr.squarei = matrix(nrow = n.prot, ncol = (n.sites.p.ref))
-  m.exp.dr.squarei.windows.rot = matrix(nrow = n.mut, ncol = n.sites.p.ref)
-  m.exp.dr.squarei.windows.contacts.rot = matrix(nrow = n.mut, ncol = n.sites.p.ref)
+  m.exp.dr.squarei.windows.rot = matrix(nrow = n.prot, ncol = n.sites.p.ref)
+  m.exp.dr.squarei.windows.contacts.rot = matrix(nrow = n.prot, ncol = n.sites.p.ref)
   m.exp.norm.dr.squarei = matrix(nrow = n.prot, ncol = (n.sites.p.ref))
   m.exp.norm.dr.squarei.windows.rot = matrix(nrow = n.prot, ncol = n.sites.p.ref)
   m.exp.norm.dr.squarei.windows.contacts.rot = matrix(nrow = n.prot, ncol = n.sites.p.ref)
   m.exp.local.score = matrix(nrow = n.prot, ncol = n.sites.p.ref)
-  m.exp.square.dif.MSF = matrix(nrow = n.mut, ncol = n.sites.p.ref)
-  m.exp.nH = matrix(nrow = n.mut, ncol = 3 * n.sites.p.ref)
-  m.exp.nR = matrix(nrow = n.mut, ncol = 3 * n.sites.p.ref)
+  m.exp.square.dif.MSF = matrix(nrow = n.prot, ncol = n.sites.p.ref)
+  m.exp.nH = matrix(nrow = n.prot, ncol = 3 * n.sites.p.ref)
+  m.exp.nR = matrix(nrow = n.prot, ncol = 3 * n.sites.p.ref)
   
   # Start a loop to evaluate each protein of the family
   for (P in (1:n.prot)) {

### 2017-04-01 MainReport.R

@@ -46,6 +46,18 @@ for (f in (1:nrow(input))) {
   rmarkdown::render('analysis-structure-core.Rmd', 
                    output_file =  paste("OUT/report_structure_CA_core_", family, "_", enm, "_R0_", R0, ".html", sep = ''))
   
+  ### MSF
+  rmarkdown::render('analysis-dynamical-MSF.Rmd', 
+                    output_file =  paste("OUT/report__dynamical_MSF_CA_", family, "_", enm, "_R0_", R0, ".html", sep = ''))
+  
+  ### nH
+  rmarkdown::render('analysis-dynamical-nH.Rmd', 
+                    output_file =  paste("OUT/report_dynamical_nH_CA_", family, "_", enm, "_R0_", R0, ".html", sep = ''))
+  
+  ### nR
+  rmarkdown::render('analysis-dynamical-nR.Rmd', 
+                    output_file =  paste("OUT/report_dynamical_nR_CA_", family, "_", enm, "_R0_", R0, ".html", sep = ''))
+  
   ### RMSD windows contacts rot
   #rmarkdown::render('analysis-structure-window-contacts.Rmd', 
    #                 output_file =  paste("OUT/report_structure_window_contacts_CA_", family, "_", enm, "_R0_", R0, ".html", sep = ''))
@@ -70,6 +82,17 @@ for (f in (1:nrow(input))) {
   ### RMSD core
   rmarkdown::render('analysis-structure-core.Rmd', 
                     output_file =  paste("OUT/report_structure_CM_core_", family, "_", enm, "_R0_", R0, ".html", sep = ''))
+  
+  ### MSF
+  rmarkdown::render('analysis-dynamical-MSF.Rmd', 
+                    output_file =  paste("OUT/report_dynamical_MSF_CM_", family, "_", enm, "_R0_", R0, ".html", sep = ''))
+  
+  ### nH
+  rmarkdown::render('analysis-dynamical-nH.Rmd', 
+                    output_file =  paste("OUT/report_dynamical_nH_CM_", family, "_", enm, "_R0_", R0, ".html", sep = ''))
+  ### nR
+  rmarkdown::render('analysis-dynamical-nR.Rmd', 
+                    output_file =  paste("OUT/report_dynamical_nR_CM_", family, "_", enm, "_R0_", R0, ".html", sep = ''))
   
   ### RMSD windows contacts rot
   #rmarkdown::render('analysis-structure-window-contacts.Rmd', 

### 2017-04-04 analysis-dynamical-MSF.Rmd
dinámica 4/4/17

@@
 square.dif.MSF.exp = read.csv(square.dif.MSF.exp.fname, header = T)
-
 square.dif.MSF.mut = read.csv(square.dif.MSF.mut.fname, header = T)
-
 square.dif.MSF.medium = read.csv(square.dif.MSF.medium.fname, header = T)
@@
 
-plot(mean.square.dif.MSF.exp, ylab = "Square dif MSF", xlab = "site", col = "blue")
+plot(mean.square.dif.MSF.exp, ylab = "<Square dif MSF>", xlab = "site", col = "blue")
 points(mean.square.dif.MSF.mut, col = "green")

### 2017-04-04 analysis-dynamical-nH.Rmd
dinámica 4/4/17

@@
 protein_list.fname = file.path(data.dir, paste(family, "_list.txt", sep = ""))
-site.info.fname = file.path(data.dir, paste(p.ref, "_m.da.ca.csv", sep = ""))
-min.da.CM.CA.fname = file.path(data.dir, paste(p.ref, "_min.da.CM.ca.csv", sep = ""))
 
@@
 
-```{r prepare_site_data}
+```{r prepare_mode_data}
 # prepare the data
 nH.exp = read.csv(nH.exp.fname, header = T)
-
 nH.mut = read.csv(nH.mut.fname, header = T)
-
 nH.medium = read.csv(nH.medium.fname, header = T)
@@
 
-```{r comparisson-of-means}
+```{r comparisson-of-means, fig.cap = "blue = experimental - green = mut - red = medium selection"}
 # calculate means
@@
 # scale profiles
-mean.nH.exp = rank(mean.nH.exp)
-mean.nH.mut = rank(mean.nH.mut)
-mean.nH.medium = rank(mean.nH.medium)
+mean.nH.exp = scale(mean.nH.exp[which(!is.na(mean.nH.exp))])
+mean.nH.mut = scale(mean.nH.mut[which(!is.na(mean.nH.mut))])
+mean.nH.medium = scale(mean.nH.medium[which(!is.na(mean.nH.medium))])
 
-plot(mean.nH.exp, ylab = "nH", xlab = "site", col = "blue")
+plot(mean.nH.exp, ylab = "<nH>", xlab = "mode", col = "blue")
+points(mean.nH.mut, col = "green")
+points(mean.nH.medium, col = "red")
+
+r.exp.mut = cor(mean.nH.exp, mean.nH.mut)
+r.exp.medium = cor(mean.nH.exp, mean.nH.medium)
+r.mut.medium = cor(mean.nH.mut, mean.nH.medium)
+
+cor.df = data.frame("comparison" = c("exp vs mut", "exp vs medium", "mut vs medium"),
+                    "R" = c(r.exp.mut, r.exp.medium, r.mut.medium))
+knitr::kable(cor.df, digits = 2)
+```
+
+```{r vs-mean-profiles}
+
+# plot exp vs simulated profiles 
+par(pty = "s")
+
+plot(x = mean.nH.exp, 
+     y = mean.nH.mut, 
+     xlab = "exp.mean.nH", 
+     ylab = "mut.mean.nH")
+abline(0, 1)
+
+plot(x = mean.nH.exp, 
+     y = mean.nH.medium, 
+     xlab = "exp.mean.nH", 
+     ylab = "medium.mean.nH")
+abline(0, 1)
+
+plot(x = mean.nH.mut, 
+     y = mean.nH.medium, 
+     xlab = "mut.mean.nH", 
+     ylab = "medium.mean.nH")
+abline(0, 1)
+```
+
+```{r comparisson-of-means-100-modes}
+
+# get first 100 modes and re-scale
+mean.nH.exp = scale(mean.nH.exp[1:100])
+mean.nH.mut = scale(mean.nH.mut[1:100])
+mean.nH.medium = scale(mean.nH.medium[1:100])
+
+plot(mean.nH.exp, ylab = "<nH>", xlab = "mode", col = "blue")
 points(mean.nH.mut, col = "green")

### 2017-04-04 analysis-dynamical-nR.Rmd
dinámica 4/4/17

@@
 
-```{r prepare_site_data}
+```{r prepare_mode_data}
 # prepare the data
 nR.exp = read.csv(nR.exp.fname, header = T)
-
 nR.mut = read.csv(nR.mut.fname, header = T)
-
 nR.medium = read.csv(nR.medium.fname, header = T)
@@
 # scale profiles
-mean.nR.exp = rank(mean.nR.exp)
-mean.nR.mut = rank(mean.nR.mut)
-mean.nR.medium = rank(mean.nR.medium)
+mean.nR.exp = scale(mean.nR.exp[which(!is.na(mean.nR.exp))])
+mean.nR.mut = scale(mean.nR.mut[which(!is.na(mean.nR.mut))])
+mean.nR.medium = scale(mean.nR.medium[which(!is.na(mean.nR.medium))])
 
-plot(mean.nR.exp, ylab = "nR", xlab = "site", col = "blue")
+plot(mean.nR.exp, ylab = "<nR>", xlab = "mode", col = "blue")
+points(mean.nR.mut, col = "green")
+points(mean.nR.medium, col = "red")
+
+r.exp.mut = cor(mean.nR.exp, mean.nR.mut)
+r.exp.medium = cor(mean.nR.exp, mean.nR.medium)
+r.mut.medium = cor(mean.nR.mut, mean.nR.medium)
+
+cor.df = data.frame("comparison" = c("exp vs mut", "exp vs medium", "mut vs medium"),
+                    "R" = c(r.exp.mut, r.exp.medium, r.mut.medium))
+knitr::kable(cor.df, digits = 2)
+```
+
+```{r vs-mean-profiles}
+
+# plot exp vs simulated profiles 
+par(pty = "s")
+
+plot(x = mean.nR.exp, 
+     y = mean.nR.mut, 
+     xlab = "exp.mean.nR", 
+     ylab = "mut.mean.nR")
+abline(0, 1)
+
+plot(x = mean.nR.exp, 
+     y = mean.nR.medium, 
+     xlab = "exp.mean.nR", 
+     ylab = "medium.mean.nR")
+abline(0, 1)
+
+plot(x = mean.nR.mut, 
+     y = mean.nR.medium, 
+     xlab = "mut.mean.nR", 
+     ylab = "medium.mean.nR")
+abline(0, 1)
+```
+
+```{r comparisson-of-means-100-modes}
+
+# get first 100 modes and re-scale
+mean.nR.exp = scale(mean.nR.exp[1:100])
+mean.nR.mut = scale(mean.nR.mut[1:100])
+mean.nR.medium = scale(mean.nR.medium[1:100])
+
+plot(mean.nR.exp, ylab = "<nR>", xlab = "mode", col = "blue")
 points(mean.nR.mut, col = "green")

### 2017-04-04 analysis-structure.Rmd
dinámica 4/4/17

@@
 ```
+### sequence - structure comparison
+
 ```{r structure-profiles-CN-comparison}
@@
 par(pty = "s")
+
 plot(x = d.exp$mean.z.RSD, y = CN, xlab = "experimental <zRSDi>")

### 2017-04-04 FUNCTIONS/AnalyzeExperimentalTheoreticalCM.R

@@ -182,9 +182,9 @@ AnalyzeExperimentalTheoreticalCM <- function(family,
   m.exp.norm.dr.squarei.windows.rot = matrix(nrow = n.prot, ncol = n.sites.p.ref)
   m.exp.norm.dr.squarei.windows.contacts.rot = matrix(nrow = n.prot, ncol = n.sites.p.ref)
   m.exp.local.score = matrix(nrow = n.prot, ncol = n.sites.p.ref)
-  m.exp.square.dif.MSF = matrix(nrow = n.mut, ncol = n.sites.p.ref)
-  m.exp.nH = matrix(nrow = n.mut, ncol = 3 * n.sites.p.ref)
-  m.exp.nR = matrix(nrow = n.mut, ncol = 3 * n.sites.p.ref)
+  m.exp.square.dif.MSF = matrix(nrow = n.prot, ncol = n.sites.p.ref)
+  m.exp.nH = matrix(nrow = n.prot, ncol = 3 * n.sites.p.ref)
+  m.exp.nR = matrix(nrow = n.prot, ncol = 3 * n.sites.p.ref)
   
   # start a loop to evaluate each protein of the family
   for (P in (1:n.prot)) {

### 2017-04-09 analysis-dynamical-MSF-structure.Rmd
dinámica 9/4/17

---
title: "Dynamical Divergence Analysis"
author: "Maria Laura Marcos, Julian Echave"
output: html_document
---

# Introduction
We study the evolutionary divergence of proteins using the LF-ENM and comparing simulated mutants with experimental data.

```{r setup, include = FALSE}
# set chunk options
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r load_packages}
# load packages
library(ggplot2)
library(reshape2)
library(plyr)
library(quantreg)
library(bio3d)

# load functions
source(file.path(data.dir, "multiplot.R"))
source(file.path(data.dir, "my-functions.R")) 
```

```{r set_my_colors}
# set my colors
myColors = c("blue", "darkgreen","darkgreen", "red", "red", "red") 
names(myColors) <- c("exp", "mut", "no-selection", "medium", "selection", "mut+sel")
```

```{r set_run_variables}
# set significance factors
f95 = 1.96
f99 = 2.6
f999 = 3.3
```

```{r set_file_names}
# set input filenames
## data
reference.fname = file.path(data.dir, paste(family, "_ref.txt", sep = ""))
protein_list.fname = file.path(data.dir, paste(family, "_list.txt", sep = ""))
site.info.fname = file.path(data.dir, paste(p.ref, "_m.da.ca.csv", sep = ""))
min.da.CM.CA.fname = file.path(data.dir, paste(p.ref, "_min.da.CM.ca.csv", sep = ""))

## profiles to compare
### square.dif.MSF
square.dif.MSF.exp.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.exp.square.dif.MSF.csv", sep = ""))
square.dif.MSF.medium.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_medium.sel_K.analysis_Keff_out_m.theo.square.dif.MSF.csv", sep = ""))
square.dif.MSF.mut.fname = file.path(data.dir,paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.square.dif.MSF.csv", sep = ""))

### dri2
dri2.exp.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.exp.norm.dr.squarei.csv", sep = ""))
dri2.medium.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_medium.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
dri2.mut.fname = file.path(data.dir,paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))

```

```{r set_reference_protein}
# which is the reference protein?
reference = as.character(read.table(reference.fname, header = F)[1, 1])
if (reference != p.ref) {
  print("Warning: different references")
}
```

We studied the `r family` family. 
We used the ENM `r enm` with R0 = `r R0` to generate mutants.
We used as reference for the ENM the protein with pdb code `r reference`. 
We simulated `r n.mut.p` mutants of this reference for each protein of the family.
The `r family` family is of the type `r type` and consists of the following proteins:

```{r set_experimental_protein_names, comment = ""}
# experimental protein names
protein.exp = read.table(protein_list.fname, header = F, stringsAsFactors = F)[, 1]
protein.exp = protein.exp[protein.exp != reference]
print(protein.exp)
```

```{r set-site-info}
# read site information of the reference protein
site.info = read.csv(site.info.fname, header = T, sep = ",")

# add info to site.info
d = ddply(site.info, "site", .fun = function(x) data.frame("da" = min(x[, c(-1, -2)])))

# define shells of active.sites site neighborhood
d$shell = cut(d$da, breaks = c(-.1, 2.5, 7.5, 12.5, 17.5, 22.5, 27.5, 32.5, 37.5, 42.5, 47.5, 52.5, max(d$da)))
levels(d$shell) = seq(length(levels(d$shell))) - 1 # rename shell levels
site.info = merge(site.info, d, by = "site")

# read reference pdb and calculate resno, AA, and CN
reference.pdb.fname = file.path(data.dir,paste(reference, ".pdb", sep = ""))
ref.pdb = read.pdb(reference.pdb.fname)
inds = atom.select(ref.pdb, elety = "CA")
ref.pdb.ca = ref.pdb$atom[inds$atom,]
cmap.ca = cmap(ref.pdb$xyz[inds$xyz], dcut = R0, scut = 0, mask.lower = F)
CN = rowSums(cmap.ca, na.rm = T) - 1 # diag(cmap.ca) returned by cmap is 1!
n.sites = length(CN)
AA = ref.pdb.ca$resid
resno = ref.pdb.ca$resno
pdb.info = data.frame(resno, AA, CN)
names(pdb.info) = c("resno", "AA", paste("CN", as.character(R0), sep = ""))

# add pdb.info to site.info
site.info = cbind(site.info, pdb.info)
```

```{r read_site_data}
# read MSF data
square.dif.MSF.exp = read.csv(square.dif.MSF.exp.fname, header = T)
square.dif.MSF.mut = read.csv(square.dif.MSF.mut.fname, header = T)
square.dif.MSF.medium = read.csv(square.dif.MSF.medium.fname, header = T)

# read data
dri2.exp = read.csv(dri2.exp.fname, header = T)
dri2.mut = read.csv(dri2.mut.fname, header = T)
dri2.medium = read.csv(dri2.medium.fname, header = T)
```

```{r prepare-site-data-MSF}

# prepare the data
## exp
tsquare.dif.MSF.exp = as.data.frame(t(as.matrix(square.dif.MSF.exp)))
tsquare.dif.MSF.exp = cbind(site.info, tsquare.dif.MSF.exp)
siteComparison.exp = melt(tsquare.dif.MSF.exp, id.vars = names(site.info), variable.name = "protein", value.name = "square.dif.MSF")

## mut
tsquare.dif.MSF.mut = as.data.frame(t(as.matrix(square.dif.MSF.mut)))
tsquare.dif.MSF.mut = cbind(site.info, tsquare.dif.MSF.mut)
siteComparison.mut = melt(tsquare.dif.MSF.mut, id.vars = names(site.info), variable.name = "protein", value.name = "square.dif.MSF")

## medium
tsquare.dif.MSF.medium = as.data.frame(t(as.matrix(square.dif.MSF.medium)))
tsquare.dif.MSF.medium = cbind(site.info, tsquare.dif.MSF.medium)
siteComparison.medium = melt(tsquare.dif.MSF.medium, id.vars = names(site.info), variable.name = "protein", value.name = "square.dif.MSF")

# bluild the data.frame
siteComparison.all.datasets = rbind(data.frame("dataset" = "exp", siteComparison.exp),
                                    data.frame("dataset" = "mut", siteComparison.mut),
                                    data.frame("dataset" = "medium", siteComparison.medium))

siteComparison.all.datasets = ddply(siteComparison.all.datasets, c("dataset", "protein"), mutate,
          "r.SDF" = rank(square.dif.MSF, na.last = "keep")) 
```

```{r prepare-site-data-dri2}

# prepare the data
## exp
tdri2.exp = as.data.frame(t(as.matrix(dri2.exp)))
tdri2.exp = cbind(site.info, tdri2.exp)
siteComparison.exp = melt(tdri2.exp, id.vars = names(site.info), variable.name = "protein", value.name = "dri2")

## mut
tdri2.mut = as.data.frame(t(as.matrix(dri2.mut)))
tdri2.mut = cbind(site.info, tdri2.mut)
siteComparison.mut = melt(tdri2.mut, id.vars = names(site.info), variable.name = "protein", value.name = "dri2")

## medium
tdri2.medium = as.data.frame(t(as.matrix(dri2.medium)))
tdri2.medium = cbind(site.info, tdri2.medium)
siteComparison.medium = melt(tdri2.medium, id.vars = names(site.info), variable.name = "protein", value.name = "dri2")

# bluild the data.frame
siteComparison.all.datasets.dri2 = rbind(data.frame("dataset" = "exp", siteComparison.exp),
                                         data.frame("dataset" = "mut", siteComparison.mut),
                                         data.frame("dataset" = "medium", siteComparison.medium))

siteComparison.all.datasets.dri2 = ddply(siteComparison.all.datasets.dri2, c("dataset", "protein"), mutate,
          "RSD" = sqrt(dri2), 
          "z.RSD" = vscale(RSD))
```

### Dynamical divergence along sites

In this section we consider dynamical divergence along Cartessian coordinates. square.dif.MSF is the square diference between MSF of the proteins relative to the reference protein. We ranked profiles because we found it is the best way to deal with large differences in MSF of divergent sites. We also tried z-normalizing but the results were not good.

```{r mean-se-r.SDF-vs-site, fig.cap = "Black lines are the active sites and grey lines are their contacts"}

# comparison of r.SDF profiles with functional sites
## prepare dat
dat = siteComparison.all.datasets
dat$dataset = revalue(dat$dataset, c("medium" = "selection"))
dat$dataset = revalue(dat$dataset, c("mut" = "no-selection"))

## dat with means and standard errors
d = ddply(dat,c("dataset", "site", "AA", "shell"), function(x) {
                mean.r.SDF = mean(x$r.SDF, na.rm = T)
                ndata = sum(!is.na(x$r.SDF))
                se.r.SDF = sd(x$r.SDF, na.rm = T) / sqrt(ndata)
                data.frame(mean.r.SDF, ndata, se.r.SDF)
})

## find the active site and its contacts
active.sites = d$site[d$shell == 0]
contacts.active.sites = d$site[d$shell == 1]

## prepare plots with mean profiles and deviations
p = ggplot(d, aes(x = site, y = mean.r.SDF, col = dataset, fill = dataset)) +
    geom_line() +
    geom_ribbon(aes(ymin = mean.r.SDF - f95 * se.r.SDF, ymax = mean.r.SDF + se.r.SDF), alpha = .4, show.legend = F) +
    geom_vline(xintercept = active.sites, show.legend = F) +
    geom_vline(xintercept = contacts.active.sites, col = "grey", show.legend = F) +
    labs(x = "site", y = "<ranked square dif MSFi>") +
    scale_colour_manual(name = NULL, values = myColors) + 
    scale_fill_manual(name = NULL, values = myColors)

## plot separate and comparative plots
p.facet = p + facet_grid(dataset~., switch = "y") + theme(legend.position = "bottom")

p.facet %+% subset(d, dataset == "exp") 
p.facet %+% subset(d, dataset == "no-selection")
p.facet %+% subset(d, dataset == "selection") 
p.facet

## plot superimposed plots
p + theme(legend.position = "bottom")
```

```{r comparison-of-means}

# extract means
d.exp = subset(d, dataset == "exp")
d.mut = subset(d, dataset == "no-selection")
d.medium = subset(d, dataset == "selection")

mean.r.square.dif.MSF.exp = d.exp$mean.r.SDF
mean.r.square.dif.MSF.mut = d.mut$mean.r.SDF
mean.r.square.dif.MSF.medium = d.medium$mean.r.SDF

# calculate correlations
r.exp.mut = cor(mean.r.square.dif.MSF.exp, mean.r.square.dif.MSF.mut)
r.exp.medium = cor(mean.r.square.dif.MSF.exp, mean.r.square.dif.MSF.medium)
r.mut.medium = cor(mean.r.square.dif.MSF.mut, mean.r.square.dif.MSF.medium)

cor.df = data.frame("comparison" = c("exp vs no-selection", "exp vs selection", "no-selection vs selection"),
                    "R" = c(r.exp.mut, r.exp.medium, r.mut.medium))

knitr::kable(cor.df, digits = 2)

# plot comparative profiles 
par(pty = "s")

plot(x = mean.r.square.dif.MSF.exp, 
     y = mean.r.square.dif.MSF.mut, 
     xlab = "exp.mean.r.square.dif.MSF", 
     ylab = "no.selection.mean.r.square.dif.MSF")
abline(0, 1)

plot(x = mean.r.square.dif.MSF.exp, 
     y = mean.r.square.dif.MSF.medium, 
     xlab = "exp.mean.r.square.dif.MSF", 
     ylab = "selection.mean.r.square.dif.MSF")
abline(0, 1)

plot(x = mean.r.square.dif.MSF.mut, 
     y = mean.r.square.dif.MSF.medium, 
     xlab = "no.selection.mean.r.square.dif.MSF", 
     ylab = "selection.mean.r.square.dif.MSF")
abline(0, 1)
```

```{r mean-z.RSD-profiles}

# prepare dat
dat = siteComparison.all.datasets.dri2
dat$dataset = revalue(dat$dataset, c("medium" = "selection"))
dat$dataset = revalue(dat$dataset, c("mut" = "no-selection"))

# dat with means and standard errors
d = ddply(dat,c("dataset", "site", "AA", "shell"), function(x) {
                mean.z.RSD = mean(x$z.RSD, na.rm = T)
                ndata = sum(!is.na(x$z.RSD))
                se.z.RSD = sd(x$z.RSD, na.rm = T) / sqrt(ndata)
                data.frame(mean.z.RSD, ndata, se.z.RSD)
})

# extract means
d.exp = subset(d, dataset == "exp")
d.mut = subset(d, dataset == "no-selection")
d.medium = subset(d, dataset == "selection")

mean.r.dri2.exp = d.exp$mean.z.RSD
mean.r.dri2.mut = d.mut$mean.z.RSD
mean.r.dri2.medium = d.medium$mean.z.RSD
```

### Comparison structure - dynamics

In this section we compare dri2 profiles (structural variability) with square dif MSF profiles (dynamical variability). To do this, we ranked each profile.

```{r structure-vs-dynamics}

# rank profiles
mean.r.dri2.exp = rank(mean.r.dri2.exp)
mean.r.dri2.mut = rank(mean.r.dri2.mut)
mean.r.dri2.medium = rank(mean.r.dri2.medium)

mean.r.square.dif.MSF.exp = rank(mean.r.square.dif.MSF.exp)
mean.r.square.dif.MSF.mut = rank(mean.r.square.dif.MSF.mut)
mean.r.square.dif.MSF.medium = rank(mean.r.square.dif.MSF.medium)

# plot comparative profiles
par(pty = "s")

plot(x = mean.r.square.dif.MSF.exp, 
     y = mean.r.dri2.exp, 
     xlab = "exp.mean.r.square.dif.MSF", 
     ylab = "exp.mean.r.dri2")
abline(0, 1)

plot(x = mean.r.square.dif.MSF.medium, 
     y = mean.r.dri2.medium, 
     xlab = "selection.mean.r.square.dif.MSF", 
     ylab = "selection.mean.r.dri2")
abline(0, 1)

plot(x = mean.r.square.dif.MSF.mut, 
     y = mean.r.dri2.mut, 
     xlab = "no.selection.mean.r.square.dif.MSF", 
     ylab = "no.selection.mean.r.dri2")
abline(0, 1)

# calculate correlations
r.exp = cor(mean.r.square.dif.MSF.exp, mean.r.dri2.exp)
r.medium = cor(mean.r.square.dif.MSF.medium, mean.r.dri2.medium)
r.mut = cor(mean.r.square.dif.MSF.mut, mean.r.dri2.mut)

cor.df = data.frame("comparison structure - dynamics" = c("exp", "selection", "no-selection"),
                    "R" = c(r.exp, r.medium, r.mut))
knitr::kable(cor.df, digits = 2)
```

### 2017-04-09 analysis-dynamical-nH.Rmd
dinámica 9/4/17

@@
 
-In this section we consider dynamical divergence using normal modes coordinates.
+In this section we consider dynamical divergence using normal modes coordinates. We calculated mean nH and we z-normalized profiles.
 
-```{r comparisson-of-means, fig.cap = "blue = experimental - green = mut - red = medium selection"}
+```{r comparison-of-means, fig.cap = "blue = experimental - green = no-selection - red = selection"}
 # calculate means
@@
 
-cor.df = data.frame("comparison" = c("exp vs mut", "exp vs medium", "mut vs medium"),
+cor.df = data.frame("comparison" = c("exp vs no-selection", "exp vs selection", "no-selection vs selection"),
                     "R" = c(r.exp.mut, r.exp.medium, r.mut.medium))
@@
      xlab = "exp.mean.nH", 
-     ylab = "mut.mean.nH")
+     ylab = "no.selection.mean.nH")
 abline(0, 1)
@@
      xlab = "exp.mean.nH", 
-     ylab = "medium.mean.nH")
+     ylab = "selection.mean.nH")
 abline(0, 1)
@@
      y = mean.nH.medium, 
-     xlab = "mut.mean.nH", 
-     ylab = "medium.mean.nH")
+     xlab = "no.selection.mean.nH", 
+     ylab = "selection.mean.nH")
 abline(0, 1)
@@
 
-```{r comparisson-of-means-100-modes}
+```{r comparison-of-means-100-modes}
 

### 2017-04-09 analysis-dynamical-nR.Rmd
dinámica 9/4/17

@@
 
-In this section we consider dynamical divergence using normal modes coordinates.
+In this section we consider dynamical divergence using normal modes coordinates. We calculated mean nR and we z-normalized profiles.
 
-```{r comparisson-of-means, fig.cap = "blue = experimental - green = mut - red = medium selection"}
+```{r comparison-of-means, fig.cap = "blue = experimental - green = no-selection - red = selection"}
 # calculate means
@@
      xlab = "exp.mean.nR", 
-     ylab = "mut.mean.nR")
+     ylab = "no.selection.mean.nR")
 abline(0, 1)
@@
      xlab = "exp.mean.nR", 
-     ylab = "medium.mean.nR")
+     ylab = "selection.mean.nR")
 abline(0, 1)
@@
      y = mean.nR.medium, 
-     xlab = "mut.mean.nR", 
-     ylab = "medium.mean.nR")
+     xlab = "no.selection.mean.nR", 
+     ylab = "selection.mean.nR")
 abline(0, 1)

### 2017-04-09 analysis-structure.Rmd
dinámica 9/4/17

@@
 myColors = c("blue", "darkgreen", "darkgreen", "red", "red") 
-names(myColors) <- c("exp", "mut", "no-selection", "strong", "selection")
+names(myColors) <- c("exp", "mut", "no-selection", "medium", "selection")
 ```
@@
 dri2.exp.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.exp.norm.dr.squarei.csv", sep = ""))
-dri2.strong.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_strong.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
+dri2.medium.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_medium.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
 dri2.mut.fname = file.path(data.dir,paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
@@
 sim.data.no.sel.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_out_df.data.csv", sep = ""))
-sim.data.strong.sel.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_strong.sel_out_df.data.csv", sep = ""))
+sim.data.medium.sel.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_medium.sel_out_df.data.csv", sep = ""))
 
@@
 
-## strong
-dri2.strong = read.csv(dri2.strong.fname, header = T)
+## medium
+dri2.medium = read.csv(dri2.medium.fname, header = T)
 site = site.info$site
-dri2.strong = dri2.strong[1:length(protein.exp), site]
-rownames(dri2.strong) = paste("strong", rownames(dri2.strong), sep = "")
+dri2.medium = dri2.medium[1:length(protein.exp), site]
+rownames(dri2.medium) = paste("medium", rownames(dri2.medium), sep = "")
 ```
@@
 
-## strong
-tdri2.strong = as.data.frame(t(as.matrix(dri2.strong)))
-tdri2.strong = cbind(site.info, tdri2.strong)
-siteComparison.strong = melt(tdri2.strong, id.vars = names(site.info), variable.name = "protein", value.name = "dri2")
+## medium
+tdri2.medium = as.data.frame(t(as.matrix(dri2.medium)))
+tdri2.medium = cbind(site.info, tdri2.medium)
+siteComparison.medium = melt(tdri2.medium, id.vars = names(site.info), variable.name = "protein", value.name = "dri2")
 
@@
                                     data.frame("dataset" = "mut", siteComparison.mut),
-                                    data.frame("dataset" = "strong", siteComparison.strong))
+                                    data.frame("dataset" = "medium", siteComparison.medium))
 
@@
 dat = siteComparison.all.datasets
-dat$dataset = revalue(dat$dataset, c("strong" = "selection"))
+dat$dataset = revalue(dat$dataset, c("medium" = "selection"))
 dat$dataset = revalue(dat$dataset, c("mut" = "no-selection"))
@@
 d.mut = subset(d, dataset == "no-selection")
-d.strong = subset(d, dataset == "selection")
+d.medium = subset(d, dataset == "selection")
 
@@
 r.exp.mut = cor(d.exp$mean.z.RSD, d.mut$mean.z.RSD)
-r.exp.strong = cor(d.exp$mean.z.RSD, d.strong$mean.z.RSD)
-r.mut.strong = cor(d.mut$mean.z.RSD, d.strong$mean.z.RSD)
+r.exp.medium = cor(d.exp$mean.z.RSD, d.medium$mean.z.RSD)
+r.mut.medium = cor(d.mut$mean.z.RSD, d.medium$mean.z.RSD)
 
-cor.df = data.frame("comparison" = c("exp vs mut", "exp vs strong", "mut vs strong"),
-                    "R" = c(r.exp.mut, r.exp.strong, r.mut.strong))
+cor.df = data.frame("comparison" = c("exp vs mut", "exp vs medium", "mut vs medium"),
+                    "R" = c(r.exp.mut, r.exp.medium, r.mut.medium))
 
@@
 plot(x = d.exp$mean.z.RSD, 
-     y = d.strong$mean.z.RSD, 
+     y = d.medium$mean.z.RSD, 
      xlab = "exp.mean.z.RSD", 
-     ylab = "strong.mean.z.RSD", 
-     xlim = c(min(c(d.exp$mean.z.RSD, d.strong$mean.z.RSD)), max(c(d.exp$mean.z.RSD, d.strong$mean.z.RSD))),
-     ylim = c(min(c(d.exp$mean.z.RSD, d.strong$mean.z.RSD)), max(c(d.exp$mean.z.RSD, d.strong$mean.z.RSD))))
-points(x = as.numeric(d.exp$mean.z.RSD)[contacts.active.sites], y = as.numeric(d.strong$mean.z.RSD)[contacts.active.sites], col = "green")
-points(x = as.numeric(d.exp$mean.z.RSD)[active.sites], y = as.numeric(d.strong$mean.z.RSD)[active.sites], col = "yellow")
+     ylab = "medium.mean.z.RSD", 
+     xlim = c(min(c(d.exp$mean.z.RSD, d.medium$mean.z.RSD)), max(c(d.exp$mean.z.RSD, d.medium$mean.z.RSD))),
+     ylim = c(min(c(d.exp$mean.z.RSD, d.medium$mean.z.RSD)), max(c(d.exp$mean.z.RSD, d.medium$mean.z.RSD))))
+points(x = as.numeric(d.exp$mean.z.RSD)[contacts.active.sites], y = as.numeric(d.medium$mean.z.RSD)[contacts.active.sites], col = "green")
+points(x = as.numeric(d.exp$mean.z.RSD)[active.sites], y = as.numeric(d.medium$mean.z.RSD)[active.sites], col = "yellow")
 abline(0, 1)
@@
 plot(x = d.mut$mean.z.RSD, 
-     y = d.strong$mean.z.RSD, 
+     y = d.medium$mean.z.RSD, 
      xlab = "mut.mean.z.RSD", 
-     ylab = "strong.mean.z.RSD", 
-     xlim = c(min(c(d.mut$mean.z.RSD, d.strong$mean.z.RSD)), max(c(d.mut$mean.z.RSD, d.strong$mean.z.RSD))),
-     ylim = c(min(c(d.mut$mean.z.RSD, d.strong$mean.z.RSD)), max(c(d.mut$mean.z.RSD, d.strong$mean.z.RSD))))
-points(x = as.numeric(d.mut$mean.z.RSD)[contacts.active.sites], y = as.numeric(d.strong$mean.z.RSD)[contacts.active.sites], col = "green")
-points(x = as.numeric(d.mut$mean.z.RSD)[active.sites], y = as.numeric(d.strong$mean.z.RSD)[active.sites], col = "yellow")
+     ylab = "medium.mean.z.RSD", 
+     xlim = c(min(c(d.mut$mean.z.RSD, d.medium$mean.z.RSD)), max(c(d.mut$mean.z.RSD, d.medium$mean.z.RSD))),
+     ylim = c(min(c(d.mut$mean.z.RSD, d.medium$mean.z.RSD)), max(c(d.mut$mean.z.RSD, d.medium$mean.z.RSD))))
+points(x = as.numeric(d.mut$mean.z.RSD)[contacts.active.sites], y = as.numeric(d.medium$mean.z.RSD)[contacts.active.sites], col = "green")
+points(x = as.numeric(d.mut$mean.z.RSD)[active.sites], y = as.numeric(d.medium$mean.z.RSD)[active.sites], col = "yellow")
 abline(0, 1)
@@
 
-## mut + sel / strong
-strong.mean.z.RSD.vec <- vec2resno(as.vector(d.strong$mean.z.RSD), sort(rep(1:ncol(pdb.xyz.ca),3)))
-write.pdb(xyz = c(pdb.xyz.ca), b = strong.mean.z.RSD.vec, file = file.path(data.dir, paste(p.ref, "_strong.pdb", sep = "")))
+## mut + sel / medium
+medium.mean.z.RSD.vec <- vec2resno(as.vector(d.medium$mean.z.RSD), sort(rep(1:ncol(pdb.xyz.ca),3)))
+write.pdb(xyz = c(pdb.xyz.ca), b = medium.mean.z.RSD.vec, file = file.path(data.dir, paste(p.ref, "_medium.pdb", sep = "")))
 ```
@@
 
-## strong sel
-sim.data.strong.sel = read.csv(sim.data.strong.sel.fname)
-mut.site.strong.sel = sim.data.strong.sel$site
-p.accept.strong.sel = sim.data.strong.sel$p.accept
+## medium sel
+sim.data.medium.sel = read.csv(sim.data.medium.sel.fname)
+mut.site.medium.sel = sim.data.medium.sel$site
+p.accept.medium.sel = sim.data.medium.sel$p.accept
 
@@
 mean.p.accept.no.sel = c()
-mean.p.accept.strong.sel = c()
+mean.p.accept.medium.sel = c()
 
@@
   mut.site.no.sel = mut.site.no.sel - n.sites
-  mut.site.strong.sel = mut.site.strong.sel - n.sites
+  mut.site.medium.sel = mut.site.medium.sel - n.sites
   CN.CM = sim.data.no.sel$CN
@@
 
-  p.accept.strong.sel.i = p.accept.strong.sel[which(mut.site.strong.sel == i)]
-  mean.p.accept.strong.sel.i = mean(p.accept.strong.sel.i)
-  mean.p.accept.strong.sel[i] = mean.p.accept.strong.sel.i
+  p.accept.medium.sel.i = p.accept.medium.sel[which(mut.site.medium.sel == i)]
+  mean.p.accept.medium.sel.i = mean(p.accept.medium.sel.i)
+  mean.p.accept.medium.sel[i] = mean.p.accept.medium.sel.i
 }
@@
 
-# compare exp vs strong sel profiles
+# compare exp vs medium sel profiles
 ## plot
@@
 
-plot(x = log(mean.p.accept.strong.sel), y = CN)
-plot(x = log(mean.p.accept.strong.sel), y = score)
+plot(x = log(mean.p.accept.medium.sel), y = CN)
+plot(x = log(mean.p.accept.medium.sel), y = score)
 plot(x = score, y = CN)
@@
 ## calculate corelations
-r.mean.p.accept.strong.sel.CN = cor(log(mean.p.accept.strong.sel), CN)
-r.mean.p.accept.strong.sel.score = cor(log(mean.p.accept.strong.sel), score)
+r.mean.p.accept.medium.sel.CN = cor(log(mean.p.accept.medium.sel), CN)
+r.mean.p.accept.medium.sel.score = cor(log(mean.p.accept.medium.sel), score)
 r.score.CN = cor(score, CN)
 
-cor.df = data.frame("comparison" = c("log(p.accept.strong.sel) vs CN", "log(p.accept.strong.sel) vs score", "score vs CN"),
-                    "R" = c(r.mean.p.accept.strong.sel.CN , r.mean.p.accept.strong.sel.score, r.score.CN))
+cor.df = data.frame("comparison" = c("log(p.accept.medium.sel) vs CN", "log(p.accept.medium.sel) vs score", "score vs CN"),
+                    "R" = c(r.mean.p.accept.medium.sel.CN , r.mean.p.accept.medium.sel.score, r.score.CN))
 
@@
 plot(x = d.mut$mean.z.RSD, y = CN, xlab = "theoretical with no selection <zRSDi>")
-plot(x = d.strong$mean.z.RSD, y = CN, xlab = "theoretical with strong selection <zRSDi>")
+plot(x = d.medium$mean.z.RSD, y = CN, xlab = "theoretical with medium selection <zRSDi>")
 
@@
 r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, CN)
-r.strong.mean.z.RSD.CN = cor(d.strong$mean.z.RSD, CN)
+r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, CN)
 
-cor.df = data.frame("comparison" = c("exp.mean.z.RSD vs CN", "mut.mean.z.RSD vs CN", "strong.mean.z.RSD vs CN"),
-                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.strong.mean.z.RSD.CN))
+cor.df = data.frame("comparison" = c("exp.mean.z.RSD vs CN", "mut.mean.z.RSD vs CN", "medium.mean.z.RSD vs CN"),
+                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))
 

### 2017-04-09 MainReport.R

@@ -47,7 +47,7 @@ for (f in (1:nrow(input))) {
                    output_file =  paste("OUT/report_structure_CA_core_", family, "_", enm, "_R0_", R0, ".html", sep = ''))
   
   ### MSF
-  rmarkdown::render('analysis-dynamical-MSF.Rmd', 
+  rmarkdown::render('analysis-dynamical-MSF-structure.Rmd', 
                     output_file =  paste("OUT/report__dynamical_MSF_CA_", family, "_", enm, "_R0_", R0, ".html", sep = ''))
   
   ### nH
@@ -84,7 +84,7 @@ for (f in (1:nrow(input))) {
                     output_file =  paste("OUT/report_structure_CM_core_", family, "_", enm, "_R0_", R0, ".html", sep = ''))
   
   ### MSF
-  rmarkdown::render('analysis-dynamical-MSF.Rmd', 
+  rmarkdown::render('analysis-dynamical-MSF-structure.Rmd', 
                     output_file =  paste("OUT/report_dynamical_MSF_CM_", family, "_", enm, "_R0_", R0, ".html", sep = ''))
   
   ### nH
@@ -101,4 +101,5 @@ for (f in (1:nrow(input))) {
   ### local enviroment 
   #rmarkdown::render('analysis-structure-local-enviroment.Rmd', 
   #                  output_file =  paste("OUT/report_structure_local_enviroment_CM_", family, "_", enm, "_R0_", R0, ".html", sep = ''))
+
 }

### 2017-04-16 analysis-structure-core.Rmd
paper y dinámica

@@
 
-```{r}
+### Sequence comparison
+In this section we compare theoretical sequence profiles with sequence scores obtained from ConsurfDB.
+To obtain theoretical profiles, we calculated the number of times we had mutated each site for each selection regimen.
+
+```{r sequence-profiles-comparison}
 # read experimental data obtained from ConsurfDB

### 2017-04-16 analysis-structure-normal-modes.Rmd
paper y dinámica

@@
 # set my colors
-myColors = c("blue", "darkgreen", "red", "red") 
-names(myColors) <- c("exp", "mut", "strong", "mut+sel")
+myColors = c("blue", "darkgreen", "darkgreen", "red", "red") 
+names(myColors) <- c("exp", "mut", "no-selection", "medium", "selection")
 ```
@@
 Pn.exp.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.exp.Pn.csv", sep = ""))
-Pn.strong.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_strong.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
+Pn.medium.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_medium.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
 Pn.mut.fname = file.path(data.dir,paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
@@
 energy.exp.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.exp.va.csv", sep = ""))
-energy.strong.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_strong.sel_K.analysis_Keff_out_m.theo.va.csv", sep = ""))
+energy.medium.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_medium.sel_K.analysis_Keff_out_m.theo.va.csv", sep = ""))
 energy.mut.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.va.csv", sep = ""))
@@
 
-Pn.strong = read.csv(Pn.strong.fname, header = T)
-rownames(Pn.strong) = paste("strong", rownames(Pn.strong), sep = "")
-energy.strong = read.csv(energy.strong.fname, header = T)
-rownames(energy.strong) = paste("strong", rownames(energy.strong), sep = "")
+Pn.medium = read.csv(Pn.medium.fname, header = T)
+rownames(Pn.medium) = paste("medium", rownames(Pn.medium), sep = "")
+energy.medium = read.csv(energy.medium.fname, header = T)
+rownames(energy.medium) = paste("medium", rownames(energy.medium), sep = "")
 
@@
 ```{r prepare-mode-data}
-mode = seq(ncol(Pn.strong))
+mode = seq(ncol(Pn.medium))
 
-# Prepare modeComparison.strong
-tPn.strong = as.data.frame(t(as.matrix(Pn.strong)))
-tPn.strong = cbind(data.frame("mode" = mode), tPn.strong)
-Pn.strong.long = melt(tPn.strong, "mode", variable.name = "protein", value.name = "Pn")
+# Prepare modeComparison.medium
+tPn.medium = as.data.frame(t(as.matrix(Pn.medium)))
+tPn.medium = cbind(data.frame("mode" = mode), tPn.medium)
+Pn.medium.long = melt(tPn.medium, "mode", variable.name = "protein", value.name = "Pn")
 
-tenergy.strong = as.data.frame(t(as.matrix(energy.strong)))
-tenergy.strong = cbind(data.frame("mode" = mode), tenergy.strong)
-energy.strong.long = melt(tenergy.strong, "mode", variable.name = "protein", value.name = "energy")
-energy.strong.long$sn2 = 1/energy.strong.long$energy
+tenergy.medium = as.data.frame(t(as.matrix(energy.medium)))
+tenergy.medium = cbind(data.frame("mode" = mode), tenergy.medium)
+energy.medium.long = melt(tenergy.medium, "mode", variable.name = "protein", value.name = "energy")
+energy.medium.long$sn2 = 1/energy.medium.long$energy
 
-modeComparison.strong = merge(energy.strong.long, Pn.strong.long, by = c("mode", "protein"))
-modeComparison.strong = ddply(modeComparison.strong, "protein", mutate, "Pn" = Pn / mean(Pn, na.rm = T))
+modeComparison.medium = merge(energy.medium.long, Pn.medium.long, by = c("mode", "protein"))
+modeComparison.medium = ddply(modeComparison.medium, "protein", mutate, "Pn" = Pn / mean(Pn, na.rm = T))
 
@@
 modeComparison.exp <- na.omit(modeComparison.exp)
-modeComparison.strong <- na.omit(modeComparison.strong)
+modeComparison.medium <- na.omit(modeComparison.medium)
 modeComparison.mut <- na.omit(modeComparison.mut)
@@
 # fit median and quantiles to simulated data and add them to data.frames
-fit.strong.rq.5 <- rq(Pn ~ sn2, tau = .5, data = modeComparison.strong, method = "fn")
-fit.strong.rq.05 <- rq(Pn ~ sn2, tau = .05, data = modeComparison.strong, method = "fn")
-fit.strong.rq.95 <- rq(Pn ~ sn2, tau = .95, data = modeComparison.strong, method = "fn")
-modeComparison.strong$rq.5 = fit.strong.rq.5$fitted.values
-modeComparison.strong$rq.05 = fit.strong.rq.05$fitted.values
-modeComparison.strong$rq.95 = fit.strong.rq.95$fitted.values
+fit.medium.rq.5 <- rq(Pn ~ sn2, tau = .5, data = modeComparison.medium, method = "fn")
+fit.medium.rq.05 <- rq(Pn ~ sn2, tau = .05, data = modeComparison.medium, method = "fn")
+fit.medium.rq.95 <- rq(Pn ~ sn2, tau = .95, data = modeComparison.medium, method = "fn")
+modeComparison.medium$rq.5 = fit.medium.rq.5$fitted.values
+modeComparison.medium$rq.05 = fit.medium.rq.05$fitted.values
+modeComparison.medium$rq.95 = fit.medium.rq.95$fitted.values
 
@@
                                     data.frame("dataset" = "mut", modeComparison.mut),
-                                    data.frame("dataset" = "strong", modeComparison.strong))
+                                    data.frame("dataset" = "medium", modeComparison.medium))
 
-modeComparison.all.datasets$dataset = factor(modeComparison.all.datasets$dataset, levels = c("exp", "mut", "strong"))
+modeComparison.all.datasets$dataset = factor(modeComparison.all.datasets$dataset, levels = c("exp", "mut", "medium"))
 ```
@@
 dat = modeComparison.all.datasets
-dat$dataset = revalue(dat$dataset,c("strong" = "mut+sel"))
 
@@
 p.facet %+% subset(dat, dataset == "mut")
-p.facet %+% subset(dat, dataset == "mut+sel")
+p.facet %+% subset(dat, dataset == "medium")
 p.facet
@@
 dat = modeComparison.all.datasets
-dat$dataset = revalue(dat$dataset,c("strong" = "mut+sel"))
+dat$dataset = revalue(dat$dataset, c("medium" = "selection"))
+dat$dataset = revalue(dat$dataset, c("mut" = "no-selection"))
 
@@
 p.facet %+% subset(dat,dataset == "exp")
-p.facet %+% subset(dat,dataset == "mut")
-p.facet %+% subset(dat,dataset == "mut+sel")
+p.facet %+% subset(dat,dataset == "no-selection")
+p.facet %+% subset(dat,dataset == "selection")
 p.facet
@@
 ```{r correlation-mode-profiles}
+#dat$dataset = revalue(dat$dataset,c("medium" = "mut+sel"))
 dat = modeComparison.all.datasets
-#dat$dataset = revalue(dat$dataset,c("strong" = "mut+sel"))
+dat$dataset = revalue(dat$dataset, c("medium" = "selection"))
+dat$dataset = revalue(dat$dataset, c("mut" = "no-selection"))
 
@@
 dat.exp = subset(dat, dataset == "exp")
-dat.mut = subset(dat,dataset == "mut")
-dat.strong = subset(dat,dataset == "strong")
+dat.mut = subset(dat,dataset == "no-selection")
+dat.medium = subset(dat,dataset == "selection")
 
 r.exp.mut = cor(dat.exp$Pn.median, dat.mut$Pn.median)
-r.exp.strong = cor(dat.exp$Pn.median, dat.strong$Pn.median)
-r.mut.strong = cor(dat.mut$Pn.median, dat.strong$Pn.median)
-cor.df = data.frame("comparison" = c("exp vs mut", "exp vs strong", "mut vs strong"),
-                    "R" = c(r.exp.mut, r.exp.strong, r.mut.strong))
+r.exp.medium = cor(dat.exp$Pn.median, dat.medium$Pn.median)
+r.mut.medium = cor(dat.mut$Pn.median, dat.medium$Pn.median)
+cor.df = data.frame("comparison" = c("exp vs mut", "exp vs medium", "mut vs medium"),
+                    "R" = c(r.exp.mut, r.exp.medium, r.mut.medium))
 knitr::kable(cor.df, digits = 2)
@@
 plot(x = dat.exp$Pn.median, 
-     y = dat.strong$Pn.median, 
+     y = dat.medium$Pn.median, 
      xlab = "exp.Pn.median", 
-     ylab = "strong.Pn.median", 
-     xlim = c(min(c(dat.exp$Pn.median, dat.strong$Pn.median)), max(c(dat.exp$Pn.median, dat.strong$Pn.median))),
-     ylim = c(min(c(dat.exp$Pn.median, dat.strong$Pn.median)), max(c(dat.exp$Pn.median, dat.strong$Pn.median))))
+     ylab = "medium.Pn.median", 
+     xlim = c(min(c(dat.exp$Pn.median, dat.medium$Pn.median)), max(c(dat.exp$Pn.median, dat.medium$Pn.median))),
+     ylim = c(min(c(dat.exp$Pn.median, dat.medium$Pn.median)), max(c(dat.exp$Pn.median, dat.medium$Pn.median))))
 abline(0, 1)
@@
 plot(x = dat.mut$Pn.median, 
-     y = dat.strong$Pn.median, 
+     y = dat.medium$Pn.median, 
      xlab = "mut.Pn.median", 
-     ylab = "strong.Pn.median", 
-     xlim = c(min(c(dat.mut$Pn.median, dat.strong$Pn.median)), max(c(dat.mut$Pn.median, dat.strong$Pn.median))),
-     ylim = c(min(c(dat.mut$Pn.median, dat.strong$Pn.median)), max(c(dat.mut$Pn.median, dat.strong$Pn.median))))
+     ylab = "medium.Pn.median", 
+     xlim = c(min(c(dat.mut$Pn.median, dat.medium$Pn.median)), max(c(dat.mut$Pn.median, dat.medium$Pn.median))),
+     ylim = c(min(c(dat.mut$Pn.median, dat.medium$Pn.median)), max(c(dat.mut$Pn.median, dat.medium$Pn.median))))
 abline(0, 1)

### 2017-04-16 analysis-structure.Rmd
paper y dinámica

@@
   geom_line() +
-  geom_text(data = subset(d, dataset == "exp" & mean.z.RSD < -.5), aes(x = site, y = mean.z.RSD, label = site), nudge_y = -.1, size = 1.8)+
+  geom_text(data = subset(d, dataset == "exp" & mean.z.RSD < -.5), aes(x = site, y = mean.z.RSD, label = site), nudge_y = -.1, size = 1.8) +
+  labs(x = "site", y = "<zRSDi>") +
   geom_vline(xintercept = active.sites, show.legend = F) +
@@
 ## experimental
-exp.mean.z.RSD.vec <- vec2resno(as.vector(d.exp$mean.z.RSD), sort(rep(1:ncol(pdb.xyz.ca),3)))
+exp.mean.z.RSD.vec <- vec2resno(as.vector(d.exp$mean.z.RSD), 1:ncol(pdb.xyz.ca))
 write.pdb(xyz = c(pdb.xyz.ca), b = exp.mean.z.RSD.vec, file =  file.path(data.dir, paste(p.ref, "_exp.pdb", sep = "")))
@@
 ## mut
-mut.mean.z.RSD.vec <- vec2resno(as.vector(d.mut$mean.z.RSD), sort(rep(1:ncol(pdb.xyz.ca),3)))
+mut.mean.z.RSD.vec <- vec2resno(as.vector(d.mut$mean.z.RSD), 1:ncol(pdb.xyz.ca))
 write.pdb(xyz = c(pdb.xyz.ca), b = mut.mean.z.RSD.vec, file = file.path(data.dir, paste(p.ref, "_mut.pdb", sep = "")))
@@
 ## mut + sel / medium
-medium.mean.z.RSD.vec <- vec2resno(as.vector(d.medium$mean.z.RSD), sort(rep(1:ncol(pdb.xyz.ca),3)))
+medium.mean.z.RSD.vec <- vec2resno(as.vector(d.medium$mean.z.RSD), 1:ncol(pdb.xyz.ca))
 write.pdb(xyz = c(pdb.xyz.ca), b = medium.mean.z.RSD.vec, file = file.path(data.dir, paste(p.ref, "_medium.pdb", sep = "")))
@@
 
-### sequence comparison
+### Sequence comparison
+
+In this section we compare theoretical sequence profiles with sequence scores obtained from ConsurfDB.
+To obtain theoretical profiles, we calculated the number of times we had mutated each site for each selection regimen.
+
 ```{r sequence-profiles-comparison}
@@
 ```
-### sequence - structure comparison
+
+### Sequence - structure comparison
 

### 2017-04-16 FIGURES/1mcta_exp.py

@@ -1,0 +1,321 @@
+import cPickle, base64
+try:
+	from SimpleSession.versions.v65 import beginRestore,\
+	    registerAfterModelsCB, reportRestoreError, checkVersion
+except ImportError:
+	from chimera import UserError
+	raise UserError('Cannot open session that was saved in a'
+	    ' newer version of Chimera; update your version')
+checkVersion([1, 11, 2, 41376])
+import chimera
+from chimera import replyobj
+replyobj.status('Restoring session...', \
+    blankAfter=0)
+replyobj.status('Beginning session restore...', \
+    blankAfter=0, secondary=True)
+beginRestore()
+
+def restoreCoreModels():
+	from SimpleSession.versions.v65 import init, restoreViewer, \
+	     restoreMolecules, restoreColors, restoreSurfaces, \
+	     restoreVRML, restorePseudoBondGroups, restoreModelAssociations
[…]

### 2017-04-16 FIGURES/1mcta_medium.py

@@ -1,0 +1,279 @@
+import cPickle, base64
+try:
+	from SimpleSession.versions.v65 import beginRestore,\
+	    registerAfterModelsCB, reportRestoreError, checkVersion
+except ImportError:
+	from chimera import UserError
+	raise UserError('Cannot open session that was saved in a'
+	    ' newer version of Chimera; update your version')
+checkVersion([1, 11, 2, 41376])
+import chimera
+from chimera import replyobj
+replyobj.status('Restoring session...', \
+    blankAfter=0)
+replyobj.status('Beginning session restore...', \
+    blankAfter=0, secondary=True)
+beginRestore()
+
+def restoreCoreModels():
+	from SimpleSession.versions.v65 import init, restoreViewer, \
+	     restoreMolecules, restoreColors, restoreSurfaces, \
+	     restoreVRML, restorePseudoBondGroups, restoreModelAssociations
[…]

### 2017-04-16 FIGURES/1mcta_mut.py

@@ -1,0 +1,279 @@
+import cPickle, base64
+try:
+	from SimpleSession.versions.v65 import beginRestore,\
+	    registerAfterModelsCB, reportRestoreError, checkVersion
+except ImportError:
+	from chimera import UserError
+	raise UserError('Cannot open session that was saved in a'
+	    ' newer version of Chimera; update your version')
+checkVersion([1, 11, 2, 41376])
+import chimera
+from chimera import replyobj
+replyobj.status('Restoring session...', \
+    blankAfter=0)
+replyobj.status('Beginning session restore...', \
+    blankAfter=0, secondary=True)
+beginRestore()
+
+def restoreCoreModels():
+	from SimpleSession.versions.v65 import init, restoreViewer, \
+	     restoreMolecules, restoreColors, restoreSurfaces, \
+	     restoreVRML, restorePseudoBondGroups, restoreModelAssociations
[…]

### 2017-04-23 analysis-dynamical-MSF-structure.Rmd
bibliografíapaper, varios r0 y dinámica

@@
 ```
-
-```{r load_packages}
+```{r load-packages}
 # load packages
@@
 
-```{r set_run_variables}
+```{r set-run-variables}
+# general parameters
+tolerance = 1e-10
+
 # set significance factors
@@
 ```
-
-```{r set_reference_protein}
+```{r set-reference-protein}
 # which is the reference protein?
@@
 ```
-
 We studied the `r family` family. 
@@
 cmap.ca = cmap(ref.pdb$xyz[inds$xyz], dcut = R0, scut = 0, mask.lower = F)
+r.p.ref = ref.pdb$xyz[inds$xyz]
 CN = rowSums(cmap.ca, na.rm = T) - 1 # diag(cmap.ca) returned by cmap is 1!
@@
 
-```{r read_site_data}
+```{r read-site-data}
 # read MSF data
@@
 
-# read data
+# read dri2 data
 dri2.exp = read.csv(dri2.exp.fname, header = T)
@@
 
+```{r MSF-p.ref}
+# calculate MSF (Mean Square Fluctuation)
+
+## calculate ENM
+ENMK.p.ref = CalculateENMKeff(matrix(r.p.ref, nrow = 3), 
+                              seq(1:n.sites), 
+                              c(), 
+                              R0, 
+                              tolerance, 
+                              K.analysis)
+## get cov matrix
+cov.p.ref = ENMK.p.ref$cov
+
+## get the diagonal of the cov matrix
+diag.p.ref = diag(cov.p.ref)
+
+## calculate the factor to split the diagonal
+factor = sort(rep(seq(1:n.sites), 3))
+
+## split the diagonal
+s.diag.p.ref = split(diag.p.ref, factor)
+
+## create a matrix to save the data
+MSF.p.ref = matrix(nrow = 1, ncol = n.sites)
+
+## start a loop to calculate sums for each site
+for (i in (1:n.sites)) {
+  MSF.p.ref[, i] = sum(unlist(s.diag.p.ref[i]), use.names = F)
+}
+
+```
+
 ```{r prepare-site-data-MSF}
-
 # prepare the data
@@
 ```{r prepare-site-data-dri2}
-
 # prepare the data
@@
                 mean.r.SDF = mean(x$r.SDF, na.rm = T)
-                ndata = sum(!is.na(x$r.SDF))
-                se.r.SDF = sd(x$r.SDF, na.rm = T) / sqrt(ndata)
-                data.frame(mean.r.SDF, ndata, se.r.SDF)
+                n.data = sum(!is.na(x$r.SDF))
+                se.r.SDF = sd(x$r.SDF, na.rm = T) / sqrt(n.data)
+                data.frame(mean.r.SDF, n.data, se.r.SDF)
 })
@@
      y = mean.r.square.dif.MSF.mut, 
-     xlab = "exp.mean.r.square.dif.MSF", 
-     ylab = "no.selection.mean.r.square.dif.MSF")
+     xlab = "<r.square.dif.MSF> experimental", 
+     ylab = "<r.square.dif.MSF> no-selection")
 abline(0, 1)
@@
      y = mean.r.square.dif.MSF.medium, 
-     xlab = "exp.mean.r.square.dif.MSF", 
-     ylab = "selection.mean.r.square.dif.MSF")
+     xlab = "<r.square.dif.MSF> experimental", 
+     ylab = "<r.square.dif.MSF> selection")
 abline(0, 1)
@@
      y = mean.r.square.dif.MSF.medium, 
-     xlab = "no.selection.mean.r.square.dif.MSF", 
-     ylab = "selection.mean.r.square.dif.MSF")
+     xlab = "<r.square.dif.MSF> no-selection", 
+     ylab = "<r.square.dif.MSF> selection")
 abline(0, 1)
@@
 
+```{r comparison-with-MSF.p.ref}
+
+# rank MSF.p.ref
+r.MSF.p.ref = rank(MSF.p.ref)
+
+# calculate correlations
+r.exp = cor(mean.r.square.dif.MSF.exp, r.MSF.p.ref)
+r.mut = cor(mean.r.square.dif.MSF.mut, r.MSF.p.ref)
+r.medium = cor(mean.r.square.dif.MSF.medium, r.MSF.p.ref)
+
+cor.df = data.frame("comparison" = c("<r.square.dif.MSF> experimental vs r.MSF.p.ref", "<r.square.dif.MSF> no-selection vs r.MSF.p.ref", "<r.square.dif.MSF> selection vs r.MSF.p.ref"),
+                    "R" = c(r.exp, r.mut, r.medium))
+
+knitr::kable(cor.df, digits = 2)
+
+# plot comparative profiles 
+par(pty = "s")
+
+plot(x = mean.r.square.dif.MSF.exp, 
+     y = r.MSF.p.ref, 
+     xlab = "<r.square.dif.MSF> experimental", 
+     ylab = "r.MSF.p.ref")
+abline(0, 1)
+
+plot(x = mean.r.square.dif.MSF.mut, 
+     y = r.MSF.p.ref, 
+     xlab = "<r.square.dif.MSF> no-selection", 
+     ylab = "r.MSF.p.ref")
+abline(0, 1)
+
+plot(x = mean.r.square.dif.MSF.medium, 
+     y = r.MSF.p.ref, 
+     xlab = "<r.square.dif.MSF> selection", 
+     ylab = "r.MSF.p.ref")
+abline(0, 1)
+```
 ```{r mean-z.RSD-profiles}
@@
                 mean.z.RSD = mean(x$z.RSD, na.rm = T)
-                ndata = sum(!is.na(x$z.RSD))
-                se.z.RSD = sd(x$z.RSD, na.rm = T) / sqrt(ndata)
-                data.frame(mean.z.RSD, ndata, se.z.RSD)
+                n.data = sum(!is.na(x$z.RSD))
+                se.z.RSD = sd(x$z.RSD, na.rm = T) / sqrt(n.data)
+                data.frame(mean.z.RSD, n.data, se.z.RSD)
 })
@@
      y = mean.r.dri2.exp, 
-     xlab = "exp.mean.r.square.dif.MSF", 
-     ylab = "exp.mean.r.dri2")
+     xlab = "r<r.square.dif.MSF> experimental", 
+     ylab = "r<dri2> experimental")
+abline(0, 1)
+
+plot(x = mean.r.square.dif.MSF.mut, 
+     y = mean.r.dri2.mut, 
+     xlab = "r<r.square.dif.MSF> no-selection", 
+     ylab = "r<dri2> no-selection")
 abline(0, 1)
@@
      y = mean.r.dri2.medium, 
-     xlab = "selection.mean.r.square.dif.MSF", 
-     ylab = "selection.mean.r.dri2")
-abline(0, 1)
-
-plot(x = mean.r.square.dif.MSF.mut, 
-     y = mean.r.dri2.mut, 
-     xlab = "no.selection.mean.r.square.dif.MSF", 
-     ylab = "no.selection.mean.r.dri2")
+     xlab = "r<r.square.dif.MSF> selection", 
+     ylab = "r<dri2> selection")
 abline(0, 1)

### 2017-04-23 analysis-dynamical-nH.Rmd
bibliografíapaper, varios r0 y dinámica

@@
 ---
-title: "Structural Divergence Analysis"
+title: "Dynamical Divergence Analysis"
 author: "Maria Laura Marcos, Julian Echave"
@@
 
-```{r set_my_colors}
-# set my colors
-myColors = c("blue", "darkgreen", "red", "red") 
-names(myColors) <- c("exp", "mut", "medium", "mut+sel")
-```
-
-```{r set_run_variables}
-# set significance factors
-f95 = 1.96
-f99 = 2.6
-f999 = 3.3
-```
-
-```{r set_file_names}
+```{r set-filenames}
 # set input filenames
@@
 nH.mut.fname = file.path(data.dir,paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.nH.csv", sep = ""))
-
 ```
@@
 ```
-
-```{r prepare_mode_data}
+```{r prepare-mode-data}
 # prepare the data
@@
 ```
-
 ### Dynamical divergence along normal modes
 
-In this section we consider dynamical divergence using normal modes coordinates. We calculated mean nH and we z-normalized profiles.
+In this section we consider dynamical divergence using normal modes coordinates. We calculated <nH> and we z-normalized profiles.
 
@@
 # scale profiles
-mean.nH.exp = scale(mean.nH.exp[which(!is.na(mean.nH.exp))])
-mean.nH.mut = scale(mean.nH.mut[which(!is.na(mean.nH.mut))])
-mean.nH.medium = scale(mean.nH.medium[which(!is.na(mean.nH.medium))])
+mean.nH.exp = vscale(mean.nH.exp[which(!is.na(mean.nH.exp))])
+mean.nH.mut = vscale(mean.nH.mut[which(!is.na(mean.nH.mut))])
+mean.nH.medium = vscale(mean.nH.medium[which(!is.na(mean.nH.medium))])
 
-plot(mean.nH.exp, ylab = "<nH>", xlab = "mode", col = "blue")
+plot(mean.nH.exp, ylab = "<z.nH>", xlab = "mode", col = "blue")
 points(mean.nH.mut, col = "green")
@@
 
-```{r vs-mean-profiles}
+```{r vs-mean-plots}
 
-# plot exp vs simulated profiles 
+# plot comparative profiles 
 par(pty = "s")
@@
      y = mean.nH.mut, 
-     xlab = "exp.mean.nH", 
-     ylab = "no.selection.mean.nH")
+     xlab = "<z.nH> experimental", 
+     ylab = "<z.nH> no-selection")
 abline(0, 1)
@@
      y = mean.nH.medium, 
-     xlab = "exp.mean.nH", 
-     ylab = "selection.mean.nH")
+     xlab = "<z.nH> experimental", 
+     ylab = "<z.nH> selection")
 abline(0, 1)
@@
      y = mean.nH.medium, 
-     xlab = "no.selection.mean.nH", 
-     ylab = "selection.mean.nH")
+     xlab = "<z.nH> no-selection", 
+     ylab = "<z.nH> selection")
 abline(0, 1)
@@
 # get first 100 modes and re-scale
-mean.nH.exp = scale(mean.nH.exp[1:100])
-mean.nH.mut = scale(mean.nH.mut[1:100])
-mean.nH.medium = scale(mean.nH.medium[1:100])
+mean.nH.exp = vscale(mean.nH.exp[1:100])
+mean.nH.mut = vscale(mean.nH.mut[1:100])
+mean.nH.medium = vscale(mean.nH.medium[1:100])
 
-plot(mean.nH.exp, ylab = "<nH>", xlab = "mode", col = "blue")
+plot(mean.nH.exp, ylab = "<z.nH>", xlab = "mode", col = "blue")
 points(mean.nH.mut, col = "green")
@@
 knitr::kable(cor.df, digits = 2)
+```
 
-# plot exp vs simulated profiles 
-par(pty = "s")
+```{r vs-mean-plots-100-modes}
 
+# plot comparative profiles 
 plot(x = mean.nH.exp, 
      y = mean.nH.mut, 
-     xlab = "exp.mean.nH", 
-     ylab = "no.selection.mean.nH")
+     xlab = "<z.nH> experimental", 
+     ylab = "<z.nH> no-selection")
 abline(0, 1)
@@
      y = mean.nH.medium, 
-     xlab = "no.selection.mean.nH", 
-     ylab = "selection.mean.nH")
+     xlab = "<z.nH> no-selection", 
+     ylab = "<z.nH> selection")
 abline(0, 1)
 ```
+```{r comparison-of-means-20-modes}
+
+# get first 100 modes and re-scale
+mean.nH.exp = vscale(mean.nH.exp[1:20])
+mean.nH.mut = vscale(mean.nH.mut[1:20])
+mean.nH.medium = vscale(mean.nH.medium[1:20])
+
+plot(mean.nH.exp, ylab = "<z.nH>", xlab = "mode", col = "blue")
+points(mean.nH.mut, col = "green")
+points(mean.nH.medium, col = "red")
+
+r.exp.mut = cor(mean.nH.exp, mean.nH.mut)
+r.exp.medium = cor(mean.nH.exp, mean.nH.medium)
+r.mut.medium = cor(mean.nH.mut, mean.nH.medium)
+
+cor.df = data.frame("comparison" = c("exp vs no-selection", "exp vs selection", "no-selection vs selection"),
+                    "R" = c(r.exp.mut, r.exp.medium, r.mut.medium))
+knitr::kable(cor.df, digits = 2)
+```
+
+```{r vs-mean-plots-20-modes}
+
+# plot comparative profiles 
+plot(x = mean.nH.exp, 
+     y = mean.nH.mut, 
+     xlab = "<z.nH> experimental", 
+     ylab = "<z.nH> no-selection")
+abline(0, 1)
+
+plot(x = mean.nH.exp, 
+     y = mean.nH.medium, 
+     xlab = "<z.nH> experimental", 
+     ylab = "<z.nH> selection")
+abline(0, 1)
+
+plot(x = mean.nH.mut, 
+     y = mean.nH.medium, 
+     xlab = "<z.nH> no-selection", 
+     ylab = "<z.nH> selection")
+abline(0, 1)
+```

### 2017-04-23 analysis-dynamical-nR.Rmd
bibliografíapaper, varios r0 y dinámica

@@
 nR.mut.fname = file.path(data.dir,paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.nR.csv", sep = ""))
-
 ```
@@
 ```
-
 ### Dynamical divergence along normal modes
 
-In this section we consider dynamical divergence using normal modes coordinates. We calculated mean nR and we z-normalized profiles.
+In this section we consider dynamical divergence using normal modes coordinates. We calculated <nR> and we z-normalized profiles.
 
@@
 # scale profiles
-mean.nR.exp = scale(mean.nR.exp[which(!is.na(mean.nR.exp))])
-mean.nR.mut = scale(mean.nR.mut[which(!is.na(mean.nR.mut))])
-mean.nR.medium = scale(mean.nR.medium[which(!is.na(mean.nR.medium))])
+mean.nR.exp = vscale(mean.nR.exp[which(!is.na(mean.nR.exp))])
+mean.nR.mut = vscale(mean.nR.mut[which(!is.na(mean.nR.mut))])
+mean.nR.medium = vscale(mean.nR.medium[which(!is.na(mean.nR.medium))])
 
-plot(mean.nR.exp, ylab = "<nR>", xlab = "mode", col = "blue")
+plot(mean.nR.exp, ylab = "<z.nR>", xlab = "mode", col = "blue")
 points(mean.nR.mut, col = "green")
@@
      y = mean.nR.mut, 
-     xlab = "exp.mean.nR", 
-     ylab = "no.selection.mean.nR")
+     xlab = "<z.nR> experimental", 
+     ylab = "<z.nR> no-selection")
 abline(0, 1)
@@
      y = mean.nR.medium, 
-     xlab = "exp.mean.nR", 
-     ylab = "selection.mean.nR")
+     xlab = "<z.nR> experimental", 
+     ylab = "<z.nR> selection")
 abline(0, 1)
@@
      y = mean.nR.medium, 
-     xlab = "no.selection.mean.nR", 
-     ylab = "selection.mean.nR")
+     xlab = "<z.nR> no-selection", 
+     ylab = "<z.nR> selection")
 abline(0, 1)
@@
 # get first 100 modes and re-scale
-mean.nR.exp = scale(mean.nR.exp[1:100])
-mean.nR.mut = scale(mean.nR.mut[1:100])
-mean.nR.medium = scale(mean.nR.medium[1:100])
+mean.nR.exp = vscale(mean.nR.exp[1:100])
+mean.nR.mut = vscale(mean.nR.mut[1:100])
+mean.nR.medium = vscale(mean.nR.medium[1:100])
 
-plot(mean.nR.exp, ylab = "<nR>", xlab = "mode", col = "blue")
+plot(mean.nR.exp, ylab = "<z.nR>", xlab = "mode", col = "blue")
 points(mean.nR.mut, col = "green")
@@
 knitr::kable(cor.df, digits = 2)
+```
 
-# plot exp vs simulated profiles 
-par(pty = "s")
+```{r vs-mean-plots-100-modes}
 
+# plot comparative profiles 
 plot(x = mean.nR.exp, 
      y = mean.nR.mut, 
-     xlab = "exp.mean.nR", 
-     ylab = "no.selection.mean.nR")
+     xlab = "<z.nR> experimental", 
+     ylab = "<z.nR> no-selection")
 abline(0, 1)
@@
      y = mean.nR.medium, 
-     xlab = "no.selection.mean.nR", 
-     ylab = "selection.mean.nR")
+     xlab = "<z.nR> no-selection", 
+     ylab = "<z.nR> selection")
 abline(0, 1)
 ```
+```{r comparison-of-means-20-modes}
+
+# get first 100 modes and re-scale
+mean.nR.exp = vscale(mean.nR.exp[1:20])
+mean.nR.mut = vscale(mean.nR.mut[1:20])
+mean.nR.medium = vscale(mean.nR.medium[1:20])
+
+plot(mean.nR.exp, ylab = "<z.nR>", xlab = "mode", col = "blue")
+points(mean.nR.mut, col = "green")
+points(mean.nR.medium, col = "red")
+
+r.exp.mut = cor(mean.nR.exp, mean.nR.mut)
+r.exp.medium = cor(mean.nR.exp, mean.nR.medium)
+r.mut.medium = cor(mean.nR.mut, mean.nR.medium)
+
+cor.df = data.frame("comparison" = c("exp vs no-selection", "exp vs selection", "no-selection vs selection"),
+                    "R" = c(r.exp.mut, r.exp.medium, r.mut.medium))
+knitr::kable(cor.df, digits = 2)
+```
+
+```{r vs-mean-plots-20-modes}
+
+# plot comparative profiles 
+plot(x = mean.nR.exp, 
+     y = mean.nR.mut, 
+     xlab = "<z.nR> experimental", 
+     ylab = "<z.nR> no-selection")
+abline(0, 1)
+
+plot(x = mean.nR.exp, 
+     y = mean.nR.medium, 
+     xlab = "<z.nR> experimental", 
+     ylab = "<z.nR> selection")
+abline(0, 1)
+
+plot(x = mean.nR.mut, 
+     y = mean.nR.medium, 
+     xlab = "<z.nR> no-selection", 
+     ylab = "<z.nR> selection")
+abline(0, 1)
+```

### 2017-04-23 analysis-structure-core.Rmd
bibliografíapaper, varios r0 y dinámica

--- 2017-02-20 analysis-structure-core.Rmd
@@
 dri2.exp.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.exp.norm.dr.squarei.csv", sep = ""))
-dri2.strong.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_strong.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
+dri2.medium.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_medium.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
 dri2.mut.fname = file.path(data.dir,paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
+
+## consurf
+score.fname = file.path(data.dir, paste(p.ref, "_consurf.csv", sep = ""))
+sim.data.mut.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_out_df.data.csv", sep = ""))
+sim.data.medium.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_medium.sel_out_df.data.csv", sep = ""))
 ```
@@
 
-## strong
-dri2.strong = read.csv(dri2.strong.fname, header = T)[, indexes.core]
-rownames(dri2.strong) = paste("strong", rownames(dri2.strong), sep = "")
+## medium
+dri2.medium = read.csv(dri2.medium.fname, header = T)[, indexes.core]
+rownames(dri2.medium) = paste("medium", rownames(dri2.medium), sep = "")
 ```
@@
 dat = siteComparison.all.datasets
-dat$dataset = revalue(dat$dataset, c("strong" = "mut+sel"))
+dat$dataset = revalue(dat$dataset, c("mut" = "no-selection"))
+dat$dataset = revalue(dat$dataset, c("medium" = "selection"))
 
@@
     geom_vline(xintercept = contacts.active.sites, col = "grey", show.legend = F) +
-    labs(x = "site", y = "structural divergence(mean z.RSD)") +
+    labs(x = "site", y = "structural divergence(<z.RSD>)") +
     coord_cartesian(ylim = c(-1.5, 2.8)) +
@@
 p.facet %+% subset(d, dataset == "exp") 
-p.facet %+% subset(d, dataset == "mut")
-p.facet %+% subset(d, dataset == "mut+sel") 
+p.facet %+% subset(d, dataset == "no-selection")
+p.facet %+% subset(d, dataset == "selection") 
 p.facet
@@
 d.exp = subset(d, dataset == "exp")
-d.mut = subset(d, dataset == "mut")
-d.strong = subset(d, dataset == "mut+sel")
+d.mut = subset(d, dataset == "no-selection")
+d.medium = subset(d, dataset == "selection")
 
@@
 r.exp.mut = cor(d.exp$mean.z.RSD, d.mut$mean.z.RSD)
-r.exp.strong = cor(d.exp$mean.z.RSD, d.strong$mean.z.RSD)
-r.mut.strong = cor(d.mut$mean.z.RSD, d.strong$mean.z.RSD)
+r.exp.medium = cor(d.exp$mean.z.RSD, d.medium$mean.z.RSD)
+r.mut.medium = cor(d.mut$mean.z.RSD, d.medium$mean.z.RSD)
 
-cor.df = data.frame("comparison" = c("exp vs mut", "exp vs strong", "mut vs strong"),
-                    "R" = c(r.exp.mut, r.exp.strong, r.mut.strong))
+cor.df = data.frame("comparison" = c("exp vs no-selection", "exp vs selection", "no-selection vs selection"),
+                    "R" = c(r.exp.mut, r.exp.medium, r.mut.medium))
 
 knitr::kable(cor.df, digits = 2, caption = "Correlation between <Z-scores> profiles")
+```
+
+### Comparison between profiles
+
+```{r comparisons-between-profiles}
 
@@
      y = d.mut$mean.z.RSD, 
-     xlab = "exp.mean.z.RSD", 
-     ylab = "mut.mean.z.RSD", 
+     xlab = "<z.RSD> experimental", 
+     ylab = "<z.RSD> no-selection", 
      xlim = c(min(c(d.exp$mean.z.RSD, d.mut$mean.z.RSD)), max(c(d.exp$mean.z.RSD, d.mut$mean.z.RSD))),
@@
 plot(x = d.exp$mean.z.RSD, 
-     y = d.strong$mean.z.RSD, 
-     xlab = "exp.mean.z.RSD", 
-     ylab = "strong.mean.z.RSD", 
-     xlim = c(min(c(d.exp$mean.z.RSD, d.strong$mean.z.RSD)), max(c(d.exp$mean.z.RSD, d.strong$mean.z.RSD))),
-     ylim = c(min(c(d.exp$mean.z.RSD, d.strong$mean.z.RSD)), max(c(d.exp$mean.z.RSD, d.strong$mean.z.RSD))))
-points(x = as.numeric(d.exp$mean.z.RSD)[contacts.active.sites], y = as.numeric(d.strong$mean.z.RSD)[contacts.active.sites], col = "green")
-points(x = as.numeric(d.exp$mean.z.RSD)[active.sites], y = as.numeric(d.strong$mean.z.RSD)[active.sites], col = "yellow")
+     y = d.medium$mean.z.RSD, 
+     xlab = "<z.RSD> experimental", 
+     ylab = "<z.RSD> selection", 
+     xlim = c(min(c(d.exp$mean.z.RSD, d.medium$mean.z.RSD)), max(c(d.exp$mean.z.RSD, d.medium$mean.z.RSD))),
+     ylim = c(min(c(d.exp$mean.z.RSD, d.medium$mean.z.RSD)), max(c(d.exp$mean.z.RSD, d.medium$mean.z.RSD))))
+points(x = as.numeric(d.exp$mean.z.RSD)[contacts.active.sites], y = as.numeric(d.medium$mean.z.RSD)[contacts.active.sites], col = "green")
+points(x = as.numeric(d.exp$mean.z.RSD)[active.sites], y = as.numeric(d.medium$mean.z.RSD)[active.sites], col = "yellow")
 abline(0, 1)
@@
 plot(x = d.mut$mean.z.RSD, 
-     y = d.strong$mean.z.RSD, 
-     xlab = "mut.mean.z.RSD", 
-     ylab = "strong.mean.z.RSD", 
-     xlim = c(min(c(d.mut$mean.z.RSD, d.strong$mean.z.RSD)), max(c(d.mut$mean.z.RSD, d.strong$mean.z.RSD))),
-     ylim = c(min(c(d.mut$mean.z.RSD, d.strong$mean.z.RSD)), max(c(d.mut$mean.z.RSD, d.strong$mean.z.RSD))))
-points(x = as.numeric(d.mut$mean.z.RSD)[contacts.active.sites], y = as.numeric(d.strong$mean.z.RSD)[contacts.active.sites], col = "green")
-points(x = as.numeric(d.mut$mean.z.RSD)[active.sites], y = as.numeric(d.strong$mean.z.RSD)[active.sites], col = "yellow")
+     y = d.medium$mean.z.RSD, 
+     xlab = "<z.RSD> no-selection", 
+     ylab = "<z.RSD> selection", 
+     xlim = c(min(c(d.mut$mean.z.RSD, d.medium$mean.z.RSD)), max(c(d.mut$mean.z.RSD, d.medium$mean.z.RSD))),
+     ylim = c(min(c(d.mut$mean.z.RSD, d.medium$mean.z.RSD)), max(c(d.mut$mean.z.RSD, d.medium$mean.z.RSD))))
+points(x = as.numeric(d.mut$mean.z.RSD)[contacts.active.sites], y = as.numeric(d.medium$mean.z.RSD)[contacts.active.sites], col = "green")
+points(x = as.numeric(d.mut$mean.z.RSD)[active.sites], y = as.numeric(d.medium$mean.z.RSD)[active.sites], col = "yellow")
 abline(0, 1)
@@
 # comparison of means.z.scores with the minimum distance to the functional sites
-plot(y = d.exp$mean.z.RSD - d.mut$mean.z.RSD, x = m.min.da.CM.CA$min.da.CA[indexes.core], xlab = "minimal distance to active site (between CAs)", ylab = "exp.mean.z.RSD - mut.mean.z.RSD")
-plot(y = d.exp$mean.z.RSD - d.mut$mean.z.RSD, x = m.min.da.CM.CA$min.da.CM[indexes.core], xlab = "minimal distance to active site (between CMs)", ylab = "exp.mean.z.RSD - mut.mean.z.RSD")
+plot(y = (d.exp$mean.z.RSD - d.mut$mean.z.RSD)[-active.sites], x = m.min.da.CM.CA$min.da.CA[indexes.core][-active.sites], xlab = "minimal distance to active site (between CAs)", ylab = "<z.RSD> experimental - <z.RSD> no-selection")
+plot(y = (d.exp$mean.z.RSD - d.mut$mean.z.RSD)[-active.sites], x = m.min.da.CM.CA$min.da.CM[indexes.core][-active.sites], xlab = "minimal distance to active site (between CMs)", ylab = "<z.RSD> experimental - <z.RSD> no-selection")
 
 ## calculate correlations between profiles
-r.min.da.CA = cor((d.exp$mean.z.RSD - d.mut$mean.z.RSD), m.min.da.CM.CA$min.da.CA[indexes.core])
-r.min.da.CM = cor((d.exp$mean.z.RSD - d.mut$mean.z.RSD), m.min.da.CM.CA$min.da.CM[indexes.core])
+r.min.da.CA = cor((d.exp$mean.z.RSD - d.mut$mean.z.RSD)[-active.sites], m.min.da.CM.CA$min.da.CA[indexes.core][-active.sites])
+r.min.da.CM = cor((d.exp$mean.z.RSD - d.mut$mean.z.RSD)[-active.sites], m.min.da.CM.CA$min.da.CM[indexes.core][-active.sites])
 
-cor.df = data.frame("comparison" = c("(exp - mut) vs min.da.CA", "(exp - mut) vs min.da.CM"), "R" = c(r.min.da.CA, r.min.da.CM))
+cor.df = data.frame("comparison" = c("(<z.RSD> experimental - <z.RSD> no-selection) vs min.da.CA", "(<z.RSD> experimental - <z.RSD> no-selection) vs min.da.CM"), "R" = c(r.min.da.CA, r.min.da.CM))
+
+knitr::kable(cor.df, digits = 2, caption = "Correlation between differences in <Z-scores> profiles and the minimal distance to the active site")
+
+# comparison of means.z.scores with the minimum distance to the functional sites
+plot(y = (d.exp$mean.z.RSD - d.medium$mean.z.RSD)[-active.sites], x = m.min.da.CM.CA$min.da.CA[indexes.core][-active.sites], xlab = "minimal distance to active site (between CAs)", ylab = "<z.RSD> experimental - <z.RSD> selection")
+plot(y = (d.exp$mean.z.RSD - d.medium$mean.z.RSD)[-active.sites], x = m.min.da.CM.CA$min.da.CM[indexes.core][-active.sites], xlab = "minimal distance to active site (between CMs)", ylab = "<z.RSD> experimental - <z.RSD> selection")
+
+## calculate correlations between profiles
+r.min.da.CA = cor((d.exp$mean.z.RSD - d.medium$mean.z.RSD)[-active.sites], m.min.da.CM.CA$min.da.CA[indexes.core][-active.sites])
+r.min.da.CM = cor((d.exp$mean.z.RSD - d.medium$mean.z.RSD)[-active.sites], m.min.da.CM.CA$min.da.CM[indexes.core][-active.sites])
+
+cor.df = data.frame("comparison" = c("(<z.RSD> experimental - <z.RSD> selection) vs min.da.CA", "(<z.RSD> experimental - <z.RSD> selection) vs min.da.CM"), "R" = c(r.min.da.CA, r.min.da.CM))
 
@@
 ```
+
+```{r comparison-sum.inv.da}
+
+# comparison of means.z.scores with the sum.inv distance to the functional sites
+plot(y = (d.exp$mean.z.RSD - d.mut$mean.z.RSD)[-active.sites], x = m.sum.inv.da.CM.CA$sum.inv.da.CA[indexes.core][-active.sites], xlab = "sum.inv distance to active site (between CAs)", ylab = "<z.RSD> experimental - <z.RSD> no-selection")
+plot(y = (d.exp$mean.z.RSD - d.mut$mean.z.RSD)[-active.sites], x = m.sum.inv.da.CM.CA$sum.inv.da.CM[indexes.core][-active.sites], xlab = "sum.inv distance to active site (between CMs)", ylab = "<z.RSD> experimental - <z.RSD> no-selection")
+
+## calculate correlations between profiles
+r.sum.inv.da.CA = cor((d.exp$mean.z.RSD - d.mut$mean.z.RSD)[-active.sites], m.sum.inv.da.CM.CA$sum.inv.da.CA[indexes.core][-active.sites])
+r.sum.inv.da.CM = cor((d.exp$mean.z.RSD - d.mut$mean.z.RSD)[-active.sites], m.sum.inv.da.CM.CA$sum.inv.da.CM[indexes.core][-active.sites])
+
+cor.df = data.frame("comparison" = c("(<z.RSD> experimental - <z.RSD> no-selection) vs sum.inv.da.CA", "(<z.RSD> experimental - <z.RSD> no-selection) vs sum.inv.da.CM"), "R" = c(r.sum.inv.da.CA, r.sum.inv.da.CM))
+
+knitr::kable(cor.df, digits = 2, caption = "Correlation between differences in <Z-scores> profiles and the sum.inv distance to the active site")
+
+# comparison of means.z.scores with the sum.inv distance to the functional sites
+plot(y = (d.exp$mean.z.RSD - d.medium$mean.z.RSD)[-active.sites], x = m.sum.inv.da.CM.CA$sum.inv.da.CA[indexes.core][-active.sites], xlab = "sum.inv distance to active site (between CAs)", ylab = "<z.RSD> experimental - <z.RSD> selection")
+plot(y = (d.exp$mean.z.RSD - d.medium$mean.z.RSD)[-active.sites], x = m.sum.inv.da.CM.CA$sum.inv.da.CM[indexes.core][-active.sites], xlab = "sum.inv distance to active site (between CMs)", ylab = "<z.RSD> experimental - <z.RSD> selection")
+
+## calculate correlations between profiles
+r.sum.inv.da.CA = cor((d.exp$mean.z.RSD - d.medium$mean.z.RSD)[-active.sites], m.sum.inv.da.CM.CA$sum.inv.da.CA[indexes.core][-active.sites])
+r.sum.inv.da.CM = cor((d.exp$mean.z.RSD - d.medium$mean.z.RSD)[-active.sites], m.sum.inv.da.CM.CA$sum.inv.da.CM[indexes.core][-active.sites])
+
+cor.df = data.frame("comparison" = c("(<z.RSD> experimental - <z.RSD> selection) vs sum.inv.da.CA", "(<z.RSD> experimental - <z.RSD> selection) vs sum.inv.da.CM"), "R" = c(r.sum.inv.da.CA, r.sum.inv.da.CM))
+
+knitr::kable(cor.df, digits = 2, caption = "Correlation between differences in <Z-scores> profiles and the sum.inv distance to the active site")
+```
+
+```{r correlation-da-CN} 
+## CN core
+CN = CN[indexes.core]
+
+## calculate correlations between profiles
+r.min.da.CA.CN = cor(CN[-active.sites], m.min.da.CM.CA$min.da.CA[indexes.core][-active.sites])
+r.min.da.CM.CN = cor(CN[-active.sites], m.min.da.CM.CA$min.da.CM[indexes.core][-active.sites])
+
+cor.df = data.frame("comparison" = c("CN vs min.da.CA", "CN vs min.da.CM"), "R" = c(r.min.da.CA.CN, r.min.da.CM.CN))
+
+knitr::kable(cor.df, digits = 2, caption = "Correlation between CN and the minimal distance to the active site")
+
+## calculate correlations between profiles
+r.sum.inv.da.CA.CN = cor(CN[-active.sites], m.sum.inv.da.CM.CA$sum.inv.da.CA[indexes.core][-active.sites])
+r.sum.inv.da.CM.CN = cor(CN[-active.sites], m.sum.inv.da.CM.CA$sum.inv.da.CM[indexes.core][-active.sites])
+
+cor.df = data.frame("comparison" = c("CN vs sum.inv.da.CA", "CN vs sum.inv.da.CM"), "R" = c(r.sum.inv.da.CA.CN, r.sum.inv.da.CM.CN))
+
+knitr::kable(cor.df, digits = 2, caption = "Correlation between CN and the sum.inv distance to the active site")
+```
+
+### Sequence comparison
+
+In this section we compare theoretical sequence divergence profiles with sequence scores obtained from ConsurfDB.
+To obtain theoretical profiles, for each selection regimen, we calculated the number of times we had mutated each site and divided this number by the number of times we had tried a mutation at the site.
+
+```{r sequence-profiles-comparison}
+# read experimental data obtained from ConsurfDB
+consurf = read.csv(score.fname, sep = ";")
+score = consurf$SCORE[indexes.core]
+
+# read simulated data
+## no sel
+sim.data.mut = read.csv(sim.data.mut.fname)
+mut.site.mut = sim.data.mut$site
+accept.mut = sim.data.mut$accept
+
+## medium sel
+sim.data.medium.sel = read.csv(sim.data.medium.sel.fname)
+mut.site.medium.sel = sim.data.medium.sel$site
+accept.medium.sel = sim.data.medium.sel$accept
+
+# calculate p.accept of simulated data
+p.accept.mut = c()
+p.accept.medium.sel = c()
+
+if (data.dir == "OUT/out_subset_CM_ANM") {
+  mut.site.mut = mut.site.mut - n.sites
+  mut.site.medium.sel = mut.site.medium.sel - n.sites
+}
+
+# core n.sites
+
+for (i in (1:n.sites)) {
+  accept.mut.i = accept.mut[which(mut.site.mut == i)]
+  p.accept.mut.i = mean(accept.mut.i)
+  p.accept.mut[i] = p.accept.mut.i
+
+  accept.medium.sel.i = accept.medium.sel[which(mut.site.medium.sel == i)]
+  p.accept.medium.sel.i = mean(accept.medium.sel.i)
+  p.accept.medium.sel[i] = p.accept.medium.sel.i
+}
+p.accept.mut = p.accept.mut[indexes.core]
+p.accept.medium.sel = p.accept.medium.sel[indexes.core]
+
+# compare exp vs no sel profiles
+## plot
+par(pty = "s")
+
+plot(x = p.accept.mut, y = CN, xlab = "log(paccept no-selection)")
+plot(x = p.accept.mut, y = score, xlab = "log(paccept no-selection)")
+plot(x = score, y = CN)
+
+## calculate corelations
+r.p.accept.mut.CN = cor(log(p.accept.mut), CN)
+r.p.accept.mut.score = cor(log(p.accept.mut), score)
+r.score.CN = cor(score, CN)
+
+cor.df = data.frame("comparison" = c("log(paccept no-selection) vs CN", "log(paccept no-selection) vs score", "score vs CN"),
+                    "R" = c(r.p.accept.mut.CN , r.p.accept.mut.score, r.score.CN))
+
+knitr::kable(cor.df, digits = 2, caption = "Correlation between sequence profiles")
+
+# compare exp vs medium sel profiles
+## plot
+par(pty = "s")
+
+plot(x = log(p.accept.medium.sel), y = CN, xlab = "log(paccept selection)")
+plot(x = log(p.accept.medium.sel), y = score, xlab = "log(paccept selection)")
+plot(x = score, y = CN)
+
+## calculate corelations
+r.p.accept.medium.sel.CN = cor(log(p.accept.medium.sel), CN)
+r.p.accept.medium.sel.score = cor(log(p.accept.medium.sel), score)
+r.score.CN = cor(score, CN)
+
+cor.df = data.frame("comparison" = c("log(paccept selection) vs CN", "log(paccept selection) vs score", "score vs CN"),
+                    "R" = c(r.p.accept.medium.sel.CN , r.p.accept.medium.sel.score, r.score.CN))
+
+knitr::kable(cor.df, digits = 2, caption = "Correlation between sequence profiles")
+
+```

### 2017-04-23 analysis-structure.Rmd
bibliografíapaper, varios r0 y dinámica

@@
 score.fname = file.path(data.dir, paste(p.ref, "_consurf.csv", sep = ""))
-sim.data.no.sel.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_out_df.data.csv", sep = ""))
+sim.data.mut.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_out_df.data.csv", sep = ""))
 sim.data.medium.sel.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_medium.sel_out_df.data.csv", sep = ""))
-
 ```
@@
 ```
-
 In this case we studied the `r family` family. 
@@
 
-```{r comparisons-between-plots}
+```{r comparisons-between-profiles}
 
@@
      y = d.medium$mean.z.RSD, 
-     xlab = "exp.mean.z.RSD", 
-     ylab = "medium.mean.z.RSD", 
+     xlab = "<z.RSD> experimental", 
+     ylab = "<z.RSD> selection", 
      xlim = c(min(c(d.exp$mean.z.RSD, d.medium$mean.z.RSD)), max(c(d.exp$mean.z.RSD, d.medium$mean.z.RSD))),
@@
      y = d.medium$mean.z.RSD, 
-     xlab = "mut.mean.z.RSD", 
-     ylab = "medium.mean.z.RSD", 
+     xlab = "<z.RSD> no-selection", 
+     ylab = "<z.RSD> selection", 
      xlim = c(min(c(d.mut$mean.z.RSD, d.medium$mean.z.RSD)), max(c(d.mut$mean.z.RSD, d.medium$mean.z.RSD))),
@@
 # comparison of means.z.scores with the minimum distance to the functional sites
-plot(y = d.exp$mean.z.RSD - d.mut$mean.z.RSD, x = m.min.da.CM.CA$min.da.CA, xlab = "minimal distance to active site (between CAs)", ylab = "exp.mean.z.RSD - mut.mean.z.RSD")
-plot(y = d.exp$mean.z.RSD - d.mut$mean.z.RSD, x = m.min.da.CM.CA$min.da.CM, xlab = "minimal distance to active site (between CMs)", ylab = "exp.mean.z.RSD - mut.mean.z.RSD")
+plot(y = (d.exp$mean.z.RSD - d.mut$mean.z.RSD)[-active.site.index], x = m.min.da.CM.CA$min.da.CA[-active.site.index], xlab = "minimal distance to active site (between CAs)", ylab = "<z.RSD> experimental - <z.RSD> no-selection")
+plot(y = (d.exp$mean.z.RSD - d.mut$mean.z.RSD)[-active.site.index], x = m.min.da.CM.CA$min.da.CM[-active.site.index], xlab = "minimal distance to active site (between CMs)", ylab = "<z.RSD> experimental - <z.RSD> no-selection")
 
 ## calculate correlations between profiles
-r.min.da.CA = cor((d.exp$mean.z.RSD - d.mut$mean.z.RSD), m.min.da.CM.CA$min.da.CA)
-r.min.da.CM = cor((d.exp$mean.z.RSD - d.mut$mean.z.RSD), m.min.da.CM.CA$min.da.CM)
+r.min.da.CA = cor((d.exp$mean.z.RSD - d.mut$mean.z.RSD)[-active.site.index], m.min.da.CM.CA$min.da.CA[-active.site.index])
+r.min.da.CM = cor((d.exp$mean.z.RSD - d.mut$mean.z.RSD)[-active.site.index], m.min.da.CM.CA$min.da.CM[-active.site.index])
 
-cor.df = data.frame("comparison" = c("(exp - mut) vs min.da.CA", "(exp - mut) vs min.da.CM"), "R" = c(r.min.da.CA, r.min.da.CM))
+cor.df = data.frame("comparison" = c("(exp - no-selection) vs min.da.CA", "(exp - no-selection) vs min.da.CM"), "R" = c(r.min.da.CA, r.min.da.CM))
+
+knitr::kable(cor.df, digits = 2, caption = "Correlation between differences in <Z-scores> profiles and the minimal distance to the active site")
+
+# comparison of means.z.scores with the minimum distance to the functional sites
+plot(y = (d.exp$mean.z.RSD - d.medium$mean.z.RSD)[-active.site.index], x = m.min.da.CM.CA$min.da.CA[-active.site.index], xlab = "minimal distance to active site (between CAs)", ylab = "<z.RSD> experimental - <z.RSD> selection")
+plot(y = (d.exp$mean.z.RSD - d.medium$mean.z.RSD)[-active.site.index], x = m.min.da.CM.CA$min.da.CM[-active.site.index], xlab = "minimal distance to active site (between CMs)", ylab = "<z.RSD> experimental - <z.RSD> selection")
+
+## calculate correlations between profiles
+r.min.da.CA = cor((d.exp$mean.z.RSD - d.medium$mean.z.RSD)[-active.site.index], m.min.da.CM.CA$min.da.CA[-active.site.index])
+r.min.da.CM = cor((d.exp$mean.z.RSD - d.medium$mean.z.RSD)[-active.site.index], m.min.da.CM.CA$min.da.CM[-active.site.index])
+
+cor.df = data.frame("comparison" = c("(exp - selection) vs min.da.CA", "(exp - selection) vs min.da.CM"), "R" = c(r.min.da.CA, r.min.da.CM))
 
@@
 # comparison of means.z.scores with the sum.inv distance to the functional sites
-plot(y = d.exp$mean.z.RSD - d.mut$mean.z.RSD, x = m.sum.inv.da.CM.CA$sum.inv.da.CA, xlab = "sum.inv distance to active site (between CAs)", ylab = "exp.mean.z.RSD - mut.mean.z.RSD")
-plot(y = d.exp$mean.z.RSD - d.mut$mean.z.RSD, x = m.sum.inv.da.CM.CA$sum.inv.da.CM, xlab = "sum.inv distance to active site (between CMs)", ylab = "exp.mean.z.RSD - mut.mean.z.RSD")
+plot(y = (d.exp$mean.z.RSD - d.mut$mean.z.RSD)[-active.site.index], x = m.sum.inv.da.CM.CA$sum.inv.da.CA[-active.site.index], xlab = "sum.inv distance to active site (between CAs)", ylab = "<z.RSD> experimental - <z.RSD> no-selection")
+plot(y = (d.exp$mean.z.RSD - d.mut$mean.z.RSD)[-active.site.index], x = m.sum.inv.da.CM.CA$sum.inv.da.CM[-active.site.index], xlab = "sum.inv distance to active site (between CMs)", ylab = "<z.RSD> experimental - <z.RSD> no-selection")
 
 ## calculate correlations between profiles
-r.sum.inv.da.CA = cor((d.exp$mean.z.RSD - d.mut$mean.z.RSD), m.sum.inv.da.CM.CA$sum.inv.da.CA)
-r.sum.inv.da.CM = cor((d.exp$mean.z.RSD - d.mut$mean.z.RSD), m.sum.inv.da.CM.CA$sum.inv.da.CM)
+r.sum.inv.da.CA = cor((d.exp$mean.z.RSD - d.mut$mean.z.RSD)[-active.site.index], m.sum.inv.da.CM.CA$sum.inv.da.CA[-active.site.index])
+r.sum.inv.da.CM = cor((d.exp$mean.z.RSD - d.mut$mean.z.RSD)[-active.site.index], m.sum.inv.da.CM.CA$sum.inv.da.CM[-active.site.index])
 
-cor.df = data.frame("comparison" = c("(exp - mut) vs sum.inv.da.CA", "(exp - mut) vs sum.inv.da.CM"), "R" = c(r.sum.inv.da.CA, r.sum.inv.da.CM))
+cor.df = data.frame("comparison" = c("(exp - no-selection) vs sum.inv.da.CA", "(exp - no-selection) vs sum.inv.da.CM"), "R" = c(r.sum.inv.da.CA, r.sum.inv.da.CM))
+
+knitr::kable(cor.df, digits = 2, caption = "Correlation between differences in <Z-scores> profiles and the sum.inv distance to the active site")
+
+# comparison of means.z.scores with the sum.inv distance to the functional sites
+plot(y = (d.exp$mean.z.RSD - d.medium$mean.z.RSD)[-active.site.index], x = m.sum.inv.da.CM.CA$sum.inv.da.CA[-active.site.index], xlab = "sum.inv distance to active site (between CAs)", ylab = "<z.RSD> experimental - <z.RSD> selection")
+plot(y = (d.exp$mean.z.RSD - d.medium$mean.z.RSD)[-active.site.index], x = m.sum.inv.da.CM.CA$sum.inv.da.CM[-active.site.index], xlab = "sum.inv distance to active site (between CMs)", ylab = "<z.RSD> experimental - <z.RSD> selection")
+
+## calculate correlations between profiles
+r.sum.inv.da.CA = cor((d.exp$mean.z.RSD - d.medium$mean.z.RSD)[-active.site.index], m.sum.inv.da.CM.CA$sum.inv.da.CA[-active.site.index])
+r.sum.inv.da.CM = cor((d.exp$mean.z.RSD - d.medium$mean.z.RSD)[-active.site.index], m.sum.inv.da.CM.CA$sum.inv.da.CM[-active.site.index])
+
+cor.df = data.frame("comparison" = c("(exp - selection) vs sum.inv.da.CA", "(exp - selection) vs sum.inv.da.CM"), "R" = c(r.sum.inv.da.CA, r.sum.inv.da.CM))
 
@@
 ## calculate correlations between profiles
-r.min.da.CA.CN = cor(CN, m.min.da.CM.CA$min.da.CA)
-r.min.da.CM.CN = cor(CN, m.min.da.CM.CA$min.da.CM)
+r.min.da.CA.CN = cor(CN[-active.site.index], m.min.da.CM.CA$min.da.CA[-active.site.index])
+r.min.da.CM.CN = cor(CN[-active.site.index], m.min.da.CM.CA$min.da.CM[-active.site.index])
 
@@
 ## calculate correlations between profiles
-r.sum.inv.da.CA.CN = cor(CN, m.sum.inv.da.CM.CA$sum.inv.da.CA)
-r.sum.inv.da.CM.CN = cor(CN, m.sum.inv.da.CM.CA$sum.inv.da.CM)
+r.sum.inv.da.CA.CN = cor(CN[-active.site.index], m.sum.inv.da.CM.CA$sum.inv.da.CA[-active.site.index])
+r.sum.inv.da.CM.CN = cor(CN[-active.site.index], m.sum.inv.da.CM.CA$sum.inv.da.CM[-active.site.index])
 
@@
 
-In this section we compare theoretical sequence profiles with sequence scores obtained from ConsurfDB.
-To obtain theoretical profiles, we calculated the number of times we had mutated each site for each selection regimen.
+In this section we compare theoretical sequence divergence profiles with sequence scores obtained from ConsurfDB.
+To obtain theoretical profiles, for each selection regimen, we calculated the number of times we had mutated each site and divided this number by the number of times we had tried a mutation at the site.
 
@@
 ## no sel
-sim.data.no.sel = read.csv(sim.data.no.sel.fname)
-mut.site.no.sel = sim.data.no.sel$site
-p.accept.no.sel = sim.data.no.sel$p.accept
+sim.data.mut = read.csv(sim.data.mut.fname)
+mut.site.mut = sim.data.mut$site
+accept.mut = sim.data.mut$accept
 
@@
 mut.site.medium.sel = sim.data.medium.sel$site
-p.accept.medium.sel = sim.data.medium.sel$p.accept
+accept.medium.sel = sim.data.medium.sel$accept
 
-# calculate mean.p.accept of simulated data
-mean.p.accept.no.sel = c()
-mean.p.accept.medium.sel = c()
+# calculate p.accept of simulated data
+p.accept.mut = c()
+p.accept.medium.sel = c()
 
@@
 if (data.dir == "OUT/out_subset_CM_ANM") {
-  mut.site.no.sel = mut.site.no.sel - n.sites
+  mut.site.mut = mut.site.mut - n.sites
   mut.site.medium.sel = mut.site.medium.sel - n.sites
-  CN.CM = sim.data.no.sel$CN
+  CN.CM = sim.data.mut$CN
   CN = c()
@@
   for (i in (1:n.sites)) {
-    CN[i] = CN.CM[which(mut.site.no.sel == i)][1]
+    CN[i] = CN.CM[which(mut.site.mut == i)][1]
   }
@@
 for (i in (1:n.sites)) {
-  p.accept.no.sel.i = p.accept.no.sel[which(mut.site.no.sel == i)]
-  mean.p.accept.no.sel.i = mean(p.accept.no.sel.i)
-  mean.p.accept.no.sel[i] = mean.p.accept.no.sel.i
+  accept.mut.i = accept.mut[which(mut.site.mut == i)]
+  p.accept.mut.i = mean(accept.mut.i)
+  p.accept.mut[i] = p.accept.mut.i
 
-  p.accept.medium.sel.i = p.accept.medium.sel[which(mut.site.medium.sel == i)]
-  mean.p.accept.medium.sel.i = mean(p.accept.medium.sel.i)
-  mean.p.accept.medium.sel[i] = mean.p.accept.medium.sel.i
+  accept.medium.sel.i = accept.medium.sel[which(mut.site.medium.sel == i)]
+  p.accept.medium.sel.i = mean(accept.medium.sel.i)
+  p.accept.medium.sel[i] = p.accept.medium.sel.i
 }
@@
 
-plot(x = mean.p.accept.no.sel, y = CN)
-plot(x = mean.p.accept.no.sel, y = score)
+plot(x = log(p.accept.mut), y = CN, xlab = "log(paccept no-selection)")
+plot(x = log(p.accept.mut), y = score, xlab = "log(paccept no-selection)")
 plot(x = score, y = CN)
@@
 ## calculate corelations
-r.mean.p.accept.no.sel.CN = cor(mean.p.accept.no.sel, CN)
-r.mean.p.accept.no.sel.score = cor(mean.p.accept.no.sel, score)
+r.p.accept.mut.CN = cor(p.accept.mut, CN)
+r.p.accept.mut.score = cor(p.accept.mut, score)
 r.score.CN = cor(score, CN)
 
-cor.df = data.frame("comparison" = c("p.accept.no.sel vs CN", "p.accept.no.sel vs score", "score vs CN"),
-                    "R" = c(r.mean.p.accept.no.sel.CN , r.mean.p.accept.no.sel.score, r.score.CN))
+cor.df = data.frame("comparison" = c("log(paccept no-selection) vs CN", "log(paccept no-selection) vs score", "score vs CN"),
+                    "R" = c(r.p.accept.mut.CN , r.p.accept.mut.score, r.score.CN))
 
 knitr::kable(cor.df, digits = 2, caption = "Correlation between sequence profiles")
+
+print("<paccept no-selection>")
+print(mean(p.accept.mut))
 
@@
 
-plot(x = log(mean.p.accept.medium.sel), y = CN)
-plot(x = log(mean.p.accept.medium.sel), y = score)
+plot(x = log(p.accept.medium.sel), y = CN, xlab = "log(paccept selection)")
+plot(x = log(p.accept.medium.sel), y = score, xlab = "log(paccept selection)")
 plot(x = score, y = CN)
@@
 ## calculate corelations
-r.mean.p.accept.medium.sel.CN = cor(log(mean.p.accept.medium.sel), CN)
-r.mean.p.accept.medium.sel.score = cor(log(mean.p.accept.medium.sel), score)
+r.p.accept.medium.sel.CN = cor(log(p.accept.medium.sel), CN)
+r.p.accept.medium.sel.score = cor(log(p.accept.medium.sel), score)
 r.score.CN = cor(score, CN)
 
-cor.df = data.frame("comparison" = c("log(p.accept.medium.sel) vs CN", "log(p.accept.medium.sel) vs score", "score vs CN"),
-                    "R" = c(r.mean.p.accept.medium.sel.CN , r.mean.p.accept.medium.sel.score, r.score.CN))
+cor.df = data.frame("comparison" = c("log(paccept selection) vs CN", "log(paccept selection) vs score", "score vs CN"),
+                    "R" = c(r.p.accept.medium.sel.CN , r.p.accept.medium.sel.score, r.score.CN))
 
@@
 
+print("<paccept selection>")
+print(mean(p.accept.medium.sel))
 ```
@@
 
-plot(x = d.exp$mean.z.RSD, y = CN, xlab = "experimental <zRSDi>")
-plot(x = d.mut$mean.z.RSD, y = CN, xlab = "theoretical with no selection <zRSDi>")
-plot(x = d.medium$mean.z.RSD, y = CN, xlab = "theoretical with medium selection <zRSDi>")
+plot(x = d.exp$mean.z.RSD, y = CN, xlab = "<zRSDi> experimental ")
+plot(x = d.mut$mean.z.RSD, y = CN, xlab = "<zRSDi> no-selection")
+plot(x = d.medium$mean.z.RSD, y = CN, xlab = "<zRSDi> selection")
 
-## calculate corelations
+## calculate correlations
 r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, CN)
@@
 
-cor.df = data.frame("comparison" = c("exp.mean.z.RSD vs CN", "mut.mean.z.RSD vs CN", "medium.mean.z.RSD vs CN"),
+cor.df = data.frame("comparison" = c("<z.RSD> experimental vs CN", "<z.RSD> no-selection vs CN", "<z.RSD> selection vs CN"),
                     "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))
 
-knitr::kable(cor.df, digits = 2, caption = "Correlation structure - sequence")
+knitr::kable(cor.df, digits = 2, caption = "Correlation structure (<z.RSD>) - sequence (CN)")
 ```

### 2017-04-27 comparison_CA_CM.Rmd
CA vs CM

---
title: "Structural Divergence Analysis"
author: "Maria Laura Marcos, Julian Echave"
output: html_document
---

```{r setup, include = FALSE}
# set chunk options
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r load-packages}
# load functions
source(file.path(data.dir, "my-functions.R"))

# load packages
library(ggplot2)
library(reshape2)
library(plyr)
library(quantreg)
library(bio3d)
```

### Structure - cartesian coordinates

```{r set-file-names}
data.dir <- paste("OUT/out_subset_CA_ANM", sep = "")
R0 = R0.CA

# set input filenames
## profiles to compare
dri2.exp.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.exp.norm.dr.squarei.csv", sep = ""))
dri2.medium.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_medium.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
dri2.mut.fname = file.path(data.dir,paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))

## consurf
score.fname = file.path(data.dir, paste(p.ref, "_consurf.csv", sep = ""))
CA.sim.data.mut.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_out_df.data.csv", sep = ""))
CA.sim.data.medium.sel.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_medium.sel_out_df.data.csv", sep = ""))

## active sites
functional.sites.fname = file.path("DATA", paste(p.ref, "_functionalSites.csv", sep = ""))

```

```{r read-functional-sites}
# which are the functional sites?
functional.sites = read.csv(functional.sites.fname, sep = ";")
active.site.index = functional.sites$index
```

```{r read-data}
# read data
dri2.exp = read.csv(dri2.exp.fname, header = T)
dri2.mut = read.csv(dri2.mut.fname, header = T)
dri2.medium = read.csv(dri2.medium.fname, header = T)

n.sites = length(dri2.exp)

rownames(dri2.exp) = paste("mut", rownames(dri2.exp), sep = "")
rownames(dri2.mut) = paste("mut", rownames(dri2.mut), sep = "")
rownames(dri2.medium) = paste("mut", rownames(dri2.medium), sep = "")

tdri2.exp = as.data.frame(t(as.matrix(dri2.exp)))
tdri2.mut = as.data.frame(t(as.matrix(dri2.mut)))
tdri2.medium = as.data.frame(t(as.matrix(dri2.medium)))

site.info = seq(1:length(dri2.mut))

tdri2.exp = cbind(site.info, tdri2.exp)
tdri2.mut = cbind(site.info, tdri2.mut)
tdri2.medium = cbind(site.info, tdri2.medium)

siteComparison.exp = melt(tdri2.exp, id.vars = c("site.info"), variable.name = "protein", value.name = "dri2")
siteComparison.mut = melt(tdri2.mut, id.vars = c("site.info"), variable.name = "protein", value.name = "dri2")
siteComparison.medium = melt(tdri2.medium, id.vars = c("site.info"), variable.name = "protein", value.name = "dri2")

# bluild the data.frame
siteComparison.all.datasets = rbind(data.frame("dataset" = "exp", siteComparison.exp),
                                    data.frame("dataset" = "mut", siteComparison.mut),
                                    data.frame("dataset" = "medium", siteComparison.medium))

siteComparison.all.datasets = ddply(siteComparison.all.datasets, c("dataset", "protein"), mutate,
          "n.SD" = dri2/mean(dri2, na.rm = T),
          "z.SD" = vscale(dri2),
          "RSD" = sqrt(dri2),
          "n.RSD" = RSD/mean(RSD, na.rm = T),
          "z.RSD" = vscale(RSD))

dat = siteComparison.all.datasets
dat$dataset = revalue(dat$dataset, c("medium" = "selection"))
dat$dataset = revalue(dat$dataset, c("mut" = "no-selection"))

## dat with means and standard errors
d.CA = ddply(dat,c("dataset", "site.info"), function(x) {
                mean.z.RSD = mean(x$z.RSD, na.rm = T)
                ndata = sum(!is.na(x$z.RSD))
                se.z.RSD = sd(x$z.RSD, na.rm = T) / sqrt(ndata)
                data.frame(mean.z.RSD, ndata, se.z.RSD)
})
```

```{r set-file-names-CM}
data.dir <- paste("OUT/out_subset_CM_ANM", sep = "")
R0 = R0.CM

# set input filenames
## profiles to compare
dri2.exp.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.exp.norm.dr.squarei.csv", sep = ""))
dri2.medium.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_medium.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
dri2.mut.fname = file.path(data.dir,paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))

## consurf
score.fname = file.path(data.dir, paste(p.ref, "_consurf.csv", sep = ""))
CM.sim.data.mut.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_out_df.data.csv", sep = ""))
CM.sim.data.medium.sel.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_medium.sel_out_df.data.csv", sep = ""))
```

```{r read-data-CM}
# read data
dri2.exp = read.csv(dri2.exp.fname, header = T)
dri2.mut = read.csv(dri2.mut.fname, header = T)
dri2.medium = read.csv(dri2.medium.fname, header = T)

rownames(dri2.exp) = paste("mut", rownames(dri2.exp), sep = "")
rownames(dri2.mut) = paste("mut", rownames(dri2.mut), sep = "")
rownames(dri2.medium) = paste("mut", rownames(dri2.medium), sep = "")

tdri2.exp = as.data.frame(t(as.matrix(dri2.exp)))
tdri2.mut = as.data.frame(t(as.matrix(dri2.mut)))
tdri2.medium = as.data.frame(t(as.matrix(dri2.medium)))

site.info = seq(1:length(dri2.mut))

tdri2.exp = cbind(site.info, tdri2.exp)
tdri2.mut = cbind(site.info, tdri2.mut)
tdri2.medium = cbind(site.info, tdri2.medium)

siteComparison.exp = melt(tdri2.exp, id.vars = c("site.info"), variable.name = "protein", value.name = "dri2")
siteComparison.mut = melt(tdri2.mut, id.vars = c("site.info"), variable.name = "protein", value.name = "dri2")
siteComparison.medium = melt(tdri2.medium, id.vars = c("site.info"), variable.name = "protein", value.name = "dri2")

# bluild the data.frame
siteComparison.all.datasets = rbind(data.frame("dataset" = "exp", siteComparison.exp),
                                    data.frame("dataset" = "mut", siteComparison.mut),
                                    data.frame("dataset" = "medium", siteComparison.medium))

siteComparison.all.datasets = ddply(siteComparison.all.datasets, c("dataset", "protein"), mutate,
          "n.SD" = dri2/mean(dri2, na.rm = T),
          "z.SD" = vscale(dri2),
          "RSD" = sqrt(dri2),
          "n.RSD" = RSD/mean(RSD, na.rm = T),
          "z.RSD" = vscale(RSD))

dat = siteComparison.all.datasets
dat$dataset = revalue(dat$dataset, c("medium" = "selection"))
dat$dataset = revalue(dat$dataset, c("mut" = "no-selection"))

## dat with means and standard errors
d.CM = ddply(dat,c("dataset", "site.info"), function(x) {
                mean.z.RSD = mean(x$z.RSD, na.rm = T)
                ndata = sum(!is.na(x$z.RSD))
                se.z.RSD = sd(x$z.RSD, na.rm = T) / sqrt(ndata)
                data.frame(mean.z.RSD, ndata, se.z.RSD)
})
```

```{r comparison-mean-z.RSD-vs-site}
# CA
d = d.CA

# calculate correlations berween profiles
d.exp = subset(d, dataset == "exp")
d.mut = subset(d, dataset == "no-selection")
d.medium = subset(d, dataset == "selection")

# calculate cors
r.exp.mut = cor(d.exp$mean.z.RSD, d.mut$mean.z.RSD)
r.exp.medium = cor(d.exp$mean.z.RSD, d.medium$mean.z.RSD)
r.mut.medium = cor(d.mut$mean.z.RSD, d.medium$mean.z.RSD)

# save data
CA.mean.exp = d.exp$mean.z.RSD
CA.mean.mut = d.mut$mean.z.RSD
CA.mean.medium = d.medium$mean.z.RSD

CA.se.exp = d.exp$se.z.RSD
CA.se.mut = d.mut$se.z.RSD
CA.se.medium = d.medium$se.z.RSD

cor.df = data.frame("comparison CA" = c("exp vs no-selection", "exp vs selection", "no-selection vs selection"),
                    "R" = c(r.exp.mut, r.exp.medium, r.mut.medium))

knitr::kable(cor.df, digits = 2, caption = "Correlation between <Z-scores> profiles")

# CM
d = d.CM

# calculate correlations berween profiles
d.exp = subset(d, dataset == "exp")
d.mut = subset(d, dataset == "no-selection")
d.medium = subset(d, dataset == "selection")

# calculate cors
r.exp.mut = cor(d.exp$mean.z.RSD, d.mut$mean.z.RSD)
r.exp.medium = cor(d.exp$mean.z.RSD, d.medium$mean.z.RSD)
r.mut.medium = cor(d.mut$mean.z.RSD, d.medium$mean.z.RSD)

# save data
CM.mean.exp = d.exp$mean.z.RSD
CM.mean.mut = d.mut$mean.z.RSD
CM.mean.medium = d.medium$mean.z.RSD

CM.se.exp = d.exp$se.z.RSD
CM.se.mut = d.mut$se.z.RSD
CM.se.medium = d.medium$se.z.RSD

cor.df = data.frame("comparison CM" = c("exp vs no-selection", "exp vs selection", "no-selection vs selection"),
                    "R" = c(r.exp.mut, r.exp.medium, r.mut.medium))

knitr::kable(cor.df, digits = 2, caption = "Correlation between <Z-scores> profiles")
```

```{r plots, fig.cap= "yellow = active sites"}
# plot comparative profiles
par(pty = "s")

# exp
plot(x = CA.mean.exp, y = CM.mean.exp, xlab = "CA <z.RSD> experimental", ylab = "CM <z.RSD> experimental")
abline(0, 1)
points(x = CA.mean.exp[active.site.index], y = CM.mean.exp[active.site.index], col = "yellow")

# mut
plot(x = CA.mean.mut, y = CM.mean.mut, xlab = "CA <z.RSD> no-selection", ylab = "CM <z.RSD> no-selection")
abline(0, 1)
points(x = CA.mean.mut[active.site.index], y = CM.mean.mut[active.site.index], col = "yellow")

# medium
plot(x = CA.mean.medium, y = CM.mean.medium, xlab = "CA <z.RSD> selection", ylab = "CM <z.RSD> selection")
abline(0, 1)
points(x = CA.mean.medium[active.site.index], y = CM.mean.medium[active.site.index], col = "yellow")
```

```{r correlations-CA-CM}
# calculate cors
r.exp = cor(CA.mean.exp, CM.mean.exp)
r.mut = cor(CA.mean.mut, CM.mean.mut)
r.medium = cor(CA.mean.medium, CM.mean.medium)

cor.df = data.frame("comparison CM" = c("exp CA vs CM", "no-selection CA vs CM", "selection CA vs CM"),
                    "R" = c(r.exp, r.mut, r.medium))

knitr::kable(cor.df, digits = 2, caption = "Correlation between CA and CM <Z-scores> profiles")
```

```{r sequence-profiles-comparison}
# read experimental data obtained from ConsurfDB
consurf = read.csv(score.fname, sep = ";")
score = consurf$SCORE

# read simulated data
## no sel
CA.sim.data.mut = read.csv(CA.sim.data.mut.fname)
mut.site.mut = CA.sim.data.mut$site
accept.mut = CA.sim.data.mut$accept

## medium sel
CA.sim.data.medium.sel = read.csv(CA.sim.data.medium.sel.fname)
mut.site.medium.sel = CA.sim.data.medium.sel$site
accept.medium.sel = CA.sim.data.medium.sel$accept

# calculate p.accept of simulated data
p.accept.mut = c()
p.accept.medium.sel = c()

# calculate CN
CN.CA = CA.sim.data.mut$CN
CN = c()

for (i in (1:n.sites)) {
  CN[i] = CN.CA[which(mut.site.mut == i)][1]
}

for (i in (1:n.sites)) {
  accept.mut.i = accept.mut[which(mut.site.mut == i)]
  p.accept.mut.i = mean(accept.mut.i)
  p.accept.mut[i] = p.accept.mut.i

  accept.medium.sel.i = accept.medium.sel[which(mut.site.medium.sel == i)]
  p.accept.medium.sel.i = mean(accept.medium.sel.i)
  p.accept.medium.sel[i] = p.accept.medium.sel.i
}

## calculate corelations
r.p.accept.mut.CN = cor(p.accept.mut, CN)
r.p.accept.mut.score = cor(p.accept.mut, score)
r.score.CN = cor(score, CN)

cor.df = data.frame("comparison CA" = c("log(paccept no-selection) vs CN", "log(paccept no-selection) vs score", "score vs CN"),
                    "R" = c(r.p.accept.mut.CN , r.p.accept.mut.score, r.score.CN))

knitr::kable(cor.df, digits = 2, caption = "Correlation between sequence profiles")

print("<paccept no-selection>")
print(mean(p.accept.mut))

## calculate corelations
r.p.accept.medium.sel.CN = cor(log(p.accept.medium.sel), CN)
r.p.accept.medium.sel.score = cor(log(p.accept.medium.sel), score)
r.score.CN = cor(score, CN)

cor.df = data.frame("comparison CA" = c("log(paccept selection) vs CN", "log(paccept selection) vs score", "score vs CN"),
                    "R" = c(r.p.accept.medium.sel.CN , r.p.accept.medium.sel.score, r.score.CN))

knitr::kable(cor.df, digits = 2, caption = "Correlation between sequence profiles")

print("<paccept selection>")
print(mean(p.accept.medium.sel))
```

```{r sequence-profiles-comparison-CM}
# read experimental data obtained from ConsurfDB
consurf = read.csv(score.fname, sep = ";")
score = consurf$SCORE

# read simulated data
## no sel
CM.sim.data.mut = read.csv(CM.sim.data.mut.fname)
mut.site.mut = CM.sim.data.mut$site
accept.mut = CM.sim.data.mut$accept

## medium sel
CM.sim.data.medium.sel = read.csv(CM.sim.data.medium.sel.fname)
mut.site.medium.sel = CM.sim.data.medium.sel$site
accept.medium.sel = CM.sim.data.medium.sel$accept

# calculate p.accept of simulated data
p.accept.mut = c()
p.accept.medium.sel = c()

# correct indexes
mut.site.mut = mut.site.mut - n.sites
mut.site.medium.sel = mut.site.medium.sel - n.sites

# calculate CN
CN.CM = CM.sim.data.mut$CN
CN = c()

for (i in (1:n.sites)) {
  CN[i] = CN.CM[which(mut.site.mut == i)][1]
}

for (i in (1:n.sites)) {
  accept.mut.i = accept.mut[which(mut.site.mut == i)]
  p.accept.mut.i = mean(accept.mut.i)
  p.accept.mut[i] = p.accept.mut.i

  accept.medium.sel.i = accept.medium.sel[which(mut.site.medium.sel == i)]
  p.accept.medium.sel.i = mean(accept.medium.sel.i)
  p.accept.medium.sel[i] = p.accept.medium.sel.i
}

## calculate corelations
r.p.accept.mut.CN = cor(p.accept.mut, CN)
r.p.accept.mut.score = cor(p.accept.mut, score)
r.score.CN = cor(score, CN)

cor.df = data.frame("comparison CM" = c("log(paccept no-selection) vs CN", "log(paccept no-selection) vs score", "score vs CN"),
                    "R" = c(r.p.accept.mut.CN , r.p.accept.mut.score, r.score.CN))

knitr::kable(cor.df, digits = 2, caption = "Correlation between sequence profiles")

print("<paccept no-selection>")
print(mean(p.accept.mut))

## calculate corelations
r.p.accept.medium.sel.CN = cor(log(p.accept.medium.sel), CN)
r.p.accept.medium.sel.score = cor(log(p.accept.medium.sel), score)
r.score.CN = cor(score, CN)

cor.df = data.frame("comparison CM" = c("log(paccept selection) vs CN", "log(paccept selection) vs score", "score vs CN"),
                    "R" = c(r.p.accept.medium.sel.CN , r.p.accept.medium.sel.score, r.score.CN))

knitr::kable(cor.df, digits = 2, caption = "Correlation between sequence profiles")

print("<paccept selection>")
print(mean(p.accept.medium.sel))
```

```{r structure-profiles-CN-comparison}
d = d.CA
# calculate correlations berween profiles
d.exp = subset(d, dataset == "exp")
d.mut = subset(d, dataset == "no-selection")
d.medium = subset(d, dataset == "selection")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, CN)
r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, CN)
r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, CN)

cor.df = data.frame("comparison CA" = c("<z.RSD> experimental vs CN", "<z.RSD> no-selection vs CN", "<z.RSD> selection vs CN"),
                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))

knitr::kable(cor.df, digits = 2, caption = "Correlation structure (<z.RSD>) - sequence (CN)")
```

```{r structure-profiles-CN-comparison-CM}
d = d.CM
# calculate correlations berween profiles
d.exp = subset(d, dataset == "exp")
d.mut = subset(d, dataset == "no-selection")
d.medium = subset(d, dataset == "selection")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, CN)
r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, CN)
r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, CN)

cor.df = data.frame("comparison CM" = c("<z.RSD> experimental vs CN", "<z.RSD> no-selection vs CN", "<z.RSD> selection vs CN"),
                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))

knitr::kable(cor.df, digits = 2, caption = "Correlation structure (<z.RSD>) - sequence (CN)")
```

### Structure - normal modes

```{r set-file-names}
data.dir <- paste("OUT/out_subset_CA_ANM", sep = "")
R0 = R0.CA

# set input filenames
## profiles to compare
Pn.exp.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.exp.Pn.csv", sep = ""))
Pn.medium.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_medium.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
Pn.mut.fname = file.path(data.dir,paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
```

```{r prepare-site-data}
# prepare the data
Pn.exp = read.csv(Pn.exp.fname, header = T)
rownames(Pn.exp) = paste("mut", rownames(Pn.exp), sep = "")

Pn.mut = read.csv(Pn.mut.fname, header = T)
rownames(Pn.mut) = paste("mut", rownames(Pn.mut), sep = "")

Pn.medium = read.csv(Pn.medium.fname, header = T)
rownames(Pn.medium) = paste("medium", rownames(Pn.medium), sep = "")

mode = seq(ncol(Pn.medium))

# Prepare modeComparison.medium
tPn.medium = as.data.frame(t(as.matrix(Pn.medium)))
tPn.medium = cbind(data.frame("mode" = mode), tPn.medium)
modeComparison.medium = melt(tPn.medium, "mode", variable.name = "protein", value.name = "Pn")
modeComparison.medium = ddply(modeComparison.medium, "protein", mutate, "Pn" = Pn / mean(Pn, na.rm = T))

# Prepare modeComparison.mut
tPn.mut = as.data.frame(t(as.matrix(Pn.mut)))
tPn.mut = cbind(data.frame("mode" = mode), tPn.mut)
modeComparison.mut = melt(tPn.mut, "mode", variable.name = "protein", value.name = "Pn")
modeComparison.mut = ddply(modeComparison.mut, "protein", mutate, "Pn" = Pn / mean(Pn, na.rm = T))

# Prepare modeComparison.exp
tPn.exp = as.data.frame(t(as.matrix(Pn.exp)))
tPn.exp = cbind(data.frame("mode" = mode), tPn.exp)
modeComparison.exp = melt(tPn.exp, "mode", variable.name = "protein", value.name = "Pn")
modeComparison.exp = ddply(modeComparison.exp, "protein", mutate, "Pn" = Pn / mean(Pn, na.rm = T))

# modeComparison.exp has NA's because for proteins with gaps when using Keff there're less modes
#print("Warning: modeComparison.exp <- na.omit(modeComparison.exp)")
modeComparison.exp <- na.omit(modeComparison.exp)
modeComparison.medium <- na.omit(modeComparison.medium)
modeComparison.mut <- na.omit(modeComparison.mut)

CA.modeComparison.all.datasets = rbind(data.frame("dataset" = "exp", modeComparison.exp),
                                       data.frame("dataset" = "mut", modeComparison.mut),
                                       data.frame("dataset" = "medium", modeComparison.medium))
```

```{r median-vs-mode-energy}
dat = CA.modeComparison.all.datasets
dat$dataset = revalue(dat$dataset, c("medium" = "selection"))
dat$dataset = revalue(dat$dataset, c("mut" = "no-selection"))

# calculate dataset of medians

dat = ddply(dat,c("dataset", "mode"), function(x) {
    Pn.median = median(x$Pn)
    Pn.median.ci = sort(x$Pn)[qbinom(c(.025, .975), length(x$Pn), 0.5)]
    Pn.median.min = Pn.median.ci[1]
    Pn.median.max = Pn.median.ci[2]
    data.frame(Pn.median.min, Pn.median.max, Pn.median)
})
```
```{r set-file-names}
data.dir <- paste("OUT/out_subset_CM_ANM", sep = "")
R0 = R0.CM

# set input filenames
## profiles to compare
Pn.exp.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.exp.Pn.csv", sep = ""))
Pn.medium.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_medium.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
Pn.mut.fname = file.path(data.dir,paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
```

```{r prepare-site-data}
# prepare the data
Pn.exp = read.csv(Pn.exp.fname, header = T)
rownames(Pn.exp) = paste("mut", rownames(Pn.exp), sep = "")

Pn.mut = read.csv(Pn.mut.fname, header = T)
rownames(Pn.mut) = paste("mut", rownames(Pn.mut), sep = "")

Pn.medium = read.csv(Pn.medium.fname, header = T)
rownames(Pn.medium) = paste("medium", rownames(Pn.medium), sep = "")

mode = seq(ncol(Pn.medium))

# Prepare modeComparison.medium
tPn.medium = as.data.frame(t(as.matrix(Pn.medium)))
tPn.medium = cbind(data.frame("mode" = mode), tPn.medium)
modeComparison.medium = melt(tPn.medium, "mode", variable.name = "protein", value.name = "Pn")
modeComparison.medium = ddply(modeComparison.medium, "protein", mutate, "Pn" = Pn / mean(Pn, na.rm = T))

# Prepare modeComparison.mut
tPn.mut = as.data.frame(t(as.matrix(Pn.mut)))
tPn.mut = cbind(data.frame("mode" = mode), tPn.mut)
modeComparison.mut = melt(tPn.mut, "mode", variable.name = "protein", value.name = "Pn")
modeComparison.mut = ddply(modeComparison.mut, "protein", mutate, "Pn" = Pn / mean(Pn, na.rm = T))

# Prepare modeComparison.exp
tPn.exp = as.data.frame(t(as.matrix(Pn.exp)))
tPn.exp = cbind(data.frame("mode" = mode), tPn.exp)
modeComparison.exp = melt(tPn.exp, "mode", variable.name = "protein", value.name = "Pn")
modeComparison.exp = ddply(modeComparison.exp, "protein", mutate, "Pn" = Pn / mean(Pn, na.rm = T))

# modeComparison.exp has NA's because for proteins with gaps when using Keff there're less modes
#print("Warning: modeComparison.exp <- na.omit(modeComparison.exp)")
modeComparison.exp <- na.omit(modeComparison.exp)
modeComparison.medium <- na.omit(modeComparison.medium)
modeComparison.mut <- na.omit(modeComparison.mut)

CM.modeComparison.all.datasets = rbind(data.frame("dataset" = "exp", modeComparison.exp),
                                       data.frame("dataset" = "mut", modeComparison.mut),
                                       data.frame("dataset" = "medium", modeComparison.medium))
```

```{r median-vs-mode-energy}
dat = CM.modeComparison.all.datasets
dat$dataset = revalue(dat$dataset, c("medium" = "selection"))
dat$dataset = revalue(dat$dataset, c("mut" = "no-selection"))

# calculate dataset of medians

d = ddply(dat,c("dataset", "mode"), function(x) {
    Pn.median = median(x$Pn)
    Pn.median.ci = sort(x$Pn)[qbinom(c(.025, .975), length(x$Pn), 0.5)]
    Pn.median.min = Pn.median.ci[1]
    Pn.median.max = Pn.median.ci[2]
    data.frame(Pn.median.min, Pn.median.max, Pn.median)
})
```

### 2017-05-01 analysis-structure.Rmd
CA vs CM y comparaciones R0s

@@
 dri2.mut = read.csv(dri2.mut.fname, header = T)
-site = site.info$site
-dri2.mut = dri2.mut[1:length(protein.exp), site]
 rownames(dri2.mut) = paste("mut", rownames(dri2.mut), sep = "")
@@
 dri2.medium = read.csv(dri2.medium.fname, header = T)
-site = site.info$site
-dri2.medium = dri2.medium[1:length(protein.exp), site]
 rownames(dri2.medium) = paste("medium", rownames(dri2.medium), sep = "")
@@
 ## dat with means and standard errors
-d = ddply(dat,c("dataset", "site", "AA", "shell"), function(x) {
+d = ddply(dat,c("dataset", "site"), function(x) {
                 mean.z.RSD = mean(x$z.RSD, na.rm = T)
@@
 
-```{r structure-profiles-CN-comparison}
+```{r structure-CN-comparison}
 

### 2017-05-01 comparison_CA_CM.Rmd
CA vs CM y comparaciones R0s

@@
 # load functions
-source(file.path(data.dir, "my-functions.R"))
+source(file.path(paste("OUT/out_subset_CA_ANM", sep = ""), "my-functions.R"))
 
@@
 
-```{r set-file-names}
+```{r prepare-data-CA}
 data.dir <- paste("OUT/out_subset_CA_ANM", sep = "")
@@
 
-```
-
-```{r read-functional-sites}
 # which are the functional sites?
@@
 active.site.index = functional.sites$index
-```
 
-```{r read-data}
 # read data
@@
 
-```{r set-file-names-CM}
+```{r prepare-data-CM}
 data.dir <- paste("OUT/out_subset_CM_ANM", sep = "")
@@
 CM.sim.data.medium.sel.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_medium.sel_out_df.data.csv", sep = ""))
-```
 
-```{r read-data-CM}
 # read data
@@
 
-cor.df = data.frame("comparison CA" = c("exp vs no-selection", "exp vs selection", "no-selection vs selection"),
+cor.df = data.frame("Comparison CA" = c("exp vs no-selection", "exp vs selection", "no-selection vs selection"),
                     "R" = c(r.exp.mut, r.exp.medium, r.mut.medium))
@@
 
-cor.df = data.frame("comparison CM" = c("exp vs no-selection", "exp vs selection", "no-selection vs selection"),
+cor.df = data.frame("Comparison CM" = c("exp vs no-selection", "exp vs selection", "no-selection vs selection"),
                     "R" = c(r.exp.mut, r.exp.medium, r.mut.medium))
@@
 
-```{r plots, fig.cap= "yellow = active sites"}
+```{r plots, fig.cap = "yellow = active sites"}
+
 # plot comparative profiles
@@
 ```{r correlations-CA-CM}
+
 # calculate cors
@@
 
-cor.df = data.frame("comparison CM" = c("exp CA vs CM", "no-selection CA vs CM", "selection CA vs CM"),
+cor.df = data.frame("Comparison" = c("exp CA vs CM", "no-selection CA vs CM", "selection CA vs CM"),
                     "R" = c(r.exp, r.mut, r.medium))
@@
 
-```{r sequence-profiles-comparison}
+```{r sequence-profiles-comparison-CA}
 # read experimental data obtained from ConsurfDB
@@
 
-cor.df = data.frame("comparison CA" = c("log(paccept no-selection) vs CN", "log(paccept no-selection) vs score", "score vs CN"),
+cor.df = data.frame("Comparison CA" = c("log(paccept no-selection) vs CN", "log(paccept no-selection) vs score", "score vs CN"),
                     "R" = c(r.p.accept.mut.CN , r.p.accept.mut.score, r.score.CN))
@@
 
-cor.df = data.frame("comparison CA" = c("log(paccept selection) vs CN", "log(paccept selection) vs score", "score vs CN"),
+cor.df = data.frame("Comparison CA" = c("log(paccept selection) vs CN", "log(paccept selection) vs score", "score vs CN"),
                     "R" = c(r.p.accept.medium.sel.CN , r.p.accept.medium.sel.score, r.score.CN))
@@
 
-cor.df = data.frame("comparison CM" = c("log(paccept no-selection) vs CN", "log(paccept no-selection) vs score", "score vs CN"),
+cor.df = data.frame("Comparison CM" = c("log(paccept no-selection) vs CN", "log(paccept no-selection) vs score", "score vs CN"),
                     "R" = c(r.p.accept.mut.CN , r.p.accept.mut.score, r.score.CN))
@@
 
-cor.df = data.frame("comparison CM" = c("log(paccept selection) vs CN", "log(paccept selection) vs score", "score vs CN"),
+cor.df = data.frame("Comparison CM" = c("log(paccept selection) vs CN", "log(paccept selection) vs score", "score vs CN"),
                     "R" = c(r.p.accept.medium.sel.CN , r.p.accept.medium.sel.score, r.score.CN))
@@
 ```{r structure-profiles-CN-comparison}
+# CA
 d = d.CA
-# calculate correlations berween profiles
+
+## calculate correlations berween profiles
 d.exp = subset(d, dataset == "exp")
@@
 
-cor.df = data.frame("comparison CA" = c("<z.RSD> experimental vs CN", "<z.RSD> no-selection vs CN", "<z.RSD> selection vs CN"),
+cor.df = data.frame("Comparison CA" = c("<z.RSD> experimental vs CN", "<z.RSD> no-selection vs CN", "<z.RSD> selection vs CN"),
                     "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))
@@
 knitr::kable(cor.df, digits = 2, caption = "Correlation structure (<z.RSD>) - sequence (CN)")
-```
 
-```{r structure-profiles-CN-comparison-CM}
+# CM
 d = d.CM
-# calculate correlations berween profiles
+
+## calculate correlations berween profiles
 d.exp = subset(d, dataset == "exp")
@@
 
-cor.df = data.frame("comparison CM" = c("<z.RSD> experimental vs CN", "<z.RSD> no-selection vs CN", "<z.RSD> selection vs CN"),
+cor.df = data.frame("Comparison CM" = c("<z.RSD> experimental vs CN", "<z.RSD> no-selection vs CN", "<z.RSD> selection vs CN"),
                     "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))
@@
 ### Structure - normal modes 
-
-```{r set-file-names}
+```{r prepare-data-Pn-CA}
 data.dir <- paste("OUT/out_subset_CA_ANM", sep = "")
@@
 Pn.mut.fname = file.path(data.dir,paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
-```
 
-```{r prepare-site-data}
 # prepare the data
@@
 Pn.medium = read.csv(Pn.medium.fname, header = T)
-rownames(Pn.medium) = paste("medium", rownames(Pn.medium), sep = "")
+rownames(Pn.medium) = paste("mut", rownames(Pn.medium), sep = "")
 
@@
                                        data.frame("dataset" = "medium", modeComparison.medium))
-```
 
-```{r median-vs-mode-energy}
 dat = CA.modeComparison.all.datasets
@@
 
-# calculate dataset of medians
+# calculate dataset of means
 
-dat = ddply(dat,c("dataset", "mode"), function(x) {
-    Pn.median = median(x$Pn)
+d.CA = ddply(dat,c("dataset", "mode"), function(x) {
+       median.Pn = median(x$Pn)
        Pn.median.ci = sort(x$Pn)[qbinom(c(.025, .975), length(x$Pn), 0.5)]
@@
        Pn.median.max = Pn.median.ci[2]
-    data.frame(Pn.median.min, Pn.median.max, Pn.median)
+       data.frame(Pn.median.min, Pn.median.max, median.Pn)
 })
 ```
-```{r set-file-names}
+
+```{r prepare-data-Pn-CM}
 data.dir <- paste("OUT/out_subset_CM_ANM", sep = "")
@@
                                        data.frame("dataset" = "medium", modeComparison.medium))
-```
 
-```{r median-vs-mode-energy}
 dat = CM.modeComparison.all.datasets
@@
 
-d = ddply(dat,c("dataset", "mode"), function(x) {
-    Pn.median = median(x$Pn)
+d.CM = ddply(dat,c("dataset", "mode"), function(x) {
+       median.Pn = median(x$Pn)
        Pn.median.ci = sort(x$Pn)[qbinom(c(.025, .975), length(x$Pn), 0.5)]
@@
        Pn.median.max = Pn.median.ci[2]
-    data.frame(Pn.median.min, Pn.median.max, Pn.median)
+       data.frame(Pn.median.min, Pn.median.max, median.Pn)
 })
 ```
+
+```{r comparison-median.Pn-vs-mode}
+# CA
+d = d.CA
+
+# calculate correlations berween profiles
+d.exp = subset(d, dataset == "exp")
+d.mut = subset(d, dataset == "no-selection")
+d.medium = subset(d, dataset == "selection")
+
+# calculate cors
+r.exp.mut = cor(d.exp$median.Pn, d.mut$median.Pn)
+r.exp.medium = cor(d.exp$median.Pn, d.medium$median.Pn)
+r.mut.medium = cor(d.mut$median.Pn, d.medium$median.Pn)
+
+# save data
+CA.mean.exp = d.exp$median.Pn
+CA.mean.mut = d.mut$median.Pn
+CA.mean.medium = d.medium$median.Pn
+
+CA.se.exp = d.exp$se.z.RSD
+CA.se.mut = d.mut$se.z.RSD
+CA.se.medium = d.medium$se.z.RSD
+
+cor.df = data.frame("Comparison CA" = c("exp vs no-selection", "exp vs selection", "no-selection vs selection"),
+                    "R" = c(r.exp.mut, r.exp.medium, r.mut.medium))
+
+knitr::kable(cor.df, digits = 2, caption = "Correlation between median.Pn profiles")
+
+# CM
+d = d.CM
+
+# calculate correlations berween profiles
+d.exp = subset(d, dataset == "exp")
+d.mut = subset(d, dataset == "no-selection")
+d.medium = subset(d, dataset == "selection")
+
+# calculate cors
+r.exp.mut = cor(d.exp$median.Pn, d.mut$median.Pn)
+r.exp.medium = cor(d.exp$median.Pn, d.medium$median.Pn)
+r.mut.medium = cor(d.mut$median.Pn, d.medium$median.Pn)
+
+# save data
+CM.mean.exp = d.exp$median.Pn
+CM.mean.mut = d.mut$median.Pn
+CM.mean.medium = d.medium$median.Pn
+
+CM.se.exp = d.exp$se.z.RSD
+CM.se.mut = d.mut$se.z.RSD
+CM.se.medium = d.medium$se.z.RSD
+
+cor.df = data.frame("Comparison CM" = c("exp vs no-selection", "exp vs selection", "no-selection vs selection"),
+                    "R" = c(r.exp.mut, r.exp.medium, r.mut.medium))
+
+knitr::kable(cor.df, digits = 2, caption = "Correlation between median.Pn profiles")
+```
+
+```{r plots-Pn}
+# plot comparative profiles
+par(pty = "s")
+
+# exp
+plot(x = CA.mean.exp, y = CM.mean.exp, xlab = "CA median.Pn experimental", ylab = "CM median.Pn experimental")
+abline(0, 1)
+
+# mut
+plot(x = CA.mean.mut, y = CM.mean.mut, xlab = "CA median.Pn no-selection", ylab = "CM median.Pn no-selection")
+abline(0, 1)
+
+# medium
+plot(x = CA.mean.medium, y = CM.mean.medium, xlab = "CA median.Pn selection", ylab = "CM median.Pn selection")
+abline(0, 1)
+```
+
+```{r correlations-CA-CM-Pn}
+
+# calculate cors
+r.exp = cor(CA.mean.exp, CM.mean.exp)
+r.mut = cor(CA.mean.mut, CM.mean.mut)
+r.medium = cor(CA.mean.medium, CM.mean.medium)
+
+cor.df = data.frame("Comparison" = c("exp CA vs CM", "no-selection CA vs CM", "selection CA vs CM"),
+                    "R" = c(r.exp, r.mut, r.medium))
+
+knitr::kable(cor.df, digits = 2, caption = "Correlation between CA and CM median.Pn profiles")
+```
+
+### Dynamics - MSF
+
+```{r prepare-data-square.dif.MSF-CA}
+data.dir <- paste("OUT/out_subset_CA_ANM", sep = "")
+R0 = R0.CA
+
+# set input filenames
+## profiles to compare
+square.dif.MSF.exp.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.exp.square.dif.MSF.csv", sep = ""))
+square.dif.MSF.medium.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_medium.sel_K.analysis_Keff_out_m.theo.square.dif.MSF.csv", sep = ""))
+square.dif.MSF.mut.fname = file.path(data.dir,paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.square.dif.MSF.csv", sep = ""))
+
+# prepare the data
+square.dif.MSF.exp = read.csv(square.dif.MSF.exp.fname, header = T)
+rownames(square.dif.MSF.exp) = paste("mut", rownames(square.dif.MSF.exp), sep = "")
+
+square.dif.MSF.mut = read.csv(square.dif.MSF.mut.fname, header = T)
+rownames(square.dif.MSF.mut) = paste("mut", rownames(square.dif.MSF.mut), sep = "")
+
+square.dif.MSF.medium = read.csv(square.dif.MSF.medium.fname, header = T)
+rownames(square.dif.MSF.medium) = paste("mut", rownames(square.dif.MSF.medium), sep = "")
+
+site = seq(ncol(square.dif.MSF.medium))
+
+# Prepare siteComparison.medium
+tsquare.dif.MSF.medium = as.data.frame(t(as.matrix(square.dif.MSF.medium)))
+tsquare.dif.MSF.medium = cbind(data.frame("site" = site), tsquare.dif.MSF.medium)
+siteComparison.medium = melt(tsquare.dif.MSF.medium, "site", variable.name = "protein", value.name = "square.dif.MSF")
+
+# Prepare siteComparison.mut
+tsquare.dif.MSF.mut = as.data.frame(t(as.matrix(square.dif.MSF.mut)))
+tsquare.dif.MSF.mut = cbind(data.frame("site" = site), tsquare.dif.MSF.mut)
+siteComparison.mut = melt(tsquare.dif.MSF.mut, "site", variable.name = "protein", value.name = "square.dif.MSF")
+
+# Prepare siteComparison.exp
+tsquare.dif.MSF.exp = as.data.frame(t(as.matrix(square.dif.MSF.exp)))
+tsquare.dif.MSF.exp = cbind(data.frame("site" = site), tsquare.dif.MSF.exp)
+siteComparison.exp = melt(tsquare.dif.MSF.exp, "site", variable.name = "protein", value.name = "square.dif.MSF")
+
+CA.siteComparison.all.datasets = rbind(data.frame("dataset" = "exp", siteComparison.exp),
+                                       data.frame("dataset" = "mut", siteComparison.mut),
+                                       data.frame("dataset" = "medium", siteComparison.medium))
+
+CA.siteComparison.all.datasets = ddply(CA.siteComparison.all.datasets, c("dataset", "protein"), mutate,
+          "r.SDF" = rank(square.dif.MSF, na.last = "keep"))
+
+dat = CA.siteComparison.all.datasets
+dat$dataset = revalue(dat$dataset, c("medium" = "selection"))
+dat$dataset = revalue(dat$dataset, c("mut" = "no-selection"))
+
+# calculate dataset of means
+d.CA = ddply(dat, c("dataset", "site"), function(x) {
+       mean.r.SDF = mean(x$r.SDF, na.rm = T)
+       data.frame(mean.r.SDF)
+})
+```
+
+```{r prepare-data-square.dif.MSF-CM}
+data.dir <- paste("OUT/out_subset_CM_ANM", sep = "")
+R0 = R0.CM
+
+# set input filenames
+## profiles to compare
+square.dif.MSF.exp.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.exp.square.dif.MSF.csv", sep = ""))
+square.dif.MSF.medium.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_medium.sel_K.analysis_Keff_out_m.theo.square.dif.MSF.csv", sep = ""))
+square.dif.MSF.mut.fname = file.path(data.dir,paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.square.dif.MSF.csv", sep = ""))
+
+# prepare the data
+square.dif.MSF.exp = read.csv(square.dif.MSF.exp.fname, header = T)
+rownames(square.dif.MSF.exp) = paste("mut", rownames(square.dif.MSF.exp), sep = "")
+
+square.dif.MSF.mut = read.csv(square.dif.MSF.mut.fname, header = T)
+rownames(square.dif.MSF.mut) = paste("mut", rownames(square.dif.MSF.mut), sep = "")
+
+square.dif.MSF.medium = read.csv(square.dif.MSF.medium.fname, header = T)
+rownames(square.dif.MSF.medium) = paste("mut", rownames(square.dif.MSF.medium), sep = "")
+
+site = seq(ncol(square.dif.MSF.medium))
+
+# Prepare siteComparison.medium
+tsquare.dif.MSF.medium = as.data.frame(t(as.matrix(square.dif.MSF.medium)))
+tsquare.dif.MSF.medium = cbind(data.frame("site" = site), tsquare.dif.MSF.medium)
+siteComparison.medium = melt(tsquare.dif.MSF.medium, "site", variable.name = "protein", value.name = "square.dif.MSF")
+
+# Prepare siteComparison.mut
+tsquare.dif.MSF.mut = as.data.frame(t(as.matrix(square.dif.MSF.mut)))
+tsquare.dif.MSF.mut = cbind(data.frame("site" = site), tsquare.dif.MSF.mut)
+siteComparison.mut = melt(tsquare.dif.MSF.mut, "site", variable.name = "protein", value.name = "square.dif.MSF")
+
+# Prepare siteComparison.exp
+tsquare.dif.MSF.exp = as.data.frame(t(as.matrix(square.dif.MSF.exp)))
+tsquare.dif.MSF.exp = cbind(data.frame("site" = site), tsquare.dif.MSF.exp)
+siteComparison.exp = melt(tsquare.dif.MSF.exp, "site", variable.name = "protein", value.name = "square.dif.MSF")
+
+CM.siteComparison.all.datasets = rbind(data.frame("dataset" = "exp", siteComparison.exp),
+                                       data.frame("dataset" = "mut", siteComparison.mut),
+                                       data.frame("dataset" = "medium", siteComparison.medium))
+
+CM.siteComparison.all.datasets = ddply(CM.siteComparison.all.datasets, c("dataset", "protein"), mutate,
+          "r.SDF" = rank(square.dif.MSF, na.last = "keep"))
+
+dat = CM.siteComparison.all.datasets
+dat$dataset = revalue(dat$dataset, c("medium" = "selection"))
+dat$dataset = revalue(dat$dataset, c("mut" = "no-selection"))
+
+# calculate dataset of means
+d.CM = ddply(dat, c("dataset", "site"), function(x) {
+       mean.r.SDF = mean(x$r.SDF, na.rm = T)
+       data.frame(mean.r.SDF)
+})
+```
+
+```{r comparison-mean.r.SDF-site}
+# CA
+d = d.CA
+
+# calculate correlations berween profiles
+d.exp = subset(d, dataset == "exp")
+d.mut = subset(d, dataset == "no-selection")
+d.medium = subset(d, dataset == "selection")
+
+# calculate cors
+r.exp.mut = cor(d.exp$mean.r.SDF, d.mut$mean.r.SDF)
+r.exp.medium = cor(d.exp$mean.r.SDF, d.medium$mean.r.SDF)
+r.mut.medium = cor(d.mut$mean.r.SDF, d.medium$mean.r.SDF)
+
+# save data
+CA.mean.exp = d.exp$mean.r.SDF
+CA.mean.mut = d.mut$mean.r.SDF
+CA.mean.medium = d.medium$mean.r.SDF
+
+CA.se.exp = d.exp$se.z.RSD
+CA.se.mut = d.mut$se.z.RSD
+CA.se.medium = d.medium$se.z.RSD
+
+cor.df = data.frame("Comparison CA" = c("exp vs no-selection", "exp vs selection", "no-selection vs selection"),
+                    "R" = c(r.exp.mut, r.exp.medium, r.mut.medium))
+
+knitr::kable(cor.df, digits = 2, caption = "Correlation between mean.r.SDF profiles")
+
+# CM
+d = d.CM
+
+# calculate correlations berween profiles
+d.exp = subset(d, dataset == "exp")
+d.mut = subset(d, dataset == "no-selection")
+d.medium = subset(d, dataset == "selection")
+
+# calculate cors
+r.exp.mut = cor(d.exp$mean.r.SDF, d.mut$mean.r.SDF)
+r.exp.medium = cor(d.exp$mean.r.SDF, d.medium$mean.r.SDF)
+r.mut.medium = cor(d.mut$mean.r.SDF, d.medium$mean.r.SDF)
+
+# save data
+CM.mean.exp = d.exp$mean.r.SDF
+CM.mean.mut = d.mut$mean.r.SDF
+CM.mean.medium = d.medium$mean.r.SDF
+
+CM.se.exp = d.exp$se.z.RSD
+CM.se.mut = d.mut$se.z.RSD
+CM.se.medium = d.medium$se.z.RSD
+
+cor.df = data.frame("Comparison CM" = c("exp vs no-selection", "exp vs selection", "no-selection vs selection"),
+                    "R" = c(r.exp.mut, r.exp.medium, r.mut.medium))
+
+knitr::kable(cor.df, digits = 2, caption = "Correlation between mean.r.SDF profiles")
+```
+
+```{r plots-MSF}
+# plot comparative profiles
+par(pty = "s")
+
+# exp
+plot(x = CA.mean.exp, y = CM.mean.exp, xlab = "CA mean.r.SDF experimental", ylab = "CM mean.r.SDF experimental")
+abline(0, 1)
+
+# mut
+plot(x = CA.mean.mut, y = CM.mean.mut, xlab = "CA mean.r.SDF no-selection", ylab = "CM mean.r.SDF no-selection")
+abline(0, 1)
+
+# medium
+plot(x = CA.mean.medium, y = CM.mean.medium, xlab = "CA mean.r.SDF selection", ylab = "CM mean.r.SDF selection")
+abline(0, 1)
+```
+
+```{r correlations-CA-CM-MSF}
+# calculate cors
+r.exp = cor(CA.mean.exp, CM.mean.exp)
+r.mut = cor(CA.mean.mut, CM.mean.mut)
+r.medium = cor(CA.mean.medium, CM.mean.medium)
+
+cor.df = data.frame("Comparison" = c("exp CA vs CM", "no-selection CA vs CM", "selection CA vs CM"),
+                    "R" = c(r.exp, r.mut, r.medium))
+
+knitr::kable(cor.df, digits = 2, caption = "Correlation between CA and CM mean.r.SDF profiles")
+```
+
+### Dynamics - normal modes (nH)
+```{r prepare-data-nH-CA}
+data.dir <- paste("OUT/out_subset_CA_ANM", sep = "")
+R0 = R0.CA
+
+# set input filenames
+## profiles to compare
+nH.exp.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.exp.nH.csv", sep = ""))
+nH.medium.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_medium.sel_K.analysis_Keff_out_m.theo.nH.csv", sep = ""))
+nH.mut.fname = file.path(data.dir,paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.nH.csv", sep = ""))
+
+# prepare the data
+nH.exp = read.csv(nH.exp.fname, header = T)
+rownames(nH.exp) = paste("mut", rownames(nH.exp), sep = "")
+
+nH.mut = read.csv(nH.mut.fname, header = T)
+rownames(nH.mut) = paste("mut", rownames(nH.mut), sep = "")
+
+nH.medium = read.csv(nH.medium.fname, header = T)
+rownames(nH.medium) = paste("mut", rownames(nH.medium), sep = "")
+
+mode = seq(ncol(nH.medium))
+
+# Prepare modeComparison.medium
+tnH.medium = as.data.frame(t(as.matrix(nH.medium)))
+tnH.medium = cbind(data.frame("mode" = mode), tnH.medium)
+modeComparison.medium = melt(tnH.medium, "mode", variable.name = "protein", value.name = "nH")
+modeComparison.medium = ddply(modeComparison.medium, "protein", mutate, "nH" = nH / mean(nH, na.rm = T))
+
+# Prepare modeComparison.mut
+tnH.mut = as.data.frame(t(as.matrix(nH.mut)))
+tnH.mut = cbind(data.frame("mode" = mode), tnH.mut)
+modeComparison.mut = melt(tnH.mut, "mode", variable.name = "protein", value.name = "nH")
+modeComparison.mut = ddply(modeComparison.mut, "protein", mutate, "nH" = nH / mean(nH, na.rm = T))
+
+# Prepare modeComparison.exp
+tnH.exp = as.data.frame(t(as.matrix(nH.exp)))
+tnH.exp = cbind(data.frame("mode" = mode), tnH.exp)
+modeComparison.exp = melt(tnH.exp, "mode", variable.name = "protein", value.name = "nH")
+modeComparison.exp = ddply(modeComparison.exp, "protein", mutate, "nH" = nH / mean(nH, na.rm = T))
+
+# modeComparison.exp has NA's because for proteins with gaps when using Keff there're less modes
+#print("Warning: modeComparison.exp <- na.omit(modeComparison.exp)")
+modeComparison.exp <- na.omit(modeComparison.exp)
+modeComparison.medium <- na.omit(modeComparison.medium)
+modeComparison.mut <- na.omit(modeComparison.mut)
+
+CA.modeComparison.all.datasets = rbind(data.frame("dataset" = "exp", modeComparison.exp),
+                                       data.frame("dataset" = "mut", modeComparison.mut),
+                                       data.frame("dataset" = "medium", modeComparison.medium))
+
+dat = CA.modeComparison.all.datasets
+dat$dataset = revalue(dat$dataset, c("medium" = "selection"))
+dat$dataset = revalue(dat$dataset, c("mut" = "no-selection"))
+
+# calculate dataset of means
+
+d.CA = ddply(dat,c("dataset", "mode"), function(x) {
+       mean.nH = mean(x$nH)
+       data.frame(mean.nH)
+})
+```
+
+```{r compare-data-nH-CM}
+data.dir <- paste("OUT/out_subset_CM_ANM", sep = "")
+R0 = R0.CM
+
+# set input filenames
+## profiles to compare
+nH.exp.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.exp.nH.csv", sep = ""))
+nH.medium.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_medium.sel_K.analysis_Keff_out_m.theo.nH.csv", sep = ""))
+nH.mut.fname = file.path(data.dir,paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.nH.csv", sep = ""))
+
+# prepare the data
+nH.exp = read.csv(nH.exp.fname, header = T)
+rownames(nH.exp) = paste("mut", rownames(nH.exp), sep = "")
+
+nH.mut = read.csv(nH.mut.fname, header = T)
+rownames(nH.mut) = paste("mut", rownames(nH.mut), sep = "")
+
+nH.medium = read.csv(nH.medium.fname, header = T)
+rownames(nH.medium) = paste("mut", rownames(nH.medium), sep = "")
+
+mode = seq(ncol(nH.medium))
+
+# Prepare modeComparison.medium
+tnH.medium = as.data.frame(t(as.matrix(nH.medium)))
+tnH.medium = cbind(data.frame("mode" = mode), tnH.medium)
+modeComparison.medium = melt(tnH.medium, "mode", variable.name = "protein", value.name = "nH")
+modeComparison.medium = ddply(modeComparison.medium, "protein", mutate, "nH" = nH / mean(nH, na.rm = T))
+
+# Prepare modeComparison.mut
+tnH.mut = as.data.frame(t(as.matrix(nH.mut)))
+tnH.mut = cbind(data.frame("mode" = mode), tnH.mut)
+modeComparison.mut = melt(tnH.mut, "mode", variable.name = "protein", value.name = "nH")
+modeComparison.mut = ddply(modeComparison.mut, "protein", mutate, "nH" = nH / mean(nH, na.rm = T))
+
+# Prepare modeComparison.exp
+tnH.exp = as.data.frame(t(as.matrix(nH.exp)))
+tnH.exp = cbind(data.frame("mode" = mode), tnH.exp)
+modeComparison.exp = melt(tnH.exp, "mode", variable.name = "protein", value.name = "nH")
+modeComparison.exp = ddply(modeComparison.exp, "protein", mutate, "nH" = nH / mean(nH, na.rm = T))
+
+# modeComparison.exp has NA's because for proteins with gaps when using Keff there're less modes
+#print("Warning: modeComparison.exp <- na.omit(modeComparison.exp)")
+modeComparison.exp <- na.omit(modeComparison.exp)
+modeComparison.medium <- na.omit(modeComparison.medium)
+modeComparison.mut <- na.omit(modeComparison.mut)
+
+CM.modeComparison.all.datasets = rbind(data.frame("dataset" = "exp", modeComparison.exp),
+                                       data.frame("dataset" = "mut", modeComparison.mut),
+                                       data.frame("dataset" = "medium", modeComparison.medium))
+
+dat = CM.modeComparison.all.datasets
+dat$dataset = revalue(dat$dataset, c("medium" = "selection"))
+dat$dataset = revalue(dat$dataset, c("mut" = "no-selection"))
+
+# calculate dataset of means
+d.CM = ddply(dat,c("dataset", "mode"), function(x) {
+       mean.nH = mean(x$nH)
+       data.frame(mean.nH)
+})
+```
+
+```{r comparison-mean.nH-vs-mode}
+# CA
+d = d.CA
+
+# calculate correlations berween profiles
+d.exp = subset(d, dataset == "exp")
+d.mut = subset(d, dataset == "no-selection")
+d.medium = subset(d, dataset == "selection")
+
+# calculate cors
+r.exp.mut = cor(d.exp$mean.nH, d.mut$mean.nH)
+r.exp.medium = cor(d.exp$mean.nH, d.medium$mean.nH)
+r.mut.medium = cor(d.mut$mean.nH, d.medium$mean.nH)
+
+# save data
+CA.mean.exp = d.exp$mean.nH
+CA.mean.mut = d.mut$mean.nH
+CA.mean.medium = d.medium$mean.nH
+
+CA.se.exp = d.exp$se.z.RSD
+CA.se.mut = d.mut$se.z.RSD
+CA.se.medium = d.medium$se.z.RSD
+
+cor.df = data.frame("Comparison CA" = c("exp vs no-selection", "exp vs selection", "no-selection vs selection"),
+                    "R" = c(r.exp.mut, r.exp.medium, r.mut.medium))
+
+knitr::kable(cor.df, digits = 2, caption = "Correlation between mean.nH profiles")
+
+# CM
+d = d.CM
+
+# calculate correlations berween profiles
+d.exp = subset(d, dataset == "exp")
+d.mut = subset(d, dataset == "no-selection")
+d.medium = subset(d, dataset == "selection")
+
+# calculate cors
+r.exp.mut = cor(d.exp$mean.nH, d.mut$mean.nH)
+r.exp.medium = cor(d.exp$mean.nH, d.medium$mean.nH)
+r.mut.medium = cor(d.mut$mean.nH, d.medium$mean.nH)
+
+# save data
+CM.mean.exp = d.exp$mean.nH
+CM.mean.mut = d.mut$mean.nH
+CM.mean.medium = d.medium$mean.nH
+
+CM.se.exp = d.exp$se.z.RSD
+CM.se.mut = d.mut$se.z.RSD
+CM.se.medium = d.medium$se.z.RSD
+
+cor.df = data.frame("Comparison CM" = c("exp vs no-selection", "exp vs selection", "no-selection vs selection"),
+                    "R" = c(r.exp.mut, r.exp.medium, r.mut.medium))
+
+knitr::kable(cor.df, digits = 2, caption = "Correlation between mean.nH profiles")
+```
+
+```{r plots-nH}
+# plot comparative profiles
+par(pty = "s")
+
+# exp
+plot(x = CA.mean.exp, y = CM.mean.exp, xlab = "CA mean.nH experimental", ylab = "CM mean.nH experimental")
+abline(0, 1)
+
+# mut
+plot(x = CA.mean.mut, y = CM.mean.mut, xlab = "CA mean.nH no-selection", ylab = "CM mean.nH no-selection")
+abline(0, 1)
+
+# medium
+plot(x = CA.mean.medium, y = CM.mean.medium, xlab = "CA mean.nH selection", ylab = "CM mean.nH selection")
+abline(0, 1)
+```
+
+```{r correlations-CA-CM-nH}
+# calculate cors
+r.exp = cor(CA.mean.exp, CM.mean.exp)
+r.mut = cor(CA.mean.mut, CM.mean.mut)
+r.medium = cor(CA.mean.medium, CM.mean.medium)
+
+cor.df = data.frame("Comparison" = c("exp CA vs CM", "no-selection CA vs CM", "selection CA vs CM"),
+                    "R" = c(r.exp, r.mut, r.medium))
+
+knitr::kable(cor.df, digits = 2, caption = "Correlation between CA and CM mean.nH profiles")
+```

### 2017-05-01 comparison_R0.Rmd
CA vs CM y comparaciones R0s

--- 2017-05-01 comparison_CA_CM.Rmd
@@
 
-```{r prepare-data-CA}
-data.dir <- paste("OUT/out_subset_CA_ANM", sep = "")
-R0 = R0.CA
+```{r prepare-data-R0.1}
+R0 = R0.1
 
@@
 score.fname = file.path(data.dir, paste(p.ref, "_consurf.csv", sep = ""))
-CA.sim.data.mut.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_out_df.data.csv", sep = ""))
-CA.sim.data.medium.sel.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_medium.sel_out_df.data.csv", sep = ""))
+R0.1.sim.data.mut.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_out_df.data.csv", sep = ""))
+R0.1.sim.data.medium.sel.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_medium.sel_out_df.data.csv", sep = ""))
 
@@
 ## dat with means and standard errors
-d.CA = ddply(dat,c("dataset", "site.info"), function(x) {
+d.R0.1 = ddply(dat,c("dataset", "site.info"), function(x) {
                 mean.z.RSD = mean(x$z.RSD, na.rm = T)
@@
 
-```{r prepare-data-CM}
-data.dir <- paste("OUT/out_subset_CM_ANM", sep = "")
-R0 = R0.CM
+```{r prepare-data-R0.2}
+R0 = R0.2
 
@@
 score.fname = file.path(data.dir, paste(p.ref, "_consurf.csv", sep = ""))
-CM.sim.data.mut.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_out_df.data.csv", sep = ""))
-CM.sim.data.medium.sel.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_medium.sel_out_df.data.csv", sep = ""))
+R0.2.sim.data.mut.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_out_df.data.csv", sep = ""))
+R0.2.sim.data.medium.sel.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_medium.sel_out_df.data.csv", sep = ""))
 
@@
 ## dat with means and standard errors
-d.CM = ddply(dat,c("dataset", "site.info"), function(x) {
+d.R0.2 = ddply(dat,c("dataset", "site.info"), function(x) {
                 mean.z.RSD = mean(x$z.RSD, na.rm = T)
@@
 ```{r comparison-mean-z.RSD-vs-site}
-# CA
-d = d.CA
+# R0.1
+d = d.R0.1
 
@@
 # save data
-CA.mean.exp = d.exp$mean.z.RSD
-CA.mean.mut = d.mut$mean.z.RSD
-CA.mean.medium = d.medium$mean.z.RSD
-
-CA.se.exp = d.exp$se.z.RSD
-CA.se.mut = d.mut$se.z.RSD
-CA.se.medium = d.medium$se.z.RSD
-
-cor.df = data.frame("Comparison CA" = c("exp vs no-selection", "exp vs selection", "no-selection vs selection"),
+R0.1.mean.exp = d.exp$mean.z.RSD
+R0.1.mean.mut = d.mut$mean.z.RSD
+R0.1.mean.medium = d.medium$mean.z.RSD
+
+R0.1.se.exp = d.exp$se.z.RSD
+R0.1.se.mut = d.mut$se.z.RSD
+R0.1.se.medium = d.medium$se.z.RSD
+
+cor.df = data.frame("Comparison R0.1" = c("exp vs no-selection", "exp vs selection", "no-selection vs selection"),
                     "R" = c(r.exp.mut, r.exp.medium, r.mut.medium))
@@
 
-# CM
-d = d.CM
+# R0.2
+d = d.R0.2
 
@@
 # save data
-CM.mean.exp = d.exp$mean.z.RSD
-CM.mean.mut = d.mut$mean.z.RSD
-CM.mean.medium = d.medium$mean.z.RSD
-
-CM.se.exp = d.exp$se.z.RSD
-CM.se.mut = d.mut$se.z.RSD
-CM.se.medium = d.medium$se.z.RSD
-
-cor.df = data.frame("Comparison CM" = c("exp vs no-selection", "exp vs selection", "no-selection vs selection"),
+R0.2.mean.exp = d.exp$mean.z.RSD
+R0.2.mean.mut = d.mut$mean.z.RSD
+R0.2.mean.medium = d.medium$mean.z.RSD
+
+R0.2.se.exp = d.exp$se.z.RSD
+R0.2.se.mut = d.mut$se.z.RSD
+R0.2.se.medium = d.medium$se.z.RSD
+
+cor.df = data.frame("Comparison R0.2" = c("exp vs no-selection", "exp vs selection", "no-selection vs selection"),
                     "R" = c(r.exp.mut, r.exp.medium, r.mut.medium))
@@
 
-```{r plots, fig.cap = "yellow = active sites"}
-
+```{r plots, fig.cap= "yellow = active sites"}
 # plot comparative profiles
@@
 # exp
-plot(x = CA.mean.exp, y = CM.mean.exp, xlab = "CA <z.RSD> experimental", ylab = "CM <z.RSD> experimental")
-abline(0, 1)
-points(x = CA.mean.exp[active.site.index], y = CM.mean.exp[active.site.index], col = "yellow")
+plot(x = R0.1.mean.exp, y = R0.2.mean.exp, xlab = "R0.1 <z.RSD> experimental", ylab = "R0.2 <z.RSD> experimental")
+abline(0, 1)
+points(x = R0.1.mean.exp[active.site.index], y = R0.2.mean.exp[active.site.index], col = "yellow")
 
 # mut
-plot(x = CA.mean.mut, y = CM.mean.mut, xlab = "CA <z.RSD> no-selection", ylab = "CM <z.RSD> no-selection")
-abline(0, 1)
-points(x = CA.mean.mut[active.site.index], y = CM.mean.mut[active.site.index], col = "yellow")
+plot(x = R0.1.mean.mut, y = R0.2.mean.mut, xlab = "R0.1 <z.RSD> no-selection", ylab = "R0.2 <z.RSD> no-selection")
+abline(0, 1)
+points(x = R0.1.mean.mut[active.site.index], y = R0.2.mean.mut[active.site.index], col = "yellow")
 
 # medium
-plot(x = CA.mean.medium, y = CM.mean.medium, xlab = "CA <z.RSD> selection", ylab = "CM <z.RSD> selection")
-abline(0, 1)
-points(x = CA.mean.medium[active.site.index], y = CM.mean.medium[active.site.index], col = "yellow")
-```
-
-```{r correlations-CA-CM}
-
-# calculate cors
-r.exp = cor(CA.mean.exp, CM.mean.exp)
-r.mut = cor(CA.mean.mut, CM.mean.mut)
-r.medium = cor(CA.mean.medium, CM.mean.medium)
-
-cor.df = data.frame("Comparison" = c("exp CA vs CM", "no-selection CA vs CM", "selection CA vs CM"),
+plot(x = R0.1.mean.medium, y = R0.2.mean.medium, xlab = "R0.1 <z.RSD> selection", ylab = "R0.2 <z.RSD> selection")
+abline(0, 1)
+points(x = R0.1.mean.medium[active.site.index], y = R0.2.mean.medium[active.site.index], col = "yellow")
+```
+
+```{r correlations-R0.1-R0.2}
+# calculate cors
+r.exp = cor(R0.1.mean.exp, R0.2.mean.exp)
+r.mut = cor(R0.1.mean.mut, R0.2.mean.mut)
+r.medium = cor(R0.1.mean.medium, R0.2.mean.medium)
+
+cor.df = data.frame("Comparison" = c("exp R0.1 vs R0.2", "no-selection R0.1 vs R0.2", "selection R0.1 vs R0.2"),
                     "R" = c(r.exp, r.mut, r.medium))
 
-knitr::kable(cor.df, digits = 2, caption = "Correlation between CA and CM <Z-scores> profiles")
-```
-
-```{r sequence-profiles-comparison-CA}
+knitr::kable(cor.df, digits = 2, caption = "Correlation between R0.1 and R0.2 <Z-scores> profiles")
+```
+
+```{r sequence-profiles-comparison}
 # read experimental data obtained from ConsurfDB
@@
 ## no sel
-CA.sim.data.mut = read.csv(CA.sim.data.mut.fname)
-mut.site.mut = CA.sim.data.mut$site
-accept.mut = CA.sim.data.mut$accept
+R0.1.sim.data.mut = read.csv(R0.1.sim.data.mut.fname)
+mut.site.mut = R0.1.sim.data.mut$site
+accept.mut = R0.1.sim.data.mut$accept
 
 ## medium sel
-CA.sim.data.medium.sel = read.csv(CA.sim.data.medium.sel.fname)
-mut.site.medium.sel = CA.sim.data.medium.sel$site
-accept.medium.sel = CA.sim.data.medium.sel$accept
+R0.1.sim.data.medium.sel = read.csv(R0.1.sim.data.medium.sel.fname)
+mut.site.medium.sel = R0.1.sim.data.medium.sel$site
+accept.medium.sel = R0.1.sim.data.medium.sel$accept
 
@@
 
+# correct indexes
+if (data.dir == "OUT/out_subset_CM_ANM") {
+  mut.site.mut = mut.site.mut - n.sites
+  mut.site.medium.sel = mut.site.medium.sel - n.sites
+}
+
 # calculate CN
-CN.CA = CA.sim.data.mut$CN
+CN.R0.1 = R0.1.sim.data.mut$CN
 CN = c()
@@
 for (i in (1:n.sites)) {
-  CN[i] = CN.CA[which(mut.site.mut == i)][1]
+  CN[i] = CN.R0.1[which(mut.site.mut == i)][1]
 }
@@
 
-cor.df = data.frame("Comparison CA" = c("log(paccept no-selection) vs CN", "log(paccept no-selection) vs score", "score vs CN"),
+cor.df = data.frame("Comparison R0.1" = c("log(paccept no-selection) vs CN", "log(paccept no-selection) vs score", "score vs CN"),
                     "R" = c(r.p.accept.mut.CN , r.p.accept.mut.score, r.score.CN))
@@
 
-cor.df = data.frame("Comparison CA" = c("log(paccept selection) vs CN", "log(paccept selection) vs score", "score vs CN"),
+cor.df = data.frame("Comparison R0.1" = c("log(paccept selection) vs CN", "log(paccept selection) vs score", "score vs CN"),
                     "R" = c(r.p.accept.medium.sel.CN , r.p.accept.medium.sel.score, r.score.CN))
@@
 print(mean(p.accept.medium.sel))
-```
-
-```{r sequence-profiles-comparison-CM}
+
 # read experimental data obtained from ConsurfDB
@@
 ## no sel
-CM.sim.data.mut = read.csv(CM.sim.data.mut.fname)
-mut.site.mut = CM.sim.data.mut$site
-accept.mut = CM.sim.data.mut$accept
+R0.2.sim.data.mut = read.csv(R0.2.sim.data.mut.fname)
+mut.site.mut = R0.2.sim.data.mut$site
+accept.mut = R0.2.sim.data.mut$accept
 
 ## medium sel
-CM.sim.data.medium.sel = read.csv(CM.sim.data.medium.sel.fname)
-mut.site.medium.sel = CM.sim.data.medium.sel$site
-accept.medium.sel = CM.sim.data.medium.sel$accept
+R0.2.sim.data.medium.sel = read.csv(R0.2.sim.data.medium.sel.fname)
+mut.site.medium.sel = R0.2.sim.data.medium.sel$site
+accept.medium.sel = R0.2.sim.data.medium.sel$accept
 
@@
 # correct indexes
+if (data.dir == "OUT/out_subset_CM_ANM") {
   mut.site.mut = mut.site.mut - n.sites
   mut.site.medium.sel = mut.site.medium.sel - n.sites
+}
 
 # calculate CN
-CN.CM = CM.sim.data.mut$CN
+CN.R0.2 = R0.2.sim.data.mut$CN
 CN = c()
@@
 for (i in (1:n.sites)) {
-  CN[i] = CN.CM[which(mut.site.mut == i)][1]
+  CN[i] = CN.R0.2[which(mut.site.mut == i)][1]
 }
@@
 
-cor.df = data.frame("Comparison CM" = c("log(paccept no-selection) vs CN", "log(paccept no-selection) vs score", "score vs CN"),
+cor.df = data.frame("Comparison R0.2" = c("log(paccept no-selection) vs CN", "log(paccept no-selection) vs score", "score vs CN"),
                     "R" = c(r.p.accept.mut.CN , r.p.accept.mut.score, r.score.CN))
@@
 
-cor.df = data.frame("Comparison CM" = c("log(paccept selection) vs CN", "log(paccept selection) vs score", "score vs CN"),
+cor.df = data.frame("Comparison R0.2" = c("log(paccept selection) vs CN", "log(paccept selection) vs score", "score vs CN"),
                     "R" = c(r.p.accept.medium.sel.CN , r.p.accept.medium.sel.score, r.score.CN))
@@
 ```{r structure-profiles-CN-comparison}
-# CA
-d = d.CA
-
-## calculate correlations berween profiles
+
+# R0.1
+d = d.R0.1
+
+# calculate correlations berween profiles
 d.exp = subset(d, dataset == "exp")
@@
 
-cor.df = data.frame("Comparison CA" = c("<z.RSD> experimental vs CN", "<z.RSD> no-selection vs CN", "<z.RSD> selection vs CN"),
+cor.df = data.frame("Comparison R0.1" = c("<z.RSD> experimental vs CN", "<z.RSD> no-selection vs CN", "<z.RSD> selection vs CN"),
                     "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))
@@
 
-# CM
-d = d.CM
-
-## calculate correlations berween profiles
+# R0.2
+d = d.R0.2
+
+# calculate correlations berween profiles
 d.exp = subset(d, dataset == "exp")
@@
 
-cor.df = data.frame("Comparison CM" = c("<z.RSD> experimental vs CN", "<z.RSD> no-selection vs CN", "<z.RSD> selection vs CN"),
+cor.df = data.frame("Comparison R0.2" = c("<z.RSD> experimental vs CN", "<z.RSD> no-selection vs CN", "<z.RSD> selection vs CN"),
                     "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))
@@
 ### Structure - normal modes 
-```{r prepare-data-Pn-CA}
-data.dir <- paste("OUT/out_subset_CA_ANM", sep = "")
-R0 = R0.CA
+```{r prepare-data-Pn-R0.1}
+R0 = R0.1
 
@@
 
-CA.modeComparison.all.datasets = rbind(data.frame("dataset" = "exp", modeComparison.exp),
+R0.1.modeComparison.all.datasets = rbind(data.frame("dataset" = "exp", modeComparison.exp),
                                        data.frame("dataset" = "mut", modeComparison.mut),
@@
 
-dat = CA.modeComparison.all.datasets
+dat = R0.1.modeComparison.all.datasets
 dat$dataset = revalue(dat$dataset, c("medium" = "selection"))
@@
 
-# calculate dataset of means
-
-d.CA = ddply(dat,c("dataset", "mode"), function(x) {
+# calculate dataset of medians
+
+d.R0.1 = ddply(dat,c("dataset", "mode"), function(x) {
        median.Pn = median(x$Pn)
@@
 
-```{r prepare-data-Pn-CM}
-data.dir <- paste("OUT/out_subset_CM_ANM", sep = "")
-R0 = R0.CM
+```{r prepare-data-Pn-R0.2}
+R0 = R0.2
 
@@
 
-CM.modeComparison.all.datasets = rbind(data.frame("dataset" = "exp", modeComparison.exp),
+R0.2.modeComparison.all.datasets = rbind(data.frame("dataset" = "exp", modeComparison.exp),
                                        data.frame("dataset" = "mut", modeComparison.mut),
@@
 
-dat = CM.modeComparison.all.datasets
+dat = R0.2.modeComparison.all.datasets
 dat$dataset = revalue(dat$dataset, c("medium" = "selection"))
@@
 
-d.CM = ddply(dat,c("dataset", "mode"), function(x) {
+d.R0.2 = ddply(dat,c("dataset", "mode"), function(x) {
        median.Pn = median(x$Pn)
@@
 ```{r comparison-median.Pn-vs-mode}
-# CA
-d = d.CA
+# R0.1
+d = d.R0.1
 
@@
 # save data
-CA.mean.exp = d.exp$median.Pn
-CA.mean.mut = d.mut$median.Pn
-CA.mean.medium = d.medium$median.Pn
-
-CA.se.exp = d.exp$se.z.RSD
-CA.se.mut = d.mut$se.z.RSD
-CA.se.medium = d.medium$se.z.RSD
-
-cor.df = data.frame("Comparison CA" = c("exp vs no-selection", "exp vs selection", "no-selection vs selection"),
+R0.1.mean.exp = d.exp$median.Pn
+R0.1.mean.mut = d.mut$median.Pn
+R0.1.mean.medium = d.medium$median.Pn
+
+R0.1.se.exp = d.exp$se.z.RSD
+R0.1.se.mut = d.mut$se.z.RSD
+R0.1.se.medium = d.medium$se.z.RSD
+
+cor.df = data.frame("Comparison R0.1" = c("exp vs no-selection", "exp vs selection", "no-selection vs selection"),
                     "R" = c(r.exp.mut, r.exp.medium, r.mut.medium))
@@
 # save data
-CM.mean.exp = d.exp$median.Pn
-CM.mean.mut = d.mut$median.Pn
-CM.mean.medium = d.medium$median.Pn
-
-CM.se.exp = d.exp$se.z.RSD
-CM.se.mut = d.mut$se.z.RSD
-CM.se.medium = d.medium$se.z.RSD
-
-cor.df = data.frame("Comparison CM" = c("exp vs no-selection", "exp vs selection", "no-selection vs selection"),
+R0.2.mean.exp = d.exp$median.Pn
+R0.2.mean.mut = d.mut$median.Pn
+R0.2.mean.medium = d.medium$median.Pn
+
+R0.2.se.exp = d.exp$se.z.RSD
+R0.2.se.mut = d.mut$se.z.RSD
+R0.2.se.medium = d.medium$se.z.RSD
+
+cor.df = data.frame("Comparison R0.2" = c("exp vs no-selection", "exp vs selection", "no-selection vs selection"),
                     "R" = c(r.exp.mut, r.exp.medium, r.mut.medium))
@@
 # exp
-plot(x = CA.mean.exp, y = CM.mean.exp, xlab = "CA median.Pn experimental", ylab = "CM median.Pn experimental")
+plot(x = R0.1.mean.exp, y = R0.2.mean.exp, xlab = "R0.1 median.Pn experimental", ylab = "R0.2 median.Pn experimental")
 abline(0, 1)
@@
 # mut
-plot(x = CA.mean.mut, y = CM.mean.mut, xlab = "CA median.Pn no-selection", ylab = "CM median.Pn no-selection")
+plot(x = R0.1.mean.mut, y = R0.2.mean.mut, xlab = "R0.1 median.Pn no-selection", ylab = "R0.2 median.Pn no-selection")
 abline(0, 1)
@@
 # medium
-plot(x = CA.mean.medium, y = CM.mean.medium, xlab = "CA median.Pn selection", ylab = "CM median.Pn selection")
-abline(0, 1)
-```
-
-```{r correlations-CA-CM-Pn}
-
-# calculate cors
-r.exp = cor(CA.mean.exp, CM.mean.exp)
-r.mut = cor(CA.mean.mut, CM.mean.mut)
-r.medium = cor(CA.mean.medium, CM.mean.medium)
-
-cor.df = data.frame("Comparison" = c("exp CA vs CM", "no-selection CA vs CM", "selection CA vs CM"),
+plot(x = R0.1.mean.medium, y = R0.2.mean.medium, xlab = "R0.1 median.Pn selection", ylab = "R0.2 median.Pn selection")
+abline(0, 1)
+```
+
+```{r correlations-R0.1-R0.2-Pn}
+# calculate cors
+r.exp = cor(R0.1.mean.exp, R0.2.mean.exp)
+r.mut = cor(R0.1.mean.mut, R0.2.mean.mut)
+r.medium = cor(R0.1.mean.medium, R0.2.mean.medium)
+
+cor.df = data.frame("Comparison" = c("exp R0.1 vs R0.2", "no-selection R0.1 vs R0.2", "selection R0.1 vs R0.2"),
                     "R" = c(r.exp, r.mut, r.medium))
 
-knitr::kable(cor.df, digits = 2, caption = "Correlation between CA and CM median.Pn profiles")
+knitr::kable(cor.df, digits = 2, caption = "Correlation between R0.1 and R0.2 median.Pn profiles")
 ```
@@
 ### Dynamics - MSF 
-
-```{r prepare-data-square.dif.MSF-CA}
-data.dir <- paste("OUT/out_subset_CA_ANM", sep = "")
-R0 = R0.CA
+```{r prepare-data-square.dif.MSF-R0.1}
+R0 = R0.1
 
@@
 
-CA.siteComparison.all.datasets = rbind(data.frame("dataset" = "exp", siteComparison.exp),
+R0.1.siteComparison.all.datasets = rbind(data.frame("dataset" = "exp", siteComparison.exp),
                                        data.frame("dataset" = "mut", siteComparison.mut),
@@
 
-CA.siteComparison.all.datasets = ddply(CA.siteComparison.all.datasets, c("dataset", "protein"), mutate,
+R0.1.siteComparison.all.datasets = ddply(R0.1.siteComparison.all.datasets, c("dataset", "protein"), mutate,
           "r.SDF" = rank(square.dif.MSF, na.last = "keep"))
 
-dat = CA.siteComparison.all.datasets
+dat = R0.1.siteComparison.all.datasets
 dat$dataset = revalue(dat$dataset, c("medium" = "selection"))
@@
 # calculate dataset of means
-d.CA = ddply(dat, c("dataset", "site"), function(x) {
+d.R0.1 = ddply(dat, c("dataset", "site"), function(x) {
        mean.r.SDF = mean(x$r.SDF, na.rm = T)
@@
 
-```{r prepare-data-square.dif.MSF-CM}
-data.dir <- paste("OUT/out_subset_CM_ANM", sep = "")
-R0 = R0.CM
+```{r prepare-data-square.dif.MSF-R0.2}
+R0 = R0.2
 
@@
 
-CM.siteComparison.all.datasets = rbind(data.frame("dataset" = "exp", siteComparison.exp),
+R0.2.siteComparison.all.datasets = rbind(data.frame("dataset" = "exp", siteComparison.exp),
                                        data.frame("dataset" = "mut", siteComparison.mut),
@@
 
-CM.siteComparison.all.datasets = ddply(CM.siteComparison.all.datasets, c("dataset", "protein"), mutate,
+R0.2.siteComparison.all.datasets = ddply(R0.2.siteComparison.all.datasets, c("dataset", "protein"), mutate,
           "r.SDF" = rank(square.dif.MSF, na.last = "keep"))
 
-dat = CM.siteComparison.all.datasets
+dat = R0.2.siteComparison.all.datasets
 dat$dataset = revalue(dat$dataset, c("medium" = "selection"))
@@
 # calculate dataset of means
-d.CM = ddply(dat, c("dataset", "site"), function(x) {
+d.R0.2 = ddply(dat, c("dataset", "site"), function(x) {
        mean.r.SDF = mean(x$r.SDF, na.rm = T)
@@
 ```{r comparison-mean.r.SDF-site}
-# CA
-d = d.CA
+# R0.1
+d = d.R0.1
 
@@
 # save data
-CA.mean.exp = d.exp$mean.r.SDF
-CA.mean.mut = d.mut$mean.r.SDF
-CA.mean.medium = d.medium$mean.r.SDF
-
-CA.se.exp = d.exp$se.z.RSD
-CA.se.mut = d.mut$se.z.RSD
-CA.se.medium = d.medium$se.z.RSD
-
-cor.df = data.frame("Comparison CA" = c("exp vs no-selection", "exp vs selection", "no-selection vs selection"),
+R0.1.mean.exp = d.exp$mean.r.SDF
+R0.1.mean.mut = d.mut$mean.r.SDF
+R0.1.mean.medium = d.medium$mean.r.SDF
+
+R0.1.se.exp = d.exp$se.z.RSD
+R0.1.se.mut = d.mut$se.z.RSD
+R0.1.se.medium = d.medium$se.z.RSD
+
+cor.df = data.frame("Comparison R0.1" = c("exp vs no-selection", "exp vs selection", "no-selection vs selection"),
                     "R" = c(r.exp.mut, r.exp.medium, r.mut.medium))
@@
 # save data
-CM.mean.exp = d.exp$mean.r.SDF
-CM.mean.mut = d.mut$mean.r.SDF
-CM.mean.medium = d.medium$mean.r.SDF
-
-CM.se.exp = d.exp$se.z.RSD
-CM.se.mut = d.mut$se.z.RSD
-CM.se.medium = d.medium$se.z.RSD
-
-cor.df = data.frame("Comparison CM" = c("exp vs no-selection", "exp vs selection", "no-selection vs selection"),
+R0.2.mean.exp = d.exp$mean.r.SDF
+R0.2.mean.mut = d.mut$mean.r.SDF
+R0.2.mean.medium = d.medium$mean.r.SDF
+
+R0.2.se.exp = d.exp$se.z.RSD
+R0.2.se.mut = d.mut$se.z.RSD
+R0.2.se.medium = d.medium$se.z.RSD
+
+cor.df = data.frame("Comparison R0.2" = c("exp vs no-selection", "exp vs selection", "no-selection vs selection"),
                     "R" = c(r.exp.mut, r.exp.medium, r.mut.medium))
@@
 # exp
-plot(x = CA.mean.exp, y = CM.mean.exp, xlab = "CA mean.r.SDF experimental", ylab = "CM mean.r.SDF experimental")
+plot(x = R0.1.mean.exp, y = R0.2.mean.exp, xlab = "R0.1 mean.r.SDF experimental", ylab = "R0.2 mean.r.SDF experimental")
 abline(0, 1)
@@
 # mut
-plot(x = CA.mean.mut, y = CM.mean.mut, xlab = "CA mean.r.SDF no-selection", ylab = "CM mean.r.SDF no-selection")
+plot(x = R0.1.mean.mut, y = R0.2.mean.mut, xlab = "R0.1 mean.r.SDF no-selection", ylab = "R0.2 mean.r.SDF no-selection")
 abline(0, 1)
@@
 # medium
-plot(x = CA.mean.medium, y = CM.mean.medium, xlab = "CA mean.r.SDF selection", ylab = "CM mean.r.SDF selection")
-abline(0, 1)
-```
-
-```{r correlations-CA-CM-MSF}
-# calculate cors
-r.exp = cor(CA.mean.exp, CM.mean.exp)
-r.mut = cor(CA.mean.mut, CM.mean.mut)
-r.medium = cor(CA.mean.medium, CM.mean.medium)
-
-cor.df = data.frame("Comparison" = c("exp CA vs CM", "no-selection CA vs CM", "selection CA vs CM"),
+plot(x = R0.1.mean.medium, y = R0.2.mean.medium, xlab = "R0.1 mean.r.SDF selection", ylab = "R0.2 mean.r.SDF selection")
+abline(0, 1)
+```
+
+```{r correlations-R0.1-R0.2-MSF}
+# calculate cors
+r.exp = cor(R0.1.mean.exp, R0.2.mean.exp)
+r.mut = cor(R0.1.mean.mut, R0.2.mean.mut)
+r.medium = cor(R0.1.mean.medium, R0.2.mean.medium)
+
+cor.df = data.frame("Comparison" = c("exp R0.1 vs R0.2", "no-selection R0.1 vs R0.2", "selection R0.1 vs R0.2"),
                     "R" = c(r.exp, r.mut, r.medium))
 
-knitr::kable(cor.df, digits = 2, caption = "Correlation between CA and CM mean.r.SDF profiles")
+knitr::kable(cor.df, digits = 2, caption = "Correlation between R0.1 and R0.2 mean.r.SDF profiles")
 ```
@@
 ### Dynamics - normal modes (nH)
-```{r prepare-data-nH-CA}
-data.dir <- paste("OUT/out_subset_CA_ANM", sep = "")
-R0 = R0.CA
+
+```{r prepare-data-nH-R0.1}
+R0 = R0.1
 
@@
 # calculate dataset of means
-
-d.CA = ddply(dat,c("dataset", "mode"), function(x) {
+d.R0.1 = ddply(dat,c("dataset", "mode"), function(x) {
        mean.nH = mean(x$nH)
@@
 
-```{r compare-data-nH-CM}
-data.dir <- paste("OUT/out_subset_CM_ANM", sep = "")
-R0 = R0.CM
+```{r prepare-data-nH-R0.2}
+R0 = R0.2
 
@@
 # calculate dataset of means
-d.CM = ddply(dat,c("dataset", "mode"), function(x) {
+d.R0.2 = ddply(dat,c("dataset", "mode"), function(x) {
        mean.nH = mean(x$nH)
@@
 ```{r comparison-mean.nH-vs-mode}
-# CA
-d = d.CA
+# R0.1
+d = d.R0.1
 
@@
 # save data
-CA.mean.exp = d.exp$mean.nH
-CA.mean.mut = d.mut$mean.nH
-CA.mean.medium = d.medium$mean.nH
-
-CA.se.exp = d.exp$se.z.RSD
-CA.se.mut = d.mut$se.z.RSD
-CA.se.medium = d.medium$se.z.RSD
-
-cor.df = data.frame("Comparison CA" = c("exp vs no-selection", "exp vs selection", "no-selection vs selection"),
+R0.1.mean.exp = d.exp$mean.nH
+R0.1.mean.mut = d.mut$mean.nH
+R0.1.mean.medium = d.medium$mean.nH
+
+R0.1.se.exp = d.exp$se.z.RSD
+R0.1.se.mut = d.mut$se.z.RSD
+R0.1.se.medium = d.medium$se.z.RSD
+
+cor.df = data.frame("Comparison R0.1" = c("exp vs no-selection", "exp vs selection", "no-selection vs selection"),
                     "R" = c(r.exp.mut, r.exp.medium, r.mut.medium))
@@
 # save data
-CM.mean.exp = d.exp$mean.nH
-CM.mean.mut = d.mut$mean.nH
-CM.mean.medium = d.medium$mean.nH
-
-CM.se.exp = d.exp$se.z.RSD
-CM.se.mut = d.mut$se.z.RSD
-CM.se.medium = d.medium$se.z.RSD
-
-cor.df = data.frame("Comparison CM" = c("exp vs no-selection", "exp vs selection", "no-selection vs selection"),
+R0.2.mean.exp = d.exp$mean.nH
+R0.2.mean.mut = d.mut$mean.nH
+R0.2.mean.medium = d.medium$mean.nH
+
+R0.2.se.exp = d.exp$se.z.RSD
+R0.2.se.mut = d.mut$se.z.RSD
+R0.2.se.medium = d.medium$se.z.RSD
+
+cor.df = data.frame("Comparison R0.2" = c("exp vs no-selection", "exp vs selection", "no-selection vs selection"),
                     "R" = c(r.exp.mut, r.exp.medium, r.mut.medium))
@@
 # exp
-plot(x = CA.mean.exp, y = CM.mean.exp, xlab = "CA mean.nH experimental", ylab = "CM mean.nH experimental")
+plot(x = R0.1.mean.exp, y = R0.2.mean.exp, xlab = "R0.1 mean.nH experimental", ylab = "R0.2 mean.nH experimental")
 abline(0, 1)
@@
 # mut
-plot(x = CA.mean.mut, y = CM.mean.mut, xlab = "CA mean.nH no-selection", ylab = "CM mean.nH no-selection")
+plot(x = R0.1.mean.mut, y = R0.2.mean.mut, xlab = "R0.1 mean.nH no-selection", ylab = "R0.2 mean.nH no-selection")
 abline(0, 1)
@@
 # medium
-plot(x = CA.mean.medium, y = CM.mean.medium, xlab = "CA mean.nH selection", ylab = "CM mean.nH selection")
-abline(0, 1)
-```
-
-```{r correlations-CA-CM-nH}
-# calculate cors
-r.exp = cor(CA.mean.exp, CM.mean.exp)
-r.mut = cor(CA.mean.mut, CM.mean.mut)
-r.medium = cor(CA.mean.medium, CM.mean.medium)
-
-cor.df = data.frame("Comparison" = c("exp CA vs CM", "no-selection CA vs CM", "selection CA vs CM"),
+plot(x = R0.1.mean.medium, y = R0.2.mean.medium, xlab = "R0.1 mean.nH selection", ylab = "R0.2 mean.nH selection")
+abline(0, 1)
+```
+
+```{r correlations-R0.1-R0.2-nH}
+# calculate cors
+r.exp = cor(R0.1.mean.exp, R0.2.mean.exp)
+r.mut = cor(R0.1.mean.mut, R0.2.mean.mut)
+r.medium = cor(R0.1.mean.medium, R0.2.mean.medium)
+
+cor.df = data.frame("Comparison" = c("exp R0.1 vs R0.2", "no-selection R0.1 vs R0.2", "selection R0.1 vs R0.2"),
                     "R" = c(r.exp, r.mut, r.medium))
 
-knitr::kable(cor.df, digits = 2, caption = "Correlation between CA and CM mean.nH profiles")
-```
+knitr::kable(cor.df, digits = 2, caption = "Correlation between R0.1 and R0.2 mean.nH profiles")
+```

### 2017-05-01 correlations.R

@@ -1,0 +1,380 @@
+# input
+R0S = c(7.5, 10, 12.5)
+data.dir = paste("OUT/out_subset_CA_ANM", sep = "")
+
+# read input
+input.fname <- "input_MainReport.csv"
+input <- read.csv(input.fname)
+
+cc.z.RSD.exp.mut = matrix(ncol = 3, nrow = length(input$family))
+cc.z.RSD.exp.medium = matrix(ncol = 3, nrow = length(input$family))
+cc.z.RSD.mut.medium = matrix(ncol = 3, nrow = length(input$family))
+
+cc.Pn.exp.mut = matrix(ncol = 3, nrow = length(input$family))
+cc.Pn.exp.medium = matrix(ncol = 3, nrow = length(input$family))
+cc.Pn.mut.medium = matrix(ncol = 3, nrow = length(input$family))
+
+cc.Pn.100.exp.mut = matrix(ncol = 3, nrow = length(input$family))
+cc.Pn.100.exp.medium = matrix(ncol = 3, nrow = length(input$family))
+cc.Pn.100.mut.medium = matrix(ncol = 3, nrow = length(input$family))
+
+cc.MSF.exp.mut = matrix(ncol = 3, nrow = length(input$family))
+cc.MSF.exp.medium = matrix(ncol = 3, nrow = length(input$family))
+cc.MSF.mut.medium = matrix(ncol = 3, nrow = length(input$family))
+
+cc.nH.exp.mut = matrix(ncol = 3, nrow = length(input$family))
+cc.nH.exp.medium = matrix(ncol = 3, nrow = length(input$family))
+cc.nH.mut.medium = matrix(ncol = 3, nrow = length(input$family))
+
+cc.nH.100.exp.mut = matrix(ncol = 3, nrow = length(input$family))
+cc.nH.100.exp.medium = matrix(ncol = 3, nrow = length(input$family))
+cc.nH.100.mut.medium = matrix(ncol = 3, nrow = length(input$family))
+
+# satart a loop for each family
+for (f in (1:nrow(input))) { 
+  print(f)
+  family <- as.character(input$family)[f]
+  type <- as.character(input$type)[f]
+  p.ref <- as.character(input$p.ref)[f]
+  enm <- as.character(input$enm)[f]
+  n.mut.p <- input$n.mut.p[f]
+  R0.CA = input$R0.CA[f]
+  R0.CM = input$R0.CM[f]
[…]

### 2017-05-10 analysis-dynamical-nH.Rmd
charla 11-5-17

@@
 ```{r prepare-mode-data}
+
 # prepare the data
 nH.exp = read.csv(nH.exp.fname, header = T)
+rownames(nH.exp) = paste("mut", rownames(nH.exp), sep = "")
 nH.mut = read.csv(nH.mut.fname, header = T)
+rownames(nH.mut) = paste("mut", rownames(nH.mut), sep = "")
 nH.medium = read.csv(nH.medium.fname, header = T)
+rownames(nH.medium) = paste("mut", rownames(nH.medium), sep = "")
+
+mode = seq(ncol(nH.medium))
+
+# Prepare modeComparison
+tnH.medium = as.data.frame(t(as.matrix(nH.medium)))
+tnH.medium = cbind(data.frame("mode" = mode), tnH.medium)
+modeComparison.medium = melt(tnH.medium, "mode", variable.name = "protein", value.name = "nH")
+modeComparison.medium = ddply(modeComparison.medium, "protein", mutate, "nH" = nH / mean(nH, na.rm = T))
+
+tnH.mut = as.data.frame(t(as.matrix(nH.mut)))
+tnH.mut = cbind(data.frame("mode" = mode), tnH.mut)
+modeComparison.mut = melt(tnH.mut, "mode", variable.name = "protein", value.name = "nH")
+modeComparison.mut = ddply(modeComparison.mut, "protein", mutate, "nH" = nH / mean(nH, na.rm = T))
+
+tnH.exp = as.data.frame(t(as.matrix(nH.exp)))
+tnH.exp = cbind(data.frame("mode" = mode), tnH.exp)
+modeComparison.exp = melt(tnH.exp, "mode", variable.name = "protein", value.name = "nH")
+modeComparison.exp = ddply(modeComparison.exp, "protein", mutate, "nH" = nH / mean(nH, na.rm = T))
+
+# modeComparison.exp has NA's because for proteins with gaps when using Keff there're less modes
+#print("Warning: modeComparison.exp <- na.omit(modeComparison.exp)")
+modeComparison.exp <- na.omit(modeComparison.exp)
+modeComparison.medium <- na.omit(modeComparison.medium)
+modeComparison.mut <- na.omit(modeComparison.mut)
+
+modeComparison.all.datasets = rbind(data.frame("dataset" = "exp", modeComparison.exp),                                                   data.frame("dataset" = "mut", modeComparison.mut),
+                                    data.frame("dataset" = "medium", modeComparison.medium))
+
+dat = modeComparison.all.datasets
+dat$dataset = revalue(dat$dataset, c("medium" = "selection"))
+dat$dataset = revalue(dat$dataset, c("mut" = "no-selection"))
+
+# calculate dataset of means
+d = ddply(dat,c("dataset", "mode"), function(x) {
+    mean.nH = mean(x$nH)
+    data.frame(mean.nH)
+    })
+
+    # calculate correlations berween profiles
+    d.exp = subset(d, dataset == "exp")
+    d.mut = subset(d, dataset == "no-selection")
+    d.medium = subset(d, dataset == "selection")
 ```
@@
 
-In this section we consider dynamical divergence using normal modes coordinates. We calculated <nH> and we z-normalized profiles.
+In this section we consider dynamical divergence using normal modes coordinates. We calculated <nH> and we normalized profiles.
 
-```{r comparison-of-means, fig.cap = "blue = experimental - green = no-selection - red = selection"}
-# calculate means
-mean.nH.exp = colMeans(nH.exp, na.rm = T)
-mean.nH.mut = colMeans(nH.mut)
-mean.nH.medium = colMeans(nH.medium)
-
-# scale profiles
-mean.nH.exp = vscale(mean.nH.exp[which(!is.na(mean.nH.exp))])
-mean.nH.mut = vscale(mean.nH.mut[which(!is.na(mean.nH.mut))])
-mean.nH.medium = vscale(mean.nH.medium[which(!is.na(mean.nH.medium))])
-
-plot(mean.nH.exp, ylab = "<z.nH>", xlab = "mode", col = "blue")
-points(mean.nH.mut, col = "green")
-points(mean.nH.medium, col = "red")
-
-r.exp.mut = cor(mean.nH.exp, mean.nH.mut)
-r.exp.medium = cor(mean.nH.exp, mean.nH.medium)
-r.mut.medium = cor(mean.nH.mut, mean.nH.medium)
-
-cor.df = data.frame("comparison" = c("exp vs no-selection", "exp vs selection", "no-selection vs selection"),
-                    "R" = c(r.exp.mut, r.exp.medium, r.mut.medium))
-knitr::kable(cor.df, digits = 2)
-```
-
-```{r vs-mean-plots}
-
-# plot comparative profiles 
-par(pty = "s")
-
-plot(x = mean.nH.exp, 
-     y = mean.nH.mut, 
-     xlab = "<z.nH> experimental", 
-     ylab = "<z.nH> no-selection")
-abline(0, 1)
-
-plot(x = mean.nH.exp, 
-     y = mean.nH.medium, 
-     xlab = "<z.nH> experimental", 
-     ylab = "<z.nH> selection")
-abline(0, 1)
-
-plot(x = mean.nH.mut, 
-     y = mean.nH.medium, 
-     xlab = "<z.nH> no-selection", 
-     ylab = "<z.nH> selection")
-abline(0, 1)
+```{r means}
+# get means
+mean.nH.exp =  subset(d, dataset == "exp")$mean.nH
+mean.nH.mut = d.mut = subset(d, dataset == "no-selection")$mean.nH
+mean.nH.medium = subset(d, dataset == "selection")$mean.nH
 ```
@@
 ```{r comparison-of-means-100-modes}
+# get first 100 modes and re-scale
+mean.nH.exp = mean.nH.exp[1:100]
+mean.nH.mut = mean.nH.mut[1:100]
+mean.nH.medium = mean.nH.medium[1:100]
 
-# get first 100 modes and re-scale
-mean.nH.exp = vscale(mean.nH.exp[1:100])
-mean.nH.mut = vscale(mean.nH.mut[1:100])
-mean.nH.medium = vscale(mean.nH.medium[1:100])
-
-plot(mean.nH.exp, ylab = "<z.nH>", xlab = "mode", col = "blue")
+plot(mean.nH.exp, ylab = "<nH>", xlab = "mode", col = "blue")
 points(mean.nH.mut, col = "green")
@@
      y = mean.nH.mut, 
-     xlab = "<z.nH> experimental", 
-     ylab = "<z.nH> no-selection")
+     xlab = "<nH> experimental", 
+     ylab = "<nH> no-selection")
 abline(0, 1)
@@
      y = mean.nH.medium, 
-     xlab = "<z.nH> experimental", 
-     ylab = "<z.nH> selection")
+     xlab = "<nH> experimental", 
+     ylab = "<nH> selection")
 abline(0, 1)
@@
      y = mean.nH.medium, 
-     xlab = "<z.nH> no-selection", 
-     ylab = "<z.nH> selection")
+     xlab = "<nH> no-selection", 
+     ylab = "<nH> selection")
 abline(0, 1)
 ```
-```{r comparison-of-means-20-modes}
-
-# get first 100 modes and re-scale
-mean.nH.exp = vscale(mean.nH.exp[1:20])
-mean.nH.mut = vscale(mean.nH.mut[1:20])
-mean.nH.medium = vscale(mean.nH.medium[1:20])
-
-plot(mean.nH.exp, ylab = "<z.nH>", xlab = "mode", col = "blue")
-points(mean.nH.mut, col = "green")
-points(mean.nH.medium, col = "red")
-
-r.exp.mut = cor(mean.nH.exp, mean.nH.mut)
-r.exp.medium = cor(mean.nH.exp, mean.nH.medium)
-r.mut.medium = cor(mean.nH.mut, mean.nH.medium)
-
-cor.df = data.frame("comparison" = c("exp vs no-selection", "exp vs selection", "no-selection vs selection"),
-                    "R" = c(r.exp.mut, r.exp.medium, r.mut.medium))
-knitr::kable(cor.df, digits = 2)
-```
-
-```{r vs-mean-plots-20-modes}
-
-# plot comparative profiles 
-plot(x = mean.nH.exp, 
-     y = mean.nH.mut, 
-     xlab = "<z.nH> experimental", 
-     ylab = "<z.nH> no-selection")
-abline(0, 1)
-
-plot(x = mean.nH.exp, 
-     y = mean.nH.medium, 
-     xlab = "<z.nH> experimental", 
-     ylab = "<z.nH> selection")
-abline(0, 1)
-
-plot(x = mean.nH.mut, 
-     y = mean.nH.medium, 
-     xlab = "<z.nH> no-selection", 
-     ylab = "<z.nH> selection")
-abline(0, 1)
-```

### 2017-05-10 analysis-dynamical-nR.Rmd
charla 11-5-17

@@
 
-plot(mean.nR.exp, ylab = "<z.nR>", xlab = "mode", col = "blue")
+plot(mean.nR.exp, ylab = "<nR>", xlab = "mode", col = "blue")
 points(mean.nR.mut, col = "green")
@@
      y = mean.nR.mut, 
-     xlab = "<z.nR> experimental", 
-     ylab = "<z.nR> no-selection")
+     xlab = "<nR> experimental", 
+     ylab = "<nR> no-selection")
 abline(0, 1)
@@
      y = mean.nR.medium, 
-     xlab = "<z.nR> experimental", 
-     ylab = "<z.nR> selection")
+     xlab = "<nR> experimental", 
+     ylab = "<nR> selection")
 abline(0, 1)
@@
      y = mean.nR.medium, 
-     xlab = "<z.nR> no-selection", 
-     ylab = "<z.nR> selection")
+     xlab = "<nR> no-selection", 
+     ylab = "<nR> selection")
 abline(0, 1)

### 2017-05-10 analysis-structure-core.Rmd
charla 11-5-17

@@
 To measure structural divergence we use z.RSD profiles, which are the best for most families.
-
 The following plot compares the mean z.RSD profiles, including standard errors (with .999 confidence level for the mean)
-*Warning: the effective number of data should be smaller than the actual data, especially for the experimental dataset because of several factors.
-We need to deal with this for quantitative analysis.
-Probably we'll need to use bootstrapping to calculate standard errors non-parametrically*
 
@@
     geom_point() +
-    geom_errorbar(aes(ymin = mean.z.RSD - f95 * se.z.RSD, ymax = mean.z.RSD + se.z.RSD), alpha = .4, show.legend = F) +
+    geom_errorbar(aes(ymin = mean.z.RSD - f95 * se.z.RSD, ymax = mean.z.RSD +  f95 * se.z.RSD), alpha = .4, show.legend = F) +
     geom_vline(xintercept = active.sites, show.legend = F) +
@@
     labs(x = "site", y = "structural divergence(<z.RSD>)") +
-    coord_cartesian(ylim = c(-1.5, 2.8)) +
+    coord_cartesian(ylim = c(-2, 3.5)) +
     scale_colour_manual(name = NULL, values = myColors) + 
@@
 
-knitr::kable(cor.df, digits = 2, caption = "Correlation between <Z-scores> profiles")
+knitr::kable(cor.df, digits = 2, caption = "Correlation between <z.RSD> profiles")
 ```
@@
 
-```{r comparisons-between-profiles}
+```{r comparisons-between-profiles, fig.cap = "Yellow points are the active sites and green points are their contacts"}
 
@@
   mut.site.medium.sel = mut.site.medium.sel - n.sites
+  CN.CM = sim.data.mut$CN
+  CN = c()
+
+  for (i in (1:n.sites)) {
+    CN[i] = CN.CM[which(mut.site.mut == i)][1]
+  }
+  CN = CN[indexes.core]
 }
@@
 # core n.sites
-
 for (i in (1:n.sites)) {
@@
 
-plot(x = p.accept.mut, y = CN, xlab = "log(paccept no-selection)")
-plot(x = p.accept.mut, y = score, xlab = "log(paccept no-selection)")
-plot(x = score, y = CN)
+plot(x = p.accept.mut, y = log(CN))
+plot(x = p.accept.mut, y = score)
+plot(x = score, y = log(CN))
 
 ## calculate corelations
-r.p.accept.mut.CN = cor(log(p.accept.mut), CN)
-r.p.accept.mut.score = cor(log(p.accept.mut), score)
-r.score.CN = cor(score, CN)
+r.p.accept.mut.CN = cor(p.accept.mut, log(CN))
+r.p.accept.mut.score = cor(p.accept.mut, score)
+r.score.CN = cor(score, log(CN))
 
-cor.df = data.frame("comparison" = c("log(paccept no-selection) vs CN", "log(paccept no-selection) vs score", "score vs CN"),
+cor.df = data.frame("comparison" = c("paccept no-selection vs log(CN)", "paccept no-selection vs score", "score vs log(CN)"),
                     "R" = c(r.p.accept.mut.CN , r.p.accept.mut.score, r.score.CN))
@@
 
-plot(x = log(p.accept.medium.sel), y = CN, xlab = "log(paccept selection)")
-plot(x = log(p.accept.medium.sel), y = score, xlab = "log(paccept selection)")
-plot(x = score, y = CN)
+plot(x = p.accept.medium.sel, y = log(CN))
+plot(x = p.accept.medium.sel, y = score)
+plot(x = score, y = log(CN))
 
 ## calculate corelations
-r.p.accept.medium.sel.CN = cor(log(p.accept.medium.sel), CN)
-r.p.accept.medium.sel.score = cor(log(p.accept.medium.sel), score)
-r.score.CN = cor(score, CN)
+r.p.accept.medium.sel.CN = cor(p.accept.medium.sel, log(CN))
+r.p.accept.medium.sel.score = cor(p.accept.medium.sel, score)
+r.score.CN = cor(score, log(CN))
 
-cor.df = data.frame("comparison" = c("log(paccept selection) vs CN", "log(paccept selection) vs score", "score vs CN"),
+cor.df = data.frame("comparison" = c("paccept selection vs log(CN)", "paccept selection vs score", "score vs log(CN)"),
                     "R" = c(r.p.accept.medium.sel.CN , r.p.accept.medium.sel.score, r.score.CN))

### 2017-05-10 analysis-structure-normal-modes.Rmd
charla 11-5-17

@@
 Pn.exp = read.csv(Pn.exp.fname, header = T)
-rownames(Pn.exp) = protein.exp
+rownames(Pn.exp) = paste("exp", rownames(Pn.exp), sep = "")
 energy.exp = read.csv(energy.exp.fname, header = T)
-rownames(energy.exp) = protein.exp
+rownames(energy.exp) = paste("exp", rownames(energy.exp), sep = "")
 
@@
     labs(x = "mode energy", y = "structural divergence") +
-    coord_cartesian(xlim = c(0,2.5)) +
+    coord_cartesian(xlim = c(0,3)) +
     scale_colour_manual(name = NULL, values = myColors) + 
@@
     scale_fill_manual(name=NULL,values=myColors)+
-    coord_cartesian(xlim=c(0,1))
+    coord_cartesian(xlim=c(0,3))
 
@@
 ### correlaction between mode profiles
+(calculated for the first 100 modes)
 

### 2017-05-10 analysis-structure-not-sequence.Rmd
charla 11-5-17

--- 2017-05-01 analysis-structure.Rmd
@@
 ```
-
-### Sequence comparison
-
-In this section we compare theoretical sequence divergence profiles with sequence scores obtained from ConsurfDB.
-To obtain theoretical profiles, for each selection regimen, we calculated the number of times we had mutated each site and divided this number by the number of times we had tried a mutation at the site.
-
-```{r sequence-profiles-comparison}
-# read experimental data obtained from ConsurfDB
-consurf = read.csv(score.fname, sep = ";")
-score = consurf$SCORE
-
-# read simulated data
-## no sel
-sim.data.mut = read.csv(sim.data.mut.fname)
-mut.site.mut = sim.data.mut$site
-accept.mut = sim.data.mut$accept
-
-## medium sel
-sim.data.medium.sel = read.csv(sim.data.medium.sel.fname)
-mut.site.medium.sel = sim.data.medium.sel$site
-accept.medium.sel = sim.data.medium.sel$accept
-
-# calculate p.accept of simulated data
-p.accept.mut = c()
-p.accept.medium.sel = c()
-
-# correct indexes
-if (data.dir == "OUT/out_subset_CM_ANM") {
-  mut.site.mut = mut.site.mut - n.sites
-  mut.site.medium.sel = mut.site.medium.sel - n.sites
-  CN.CM = sim.data.mut$CN
-  CN = c()
-
-  for (i in (1:n.sites)) {
-    CN[i] = CN.CM[which(mut.site.mut == i)][1]
-  }
-}
-
-for (i in (1:n.sites)) {
-  accept.mut.i = accept.mut[which(mut.site.mut == i)]
-  p.accept.mut.i = mean(accept.mut.i)
-  p.accept.mut[i] = p.accept.mut.i
-
-  accept.medium.sel.i = accept.medium.sel[which(mut.site.medium.sel == i)]
-  p.accept.medium.sel.i = mean(accept.medium.sel.i)
-  p.accept.medium.sel[i] = p.accept.medium.sel.i
-}
-
-# compare exp vs no sel profiles
-## plot
-par(pty = "s")
-
-plot(x = log(p.accept.mut), y = CN, xlab = "log(paccept no-selection)")
-plot(x = log(p.accept.mut), y = score, xlab = "log(paccept no-selection)")
-plot(x = score, y = CN)
-
-## calculate corelations
-r.p.accept.mut.CN = cor(p.accept.mut, CN)
-r.p.accept.mut.score = cor(p.accept.mut, score)
-r.score.CN = cor(score, CN)
-
-cor.df = data.frame("comparison" = c("log(paccept no-selection) vs CN", "log(paccept no-selection) vs score", "score vs CN"),
-                    "R" = c(r.p.accept.mut.CN , r.p.accept.mut.score, r.score.CN))
-
-knitr::kable(cor.df, digits = 2, caption = "Correlation between sequence profiles")
-
-print("<paccept no-selection>")
-print(mean(p.accept.mut))
-
-# compare exp vs medium sel profiles
-## plot
-par(pty = "s")
-
-plot(x = log(p.accept.medium.sel), y = CN, xlab = "log(paccept selection)")
-plot(x = log(p.accept.medium.sel), y = score, xlab = "log(paccept selection)")
-plot(x = score, y = CN)
-
-## calculate corelations
-r.p.accept.medium.sel.CN = cor(log(p.accept.medium.sel), CN)
-r.p.accept.medium.sel.score = cor(log(p.accept.medium.sel), score)
-r.score.CN = cor(score, CN)
-
-cor.df = data.frame("comparison" = c("log(paccept selection) vs CN", "log(paccept selection) vs score", "score vs CN"),
-                    "R" = c(r.p.accept.medium.sel.CN , r.p.accept.medium.sel.score, r.score.CN))
-
-knitr::kable(cor.df, digits = 2, caption = "Correlation between sequence profiles")
-
-print("<paccept selection>")
-print(mean(p.accept.medium.sel))
-```
-
-### Sequence - structure comparison
-
-```{r structure-CN-comparison}
-
-# compare profiles
-## plot
-par(pty = "s")
-
-plot(x = d.exp$mean.z.RSD, y = CN, xlab = "<zRSDi> experimental ")
-plot(x = d.mut$mean.z.RSD, y = CN, xlab = "<zRSDi> no-selection")
-plot(x = d.medium$mean.z.RSD, y = CN, xlab = "<zRSDi> selection")
-
-## calculate correlations
-r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, CN)
-r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, CN)
-r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, CN)
-
-cor.df = data.frame("comparison" = c("<z.RSD> experimental vs CN", "<z.RSD> no-selection vs CN", "<z.RSD> selection vs CN"),
-                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))
-
-knitr::kable(cor.df, digits = 2, caption = "Correlation structure (<z.RSD>) - sequence (CN)")
-```

### 2017-05-10 analysis-structure.Rmd
charla 11-5-17

@@
 site.info = cbind(site.info, pdb.info)
+
+# find the active site and its contacts
+active.sites = d$site[d$shell == 0]
+contacts.active.sites = d$site[d$shell == 1]
+
 ```
@@
 To measure structural divergence we use z.RSD profiles, which are the best for most families.
-
-The following plot compares the mean z.RSD profiles, including standard errors (with .999 confidence level for the mean)
-*Warning: the effective number of data should be smaller than the actual data, especially for the experimental dataset because of several factors.
-We need to deal with this for quantitative analysis.
-Probably we'll need to use bootstrapping to calculate standard errors non-parametrically*
+The following plot compares the mean z.RSD profiles, including standard errors (with .999 confidence level for the mean).
 
@@
 
-## find the active site and its contacts
-active.sites = d$site[d$shell == 0]
-contacts.active.sites = d$site[d$shell == 1]
+print(active.sites)
 
@@
     geom_ribbon(aes(ymin = mean.z.RSD - f95 * se.z.RSD, ymax = mean.z.RSD + se.z.RSD), alpha = .4, show.legend = F) +
-    geom_vline(xintercept = active.sites, show.legend = F) +
+    geom_vline(xintercept = c(active.sites), show.legend = F) +
     geom_vline(xintercept = contacts.active.sites, col = "grey", show.legend = F) +
     labs(x = "site", y = "<zRSDi>") +
-    coord_cartesian(ylim = c(-1.5, 2.8)) +
+    coord_cartesian(ylim = c(-2, 3.5)) + 
     scale_colour_manual(name = NULL, values = myColors) + 
@@
 
-```{r comparison-mean-z.RSD-vs-site}
+```{r comparison-mean-z.RSD-vs-site, fig.cap = "Yellow points are the active sites and green points are their contacts"}
 
 # comparison of z.RSD profiles
-
 ggplot(d, aes(x = site, y = mean.z.RSD, col = dataset)) +
@@
   geom_vline(xintercept = contacts.active.sites, col = "grey", show.legend = F) +   
+  coord_cartesian(ylim = c(-2,3.5)) +
   scale_colour_manual(name = NULL, values = myColors)
@@
 
-plot(x = log(p.accept.mut), y = CN, xlab = "log(paccept no-selection)")
-plot(x = log(p.accept.mut), y = score, xlab = "log(paccept no-selection)")
-plot(x = score, y = CN)
+plot(x = p.accept.mut, y = log(CN))
+plot(x = p.accept.mut, y = score)
+plot(x = score, y = log(CN))
 
 ## calculate corelations
-r.p.accept.mut.CN = cor(p.accept.mut, CN)
+r.p.accept.mut.CN = cor(p.accept.mut, log(CN))
 r.p.accept.mut.score = cor(p.accept.mut, score)
-r.score.CN = cor(score, CN)
+r.score.CN = cor(score, log(CN))
 
-cor.df = data.frame("comparison" = c("log(paccept no-selection) vs CN", "log(paccept no-selection) vs score", "score vs CN"),
+cor.df = data.frame("comparison" = c("paccept no-selection vs log(CN)", "paccept no-selection vs score", "score vs log(CN)"),
                     "R" = c(r.p.accept.mut.CN , r.p.accept.mut.score, r.score.CN))
@@
 
-plot(x = d.exp$mean.z.RSD, y = CN, xlab = "<zRSDi> experimental ")
-plot(x = d.mut$mean.z.RSD, y = CN, xlab = "<zRSDi> no-selection")
-plot(x = d.medium$mean.z.RSD, y = CN, xlab = "<zRSDi> selection")
+plot(x = d.exp$mean.z.RSD, y = log(CN), xlab = "<zRSDi> experimental ")
+plot(x = d.mut$mean.z.RSD, y = log(CN), xlab = "<zRSDi> no-selection")
+plot(x = d.medium$mean.z.RSD, y = log(CN), xlab = "<zRSDi> selection")
 
 ## calculate correlations
-r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, CN)
-r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, CN)
-r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, CN)
+r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN))
+r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN))
+r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN))
 
-cor.df = data.frame("comparison" = c("<z.RSD> experimental vs CN", "<z.RSD> no-selection vs CN", "<z.RSD> selection vs CN"),
+cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
                     "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))

### 2017-05-10 comparison_CA_CM.Rmd
charla 11-5-17

@@
 ## calculate corelations
-r.p.accept.mut.CN = cor(p.accept.mut, CN)
+r.p.accept.mut.CN = cor(p.accept.mut, log(CN))
 r.p.accept.mut.score = cor(p.accept.mut, score)
-r.score.CN = cor(score, CN)
-
-cor.df = data.frame("Comparison CA" = c("log(paccept no-selection) vs CN", "log(paccept no-selection) vs score", "score vs CN"),
+r.score.CN = cor(score, log(CN))
+
+cor.df = data.frame("Comparison CA" = c("paccept no-selection vs log(CN)", "paccept no-selection vs score", "score vs log(CN)"),
                     "R" = c(r.p.accept.mut.CN , r.p.accept.mut.score, r.score.CN))
@@
 ## calculate corelations
-r.p.accept.medium.sel.CN = cor(log(p.accept.medium.sel), CN)
-r.p.accept.medium.sel.score = cor(log(p.accept.medium.sel), score)
-r.score.CN = cor(score, CN)
-
-cor.df = data.frame("Comparison CA" = c("log(paccept selection) vs CN", "log(paccept selection) vs score", "score vs CN"),
+r.p.accept.medium.sel.CN = cor(p.accept.medium.sel, log(CN))
+r.p.accept.medium.sel.score = cor(p.accept.medium.sel, score)
+r.score.CN = cor(score, log(CN))
+
+cor.df = data.frame("Comparison CA" = c("paccept selection vs log(CN)", "paccept selection vs score", "score vs log(CN)"),
                     "R" = c(r.p.accept.medium.sel.CN , r.p.accept.medium.sel.score, r.score.CN))
@@
 ## calculate corelations
-r.p.accept.mut.CN = cor(p.accept.mut, CN)
+r.p.accept.mut.CN = cor(p.accept.mut, log(CN))
 r.p.accept.mut.score = cor(p.accept.mut, score)
-r.score.CN = cor(score, CN)
-
-cor.df = data.frame("Comparison CM" = c("log(paccept no-selection) vs CN", "log(paccept no-selection) vs score", "score vs CN"),
+r.score.CN = cor(score, log(CN))
+
+cor.df = data.frame("Comparison CM" = c("paccept no-selection vs log(CN)", "paccept no-selection vs score", "score vs log(CN)"),
                     "R" = c(r.p.accept.mut.CN , r.p.accept.mut.score, r.score.CN))
@@
 ## calculate corelations
-r.p.accept.medium.sel.CN = cor(log(p.accept.medium.sel), CN)
-r.p.accept.medium.sel.score = cor(log(p.accept.medium.sel), score)
-r.score.CN = cor(score, CN)
-
-cor.df = data.frame("Comparison CM" = c("log(paccept selection) vs CN", "log(paccept selection) vs score", "score vs CN"),
+r.p.accept.medium.sel.CN = cor(p.accept.medium.sel, log(CN))
+r.p.accept.medium.sel.score = cor(p.accept.medium.sel, score)
+r.score.CN = cor(score, log(CN))
+
+cor.df = data.frame("Comparison CM" = c("paccept selection vs log(CN)", "paccept selection vs score", "score vs log(CN)"),
                     "R" = c(r.p.accept.medium.sel.CN , r.p.accept.medium.sel.score, r.score.CN))
@@
 # calculate cors
-r.exp.mut = cor(d.exp$median.Pn, d.mut$median.Pn)
-r.exp.medium = cor(d.exp$median.Pn, d.medium$median.Pn)
-r.mut.medium = cor(d.mut$median.Pn, d.medium$median.Pn)
+r.exp.mut = cor(d.exp$median.Pn[1:100], d.mut$median.Pn[1:100])
+r.exp.medium = cor(d.exp$median.Pn[1:100], d.medium$median.Pn[1:100])
+r.mut.medium = cor(d.mut$median.Pn[1:100], d.medium$median.Pn[1:100])
 
 # save data
-CA.mean.exp = d.exp$median.Pn
-CA.mean.mut = d.mut$median.Pn
-CA.mean.medium = d.medium$median.Pn
+CA.mean.exp = d.exp$median.Pn[1:100]
+CA.mean.mut = d.mut$median.Pn[1:100]
+CA.mean.medium = d.medium$median.Pn[1:100]
 
@@
 # calculate cors
-r.exp.mut = cor(d.exp$median.Pn, d.mut$median.Pn)
-r.exp.medium = cor(d.exp$median.Pn, d.medium$median.Pn)
-r.mut.medium = cor(d.mut$median.Pn, d.medium$median.Pn)
+r.exp.mut = cor(d.exp$median.Pn[1:100], d.mut$median.Pn[1:100])
+r.exp.medium = cor(d.exp$median.Pn[1:100], d.medium$median.Pn[1:100])
+r.mut.medium = cor(d.mut$median.Pn[1:100], d.medium$median.Pn[1:100])
 
 # save data
-CM.mean.exp = d.exp$median.Pn
-CM.mean.mut = d.mut$median.Pn
-CM.mean.medium = d.medium$median.Pn
+CM.mean.exp = d.exp$median.Pn[1:100]
+CM.mean.mut = d.mut$median.Pn[1:100]
+CM.mean.medium = d.medium$median.Pn[1:100]
 
@@
 # calculate cors
-r.exp.mut = cor(d.exp$mean.nH, d.mut$mean.nH)
-r.exp.medium = cor(d.exp$mean.nH, d.medium$mean.nH)
-r.mut.medium = cor(d.mut$mean.nH, d.medium$mean.nH)
+r.exp.mut = cor(d.exp$mean.nH[1:100], d.mut$mean.nH[1:100])
+r.exp.medium = cor(d.exp$mean.nH[1:100], d.medium$mean.nH[1:100])
+r.mut.medium = cor(d.mut$mean.nH[1:100], d.medium$mean.nH[1:100])
 
 # save data
-CA.mean.exp = d.exp$mean.nH
-CA.mean.mut = d.mut$mean.nH
-CA.mean.medium = d.medium$mean.nH
+CA.mean.exp = d.exp$mean.nH[1:100]
+CA.mean.mut = d.mut$mean.nH[1:100]
+CA.mean.medium = d.medium$mean.nH[1:100]
 
@@
 # calculate cors
-r.exp.mut = cor(d.exp$mean.nH, d.mut$mean.nH)
-r.exp.medium = cor(d.exp$mean.nH, d.medium$mean.nH)
-r.mut.medium = cor(d.mut$mean.nH, d.medium$mean.nH)
+r.exp.mut = cor(d.exp$mean.nH[1:100], d.mut$mean.nH[1:100])
+r.exp.medium = cor(d.exp$mean.nH[1:100], d.medium$mean.nH[1:100])
+r.mut.medium = cor(d.mut$mean.nH[1:100], d.medium$mean.nH[1:100])
 
 # save data
-CM.mean.exp = d.exp$mean.nH
-CM.mean.mut = d.mut$mean.nH
-CM.mean.medium = d.medium$mean.nH
+CM.mean.exp = d.exp$mean.nH[1:100]
+CM.mean.mut = d.mut$mean.nH[1:100]
+CM.mean.medium = d.medium$mean.nH[1:100]
 

### 2017-05-10 comparison_R0.Rmd
charla 11-5-17

@@
 ## calculate corelations
-r.p.accept.mut.CN = cor(p.accept.mut, CN)
+r.p.accept.mut.CN = cor(p.accept.mut, log(CN))
 r.p.accept.mut.score = cor(p.accept.mut, score)
-r.score.CN = cor(score, CN)
-
-cor.df = data.frame("Comparison R0.1" = c("log(paccept no-selection) vs CN", "log(paccept no-selection) vs score", "score vs CN"),
+r.score.CN = cor(score, log(CN))
+
+cor.df = data.frame("Comparison R0.1" = c("paccept no-selection vs log(CN)", "paccept no-selection vs score", "score vs log(CN)"),
                     "R" = c(r.p.accept.mut.CN , r.p.accept.mut.score, r.score.CN))
@@
 ## calculate corelations
-r.p.accept.medium.sel.CN = cor(log(p.accept.medium.sel), CN)
-r.p.accept.medium.sel.score = cor(log(p.accept.medium.sel), score)
-r.score.CN = cor(score, CN)
-
-cor.df = data.frame("Comparison R0.1" = c("log(paccept selection) vs CN", "log(paccept selection) vs score", "score vs CN"),
+r.p.accept.medium.sel.CN = cor(p.accept.medium.sel, log(CN))
+r.p.accept.medium.sel.score = cor(p.accept.medium.sel, score)
+r.score.CN = cor(score, log(CN))
+
+cor.df = data.frame("Comparison R0.1" = c("paccept selection vs log(CN)", "paccept selection vs score", "score vs log(CN)"),
                     "R" = c(r.p.accept.medium.sel.CN , r.p.accept.medium.sel.score, r.score.CN))
@@
 ## calculate corelations
-r.p.accept.mut.CN = cor(p.accept.mut, CN)
+r.p.accept.mut.CN = cor(p.accept.mut, log(CN))
 r.p.accept.mut.score = cor(p.accept.mut, score)
-r.score.CN = cor(score, CN)
-
-cor.df = data.frame("Comparison R0.2" = c("log(paccept no-selection) vs CN", "log(paccept no-selection) vs score", "score vs CN"),
+r.score.CN = cor(score, log(CN))
+
+cor.df = data.frame("Comparison R0.2" = c("paccept no-selection vs log(CN)", "paccept no-selection vs score", "score vs log(CN)"),
                     "R" = c(r.p.accept.mut.CN , r.p.accept.mut.score, r.score.CN))
@@
 ## calculate corelations
-r.p.accept.medium.sel.CN = cor(log(p.accept.medium.sel), CN)
-r.p.accept.medium.sel.score = cor(log(p.accept.medium.sel), score)
-r.score.CN = cor(score, CN)
-
-cor.df = data.frame("Comparison R0.2" = c("log(paccept selection) vs CN", "log(paccept selection) vs score", "score vs CN"),
+r.p.accept.medium.sel.CN = cor(p.accept.medium.sel, log(CN))
+r.p.accept.medium.sel.score = cor(p.accept.medium.sel, score)
+r.score.CN = cor(score, log(CN))
+
+cor.df = data.frame("Comparison R0.2" = c("paccept selection vs log(CN)", "paccept selection vs score", "score vs log(CN)"),
                     "R" = c(r.p.accept.medium.sel.CN , r.p.accept.medium.sel.score, r.score.CN))
@@
 # calculate cors
-r.exp.mut = cor(d.exp$median.Pn, d.mut$median.Pn)
-r.exp.medium = cor(d.exp$median.Pn, d.medium$median.Pn)
-r.mut.medium = cor(d.mut$median.Pn, d.medium$median.Pn)
+r.exp.mut = cor(d.exp$median.Pn[1:100], d.mut$median.Pn[1:100])
+r.exp.medium = cor(d.exp$median.Pn[1:100], d.medium$median.Pn[1:100])
+r.mut.medium = cor(d.mut$median.Pn[1:100], d.medium$median.Pn[1:100])
 
 # save data
-R0.1.mean.exp = d.exp$median.Pn
-R0.1.mean.mut = d.mut$median.Pn
-R0.1.mean.medium = d.medium$median.Pn
+R0.1.mean.exp = d.exp$median.Pn[1:100]
+R0.1.mean.mut = d.mut$median.Pn[1:100]
+R0.1.mean.medium = d.medium$median.Pn[1:100]
 
@@
 # calculate cors
-r.exp.mut = cor(d.exp$median.Pn, d.mut$median.Pn)
-r.exp.medium = cor(d.exp$median.Pn, d.medium$median.Pn)
-r.mut.medium = cor(d.mut$median.Pn, d.medium$median.Pn)
+r.exp.mut = cor(d.exp$median.Pn[1:100], d.mut$median.Pn[1:100])
+r.exp.medium = cor(d.exp$median.Pn[1:100], d.medium$median.Pn[1:100])
+r.mut.medium = cor(d.mut$median.Pn[1:100], d.medium$median.Pn[1:100])
 
 # save data
-R0.2.mean.exp = d.exp$median.Pn
-R0.2.mean.mut = d.mut$median.Pn
-R0.2.mean.medium = d.medium$median.Pn
+R0.2.mean.exp = d.exp$median.Pn[1:100]
+R0.2.mean.mut = d.mut$median.Pn[1:100]
+R0.2.mean.medium = d.medium$median.Pn[1:100]
 
@@
 # calculate cors
-r.exp.mut = cor(d.exp$mean.nH, d.mut$mean.nH)
-r.exp.medium = cor(d.exp$mean.nH, d.medium$mean.nH)
-r.mut.medium = cor(d.mut$mean.nH, d.medium$mean.nH)
+r.exp.mut = cor(d.exp$mean.nH[1:100], d.mut$mean.nH[1:100])
+r.exp.medium = cor(d.exp$mean.nH[1:100], d.medium$mean.nH[1:100])
+r.mut.medium = cor(d.mut$mean.nH[1:100], d.medium$mean.nH[1:100])
 
 # save data
-R0.1.mean.exp = d.exp$mean.nH
-R0.1.mean.mut = d.mut$mean.nH
-R0.1.mean.medium = d.medium$mean.nH
+R0.1.mean.exp = d.exp$mean.nH[1:100]
+R0.1.mean.mut = d.mut$mean.nH[1:100]
+R0.1.mean.medium = d.medium$mean.nH[1:100]
 
@@
 # calculate cors
-r.exp.mut = cor(d.exp$mean.nH, d.mut$mean.nH)
-r.exp.medium = cor(d.exp$mean.nH, d.medium$mean.nH)
-r.mut.medium = cor(d.mut$mean.nH, d.medium$mean.nH)
+r.exp.mut = cor(d.exp$mean.nH[1:100], d.mut$mean.nH[1:100])
+r.exp.medium = cor(d.exp$mean.nH[1:100], d.medium$mean.nH[1:100])
+r.mut.medium = cor(d.mut$mean.nH[1:100], d.medium$mean.nH[1:100])
 
 # save data
-R0.2.mean.exp = d.exp$mean.nH
-R0.2.mean.mut = d.mut$mean.nH
-R0.2.mean.medium = d.medium$mean.nH
+R0.2.mean.exp = d.exp$mean.nH[1:100]
+R0.2.mean.mut = d.mut$mean.nH[1:100]
+R0.2.mean.medium = d.medium$mean.nH[1:100]
 

### 2017-05-10 comparison_families.Rmd
charla 11-5-17

---
title: "Structural and Dybamical Divergence Analysis -  Comparisons"
output: html_document
---

# Introduction
We study the evolutionary divergence of proteins using the mutational model LF-ENM and the selection model Stress Model. We compare simulated mutants with experimental data. 
In this report we compare the results obtained for diferrent families, using different R0s, and considering two different enm: CA (one node per site enm model: CA) and CM (two nodes per site enm model: CA and CM of side chains). 
R0 used were 7.5, 10 and 12.5 for CA and 5, 7.5 and 10 for CM.

```{r setup, include = FALSE}
# set chunk options
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r load-packages}
# load packages
library(ggplot2)
library(reshape2)
library(bio3d)
library(plyr)

# load functions
source(file.path(data.dir, "multiplot.R"))
source(file.path(data.dir, "my-functions.R"))
```
We analyzed the following families:

```{r input-families}
# read input
input.fname <- "input_MainReport.csv"
input <- read.csv(input.fname)
families <- input$family
print(as.character(families))
```
# Results

```{r calculate-correlations-CA}

# input
R0S = c(7.5, 10, 12.5)
data.dir = paste("OUT/out_subset_CA_ANM", sep = "")

number.R0 = length(R0S)
number.families = length(families)

cc.z.RSD.exp.mut = matrix(ncol = number.R0, nrow = number.families)
cc.z.RSD.exp.medium = matrix(ncol = number.R0, nrow = number.families)
cc.z.RSD.mut.medium = matrix(ncol = number.R0, nrow = number.families)

cc.Pn.exp.mut = matrix(ncol = number.R0, nrow = number.families)
cc.Pn.exp.medium = matrix(ncol = number.R0, nrow = number.families)
cc.Pn.mut.medium = matrix(ncol = number.R0, nrow = number.families)

cc.Pn.100.exp.mut = matrix(ncol = number.R0, nrow = number.families)
cc.Pn.100.exp.medium = matrix(ncol = number.R0, nrow = number.families)
cc.Pn.100.mut.medium = matrix(ncol = number.R0, nrow = number.families)

cc.MSF.exp.mut = matrix(ncol = number.R0, nrow = number.families)
cc.MSF.exp.medium = matrix(ncol = number.R0, nrow = number.families)
cc.MSF.mut.medium = matrix(ncol = number.R0, nrow = number.families)

cc.nH.exp.mut = matrix(ncol = number.R0, nrow = number.families)
cc.nH.exp.medium = matrix(ncol = number.R0, nrow = number.families)
cc.nH.mut.medium = matrix(ncol = number.R0, nrow = number.families)

cc.nH.100.exp.mut = matrix(ncol = number.R0, nrow = number.families)
cc.nH.100.exp.medium = matrix(ncol = number.R0, nrow = number.families)
cc.nH.100.mut.medium = matrix(ncol = number.R0, nrow = number.families)

# satart a loop for each family
for (f in (1:nrow(input))) { 
  family <- as.character(input$family)[f]
  type <- as.character(input$type)[f]
  p.ref <- as.character(input$p.ref)[f]
  enm <- as.character(input$enm)[f]
  n.mut.p <- input$n.mut.p[f]
  R0.CA = input$R0.CA[f]
  R0.CM = input$R0.CM[f]
  chain.p.ref <- as.character(input$chain.p.ref)[f]

  for (R0 in (R0S)) {

    ### z.RSD ###

    # set input filenames
    dri2.exp.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.exp.norm.dr.squarei.csv", sep = ""))
    dri2.medium.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_medium.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
    dri2.mut.fname = file.path(data.dir,paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))

    # read data
    dri2.exp = read.csv(dri2.exp.fname, header = T)
    dri2.mut = read.csv(dri2.mut.fname, header = T)
    dri2.medium = read.csv(dri2.medium.fname, header = T)
    n.sites = length(dri2.exp)

    # prepare data
    rownames(dri2.exp) = paste("mut", rownames(dri2.exp), sep = "")
    rownames(dri2.mut) = paste("mut", rownames(dri2.mut), sep = "")
    rownames(dri2.medium) = paste("mut", rownames(dri2.medium), sep = "")

    tdri2.exp = as.data.frame(t(as.matrix(dri2.exp)))
    tdri2.mut = as.data.frame(t(as.matrix(dri2.mut)))
    tdri2.medium = as.data.frame(t(as.matrix(dri2.medium)))

    site.info = seq(1:length(dri2.mut))

    tdri2.exp = cbind(site.info, tdri2.exp)
    tdri2.mut = cbind(site.info, tdri2.mut)
    tdri2.medium = cbind(site.info, tdri2.medium)

    siteComparison.exp = melt(tdri2.exp, id.vars = c("site.info"), variable.name = "protein", value.name = "dri2")
    siteComparison.mut = melt(tdri2.mut, id.vars = c("site.info"), variable.name = "protein", value.name = "dri2")
    siteComparison.medium = melt(tdri2.medium, id.vars = c("site.info"), variable.name = "protein", value.name = "dri2")

    # bluild the data.frame
    siteComparison.all.datasets = rbind(data.frame("dataset" = "exp", siteComparison.exp),
                                        data.frame("dataset" = "mut", siteComparison.mut),
                                        data.frame("dataset" = "medium", siteComparison.medium))

    siteComparison.all.datasets = ddply(siteComparison.all.datasets, c("dataset", "protein"), mutate,
                                        "n.SD" = dri2/mean(dri2, na.rm = T),
                                        "z.SD" = vscale(dri2),
                                        "RSD" = sqrt(dri2),
                                        "n.RSD" = RSD/mean(RSD, na.rm = T),
                                        "z.RSD" = vscale(RSD))

    dat = siteComparison.all.datasets
    dat$dataset = revalue(dat$dataset, c("medium" = "selection"))
    dat$dataset = revalue(dat$dataset, c("mut" = "no-selection"))

    ## dat with means and standard errors
    d = ddply(dat,c("dataset", "site.info"), function(x) {
        mean.z.RSD = mean(x$z.RSD, na.rm = T)
        ndata = sum(!is.na(x$z.RSD))
        se.z.RSD = sd(x$z.RSD, na.rm = T) / sqrt(ndata)
        data.frame(mean.z.RSD, ndata, se.z.RSD)
    })

    # calculate correlations berween profiles
    d.exp = subset(d, dataset == "exp")
    d.mut = subset(d, dataset == "no-selection")
    d.medium = subset(d, dataset == "selection")

    r.exp.mut = cor(d.exp$mean.z.RSD, d.mut$mean.z.RSD)
    r.exp.medium = cor(d.exp$mean.z.RSD, d.medium$mean.z.RSD)
    r.mut.medium = cor(d.mut$mean.z.RSD, d.medium$mean.z.RSD)

    cc.z.RSD.exp.mut[which(input$family == family), which(R0S == R0)] = r.exp.mut
    cc.z.RSD.exp.medium[which(input$family == family), which(R0S == R0)] = r.exp.medium
    cc.z.RSD.mut.medium[which(input$family == family), which(R0S == R0)] = r.mut.medium

    ### Pn ###

    # set input filenames
    Pn.exp.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.exp.Pn.csv", sep = ""))
    Pn.medium.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_medium.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
    Pn.mut.fname = file.path(data.dir,paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))

    # prepare the data
    Pn.exp = read.csv(Pn.exp.fname, header = T)
    rownames(Pn.exp) = paste("mut", rownames(Pn.exp), sep = "")
    Pn.mut = read.csv(Pn.mut.fname, header = T)
    rownames(Pn.mut) = paste("mut", rownames(Pn.mut), sep = "")
    Pn.medium = read.csv(Pn.medium.fname, header = T)
    rownames(Pn.medium) = paste("mut", rownames(Pn.medium), sep = "")

    mode = seq(ncol(Pn.medium))

    # Prepare modeComparison
    tPn.medium = as.data.frame(t(as.matrix(Pn.medium)))
    tPn.medium = cbind(data.frame("mode" = mode), tPn.medium)
    modeComparison.medium = melt(tPn.medium, "mode", variable.name = "protein", value.name = "Pn")
    modeComparison.medium = ddply(modeComparison.medium, "protein", mutate, "Pn" = Pn / mean(Pn, na.rm = T))

    tPn.mut = as.data.frame(t(as.matrix(Pn.mut)))
    tPn.mut = cbind(data.frame("mode" = mode), tPn.mut)
    modeComparison.mut = melt(tPn.mut, "mode", variable.name = "protein", value.name = "Pn")
    modeComparison.mut = ddply(modeComparison.mut, "protein", mutate, "Pn" = Pn / mean(Pn, na.rm = T))

    tPn.exp = as.data.frame(t(as.matrix(Pn.exp)))
    tPn.exp = cbind(data.frame("mode" = mode), tPn.exp)
    modeComparison.exp = melt(tPn.exp, "mode", variable.name = "protein", value.name = "Pn")
    modeComparison.exp = ddply(modeComparison.exp, "protein", mutate, "Pn" = Pn / mean(Pn, na.rm = T))

    # modeComparison.exp has NA's because for proteins with gaps when using Keff there're less modes
    #print("Warning: modeComparison.exp <- na.omit(modeComparison.exp)")
    modeComparison.exp <- na.omit(modeComparison.exp)
    modeComparison.medium <- na.omit(modeComparison.medium)
    modeComparison.mut <- na.omit(modeComparison.mut)

    modeComparison.all.datasets = rbind(data.frame("dataset" = "exp", modeComparison.exp),
                                        data.frame("dataset" = "mut", modeComparison.mut),
                                        data.frame("dataset" = "medium", modeComparison.medium))

    dat = modeComparison.all.datasets
    dat$dataset = revalue(dat$dataset, c("medium" = "selection"))
    dat$dataset = revalue(dat$dataset, c("mut" = "no-selection"))

    # calculate dataset of medians
    d = ddply(dat,c("dataset", "mode"), function(x) {
        median.Pn = median(x$Pn)
        data.frame(median.Pn)
    })

    # calculate correlations berween profiles
    d.exp = subset(d, dataset == "exp")
    d.mut = subset(d, dataset == "no-selection")
    d.medium = subset(d, dataset == "selection")

    r.exp.mut = cor(d.exp$median.Pn, d.mut$median.Pn)
    r.exp.medium = cor(d.exp$median.Pn, d.medium$median.Pn)
    r.mut.medium = cor(d.mut$median.Pn, d.medium$median.Pn)

    cc.Pn.exp.mut[which(input$family == family), which(R0S == R0)] = r.exp.mut
    cc.Pn.exp.medium[which(input$family == family), which(R0S == R0)] = r.exp.medium
    cc.Pn.mut.medium[which(input$family == family), which(R0S == R0)] = r.mut.medium

    # 100 modes
    r.exp.mut = cor(d.exp$median.Pn[1:100], d.mut$median.Pn[1:100])
    r.exp.medium = cor(d.exp$median.Pn[1:100], d.medium$median.Pn[1:100])
    r.mut.medium = cor(d.mut$median.Pn[1:100], d.medium$median.Pn[1:100])

    cc.Pn.100.exp.mut[which(input$family == family), which(R0S == R0)] = r.exp.mut
    cc.Pn.100.exp.medium[which(input$family == family), which(R0S == R0)] = r.exp.medium
    cc.Pn.100.mut.medium[which(input$family == family), which(R0S == R0)] = r.mut.medium

    ### MSF ###

    # set input filenames
    square.dif.MSF.exp.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.exp.square.dif.MSF.csv", sep = ""))
    square.dif.MSF.medium.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_medium.sel_K.analysis_Keff_out_m.theo.square.dif.MSF.csv", sep = ""))
    square.dif.MSF.mut.fname = file.path(data.dir,paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.square.dif.MSF.csv", sep = ""))

    # prepare the data
    square.dif.MSF.exp = read.csv(square.dif.MSF.exp.fname, header = T)
    rownames(square.dif.MSF.exp) = paste("mut", rownames(square.dif.MSF.exp), sep = "")
    square.dif.MSF.mut = read.csv(square.dif.MSF.mut.fname, header = T)
    rownames(square.dif.MSF.mut) = paste("mut", rownames(square.dif.MSF.mut), sep = "")
    square.dif.MSF.medium = read.csv(square.dif.MSF.medium.fname, header = T)
    rownames(square.dif.MSF.medium) = paste("mut", rownames(square.dif.MSF.medium), sep = "")

    site = seq(ncol(square.dif.MSF.medium))

    # Prepare siteComparison
    tsquare.dif.MSF.medium = as.data.frame(t(as.matrix(square.dif.MSF.medium)))
    tsquare.dif.MSF.medium = cbind(data.frame("site" = site), tsquare.dif.MSF.medium)
    siteComparison.medium = melt(tsquare.dif.MSF.medium, "site", variable.name = "protein", value.name = "square.dif.MSF")

    tsquare.dif.MSF.mut = as.data.frame(t(as.matrix(square.dif.MSF.mut)))
    tsquare.dif.MSF.mut = cbind(data.frame("site" = site), tsquare.dif.MSF.mut)
    siteComparison.mut = melt(tsquare.dif.MSF.mut, "site", variable.name = "protein", value.name = "square.dif.MSF")

    tsquare.dif.MSF.exp = as.data.frame(t(as.matrix(square.dif.MSF.exp)))
    tsquare.dif.MSF.exp = cbind(data.frame("site" = site), tsquare.dif.MSF.exp)
    siteComparison.exp = melt(tsquare.dif.MSF.exp, "site", variable.name = "protein", value.name = "square.dif.MSF")

    siteComparison.all.datasets = rbind(data.frame("dataset" = "exp", siteComparison.exp),
                                        data.frame("dataset" = "mut", siteComparison.mut),
                                        data.frame("dataset" = "medium", siteComparison.medium))

    siteComparison.all.datasets = ddply(siteComparison.all.datasets, c("dataset", "protein"), mutate,
                                             "r.SDF" = rank(square.dif.MSF, na.last = "keep"))

    dat = siteComparison.all.datasets
    dat$dataset = revalue(dat$dataset, c("medium" = "selection"))
    dat$dataset = revalue(dat$dataset, c("mut" = "no-selection"))

    # calculate dataset of means
    d = ddply(dat, c("dataset", "site"), function(x) {
        mean.r.SDF = mean(x$r.SDF, na.rm = T)
        data.frame(mean.r.SDF)
    })

    # calculate correlations berween profiles
    d.exp = subset(d, dataset == "exp")
    d.mut = subset(d, dataset == "no-selection")
    d.medium = subset(d, dataset == "selection")

    r.exp.mut = cor(d.exp$mean.r.SDF, d.mut$mean.r.SDF)
    r.exp.medium = cor(d.exp$mean.r.SDF, d.medium$mean.r.SDF)
    r.mut.medium = cor(d.mut$mean.r.SDF, d.medium$mean.r.SDF)

    cc.MSF.exp.mut[which(input$family == family), which(R0S == R0)] = r.exp.mut
    cc.MSF.exp.medium[which(input$family == family), which(R0S == R0)] = r.exp.medium
    cc.MSF.mut.medium[which(input$family == family), which(R0S == R0)] = r.mut.medium

    ### nH ###
    # set input filenames
    nH.exp.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.exp.nH.csv", sep = ""))
    nH.medium.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_medium.sel_K.analysis_Keff_out_m.theo.nH.csv", sep = ""))
    nH.mut.fname = file.path(data.dir,paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.nH.csv", sep = ""))

    # prepare the data
    nH.exp = read.csv(nH.exp.fname, header = T)
    rownames(nH.exp) = paste("mut", rownames(nH.exp), sep = "")
    nH.mut = read.csv(nH.mut.fname, header = T)
    rownames(nH.mut) = paste("mut", rownames(nH.mut), sep = "")
    nH.medium = read.csv(nH.medium.fname, header = T)
    rownames(nH.medium) = paste("mut", rownames(nH.medium), sep = "")

    mode = seq(ncol(nH.medium))

    # Prepare modeComparison
    tnH.medium = as.data.frame(t(as.matrix(nH.medium)))
    tnH.medium = cbind(data.frame("mode" = mode), tnH.medium)
    modeComparison.medium = melt(tnH.medium, "mode", variable.name = "protein", value.name = "nH")
    modeComparison.medium = ddply(modeComparison.medium, "protein", mutate, "nH" = nH / mean(nH, na.rm = T))

    tnH.mut = as.data.frame(t(as.matrix(nH.mut)))
    tnH.mut = cbind(data.frame("mode" = mode), tnH.mut)
    modeComparison.mut = melt(tnH.mut, "mode", variable.name = "protein", value.name = "nH")
    modeComparison.mut = ddply(modeComparison.mut, "protein", mutate, "nH" = nH / mean(nH, na.rm = T))

    tnH.exp = as.data.frame(t(as.matrix(nH.exp)))
    tnH.exp = cbind(data.frame("mode" = mode), tnH.exp)
    modeComparison.exp = melt(tnH.exp, "mode", variable.name = "protein", value.name = "nH")
    modeComparison.exp = ddply(modeComparison.exp, "protein", mutate, "nH" = nH / mean(nH, na.rm = T))

    # modeComparison.exp has NA's because for proteins with gaps when using Keff there're less modes
    #print("Warning: modeComparison.exp <- na.omit(modeComparison.exp)")
    modeComparison.exp <- na.omit(modeComparison.exp)
    modeComparison.medium <- na.omit(modeComparison.medium)
    modeComparison.mut <- na.omit(modeComparison.mut)

    modeComparison.all.datasets = rbind(data.frame("dataset" = "exp", modeComparison.exp),
                                        data.frame("dataset" = "mut", modeComparison.mut),
                                        data.frame("dataset" = "medium", modeComparison.medium))

    dat = modeComparison.all.datasets
    dat$dataset = revalue(dat$dataset, c("medium" = "selection"))
    dat$dataset = revalue(dat$dataset, c("mut" = "no-selection"))

    # calculate dataset of means
    d = ddply(dat,c("dataset", "mode"), function(x) {
        mean.nH = mean(x$nH)
        data.frame(mean.nH)
    })

    # calculate correlations berween profiles
    d.exp = subset(d, dataset == "exp")
    d.mut = subset(d, dataset == "no-selection")
    d.medium = subset(d, dataset == "selection")

    r.exp.mut = cor(d.exp$mean.nH, d.mut$mean.nH)
    r.exp.medium = cor(d.exp$mean.nH, d.medium$mean.nH)
    r.mut.medium = cor(d.mut$mean.nH, d.medium$mean.nH)

    cc.nH.exp.mut[which(input$family == family), which(R0S == R0)] = r.exp.mut
    cc.nH.exp.medium[which(input$family == family), which(R0S == R0)] = r.exp.medium
    cc.nH.mut.medium[which(input$family == family), which(R0S == R0)] = r.mut.medium

    # 100 modes
    r.exp.mut = cor(d.exp$mean.nH[1:100], d.mut$mean.nH[1:100])
    r.exp.medium = cor(d.exp$mean.nH[1:100], d.medium$mean.nH[1:100])
    r.mut.medium = cor(d.mut$mean.nH[1:100], d.medium$mean.nH[1:100])

    cc.nH.100.exp.mut[which(input$family == family), which(R0S == R0)] = r.exp.mut
    cc.nH.100.exp.medium[which(input$family == family), which(R0S == R0)] = r.exp.medium
    cc.nH.100.mut.medium[which(input$family == family), which(R0S == R0)] = r.mut.medium
  }
}

cc.z.RSD = data.frame(cc.z.RSD.exp.mut, cc.z.RSD.exp.medium, cc.z.RSD.mut.medium)
cc.z.RSD = cc.z.RSD
cc.z.RSD = rbind(cc.z.RSD, colMeans(cc.z.RSD))
family = as.character(input$family)
cc.z.RSD_CA = data.frame(c(family, "mean"), cc.z.RSD)
colnames(cc.z.RSD_CA) = c("family", paste("exp-mut-R0.", seq(1:number.R0), sep = ""), paste("exp-sel-R0.", seq(1:number.R0), sep = ""), paste("mut-sel-R0.", seq(1:number.R0), sep = ""))

write.csv(cc.z.RSD_CA, file = "cc_z.RSD_CA.csv")

cc.Pn = data.frame(cc.Pn.exp.mut, cc.Pn.exp.medium, cc.Pn.mut.medium)
cc.Pn = cc.Pn
cc.Pn = rbind(cc.Pn, colMeans(cc.Pn))
family = as.character(input$family)
cc.Pn_CA = data.frame(c(family, "mean"), cc.Pn)
colnames(cc.Pn_CA) = c("family", paste("exp-mut-R0.", seq(1:number.R0), sep = ""), paste("exp-sel-R0.", seq(1:number.R0), sep = ""), paste("mut-sel-R0.", seq(1:number.R0), sep = ""))

write.csv(cc.Pn_CA, file = "cc_Pn_CA.csv")

cc.Pn.100 = data.frame(cc.Pn.100.exp.mut, cc.Pn.100.exp.medium, cc.Pn.100.mut.medium)
cc.Pn.100 = cc.Pn.100
cc.Pn.100 = rbind(cc.Pn.100, colMeans(cc.Pn.100))
family = as.character(input$family)
cc.Pn.100_CA = data.frame(c(family, "mean"), cc.Pn.100)
colnames(cc.Pn.100_CA) = c("family", paste("exp-mut-R0.", seq(1:number.R0), sep = ""), paste("exp-sel-R0.", seq(1:number.R0), sep = ""), paste("mut-sel-R0.", seq(1:number.R0), sep = ""))

write.csv(cc.Pn.100_CA, file = "cc_Pn_100_CA.csv")

cc.MSF = data.frame(cc.MSF.exp.mut, cc.MSF.exp.medium, cc.MSF.mut.medium)
cc.MSF = cc.MSF
cc.MSF = rbind(cc.MSF, colMeans(cc.MSF))
family = as.character(input$family)
cc.MSF_CA = data.frame(c(family, "mean"), cc.MSF)
colnames(cc.MSF_CA) = c("family", paste("exp-mut-R0.", seq(1:number.R0), sep = ""), paste("exp-sel-R0.", seq(1:number.R0), sep = ""), paste("mut-sel-R0.", seq(1:number.R0), sep = ""))

write.csv(cc.MSF_CA, file = "cc_MSF_CA.csv")

cc.nH = data.frame(cc.nH.exp.mut, cc.nH.exp.medium, cc.nH.mut.medium)
cc.nH = cc.nH
cc.nH = rbind(cc.nH, colMeans(cc.nH))
family = as.character(input$family)
cc.nH_CA = data.frame(c(family, "mean"), cc.nH)
colnames(cc.nH_CA) = c("family", paste("exp-mut-R0.", seq(1:number.R0), sep = ""), paste("exp-sel-R0.", seq(1:number.R0), sep = ""), paste("mut-sel-R0.", seq(1:number.R0), sep = ""))

write.csv(cc.nH_CA, file = "cc_nH_CA.csv")

cc.nH.100 = data.frame(cc.nH.100.exp.mut, cc.nH.100.exp.medium, cc.nH.100.mut.medium)
cc.nH.100 = cc.nH.100
cc.nH.100 = rbind(cc.nH.100, colMeans(cc.nH.100))
family = as.character(input$family)
cc.nH.100_CA = data.frame(c(family, "mean"), cc.nH.100)
colnames(cc.nH.100_CA) = c("family", paste("exp-mut-R0.", seq(1:number.R0), sep = ""), paste("exp-sel-R0.", seq(1:number.R0), sep = ""), paste("mut-sel-R0.", seq(1:number.R0), sep = ""))

write.csv(cc.nH.100_CA, file = "cc_nH_100_CA.csv")
```

```{r calculate-correlations-CM}

# input
R0S = c(5, 7.5, 10)
data.dir = paste("OUT/out_subset_CM_ANM", sep = "")

cc.z.RSD.exp.mut = matrix(ncol = number.R0, nrow = number.families)
cc.z.RSD.exp.medium = matrix(ncol = number.R0, nrow = number.families)
cc.z.RSD.mut.medium = matrix(ncol = number.R0, nrow = number.families)

cc.Pn.exp.mut = matrix(ncol = number.R0, nrow = number.families)
cc.Pn.exp.medium = matrix(ncol = number.R0, nrow = number.families)
cc.Pn.mut.medium = matrix(ncol = number.R0, nrow = number.families)

cc.Pn.100.exp.mut = matrix(ncol = number.R0, nrow = number.families)
cc.Pn.100.exp.medium = matrix(ncol = number.R0, nrow = number.families)
cc.Pn.100.mut.medium = matrix(ncol = number.R0, nrow = number.families)

cc.MSF.exp.mut = matrix(ncol = number.R0, nrow = number.families)
cc.MSF.exp.medium = matrix(ncol = number.R0, nrow = number.families)
cc.MSF.mut.medium = matrix(ncol = number.R0, nrow = number.families)

cc.nH.exp.mut = matrix(ncol = number.R0, nrow = number.families)
cc.nH.exp.medium = matrix(ncol = number.R0, nrow = number.families)
cc.nH.mut.medium = matrix(ncol = number.R0, nrow = number.families)

cc.nH.100.exp.mut = matrix(ncol = number.R0, nrow = number.families)
cc.nH.100.exp.medium = matrix(ncol = number.R0, nrow = number.families)
cc.nH.100.mut.medium = matrix(ncol = number.R0, nrow = number.families)

# satart a loop for each family
for (f in (1:nrow(input))) { 
  family <- as.character(input$family)[f]
  type <- as.character(input$type)[f]
  p.ref <- as.character(input$p.ref)[f]
  enm <- as.character(input$enm)[f]
  n.mut.p <- input$n.mut.p[f]
  R0.CA = input$R0.CA[f]
  R0.CM = input$R0.CM[f]
  chain.p.ref <- as.character(input$chain.p.ref)[f]

  for (R0 in (R0S)) {

    ### z.RSD ###

    # set input filenames
    dri2.exp.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.exp.norm.dr.squarei.csv", sep = ""))
    dri2.medium.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_medium.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
    dri2.mut.fname = file.path(data.dir,paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))

    # read data
    dri2.exp = read.csv(dri2.exp.fname, header = T)
    dri2.mut = read.csv(dri2.mut.fname, header = T)
    dri2.medium = read.csv(dri2.medium.fname, header = T)
    n.sites = length(dri2.exp)

    # prepare data
    rownames(dri2.exp) = paste("mut", rownames(dri2.exp), sep = "")
    rownames(dri2.mut) = paste("mut", rownames(dri2.mut), sep = "")
    rownames(dri2.medium) = paste("mut", rownames(dri2.medium), sep = "")

    tdri2.exp = as.data.frame(t(as.matrix(dri2.exp)))
    tdri2.mut = as.data.frame(t(as.matrix(dri2.mut)))
    tdri2.medium = as.data.frame(t(as.matrix(dri2.medium)))

    site.info = seq(1:length(dri2.mut))

    tdri2.exp = cbind(site.info, tdri2.exp)
    tdri2.mut = cbind(site.info, tdri2.mut)
    tdri2.medium = cbind(site.info, tdri2.medium)

    siteComparison.exp = melt(tdri2.exp, id.vars = c("site.info"), variable.name = "protein", value.name = "dri2")
    siteComparison.mut = melt(tdri2.mut, id.vars = c("site.info"), variable.name = "protein", value.name = "dri2")
    siteComparison.medium = melt(tdri2.medium, id.vars = c("site.info"), variable.name = "protein", value.name = "dri2")

    # bluild the data.frame
    siteComparison.all.datasets = rbind(data.frame("dataset" = "exp", siteComparison.exp),
                                        data.frame("dataset" = "mut", siteComparison.mut),
                                        data.frame("dataset" = "medium", siteComparison.medium))

    siteComparison.all.datasets = ddply(siteComparison.all.datasets, c("dataset", "protein"), mutate,
                                        "n.SD" = dri2/mean(dri2, na.rm = T),
                                        "z.SD" = vscale(dri2),
                                        "RSD" = sqrt(dri2),
                                        "n.RSD" = RSD/mean(RSD, na.rm = T),
                                        "z.RSD" = vscale(RSD))

    dat = siteComparison.all.datasets
    dat$dataset = revalue(dat$dataset, c("medium" = "selection"))
    dat$dataset = revalue(dat$dataset, c("mut" = "no-selection"))

    ## dat with means and standard errors
    d = ddply(dat,c("dataset", "site.info"), function(x) {
        mean.z.RSD = mean(x$z.RSD, na.rm = T)
        ndata = sum(!is.na(x$z.RSD))
        se.z.RSD = sd(x$z.RSD, na.rm = T) / sqrt(ndata)
        data.frame(mean.z.RSD, ndata, se.z.RSD)
    })

    # calculate correlations berween profiles
    d.exp = subset(d, dataset == "exp")
    d.mut = subset(d, dataset == "no-selection")
    d.medium = subset(d, dataset == "selection")

    r.exp.mut = cor(d.exp$mean.z.RSD, d.mut$mean.z.RSD)
    r.exp.medium = cor(d.exp$mean.z.RSD, d.medium$mean.z.RSD)
    r.mut.medium = cor(d.mut$mean.z.RSD, d.medium$mean.z.RSD)

    cc.z.RSD.exp.mut[which(input$family == family), which(R0S == R0)] = r.exp.mut
    cc.z.RSD.exp.medium[which(input$family == family), which(R0S == R0)] = r.exp.medium
    cc.z.RSD.mut.medium[which(input$family == family), which(R0S == R0)] = r.mut.medium

    ### Pn ###

    # set input filenames
    Pn.exp.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.exp.Pn.csv", sep = ""))
    Pn.medium.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_medium.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
    Pn.mut.fname = file.path(data.dir,paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))

    # prepare the data
    Pn.exp = read.csv(Pn.exp.fname, header = T)
    rownames(Pn.exp) = paste("mut", rownames(Pn.exp), sep = "")
    Pn.mut = read.csv(Pn.mut.fname, header = T)
    rownames(Pn.mut) = paste("mut", rownames(Pn.mut), sep = "")
    Pn.medium = read.csv(Pn.medium.fname, header = T)
    rownames(Pn.medium) = paste("mut", rownames(Pn.medium), sep = "")

    mode = seq(ncol(Pn.medium))

    # Prepare modeComparison
    tPn.medium = as.data.frame(t(as.matrix(Pn.medium)))
    tPn.medium = cbind(data.frame("mode" = mode), tPn.medium)
    modeComparison.medium = melt(tPn.medium, "mode", variable.name = "protein", value.name = "Pn")
    modeComparison.medium = ddply(modeComparison.medium, "protein", mutate, "Pn" = Pn / mean(Pn, na.rm = T))

    tPn.mut = as.data.frame(t(as.matrix(Pn.mut)))
    tPn.mut = cbind(data.frame("mode" = mode), tPn.mut)
    modeComparison.mut = melt(tPn.mut, "mode", variable.name = "protein", value.name = "Pn")
    modeComparison.mut = ddply(modeComparison.mut, "protein", mutate, "Pn" = Pn / mean(Pn, na.rm = T))

    tPn.exp = as.data.frame(t(as.matrix(Pn.exp)))
    tPn.exp = cbind(data.frame("mode" = mode), tPn.exp)
    modeComparison.exp = melt(tPn.exp, "mode", variable.name = "protein", value.name = "Pn")
    modeComparison.exp = ddply(modeComparison.exp, "protein", mutate, "Pn" = Pn / mean(Pn, na.rm = T))

    # modeComparison.exp has NA's because for proteins with gaps when using Keff there're less modes
    #print("Warning: modeComparison.exp <- na.omit(modeComparison.exp)")
    modeComparison.exp <- na.omit(modeComparison.exp)
    modeComparison.medium <- na.omit(modeComparison.medium)
    modeComparison.mut <- na.omit(modeComparison.mut)

    modeComparison.all.datasets = rbind(data.frame("dataset" = "exp", modeComparison.exp),
                                        data.frame("dataset" = "mut", modeComparison.mut),
                                        data.frame("dataset" = "medium", modeComparison.medium))

    dat = modeComparison.all.datasets
    dat$dataset = revalue(dat$dataset, c("medium" = "selection"))
    dat$dataset = revalue(dat$dataset, c("mut" = "no-selection"))

    # calculate dataset of medians
    d = ddply(dat,c("dataset", "mode"), function(x) {
        median.Pn = median(x$Pn)
        data.frame(median.Pn)
    })

    # calculate correlations berween profiles
    d.exp = subset(d, dataset == "exp")
    d.mut = subset(d, dataset == "no-selection")
    d.medium = subset(d, dataset == "selection")

    r.exp.mut = cor(d.exp$median.Pn, d.mut$median.Pn)
    r.exp.medium = cor(d.exp$median.Pn, d.medium$median.Pn)
    r.mut.medium = cor(d.mut$median.Pn, d.medium$median.Pn)

    cc.Pn.exp.mut[which(input$family == family), which(R0S == R0)] = r.exp.mut
    cc.Pn.exp.medium[which(input$family == family), which(R0S == R0)] = r.exp.medium
    cc.Pn.mut.medium[which(input$family == family), which(R0S == R0)] = r.mut.medium

    # 100 modes
    r.exp.mut = cor(d.exp$median.Pn[1:100], d.mut$median.Pn[1:100])
    r.exp.medium = cor(d.exp$median.Pn[1:100], d.medium$median.Pn[1:100])
    r.mut.medium = cor(d.mut$median.Pn[1:100], d.medium$median.Pn[1:100])

    cc.Pn.100.exp.mut[which(input$family == family), which(R0S == R0)] = r.exp.mut
    cc.Pn.100.exp.medium[which(input$family == family), which(R0S == R0)] = r.exp.medium
    cc.Pn.100.mut.medium[which(input$family == family), which(R0S == R0)] = r.mut.medium

    ### MSF ###

    # set input filenames
    square.dif.MSF.exp.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.exp.square.dif.MSF.csv", sep = ""))
    square.dif.MSF.medium.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_medium.sel_K.analysis_Keff_out_m.theo.square.dif.MSF.csv", sep = ""))
    square.dif.MSF.mut.fname = file.path(data.dir,paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.square.dif.MSF.csv", sep = ""))

    # prepare the data
    square.dif.MSF.exp = read.csv(square.dif.MSF.exp.fname, header = T)
    rownames(square.dif.MSF.exp) = paste("mut", rownames(square.dif.MSF.exp), sep = "")
    square.dif.MSF.mut = read.csv(square.dif.MSF.mut.fname, header = T)
    rownames(square.dif.MSF.mut) = paste("mut", rownames(square.dif.MSF.mut), sep = "")
    square.dif.MSF.medium = read.csv(square.dif.MSF.medium.fname, header = T)
    rownames(square.dif.MSF.medium) = paste("mut", rownames(square.dif.MSF.medium), sep = "")

    site = seq(ncol(square.dif.MSF.medium))

    # Prepare siteComparison
    tsquare.dif.MSF.medium = as.data.frame(t(as.matrix(square.dif.MSF.medium)))
    tsquare.dif.MSF.medium = cbind(data.frame("site" = site), tsquare.dif.MSF.medium)
    siteComparison.medium = melt(tsquare.dif.MSF.medium, "site", variable.name = "protein", value.name = "square.dif.MSF")

    tsquare.dif.MSF.mut = as.data.frame(t(as.matrix(square.dif.MSF.mut)))
    tsquare.dif.MSF.mut = cbind(data.frame("site" = site), tsquare.dif.MSF.mut)
    siteComparison.mut = melt(tsquare.dif.MSF.mut, "site", variable.name = "protein", value.name = "square.dif.MSF")

    tsquare.dif.MSF.exp = as.data.frame(t(as.matrix(square.dif.MSF.exp)))
    tsquare.dif.MSF.exp = cbind(data.frame("site" = site), tsquare.dif.MSF.exp)
    siteComparison.exp = melt(tsquare.dif.MSF.exp, "site", variable.name = "protein", value.name = "square.dif.MSF")

    siteComparison.all.datasets = rbind(data.frame("dataset" = "exp", siteComparison.exp),
                                        data.frame("dataset" = "mut", siteComparison.mut),
                                        data.frame("dataset" = "medium", siteComparison.medium))

    siteComparison.all.datasets = ddply(siteComparison.all.datasets, c("dataset", "protein"), mutate,
                                             "r.SDF" = rank(square.dif.MSF, na.last = "keep"))

    dat = siteComparison.all.datasets
    dat$dataset = revalue(dat$dataset, c("medium" = "selection"))
    dat$dataset = revalue(dat$dataset, c("mut" = "no-selection"))

    # calculate dataset of means
    d = ddply(dat, c("dataset", "site"), function(x) {
        mean.r.SDF = mean(x$r.SDF, na.rm = T)
        data.frame(mean.r.SDF)
    })

    # calculate correlations berween profiles
    d.exp = subset(d, dataset == "exp")
    d.mut = subset(d, dataset == "no-selection")
    d.medium = subset(d, dataset == "selection")

    r.exp.mut = cor(d.exp$mean.r.SDF, d.mut$mean.r.SDF)
    r.exp.medium = cor(d.exp$mean.r.SDF, d.medium$mean.r.SDF)
    r.mut.medium = cor(d.mut$mean.r.SDF, d.medium$mean.r.SDF)

    cc.MSF.exp.mut[which(input$family == family), which(R0S == R0)] = r.exp.mut
    cc.MSF.exp.medium[which(input$family == family), which(R0S == R0)] = r.exp.medium
    cc.MSF.mut.medium[which(input$family == family), which(R0S == R0)] = r.mut.medium

    ### nH ###
    # set input filenames
    nH.exp.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.exp.nH.csv", sep = ""))
    nH.medium.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_medium.sel_K.analysis_Keff_out_m.theo.nH.csv", sep = ""))
    nH.mut.fname = file.path(data.dir,paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.nH.csv", sep = ""))

    # prepare the data
    nH.exp = read.csv(nH.exp.fname, header = T)
    rownames(nH.exp) = paste("mut", rownames(nH.exp), sep = "")
    nH.mut = read.csv(nH.mut.fname, header = T)
    rownames(nH.mut) = paste("mut", rownames(nH.mut), sep = "")
    nH.medium = read.csv(nH.medium.fname, header = T)
    rownames(nH.medium) = paste("mut", rownames(nH.medium), sep = "")

    mode = seq(ncol(nH.medium))

    # Prepare modeComparison
    tnH.medium = as.data.frame(t(as.matrix(nH.medium)))
    tnH.medium = cbind(data.frame("mode" = mode), tnH.medium)
    modeComparison.medium = melt(tnH.medium, "mode", variable.name = "protein", value.name = "nH")
    modeComparison.medium = ddply(modeComparison.medium, "protein", mutate, "nH" = nH / mean(nH, na.rm = T))

    tnH.mut = as.data.frame(t(as.matrix(nH.mut)))
    tnH.mut = cbind(data.frame("mode" = mode), tnH.mut)
    modeComparison.mut = melt(tnH.mut, "mode", variable.name = "protein", value.name = "nH")
    modeComparison.mut = ddply(modeComparison.mut, "protein", mutate, "nH" = nH / mean(nH, na.rm = T))

    tnH.exp = as.data.frame(t(as.matrix(nH.exp)))
    tnH.exp = cbind(data.frame("mode" = mode), tnH.exp)
    modeComparison.exp = melt(tnH.exp, "mode", variable.name = "protein", value.name = "nH")
    modeComparison.exp = ddply(modeComparison.exp, "protein", mutate, "nH" = nH / mean(nH, na.rm = T))

    # modeComparison.exp has NA's because for proteins with gaps when using Keff there're less modes
    #print("Warning: modeComparison.exp <- na.omit(modeComparison.exp)")
    modeComparison.exp <- na.omit(modeComparison.exp)
    modeComparison.medium <- na.omit(modeComparison.medium)
    modeComparison.mut <- na.omit(modeComparison.mut)

    modeComparison.all.datasets = rbind(data.frame("dataset" = "exp", modeComparison.exp),
                                        data.frame("dataset" = "mut", modeComparison.mut),
                                        data.frame("dataset" = "medium", modeComparison.medium))

    dat = modeComparison.all.datasets
    dat$dataset = revalue(dat$dataset, c("medium" = "selection"))
    dat$dataset = revalue(dat$dataset, c("mut" = "no-selection"))

    # calculate dataset of means
    d = ddply(dat,c("dataset", "mode"), function(x) {
        mean.nH = mean(x$nH)
        data.frame(mean.nH)
    })

    # calculate correlations berween profiles
    d.exp = subset(d, dataset == "exp")
    d.mut = subset(d, dataset == "no-selection")
    d.medium = subset(d, dataset == "selection")

    r.exp.mut = cor(d.exp$mean.nH, d.mut$mean.nH)
    r.exp.medium = cor(d.exp$mean.nH, d.medium$mean.nH)
    r.mut.medium = cor(d.mut$mean.nH, d.medium$mean.nH)

    cc.nH.exp.mut[which(input$family == family), which(R0S == R0)] = r.exp.mut
    cc.nH.exp.medium[which(input$family == family), which(R0S == R0)] = r.exp.medium
    cc.nH.mut.medium[which(input$family == family), which(R0S == R0)] = r.mut.medium

    # 100 modes
    r.exp.mut = cor(d.exp$mean.nH[1:100], d.mut$mean.nH[1:100])
    r.exp.medium = cor(d.exp$mean.nH[1:100], d.medium$mean.nH[1:100])
    r.mut.medium = cor(d.mut$mean.nH[1:100], d.medium$mean.nH[1:100])

    cc.nH.100.exp.mut[which(input$family == family), which(R0S == R0)] = r.exp.mut
    cc.nH.100.exp.medium[which(input$family == family), which(R0S == R0)] = r.exp.medium
    cc.nH.100.mut.medium[which(input$family == family), which(R0S == R0)] = r.mut.medium
  }
}

cc.z.RSD = data.frame(cc.z.RSD.exp.mut, cc.z.RSD.exp.medium, cc.z.RSD.mut.medium)
cc.z.RSD = cc.z.RSD
cc.z.RSD = rbind(cc.z.RSD, colMeans(cc.z.RSD))
family = as.character(input$family)
cc.z.RSD_CM = data.frame(c(family, "mean"), cc.z.RSD)
colnames(cc.z.RSD_CM) = c("family", paste("exp-mut-R0.", seq(1:number.R0), sep = ""), paste("exp-sel-R0.", seq(1:number.R0), sep = ""), paste("mut-sel-R0.", seq(1:number.R0), sep = ""))

write.csv(cc.z.RSD_CM, file = "cc_z.RSD_CM.csv")

cc.Pn = data.frame(cc.Pn.exp.mut, cc.Pn.exp.medium, cc.Pn.mut.medium)
cc.Pn = cc.Pn
cc.Pn = rbind(cc.Pn, colMeans(cc.Pn))
family = as.character(input$family)
cc.Pn_CM = data.frame(c(family, "mean"), cc.Pn)
colnames(cc.Pn_CM) = c("family", paste("exp-mut-R0.", seq(1:number.R0), sep = ""), paste("exp-sel-R0.", seq(1:number.R0), sep = ""), paste("mut-sel-R0.", seq(1:number.R0), sep = ""))

write.csv(cc.Pn_CM, file = "cc_Pn_CM.csv")

cc.Pn.100 = data.frame(cc.Pn.100.exp.mut, cc.Pn.100.exp.medium, cc.Pn.100.mut.medium)
cc.Pn.100 = cc.Pn.100
cc.Pn.100 = rbind(cc.Pn.100, colMeans(cc.Pn.100))
family = as.character(input$family)
cc.Pn.100_CM = data.frame(c(family, "mean"), cc.Pn.100)
colnames(cc.Pn.100_CM) = c("family", paste("exp-mut-R0.", seq(1:number.R0), sep = ""), paste("exp-sel-R0.", seq(1:number.R0), sep = ""), paste("mut-sel-R0.", seq(1:number.R0), sep = ""))

write.csv(cc.Pn.100_CM, file = "cc_Pn_100_CM.csv")

cc.MSF = data.frame(cc.MSF.exp.mut, cc.MSF.exp.medium, cc.MSF.mut.medium)
cc.MSF = cc.MSF
cc.MSF = rbind(cc.MSF, colMeans(cc.MSF))
family = as.character(input$family)
cc.MSF_CM = data.frame(c(family, "mean"), cc.MSF)
colnames(cc.MSF_CM) = c("family", paste("exp-mut-R0.", seq(1:number.R0), sep = ""), paste("exp-sel-R0.", seq(1:number.R0), sep = ""), paste("mut-sel-R0.", seq(1:number.R0), sep = ""))

write.csv(cc.MSF_CM, file = "cc_MSF_CM.csv")

cc.nH = data.frame(cc.nH.exp.mut, cc.nH.exp.medium, cc.nH.mut.medium)
cc.nH = cc.nH
cc.nH = rbind(cc.nH, colMeans(cc.nH))
family = as.character(input$family)
cc.nH_CM = data.frame(c(family, "mean"), cc.nH)
colnames(cc.nH_CM) = c("family", paste("exp-mut-R0.", seq(1:number.R0), sep = ""), paste("exp-sel-R0.", seq(1:number.R0), sep = ""), paste("mut-sel-R0.", seq(1:number.R0), sep = ""))

write.csv(cc.nH_CM, file = "cc_nH_CM.csv")

cc.nH.100 = data.frame(cc.nH.100.exp.mut, cc.nH.100.exp.medium, cc.nH.100.mut.medium)
cc.nH.100 = cc.nH.100
cc.nH.100 = rbind(cc.nH.100, colMeans(cc.nH.100))
family = as.character(input$family)
cc.nH.100_CM = data.frame(c(family, "mean"), cc.nH.100)
colnames(cc.nH.100_CM) = c("family", paste("exp-mut-R0.", seq(1:number.R0), sep = ""), paste("exp-sel-R0.", seq(1:number.R0), sep = ""), paste("mut-sel-R0.", seq(1:number.R0), sep = ""))

write.csv(cc.nH.100_CM, file = "cc_nH_100_CM.csv")
```

```{r prepare-site-data-plot-z.RSD}
# set
n.sets = ncol(cc.z.RSD_CA)- 1

# CA
# prepare the data
cc.z.RSD_CA = cc.z.RSD_CA[1:number.families, 2:ncol(cc.z.RSD_CA)]
c.R0 = rep(rep(paste("R0.", seq(number.R0), sep = ""), n.sets/number.R0), number.families)
comparison = rep(c(rep("exp vs mut",  number.R0), rep("exp vs selection", number.R0), rep("selection vs no-selection",  number.R0)), number.families)
df.cc.z.RSD_CA = cbind(data.frame("comparison" = comparison, "c.R0" = c.R0), cc.z.RSD = c(t(cc.z.RSD_CA)))

dat = df.cc.z.RSD_CA

d = ddply(dat,c("comparison", "c.R0"), function(x) {
    cc.mean = mean(x$cc.z.RSD)
    cc.sd = sd(x$cc.z.RSD)
    data.frame(cc.mean, cc.sd)
})

## prepare plots with mean profiles and deviations
limits <- aes(ymax = d$cc.mean + d$cc.sd,
              ymin = d$cc.mean - d$cc.sd)
ggplot(d, aes(x = c.R0, y = cc.mean, col = comparison, fill = comparison)) +
  labs(x = "R0", y = "<cc z.RSD CA>") +
  geom_bar(stat = "identity",
      position = position_dodge(0.9)) +
      geom_errorbar(limits, position = position_dodge(0.9),
                               width = 0.25,
                               col = "black") 
# CM
cc.z.RSD_CM = cc.z.RSD_CM[1:number.families, 2:ncol(cc.z.RSD_CM)]
df.cc.z.RSD_CM = cbind(data.frame("comparison" = comparison, "c.R0" = c.R0), cc.z.RSD = c(t(cc.z.RSD_CM)))

dat = df.cc.z.RSD_CM

d = ddply(dat,c("comparison", "c.R0"), function(x) {
  cc.mean = mean(x$cc.z.RSD)
  cc.sd = sd(x$cc.z.RSD)
  data.frame(cc.mean, cc.sd)
})

## prepare plots with mean profiles and deviations
limits <- aes(ymax = d$cc.mean + d$cc.sd,
              ymin = d$cc.mean - d$cc.sd)
ggplot(d, aes(x = c.R0, y = cc.mean, col = comparison, fill = comparison)) +
  labs(x = "R0", y = "<cc z.RSD CM>") +
  geom_bar(stat = "identity",
      position = position_dodge(0.9)) +
      geom_errorbar(limits, position = position_dodge(0.9),
                               width = 0.25,
                               col = "black") 
```

```{r prepare-site-data-plot-Pn}
# CA
# prepare the data
cc.Pn_CA = cc.Pn_CA[1:number.families, 2:ncol(cc.Pn_CA)]
df.cc.Pn_CA = cbind(data.frame("comparison" = comparison, "c.R0" = c.R0), cc.Pn = c(t(cc.Pn_CA)))

dat = df.cc.Pn_CA

d = ddply(dat,c("comparison", "c.R0"), function(x) {
    cc.mean = mean(x$cc.Pn)
    cc.sd = sd(x$cc.Pn)
    data.frame(cc.mean, cc.sd)
})

## prepare plots with mean profiles and deviations
limits <- aes(ymax = d$cc.mean + d$cc.sd,
              ymin = d$cc.mean - d$cc.sd)
ggplot(d, aes(x = c.R0, y = cc.mean, col = comparison, fill = comparison)) +
  labs(x = "R0", y = "<cc Pn CA>") +
  geom_bar(stat = "identity",
      position = position_dodge(0.9)) +
      geom_errorbar(limits, position = position_dodge(0.9),
                               width = 0.25,
                               col = "black") 
# CM
cc.Pn_CM = cc.Pn_CM[1:number.families, 2:ncol(cc.Pn_CM)]
df.cc.Pn_CM = cbind(data.frame("comparison" = comparison, "c.R0" = c.R0), cc.Pn = c(t(cc.Pn_CM)))

dat = df.cc.Pn_CM

d = ddply(dat,c("comparison", "c.R0"), function(x) {
  cc.mean = mean(x$cc.Pn)
  cc.sd = sd(x$cc.Pn)
  data.frame(cc.mean, cc.sd)
})

## prepare plots with mean profiles and deviations
limits <- aes(ymax = d$cc.mean + d$cc.sd,
              ymin = d$cc.mean - d$cc.sd)
ggplot(d, aes(x = c.R0, y = cc.mean, col = comparison, fill = comparison)) +
  labs(x = "R0", y = "<cc Pn CM>") +
  geom_bar(stat = "identity",
      position = position_dodge(0.9)) +
      geom_errorbar(limits, position = position_dodge(0.9),
                               width = 0.25,
                               col = "black") 
```

```{r prepare-site-data-plot-Pn.100}
# CA
# prepare the data
cc.Pn.100_CA = cc.Pn.100_CA[1:number.families, 2:ncol(cc.Pn.100_CA)]
df.cc.Pn.100_CA = cbind(data.frame("comparison" = comparison, "c.R0" = c.R0), cc.Pn.100 = c(t(cc.Pn.100_CA)))

dat = df.cc.Pn.100_CA

d = ddply(dat,c("comparison", "c.R0"), function(x) {
    cc.mean = mean(x$cc.Pn.100)
    cc.sd = sd(x$cc.Pn.100)
    data.frame(cc.mean, cc.sd)
})

## prepare plots with mean profiles and deviations
limits <- aes(ymax = d$cc.mean + d$cc.sd,
              ymin = d$cc.mean - d$cc.sd)
ggplot(d, aes(x = c.R0, y = cc.mean, col = comparison, fill = comparison)) +
  labs(x = "R0", y = "<cc Pn.100 CA>") +
  geom_bar(stat = "identity",
      position = position_dodge(0.9)) +
      geom_errorbar(limits, position = position_dodge(0.9),
                               width = 0.25,
                               col = "black") 
# CM
cc.Pn.100_CM = cc.Pn.100_CM[1:number.families, 2:ncol(cc.Pn.100_CM)]
df.cc.Pn.100_CM = cbind(data.frame("comparison" = comparison, "c.R0" = c.R0), cc.Pn.100 = c(t(cc.Pn.100_CM)))

dat = df.cc.Pn.100_CM

d = ddply(dat,c("comparison", "c.R0"), function(x) {
  cc.mean = mean(x$cc.Pn.100)
  cc.sd = sd(x$cc.Pn.100)
  data.frame(cc.mean, cc.sd)
})

## prepare plots with mean profiles and deviations
limits <- aes(ymax = d$cc.mean + d$cc.sd,
              ymin = d$cc.mean - d$cc.sd)
ggplot(d, aes(x = c.R0, y = cc.mean, col = comparison, fill = comparison)) +
  labs(x = "R0", y = "<cc Pn.100 CM>") +
  geom_bar(stat = "identity",
      position = position_dodge(0.9)) +
      geom_errorbar(limits, position = position_dodge(0.9),
                               width = 0.25,
                               col = "black") 
```

```{r prepare-site-data-plot-MSF}
# CA
# prepare the data
cc.MSF_CA = cc.MSF_CA[1:number.families, 2:ncol(cc.MSF_CA)]
df.cc.MSF_CA = cbind(data.frame("comparison" = comparison, "c.R0" = c.R0), cc.MSF = c(t(cc.MSF_CA)))

dat = df.cc.MSF_CA

d = ddply(dat,c("comparison", "c.R0"), function(x) {
    cc.mean = mean(x$cc.MSF)
    cc.sd = sd(x$cc.MSF)
    data.frame(cc.mean, cc.sd)
})

## prepare plots with mean profiles and deviations
limits <- aes(ymax = d$cc.mean + d$cc.sd,
              ymin = d$cc.mean - d$cc.sd)
ggplot(d, aes(x = c.R0, y = cc.mean, col = comparison, fill = comparison)) +
  labs(x = "R0", y = "<cc r.MSF CA>") +
  geom_bar(stat = "identity",
      position = position_dodge(0.9)) +
      geom_errorbar(limits, position = position_dodge(0.9),
                               width = 0.25,
                               col = "black") 
# CM
cc.MSF_CM = cc.MSF_CM[1:number.families, 2:ncol(cc.MSF_CM)]
df.cc.MSF_CM = cbind(data.frame("comparison" = comparison, "c.R0" = c.R0), cc.MSF = c(t(cc.MSF_CM)))

dat = df.cc.MSF_CM

d = ddply(dat,c("comparison", "c.R0"), function(x) {
  cc.mean = mean(x$cc.MSF)
  cc.sd = sd(x$cc.MSF)
  data.frame(cc.mean, cc.sd)
})

## prepare plots with mean profiles and deviations
limits <- aes(ymax = d$cc.mean + d$cc.sd,
              ymin = d$cc.mean - d$cc.sd)
ggplot(d, aes(x = c.R0, y = cc.mean, col = comparison, fill = comparison)) +
  labs(x = "R0", y = "<cc r.MSF CM>") +
  geom_bar(stat = "identity",
      position = position_dodge(0.9)) +
      geom_errorbar(limits, position = position_dodge(0.9),
                               width = 0.25,
                               col = "black") 
```

```{r prepare-site-data-plot-nH}
# CA
# prepare the data
cc.nH_CA = cc.nH_CA[1:number.families, 2:ncol(cc.nH_CA)]
df.cc.nH_CA = cbind(data.frame("comparison" = comparison, "c.R0" = c.R0), cc.nH = c(t(cc.nH_CA)))

dat = df.cc.nH_CA

d = ddply(dat,c("comparison", "c.R0"), function(x) {
    cc.mean = mean(x$cc.nH)
    cc.sd = sd(x$cc.nH)
    data.frame(cc.mean, cc.sd)
})

## prepare plots with mean profiles and deviations
limits <- aes(ymax = d$cc.mean + d$cc.sd,
              ymin = d$cc.mean - d$cc.sd)
ggplot(d, aes(x = c.R0, y = cc.mean, col = comparison, fill = comparison)) +
  labs(x = "R0", y = "<cc nH CA>") +
  geom_bar(stat = "identity",
      position = position_dodge(0.9)) +
      geom_errorbar(limits, position = position_dodge(0.9),
                               width = 0.25,
                               col = "black") 
# CM
cc.nH_CM = cc.nH_CM[1:number.families, 2:ncol(cc.nH_CM)]
df.cc.nH_CM = cbind(data.frame("comparison" = comparison, "c.R0" = c.R0), cc.nH = c(t(cc.nH_CM)))

dat = df.cc.nH_CM

d = ddply(dat,c("comparison", "c.R0"), function(x) {
  cc.mean = mean(x$cc.nH)
  cc.sd = sd(x$cc.nH)
  data.frame(cc.mean, cc.sd)
})

## prepare plots with mean profiles and deviations
limits <- aes(ymax = d$cc.mean + d$cc.sd,
              ymin = d$cc.mean - d$cc.sd)
ggplot(d, aes(x = c.R0, y = cc.mean, col = comparison, fill = comparison)) +
  labs(x = "R0", y = "<cc nH CM>") +
  geom_bar(stat = "identity",
      position = position_dodge(0.9)) +
      geom_errorbar(limits, position = position_dodge(0.9),
                               width = 0.25,
                               col = "black") 
```

```{r prepare-site-data-plot-nH.100}
# CA
# prepare the data
cc.nH.100_CA = cc.nH.100_CA[1:number.families, 2:ncol(cc.nH.100_CA)]
df.cc.nH.100_CA = cbind(data.frame("comparison" = comparison, "c.R0" = c.R0), cc.nH.100 = c(t(cc.nH.100_CA)))

dat = df.cc.nH.100_CA

d = ddply(dat,c("comparison", "c.R0"), function(x) {
    cc.mean = mean(x$cc.nH.100)
    cc.sd = sd(x$cc.nH.100)
    data.frame(cc.mean, cc.sd)
})

## prepare plots with mean profiles and deviations
limits <- aes(ymax = d$cc.mean + d$cc.sd,
              ymin = d$cc.mean - d$cc.sd)
ggplot(d, aes(x = c.R0, y = cc.mean, col = comparison, fill = comparison)) +
  labs(x = "R0", y = "<cc nH.100 CA>") +
  geom_bar(stat = "identity",
      position = position_dodge(0.9)) +
      geom_errorbar(limits, position = position_dodge(0.9),
                               width = 0.25,
                               col = "black") 
# CM
cc.nH.100_CM = cc.nH.100_CM[1:number.families, 2:ncol(cc.nH.100_CM)]
df.cc.nH.100_CM = cbind(data.frame("comparison" = comparison, "c.R0" = c.R0), cc.nH.100 = c(t(cc.nH.100_CM)))

dat = df.cc.nH.100_CM

d = ddply(dat,c("comparison", "c.R0"), function(x) {
  cc.mean = mean(x$cc.nH.100)
  cc.sd = sd(x$cc.nH.100)
  data.frame(cc.mean, cc.sd)
})

## prepare plots with mean profiles and deviations
limits <- aes(ymax = d$cc.mean + d$cc.sd,
              ymin = d$cc.mean - d$cc.sd)
ggplot(d, aes(x = c.R0, y = cc.mean, col = comparison, fill = comparison)) +
  labs(x = "R0", y = "<cc nH.100 CM>") +
  geom_bar(stat = "identity",
      position = position_dodge(0.9)) +
      geom_errorbar(limits, position = position_dodge(0.9),
                               width = 0.25,
                               col = "black") 
```

### 2017-05-10 MainProgram.R

@@ -204,7 +204,3 @@ for (f in (1:nrow(input))) {
     }
   }
 }
-
-
-
-  

### 2017-06-04 MY-FILES/OTHER FILES/analysis-structure-antes.Rmd
estructura-CN/WCN

--- 2017-05-10 analysis-structure.Rmd
@@
 
+ReadCA.fname <- "FUNCTIONS/ReadCA.R"
+CalculateSideChainCM.fname <- "FUNCTIONS/CalculateSideChainCM.R"
+
 # load functions
+source(ReadCA.fname) 
+source(CalculateSideChainCM.fname)
 source(file.path(data.dir, "multiplot.R"))
@@
 names(pdb.info) = c("resno", "AA", paste("CN", as.character(R0), sep = ""))
+
+if (data.dir == "OUT/out_subset_CM_ANM") {
+
+  # Read PDB of p.ref
+  pdb.ca = ReadCA(reference.pdb.fname, chain.p.ref)
+  r.ca.p.ref = pdb.ca$xyz.calpha
+  n.aa = pdb.ca$n.sites
+
+  r.CM.p.ref = CalculateSideChainCM(reference.pdb.fname, chain.p.ref)
+  n.CM = ncol(r.CM.p.ref)
+
+  cmap.CM = cmap(r.CM.p.ref, dcut = R0, scut = 0, mask.lower = F)
+  CN = rowSums(cmap.CM, na.rm = T) - 2
+}
 
@@
 
-plot(x = d.exp$mean.z.RSD, y = log(CN), xlab = "<zRSDi> experimental ")
+plot(x = d.exp$mean.z.RSD, y = log(CN), xlab = "<zRSDi> experimental")
 plot(x = d.mut$mean.z.RSD, y = log(CN), xlab = "<zRSDi> no-selection")
@@
 
-knitr::kable(cor.df, digits = 2, caption = "Correlation structure (<z.RSD>) - sequence (CN)")
+knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
+
+## calculate correlations
+r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN), method = "spearman")
+r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN), method = "spearman")
+r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN), method = "spearman")
+
+cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
+                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))
+
+knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
+
+# mean profiles
+
+CN.simple = CN[!duplicated(CN)]
+
+CN.i.mean = c()
+exp.mean.z.RSD.i.mean = c()
+mut.mean.z.RSD.i.mean = c()
+medium.mean.z.RSD.i.mean = c()
+
+count = 0
+for (i in (CN.simple)) {
+  count = count + 1
+  index = 0
+  for (j in (1:length(CN))){
+    if (CN[j] == i) {
+      index = cbind(index, j)
+    } 
+  }
+  CN.i.mean[count] = mean(CN[index])
+  exp.mean.z.RSD.i.mean[count] = mean(d.exp$mean.z.RSD[index])
+  mut.mean.z.RSD.i.mean[count] = mean(d.mut$mean.z.RSD[index])
+  medium.mean.z.RSD.i.mean[count] = mean(d.medium$mean.z.RSD[index])
+}
+
+## plot
+par(pty = "s")
+
+plot(x = exp.mean.z.RSD.i.mean, y = log(CN.i.mean), xlab = "mean <zRSDi> experimental for each CN", ylab = "log(CN)")
+plot(x = mut.mean.z.RSD.i.mean, y = log(CN.i.mean), xlab = "mean <zRSDi> no-selection for each CN", ylab = "log(CN)")
+plot(x = medium.mean.z.RSD.i.mean, y = log(CN.i.mean), xlab = "mean <zRSDi> selection for each CN", ylab = "log(CN)")
+
+## calculate correlations
+r.exp.mean.z.RSD.CN = cor(exp.mean.z.RSD.i.mean, log(CN.i.mean), method = "s")
+r.mut.mean.z.RSD.CN = cor(mut.mean.z.RSD.i.mean, log(CN.i.mean), method = "s")
+r.medium.mean.z.RSD.CN = cor(medium.mean.z.RSD.i.mean, log(CN.i.mean), method = "s")
+
+cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
+                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))
+
+knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
+
+## calculate correlations
+r.exp.mean.z.RSD.CN = cor(exp.mean.z.RSD.i.mean, log(CN.i.mean), method = "p")
+r.mut.mean.z.RSD.CN = cor(mut.mean.z.RSD.i.mean, log(CN.i.mean), method = "p")
+r.medium.mean.z.RSD.CN = cor(medium.mean.z.RSD.i.mean, log(CN.i.mean), method = "p")
+
+cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
+                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))
+
+knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
 ```
+
+### Sequence - structure comparison WCN
+
+```{r structure-WCN-comparison}
+
+# compare profiles
+## plot
+par(pty = "s")
+
+plot(x = d.exp$mean.z.RSD, y = log(WCN), xlab = "<zRSDi> experimental")
+plot(x = d.mut$mean.z.RSD, y = log(WCN), xlab = "<zRSDi> no-selection")
+plot(x = d.medium$mean.z.RSD, y = log(WCN), xlab = "<zRSDi> selection")
+
+## calculate correlations
+r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(WCN))
+r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(WCN))
+r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(WCN))
+
+cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(WCN)", "<z.RSD> no-selection vs log(WCN)", "<z.RSD> selection vs log(WCN)"),
+                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))
+
+knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (WCN)")
+
+## calculate correlations
+r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(WCN), method = "spearman")
+r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(WCN), method = "spearman")
+r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(WCN), method = "spearman")
+
+cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(WCN)", "<z.RSD> no-selection vs log(WCN)", "<z.RSD> selection vs log(WCN)"),
+                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))
+
+knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (WCN)")
+
+```

### 2017-06-04 analysis-structure-CN-WCN-exp-2.Rmd
estructura-CN/WCN

---
title: "Structural Divergence Analysis"
author: "Maria Laura Marcos, Julian Echave"
output: html_document
---

# Introduction

```{r setup, include = FALSE}
# set chunk options
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r load-packages}
# load packages
library(ggplot2)
library(reshape2)
library(plyr)
library(quantreg)
library(bio3d)

# load functions
source("FUNCTIONS/ReadCA.R") 
source("FUNCTIONS/CalculateSideChainCM.R")
source(file.path(data.dir, "multiplot.R"))
source(file.path(data.dir, "my-functions.R"))
```

```{r set-file-names}
# set input filenames

## CM
data.dir <- paste("OUT/out_subset_CM_ANM", sep = "")
R0 = R0.CM

## data
reference.fname = file.path(data.dir, paste(family, "_ref.txt", sep = ""))
protein_list.fname = file.path(data.dir, paste(family, "_list.txt", sep = ""))

## profiles to compare
dri2.exp.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.exp.norm.dr.squarei.csv", sep = ""))
dri2.medium.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_medium.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
dri2.mut.fname = file.path(data.dir,paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))

## consurf
score.fname = file.path(data.dir, paste(p.ref, "_consurf.csv", sep = ""))
sim.data.mut.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_out_df.data.csv", sep = ""))
sim.data.medium.sel.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_medium.sel_out_df.data.csv", sep = ""))
```

```{r set-reference-protein}
# which is the reference protein?
reference = as.character(read.table(reference.fname, header = F)[1, 1])
if (reference != p.ref) {
  print("Warning: different references")
}
```

In this case we studied the `r family` family. 
We used as reference for the ENM the protein with pdb code `r reference`. 
We simulated `r n.mut.p` mutants of this reference for each protein of the family.
The `r family` family is of the type `r type` and consists of the following proteins:

```{r set-experimental-protein-names}
# experimental protein names
protein.exp = read.table(protein_list.fname, header = F, stringsAsFactors = F)[, 1]
protein.exp = protein.exp[protein.exp != reference]
print(protein.exp)
```

```{r set-site-info, include = FALSE}

# read reference pdb and calculate resno, AA, and CN
reference.pdb.fname = file.path(data.dir,paste(reference, ".pdb", sep = ""))
ref.pdb = read.pdb(reference.pdb.fname)
inds = atom.select(ref.pdb, elety = "CA")
ref.pdb.ca = ref.pdb$atom[inds$atom, ]
n.sites = length(ref.pdb.ca$resid)
AA = ref.pdb.ca$resid
resno = seq(1:n.sites)
pdb.info = data.frame(resno, AA)
names(pdb.info) = c("resno", "AA")
print(n.sites)

site.info = pdb.info

### CA ###

# calculate CN
R0 = -0.1
cmap.ca.1 = cmap(ref.pdb$xyz[inds$xyz], dcut = R0, scut = 0, mask.lower = F)
CN.R0.neg.0.1.CA = rep(0, n.sites)

R0 = 2.5
cmap.ca.R0.2.5 = cmap(ref.pdb$xyz[inds$xyz], dcut = R0, scut = 0, mask.lower = F)
CN.R0.2.5.CA = rep(0, n.sites)

R0 = 7.5
cmap.ca.R0.7.5 = cmap(ref.pdb$xyz[inds$xyz], dcut = R0, scut = 0, mask.lower = F)
CN.R0.7.5.CA = rowSums(cmap.ca.R0.7.5, na.rm = T) - 1 # diag(cmap.ca) returned by cmap is 1!

R0 = 12.5
cmap.ca.R0.12.5 = cmap(ref.pdb$xyz[inds$xyz], dcut = R0, scut = 0, mask.lower = F)
CN.R0.12.5.CA = rowSums(cmap.ca.R0.12.5, na.rm = T) - 1 # diag(cmap.ca) returned by cmap is 1!

R0 = 17.5
cmap.ca.R0.17.5 = cmap(ref.pdb$xyz[inds$xyz], dcut = R0, scut = 0, mask.lower = F)
CN.R0.17.5.CA = rowSums(cmap.ca.R0.17.5, na.rm = T) - 1 # diag(cmap.ca) returned by cmap is 1!

R0 = 22.5
cmap.ca.R0.22.5 = cmap(ref.pdb$xyz[inds$xyz], dcut = R0, scut = 0, mask.lower = F)
CN.R0.22.5.CA = rowSums(cmap.ca.R0.22.5, na.rm = T) - 1 # diag(cmap.ca) returned by cmap is 1!

R0 = 27.5
cmap.ca.R0.27.5 = cmap(ref.pdb$xyz[inds$xyz], dcut = R0, scut = 0, mask.lower = F)
CN.R0.27.5.CA = rowSums(cmap.ca.R0.27.5, na.rm = T) - 1 # diag(cmap.ca) returned by cmap is 1!

R0 = 32.5
cmap.ca.R0.32.5 = cmap(ref.pdb$xyz[inds$xyz], dcut = R0, scut = 0, mask.lower = F)
CN.R0.32.5.CA = rowSums(cmap.ca.R0.32.5, na.rm = T) - 1 # diag(cmap.ca) returned by cmap is 1!

R0 = 37.5
cmap.ca.R0.37.5 = cmap(ref.pdb$xyz[inds$xyz], dcut = R0, scut = 0, mask.lower = F)
CN.R0.37.5.CA = rowSums(cmap.ca.R0.37.5, na.rm = T) - 1 # diag(cmap.ca) returned by cmap is 1!

R0 = 42.5
cmap.ca.R0.42.5 = cmap(ref.pdb$xyz[inds$xyz], dcut = R0, scut = 0, mask.lower = F)
CN.R0.42.5.CA = rowSums(cmap.ca.R0.42.5, na.rm = T) - 1 # diag(cmap.ca) returned by cmap is 1!

R0 = 47.5
cmap.ca.R0.47.5 = cmap(ref.pdb$xyz[inds$xyz], dcut = R0, scut = 0, mask.lower = F)
CN.R0.47.5.CA = rowSums(cmap.ca.R0.47.5, na.rm = T) - 1 # diag(cmap.ca) returned by cmap is 1!

R0 = 52.5
cmap.ca.R0.52.5 = cmap(ref.pdb$xyz[inds$xyz], dcut = R0, scut = 0, mask.lower = F)
CN.R0.52.5.CA = rowSums(cmap.ca.R0.52.5, na.rm = T) - 1 # diag(cmap.ca) returned by cmap is 1!

# calculate WCN
r.p.ref = matrix(ref.pdb$xyz[inds$xyz], nrow = 3)
dist.r.p.ref = dist.xyz(t(r.p.ref))
WCN.CA = c()
for (i in (1:ncol(r.p.ref))) {
  WCN.CA[i] = sum(1/dist.r.p.ref[i, -i]^2)
}

### CM ###

# Read PDB of p.ref
pdb.ca = ReadCA(reference.pdb.fname, chain.p.ref)
r.ca.p.ref = pdb.ca$xyz.calpha
r.CM.p.ref = CalculateSideChainCM(reference.pdb.fname, chain.p.ref)
r.p.ref = cbind(r.CM.p.ref, r.ca.p.ref)

# calculate CN
R0 = -0.1
cmap.CM.1 = cmap(as.vector(r.p.ref), dcut = R0, scut = 0, mask.lower = F)
CN.R0.neg.0.1.CM = rep(0, n.sites)

R0 = 2.5
cmap.CM.R0.2.5 = cmap(as.vector(r.p.ref), dcut = R0, scut = 0, mask.lower = F)
CN.R0.2.5.CM = rep(0, n.sites)

R0 = 7.5
cmap.CM.R0.7.5 = cmap(as.vector(r.p.ref), dcut = R0, scut = 0, mask.lower = F)
CN.R0.7.5.CM = (rowSums(cmap.CM.R0.7.5, na.rm = T) - 2)[1:ncol(r.CM.p.ref)]

R0 = 12.5
cmap.CM.12.5 = cmap(as.vector(r.p.ref), dcut = R0, scut = 0, mask.lower = F)
CN.R0.12.5.CM = (rowSums(cmap.CM.12.5, na.rm = T) - 2)[1:ncol(r.CM.p.ref)]

R0 = 17.5
cmap.CM.R0.17.5 = cmap(as.vector(r.p.ref), dcut = R0, scut = 0, mask.lower = F)
CN.R0.17.5.CM = (rowSums(cmap.CM.R0.17.5, na.rm = T) - 2)[1:ncol(r.CM.p.ref)]

R0 = 22.5
cmap.CM.R0.22.5 = cmap(ref.pdb$xyz[inds$xyz], dcut = R0, scut = 0, mask.lower = F)
CN.R0.22.5.CM = (rowSums(cmap.CM.R0.22.5, na.rm = T) - 2)[1:ncol(r.CM.p.ref)]

R0 = 27.5
cmap.CM.R0.27.5 = cmap(ref.pdb$xyz[inds$xyz], dcut = R0, scut = 0, mask.lower = F)
CN.R0.27.5.CM = (rowSums(cmap.CM.R0.27.5, na.rm = T) - 2)[1:ncol(r.CM.p.ref)]

R0 = 32.5
cmap.CM.R0.32.5 = cmap(as.vector(r.p.ref), dcut = R0, scut = 0, mask.lower = F)
CN.R0.32.5.CM = (rowSums(cmap.CM.R0.32.5, na.rm = T) - 2)[1:ncol(r.CM.p.ref)]

R0 = 37.5
cmap.CM.R0.37.5 = cmap(as.vector(r.p.ref), dcut = R0, scut = 0, mask.lower = F)
CN.R0.37.5.CM = (rowSums(cmap.CM.R0.37.5, na.rm = T) - 2)[1:ncol(r.CM.p.ref)]

R0 = 42.5
cmap.CM.R0.42.5 = cmap(ref.pdb$xyz[inds$xyz], dcut = R0, scut = 0, mask.lower = F)
CN.R0.42.5.CM = (rowSums(cmap.CM.R0.42.5, na.rm = T) - 2)[1:ncol(r.CM.p.ref)]

R0 = 47.5
cmap.CM.R0.47.5 = cmap(ref.pdb$xyz[inds$xyz], dcut = R0, scut = 0, mask.lower = F)
CN.R0.47.5.CM = (rowSums(cmap.CM.R0.47.5, na.rm = T) - 2)[1:ncol(r.CM.p.ref)]

R0 = 52.5
cmap.CM.R0.52.5 = cmap(ref.pdb$xyz[inds$xyz], dcut = R0, scut = 0, mask.lower = F)
CN.R0.52.5.CM = (rowSums(cmap.CM.R0.52.5, na.rm = T) - 2)[1:ncol(r.CM.p.ref)]

# calculate WCN
dist.r.CM.p.ref = dist.xyz(t(r.p.ref))
WCN.CM = c()
for (i in (1:ncol(r.CM.p.ref))) {
  WCN.CM[i] = sum(1/(dist.r.CM.p.ref[i, -c(i, (i + ncol(r.CM.p.ref)))]^2))
}

```

```{r read-data}
# read data
## exp
dri2.exp = read.csv(dri2.exp.fname, header = T)
site = site.info$site
rownames(dri2.exp) = paste("exp", rownames(dri2.exp), sep = "")

## mut
dri2.mut = read.csv(dri2.mut.fname, header = T)
rownames(dri2.mut) = paste("mut", rownames(dri2.mut), sep = "")

## medium
dri2.medium = read.csv(dri2.medium.fname, header = T)
rownames(dri2.medium) = paste("medium", rownames(dri2.medium), sep = "")
```

```{r prepare-site-data}
# prepare the data
## exp
tdri2.exp = as.data.frame(t(as.matrix(dri2.exp)))
tdri2.exp = cbind(site.info, tdri2.exp)
siteComparison.exp = melt(tdri2.exp, id.vars = names(site.info), variable.name = "protein", value.name = "dri2")

## mut
tdri2.mut = as.data.frame(t(as.matrix(dri2.mut)))
tdri2.mut = cbind(site.info, tdri2.mut)
siteComparison.mut = melt(tdri2.mut, id.vars = names(site.info), variable.name = "protein", value.name = "dri2")

## medium
tdri2.medium = as.data.frame(t(as.matrix(dri2.medium)))
tdri2.medium = cbind(site.info, tdri2.medium)
siteComparison.medium = melt(tdri2.medium, id.vars = names(site.info), variable.name = "protein", value.name = "dri2")

# bluild the data.frame
siteComparison.all.datasets = rbind(data.frame("dataset" = "exp", siteComparison.exp),
                                    data.frame("dataset" = "mut", siteComparison.mut),
                                    data.frame("dataset" = "medium", siteComparison.medium))

siteComparison.all.datasets = ddply(siteComparison.all.datasets, c("dataset", "protein"), mutate,
                     "n.SD" = dri2/mean(dri2, na.rm = T),
                     "z.SD" = vscale(dri2),
                      "RSD" = sqrt(dri2),
                    "n.RSD" = RSD/mean(RSD, na.rm = T),
                    "z.RSD" = vscale(RSD))
```

```{r mean-se-z.RSD-vs-site}
# comparison of z.RSD profiles with functional sites
## prepare dat
dat = siteComparison.all.datasets
dat$dataset = revalue(dat$dataset, c("medium" = "selection"))
dat$dataset = revalue(dat$dataset, c("mut" = "no-selection"))

## dat with means and standard errors
d = ddply(dat,c("dataset", "resno"), function(x) {
                mean.z.RSD = mean(x$z.RSD, na.rm = T)
                ndata = sum(!is.na(x$z.RSD))
                se.z.RSD = sd(x$z.RSD, na.rm = T) / sqrt(ndata)
                data.frame(mean.z.RSD, ndata, se.z.RSD)
})

# calculate correlations berween profiles
d.exp = subset(d, dataset == "exp")
d.mut = subset(d, dataset == "no-selection")
d.medium = subset(d, dataset == "selection")
```
### Sequence - structure comparison

```{r structure-CN-WCN-CA-comparison}

# compare profiles

CA.cor.p = c()
CA.cor.s = c()

## plot
par(pty = "s")

plot(x = d.exp$mean.z.RSD, y = CN.R0.neg.0.1.CA, xlab = "<zRSDi> experimental")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, CN.R0.neg.0.1.CA)
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs CN"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
CA.cor.p = c(CA.cor.p, r.exp.mean.z.RSD.CN)

r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, CN.R0.neg.0.1.CA, method = "spearman")
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs CN"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
CA.cor.s = c(CA.cor.s, r.exp.mean.z.RSD.CN)

########

plot(x = d.exp$mean.z.RSD, y = CN.R0.2.5.CA, xlab = "<zRSDi> experimental")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, CN.R0.2.5.CA)
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs CN"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
CA.cor.p = c(CA.cor.p, r.exp.mean.z.RSD.CN)

r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, CN.R0.2.5.CA, method = "spearman")
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs CN"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
CA.cor.s = c(CA.cor.s, r.exp.mean.z.RSD.CN)

######
plot(x = d.exp$mean.z.RSD, y = log(CN.R0.7.5.CA), xlab = "<zRSDi> experimental")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.R0.7.5.CA))
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
CA.cor.p = c(CA.cor.p, r.exp.mean.z.RSD.CN)

r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.R0.7.5.CA), method = "spearman")
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
CA.cor.s = c(CA.cor.s, r.exp.mean.z.RSD.CN)

#######
plot(x = d.exp$mean.z.RSD, y = log(CN.R0.12.5.CA), xlab = "<zRSDi> experimental")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.R0.12.5.CA))
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
CA.cor.p = c(CA.cor.p, r.exp.mean.z.RSD.CN)

r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.R0.12.5.CA), method = "spearman")
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
CA.cor.s = c(CA.cor.s, r.exp.mean.z.RSD.CN)

#####
plot(x = d.exp$mean.z.RSD, y = log(CN.R0.17.5.CA), xlab = "<zRSDi> experimental")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.R0.17.5.CA))
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
CA.cor.p = c(CA.cor.p, r.exp.mean.z.RSD.CN)

r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.R0.17.5.CA), method = "spearman")
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
CA.cor.s = c(CA.cor.s, r.exp.mean.z.RSD.CN)

#####
plot(x = d.exp$mean.z.RSD, y = log(CN.R0.22.5.CA), xlab = "<zRSDi> experimental")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.R0.22.5.CA))
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
CA.cor.p = c(CA.cor.p, r.exp.mean.z.RSD.CN)

r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.R0.22.5.CA), method = "spearman")
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
CA.cor.s = c(CA.cor.s, r.exp.mean.z.RSD.CN)

#####
plot(x = d.exp$mean.z.RSD, y = log(CN.R0.27.5.CA), xlab = "<zRSDi> experimental")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.R0.27.5.CA))
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
CA.cor.p = c(CA.cor.p, r.exp.mean.z.RSD.CN)

r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.R0.27.5.CA), method = "spearman")
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
CA.cor.s = c(CA.cor.s, r.exp.mean.z.RSD.CN)

######
plot(x = d.exp$mean.z.RSD, y = log(CN.R0.32.5.CA), xlab = "<zRSDi> experimental")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.R0.32.5.CA))
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
CA.cor.p = c(CA.cor.p, r.exp.mean.z.RSD.CN)

r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.R0.32.5.CA), method = "spearman")
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
CA.cor.s = c(CA.cor.s, r.exp.mean.z.RSD.CN)

#######
plot(x = d.exp$mean.z.RSD, y = log(CN.R0.37.5.CA), xlab = "<zRSDi> experimental")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.R0.37.5.CA))
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
CA.cor.p = c(CA.cor.p, r.exp.mean.z.RSD.CN)

r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.R0.37.5.CA), method = "spearman")
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
CA.cor.s = c(CA.cor.s, r.exp.mean.z.RSD.CN)

#####
plot(x = d.exp$mean.z.RSD, y = log(CN.R0.42.5.CA), xlab = "<zRSDi> experimental")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.R0.42.5.CA))
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
CA.cor.p = c(CA.cor.p, r.exp.mean.z.RSD.CN)

r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.R0.42.5.CA), method = "spearman")
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
CA.cor.s = c(CA.cor.s, r.exp.mean.z.RSD.CN)

#####
plot(x = d.exp$mean.z.RSD, y = log(CN.R0.47.5.CA), xlab = "<zRSDi> experimental")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.R0.47.5.CA))
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
CA.cor.p = c(CA.cor.p, r.exp.mean.z.RSD.CN)

r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.R0.47.5.CA), method = "spearman")
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
CA.cor.s = c(CA.cor.s, r.exp.mean.z.RSD.CN)

#####
plot(x = d.exp$mean.z.RSD, y = log(CN.R0.52.5.CA), xlab = "<zRSDi> experimental")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.R0.52.5.CA))
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
CA.cor.p = c(CA.cor.p, r.exp.mean.z.RSD.CN)

r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.R0.52.5.CA), method = "spearman")
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
CA.cor.s = c(CA.cor.s, r.exp.mean.z.RSD.CN)

# WCN
plot(x = d.exp$mean.z.RSD, y = log(WCN.CA), xlab = "<zRSDi> experimental")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(WCN.CA))
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(WCN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (WCN)")
CA.cor.p = c(CA.cor.p, r.exp.mean.z.RSD.CN)

r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(WCN.CA), method = "spearman")
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(WCN)"),
                             "R" = r.exp.mean.z.RSD.CN)

knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (WCN)")
CA.cor.s = c(CA.cor.s, r.exp.mean.z.RSD.CN)

```

```{r structure-CN-WCN-CM-comparison}

# compare profiles

CM.cor.p = c()
CM.cor.s = c()

## plot
par(pty = "s")

plot(x = d.exp$mean.z.RSD, y = CN.R0.neg.0.1.CM, xlab = "<zRSDi> experimental")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, CN.R0.neg.0.1.CM)
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs CN"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
CM.cor.p = c(CM.cor.p, r.exp.mean.z.RSD.CN)

r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, CN.R0.neg.0.1.CM, method = "spearman")
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs CN"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
CM.cor.s = c(CM.cor.s, r.exp.mean.z.RSD.CN)

########

plot(x = d.exp$mean.z.RSD, y = CN.R0.2.5.CM, xlab = "<zRSDi> experimental")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, CN.R0.2.5.CM)
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs CN"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
CM.cor.p = c(CM.cor.p, r.exp.mean.z.RSD.CN)

r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, CN.R0.2.5.CM, method = "spearman")
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs CN"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
CM.cor.s = c(CM.cor.s, r.exp.mean.z.RSD.CN)

######
plot(x = d.exp$mean.z.RSD, y = log(CN.R0.7.5.CM), xlab = "<zRSDi> experimental")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.R0.7.5.CM))
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
CM.cor.p = c(CM.cor.p, r.exp.mean.z.RSD.CN)

r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.R0.7.5.CM), method = "spearman")
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
CM.cor.s = c(CM.cor.s, r.exp.mean.z.RSD.CN)

#######
plot(x = d.exp$mean.z.RSD, y = log(CN.R0.12.5.CM), xlab = "<zRSDi> experimental")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.R0.12.5.CM))
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
CM.cor.p = c(CM.cor.p, r.exp.mean.z.RSD.CN)

r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.R0.12.5.CM), method = "spearman")
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
CM.cor.s = c(CM.cor.s, r.exp.mean.z.RSD.CN)

#####
plot(x = d.exp$mean.z.RSD, y = log(CN.R0.17.5.CM), xlab = "<zRSDi> experimental")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.R0.17.5.CM))
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
CM.cor.p = c(CM.cor.p, r.exp.mean.z.RSD.CN)

r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.R0.17.5.CM), method = "spearman")
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
CM.cor.s = c(CM.cor.s, r.exp.mean.z.RSD.CN)

#####
plot(x = d.exp$mean.z.RSD, y = log(CN.R0.22.5.CM), xlab = "<zRSDi> experimental")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.R0.22.5.CM))
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
CM.cor.p = c(CM.cor.p, r.exp.mean.z.RSD.CN)

r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.R0.22.5.CM), method = "spearman")
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
CM.cor.s = c(CM.cor.s, r.exp.mean.z.RSD.CN)

#####
plot(x = d.exp$mean.z.RSD, y = log(CN.R0.27.5.CM), xlab = "<zRSDi> experimental")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.R0.27.5.CM))
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
CM.cor.p = c(CM.cor.p, r.exp.mean.z.RSD.CN)

r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.R0.27.5.CM), method = "spearman")
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
CM.cor.s = c(CM.cor.s, r.exp.mean.z.RSD.CN)

######
plot(x = d.exp$mean.z.RSD, y = log(CN.R0.32.5.CM), xlab = "<zRSDi> experimental")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.R0.32.5.CM))
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
CM.cor.p = c(CM.cor.p, r.exp.mean.z.RSD.CN)

r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.R0.32.5.CM), method = "spearman")
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
CM.cor.s = c(CM.cor.s, r.exp.mean.z.RSD.CN)

#######
plot(x = d.exp$mean.z.RSD, y = log(CN.R0.37.5.CM), xlab = "<zRSDi> experimental")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.R0.37.5.CM))
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
CM.cor.p = c(CM.cor.p, r.exp.mean.z.RSD.CN)

r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.R0.37.5.CM), method = "spearman")
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
CM.cor.s = c(CM.cor.s, r.exp.mean.z.RSD.CN)

#####
plot(x = d.exp$mean.z.RSD, y = log(CN.R0.42.5.CM), xlab = "<zRSDi> experimental")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.R0.42.5.CM))
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
CM.cor.p = c(CM.cor.p, r.exp.mean.z.RSD.CN)

r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.R0.42.5.CM), method = "spearman")
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
CM.cor.s = c(CM.cor.s, r.exp.mean.z.RSD.CN)

#####
plot(x = d.exp$mean.z.RSD, y = log(CN.R0.47.5.CM), xlab = "<zRSDi> experimental")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.R0.47.5.CM))
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
CM.cor.p = c(CM.cor.p, r.exp.mean.z.RSD.CN)

r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.R0.47.5.CM), method = "spearman")
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
CM.cor.s = c(CM.cor.s, r.exp.mean.z.RSD.CN)

#####
plot(x = d.exp$mean.z.RSD, y = log(CN.R0.52.5.CM), xlab = "<zRSDi> experimental")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.R0.52.5.CM))
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
CM.cor.p = c(CM.cor.p, r.exp.mean.z.RSD.CN)

r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.R0.52.5.CM), method = "spearman")
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
CM.cor.s = c(CM.cor.s, r.exp.mean.z.RSD.CN)

# WCN
plot(x = d.exp$mean.z.RSD, y = log(WCN.CM), xlab = "<zRSDi> experimental")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(WCN.CM))
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(WCN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (WCN)")
CM.cor.p = c(CM.cor.p, r.exp.mean.z.RSD.CN)

r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(WCN.CM), method = "spearman")
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(WCN)"),
                             "R" = r.exp.mean.z.RSD.CN)

knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (WCN)")
CM.cor.s = c(CM.cor.s, r.exp.mean.z.RSD.CN)

```

### All correlations

```{r correlations}
# build a data frame
cor = data.frame("CA pearson" = CA.cor.p,
                 "CM pearson" = CM.cor.p,
                 "CA spearman" = CA.cor.s,
                 "CM spearman" = CM.cor.s)
rownames(cor) = c("CN R0 = -0.1", "CN R0 = 2.5", "CN R0 = 7.5", "CN R0 = 12.5", "CN R0 = 17.5", "CN R0 = 22.5", "CN R0 = 27.5", "CN R0 = 32.5", "CN R0 = 37.5", "CN R0 = 42.5", "CN R0 = 47.5", "CN R0 = 52.5", "WCN")
knitr::kable(cor, digits = 2, caption = "Correlation structure (<z.RSD>) - sequence (CN/WCN)")
```

### 2017-06-04 analysis-structure-CN-WCN-exp.Rmd
estructura-CN/WCN

---
title: "Structural Divergence Analysis"
author: "Maria Laura Marcos, Julian Echave"
output: html_document
---

# Introduction
We study the evolutionary divergence of proteins using the LF-ENM and comparing simulated mutants with experimental data.

```{r setup, include = FALSE}
# set chunk options
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r load-packages}
# load packages
library(ggplot2)
library(reshape2)
library(plyr)
library(quantreg)
library(bio3d)

# load functions
source("FUNCTIONS/ReadCA.R") 
source("FUNCTIONS/CalculateSideChainCM.R")
source(file.path(data.dir, "multiplot.R"))
source(file.path(data.dir, "my-functions.R"))
```

```{r set-file-names}
# set input filenames

## CM
data.dir <- paste("OUT/out_subset_CM_ANM", sep = "")
R0 = R0.CM

## data
reference.fname = file.path(data.dir, paste(family, "_ref.txt", sep = ""))
protein_list.fname = file.path(data.dir, paste(family, "_list.txt", sep = ""))

## profiles to compare
dri2.exp.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.exp.norm.dr.squarei.csv", sep = ""))
dri2.medium.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_medium.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
dri2.mut.fname = file.path(data.dir,paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))

## consurf
score.fname = file.path(data.dir, paste(p.ref, "_consurf.csv", sep = ""))
sim.data.mut.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_out_df.data.csv", sep = ""))
sim.data.medium.sel.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_medium.sel_out_df.data.csv", sep = ""))
```

```{r set-reference-protein}
# which is the reference protein?
reference = as.character(read.table(reference.fname, header = F)[1, 1])
if (reference != p.ref) {
  print("Warning: different references")
}
```

In this case we studied the `r family` family. 
We used as reference for the ENM the protein with pdb code `r reference`. 
We simulated `r n.mut.p` mutants of this reference for each protein of the family.
The `r family` family is of the type `r type` and consists of the following proteins:

```{r set-experimental-protein-names}
# experimental protein names
protein.exp = read.table(protein_list.fname, header = F, stringsAsFactors = F)[, 1]
protein.exp = protein.exp[protein.exp != reference]
print(protein.exp)
```

```{r set-site-info, include = FALSE}

# read reference pdb and calculate resno, AA, and CN
reference.pdb.fname = file.path(data.dir,paste(reference, ".pdb", sep = ""))
ref.pdb = read.pdb(reference.pdb.fname)
inds = atom.select(ref.pdb, elety = "CA")
ref.pdb.ca = ref.pdb$atom[inds$atom, ]
n.sites = length(ref.pdb.ca$resid)
AA = ref.pdb.ca$resid
resno = seq(1:n.sites)
pdb.info = data.frame(resno, AA)
names(pdb.info) = c("resno", "AA")
print(n.sites)

site.info = pdb.info

### CA ###

# calculate CN
R0 = 5
cmap.ca.1 = cmap(ref.pdb$xyz[inds$xyz], dcut = R0, scut = 0, mask.lower = F)
CN.1.CA = rowSums(cmap.ca.1, na.rm = T) - 1 # diag(cmap.ca) returned by cmap is 1!

R0 = 7.5
cmap.ca.2 = cmap(ref.pdb$xyz[inds$xyz], dcut = R0, scut = 0, mask.lower = F)
CN.2.CA = rowSums(cmap.ca.2, na.rm = T) - 1 # diag(cmap.ca) returned by cmap is 1!

R0 = 10
cmap.ca.3 = cmap(ref.pdb$xyz[inds$xyz], dcut = R0, scut = 0, mask.lower = F)
CN.3.CA = rowSums(cmap.ca.3, na.rm = T) - 1 # diag(cmap.ca) returned by cmap is 1!

R0 = 12.5
cmap.ca.4 = cmap(ref.pdb$xyz[inds$xyz], dcut = R0, scut = 0, mask.lower = F)
CN.4.CA = rowSums(cmap.ca.4, na.rm = T) - 1 # diag(cmap.ca) returned by cmap is 1!

R0 = 15
cmap.ca.5 = cmap(ref.pdb$xyz[inds$xyz], dcut = R0, scut = 0, mask.lower = F)
CN.5.CA = rowSums(cmap.ca.5, na.rm = T) - 1 # diag(cmap.ca) returned by cmap is 1!

R0 = 17.5
cmap.ca.6 = cmap(ref.pdb$xyz[inds$xyz], dcut = R0, scut = 0, mask.lower = F)
CN.6.CA = rowSums(cmap.ca.6, na.rm = T) - 1 # diag(cmap.ca) returned by cmap is 1!

R0 = 20
cmap.ca.7 = cmap(ref.pdb$xyz[inds$xyz], dcut = R0, scut = 0, mask.lower = F)
CN.7.CA = rowSums(cmap.ca.7, na.rm = T) - 1 # diag(cmap.ca) returned by cmap is 1!

# calculate WCN
r.p.ref = matrix(ref.pdb$xyz[inds$xyz], nrow=3)
dist.r.p.ref = dist.xyz(t(r.p.ref))
WCN.CA = c()
for (i in (1:ncol(r.p.ref))) {
  WCN.CA[i] = sum(1/dist.r.p.ref[i, -i]^2)
}

### CM ###

# Read PDB of p.ref
pdb.ca = ReadCA(reference.pdb.fname, chain.p.ref)
r.ca.p.ref = pdb.ca$xyz.calpha
r.CM.p.ref = CalculateSideChainCM(reference.pdb.fname, chain.p.ref)
r.p.ref = cbind(r.CM.p.ref, r.ca.p.ref)

# calculate CN
R0 = 5
cmap.CM.1 = cmap(as.vector(r.p.ref), dcut = R0, scut = 0, mask.lower = F)
CN.1.CM = (rowSums(cmap.CM.1, na.rm = T) - 2)[1:ncol(r.CM.p.ref)]

R0 = 7.5
cmap.CM.2 = cmap(as.vector(r.p.ref), dcut = R0, scut = 0, mask.lower = F)
CN.2.CM = (rowSums(cmap.CM.2, na.rm = T) - 2)[1:ncol(r.CM.p.ref)]

R0 = 10
cmap.CM.3 = cmap(as.vector(r.p.ref), dcut = R0, scut = 0, mask.lower = F)
CN.3.CM = (rowSums(cmap.CM.3, na.rm = T) - 2)[1:ncol(r.CM.p.ref)]

R0 = 12.5
cmap.CM.4 = cmap(as.vector(r.p.ref), dcut = R0, scut = 0, mask.lower = F)
CN.4.CM = (rowSums(cmap.CM.4, na.rm = T) - 2)[1:ncol(r.CM.p.ref)]

R0 = 15
cmap.CM.5 = cmap(as.vector(r.p.ref), dcut = R0, scut = 0, mask.lower = F)
CN.5.CM = (rowSums(cmap.CM.5, na.rm = T) - 2)[1:ncol(r.CM.p.ref)]

R0 = 17.5
cmap.CM.6 = cmap(ref.pdb$xyz[inds$xyz], dcut = R0, scut = 0, mask.lower = F)
CN.6.CM = (rowSums(cmap.CM.6, na.rm = T) - 2)[1:ncol(r.CM.p.ref)]

R0 = 20
cmap.CM.7 = cmap(ref.pdb$xyz[inds$xyz], dcut = R0, scut = 0, mask.lower = F)
CN.7.CM = (rowSums(cmap.CM.6, na.rm = T) - 2)[1:ncol(r.CM.p.ref)]

# calculate WCN
dist.r.CM.p.ref = dist.xyz(t(r.p.ref))
WCN.CM = c()
for (i in (1:ncol(r.CM.p.ref))) {
  WCN.CM[i] = sum(1/dist.r.CM.p.ref[i, -c(i, (i + ncol(r.CM.p.ref)))]^2)
}

```

```{r read-data}
# read data
## exp
dri2.exp = read.csv(dri2.exp.fname, header = T)
site = site.info$site
rownames(dri2.exp) = paste("exp", rownames(dri2.exp), sep = "")

## mut
dri2.mut = read.csv(dri2.mut.fname, header = T)
rownames(dri2.mut) = paste("mut", rownames(dri2.mut), sep = "")

## medium
dri2.medium = read.csv(dri2.medium.fname, header = T)
rownames(dri2.medium) = paste("medium", rownames(dri2.medium), sep = "")
```

```{r prepare-site-data}
# prepare the data
## exp
tdri2.exp = as.data.frame(t(as.matrix(dri2.exp)))
tdri2.exp = cbind(site.info, tdri2.exp)
siteComparison.exp = melt(tdri2.exp, id.vars = names(site.info), variable.name = "protein", value.name = "dri2")

## mut
tdri2.mut = as.data.frame(t(as.matrix(dri2.mut)))
tdri2.mut = cbind(site.info, tdri2.mut)
siteComparison.mut = melt(tdri2.mut, id.vars = names(site.info), variable.name = "protein", value.name = "dri2")

## medium
tdri2.medium = as.data.frame(t(as.matrix(dri2.medium)))
tdri2.medium = cbind(site.info, tdri2.medium)
siteComparison.medium = melt(tdri2.medium, id.vars = names(site.info), variable.name = "protein", value.name = "dri2")

# bluild the data.frame
siteComparison.all.datasets = rbind(data.frame("dataset" = "exp", siteComparison.exp),
                                    data.frame("dataset" = "mut", siteComparison.mut),
                                    data.frame("dataset" = "medium", siteComparison.medium))

siteComparison.all.datasets = ddply(siteComparison.all.datasets, c("dataset", "protein"), mutate,
                     "n.SD" = dri2/mean(dri2, na.rm = T),
                     "z.SD" = vscale(dri2),
                      "RSD" = sqrt(dri2),
                    "n.RSD" = RSD/mean(RSD, na.rm = T),
                    "z.RSD" = vscale(RSD))
```

```{r mean-se-z.RSD-vs-site}
# comparison of z.RSD profiles with functional sites
## prepare dat
dat = siteComparison.all.datasets
dat$dataset = revalue(dat$dataset, c("medium" = "selection"))
dat$dataset = revalue(dat$dataset, c("mut" = "no-selection"))

## dat with means and standard errors
d = ddply(dat,c("dataset", "resno"), function(x) {
                mean.z.RSD = mean(x$z.RSD, na.rm = T)
                ndata = sum(!is.na(x$z.RSD))
                se.z.RSD = sd(x$z.RSD, na.rm = T) / sqrt(ndata)
                data.frame(mean.z.RSD, ndata, se.z.RSD)
})

# calculate correlations berween profiles
d.exp = subset(d, dataset == "exp")
d.mut = subset(d, dataset == "no-selection")
d.medium = subset(d, dataset == "selection")
```
### Sequence - structure comparison

1 = R0 5
2 = R0 7.5
3 = R0 10
4 = R0 12.5
5 = R0 15
6 = R0 17.5
7 = R0 20

```{r structure-CN-WCN-CA-comparison}

# compare profiles

CA.cor.p = c()
CA.cor.s = c()

## plot
par(pty = "s")

plot(x = d.exp$mean.z.RSD, y = log(CN.1.CA), xlab = "<zRSDi> experimental")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.1.CA))
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
CA.cor.p = c(CA.cor.p, r.exp.mean.z.RSD.CN)

r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.1.CA), method = "spearman")
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
CA.cor.s = c(CA.cor.s, r.exp.mean.z.RSD.CN)

########

plot(x = d.exp$mean.z.RSD, y = log(CN.2.CA), xlab = "<zRSDi> experimental")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.2.CA))
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
CA.cor.p = c(CA.cor.p, r.exp.mean.z.RSD.CN)

r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.2.CA), method = "spearman")
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
CA.cor.s = c(CA.cor.s, r.exp.mean.z.RSD.CN)

######
plot(x = d.exp$mean.z.RSD, y = log(CN.3.CA), xlab = "<zRSDi> experimental")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.3.CA))
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
CA.cor.p = c(CA.cor.p, r.exp.mean.z.RSD.CN)

r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.3.CA), method = "spearman")
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
CA.cor.s = c(CA.cor.s, r.exp.mean.z.RSD.CN)

#######
plot(x = d.exp$mean.z.RSD, y = log(CN.4.CA), xlab = "<zRSDi> experimental")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.4.CA))
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
CA.cor.p = c(CA.cor.p, r.exp.mean.z.RSD.CN)

r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.4.CA), method = "spearman")
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
CA.cor.s = c(CA.cor.s, r.exp.mean.z.RSD.CN)

#####
plot(x = d.exp$mean.z.RSD, y = log(CN.5.CA), xlab = "<zRSDi> experimental")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.5.CA))
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
CA.cor.p = c(CA.cor.p, r.exp.mean.z.RSD.CN)

r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.5.CA), method = "spearman")
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
CA.cor.s = c(CA.cor.s, r.exp.mean.z.RSD.CN)

#####
plot(x = d.exp$mean.z.RSD, y = log(CN.6.CA), xlab = "<zRSDi> experimental")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.6.CA))
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
CA.cor.p = c(CA.cor.p, r.exp.mean.z.RSD.CN)

r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.6.CA), method = "spearman")
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
CA.cor.s = c(CA.cor.s, r.exp.mean.z.RSD.CN)

#####
plot(x = d.exp$mean.z.RSD, y = log(CN.7.CA), xlab = "<zRSDi> experimental")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.7.CA))
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
CA.cor.p = c(CA.cor.p, r.exp.mean.z.RSD.CN)

r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.7.CA), method = "spearman")
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
CA.cor.s = c(CA.cor.s, r.exp.mean.z.RSD.CN)

# WCN
plot(x = d.exp$mean.z.RSD, y = log(WCN.CA), xlab = "<zRSDi> experimental")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(WCN.CA))
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(WCN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (WCN)")
CA.cor.p = c(CA.cor.p, r.exp.mean.z.RSD.CN)

r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(WCN.CA), method = "spearman")
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(WCN)"),
                             "R" = r.exp.mean.z.RSD.CN)

knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (WCN)")
CA.cor.s = c(CA.cor.s, r.exp.mean.z.RSD.CN)

```

```{r structure-CN-WCN-CM-comparison}

# compare profiles

CM.cor.p = c()
CM.cor.s = c()

## plot
par(pty = "s")

plot(x = d.exp$mean.z.RSD, y = log(CN.1.CM), xlab = "<zRSDi> experimental")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.1.CM))
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
CM.cor.p = c(CM.cor.p, r.exp.mean.z.RSD.CN)

r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.1.CM), method = "spearman")
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
CM.cor.s = c(CM.cor.s, r.exp.mean.z.RSD.CN)

########

plot(x = d.exp$mean.z.RSD, y = log(CN.2.CM), xlab = "<zRSDi> experimental")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.2.CM))
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
CM.cor.p = c(CM.cor.p, r.exp.mean.z.RSD.CN)

r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.2.CM), method = "spearman")
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
CM.cor.s = c(CM.cor.s, r.exp.mean.z.RSD.CN)

######
plot(x = d.exp$mean.z.RSD, y = log(CN.3.CM), xlab = "<zRSDi> experimental")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.3.CM))
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
CM.cor.p = c(CM.cor.p, r.exp.mean.z.RSD.CN)

r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.3.CM), method = "spearman")
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
CM.cor.s = c(CM.cor.s, r.exp.mean.z.RSD.CN)

#######
plot(x = d.exp$mean.z.RSD, y = log(CN.4.CM), xlab = "<zRSDi> experimental")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.4.CM))
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
CM.cor.p = c(CM.cor.p, r.exp.mean.z.RSD.CN)

r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.4.CM), method = "spearman")
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
CM.cor.s = c(CM.cor.s, r.exp.mean.z.RSD.CN)

#####
plot(x = d.exp$mean.z.RSD, y = log(CN.5.CM), xlab = "<zRSDi> experimental")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.5.CM))
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
CM.cor.p = c(CM.cor.p, r.exp.mean.z.RSD.CN)

r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.5.CM), method = "spearman")
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
CM.cor.s = c(CM.cor.s, r.exp.mean.z.RSD.CN)

#####
plot(x = d.exp$mean.z.RSD, y = log(CN.6.CM), xlab = "<zRSDi> experimental")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.6.CM))
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
CM.cor.p = c(CM.cor.p, r.exp.mean.z.RSD.CN)

r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.6.CM), method = "spearman")
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
CM.cor.s = c(CM.cor.s, r.exp.mean.z.RSD.CN)

#####
plot(x = d.exp$mean.z.RSD, y = log(CN.7.CM), xlab = "<zRSDi> experimental")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.7.CM))
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
CM.cor.p = c(CM.cor.p, r.exp.mean.z.RSD.CN)

r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.7.CM), method = "spearman")
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
CM.cor.s = c(CM.cor.s, r.exp.mean.z.RSD.CN)

# WCN
plot(x = d.exp$mean.z.RSD, y = log(WCN.CM), xlab = "<zRSDi> experimental")

## calculate correlations
r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(WCN.CM))
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(WCN)"),
                             "R" = r.exp.mean.z.RSD.CN)
knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (WCN)")
CM.cor.p = c(CM.cor.p, r.exp.mean.z.RSD.CN)

r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(WCN.CM), method = "spearman")
cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(WCN)"),
                             "R" = r.exp.mean.z.RSD.CN)

knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (WCN)")
CM.cor.s = c(CM.cor.s, r.exp.mean.z.RSD.CN)
```

### All correlations

```{r correlations}
# build a data frame
cor = data.frame("CA pearson" = CA.cor.p,
                 "CM pearson" = CM.cor.p,
                 "CA spearman" = CA.cor.s,
                 "CM spearman" = CM.cor.s)
rownames(cor) = c("CN R0 = 5", "CN R0 = 7.5", "CN R0 = 10", "CN R0 = 12.5", "CN R0 = 15", "CN R0 = 17.5", "CN R0 = 20", "WCN")
knitr::kable(cor, digits = 2, caption = "Correlation structure (<z.RSD>) - sequence (CN/WCN)")
```

### 2017-06-04 analysis-structure-CN-WCN.Rmd
estructura-CN/WCN

--- 2017-06-04 analysis-structure-CN-WCN-exp.Rmd
@@
 # compare profiles
+## plot
+par(pty = "s")
 
-CA.cor.p = c()
-CA.cor.s = c()
+plot(x = d.exp$mean.z.RSD, y = log(CN.1.CA), xlab = "<zRSDi> experimental")
+plot(x = d.mut$mean.z.RSD, y = log(CN.1.CA), xlab = "<zRSDi> no-selection")
+plot(x = d.medium$mean.z.RSD, y = log(CN.1.CA), xlab = "<zRSDi> selection")
+
+## calculate correlations
+r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.1.CA))
+r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN.1.CA))
+r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN.1.CA))
+
+cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
+                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))
+
+knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
+
+## calculate correlations
+r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.1.CA), method = "spearman")
+r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN.1.CA), method = "spearman")
+r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN.1.CA), method = "spearman")
+
+cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
+                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))
+
+knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
+
+########
 
@@
 
-plot(x = d.exp$mean.z.RSD, y = log(CN.1.CA), xlab = "<zRSDi> experimental")
-
-## calculate correlations
-r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.1.CA))
-cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
-                             "R" = r.exp.mean.z.RSD.CN)
-knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
-CA.cor.p = c(CA.cor.p, r.exp.mean.z.RSD.CN)
-
-r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.1.CA), method = "spearman")
-cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
-                             "R" = r.exp.mean.z.RSD.CN)
-knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
-CA.cor.s = c(CA.cor.s, r.exp.mean.z.RSD.CN)
-
-########
-
 plot(x = d.exp$mean.z.RSD, y = log(CN.2.CA), xlab = "<zRSDi> experimental")
+plot(x = d.mut$mean.z.RSD, y = log(CN.2.CA), xlab = "<zRSDi> no-selection")
+plot(x = d.medium$mean.z.RSD, y = log(CN.2.CA), xlab = "<zRSDi> selection")
 
@@
 r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.2.CA))
-cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
-                             "R" = r.exp.mean.z.RSD.CN)
+r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN.2.CA))
+r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN.2.CA))
+
+cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
+                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))
+
 knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
-CA.cor.p = c(CA.cor.p, r.exp.mean.z.RSD.CN)
 
+## calculate correlations
 r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.2.CA), method = "spearman")
-cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
-                             "R" = r.exp.mean.z.RSD.CN)
+r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN.2.CA), method = "spearman")
+r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN.2.CA), method = "spearman")
+
+cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
+                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))
+
 knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
-CA.cor.s = c(CA.cor.s, r.exp.mean.z.RSD.CN)
 
 ######
+## plot
+par(pty = "s")
+
 plot(x = d.exp$mean.z.RSD, y = log(CN.3.CA), xlab = "<zRSDi> experimental")
+plot(x = d.mut$mean.z.RSD, y = log(CN.3.CA), xlab = "<zRSDi> no-selection")
+plot(x = d.medium$mean.z.RSD, y = log(CN.3.CA), xlab = "<zRSDi> selection")
 
@@
 r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.3.CA))
-cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
-                             "R" = r.exp.mean.z.RSD.CN)
+r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN.3.CA))
+r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN.3.CA))
+
+cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
+                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))
+
 knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
-CA.cor.p = c(CA.cor.p, r.exp.mean.z.RSD.CN)
 
+## calculate correlations
 r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.3.CA), method = "spearman")
-cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
-                             "R" = r.exp.mean.z.RSD.CN)
+r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN.3.CA), method = "spearman")
+r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN.3.CA), method = "spearman")
+
+cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
+                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))
+
 knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
-CA.cor.s = c(CA.cor.s, r.exp.mean.z.RSD.CN)
 
 #######
+## plot
+par(pty = "s")
+
 plot(x = d.exp$mean.z.RSD, y = log(CN.4.CA), xlab = "<zRSDi> experimental")
+plot(x = d.mut$mean.z.RSD, y = log(CN.4.CA), xlab = "<zRSDi> no-selection")
+plot(x = d.medium$mean.z.RSD, y = log(CN.4.CA), xlab = "<zRSDi> selection")
 
@@
 r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.4.CA))
-cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
-                             "R" = r.exp.mean.z.RSD.CN)
+r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN.4.CA))
+r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN.4.CA))
+
+cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
+                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))
+
 knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
-CA.cor.p = c(CA.cor.p, r.exp.mean.z.RSD.CN)
 
+## calculate correlations
 r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.4.CA), method = "spearman")
-cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
-                             "R" = r.exp.mean.z.RSD.CN)
+r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN.4.CA), method = "spearman")
+r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN.4.CA), method = "spearman")
+
+cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
+                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))
+
 knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
-CA.cor.s = c(CA.cor.s, r.exp.mean.z.RSD.CN)
 
 #####
+## plot
+par(pty = "s")
+
 plot(x = d.exp$mean.z.RSD, y = log(CN.5.CA), xlab = "<zRSDi> experimental")
+plot(x = d.mut$mean.z.RSD, y = log(CN.5.CA), xlab = "<zRSDi> no-selection")
+plot(x = d.medium$mean.z.RSD, y = log(CN.5.CA), xlab = "<zRSDi> selection")
 
@@
 r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.5.CA))
-cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
-                             "R" = r.exp.mean.z.RSD.CN)
+r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN.5.CA))
+r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN.5.CA))
+
+cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
+                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))
+
 knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
-CA.cor.p = c(CA.cor.p, r.exp.mean.z.RSD.CN)
 
+## calculate correlations
 r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.5.CA), method = "spearman")
-cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
-                             "R" = r.exp.mean.z.RSD.CN)
+r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN.5.CA), method = "spearman")
+r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN.5.CA), method = "spearman")
+
+cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
+                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))
+
 knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
-CA.cor.s = c(CA.cor.s, r.exp.mean.z.RSD.CN)
 
 #####
+## plot
+par(pty = "s")
+
 plot(x = d.exp$mean.z.RSD, y = log(CN.6.CA), xlab = "<zRSDi> experimental")
+plot(x = d.mut$mean.z.RSD, y = log(CN.6.CA), xlab = "<zRSDi> no-selection")
+plot(x = d.medium$mean.z.RSD, y = log(CN.6.CA), xlab = "<zRSDi> selection")
 
@@
 r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.6.CA))
-cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
-                             "R" = r.exp.mean.z.RSD.CN)
+r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN.6.CA))
+r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN.6.CA))
+
+cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
+                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))
+
 knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
-CA.cor.p = c(CA.cor.p, r.exp.mean.z.RSD.CN)
 
+## calculate correlations
 r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.6.CA), method = "spearman")
-cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
-                             "R" = r.exp.mean.z.RSD.CN)
+r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN.6.CA), method = "spearman")
+r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN.6.CA), method = "spearman")
+
+cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
+                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))
+
 knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
-CA.cor.s = c(CA.cor.s, r.exp.mean.z.RSD.CN)
 
 #####
+## plot
+par(pty = "s")
+
 plot(x = d.exp$mean.z.RSD, y = log(CN.7.CA), xlab = "<zRSDi> experimental")
+plot(x = d.mut$mean.z.RSD, y = log(CN.7.CA), xlab = "<zRSDi> no-selection")
+plot(x = d.medium$mean.z.RSD, y = log(CN.7.CA), xlab = "<zRSDi> selection")
 
@@
 r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.7.CA))
-cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
-                             "R" = r.exp.mean.z.RSD.CN)
+r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN.7.CA))
+r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN.7.CA))
+
+cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
+                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))
+
 knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
-CA.cor.p = c(CA.cor.p, r.exp.mean.z.RSD.CN)
 
+## calculate correlations
 r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.7.CA), method = "spearman")
-cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
-                             "R" = r.exp.mean.z.RSD.CN)
+r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN.7.CA), method = "spearman")
+r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN.7.CA), method = "spearman")
+
+cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
+                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))
+
 knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
-CA.cor.s = c(CA.cor.s, r.exp.mean.z.RSD.CN)
 
 # WCN
+## plot
+par(pty = "s")
+
 plot(x = d.exp$mean.z.RSD, y = log(WCN.CA), xlab = "<zRSDi> experimental")
+plot(x = d.mut$mean.z.RSD, y = log(WCN.CA), xlab = "<zRSDi> no-selection")
+plot(x = d.medium$mean.z.RSD, y = log(WCN.CA), xlab = "<zRSDi> selection")
 
@@
 r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(WCN.CA))
-cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(WCN)"),
-                             "R" = r.exp.mean.z.RSD.CN)
+r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(WCN.CA))
+r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(WCN.CA))
+
+cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(WCN)", "<z.RSD> no-selection vs log(WCN)", "<z.RSD> selection vs log(WCN)"),
+                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))
+
 knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (WCN)")
-CA.cor.p = c(CA.cor.p, r.exp.mean.z.RSD.CN)
 
+## calculate correlations
 r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(WCN.CA), method = "spearman")
-cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(WCN)"),
-                             "R" = r.exp.mean.z.RSD.CN)
+r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(WCN.CA), method = "spearman")
+r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(WCN.CA), method = "spearman")
+
+cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(WCN)", "<z.RSD> no-selection vs log(WCN)", "<z.RSD> selection vs log(WCN)"),
+                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))
 
 knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (WCN)")
-CA.cor.s = c(CA.cor.s, r.exp.mean.z.RSD.CN)
 
@@
 # compare profiles
+## plot
+par(pty = "s")
 
-CM.cor.p = c()
-CM.cor.s = c()
+plot(x = d.exp$mean.z.RSD, y = log(CN.1.CM), xlab = "<zRSDi> experimental")
+plot(x = d.mut$mean.z.RSD, y = log(CN.1.CM), xlab = "<zRSDi> no-selection")
+plot(x = d.medium$mean.z.RSD, y = log(CN.1.CM), xlab = "<zRSDi> selection")
+
+## calculate correlations
+r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.1.CM))
+r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN.1.CM))
+r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN.1.CM))
+
+cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
+                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))
+
+knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
+
+## calculate correlations
+r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.1.CM), method = "spearman")
+r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN.1.CM), method = "spearman")
+r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN.1.CM), method = "spearman")
+
+cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
+                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))
+
+knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
+
+########
 
@@
 
-plot(x = d.exp$mean.z.RSD, y = log(CN.1.CM), xlab = "<zRSDi> experimental")
-
-## calculate correlations
-r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.1.CM))
-cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
-                             "R" = r.exp.mean.z.RSD.CN)
-knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
-CM.cor.p = c(CM.cor.p, r.exp.mean.z.RSD.CN)
-
-r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.1.CM), method = "spearman")
-cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
-                             "R" = r.exp.mean.z.RSD.CN)
-knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
-CM.cor.s = c(CM.cor.s, r.exp.mean.z.RSD.CN)
-
-########
-
 plot(x = d.exp$mean.z.RSD, y = log(CN.2.CM), xlab = "<zRSDi> experimental")
+plot(x = d.mut$mean.z.RSD, y = log(CN.2.CM), xlab = "<zRSDi> no-selection")
+plot(x = d.medium$mean.z.RSD, y = log(CN.2.CM), xlab = "<zRSDi> selection")
 
@@
 r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.2.CM))
-cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
-                             "R" = r.exp.mean.z.RSD.CN)
+r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN.2.CM))
+r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN.2.CM))
+
+cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
+                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))
+
 knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
-CM.cor.p = c(CM.cor.p, r.exp.mean.z.RSD.CN)
 
+## calculate correlations
 r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.2.CM), method = "spearman")
-cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
-                             "R" = r.exp.mean.z.RSD.CN)
+r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN.2.CM), method = "spearman")
+r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN.2.CM), method = "spearman")
+
+cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
+                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))
+
 knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
-CM.cor.s = c(CM.cor.s, r.exp.mean.z.RSD.CN)
 
 ######
+## plot
+par(pty = "s")
+
 plot(x = d.exp$mean.z.RSD, y = log(CN.3.CM), xlab = "<zRSDi> experimental")
+plot(x = d.mut$mean.z.RSD, y = log(CN.3.CM), xlab = "<zRSDi> no-selection")
+plot(x = d.medium$mean.z.RSD, y = log(CN.3.CM), xlab = "<zRSDi> selection")
 
@@
 r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.3.CM))
-cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
-                             "R" = r.exp.mean.z.RSD.CN)
+r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN.3.CM))
+r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN.3.CM))
+
+cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
+                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))
+
 knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
-CM.cor.p = c(CM.cor.p, r.exp.mean.z.RSD.CN)
 
+## calculate correlations
 r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.3.CM), method = "spearman")
-cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
-                             "R" = r.exp.mean.z.RSD.CN)
+r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN.3.CM), method = "spearman")
+r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN.3.CM), method = "spearman")
+
+cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
+                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))
+
 knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
-CM.cor.s = c(CM.cor.s, r.exp.mean.z.RSD.CN)
 
 #######
+## plot
+par(pty = "s")
+
 plot(x = d.exp$mean.z.RSD, y = log(CN.4.CM), xlab = "<zRSDi> experimental")
+plot(x = d.mut$mean.z.RSD, y = log(CN.4.CM), xlab = "<zRSDi> no-selection")
+plot(x = d.medium$mean.z.RSD, y = log(CN.4.CM), xlab = "<zRSDi> selection")
 
@@
 r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.4.CM))
-cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
-                             "R" = r.exp.mean.z.RSD.CN)
+r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN.4.CM))
+r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN.4.CM))
+
+cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
+                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))
+
 knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
-CM.cor.p = c(CM.cor.p, r.exp.mean.z.RSD.CN)
 
+## calculate correlations
 r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.4.CM), method = "spearman")
-cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
-                             "R" = r.exp.mean.z.RSD.CN)
+r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN.4.CM), method = "spearman")
+r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN.4.CM), method = "spearman")
+
+cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
+                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))
+
 knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
-CM.cor.s = c(CM.cor.s, r.exp.mean.z.RSD.CN)
 
 #####
+## plot
+par(pty = "s")
+
 plot(x = d.exp$mean.z.RSD, y = log(CN.5.CM), xlab = "<zRSDi> experimental")
+plot(x = d.mut$mean.z.RSD, y = log(CN.5.CM), xlab = "<zRSDi> no-selection")
+plot(x = d.medium$mean.z.RSD, y = log(CN.5.CM), xlab = "<zRSDi> selection")
 
@@
 r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.5.CM))
-cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
-                             "R" = r.exp.mean.z.RSD.CN)
+r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN.5.CM))
+r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN.5.CM))
+
+cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
+                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))
+
 knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
-CM.cor.p = c(CM.cor.p, r.exp.mean.z.RSD.CN)
 
+## calculate correlations
 r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.5.CM), method = "spearman")
-cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
-                             "R" = r.exp.mean.z.RSD.CN)
+r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN.5.CM), method = "spearman")
+r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN.5.CM), method = "spearman")
+
+cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
+                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))
+
 knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
-CM.cor.s = c(CM.cor.s, r.exp.mean.z.RSD.CN)
 
 #####
+## plot
+par(pty = "s")
+
 plot(x = d.exp$mean.z.RSD, y = log(CN.6.CM), xlab = "<zRSDi> experimental")
+plot(x = d.mut$mean.z.RSD, y = log(CN.6.CM), xlab = "<zRSDi> no-selection")
+plot(x = d.medium$mean.z.RSD, y = log(CN.6.CM), xlab = "<zRSDi> selection")
 
@@
 r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.6.CM))
-cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
-                             "R" = r.exp.mean.z.RSD.CN)
+r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN.6.CM))
+r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN.6.CM))
+
+cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
+                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))
+
 knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
-CM.cor.p = c(CM.cor.p, r.exp.mean.z.RSD.CN)
 
+## calculate correlations
 r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.6.CM), method = "spearman")
-cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
-                             "R" = r.exp.mean.z.RSD.CN)
+r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN.6.CM), method = "spearman")
+r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN.6.CM), method = "spearman")
+
+cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
+                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))
+
 knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
-CM.cor.s = c(CM.cor.s, r.exp.mean.z.RSD.CN)
 
 #####
+## plot
+par(pty = "s")
+
 plot(x = d.exp$mean.z.RSD, y = log(CN.7.CM), xlab = "<zRSDi> experimental")
+plot(x = d.mut$mean.z.RSD, y = log(CN.7.CM), xlab = "<zRSDi> no-selection")
+plot(x = d.medium$mean.z.RSD, y = log(CN.7.CM), xlab = "<zRSDi> selection")
 
@@
 r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.7.CM))
-cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
-                             "R" = r.exp.mean.z.RSD.CN)
+r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN.7.CM))
+r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN.7.CM))
+
+cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
+                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))
+
 knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
-CM.cor.p = c(CM.cor.p, r.exp.mean.z.RSD.CN)
 
+## calculate correlations
 r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN.7.CM), method = "spearman")
-cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)"),
-                             "R" = r.exp.mean.z.RSD.CN)
+r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN.7.CM), method = "spearman")
+r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN.7.CM), method = "spearman")
+
+cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
+                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))
+
 knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
-CM.cor.s = c(CM.cor.s, r.exp.mean.z.RSD.CN)
 
 # WCN
+## plot
+par(pty = "s")
+
 plot(x = d.exp$mean.z.RSD, y = log(WCN.CM), xlab = "<zRSDi> experimental")
+plot(x = d.mut$mean.z.RSD, y = log(WCN.CM), xlab = "<zRSDi> no-selection")
+plot(x = d.medium$mean.z.RSD, y = log(WCN.CM), xlab = "<zRSDi> selection")
 
@@
 r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(WCN.CM))
-cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(WCN)"),
-                             "R" = r.exp.mean.z.RSD.CN)
+r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(WCN.CM))
+r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(WCN.CM))
+
+cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(WCN)", "<z.RSD> no-selection vs log(WCN)", "<z.RSD> selection vs log(WCN)"),
+                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))
+
 knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (WCN)")
-CM.cor.p = c(CM.cor.p, r.exp.mean.z.RSD.CN)
 
+## calculate correlations
 r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(WCN.CM), method = "spearman")
-cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(WCN)"),
-                             "R" = r.exp.mean.z.RSD.CN)
+r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(WCN.CM), method = "spearman")
+r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(WCN.CM), method = "spearman")
+
+cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(WCN)", "<z.RSD> no-selection vs log(WCN)", "<z.RSD> selection vs log(WCN)"),
+                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))
 
 knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (WCN)")
-CM.cor.s = c(CM.cor.s, r.exp.mean.z.RSD.CN)
+
 ```
-
-### All correlations
-
-```{r correlations}
-# build a data frame
-cor = data.frame("CA pearson" = CA.cor.p,
-                 "CM pearson" = CM.cor.p,
-                 "CA spearman" = CA.cor.s,
-                 "CM spearman" = CM.cor.s)
-rownames(cor) = c("CN R0 = 5", "CN R0 = 7.5", "CN R0 = 10", "CN R0 = 12.5", "CN R0 = 15", "CN R0 = 17.5", "CN R0 = 20", "WCN")
-knitr::kable(cor, digits = 2, caption = "Correlation structure (<z.RSD>) - sequence (CN/WCN)")
-```

### 2017-06-04 analysis-structure-core.Rmd
estructura-CN/WCN

@@
 names(pdb.info) = c("resno", "AA", paste("CN", as.character(R0), sep = ""))
+
+# calculate WCN
+
+r.p.ref = matrix(ref.pdb$xyz[inds$xyz], nrow=3)
+dist.r.p.ref = dist.xyz(t(r.p.ref))
+WCN = c()
+for (i in (1:ncol(r.p.ref))) {
+  WCN[i] = sum(1/dist.r.p.ref[i, -i]^2)
+}
 
@@
 CN = CN[indexes.core]
+WCN = WCN[indexes.core]
 
@@
 ```
+
+### Sequence - structure comparison
+
+```{r structure-CN-comparison}
+
+# compare profiles
+## plot
+par(pty = "s")
+
+plot(x = d.exp$mean.z.RSD, y = log(CN), xlab = "<zRSDi> experimental")
+plot(x = d.mut$mean.z.RSD, y = log(CN), xlab = "<zRSDi> no-selection")
+plot(x = d.medium$mean.z.RSD, y = log(CN), xlab = "<zRSDi> selection")
+
+## calculate correlations
+r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN))
+r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN))
+r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN))
+
+cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
+                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))
+
+knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
+
+## calculate correlations
+r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN), method = "spearman")
+r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN), method = "spearman")
+r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN), method = "spearman")
+
+cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
+                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))
+
+knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
+
+# mean profiles
+
+CN.simple = CN[!duplicated(CN)]
+
+CN.i.mean = c()
+exp.mean.z.RSD.i.mean = c()
+mut.mean.z.RSD.i.mean = c()
+medium.mean.z.RSD.i.mean = c()
+
+count = 0
+for (i in (CN.simple)) {
+  count = count + 1
+  index = 0
+  for (j in (1:length(CN))){
+    if (CN[j] == i) {
+      index = cbind(index, j)
+    } 
+  }
+  CN.i.mean[count] = mean(CN[index])
+  exp.mean.z.RSD.i.mean[count] = mean(d.exp$mean.z.RSD[index])
+  mut.mean.z.RSD.i.mean[count] = mean(d.mut$mean.z.RSD[index])
+  medium.mean.z.RSD.i.mean[count] = mean(d.medium$mean.z.RSD[index])
+}
+
+## plot
+par(pty = "s")
+
+plot(x = exp.mean.z.RSD.i.mean, y = log(CN.i.mean), xlab = "mean <zRSDi> experimental for each CN", ylab = "log(CN)")
+plot(x = mut.mean.z.RSD.i.mean, y = log(CN.i.mean), xlab = "mean <zRSDi> no-selection for each CN", ylab = "log(CN)")
+plot(x = medium.mean.z.RSD.i.mean, y = log(CN.i.mean), xlab = "mean <zRSDi> selection for each CN", ylab = "log(CN)")
+
+## calculate correlations
+r.exp.mean.z.RSD.CN = cor(exp.mean.z.RSD.i.mean, log(CN.i.mean), method = "s")
+r.mut.mean.z.RSD.CN = cor(mut.mean.z.RSD.i.mean, log(CN.i.mean), method = "s")
+r.medium.mean.z.RSD.CN = cor(medium.mean.z.RSD.i.mean, log(CN.i.mean), method = "s")
+
+cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
+                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))
+
+knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
+
+## calculate correlations
+r.exp.mean.z.RSD.CN = cor(exp.mean.z.RSD.i.mean, log(CN.i.mean), method = "p")
+r.mut.mean.z.RSD.CN = cor(mut.mean.z.RSD.i.mean, log(CN.i.mean), method = "p")
+r.medium.mean.z.RSD.CN = cor(medium.mean.z.RSD.i.mean, log(CN.i.mean), method = "p")
+
+cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
+                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))
+
+knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
+```
+
+### Sequence - structure comparison WCN
+
+```{r structure-WCN-comparison}
+
+# compare profiles
+## plot
+par(pty = "s")
+
+plot(x = d.exp$mean.z.RSD, y = log(WCN), xlab = "<zRSDi> experimental")
+plot(x = d.mut$mean.z.RSD, y = log(WCN), xlab = "<zRSDi> no-selection")
+plot(x = d.medium$mean.z.RSD, y = log(WCN), xlab = "<zRSDi> selection")
+
+## calculate correlations
+r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(WCN))
+r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(WCN))
+r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(WCN))
+
+cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(WCN)", "<z.RSD> no-selection vs log(WCN)", "<z.RSD> selection vs log(WCN)"),
+                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))
+
+knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (WCN)")
+
+## calculate correlations
+r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(WCN), method = "spearman")
+r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(WCN), method = "spearman")
+r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(WCN), method = "spearman")
+
+cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(WCN)", "<z.RSD> no-selection vs log(WCN)", "<z.RSD> selection vs log(WCN)"),
+                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))
+
+knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (WCN)")
+
+```

### 2017-06-04 analysis-structure-pfANM.Rmd
estructura-CN/WCN

--- 2017-05-10 analysis-structure.Rmd
@@
 # load functions
+source(ReadCA.fname) 
+source(CalculateSideChainCM.fname)
 source(file.path(data.dir, "multiplot.R"))
 source(file.path(data.dir, "my-functions.R"))
-source("FUNCTIONS/readCA.R") 
 ```
@@
 ref.pdb.ca = ref.pdb$atom[inds$atom,]
-cmap.ca = cmap(ref.pdb$xyz[inds$xyz], dcut = R0, scut = 0, mask.lower = F)
-CN = rowSums(cmap.ca, na.rm = T) - 1 # diag(cmap.ca) returned by cmap is 1!
-n.sites = length(CN)
+n.sites = length(ref.pdb$xyz[inds$xyz])/3
 AA = ref.pdb.ca$resid
 resno = ref.pdb.ca$resno
-pdb.info = data.frame(resno, AA, CN)
-names(pdb.info) = c("resno", "AA", paste("CN", as.character(R0), sep = ""))
+pdb.info = data.frame(resno, AA)
+names(pdb.info) = c("resno", "AA")
+
+# calculate WCN
+r.p.ref = matrix(ref.pdb$xyz[inds$xyz], nrow=3)
+dist.r.p.ref = dist.xyz(t(r.p.ref))
+WCN = c()
+for (i in (1:ncol(r.p.ref))) {
+  WCN[i] = sum(1/dist.r.p.ref[i, -i]^2)
+}
 
@@
 contacts.active.sites = d$site[d$shell == 1]
-
 ```
@@
 
-```{r correlation-da-CN} 
+```{r correlation-da-WCN} 
 ## calculate correlations between profiles
-r.min.da.CA.CN = cor(CN[-active.site.index], m.min.da.CM.CA$min.da.CA[-active.site.index])
-r.min.da.CM.CN = cor(CN[-active.site.index], m.min.da.CM.CA$min.da.CM[-active.site.index])
+r.min.da.CA.WCN = cor(WCN[-active.site.index], m.min.da.CM.CA$min.da.CA[-active.site.index])
+r.min.da.CM.WCN = cor(WCN[-active.site.index], m.min.da.CM.CA$min.da.CM[-active.site.index])
 
-cor.df = data.frame("comparison" = c("CN vs min.da.CA", "CN vs min.da.CM"), "R" = c(r.min.da.CA.CN, r.min.da.CM.CN))
+cor.df = data.frame("comparison" = c("WCN vs min.da.CA", "WCN vs min.da.CM"), "R" = c(r.min.da.CA.WCN, r.min.da.CM.WCN))
 
-knitr::kable(cor.df, digits = 2, caption = "Correlation between CN and the minimal distance to the active site")
+knitr::kable(cor.df, digits = 2, caption = "Correlation between WCN and the minimal distance to the active site")
 
 ## calculate correlations between profiles
-r.sum.inv.da.CA.CN = cor(CN[-active.site.index], m.sum.inv.da.CM.CA$sum.inv.da.CA[-active.site.index])
-r.sum.inv.da.CM.CN = cor(CN[-active.site.index], m.sum.inv.da.CM.CA$sum.inv.da.CM[-active.site.index])
+r.sum.inv.da.CA.WCN = cor(WCN[-active.site.index], m.sum.inv.da.CM.CA$sum.inv.da.CA[-active.site.index])
+r.sum.inv.da.CM.WCN = cor(WCN[-active.site.index], m.sum.inv.da.CM.CA$sum.inv.da.CM[-active.site.index])
 
-cor.df = data.frame("comparison" = c("CN vs sum.inv.da.CA", "CN vs sum.inv.da.CM"), "R" = c(r.sum.inv.da.CA.CN, r.sum.inv.da.CM.CN))
+cor.df = data.frame("comparison" = c("WCN vs sum.inv.da.CA", "WCN vs sum.inv.da.CM"), "R" = c(r.sum.inv.da.CA.WCN, r.sum.inv.da.CM.WCN))
 
-knitr::kable(cor.df, digits = 2, caption = "Correlation between CN and the sum.inv distance to the active site")
+knitr::kable(cor.df, digits = 2, caption = "Correlation between WCN and the sum.inv distance to the active site")
 ```
@@
 
-# correct indexes
-if (data.dir == "OUT/out_subset_CM_ANM") {
-  mut.site.mut = mut.site.mut - n.sites
-  mut.site.medium.sel = mut.site.medium.sel - n.sites
-  CN.CM = sim.data.mut$CN
-  CN = c()
-
-  for (i in (1:n.sites)) {
-    CN[i] = CN.CM[which(mut.site.mut == i)][1]
-  }
-}
-
 for (i in (1:n.sites)) {
@@
 
-plot(x = p.accept.mut, y = log(CN))
+plot(x = p.accept.mut, y = log(WCN))
 plot(x = p.accept.mut, y = score)
-plot(x = score, y = log(CN))
+plot(x = score, y = log(WCN))
 
 ## calculate corelations
-r.p.accept.mut.CN = cor(p.accept.mut, log(CN))
+r.p.accept.mut.WCN = cor(p.accept.mut, log(WCN))
 r.p.accept.mut.score = cor(p.accept.mut, score)
-r.score.CN = cor(score, log(CN))
+r.score.WCN = cor(score, log(WCN))
 
-cor.df = data.frame("comparison" = c("paccept no-selection vs log(CN)", "paccept no-selection vs score", "score vs log(CN)"),
-                    "R" = c(r.p.accept.mut.CN , r.p.accept.mut.score, r.score.CN))
+cor.df = data.frame("comparison" = c("paccept no-selection vs log(WCN)", "paccept no-selection vs score", "score vs log(WCN)"),
+                    "R" = c(r.p.accept.mut.WCN , r.p.accept.mut.score, r.score.WCN))
 
@@
 
-plot(x = p.accept.medium.sel, y = log(CN))
+plot(x = p.accept.medium.sel, y = log(WCN))
 plot(x = p.accept.medium.sel, y = score)
-plot(x = score, y = log(CN))
+plot(x = score, y = log(WCN))
 
 ## calculate corelations
-r.p.accept.medium.sel.CN = cor(p.accept.medium.sel, log(CN))
+r.p.accept.medium.sel.WCN = cor(p.accept.medium.sel, log(WCN))
 r.p.accept.medium.sel.score = cor(p.accept.medium.sel, score)
-r.score.CN = cor(score, log(CN))
+r.score.WCN = cor(score, log(WCN))
 
-cor.df = data.frame("comparison" = c("paccept selection vs log(CN)", "paccept selection vs score", "score vs log(CN)"),
-                    "R" = c(r.p.accept.medium.sel.CN , r.p.accept.medium.sel.score, r.score.CN))
+cor.df = data.frame("comparison" = c("paccept selection vs log(WCN)", "paccept selection vs score", "score vs log(WCN)"),
+                    "R" = c(r.p.accept.medium.sel.WCN , r.p.accept.medium.sel.score, r.score.WCN))
 
@@
 
-```{r structure-CN-comparison}
+```{r structure-WCN-comparison}
 
@@
 
-plot(x = d.exp$mean.z.RSD, y = log(CN), xlab = "<zRSDi> experimental ")
-plot(x = d.mut$mean.z.RSD, y = log(CN), xlab = "<zRSDi> no-selection")
-plot(x = d.medium$mean.z.RSD, y = log(CN), xlab = "<zRSDi> selection")
+plot(x = d.exp$mean.z.RSD, y = log(WCN), xlab = "<zRSDi> experimental")
+plot(x = d.mut$mean.z.RSD, y = log(WCN), xlab = "<zRSDi> no-selection")
+plot(x = d.medium$mean.z.RSD, y = log(WCN), xlab = "<zRSDi> selection")
 
 ## calculate correlations
-r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN))
-r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN))
-r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN))
+r.exp.mean.z.RSD.WCN = cor(d.exp$mean.z.RSD, log(WCN))
+r.mut.mean.z.RSD.WCN = cor(d.mut$mean.z.RSD, log(WCN))
+r.medium.mean.z.RSD.WCN = cor(d.medium$mean.z.RSD, log(WCN))
 
-cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
-                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))
+cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(WCN)", "<z.RSD> no-selection vs log(WCN)", "<z.RSD> selection vs log(WCN)"),
+                    "R" = c(r.exp.mean.z.RSD.WCN , r.mut.mean.z.RSD.WCN, r.medium.mean.z.RSD.WCN))
 
-knitr::kable(cor.df, digits = 2, caption = "Correlation structure (<z.RSD>) - sequence (CN)")
+knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (WCN)")
+
+## calculate correlations
+r.exp.mean.z.RSD.WCN = cor(d.exp$mean.z.RSD, log(WCN), method = "spearman")
+r.mut.mean.z.RSD.WCN = cor(d.mut$mean.z.RSD, log(WCN), method = "spearman")
+r.medium.mean.z.RSD.WCN = cor(d.medium$mean.z.RSD, log(WCN), method = "spearman")
+
+cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(WCN)", "<z.RSD> no-selection vs log(WCN)", "<z.RSD> selection vs log(WCN)"),
+                    "R" = c(r.exp.mean.z.RSD.WCN , r.mut.mean.z.RSD.WCN, r.medium.mean.z.RSD.WCN))
+
+knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (WCN)")
+
 ```

### 2017-06-04 analysis-structure.Rmd
estructura-CN/WCN

@@
 
-knitr::kable(cor.df, digits = 2, caption = "Correlation structure (<z.RSD>) - sequence (CN)")
+knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
+
+## calculate correlations
+r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN), method = "spearman")
+r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN), method = "spearman")
+r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN), method = "spearman")
+
+cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
+                    "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))
+
+knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
 ```

### 2017-06-25 analysis-MSF-SD-RSD.Rmd
23/6/17

--- 2017-04-23 analysis-dynamical-MSF-structure.Rmd
@@
 ---
-
 # Introduction
-We study the evolutionary divergence of proteins using the LF-ENM and comparing simulated mutants with experimental data.
+In this report we compare structural divergence profiles in cartesian coordinates (RMSD and MSD) with the Mean Square Fluctuation (MSF) of the sites.
 
@@
 ```
+
 ```{r load-packages}
@@
 ## profiles to compare
-### square.dif.MSF
-square.dif.MSF.exp.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.exp.square.dif.MSF.csv", sep = ""))
-square.dif.MSF.medium.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_medium.sel_K.analysis_Keff_out_m.theo.square.dif.MSF.csv", sep = ""))
-square.dif.MSF.mut.fname = file.path(data.dir,paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.square.dif.MSF.csv", sep = ""))
-
 ### dri2
@@
 dri2.mut.fname = file.path(data.dir,paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
+```
 
-```
 ```{r set-reference-protein}
@@
 resno = ref.pdb.ca$resno
+
 pdb.info = data.frame(resno, AA, CN)
@@
 ```{r read-site-data}
-# read MSF data
-square.dif.MSF.exp = read.csv(square.dif.MSF.exp.fname, header = T)
-square.dif.MSF.mut = read.csv(square.dif.MSF.mut.fname, header = T)
-square.dif.MSF.medium = read.csv(square.dif.MSF.medium.fname, header = T)
-
 # read dri2 data
@@
 
-```{r MSF-p.ref}
-# calculate MSF (Mean Square Fluctuation)
-
+```{r calculate-MSF-p.ref}
+# calculate MSF of p.ref (Mean Square Fluctuation)
 ## calculate ENM
@@
 
-```{r prepare-site-data-MSF}
-# prepare the data
-## exp
-tsquare.dif.MSF.exp = as.data.frame(t(as.matrix(square.dif.MSF.exp)))
-tsquare.dif.MSF.exp = cbind(site.info, tsquare.dif.MSF.exp)
-siteComparison.exp = melt(tsquare.dif.MSF.exp, id.vars = names(site.info), variable.name = "protein", value.name = "square.dif.MSF")
-
-## mut
-tsquare.dif.MSF.mut = as.data.frame(t(as.matrix(square.dif.MSF.mut)))
-tsquare.dif.MSF.mut = cbind(site.info, tsquare.dif.MSF.mut)
-siteComparison.mut = melt(tsquare.dif.MSF.mut, id.vars = names(site.info), variable.name = "protein", value.name = "square.dif.MSF")
-
-## medium
-tsquare.dif.MSF.medium = as.data.frame(t(as.matrix(square.dif.MSF.medium)))
-tsquare.dif.MSF.medium = cbind(site.info, tsquare.dif.MSF.medium)
-siteComparison.medium = melt(tsquare.dif.MSF.medium, id.vars = names(site.info), variable.name = "protein", value.name = "square.dif.MSF")
-
-# bluild the data.frame
-siteComparison.all.datasets = rbind(data.frame("dataset" = "exp", siteComparison.exp),
-                                    data.frame("dataset" = "mut", siteComparison.mut),
-                                    data.frame("dataset" = "medium", siteComparison.medium))
-
-siteComparison.all.datasets = ddply(siteComparison.all.datasets, c("dataset", "protein"), mutate,
-          "r.SDF" = rank(square.dif.MSF, na.last = "keep")) 
-```
-
 ```{r prepare-site-data-dri2}
@@
           "RSD" = sqrt(dri2), 
-        "z.RSD" = vscale(RSD))
+           "SD" = dri2, 
+        "z.RSD" = vscale(RSD),
+         "z.SD" = vscale(SD))
 ```
 
-### Dynamical divergence along sites
-
-In this section we consider dynamical divergence along Cartessian coordinates.
-square.dif.MSF is the square diference between MSF of the proteins relative to the reference protein.
-We ranked profiles because we found it is the best way to deal with large differences in MSF of divergent sites.
-We also tried z-normalizing but the results were not good.
-
-```{r mean-se-r.SDF-vs-site, fig.cap = "Black lines are the active sites and grey lines are their contacts"}
-
-# comparison of r.SDF profiles with functional sites
-## prepare dat
-dat = siteComparison.all.datasets
-dat$dataset = revalue(dat$dataset, c("medium" = "selection"))
-dat$dataset = revalue(dat$dataset, c("mut" = "no-selection"))
-
-## dat with means and standard errors
-d = ddply(dat,c("dataset", "site", "AA", "shell"), function(x) {
-                mean.r.SDF = mean(x$r.SDF, na.rm = T)
-                n.data = sum(!is.na(x$r.SDF))
-                se.r.SDF = sd(x$r.SDF, na.rm = T) / sqrt(n.data)
-                data.frame(mean.r.SDF, n.data, se.r.SDF)
-})
-
-## find the active site and its contacts
-active.sites = d$site[d$shell == 0]
-contacts.active.sites = d$site[d$shell == 1]
-
-## prepare plots with mean profiles and deviations
-p = ggplot(d, aes(x = site, y = mean.r.SDF, col = dataset, fill = dataset)) +
-    geom_line() +
-    geom_ribbon(aes(ymin = mean.r.SDF - f95 * se.r.SDF, ymax = mean.r.SDF + se.r.SDF), alpha = .4, show.legend = F) +
-    geom_vline(xintercept = active.sites, show.legend = F) +
-    geom_vline(xintercept = contacts.active.sites, col = "grey", show.legend = F) +
-    labs(x = "site", y = "<ranked square dif MSFi>") +
-    scale_colour_manual(name = NULL, values = myColors) + 
-    scale_fill_manual(name = NULL, values = myColors)
-
-## plot separate and comparative plots
-p.facet = p + facet_grid(dataset~., switch = "y") + theme(legend.position = "bottom")
-
-p.facet %+% subset(d, dataset == "exp") 
-p.facet %+% subset(d, dataset == "no-selection")
-p.facet %+% subset(d, dataset == "selection") 
-p.facet
-
-## plot superimposed plots
-p + theme(legend.position = "bottom")
-```
-
-```{r comparison-of-means}
-
-# extract means
-d.exp = subset(d, dataset == "exp")
-d.mut = subset(d, dataset == "no-selection")
-d.medium = subset(d, dataset == "selection")
-
-mean.r.square.dif.MSF.exp = d.exp$mean.r.SDF
-mean.r.square.dif.MSF.mut = d.mut$mean.r.SDF
-mean.r.square.dif.MSF.medium = d.medium$mean.r.SDF
-
-# calculate correlations
-r.exp.mut = cor(mean.r.square.dif.MSF.exp, mean.r.square.dif.MSF.mut)
-r.exp.medium = cor(mean.r.square.dif.MSF.exp, mean.r.square.dif.MSF.medium)
-r.mut.medium = cor(mean.r.square.dif.MSF.mut, mean.r.square.dif.MSF.medium)
-
-cor.df = data.frame("comparison" = c("exp vs no-selection", "exp vs selection", "no-selection vs selection"),
-                    "R" = c(r.exp.mut, r.exp.medium, r.mut.medium))
-
-knitr::kable(cor.df, digits = 2)
-
-# plot comparative profiles 
-par(pty = "s")
-
-plot(x = mean.r.square.dif.MSF.exp, 
-     y = mean.r.square.dif.MSF.mut, 
-     xlab = "<r.square.dif.MSF> experimental", 
-     ylab = "<r.square.dif.MSF> no-selection")
-abline(0, 1)
-
-plot(x = mean.r.square.dif.MSF.exp, 
-     y = mean.r.square.dif.MSF.medium, 
-     xlab = "<r.square.dif.MSF> experimental", 
-     ylab = "<r.square.dif.MSF> selection")
-abline(0, 1)
-
-plot(x = mean.r.square.dif.MSF.mut, 
-     y = mean.r.square.dif.MSF.medium, 
-     xlab = "<r.square.dif.MSF> no-selection", 
-     ylab = "<r.square.dif.MSF> selection")
-abline(0, 1)
-```
-
-```{r comparison-with-MSF.p.ref}
-
-# rank MSF.p.ref
-r.MSF.p.ref = rank(MSF.p.ref)
-
-# calculate correlations
-r.exp = cor(mean.r.square.dif.MSF.exp, r.MSF.p.ref)
-r.mut = cor(mean.r.square.dif.MSF.mut, r.MSF.p.ref)
-r.medium = cor(mean.r.square.dif.MSF.medium, r.MSF.p.ref)
-
-cor.df = data.frame("comparison" = c("<r.square.dif.MSF> experimental vs r.MSF.p.ref", "<r.square.dif.MSF> no-selection vs r.MSF.p.ref", "<r.square.dif.MSF> selection vs r.MSF.p.ref"),
-                    "R" = c(r.exp, r.mut, r.medium))
-
-knitr::kable(cor.df, digits = 2)
-
-# plot comparative profiles 
-par(pty = "s")
-
-plot(x = mean.r.square.dif.MSF.exp, 
-     y = r.MSF.p.ref, 
-     xlab = "<r.square.dif.MSF> experimental", 
-     ylab = "r.MSF.p.ref")
-abline(0, 1)
-
-plot(x = mean.r.square.dif.MSF.mut, 
-     y = r.MSF.p.ref, 
-     xlab = "<r.square.dif.MSF> no-selection", 
-     ylab = "r.MSF.p.ref")
-abline(0, 1)
-
-plot(x = mean.r.square.dif.MSF.medium, 
-     y = r.MSF.p.ref, 
-     xlab = "<r.square.dif.MSF> selection", 
-     ylab = "r.MSF.p.ref")
-abline(0, 1)
-```
-```{r mean-z.RSD-profiles}
-
+```{r mean-profiles-comparisons}
 # prepare dat
@@
                 mean.z.RSD = mean(x$z.RSD, na.rm = T)
+                mean.RSD = mean(x$RSD, na.rm = T)
+                mean.z.SD = mean(x$z.SD, na.rm = T)
+                mean.SD = mean(x$SD, na.rm = T)
                 n.data = sum(!is.na(x$z.RSD))
                 se.z.RSD = sd(x$z.RSD, na.rm = T) / sqrt(n.data)
-                data.frame(mean.z.RSD, n.data, se.z.RSD)
+                data.frame(mean.z.RSD,mean.RSD, mean.z.SD, mean.SD, n.data, se.z.RSD)
 })
@@
 
-mean.r.dri2.exp = d.exp$mean.z.RSD
-mean.r.dri2.mut = d.mut$mean.z.RSD
-mean.r.dri2.medium = d.medium$mean.z.RSD
-```
+# MSF.p.ref vs z.RSD and z.SD
+MSF.p.ref = as.vector(MSF.p.ref)
 
-### Comparison structure - dynamics
+# z.RSD
+## correlations
+r.exp = cor(d.exp$mean.RSD, MSF.p.ref)
+r.medium = cor(d.mut$mean.RSD, MSF.p.ref)
+r.mut = cor(d.medium$mean.RSD, MSF.p.ref)
 
-In this section we compare dri2 profiles (structural variability) with square dif MSF profiles (dynamical variability). To do this, we ranked each profile.
+cor.df = data.frame("MSF vs RSD" = c("exp", "selection", "no-selection"),
+                             "R" = c(r.exp, r.medium, r.mut))
+knitr::kable(cor.df, digits = 2)
 
-```{r structure-vs-dynamics}
-
-# rank profiles
-mean.r.dri2.exp = rank(mean.r.dri2.exp)
-mean.r.dri2.mut = rank(mean.r.dri2.mut)
-mean.r.dri2.medium = rank(mean.r.dri2.medium)
-
-mean.r.square.dif.MSF.exp = rank(mean.r.square.dif.MSF.exp)
-mean.r.square.dif.MSF.mut = rank(mean.r.square.dif.MSF.mut)
-mean.r.square.dif.MSF.medium = rank(mean.r.square.dif.MSF.medium)
-
-# plot comparative profiles
+## plots
 par(pty = "s")
 
-plot(x = mean.r.square.dif.MSF.exp, 
-     y = mean.r.dri2.exp, 
-     xlab = "r<r.square.dif.MSF> experimental", 
-     ylab = "r<dri2> experimental")
-abline(0, 1)
+plot(y = d.exp$mean.RSD, x = MSF.p.ref, ylab = "RSD experimental")
+lm = lm(d.exp$mean.RSD ~ MSF.p.ref)
+abline(lm)
+legend("topleft", paste ("r = ", round(r.exp, digits = 2)), bty = "n")
 
-plot(x = mean.r.square.dif.MSF.mut, 
-     y = mean.r.dri2.mut, 
-     xlab = "r<r.square.dif.MSF> no-selection", 
-     ylab = "r<dri2> no-selection")
-abline(0, 1)
+plot(y = d.mut$mean.RSD, x = MSF.p.ref, ylab = "RSD no-selection")
+lm = lm(d.mut$mean.RSD ~ MSF.p.ref)
+abline(lm)
+legend("topleft", paste ("r = ", round(r.mut, digits = 2)), bty = "n")
 
-plot(x = mean.r.square.dif.MSF.medium, 
-     y = mean.r.dri2.medium, 
-     xlab = "r<r.square.dif.MSF> selection", 
-     ylab = "r<dri2> selection")
-abline(0, 1)
+plot(y = d.medium$mean.RSD, x = MSF.p.ref, ylab = "RSD selection")
+lm = lm(d.medium$mean.RSD ~ MSF.p.ref)
+abline(lm)
+legend("topleft", paste ("r = ", round(r.medium, digits = 2)), bty = "n")
 
-# calculate correlations
-r.exp = cor(mean.r.square.dif.MSF.exp, mean.r.dri2.exp)
-r.medium = cor(mean.r.square.dif.MSF.medium, mean.r.dri2.medium)
-r.mut = cor(mean.r.square.dif.MSF.mut, mean.r.dri2.mut)
+# SD
+## correlations
+r.exp = cor(d.exp$mean.SD, MSF.p.ref)
+r.medium = cor(d.mut$mean.SD, MSF.p.ref)
+r.mut = cor(d.medium$mean.SD, MSF.p.ref)
 
-cor.df = data.frame("comparison structure - dynamics" = c("exp", "selection", "no-selection"),
+cor.df = data.frame("MSF vs SD" = c("exp", "selection", "no-selection"),
                             "R" = c(r.exp, r.medium, r.mut))
 knitr::kable(cor.df, digits = 2)
+
+## plots
+par(pty = "s")
+
+plot(y = d.exp$mean.SD, x = MSF.p.ref, ylab = "SD experimental")
+lm = lm(d.exp$mean.SD ~ MSF.p.ref)
+abline(lm)
+legend("topleft", paste ("r = ", round(r.exp, digits = 2)), bty = "n")
+
+plot(y = d.mut$mean.SD, x = MSF.p.ref, ylab = "SD no-selection")
+lm = lm(d.mut$mean.SD ~ MSF.p.ref)
+abline(lm)
+legend("topleft", paste ("r = ", round(r.mut, digits = 2)), bty = "n")
+
+plot(y = d.medium$mean.SD, x = MSF.p.ref, ylab = "SD selection")
+lm = lm(d.medium$mean.SD ~ MSF.p.ref)
+abline(lm)
+legend("topleft", paste ("r = ", round(r.medium, digits = 2)), bty = "n")
 ```

### 2017-06-25 analysis-Pn-energy.Rmd
23/6/17

--- 2017-05-10 analysis-structure-normal-modes.Rmd
@@
 ---
-title: "Structural Divergence Analysis"
+title: "Structural Divergence - Protein dynamics"
 author: "Maria Laura Marcos, Julian Echave"
@@
 # Introduction
-We study the evolutionary divergence of proteins using the LF-ENM and comparing simulated mutants with experimental data.
+In this report we compare Pn profiles with the fluctuation along normal modes.
 
@@
 site.info.fname = file.path(data.dir, paste(p.ref, "_m.da.ca.csv", sep = ""))
-min.da.CM.CA.fname = file.path(data.dir, paste(p.ref, "_min.da.CM.ca.csv", sep = ""))
 
@@
 rownames(energy.medium) = paste("medium", rownames(energy.medium), sep = "")
-
 ```
-
-### Structural divergence along normal modes
-
-In this section we consider structural divergence using normal mode coordinates. Pn is the square divergence along a normal mode relative to the mean.
 
@@
 modeComparison.exp = merge(energy.exp.long,Pn.exp.long,by=c("mode", "protein"))
-# renormalize Pn
 modeComparison.exp = ddply(modeComparison.exp, "protein", mutate, "Pn" = Pn / mean(Pn, na.rm = T))
 
-# modeComparison.exp has NA's because for proteins with gaps when using Keff there're less modes
-#print("Warning: modeComparison.exp <- na.omit(modeComparison.exp)")
 modeComparison.exp <- na.omit(modeComparison.exp)
@@
 modeComparison.mut <- na.omit(modeComparison.mut)
-```
-
-```{r add-quantile-regression-data}
-
-## Quantile regression
-
-# fit median and quantiles to simulated data and add them to data.frames
-fit.medium.rq.5 <- rq(Pn ~ sn2, tau = .5, data = modeComparison.medium, method = "fn")
-fit.medium.rq.05 <- rq(Pn ~ sn2, tau = .05, data = modeComparison.medium, method = "fn")
-fit.medium.rq.95 <- rq(Pn ~ sn2, tau = .95, data = modeComparison.medium, method = "fn")
-modeComparison.medium$rq.5 = fit.medium.rq.5$fitted.values
-modeComparison.medium$rq.05 = fit.medium.rq.05$fitted.values
-modeComparison.medium$rq.95 = fit.medium.rq.95$fitted.values
-
-# fit median and quantiles to simulated data and add them to data.frames
-fit.mut.rq.5 <- rq(Pn ~ sn2, tau = .5, data = modeComparison.mut, method = "fn")
-fit.mut.rq.05 <- rq(Pn ~ sn2, tau = .05, data = modeComparison.mut, method = "fn")
-fit.mut.rq.95 <- rq(Pn ~ sn2, tau = .95, data = modeComparison.mut, method = "fn")
-modeComparison.mut$rq.5 = fit.mut.rq.5$fitted.values
-modeComparison.mut$rq.05 = fit.mut.rq.05$fitted.values
-modeComparison.mut$rq.95 = fit.mut.rq.95$fitted.values
-
-# fit median and quantiles to experimental data
-fit.exp.rq.5 <- rq(Pn ~ sn2, tau = .5, data = modeComparison.exp, method = "fn")
-fit.exp.rq.05 <- rq(Pn ~ sn2, tau = .05, data = modeComparison.exp, method = "fn")
-fit.exp.rq.95 <- rq(Pn ~ sn2, tau = .95, data = modeComparison.exp, method = "fn")
-modeComparison.exp$rq.5 = fit.exp.rq.5$fitted.values
-modeComparison.exp$rq.05 = fit.exp.rq.05$fitted.values
-modeComparison.exp$rq.95 = fit.exp.rq.95$fitted.values
 
 # put simulated and experimental data together
-
 modeComparison.all.datasets = rbind(data.frame("dataset" = "exp", modeComparison.exp),
@@
 ```
-### Pn vs. mode energy
-
-Note: lines are the median, 0.05 and 0.95 quantiles fit using rq(Pn ~ sn2).
-sn2 = 1/energy is the expected MSD of along mode n.
-The mean value of Pn should be a linear function of sn2 (Pn is normalized, sn2 is not).
-
-Here we show the square deviation along each normal mode (normalized so that = 1) vs.
-the normal-mode's energy.
-For the empirical data, we use the actual energy obtained from Keff for the given comparison.
-It is this energy the one that should be used, since it's inverse is the expected value of Pn.
-Lines are the .5 (median), .05, and .95 quantiles obtained using rq()
-
-Upper panel: simulated vs empirical data, shown separately.
-Lower panel: simulated vs empirical overlaped and zoomed to better see the pattern.
-
-```{r Pn-vs-energy}
-
-# Plot Pn vs energy
-dat = modeComparison.all.datasets
-
-# p is just the median and quantiles
-p.points.rq = ggplot(dat, aes(x = energy, y = Pn, col = dataset)) + 
-    geom_point(alpha = .4, size = .2) +
-    geom_line(aes(y = rq.5)) +
-    geom_line(aes(y = rq.05)) +
-    geom_line(aes(y = rq.95)) 
-p = p.points.rq +  
-    labs(x = "mode energy", y = "structural divergence") +
-    coord_cartesian(xlim = c(0,3)) +
-    scale_colour_manual(name = NULL, values = myColors) + 
-    scale_fill_manual(name=NULL, values = myColors)
-
-p.facet = p + facet_grid(dataset~., switch = "y") + theme(legend.position = "none")
-p.facet %+% subset(dat, dataset == "exp")
-p.facet %+% subset(dat, dataset == "mut")
-p.facet %+% subset(dat, dataset == "medium")
-p.facet
-```
-
-### median(Pn) vs mode energy
 
@@
     energy.mean = mean(x$energy)
-    Pn.median = median(x$Pn)
-    Pn.median.ci = sort(x$Pn)[qbinom(c(.025, .975), length(x$Pn), 0.5)]
-    Pn.median.min = Pn.median.ci[1]
-    Pn.median.max = Pn.median.ci[2]
-    rq.5 = mean(x$rq.5)
-    data.frame(energy.mean, Pn.median.min, Pn.median.max, Pn.median, rq.5)
+    Pn.mean = mean(x$Pn)
+    ndata = sum(!is.na(x$Pn))
+    Pn.se = sd(x$Pn, na.rm = T) / sqrt(ndata)
+    data.frame(energy.mean, Pn.mean, Pn.se)
 })
 
-p = ggplot(dat,aes(x=energy.mean,y=Pn.median,col=dataset,fill=dataset)) +
-    geom_pointrange(aes(ymin=Pn.median.min,ymax = Pn.median.max),size=.2,alpha=.4) +
-    geom_line(aes(y=rq.5))  +
-    labs(x="mode energy",y="structural divergence (median Pn) ") +
-    scale_colour_manual(name = NULL,values = myColors) + 
-    scale_fill_manual(name=NULL,values=myColors)+
-    coord_cartesian(xlim=c(0,3))
+p = ggplot(dat, aes(x = mode, y = Pn.mean, col = dataset, fill = dataset)) +
+    geom_line() +
+    geom_ribbon(aes(ymin = Pn.mean - f95 * Pn.se, ymax = Pn.mean + Pn.se), alpha = .4, show.legend = F) +
+    labs(x = "mode", y = "<Pn>") +
+    scale_colour_manual(name = NULL, values = myColors) + 
+    scale_fill_manual(name = NULL, values = myColors)
+
+p.facet = p + facet_grid(dataset~., switch = "y") + theme(legend.position = "none")
+p.facet %+% subset(dat,dataset == "exp")
+p.facet %+% subset(dat,dataset == "no-selection")
+p.facet %+% subset(dat,dataset == "selection")
+p.facet
+p + theme(legend.position = "bottom")
+
+p = ggplot(dat, aes(x = (1/energy.mean), y = Pn.mean, col = dataset, fill = dataset)) +
+    geom_point() +
+    labs(x = "1/lambda_n", y = "<Pn>") +
+    scale_colour_manual(name = NULL, values = myColors) + 
+    scale_fill_manual(name = NULL, values = myColors)
 
@@
 
-```{r correlation-mode-profiles}
-#dat$dataset = revalue(dat$dataset,c("medium" = "mut+sel"))
-dat = modeComparison.all.datasets
-dat$dataset = revalue(dat$dataset, c("medium" = "selection"))
-dat$dataset = revalue(dat$dataset, c("mut" = "no-selection"))
-
-# calculate dataset of medians
-dat = ddply(dat, c("dataset", "mode"), function(x) {
-    energy.mean = mean(x$energy)
-    Pn.median = median(x$Pn)
-    data.frame(energy.mean, Pn.median)
-})
-
+```{r correlation}
 dat = subset(dat, mode < 101)
@@
 
-r.exp.mut = cor(dat.exp$Pn.median, dat.mut$Pn.median)
-r.exp.medium = cor(dat.exp$Pn.median, dat.medium$Pn.median)
-r.mut.medium = cor(dat.mut$Pn.median, dat.medium$Pn.median)
-cor.df = data.frame("comparison" = c("exp vs mut", "exp vs medium", "mut vs medium"),
-                    "R" = c(r.exp.mut, r.exp.medium, r.mut.medium))
+r.exp = cor(dat.exp$Pn.mean, (1/dat.exp$energy.mean))
+r.mut = cor(dat.mut$Pn.mean, (1/dat.mut$energy.mean))
+r.medium = cor(dat.medium$Pn.mean, (1/dat.medium$energy.mean))
+cor.df = data.frame("comparison" = c("exp", "mut", "medium"),
+                    "R" = c(r.exp, r.mut, r.medium))
 knitr::kable(cor.df, digits = 2)
 
-# plot exp vs simulated profiles 
+# plots
 par(pty = "s")
 
-plot(x = dat.exp$Pn.median, 
-     y = dat.mut$Pn.median, 
-     xlab = "exp.Pn.median", 
-     ylab = "mut.Pn.median", 
-     xlim = c(min(c(dat.exp$Pn.median, dat.mut$Pn.median)), max(c(dat.exp$Pn.median, dat.mut$Pn.median))),
-     ylim = c(min(c(dat.exp$Pn.median, dat.mut$Pn.median)), max(c(dat.exp$Pn.median, dat.mut$Pn.median))))
-abline(0, 1)
+plot(y = dat.exp$Pn.mean, x = (1/dat.exp$energy.mean), xlab = "1/lambda_n", ylab = "<Pn> experimental")
+fluc = (1/dat.exp$energy.mean)
+lm = lm(dat.exp$Pn.mean ~ fluc)
+abline(lm)
+legend("topleft", paste ("r = ", round(r.exp, digits = 2)), bty = "n")
 
-plot(x = dat.exp$Pn.median, 
-     y = dat.medium$Pn.median, 
-     xlab = "exp.Pn.median", 
-     ylab = "medium.Pn.median", 
-     xlim = c(min(c(dat.exp$Pn.median, dat.medium$Pn.median)), max(c(dat.exp$Pn.median, dat.medium$Pn.median))),
-     ylim = c(min(c(dat.exp$Pn.median, dat.medium$Pn.median)), max(c(dat.exp$Pn.median, dat.medium$Pn.median))))
-abline(0, 1)
+plot(y = dat.mut$Pn.mean, x = (1/dat.mut$energy.mean), xlab = "1/lambda_n", ylab = "<Pn> no-selection")
+fluc = (1/dat.mut$energy.mean)
+lm = lm(dat.mut$Pn.mean ~ fluc)
+abline(lm)
+legend("topleft", paste ("r = ", round(r.mut, digits = 2)), bty = "n")
 
-plot(x = dat.mut$Pn.median, 
-     y = dat.medium$Pn.median, 
-     xlab = "mut.Pn.median", 
-     ylab = "medium.Pn.median", 
-     xlim = c(min(c(dat.mut$Pn.median, dat.medium$Pn.median)), max(c(dat.mut$Pn.median, dat.medium$Pn.median))),
-     ylim = c(min(c(dat.mut$Pn.median, dat.medium$Pn.median)), max(c(dat.mut$Pn.median, dat.medium$Pn.median))))
-abline(0, 1)
+plot(y = dat.medium$Pn.mean, x = (1/dat.medium$energy.mean), xlab = "1/lambda_n", ylab = "<Pn> selection")
+fluc = (1/dat.medium$energy.mean)
+lm = lm(dat.medium$Pn.mean ~ fluc)
+abline(lm)
+legend("topleft", paste ("r = ", round(r.medium, digits = 2)), bty = "n")
 ```

### 2017-06-25 analysis-dynamical-MSF-structure.Rmd
23/6/17

@@
           "RSD" = sqrt(dri2), 
-        "z.RSD" = vscale(RSD))
+           "SD" = dri2, 
+        "z.RSD" = vscale(RSD),
+         "z.SD" = vscale(SD))
 ```
@@
 mean.r.dri2.medium = d.medium$mean.z.RSD
+
+# MSF.p.ref vs z.RSD and z.SD
+MSF.p.ref = as.vector(MSF.p.ref)
+
+## correlations
+r.exp = cor(d.exp$mean.RSD, MSF.p.ref)
+r.medium = cor(d.mut$mean.RSD, MSF.p.ref)
+r.mut = cor(d.medium$mean.RSD, MSF.p.ref)
+
+cor.df = data.frame("MSF vs RSD" = c("exp", "selection", "no-selection"),
+                    "R" = c(r.exp, r.medium, r.mut))
+knitr::kable(cor.df, digits = 2)
+
+## plots
+
+par(pty = "s")
+
+plot(y = d.exp$mean.RSD, x = MSF.p.ref, ylab = "RSD experimental")
+lm = lm(d.exp$mean.RSD ~ MSF.p.ref)
+abline(lm)
+legend("topleft", paste ("r = ", round(r.exp, digits = 2)), bty = "n")
+
+plot(y = d.mut$mean.RSD, x = MSF.p.ref, ylab = "RSD no-selection")
+lm = lm(d.mut$mean.RSD ~ MSF.p.ref)
+abline(lm)
+legend("topleft", paste ("r = ", round(r.mut, digits = 2)), bty = "n")
+
+plot(y = d.medium$mean.RSD, x = MSF.p.ref, ylab = "RSD selection")
+lm = lm(d.medium$mean.RSD ~ MSF.p.ref)
+abline(lm)
+legend("topleft", paste ("r = ", round(r.medium, digits = 2)), bty = "n")
+
+## correlations
+r.exp = cor(d.exp$mean.SD, MSF.p.ref)
+r.medium = cor(d.mut$mean.SD, MSF.p.ref)
+r.mut = cor(d.medium$mean.SD, MSF.p.ref)
+
+cor.df = data.frame("MSF vs SD" = c("exp", "selection", "no-selection"),
+                    "R" = c(r.exp, r.medium, r.mut))
+knitr::kable(cor.df, digits = 2)
+
+## plots
+par(pty = "s")
+
+plot(y = d.exp$mean.SD, x = MSF.p.ref, ylab = "SD experimental")
+lm = lm(d.exp$mean.SD ~ MSF.p.ref)
+abline(lm)
+legend("topleft", paste ("r = ", round(r.exp, digits = 2)), bty = "n")
+
+plot(y = d.mut$mean.SD, x = MSF.p.ref, ylab = "SD no-selection")
+lm = lm(d.mut$mean.SD ~ MSF.p.ref)
+abline(lm)
+legend("topleft", paste ("r = ", round(r.mut, digits = 2)), bty = "n")
+
+plot(y = d.medium$mean.SD, x = MSF.p.ref, ylab = "SD selection")
+lm = lm(d.medium$mean.SD ~ MSF.p.ref)
+abline(lm)
+legend("topleft", paste ("r = ", round(r.medium, digits = 2)), bty = "n")
+
 ```

### 2017-06-25 analysis-structure-MSD-RMSD-CN-WCN.Rmd
23/6/17

---
title: "Structural Divergence Analysis"
author: "Maria Laura Marcos, Julian Echave"
output: html_document
---

```{r load-packages}
# load packages
library(ggplot2)
library(reshape2)
library(plyr)
library(quantreg)
library(bio3d)

# load functions
source("FUNCTIONS/ReadCA.R") 
source("FUNCTIONS/CalculateSideChainCM.R")
source(file.path(data.dir, "multiplot.R"))
source(file.path(data.dir, "my-functions.R"))
```

```{r set-file-names}
# set input filenames
cc.matrix = c()
s.cc.matrix = c()

# satart a loop for each family
for (f in (1:nrow(input))) { 
  print(f)
  family <- as.character(input$family)[f]
  type <- as.character(input$type)[f]
  p.ref <- as.character(input$p.ref)[f]
  enm <- as.character(input$enm)[f]
  n.mut.p <- input$n.mut.p[f]
  R0.CA = input$R0.CA[f]
  R0.CM = input$R0.CM[f]
  chain.p.ref <- as.character(input$chain.p.ref)[f]
  print(family)

  data.dir <- paste("OUT/out_subset_CA_ANM", sep = "")
  R0 = 10

  ## data
  reference.fname = file.path(data.dir, paste(family, "_ref.txt", sep = ""))
  protein_list.fname = file.path(data.dir, paste(family, "_list.txt", sep = ""))

  ## profiles to compare
  dri2.exp.fname = file.path(data.dir, paste(family, "_R0_", R0,   "_beta_no.sel_K.analysis_Keff_out_m.exp.norm.dr.squarei.csv", sep = ""))
  dri2.medium.fname = file.path(data.dir, paste(family, "_R0_", R0, "_beta_medium.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
  dri2.mut.fname = file.path(data.dir,paste(family, "_R0_", R0, "_beta_no.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))

# which is the reference protein?
reference = as.character(read.table(reference.fname, header = F)[1, 1])
if (reference != p.ref) {
  print("Warning: different references")
}

# experimental protein names
protein.exp = read.table(protein_list.fname, header = F, stringsAsFactors = F)[, 1]
protein.exp = protein.exp[protein.exp != reference]
print(protein.exp)

# read reference pdb and calculate resno, AA, and CN
reference.pdb.fname = file.path(data.dir,paste(reference, ".pdb", sep = ""))
ref.pdb = read.pdb(reference.pdb.fname)
inds = atom.select(ref.pdb, elety = "CA")
ref.pdb.ca = ref.pdb$atom[inds$atom, ]
n.sites = length(ref.pdb.ca$resid)
AA = ref.pdb.ca$resid
resno = seq(1:n.sites)
pdb.info = data.frame(resno, AA)
names(pdb.info) = c("resno", "AA")
print(n.sites)

site.info = pdb.info

### CA ###

# calculate CN
R0 = 10
cmap.ca.R0.10 = cmap(ref.pdb$xyz[inds$xyz], dcut = R0, scut = 0, mask.lower = F)
CN = rowSums(cmap.ca.R0.10, na.rm = T) - 1 # diag(cmap.ca) returned by cmap is 1!

# calculate WCN
r.p.ref = matrix(ref.pdb$xyz[inds$xyz], nrow = 3)
dist.r.p.ref = dist.xyz(t(r.p.ref))
WCN = c()
for (i in (1:ncol(r.p.ref))) {
  WCN[i] = sum(1/dist.r.p.ref[i, -i]^2)
}

# read data
## exp
dri2.exp = read.csv(dri2.exp.fname, header = T)
site = site.info$site
rownames(dri2.exp) = paste("exp", rownames(dri2.exp), sep = "")

## mut
dri2.mut = read.csv(dri2.mut.fname, header = T)
rownames(dri2.mut) = paste("mut", rownames(dri2.mut), sep = "")

## medium
dri2.medium = read.csv(dri2.medium.fname, header = T)
rownames(dri2.medium) = paste("medium", rownames(dri2.medium), sep = "")

# prepare the data
## exp
tdri2.exp = as.data.frame(t(as.matrix(dri2.exp)))
tdri2.exp = cbind(site.info, tdri2.exp)
siteComparison.exp = melt(tdri2.exp, id.vars = names(site.info), variable.name = "protein", value.name = "dri2")

## mut
tdri2.mut = as.data.frame(t(as.matrix(dri2.mut)))
tdri2.mut = cbind(site.info, tdri2.mut)
siteComparison.mut = melt(tdri2.mut, id.vars = names(site.info), variable.name = "protein", value.name = "dri2")

## medium
tdri2.medium = as.data.frame(t(as.matrix(dri2.medium)))
tdri2.medium = cbind(site.info, tdri2.medium)
siteComparison.medium = melt(tdri2.medium, id.vars = names(site.info), variable.name = "protein", value.name = "dri2")

# bluild the data.frame
siteComparison.all.datasets = rbind(data.frame("dataset" = "exp", siteComparison.exp),
                                    data.frame("dataset" = "mut", siteComparison.mut),
                                    data.frame("dataset" = "medium", siteComparison.medium))

siteComparison.all.datasets = ddply(siteComparison.all.datasets, c("dataset", "protein"), mutate,
                     "z.SD" = vscale(dri2),
                      "RSD" = sqrt(dri2),
                    "z.RSD" = vscale(RSD))

## prepare dat
dat = siteComparison.all.datasets
dat$dataset = revalue(dat$dataset, c("medium" = "selection"))
dat$dataset = revalue(dat$dataset, c("mut" = "no-selection"))

## dat with means and standard errors
d = ddply(dat,c("dataset", "resno"), function(x) {
                mean.z.RSD = mean(x$z.RSD, na.rm = T)
                mean.z.SD = mean(x$z.SD, na.rm = T)
                ndata = sum(!is.na(x$z.RSD))
                data.frame(mean.z.RSD, mean.z.SD, ndata)
})

# calculate correlations berween profiles
d.exp = subset(d, dataset == "exp")
d.mut = subset(d, dataset == "no-selection")
d.medium = subset(d, dataset == "selection")

# calculate correlations

cc = c()
cc = c(cc,cor(d.exp$mean.z.RSD, CN))
cc = c(cc,cor(d.exp$mean.z.RSD, WCN))
cc = c(cc,cor(d.exp$mean.z.RSD, 1/CN))
cc = c(cc,cor(d.exp$mean.z.RSD, 1/WCN))
cc = c(cc,cor(d.mut$mean.z.RSD, CN))
cc = c(cc,cor(d.mut$mean.z.RSD, WCN))
cc = c(cc,cor(d.mut$mean.z.RSD, 1/CN))
cc = c(cc,cor(d.mut$mean.z.RSD, 1/WCN))
cc = c(cc,cor(d.medium$mean.z.RSD, CN))
cc = c(cc,cor(d.medium$mean.z.RSD, WCN))
cc = c(cc,cor(d.medium$mean.z.RSD, 1/CN))
cc = c(cc,cor(d.medium$mean.z.RSD, 1/WCN))

cc = c(cc,cor(d.exp$mean.z.SD, CN))
cc = c(cc,cor(d.exp$mean.z.SD, WCN))
cc = c(cc,cor(d.exp$mean.z.SD, 1/CN))
cc = c(cc,cor(d.exp$mean.z.SD, 1/WCN))
cc = c(cc,cor(d.mut$mean.z.SD, CN))
cc = c(cc,cor(d.mut$mean.z.SD, WCN))
cc = c(cc,cor(d.mut$mean.z.SD, 1/CN))
cc = c(cc,cor(d.mut$mean.z.SD, 1/WCN))
cc = c(cc,cor(d.medium$mean.z.SD, CN))
cc = c(cc,cor(d.medium$mean.z.SD, WCN))
cc = c(cc,cor(d.medium$mean.z.SD, 1/CN))
cc = c(cc,cor(d.medium$mean.z.SD, 1/WCN))

cc.matrix = cbind(cc.matrix, cc)

cc = c()
cc = c(cc,cor(d.exp$mean.z.RSD, CN, method = "spearman"))
cc = c(cc,cor(d.exp$mean.z.RSD, WCN, method = "spearman"))
cc = c(cc,cor(d.exp$mean.z.RSD, 1/CN, method = "spearman"))
cc = c(cc,cor(d.exp$mean.z.RSD, 1/WCN, method = "spearman"))
cc = c(cc,cor(d.mut$mean.z.RSD, CN, method = "spearman"))
cc = c(cc,cor(d.mut$mean.z.RSD, WCN, method = "spearman"))
cc = c(cc,cor(d.mut$mean.z.RSD, 1/CN, method = "spearman"))
cc = c(cc,cor(d.mut$mean.z.RSD, 1/WCN, method = "spearman"))
cc = c(cc,cor(d.medium$mean.z.RSD, CN, method = "spearman"))
cc = c(cc,cor(d.medium$mean.z.RSD, WCN, method = "spearman"))
cc = c(cc,cor(d.medium$mean.z.RSD, 1/CN, method = "spearman"))
cc = c(cc,cor(d.medium$mean.z.RSD, 1/WCN, method = "spearman"))

cc = c(cc,cor(d.exp$mean.z.SD, CN, method = "spearman"))
cc = c(cc,cor(d.exp$mean.z.SD, WCN, method = "spearman"))
cc = c(cc,cor(d.exp$mean.z.SD, 1/CN, method = "spearman"))
cc = c(cc,cor(d.exp$mean.z.SD, 1/WCN, method = "spearman"))
cc = c(cc,cor(d.mut$mean.z.SD, CN, method = "spearman"))
cc = c(cc,cor(d.mut$mean.z.SD, WCN, method = "spearman"))
cc = c(cc,cor(d.mut$mean.z.SD, 1/CN, method = "spearman"))
cc = c(cc,cor(d.mut$mean.z.SD, 1/WCN, method = "spearman"))
cc = c(cc,cor(d.medium$mean.z.SD, CN, method = "spearman"))
cc = c(cc,cor(d.medium$mean.z.SD, WCN, method = "spearman"))
cc = c(cc,cor(d.medium$mean.z.SD, 1/CN, method = "spearman"))
cc = c(cc,cor(d.medium$mean.z.SD, 1/WCN, method = "spearman"))

s.cc.matrix = cbind(s.cc.matrix, cc)
}

colnames(cc.matrix) = input$family
colnames(s.cc.matrix) = input$family

names = c(                "exp.mean.z.RSD vs CN",
                        "exp.mean.z.RSD vs WCN",
                        "exp.mean.z.RSD vs 1/CN",
                        "exp.mean.z.RSD vs 1/WCN",
                        "no-sel.mean.z.RSD vs CN",
                        "no-sel.mean.z.RSD vs WCN",
                        "no-sel.mean.z.RSD vs 1/CN",
                        "no-sel.mean.z.RSD vs 1/WCN",
                        "sel.mean.z.RSD vs CN",
                        "sel.mean.z.RSD vs WCN",
                        "sel.mean.z.RSD vs 1/CN",
                        "sel.mean.z.RSD vs 1/WCN",
                        "exp.mean.z.SD vs CN",
                        "exp.mean.z.SD vs WCN",
                        "exp.mean.z.SD vs 1/CN",
                        "exp.mean.z.SD vs 1/WCN",
                        "no-sel.mean.z.SD vs CN",
                        "no-sel.mean.z.SD vs WCN",
                        "no-sel.mean.z.SD vs 1/CN",
                        "no-sel.mean.z.SD vs 1/WCN",
                        "sel.mean.z.SD vs CN",
                        "sel.mean.z.SD vs WCN",
                        "sel.mean.z.SD vs 1/CN",
                        "sel.mean.z.SD vs 1/WCN")
rownames(cc.matrix) = names
rownames(s.cc.matrix) = names

write.csv(cc.matrix, file="pearson.cc.SDvsPD.csv")
write.csv(s.cc.matrix, file="spearman.cc.SDvsPD.csv")

```

### All correlations

```{r correlations}
# build a data frame
cor = data.frame("CA pearson" = CA.cor.p,
                 "CM pearson" = CM.cor.p,
                 "CA spearman" = CA.cor.s,
                 "CM spearman" = CM.cor.s)
rownames(cor) = c("CN R0 = -0.1", "CN R0 = 2.5", "CN R0 = 7.5", "CN R0 = 12.5", "CN R0 = 17.5", "CN R0 = 22.5", "CN R0 = 27.5", "CN R0 = 32.5", "CN R0 = 37.5", "CN R0 = 42.5", "CN R0 = 47.5", "CN R0 = 52.5", "WCN")
knitr::kable(cor, digits = 2, caption = "Correlation structure (<z.RSD>) - sequence (CN/WCN)")
```

### 2017-06-25 analysis-structure-normal-modes.Rmd
23/6/17

@@
 
+p = ggplot(dat,aes(x=mode,y=Pn.median,col=dataset,fill=dataset)) +
+    geom_pointrange(aes(ymin=Pn.median.min,ymax = Pn.median.max),size=.2,alpha=.4) +
+    geom_line(aes(y=rq.5))  +
+    labs(x="mode energy",y="structural divergence (median Pn) ") +
+    scale_colour_manual(name = NULL,values = myColors) + 
+    scale_fill_manual(name=NULL,values=myColors)+
+    coord_cartesian(xlim=c(0,3))
+
+p.facet = p + facet_grid(dataset~., switch = "y") + theme(legend.position = "none")
+p.facet %+% subset(dat,dataset == "exp")
+p.facet %+% subset(dat,dataset == "no-selection")
+p.facet %+% subset(dat,dataset == "selection")
+p.facet
+p + theme(legend.position = "bottom")
 ```

### 2017-06-25 analysis-structure.Rmd
23/6/17

@@
 
-plot(x = d.exp$mean.z.RSD, y = log(CN), xlab = "<zRSDi> experimental")
-plot(x = d.mut$mean.z.RSD, y = log(CN), xlab = "<zRSDi> no-selection")
-plot(x = d.medium$mean.z.RSD, y = log(CN), xlab = "<zRSDi> selection")
+plot(x = d.exp$mean.z.RSD, y = (1/CN), xlab = "<zRSDi> experimental")
+plot(x = d.mut$mean.z.RSD, y = (1/CN), xlab = "<zRSDi> no-selection")
+plot(x = d.medium$mean.z.RSD, y = (1/CN), xlab = "<zRSDi> selection")
 
 ## calculate correlations
-r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN))
-r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN))
-r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN))
+r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, (1/CN))
+r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, (1/CN))
+r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, (1/CN))
 
-cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
+cor.df = data.frame("comparison" = c("<z.RSD> experimental vs 1/CN", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs 1/CN"),
                     "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))
 
-knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (CN)")
+knitr::kable(cor.df, digits = 2, caption = "Pearson Correlation structure (<z.RSD>) - sequence (1/CN)")
 
 ## calculate correlations
-r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, log(CN), method = "spearman")
-r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, log(CN), method = "spearman")
-r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, log(CN), method = "spearman")
+r.exp.mean.z.RSD.CN = cor(d.exp$mean.z.RSD, (1/CN), method = "spearman")
+r.mut.mean.z.RSD.CN = cor(d.mut$mean.z.RSD, (1/CN), method = "spearman")
+r.medium.mean.z.RSD.CN = cor(d.medium$mean.z.RSD, (1/CN), method = "spearman")
 
-cor.df = data.frame("comparison" = c("<z.RSD> experimental vs log(CN)", "<z.RSD> no-selection vs log(CN)", "<z.RSD> selection vs log(CN)"),
+cor.df = data.frame("comparison" = c("<z.RSD> experimental vs 1/CN", "<z.RSD> no-selection vs 1/CN", "<z.RSD> selection vs 1/CN"),
                     "R" = c(r.exp.mean.z.RSD.CN , r.mut.mean.z.RSD.CN, r.medium.mean.z.RSD.CN))
 
-knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (CN)")
+knitr::kable(cor.df, digits = 2, caption = "Spearman Correlation structure (<z.RSD>) - sequence (1/CN)")
 ```

### 2017-06-25 comparison_families.Rmd
23/6/17

@@
 df.cc.z.RSD_CA = cbind(data.frame("comparison" = comparison, "c.R0" = c.R0), cc.z.RSD = c(t(cc.z.RSD_CA)))
+
+## comparison mut - sel
+plot(x = cc.z.RSD_CA[,3], y = cc.z.RSD_CA[,6], xlab = "cc <z.RSD> exp - <z.RSD> no-selection", ylab = "cc <z.RSD> exp - <z.RSD> selection")
+abline(0,1)
+legend("topleft", paste ("r = ", round(cor(cc.z.RSD_CA[,3], cc.z.RSD_CA[,6]), digits = 2)), bty = "n")
 
@@
 
+plot(x = cc.Pn_CA[,3], y = cc.Pn_CA[,6], xlab = "cc <Pn> exp -  <Pn> no-selection", ylab = "cc <Pn> exp -  <Pn> selection")
+abline(0,1)
+legend("topleft", paste ("r = ", round(cor(cc.Pn_CA[,3], cc.Pn_CA[,6]), digits = 2)), bty = "n")
+
 dat = df.cc.Pn_CA
@@
 
+## comparison mut - sel
+plot(x = cc.MSF_CA[,3], y = cc.MSF_CA[,6], xlab = "cc <MSF> exp - <MSF> no-selection", ylab = "cc <MSF> exp -  <MSF> selection")
+abline(0,1)
+legend("topleft", paste ("r = ", round(cor(cc.MSF_CA[,3], cc.MSF_CA[,6]), digits = 2)), bty = "n")
+
 dat = df.cc.MSF_CA
@@
 
+## comparison mut - sel
+plot(x = cc.nH_CA[,3], y = cc.nH_CA[,6], xlab = "cc <nH> exp -  <MSF> no-selection", ylab = "cc <nH> exp -  <MSF> selection")
+abline(0,1)
+legend("topleft", paste ("r = ", round(cor(cc.nH_CA[,3], cc.nH_CA[,6]), digits = 2)), bty = "n")
+
 dat = df.cc.nH_CA

### 2017-06-25 MainReport.R

@@ -30,7 +30,7 @@ for (f in (1:nrow(input))) {
   print(family)
   
   
-  ## pfANM
+  ## pfANM CA
   R0 = "NC"
   data.dir <- paste("OUT/out_subset_CA_pfANM", sep = "")
 
@@ -38,16 +38,25 @@ for (f in (1:nrow(input))) {
   rmarkdown::render('analysis-structure-pfANM.Rmd', 
                     output_file =  paste("OUT/report_structure_pfANM_", family, ".html", sep = ''))
   
-  ## CA
+  ## ANM CA
   data.dir <- paste("OUT/out_subset_CA_ANM", sep = "")
   R0 = R0.CA
   
+  ### Pn vs. energy
+  rmarkdown::render('analysis-Pn-energy.Rmd', 
+                    output_file =  paste("OUT/report_Pn_energy_", family, ".html", sep = ''))
+  
+  ### RSD/SD vs. MSF
+  rmarkdown::render('analysis-MSF-SD-RSD.Rmd', 
+                    output_file =  paste("OUT/report_MSF_SD_RSD_", family, ".html", sep = ''))
+  
+
   ### RMSD
   rmarkdown::render('analysis-structure.Rmd', 
                     output_file =  paste("OUT/report_structure_CA_", family, "_", enm, "_R0_", R0, ".html", sep = ''))
   
   ### RMSD - SEQUENCE
-  rmarkdown::render('analysis-structure-CN-WCN-exp-2.Rmd', 
+  rmarkdown::render('analysis-structure-CN-WCN-exp.Rmd', 
                     output_file =  paste("OUT/report_structure_CN_WCN_", family, ".html", sep = ''))
   
   ### Pn
@@ -90,10 +99,6 @@ for (f in (1:nrow(input))) {
   ### RMSD
   rmarkdown::render('analysis-structure.Rmd', 
                     output_file =  paste("OUT/report_structure_CM_", family, "_", enm, "_R0_", R0, ".html", sep = ''))
-  
-  ### RMSD vs CN-WCN
-  rmarkdown::render('analysis-structure-CN-WCN.Rmd', 
-                    output_file =  paste("OUT/report_structure-CN-WCN_CM_", family, "_", enm, ".html", sep = ''))
   
   ### MSF
   rmarkdown::render('analysis-dynamical-MSF-structure.Rmd', 
